### 2013-10-09 hps-testrun-nim.tex
Initial tex commit

%% This is file `elsarticle-template-1-num.tex',
%%
%% Copyright 2009 Elsevier Ltd
%%
%% This file is part of the 'Elsarticle Bundle'.
%% ---------------------------------------------
%%
%% It may be distributed under the conditions of the LaTeX Project Public
%% License, either version 1.2 of this license or (at your option) any
%% later version.  The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.2 or later is part of all distributions of LaTeX
%% version 1999/12/01 or later.
%%
%% The list of all files belonging to the 'Elsarticle Bundle' is
%% given in the file `manifest.txt'.
%%
%% Template article for Elsevier's document class `elsarticle'
%% with numbered style bibliographic references
%%
%% $Id: elsarticle-template-1-num.tex 149 2009-10-08 05:01:15Z rishi $
%% $URL: http://lenova.river-valley.com/svn/elsbst/trunk/elsarticle-template-1-num.tex $
%%
%%\documentclass[preprint,12pt]{elsarticle}

%% Use the option review to obtain double line spacing
%% \documentclass[preprint,review,12pt]{elsarticle}

%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
%% for a journal layout:
%% \documentclass[final,1p,times]{elsarticle}
%% \documentclass[final,1p,times,twocolumn]{elsarticle}
%% \documentclass[final,3p,times]{elsarticle}
 \documentclass[final,3p,times,twocolumn]{elsarticle}
%% \documentclass[final,5p,times]{elsarticle}
%% \documentclass[final,5p,times,twocolumn]{elsarticle}

%% if you use PostScript figures in your article
%% use the graphics package for simple commands
%% \usepackage{graphics}
%% or use the graphicx package for more complicated commands
%% \usepackage{graphicx}
%% or use the epsfig package if you prefer to use the old commands
%% \usepackage{epsfig}

%% The amssymb package provides various useful mathematical symbols
\usepackage{amssymb}
%% The amsthm package provides extended theorem environments
%% \usepackage{amsthm}

%% The lineno packages adds line numbers. Start line numbering with
%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
%% for the whole article with \linenumbers after \end{frontmatter}.
%% \usepackage{lineno}

%% natbib.sty is loaded by default. However, natbib options can be
%% provided with \biboptions{...} command. Following options are
%% valid:

%%   round  -  round parentheses are used (default)
%%   square -  square brackets are used   [option]
%%   curly  -  curly braces are used      {option}
%%   angle  -  angle brackets are used    <option>
%%   semicolon  -  multiple citations separated by semi-colon
%%   colon  - same as semicolon, an earlier confusion
%%   comma  -  separated by comma
%%   numbers-  selects numerical citations
%%   super  -  numerical citations as superscripts
%%   sort   -  sorts multiple citations according to order in ref. list
%%   sort&compress   -  like sort, but also compresses numerical citations
%%   compress - compresses without sorting
%%
%% \biboptions{comma,round}

% \biboptions{}

% HPS stuff
%\usepackage{multicol}
\newcommand{\Aprime}{A$^\prime$}
\newcommand{\ee}{e$^+$e$^-$}

\journal{Nuclear Physics B}

\begin{document}

\begin{frontmatter}

%% Title, authors and addresses

%% use the tnoteref command within \title for footnotes;
%% use the tnotetext command for the associated footnote;
%% use the fnref command within \author or \address for footnotes;
%% use the fntext command for the associated footnote;
%% use the corref command within \author for corresponding author footnotes;
%% use the cortext command for the associated footnote;
%% use the ead command for the email address,
%% and the form \ead[url] for the home page:
%%
%% \title{Title\tnoteref{label1}}
%% \tnotetext[label1]{}
%% \author{Name\corref{cor1}\fnref{label2}}
%% \ead{email address}
%% \ead[url]{home page}
%% \fntext[label2]{}
%% \cortext[cor1]{}
%% \address{Address\fnref{label3}}
%% \fntext[label3]{}

\title{The Heavy Photon Search Test Detector}

%% use optional labels to link authors explicitly to addresses:
%% \author[label1,label2]{<author name>}
%% \address[label1]{<address>}
%% \address[label2]{<address>}

\author[label1]{Per Ledin}
\ead{contact@hps.discovery.com}
%\author[slac]{Per Hansson Adrian\corref{cor1}}
%\ead{phansson@slac.stanford.edu}
%\author[slac]{Timothy K. Nelson}
%\address[slac]{SLAC National Accelerator Laboratory, 94025, Menlo Park, CA, USA}
\address[label1]{Lule\aa~Hockey}

\begin{abstract}
Recent astrophysical data motivates searches for a massive, dark sector analog to the photon. The 
preferred parameter space for this "heavy photon" requires very high luminosity for direct production, 
favoring fixed target experiments, and results in long-lived decays of these new force carriers to pairs of 
light, charged fermions.  Identification of these states on large backgrounds requires precision tracking and 
vertexing at high rates in a difficult experimental environment. The Heavy Photon Search, or HPS, 
proposes a novel silicon tracking and vertexing detector, the HPS Silicon Vertex Tracker (SVT), to search 
for these states in a fixed target experiment at Thomas Jefferson National Accelerator Facility (JLab). 
The HPS SVT employs actively cooled silicon 
microstrip sensors with fast readout directly downstream of a target and inside of a dipole magnet to 
instrument a large acceptance with a relatively small detector. The readout is triggered by a fast, 
radiation-hard, compact, lead tungstate electromagnetic calorimeter.  As a first step; a simpler, small scale 
version of this detector has been assembled and operated on beam at JLab. A detector description and 
results on multiple Coulomb scattering models are outlined in this paper.
\end{abstract}

\begin{keyword}
%% keywords here, in the form: keyword \sep keyword
silicon microstrips \sep tracking  \sep vertexing \sep heavy photon \sep electromagnetic calorimeter
%% MSC codes here, in the form: \MSC code \sep code
%% or \MSC[2008] code \sep code (2000 is the default)

\end{keyword}

\end{frontmatter}

\tableofcontents
\clearpage
\newpage
\newpage

%%
%% Start line numbering here if you want
%%
% \linenumbers

%% main text
\section{Introduction}
\label{introduction}
One of the more striking anomalies in recent astrophysical observations is an excess of high energy electrons and positrons consistent with a large, unknown source of pair production~\cite{Adriani:2008zr}\cite{FermiLAT:2011ab}. The existence of a massive, hidden sector vector boson; a ``dark photon;" that mixes kinetically with the Standard Model photon and mediates annihilation or decay of dark matter particles is a theoretically attractive explanation of this cosmic-ray excess~\cite{Holdom:1985ag}\cite{ArkaniHamed:2008qn}.
\begin{center}
{\small
\begin{figure*}[ht]
    \includegraphics[width=0.8\textwidth]{figures/hps_testrun_rendering}
\caption{Rendering of the HPS Test apparatus installed on the beam line. SHOULD FIND A PIC WITH LOWER HEIGHT.}
\label{fig:testrundetector}
\end{figure*}
}
\end{center}

There are two necessary parameters that determine the properties of this ``heavy photon," designated the 
\Aprime.  The first is the mixing of this state with the Standard Model photon, $\epsilon$, which results in 
a coupling of the \Aprime to Standard Model fermions with a strength of $\epsilon e$.  In simple models 
with kinetic mixing, $\epsilon$ is favored to be in the range of $10^{-2} -10^{-5}$.  The second is the mass 
of the \Aprime.  Under the assumption that this mass is generated via a Higgs-like symmetry breaking, 
the mass would be roughly of the order $\sqrt{\epsilon} m_W \sim$~MeV-GeV.  These ranges are further 
motivated by explanations of other dark matter anomalies involving non-minimal dark sectors~
\cite{TuckerSmith:2001hy} and the fact that no similar excess in proton-antiproton pairs is observed, which 
would be simply explained if $ m_{\textrm{A}^\prime} < 2m_p$~\cite{Adriani:2010rc}.

Searches for these heavy photons with high-intensity, fixed target experiments offer the best sensitivity in 
this region of the parameter space~\cite{Bjorken:2009mm}.  In these experiments, an \Aprime is 
radiated off the incident electron, much like a bremsstrahlung photon, which subsequently decays to a pair 
of Standard Model fermions.  However, achieving sensitivity to this parameter space presents a number of 
challenges.  At larger couplings, large data samples are required to identify a small invariant mass peak on 
significant background.  At smaller couplings, the  \Aprime becomes long-lived, which enables 
sensitivity from extremely high-luminosity beam-dump experiments that screen out the Standard Model 
backgrounds.  However, in the intermediate region, lifetimes are too short to screen out backgrounds with a 
shield, but signal cross sections are so small that collecting large enough event samples to distinguish the 
signal requires unacceptable data rates or running times.  Gaining sensitivity to this region requires a fast 
detector capable of precision mass reconstruction of \Aprime final states together with the best possible 
rejection of prompt vertexes to eliminate backgrounds. The HPS experiment aims to achieve these goals 
by placing a compact silicon and vertexing detector ($\approx 1$ m long) immediately downstream ($
\approx 10$ cm) of a thin target ($\approx0.25$ X$_0$ tungsten) and inside of a dipole magnet ($\approx 
1$ T)~\cite{HPS_proposal_2010}.

The HPS Test run was proposed to DOE early in 2011 as the first stage of the HPS experiment. Its
purposes included demonstrating that the apparatus and data acquisition systems are feasible and
that the trigger rates and occupancies encountered in electron-beam running are as simulated.  It also
provided valuable experience to the HPS Collaboration in all aspects of designing, building, installing,
and running the experiment at JLab. Furthermore, in the case that HPS Test detector met all of the 
performance goals and was given dedicated running time with an electron beam, the HPS Test Run 
could provide new sensitivity to heavy photons. The HPS Test apparatus was installed on April 19, 2012, 
and 
ran parasitically with the HDice experiment, using a photon beam, until May 18. The JLab run schedule 
precluded any dedicated electron beam running, but the HPS Test Run was allowed a short and valuable
dedicated run with the photon beam.

This paper reviews the HPS Test Run apparatus, a simplified version of that 
planned for the full HPS experiment, and demonstrates the feasibility of the detector
technologies proposed for silicon tracker, ECal, and data acquisition systems. It documents the
performance of the trigger, data acquisition, silicon tracker, and ECal
and shows that the performance assumed in calculating the physics reach of the experiment is realistic.
Of particular importance, data from dedicated photon beam running has been used to compare
the observed trigger rates with that expected in simulation. The trigger rate is almost entirely due to
photons which have converted to \ee upstream of HPS and is sensitive to the multiple
Coulomb scattering of electrons and positrons in the conversion target.  Since scattered primary beam is 
the dominant 
source of occupancy in running HPS in an electron beam, good agreement between data and simulation 
confirm the background simulation used to benchmark the physics reach of the HPS experiment.

The very small signal rate compared to the large background, the need to fully reconstruct the final states of 
the electron and positron and doing it in a dense radiation environment millimeters from a high-current beam place stringent requirements on the detector, which should have,
\begin{itemize}
\item large and uniform acceptance in the forward region to catch boosted decay products,
\item excellent reconstruction efficiency for electron and positrons  with energy down to $XXXX$~MeV,
\item good momentum resolution to separate a promptly decaying \Aprime signal from the irreducible background,
\item excellent vertex resolution along the beam line direction to search for displaced \Aprime decays,
\item low-noise electronics with event timing resolution down to 2~ns, 
\item a flexible, redundant and efficient trigger selecting electron and positron pairs at rates up to 50kHz,
\item an online computing framework and data acquisition capable of handling event rates of 50~kHz and 
bandwidths of 100~MB/s to permanent storage,
\item detector components that can survive and efficiently operate in a high radiation environment with 
local doses exceeding $XXXX$~MRad
\end{itemize}

\section{Detector Overview}
\label{detector}
The HPS experiment is proposed to run in Hall B at JLab using the CEBAF electron beam. This electron 
beam is delivered at 499 MHz at energies ranging from 1.1 GeV to 5.5 GeV and currents up to 800 nA.  An 
energy upgrade to be completed in 2014 doubles this range. The HPS Test apparatus was designed as a 
first step of a multi-stage approach 
to the HPS experiment. The primary goal was to demonstrate that the technology and design approach 
chosen by HPS was sound for running in the challenging environment. Nevertheless, a secondary but 
important aspect was that, after proving the technical concepts,  the apparatus would have the 
capability to discover \Aprime events. The implication was that the design of the HPS Test apparatus 
would be subject to almost the same constraints and requirements as the full experiment.
The kinematics of \Aprime production 
typically results in final state particles within a few degrees of the incoming beam, especially at low 
$m_{\textrm{A}^\prime}$.  Because of this, the apparatus must accommodate passage of the beam 
downstream of the target and operate as close to that beam as possible.  Because background rates in this 
region from the scattered beam are very large, a fast trigger and excellent time tagging of hits are required 
to select interesting data and reduce the bandwidth required to transfer data from the detector. This method 
of background reduction is the motivation for operating HPS in a nearly continuous beam: in a beam with 
large per-bunch charge, background from a single bunch would fully occupy the detector at the required 
beam intensity. At masses below $2 m_\mu$ only decays to electrons are allowed, so the key trigger 
comes from a lead-tungstate calorimeter with 250~MHz readout.  
%Above the di-muon threshold, a 
%downstream muon detector completes the trigger acceptance and may allow triggering for pion final states 
%required for sensitivity near the $\rho$ mass.

The HPS Test apparatus, a simplified version of that 
planned for the full HPS experiment, demonstrates the feasibility of the detector
technologies proposed for silicon tracker, electromagnetic calorimeter, and data acquisition systems. 
A rendering of the HPS Test apparatus installed on the beam line is shown in 
Fig.~\ref{fig:testrundetector}.
Most technologies used in the HPS Test apparatus will be used in the HPS detector with some 
improvements to each of the systems; both from lessons learned during running of the HPS Test but 
also from less schedule and budget constraints.

\subsection{Detector Components}
An overview of the coverage, segmentation and performance of the HPS Test detector is given in Tab.~\ref{tab:detector-overview}.

%\begin{multicols}{2}
\begin{center}
\begin{table*}[t]
{\small
\caption{Overview of the coverage, segmentation and performance of the HPS Test detector. }
\begin{tabular}{lccccccc}
\hline 
System & Coverage & \# channels & ADC & Time resolution & \# layers & Segmentation & Performance \\
 & (mrad) &  & (bit) & (ns) &  &  &  \\
\hline
SVT & $15<\theta_{y} < XXXX$ & 12800 & 14 & $\approx 2$~ns & 5  & $\approx 120~\mu$m $r-\phi$ & $\sigma_{d0,y}  \approx 100~\mu$m \\
& &  &  &  & (stereo layers) & $\approx 6~\mu$m $z$ & $\sigma_{d0,x} \approx 300~\mu$m \\
& &  &  &  &  &  & $\sigma_{d0,z}\approx 1$~mm \\
\hline
ECal & $15<\theta_{y} < XXXX$ & 442 & 12 & 4~ns & 1 & $1.3\times1.3$~cm$^2$  & $\sigma(E)/E \approx 4.5\%$ \\ 
 &  &  &  &  &  & $1.6\times1.6$~cm$^2$  &  \\ 
\hline
\end{tabular}
\label{tab:detector-overview}
}
\end{table*}
\end{center}
%\end{multicols}

The silicon tracking and vertexing detector for HPS Test, or SVT, operates in an existing vacuum chamber 
inside the pair spectrometer analyzing magnet in Hall B at JLab.  The design principles of the SVT are 
described in further detail in the HPS Test Run Proposal  \cite{HPS_tPROP}. There are five measurement 
stations, or ``layers,'' placed immediately downstream of the target. Each layer comprises a pair of closely-
spaced planes and each plane is responsible for measuring a single coordinate, or ``view.'' Introduction of 
a stereo angle between the two planes of each layer provides three-dimensional tracking and vertexing 
throughout the acceptance of the detector with one redundant layer.

In order to accommodate the dead zone, the SVT is built in two halves that are mirror reflections of one 
another about the plane of the nominal electron beam.  Each half consists of five double-sided modules 
mounted on a support plate that provides services to the modules and allows them to be moved as a group 
relative to the dead zone. Each module places a pair of silicon microstrip sensors back-to-back at a 
specified stereo angle with independent cooling and support.

\subsection{Electronics, Trigger, Data Acquisition and Online Computing}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{The CEBAF Accelerator and Its Impact on the HPS Test Detector }
\label{cebaf}
\subsection{The CEBAF Accelerator}

\subsection{The HPS Test Beamline}
In Figure \ref{fig:hpstest_layout}, the layout of the parasitic run is shown. The silicon vertex tracker was installed inside the Hall B pair spectrometer magnet vacuum chamber with the electromagnetic calorimeter mounted downstream.
Both the tracker and the ECal were retracted off the beam plane to allow clean passage of the photon beam through the system.

\begin{figure}[ht]
    \includegraphics[width=0.5\textwidth]{figures/HPS_dimensions}
\caption{\small{Layout of the HPS parasitic run.} }
\label{fig:hpstest_layout}
\end{figure}

For dedicated HPS running the photon beam was generated in the interaction of the $5.5$ GeV electrons with a gold radiator of $10^{-4}$ r.l., located $\approx 8$ meters upstream of the PS pair converter. After collimation ($D=6.4$ mm), the photon beam passes through the pair converter and through the HPS system. The converter was located $\approx 77$~cm upstream of the first layer of the silicon vertex tracker. Data were taken on different converters (empty, $1.8\times 10^{-3}$ r.l., $4.5\times 10^{-3}$ r.l., and $1.6\times 10^{-2}$ r.l.). These measurements were repeated for the reverse field setting of the pair spectrometer dipole.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Silicon Vertex Tracker}
\label{svt}

The principle purpose of the HPS Test Silicon Vertex Tracker (SVT) is the efficient detection of 
charged particles and reconstruction of their momentum and angles. The precise measurements 
forms the primary input to the extraction of a signal from \Aprime decays; both from the precise 
measurement of the invariant mass of it's \ee decay products and the position of it's decay vertex 
downstream of the target. Track reconstruction is also important for energy scale calibration of the 
electromagnetic calorimeter due to the better momentum resolution of tracks compared to clusters 
in the calorimeter.

\subsection{SVT Requirements and Constraints}
%The primary goal was to demonstrate that the technology and design approach 
%chosen for the SVT was sound for running in the challenging environment at JLab. 
%Nevertheless, a secondary but 
%important aspect was that, after proving the technical concepts,  the apparatus would have the 
%capability to discover \Aprime events. The implication was that the design of the SVT in the 
%HPS Test apparatus would be subject to almost the same constraints and requirements as the full 
%experiment except for certain aspects regarding longevity and robustness subject to cost, beam time 
%and construction and design time constraints for the Test run.

The design of the SVT presents a number of significant challenges.  First, the A$^\prime$ decay products 
have momenta in the range of 1 GeV, so multiple scattering dominates mass and vertexing errors for any 
possible material budget.  Therefore, the construction of the SVT must place the smallest amount of 
material in the tracking volume.  Second, the signal yield for long-lived A$^\prime$ will be very small, so 
the rejection of prompt vertexes must be exceedingly pure, on the order of $10^{-7}$, in order to eliminate 
all prompt backgrounds.  This requires great care in design, calibration, and operation of the detector. 
Finally, the passage of degraded primary beam through the apparatus creates a region of extreme 
occupancy and radiation that is critical for sensitivity to low-mass A$^\prime$ that have decay products 
nearly collinear with the beam.  This places low-mass acceptance in opposition to tracking and vertexing 
purity and the longevity of the detector.

It is this last challenge that has the most interesting and obvious impacts on the design of the SVT. To 
achieve good vertexing performance, the first layer must be placed no more than about 10 cm downstream 
of the target. At that distance, it is found that the active region of a sensor can be placed as close to 1.5 mm 
from the center of the beam, defining a 15 mrad ``dead zone" in the detector around the plane of the 
primary beam. At the edge of this ``dead zone," the radiation dose approaches $10^{15}$ electrons/cm
$^2$/month, or roughly $3 \times 10^{13}$ 1 MeV neutron equivalent/cm$^2$/month, as shown in Fig.~
\ref{fig:radiation} and~\ref{fig:rates}~\cite{Rashevskaya:2002nd}. 
%===================
\begin{figure}[htp]
\includegraphics[width=7cm]{figures/radiation}
\label{fig:radiation}
\caption{Electron fluences: electrons bend towards $+x$.}
\end{figure}
\begin{figure}[htp]
\includegraphics[width=7cm]{figures/rates}
\label{fig:rates}
\caption{The environment near the dead zone 10 cm from the target.}
\end{figure}
%\begin{figure}[htp]
%\subfigure[\label{fig:rates}The occupancy in an 8 ns window in 60 micron strips.]
%{\includegraphics[width=8cm]{figures/rates}}
%\subfigure[\label{fig:radiation}Electron fluences: electrons bend towards $+x$.]
%{\includegraphics[width=7cm]{figures/radiation}}
%\subfigure[\label{fig:rates}The occupancy in an 8 ns window in 60 micron strips.]
%{\includegraphics[width=8cm]{figures/rates}}
%\caption{The environment near the dead zone 10 cm from the target.}
%\end{figure}
%===================
This requires the sensors to be actively cooled. Meanwhile, very low-energy delta rays from beam gas interactions multiply the density of background hits, so the SVT must operate inside the beam vacuum.  Finally, in order protect the sensors, the detector must be movable so that it can be retracted during periods of uncertain beam conditions.

%To summarize the SVT must:
%\begin{itemize}
%\item have a uniform acceptance in the forward region; up to $\theta_y=XXXXmrad$ and as close as 
%possible to the beam axis to catch boosted decay products,
%\item >95\% reconstruction efficiency for electron and positrons  with energy down to $XXXX$~MeV,
%\item momentum resolution of XXXX\% to separate a promptly decaying \Aprime signal from the irreducible background,
%\item vertex resolution $<XXXX$~mm along the beam line direction to search for displaced \Aprime decays,
%\item event timing resolution down to 2~ns, 
%\item sustain a occupancy of up to 1\%, trigger rates of $\approx50$~kHz and data rates up to 100~MB/s,
%\item survive and efficiently operate after $1\times10^{14} neutron eq. fluence,
%
%dosedetector components that can survive and efficiently operate in a high radiation environment with 
%local doses exceeding $XXXX$~MRad
%\end{itemize}

\subsection{SVT Layout}

A realistic simulation of the detector using the java-based org.lcsim package and including full backgrounds has been used to optimize the layout for acceptance, tracking efficiency, mass resolution and prompt vertex rejection~\cite{Graf:2011zzc}. The layout of the SVT is summarized in Table~\ref{tab:trk} and shown in Figure~\ref{fig:tracker_model}.

The layout of the SVT is shown in Fig.~\ref{fig:tracker_model} and summarized in Table \ref{tab:trk}. The 
vacuum chamber is too small vertically to accommodate 90-degree stereo layers to optimize the vertex 
resolution. Instead, 100~mrad stereo is used in the first three layers 
to provide higher-resolution 3-D space points for vertexing. The 50~mrad stereo of the last two layers 
breaks the tracking degeneracy of having five identical layers and minimizes fakes from ghost hits, 
improving pattern recognition while still providing sufficient pointing resolution into the third layer
 for robust hit 
association in the denser environment there. Altogether, this layout comprises 20 sensors and hybrids and 
100 APV25 chips for a total of 12780 readout channels. 
%=======================
\begin{center}
\begin{table}[ht]
{\small
\begin{tabular}{lccccc}   
\hline \hline 
    Layer & 1 & 2 & 3 & 4 & 5 \\      
\hline
    $z$ from target (cm)  & 10 & 20 & 30 & 50 & 70  \\ 
    Stereo angle (mrad)  & 100 & 100 & 100 & 50 & 50 \\ 
    Bend res. ($\mu$m)  & $\approx$60 & $\approx$60 & $\approx$60 & $\approx$120 & $\approx$120  \\ 
    Non-bend res. ($\mu$m)  & $\approx$6 & $\approx$6 & $\approx$6 & $\approx$6 & $\approx$6  \\ 
    \# of sensors  & 4 & 4 & 4 & 4 & 4  \\ 
    Dead zone (mm) & $\pm1.5$  & $\pm3.0$  & $\pm4.5$  & $\pm7.5$  & $\pm10.5$  \\ 
    Power cons. (W) & 6.9 & 6.9 & 6.9 & 6.9 & 6.9 \\
\hline \hline
\end{tabular}
\caption{Layout of the HPS Test SVT.  Note the elimination of one layer and 90-degree stereo, and the use of only small, single-sensor-sized double-sided modules both above and below he dead zone. }
}
\label{tab:trk} 
\end{table}
\end{center}
%=======================
\begin{center}
\begin{figure}[htp]
    \includegraphics[width=7cm]{figures/HPS_nochamber}
\caption{A rendering of the Test SVT showing the modules on their support plates held by the hinged C-support on the left and the motion levers on the right. The sensors are shown in red and the hybrids in green. The beam enters from the right through a vacuum box with flanges for services. }
\label{fig:tracker_model}
\vspace*{-5mm}
\end{figure}
\end{center}
%=======================
The Test SVT is built in two separate halves that are mirror reflections of one another about the plane of the 
nominal electron beam.  Each half consists of five, double-sided modules mounted on a support plate that 
provides services to the modules and allows them to be moved as a group relative to the dead zone. The 
two halves of the tracker are connected to hinges mounted on a C-shaped support just beyond layer 5 that 
defines the nominal spacing between the upper and lower halves of the tracker.  A shaft attached to each 
support plate in front of layer 1 extends upstream and connects to a linear shift that transfers motion into the 
vacuum box through bellows to open and close the tracker around the dead zone. The C-support is 
mounted to an aluminum baseplate that defines the position of the SVT with respect to the vacuum 
chamber. Figure~\ref{fig:tracker_halves} shows a photograph of both completed detector halves prior to 
final assembly. 
%=======================
\begin{figure}[htp]
\begin{center}
    \includegraphics[width=7cm]{figures/2012-101-PHOTON-DETECTOR-001}
\caption{\small{Both halves of the HPS Test SVT after final assembly at SLAC.  The cooling manifolds and 
integrated cable runs are clearly seen.} }
\label{fig:tracker_halves}
\end{center}
\vspace*{-5mm}
\end{figure}
%=======================

\subsection{SVT Components}

\subsubsection{Silicon Sensors}
The sensors for the SVT are selected according to a number of requirements.  First, the sensors must be 
radiation tolerant to approximately $1.5\times10^{14}$ 1 MeV neq/cm$^2$ for a six month run.  This 
corresponds to about 4 MHz/mm$^2$, so the sensor and readout technology must be capable of handling 
very high local occupancies. Since sensitivity is limited by multiple scattering, a material budget of less 
than 1\% $X_0$/layer is imperative and far less is desirable.  The best vertex resolution with a small beam 
spot ($\approx 10 \mu$m) requires single-hit resolution better than 20 $\mu$m in both measurement 
coordinates.  Finally, the sensor technology must be mature and readily available at low cost.  Surprisingly, 
we find that silicon microstrips are the best match to these requirements, and a supply of appropriate 
microstrip sensors purchased from the Hamamatsu Photonics Corporation for the Run 2b upgrade of D\O~
\cite{Denisov:2001aa} are readily available. These are $p+$ on $n$, single sided, AC coupled, polysilicon-
biased sensors fabricated on $<100>$ silicon and have 30(60) micron sense(readout) pitch over their 4 cm 
$\times$ 10 cm surface. Although a maximum bias of 350 V is specified, the vast majority are operable to 
1000V and therefore remain fully depleted to a dose of approximately $1.5\times10^{14}$ 1 MeV neq/cm
$^2$.

\subsubsection{Front-end Electronics}

Because the regions of high occupancy are small spots in two dimensions, only a short length of any one 
strip sees significant occupancy, and the strips in that region act as long pixels. However, the rates are still 
very high and lowering the peak occupancy in the sensors to approximately 1\% for tracking requires a 
trigger window and tagging of hit times to roughly 8 ns, as shown in Figure~\ref{fig:rates}.  The FADC 
readout for the ECal and muon system are capable of this, but achieving achieving $2\sigma$ efficiency for 
silicon hits then requires 2 ns time resolution for the hits in the SVT. This performance can be achieved with 
the APV25 readout ASIC developed for the CMS experiment at CERN~\cite{French:2001xb}.  When 
operated in ``multi-peak mode", the APV25 captures successive samples of the output of the shaper in sets 
of three.  By fitting the known $CR$-$RC$ shaping curve to these samples, the initial time of the hit can be 
determined to a precision of 2 ns for S/N$>$25, an achievable figure with our sensors if read out 
individually~\cite{Friedl:2009zz}.  For the SVT, six-sample readout and the shortest possible shaping time 
(35 ns) will be used to best distinguish hits that overlap in time.
The APV25 chips are hosted on simple FR4 hybrids since these hybrids and their cooling system are 
outside the tracking volume.  Along with the sensors, these are assembled into large multi-sensor modules, 
one for each tracking view.

\subsubsection{Support Structure}

The sensor modules for the SVT consist of a pair of identical half-modules, sandwiched back-to-back around an aluminum cooling block at one end and a similar PEEK spacer block at the other. Figure \ref{fig:tracker_module} shows a prototype module assembly.
%=======================
\begin{figure}[htp]
	\begin{center}
   	 \includegraphics[width=7cm]{figures/IMG_5200}
	\caption{\small{A prototype module assembly (foreground) with the 50 mrad (left) and 100 mrad (right) module assembly fixtures in the background.  A pair of cooling blocks and a spacer block can be seen on the fixtures.} }
	\label{fig:tracker_module}
	\end{center}
\vspace*{-5mm}
\end{figure}
%=======================
The cooling block provides the primary mechanical support for the module as well as cooling via copper 
tubes pressed into grooves in the plates. The spacer block defines the spacing between the sensors at the 
far end of the module, stiffens the module structure, and improves the stability of the sensor alignments.

The total power consumption of the five APV25 chips mounted on 
the hybrid readout board is about 2~W. Since heating from the leakage current is only significant at a 
single small spot on the sensor, the 
dominant heat load on the sensor, event after irradiation, is radiant heat from the inside wall of the vacuum 
chamber, less than 0.5~W per sensor. The total power consumption budget of about 40~W is removed by a 
water/glycol mixture circulated through a flexible manifold attached to the cupper tubes in the cooling blocks. The total mass flow is about XXXXg/s to operate the sensors at XXXX degrees C.

Each half module consists of a single sensor and a hybrid electronic readout board glued to a 
polyamide-laminated carbon fiber composite backing.  A window is machined in the carbon fiber leaving 
only a frame 
around the periphery of the silicon to minimize material. A 50~$\mu$m sheet of polyamide is laminated to 
the surface of the carbon fiber with 1 mm overhang at all openings to ensure good isolation between the 
backside of the sensor, carrying high-voltage bias, and the carbon fiber which is held near ground.  The 
average support material in the tracking volume is approximately 0.06\% $X_{0}$ per double-sided module 
for a total of 0.7\% per layer.

\subsection{SVT Digitization, Event Building and Data Transmission}
\label{sec:svt_daq}
The SVT Data Acquisition (DAQ) is a SLAC-standard system using consisting of a single ATCA crate with 
two Cluster On Board (COB) cards and a 10~Gb/s switch~\cite{Larsen:2011zb}.  
The COBs connect to Rear Transition 
Modules (RTM) housing 14-bit ADCs that accept input data from the APV25 chips.  
The COB house FPGA-based 
Data Processing Modules (DPM) and the Trigger Interface (TI) to the ECal trigger.  This system is capable 
of 20~kHz operation, whereas upgrades for the full experiment pushes this up to 50~kHz. 
Power is provided to each hybrid using CAEN power supplies from the decommissioned CDF SVXII 
detector.

{\bf  This needs to be expanded. I should talk about the data reduction and event handling. }

\subsection{Production, Assembly and Shipping}

Hybrid readout boards and half-modules were assembled at SLAC.  Mounting APV25 chips and all 
wirebonding and QA testing were performed at Univerity of California, Santa Cruz. Of the sensors tested 
during production, 90\% were 
capable of 1000~V bias. Hybrids underwent quick QA testing and each half-module was run at low 
temperature ($\approx5^{\circ}$ C) and fully characterized for pedestals, gains, noise and time response 
after assembly.  All 29 production modules were assembled between mid-February and the end of March, 
2012.  Module yields were excellent for such a small production.  Of 165 APV chips acquired, 150 were 
used to assemble 30 production hybrids, of which 29 passed QA testing.  Of 29 modules built, 28 passed 
QA testing, leaving 8 spare modules after completion of the SVT.  Full-module assembly and 
mechanical surveys were performed at SLAC in early April 2012 before final assembly, testing and 
shipping of the SVT to JLab on April 11.  A custom shipping container, based on experience 
at FNAL~\cite{shipping}, was built in order to safely send the partly assembled of the SVT. The two fully 
assembled SVT halves were attached to a baseplate supported by four wire-rope isolators. This plate, 
covered by a clean lexan cover was mounted inside an inner box surrounded by 4 inches of Polyurethane 
foam to complete the two-spring construction. At JLab, the entire SVT was integrated with the full DAQ and 
the power supplies for the first time in the cleanroom, before moving the module-loaded support plates to 
Hall~B for final mechanical assembly and installation inside of the vacuum chamber on April 19.

\subsection{Monitoring and Calibration}

\subsection{Data Analysis and Performance}

During the duration of the dedicated photon run all SVT modules and APV25 
readout chips were configured to their nominal operating 
points~\cite{Jones:1069892} while all sensors were reverse-bias at 180~V.  The 
sensors were operated within a temperature range of  20 to 24$^\circ$C 
throughout the test run. Multiple calibration runs established a noise level of $\approx$ 750 - 850 electrons  
which was stable across the SVT modules.

Throughout the duration of the test run, approximately 97\% of the 12,780 SVT channels were found to be 
operating normally. The fraction of dead or noisy channels varied from 2.4\% to 4.7\%; 
most of these were due to misconfigured readout chips (2--4 misconfigured chips out of 100 total) 
a known noisy half-module, and a couple of known noisy readout chips.

\subsubsection{Cluster and Hit Reconstruction}
After a trigger is received, six samples of the corresponding output of the APV25 shaper circuit are digitized. 
The samples from every channel on a sensor surviving the 
data reduction, described in Sec.~\ref{sec:svtdaq}, are the basis for offline hit reconstruction. 
The six samples of the APV25 pulse shaper output 
are fitted to an ideal $CR-RC$ function to extract the amplitude and the $t_0$ of the hit. 
The typical pulse shape obtained is shown in Figure~\ref{fig:pulse_shape} also demonstrates that the SVT 
was well timed in to the trigger with the rise of the pulse at the 3rd sampling point.
\begin{figure}[h]
	\begin{center}
	\includegraphics[width=6cm]{figures/08062012_run1351_samples_vs_amplitude}
    	\caption{{\small The six pedestal subtracted samples associated with a hit on a track.}}
	\label{fig:pulse_shape}
	\end{center}
\end{figure}
These hits are passed through a simple clustering algorithm which forms clusters by grouping adjacent 
strips. The position of a cluster on the sensor is determined by a pulse height weighted mean (FIX THIS).
With a linear gain up to $\approx 3$~MIPs, the cluster charge for hits associated with a track follow 
the characteristic Landau shape as expected, see Fig.~\ref{fig:cluster_pulse}. 
\begin{figure}[h]
	\begin{center}
	\includegraphics[width=6cm]{figures/run1351_mip_small.pdf}
    	\caption{{\small The cluster charge distribution. }}
	\label{fig:cluster_pulse}
	\end{center}
\end{figure}

After clustering hits on a sensor, the hit time for each cluster is computed as the amplitude-weighted 
average of the fitted $t_0$ channel times. The $t_0$-resolution is studied by comparing the cluster hit time 
with the average of all cluster hit times, the ``track time'' which has the expected jitter due to clock phase 
and trigger $\approx 25$~ns. Figure~\ref{fig:tracktime} shows the residual to the individual cluster times. 
\begin{figure}[h]
	\begin{center}
%	\includegraphics[width=7cm]{figures/top_track_time.pdf}
	\includegraphics[width=6cm]{figures/t0_resolution.pdf}
	\caption{\small{
%	Track time distribution (left) and cluster time residual (right). The track time is measured relative to the APV25 clock. The width of the distribution is due to trigger jitter (24~ns jitter in the tracker readout clock, plus 16~ns jitter in the trigger system). 
	The cluster time residual is for a representative sensor relative to the track time.}}
	\label{fig:tracktime}
	\end{center}
\end{figure}
After correcting for offsets from each sensor (time-of-flight, clock phase) the extracted $t0$ resolution is 
2.6~ns. This is somewhat worse than the $\approx 2$~ns resolution expected which we attribute to the true 
pulse shape differing from our idealized fit function which will be improved in the future. Reducing the 
APV25 pulse shaping time will also improve time resolution. These results show that we can operate with 
the critical six sample readout mode of the APV25 chip and achieve time resolution adequate for pileup 
rejection during electron running.

While occupancy was slightly larger than expected, good agreement between data and simulation was 
found after taking into account dead or noisy channels. The hit efficiency, see Fig~\ref{fig:hit_efficiency} 
was measured to be above 98\% and fairly uniform across the SVT.
\begin{figure}[h]
	\begin{center}
    	\includegraphics[width=7cmh]{figures/hit_efficiency_vs_layer.pdf}
        \caption{{\small The hit reconstruction efficiency as a function of detector layer.}} 
	\label{fig:hit_efficiency}
	\end{center}
\end{figure}

The spatial resolution of similar microstrip sensors is well established by test beam data, against which the 
charge deposition model in the simulation is validated.  This resolution can be parameterized as a 
function of the total signal to single-strip noise (S/N) and the crossing angle of tracks through the sensor.  
The single-hit resolution for charged particles with $S/N > 20$, as demonstrated here, is relatively constant 
at approximately 6 $\mu$m for tracks that are close to normal to the sensors as in HPS.

\subsubsection{Alignment}
The SVT was aligned using a combination of optical, laser and touch probe surveys at SLAC and JLab. The 
optical survey of individual modules with precision of a few microns are combined with a touch-prove survey 
of the overall SVT support structure, with 25-100 microns precision, to locate the silicon sensor layers with 
respect to the support plates and the mechanical survey balls on the base plate.
After full assembly and installation of the SVT at JLab, a mechanical survey of the SVT base plate position 
inside the pair spectrometer vacuum chamber is used to determine the global position of the SVT with 
respect to CEBAF beam line. 
The resulting survey-based alignment has the position of the silicon sensors correct to within a few hundred 
microns a more sophisticated global track-based alignment technique to reach 
the final alignment precision is used.

\subsubsection{Momentum and Vertexing Resolution}

By selecting e$^{+}$e$^{-}$ pairs from the triggered events we are able to study basic distributions of pair production kinematics and in particular those related to our vertex performance. Pairs of opposite charge tracks, one in the top and one in the bottom half of the SVT, with larger than 400~MeV were selected. The pair production kinematics are relatively well reproduced given the alignment of the tracker; Fig.~\ref{fig:pair_kin} shows the invariant mass and ratio of electron momentum over the sum of electron and positron. 
 \begin{center}
{\small
\begin{figure*}[ht]
   \includegraphics[width=5cm]{figures/h_trk_top_px_h_trk_top_px_trigseltwotrksel4hit_recoilmc_twotrkfilt.png}
   \includegraphics[width=5cm]{figures/h_invM_h_invM_dataMC_trigseltwotrksel4hit_recoilmc_twotrkfilt.png}
   \includegraphics[width=5cm]{figures/h_sumE_h_sumE_dataMC_trigseltwotrksel4hit_recoilmc_twotrkfilt.png}
%   \includegraphics[scale=0.25]{test2012/vertexing/figures/h_ratioEsum_h_ratioEsum_dataMC_trigseltwotrksel4hit_recoilmc_twotrkfilt.png}
\caption{Kinematic distributions for e$^+$e$^-$ pairs selected by opposite charged tracks in the top and bottom half of the tracker: track momentum in the top half of the SVT (left), invariant mass (middle) and the sum of the track momentum for the pair.}
\label{fig:pair_kin}
\end{figure*}
}
\end{center}

For the vertexing 
performance the foremost difference compared to electron beam running is that the target was 
located $\sim67$~cm from our nominal target position; giving almost collinear tracks in the detector. This 
degrades the vertex resolution along the 
beam line compared to that expected in an electron beam with tracks from the nominal target position. 
Furthermore, tails of the vertex distributions are impossible to study with the finite sample of events from the 
Test Run. 
Nevertheless, useful information can still be 
obtained by studying the vertex distributions. Figure~\ref{fig:vtx_pos} shows the distance of closest 
approach of the momentum vectors extrapolated in the 
upstream direction from our analyzing magnet, taking into account the measured fringe field. 
 \begin{center}
{\small
	 \begin{figure*}[ht]
	\includegraphics[width=5cm]{figures/h_vtx_fr_x_h_vtx_x_dataMC_trigseltwotrksel4hit_recoilmc_twotrkfilt.png}
	\includegraphics[ width=5cm]{figures/h_vtx_fr_y_h_vtx_y_dataMC_trigseltwotrksel4hit_recoilmc_twotrkfilt.png}
	\includegraphics[width=5cm]{figures/h_vtx_fr_z_h_vtx_z_dataMC_trigseltwotrksel4hit_recoilmc_twotrkfilt.png}
	\caption{Vertex position represented by the distance of closest approach of the extrapolated 
	momentum vectors upstream of the analyzing magnet. The overall shift from zero in the x-direction is 
	due to a 30~mrad rotation of the SVT with respect to the beam line.}
	\label{fig:vtx_pos}
\end{figure*}
}
\end{center}

While the tails of the vertex distribution expected in electron beam running is not accessible here the 
fact that the core is relatively well described provides confidence of the description of the amount of 
material and the multiple scattering description.  These are crucial for benchmarking the physics reach of the 
HPS detector since both the mass and vertex resolution that determine the physics reach are limited by multiple scattering.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Electromagnetic Calorimeter}
\label{ecal}

The electromagnetic calorimeter just downstream of the tracker uses detectors with comparably short 
live time and high rate capability. It performs two essential functions for the experiment: triggering and 
electron identification. The device is highly segmented. It is fast, able to readout at rates comparable to 
those in the tracker, and able to provide good spatial and energy information to the trigger electronics. Like 
the tracker system, the electromagnetic calorimeter is split to avoid impinging on the “dead zone”. The beam 
and radiative secondaries pass through the calorimeter in vacuum, to avoid generating unnecessary backgrounds.

\subsection{Purpose and Design Requirements}

The electromagnetic calorimeter (ECal) provide the trigger for the data acquisition and will be used for 
electron identification during the data analysis. The ECal is positioned after the analyzing dipole 
magnet and cover the full acceptance region of the SVT. It consist of two halves, split in the horizontal 
beam plane. The gap between upper and lower parts, $XXXX$~mrad (15mrad for electron running),  
as seen from the target location, is necessary to avoid the "dead zone" where occupancy and radiation 
prevents any instrumentation to be situated.

The energy of electrons of interest will be in the range 
$0.5-6.5$~GeV. The ECal modules must have sufficient radiation lengths to absorb the full energy of these 
scattered electrons, have fine enough granularity to handle a high rate of electromagnetic 
background and survive large doses of radiation, especially near the beam plane. In addition, it needs to 
have excellent hit time resolution, $<10$~ns, in order to beat down beam backgrounds.

The compact design requirements: high radiation environment , high rate and the presence of 
high magnetic field, are fulfilled by a lead-tungstate (PbWO$_{4}$) crystal calorimeter with magnetic field 
resistant avalanche photodiode (APD) readout.  Such crystals has been operational in the inner 
calorimeter of the CLAS experiment~[XXXX] at JLab since 2005 and meet all requirements set by 
HPS. These crystals were subsequently repurposed for the ECal.

\subsection{Layout}
The modules in the ECal are arranged in two formations, as shown in Fig.~\ref{fig:ecal}. 
\begin{center}
{\small
\begin{figure*}[]
\includegraphics[width=7cm]{figures/ECal}
\includegraphics[width=7cm]{figures/ecal_assembly}
\caption{Schematic layout view of the two halves of the ECal (left) and a picture of one half being assembled before installation on beam line (right). }
\label{fig:ecal}
\end{figure*}
}
\end{center}
There are 5 layers in each formation. Each layer has $46$ crystals except for the layers closest to the beam 
plane where 9 modules were removed to allow a larger opening for the outgoing electron and photon beams. 
The ECal is mounted downstream of the analyzing dipole magnet at the distance of about $137$~cm from the 
upstream edge of the magnet. The two ECal modules are positioned just above and below the ECal vacuum 
chamber, through which the beam, radiated photons, and the wall of flame will pass
unimpeded. The innermost edge of the crystals is just $2$~cm from the beam.

\subsection{ECal Components}

\subsubsection{PbWO$_4$ Crystals}
The ECal PbWO$_{4}$ crystals, from the same crystals that were used in the IC. The IC calorimeter was assembled from 424 lead tungstate tapered crystals with dimensions of $13.3\times13.3$~mm$^2$ (front face), $16\times16$~mm$^2$ (rear face) and 160~mm length. The crystals were fabricated with very tight tolerances: $19~\mu$m for 13.3~mm dimension and $13~\mu$m for the 16~mm dimension. Each crystal is wrapped in VM2000 multilayer polymer mirror film.

\subsubsection{Support Structure}
In order to stabilize the 
calorimeter's performance, the crystals, APDs, and amplifiers are enclosed within a temperature controlled 
environment, held constant at the level of $1^\circ~$F.

\subsubsection{Avalanche Photodiode Readout and Preamplifiers}
\label{sec:apd}
Avalanche Photodiodes (APD) S8664-55 produced by Hamamatsu Corp. are used as photodetectors. 
They have a $5\times5$~mm$^2$ active area and quantum efficiency of about 75\%. Single APDs were 
centered on the back ends of the crystals using MeltMount 1.7 thermal plastic adhesive. 
The low? amplitude signals of APDs are amplified using custom?made preamplifier boards. 
Figure~\ref{fig:ecal-module} shows a schematic view of the module assembly.
\begin{center}
{\small
\begin{figure}[]
\includegraphics[width=7cm]{figures/ecal-module-schematic.png}
\caption{Schematic vied of an ECal module.}
\label{fig:ecal-module}
\end{figure}
}
\end{center}
The gain uniformity of the APDs is on the order of XXXX\%; with APD high voltage bias varying by as 
much as 100V. Since only a limited number of high voltage channels were available during the test, 10 
channels were grouped together with an attempt to group modules with similar gains.

The signals from the preamplifier boards were sent, through a $2:1$ signal splitter to a time-to-digital 
converter and the Flash ADC readout boards discussed in Sec.~\ref{sec:fadc}.

\subsection{Calibration and Performance}
\label{sec:ecal_calibration}
Of 442 modules, 39 were disabled or disconnected and were not read out by the DAQ. 
13 of these were not read out because of a shortage of FADC readout boards (see Sec.~\ref{sec:fadc}).
The remainder either had no HV bias on the APD, or were disabled in the FADC software due to noise.
In the data, we identified two types of abnormal channels. 
One FADC was not sending trigger signals correctly, resulting in low efficiency.
 This affected the 13 channels read out by that FADC. 5 channels were diagnosed as noisy because they 
 had a high incidence of hits out of coincidence with the trigger. A large number of channels were originally 
 misidentified as noisy because they had much higher hit occupancy than neighboring channels.
Gain calibration shows that these channels have high gain (and thus lower energy threshold) but are otherwise normal. The abnormal channels were ignored in analysis in order to simplify comparison with Monte Carlo. This leaves 385 useful channels---87\% of the ECal.

The noise level of the ECal modules were measured to be approximately 15~MeV. The ECal was operated 
with an effective readout threshold of 70~MeV.

Modules above thresholds are clustered using a simple robust algorithm described in Sec.~\ref{sec:trigger}.

\subsubsection{Calibration}
\label{sec:ecal_calibration}
The noise and pedestal of the readout chain are calibrated by running the ECal readout in a mode where the 
preamplifier output is sampled every 4~ns in a time window of 100 samples: by looking at a part of the 
window before the hit, we calibrate the readout channel. The The readout threshold

We calibrate gain of the individual ECal channels using the SVT measurement of track momentum and 
comparison to Monte Carlo simulation.  We disable all SVT and ECal channels in the simulation that were 
inoperable or noisy in the test run, so any efficiency or bias effects that affect the real data should be reflected 
in the simulation as well; then we use a formula to compute the ``weighted E/p'' for a crystal, representing the average E/p for clusters that include the crystal
% $\frac{\sum_j w_{j,i}}{\sum_j\frac{P_j}{E_j}w_{j,i}}$
, and iteratively adjust the gains until the weighted E/p is equal for test run data and simulation.
\begin{figure}[ht]
	\includegraphics[width=7cm]{figures/ecalgainplots_corr_sim}
	\includegraphics[width=7cm]{figures/gains}
	\caption{\small{Weighted E/p from Monte Carlo simulation (top), calibrated values of gain in units of MeV 
	per ADC count (bottom).}}
	\label{fig:gains}
\end{figure}

These gains can then be used to convert from ADC counts in a channel to the energy deposited into that ECal 
crystal.
The other information needed to find the energy of an incident particle is the sampling fraction---the ratio of 
energy read out from crystals to energy of an incident particle. The conventional sampling fraction, 
the fraction of incident energy that is deposited in crystals, is approximately 0.9  for the ECal and less at the 
edges. For our readout, there is additional energy lost because crystals under the readout threshold are not 
read out. The weighted E/p used in calibration (see Figure \ref{fig:gains}) is an approximate measurement of sampling fraction, but the sampling fraction is energy-dependent because of the effect of readout threshold. 
A full computation of sampling fraction can be done using simulation.

\subsection{Monitoring}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Trigger and Data Acquisition}
The HPS Test apparatus DAQ handles the acquisition of data for two sub-detectors: the 
SVT and ECal . It employs two DAQ architectures: the SVT is readout with Advanced 
Telecom Communications Architecture (ATCA) hardware while the ECal and Muon System use VXS based 
hardware. The trigger system receives input from the ECal and distributes a trigger signal 
to all detector sub- systems to read out a selected event.

\subsection{Electronics}
\label{sec:electronics}

\subsubsection{Flash ADC Readout Board}
\label{sec:fadc}
The analog signals from the individual APD's of the ECal (shaped and amplified as described in 
Sec.~\ref{sec:aid}) are input to a single channel on the 16-channel JLab FADC250 VXS module (FADC), 
shown in Fig. ~\ref{fig:fadc}. 
\begin{center}
{\small
\begin{figure}[t]
\includegraphics[width=7cm]{figures/FADC250_Photo_001.jpg}
\caption{A Jefferson Lab FADC250 VXS module.}
\label{fig:fadc}
\end{figure}
}
\end{center}
Three 20-slot VXS crates are needed to accommodate the system: one for each half of the ECal with 221 
channels and one for the Muon System with a total of 232 channels.

The FADCs store 12-bit digitized samples at 250~MHz in 8~$\mu$s deep pipelines. 
When a trigger is received, the appropriate part of the pipeline is accessed. If a FADC   
signal exceeds a predefined threshold within that time window, the integrated amplitude of a pre-defined 
number of samples before (NSB) and after (NSA) the signal passed threshold, in addition to the time, are 
recorded. 
%as explained in Fig.~\ref{fig:hps_trigger_data}. 
This scheme significantly compresses the data input 
to the FADC. During data analysis, a pedestal value is subtracted to obtain the actual summed energy.
The main characteristics of the FADC are:
\begin{itemize}
\item 12-bit digitizer with sampling rate of 250~Msps, 
\item 50$\Omega$ termination input, 
\item front-end input range:  -0.5V, -1V or -2V (sufficient to avoid signal clipping for large pulse heights),
\item nominal charge resolution between 10-39~fC per ADC (see Tab.~\ref{tab:charge_resolution}).
\end{itemize}
\begin{center}
{\small
\begin{table}[h]
\centering
\begin{tabular}{|c|c|}
\hline
Input range & Nominal charge resolution\\
(V) & (fC per ADC count)\\\hline
-0.5 & 9.76  \\\hline
-1.0 & 19.53  \\\hline
-2.0 & 39.06 \\\hline
\end{tabular}
\caption{Nominal FADC charge resolution for different front-end input ranges.}
\label{tab:charge_resolution}
\end{table}
}
\end{center}
As shown in Fig.~\ref{fig:hps_trigger_data}, the FADC has two parallel data paths: the readout and trigger paths. The trigger path runs continuously to report hits to the trigger system. The readout path only reports hits to the DAQ when the FADC receives a trigger.

For the readout path, every FADC has the following parameters:
 \begin{itemize}
 \item the number of samples integrated before the signal crossed threshold ($NSB$), 
 \item the number of samples integrated after the signal crossed threshold ($NSA$),
 \item the readout threshold, measured in ADC counts.
 \end{itemize}
The number of samples for a given channel integration is the sum of $NSB+NSA$ samples. It is a fixed gate width pulse integration with no pedestal subtraction where the sum is stored in a 17-bit register for readout (pedestal subtraction happens offline). 
\begin{center}
{\small
\begin{figure}[]
\includegraphics[width=7cm]{figures/hps_trigger_data}
\caption{\small{FADC data paths}}
\label{fig:hps_trigger_data}
\end{figure}
}
\end{center}
For the trigger path, every channel has, in addition to $NSB$ and $NSA$: 
\begin{itemize}
% \item number of samples integrated before the threshold crossing (NSB),
 %\item number of samples integrated after the  threshold crossing (NSA),
 \item trigger threshold, measured in ADC counts, 
 \item a pedestal, 
 \item a conversion factor (gain) that converts the ADC counts to energy in MeV (with 13 bits:  from 0 to 8191~MeV), 
 \item an energy discriminator threshold (minimum energy cutoff).
 \end{itemize}
Note that the threshold for the trigger path can be set independently from the readout threshold.
The pedestal value is subtracted from the integrated sum over $NSB+NSA$ samples and 
converted to MeV units using a supplied gain conversion factor. The energy discriminator can be used to cut 
off low energy pulses before reporting to the Crate Trigger Processor. 
The values reported to the Crate Trigger Processor are the 13-bit pulse energy and the time at which the 
pulse crossed the threshold. Data for every channel is sent every 32~ns (if there is no hit a 0 energy pulse is 
sent) which sets a worst case double pulse resolution of 32~ns for individual channels, but less if pulses 
occur in adjacent 32~ns windows.

\subsubsection{Trigger Boards}
Describe CTP and SSP?

\subsection{Trigger}
\label{sec:trigger}
The trigger system is designed to efficiently select \ee events by 
using information from the ECal . The trigger looks for time coincidences of clusters in the top and bottom half 
of the ECal.  The trigger system can be broken down into three sections (see Fig.~\ref{fig:hps_trigger_cal}):
 \begin{itemize}
 \item FADC (pulse finding): samples and digitizes the signal pulses from each detector channel. Sends the measured pulse energy and arrival time to the CTP.
\item CTP (cluster finding): groups FADC pulses from each half of the ECal into clusters. The cluster energy, arrival time, and hit pattern are sent to the SSP.
 \item SSP (cluster pair finding): searches for time coincidence of pairs of clusters from the top and bottom half of the ECal and applies topological selections.
 \end{itemize}
\begin{center}
{\small
 \begin{figure}[t]
 \includegraphics[width=7cm]{figures/hps_trigger_cal}
\caption{Block diagram of the ECAL trigger system consisting of the FADC that samples and digitizes the detector channel signals and sends them for cluster finding in the CTP. The CTP clusters are sent to the SSP where the final trigger decision is taken based on pairs of clusters in both halves of the ECal. The decision is sent to the Trigger Supervisor (TS) that generates the necessary signals to readout the sub-detectors.}
 \label{fig:hps_trigger_cal}
 \end{figure}
}
\end{center}
The time coincidence window of pairs of clusters in the top and bottom half of the ECal are programmable 
with 4~ns resolution.

As described above in Sec.~\ref{sec:fadc}, the first stage of the trigger logic is incorporated into the 
FPGA's on the FADC boards which sends crystal energy and time information to the CTP. With the available 
3-bit time information, the CTP looks for time coincidence of crystal signals with 8~ns resolution (limit is 4~ns).
The cluster finding algorithm is very fast and makes use of the parallel processing nature of FPGA's by 
simultaneously searching for 125 clusters, up to 3x3 in size, across the calorimeter crystal array and performs 
the following tasks:
\begin{itemize}
\item Adds energy from hits together for every 3x3 square of channels in ECal.
\item Hits are added together if they occur (leading edge) within a programmable number of 4~ns clock cycles of each other (HPS will use 8~ns time coincidence time interval).
\item If the 3x3 energy sum is larger than the programmable cluster energy threshold and the sum is greater than any neighboring 3x3 windows, the CTP reports the cluster parameters to the SSP. 
\end{itemize}
The CTP evaluates all hits in its half of the calorimeter every 4~ns. A programmable time window is used to 
allow hits that are out of time with each other to be considered as part of a cluster sum. This is done by 
reporting hits when they occur and then reporting them again for the next $N$ number of 4~ns clock cycles, 
where $N \in [0,7]$. This is useful to deal with skew and jitter that develop from the detector, cabling, and 
electronics. As described above, the CTP only selects the 3x3 window with the highest energy sum of its 
neighbors. This filtering is applied to deal with overlapping clusters and cases where the cluster is larger than 
a 3x3 window.

 The final trigger decision is made in the CTP and Sub-System Processor (SSP). The Trigger Supervisor generates all necessary signals and controls the entire DAQ 
system readout through the Trigger Interface (TI) units. The TI units are installed in every crate that participate 
in the readout process.

The trigger system is free-running and driven by the 250~MHz global clock and has essentially zero dead 
time at occupancies expected by HPS. The Trigger Supervisor can apply dead time if necessary, for example 
on a `busy' or `full' condition from front-end electronics. The system is designed to handle trigger rates above 
50~kHz and a latency set to $\approx 3~\mu$s to match that required by the SVT APV25 chip.

\subsubsection{Performance}
As discussed above, the trigger and DAQ integrate pulses differently to measure hit energy. The trigger 
integrates using a time-over-threshold window, and the DAQ readout integrates using a constant window 
(5 samples before and 30 samples after a threshold crossing). For every event, the trigger reports the 
trigger decision as a bit mask (top trigger, bottom trigger, or both) and the time the trigger fires.

We study trigger performance by simulating the trigger for each event and comparing to how events were 
actually triggered.
First, we simulate the FADC readout board to convert from readout hits (constant integration window) to 
trigger hits (time-over-threshold integration). We then simulate the CTP clustering algorithm and the trigger 
decision before we compare the trigger decision and trigger time reported by the simulation to what was 
reported by the real trigger.

To eliminate trigger bias in checking the trigger decision, we use a tag and probe method. To check trigger 
performance in one half of the ECal, we tag events where there was a trigger in the other half, and exactly one 
probe cluster in the ECal half under test. 
We then measure trigger efficiency (proportion of tagged events where there was a trigger) as a function of 
ADC counts and energy of the probe cluster.
These turn-on curves are shown for the top half of the ECal in Fig.~\ref{fig:turnon}. 
\begin{center}
{\small
\begin{figure}[ht]
	\includegraphics[width=7cm]{figures/top_turnon_adc}
	\includegraphics[width=7cm]{figures/top_turnon_e}
	\caption{Trigger turn-on as a function of probe cluster ADC counts (top) and probe cluster energy in MeV 
	(bottom). Both plots are for the top half of the ECal; bottom is similar. Energy is not corrected for sampling 
	fraction.}
\label{fig:turnon}
\end{figure}
}
\end{center}
The trigger threshold is seen to be 1280 ADC counts as expected. The threshold is not perfectly sharp in this 
analysis because of uncertainties in the conversion from readout to trigger hits but based on comparisons 
with Monte Carlo simulation we believe the trigger worked exactly as specified. 
The trigger threshold in terms of cluster energy is very uneven for two reasons; gain variations between 
different ECal crystals lead to threshold variations and the nonlinearity of the time-over-threshold integral 
means that the effective threshold is higher for clusters that span multiple crystals.
Overall the trigger appears to have functioned exactly as intended. Changes planned for the next run 
(constant integration window and per-crystal gain calibration constants for the trigger) will solve both of the 
issues that led to threshold variations in the test run.

\subsection{Data Acquisition and Online Computing}
For the ECal, every VXS crate contains a Readout Controller (ROC)
that collects digitized information, processes it, and sends it on to the Event Builder (EB). The ROC is a single 
blade Intel-based CPU module running DAQ software under CentOS Linux OS. For the SVT ATCA system, 
the ROC application runs on an embedded processor situated on the ATCA main board. The EB assembles 
information from the SVT, ECal and Muon System ROCs into a single event which is passed to the Event 
Recorder (ER) that writes it to a RAID5-based data storage system capable of handling up to 100 MB/s. The 
EB and other critical components run on multicore Intel-based multi-CPU servers. The DAQ network system is 
a Foundry router providing high-speed connections between the DAQ components and to the JLab 
computing facility. The SVT ROC, which must handle large data volumes, has a 10 Gbit/s link to the Foundry 
router, while a 1 Gbit/s link is adequate for the ECal and Muon System. A 10 Gbit/s uplink to the JLab 
computing facility is used for long-term storage.

The SVT DAQ is described in more details in Sec.~\ref{sec:svt_daq}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Multiple Coulomb Scattering Distributions}

Occupancies close to the beam create many of the key challenges in the HPS experiment
and determine the limits of sensitivity to low \Aprime masses.
These occupancies are dominated by electrons which have multiple Coulomb scattered (MCS) 
to relatively large 
angles in the converter. Because HPS is sensitive to scattering angles far out on the tail of the MCS 
distribution, well beyond the angles important in other experiments, care must be taken
to ensure our simulations are correct in this regime.

\subsection{Multiple Coulomb Scattering Models}

In particular,
{\sc Geant4}~\cite{Agostinelli2003250} overestimates the MCS rate by a factor of two  
at large angles. One of the main goals of the HPS Test was to evaluate the description of the tails of the 
multiple Coulomb scattering in order 
to gain further confidence in the expected detector occupancy in the full HPS experiment.

Figure~\ref{fig:schematic_testrun_vs_erun} gives a schematic view of the main differences 
between the photon and electron beam setup. 
\begin{figure}[ht]
\includegraphics[ width=7cm]{figures/photon_vs_electron_beam_schematic.png}
\caption{\small{Schematic comparison of HPS Test run photon beam compared to the HPS electron beam.}}\label{fig:schematic_testrun_vs_erun}
\end{figure}
In particular, the angular distribution of the pair produced electron and positron emerging 
from the converter has comparable contributions from {\it i)} the pair production angle
and {\it ii)} the MCS of the electron and positron in the converter after production. By measuring the 
scattering rate at several different converter thicknesses we can vary the contribution from MCS 
to confirm our model of MCS despite the fact that all data was taken with a photon beam.

\subsection{Running Conditions}

Data was taken at three different converter thicknesses with a beam current varying between 
$30-70$~nA, see~Tab.~\ref{tab:currents}.  The photon beam line during the test run produced a relatively 
large fraction of pairs 
originating upstream of the converter. This contribution was measured during data taking 
with ``empty'' converter runs i.e. removing the converter but with all other conditions 
the same. 
The upstream background measured in the ``empty'' converter runs was subtracted 
from the other runs, properly normalized using the measured integrated currents.
\begin{table}
\begin{center}
{\small
\begin{tabular}{|c|c|c|}
\hline
Converter thickness & Duration &  $e^-$ on converter \\
 (\%r.l.) & (s) & (nC)    \\   
\hline
%\hline
1.6   & 911 &     24385.9     \\ %27 nA
%\hline
0.18   & 2640 &    193508.9  \\  %73 nA
%\hline
0.45  & 2149 &       140709.9  \\ %65.5 nA
%\hline
0    & 1279  &   88079.6  \\
\hline
\end{tabular}
\caption{Measured integrated currents for the dedicated photon runs.}
\label{tab:currents}
}
\end{center}
\end{table}

\subsection{Measured Angular Distributions}

For this analysis, we measure angular distribution of electrons and positrons using the ECal.
Cluster reconstruction was done using the algorithm described in Sec.~\ref{sec:ecal_clustering}: build 
clusters around seed hits (hits above a ``seed'' energy threshold and with greater energy than any 
neighboring hits), and add all neighboring hits above an ``add'' energy threshold.
Hit energy is calibrated by matching track momentum to cluster energy, as described in Sec.~\ref{sec:ecal_calibration}.

The measured angular distribution in the ECal for the three converter thicknesses are shown in 
Fig.~\ref{fig:ang_distr_data} (left).  
\begin{center}
{\small
	\begin{figure}[]
	\includegraphics[ width=7cm]{figures/rate_ecalrow_raw.png}
	\includegraphics[ width=7cm]{figures/rate_ecalrow_norm_subtr.png}
	\caption{Measured raw vertical angular distributions before (top) and after (bottom) 
	normalization and background subtraction.}
	\label{fig:ang_distr_data}
	\end{figure}
}
\end{center}
The background fraction for the there converter thicknesses was 16\%, 52\% and 71\% 
for converter thicknesses of 1.6\%, 0.45\% and 0.18\%, respectively. The background fraction was also 
cross-checked by pointing back tracks reconstructed in the SVT to identify the fraction of tracks not emanating from the converter. 
%This can be seen in Fig.~\ref{fig:extrapol_converter} (bottom) where small 
%satellite peaks at $\pm 10$~mm can be identified as tracks from the upstream background. The angular distribution, after normalization and subtracting the upstream background, are shown in 
%Fig.~\ref{fig:ang_distr_data} (right).  
We also checked that the contribution from photons to our triggered 
sample was less than 2\% (without angular selections which would further reduce the contribution).

These measured angular distributions are compared to simulation to validate the modeling of the 
MCS. As described in more detail in Appendix XXXX, {\sc EGS5}~\cite{egs5} is used to generate 
the electromagnetic interactions in the converter while {\sc GEANT4} is used to simulate the particles after the converter.  Figure~\ref{fig:ang_distr_dataMC} shows the angular distribution comparing data and 
EGS5 normalized to 1~s of beam at 90~nA beam current. 
\begin{center}
{\small
	\begin{figure*}[t]
	\includegraphics[ scale=0.25]{figures/dataMC_1351_Hit_Y_top_norm_bkgsub.png}
	\includegraphics[ scale=0.25]{figures/dataMC_1354_Hit_Y_top_norm_bkgsub.png}
	\includegraphics[ scale=0.25]{figures/dataMC_1353_Hit_Y_top_norm_bkgsub.png}
	\caption{Comparison between the observed and predicted angular 
distribution using {\sc EGS5} for a converter thickness of 1.6\% (left), 0.45\% (middle) and 0.18\% 
(right).  Only statistical uncertainties are included. }
	\label{fig:ang_distr_dataMC}
	\end{figure*}
}
\end{center}
The total rate measurements are in Fig.~\ref{fig:rate_vs_thickness} and summarized in 
Tab.~\ref{tab:ang_distr_dataMC}.
\begin{center}
{\small
	\begin{figure*}[t]
	\includegraphics[ scale=0.3]{figures/dataMC_geant4.png}
	\includegraphics[ scale=0.3]{figures/dataMC_egs.png}
	\caption{\small{The measured rate as a function of converter thickness comparing GEANT4 (left) and EGS5 (right)}.} 
	\label{fig:rate_vs_thickness}
	\end{figure*}
}
\end{center}
The total systematic uncertainty was estimated to be between 10-18\% depending on the run including:  
a 5\% uncertainty on the integrated current normalization, alignment of the ECal, uncertainty from the 
background normalization, and limited Monte Carlo statistics.  
\begin{center}
{\small
\begin{table}
\begin{tabular}{|l|c|c|c|}
\hline
Converter (\% r.l.) & 1.60 & 0.45 &	0.18 \\
\hline
EGS5 &	1162 $\pm$ 112 &	255 $\pm$ 28 &	94 $\pm$ 17	\\
\hline
GEANT4 & 2633 $\pm$ 250 & 	371 $\pm$ 38 &	114 $\pm$ 18 \\
\hline
Observed 	& 1064 $\pm$ 2 & 196 $\pm$ 1 &	92 $\pm$ 1 \\						
\hline
\end{tabular}
\caption{ Observed and predicted number of events for 1~s of beam at 90~nA for three different converter 
thicknesses. The uncertainty on the prediction includes systematic uncertainties. }
\label{tab:ang_distr_dataMC}
\end{table}
}
\end{center}

\subsection{Conclusion}
In summary, the accurate modeling of the MCS is fundamental to estimate occupancies and trigger rates 
for HPS. {\sc EGS5} predicts the correct angular distribution across all converter thicknesses while 
{\sc GEANT4} overestimates the rates; with the disagreement increasing  with larger converter thickness. 
This preliminary result verifies our modeling of the MCS using {\sc EGS5} for HPS.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Summary and Outlook}

This paper reviewed the HPS Test Run apparatus, a simplified version of that 
planned for the full HPS experiment, and demonstrates the feasibility of the detector
technologies proposed for silicon tracker, ECal, and data acquisition systems. It documents the
performance of the trigger, data acquisition, silicon tracker, and ECal
and shows that the performance assumed in calculating the physics reach of the experiment is realistic.
Of particular importance, data from dedicated photon beam running has been used to compare
the observed trigger rates with that expected in simulation. The trigger rate is almost entirely due to
photons which have converted to e$^+$e$^-$ upstream of HPS and is sensitive to the multiple
Coulomb scattering of electrons and positrons in the conversion target.  Since scattered primary beam is 
the dominant 
source of occupancy in running HPS in an electron beam, good agreement between data and simulation 
confirm the background simulation used to benchmark the physics reach of the HPS experiment.

In addition to this important test of our background simulation, the test run accomplished the following goals:\begin{enumerate}
	\item More than 97\% of SVT channels functioned properly
	\item SVT readout signal to noise of 25.5, required to achieve the expected spatial and temporal resolutions
	\item SVT hit time resolution of 2.6~ns, proving hit time reconstruction will work for HPS
	\item SVT hit efficiency greater than 98\%
	%\item SVT track reconstruction efficiency greater than 98\%
	\item Survey-based SVT alignment performed as expected and will allow track-based alignment
	\item 87\% of ECal crystals functioned properly, with defects to be corrected by planned ECal upgrades
	\item The ECal has been calibrated using SVT tracks
	\item The SVT and JLab DAQ were successfully integrated
	\item The trigger functioned as designed; FADC trigger rate was tested to greater than 100~kHz
	% deficiencies found in test run trigger performance are addressed for the 2014-2015 run
\end{enumerate}

While the Test Run successfully allowed us to test many aspects of the HPS experiment, there were 
limitations to what could be achieved in some key areas such as mass resolution and vertexing 
performance. In particular, the low statistics and lack of resonances or scattered beam electrons prohibits a 
direct analysis of the momentum 
and tails of the vertex distribution. However, for both of these performance parameters, the observed 
agreement between data and simulation in key distributions supports the performance expected for the 
proposed experiment.

\subsection{Lessons Learned}

In the process of developing the HPS Test design, it was found that this simple system was capable of 
delivering a surprising fraction of the physics potential anticipated for the full experiment.  With this in mind, 
we have proposed a new design for the HPS detector that builds upon the HPS Test , principally 
by addressing the compromises made for HPS Test to ensure the best possible performance for A$^\prime$ 
physics within the envelope of the existing beam line layout and analyzing magnet. For the SVT, 
this design uses the same sensors, readout chips, and module concept and for the ECal the crystal and 
detector layout will be identical, retaining the most successful 
elements of the test run apparatus and addressing the weaknesses identified during assembly and 
operation to ensure the success of the 
experiment. The new SVT layout restores the sixth layer for more robust tracking, adds acceptance in the 
deeper layers to increase sensitivity and provides better silicon cooling to improve longevity. Other major 
updates needed for the full experiment are updates to the SVT electronics and 
DAQ; improving connectivity and cabling, moving digitization closer to the front-end electronics and 
updating the data reduction, event handling and trigger synchronization to reach 50kHz 
trigger rates. 
This first generation of 
the full experiment will be ready to take physics data when CEBAF begins operation again in 2014.

%% The Appendices part is started with the command \appendix;
%% appendix sections are then done as normal sections
%% \appendix

%% \section{}
%% \label{}

%% References
%%
%% Following citation commands can be used in the body text:
%% Usage of \cite is as follows:
%%   \cite{key}          ==>>  [#]
%%   \cite[chap. 2]{key} ==>>  [#, chap. 2]
%%   \citet{key}         ==>>  Author [#]

%% References with bibTeX database:

\bibliographystyle{model1-num-names}
%\bibliography{<your-bib-database>}
\bibliography{hps-testrun-nim}

%% Authors are advised to submit their bibtex database files. They are
%% requested to list a bibtex style file in the manuscript if they do
%% not want to use model1-num-names.bst.

%% References without bibTeX database:

% \begin{thebibliography}{00}

%% \bibitem must have the following form:
%%   \bibitem{key}...
%%

% \bibitem{}

% \end{thebibliography}

\end{document}

%%
%% End of file `elsarticle-template-1-num.tex'.

### 2013-10-21 hps-testrun-nim.tex
Stepan changes to section 2

@@
 \label{detector}
-The HPS experiment is proposed to run in Hall B at JLab using the CEBAF electron beam. This electron 
-beam is delivered at 499 MHz at energies ranging from 1.1 GeV to 5.5 GeV and currents up to 800 nA.  An 
-energy upgrade to be completed in 2014 doubles this range. The HPS Test apparatus was designed as a 
+The HPS experiment is proposed to run in Hall B using electron beams of Continuos Electron Beam 
+Accelerator Facility (CEBAF) at JLab. CEBAF can simultaneously deliver  electron 
+beams to multiple experimental hall at 499 MHz frequency with beam currents of up to 150 $\mu$A (for Hall-B 
+the current is limited to $<1 ~\mu$A).  Currently CEBAF facilities are undergoing energy upgrade that will be 
+completed in a year. The upgraded CEBAF machine will double its energy range from up to $6$ GeV during 
+the HPS test run to $12$ GeV.
+
+The HPS Test apparatus was designed as a 
 first step of a multi-stage approach 
 to the HPS experiment. The primary goal was to demonstrate that the technology and design approach 
-chosen by HPS was sound for running in the challenging environment. Nevertheless, a secondary but 
+chosen by HPS are sound for running in a challenging environment. Nevertheless, a secondary but 
 important aspect was that, after proving the technical concepts,  the apparatus would have the 
@@
 would be subject to almost the same constraints and requirements as the full experiment.
-The kinematics of \Aprime production 
-typically results in final state particles within a few degrees of the incoming beam, especially at low 
-$m_{\textrm{A}^\prime}$.  Because of this, the apparatus must accommodate passage of the beam 
-downstream of the target and operate as close to that beam as possible.  Because background rates in this 
-region from the scattered beam are very large, a fast trigger and excellent time tagging of hits are required 
-to select interesting data and reduce the bandwidth required to transfer data from the detector. This method 
-of background reduction is the motivation for operating HPS in a nearly continuous beam: in a beam with 
-large per-bunch charge, background from a single bunch would fully occupy the detector at the required 
-beam intensity. At masses below $2 m_\mu$ only decays to electrons are allowed, so the key trigger 
-comes from a lead-tungstate calorimeter with 250~MHz readout.  
-%Above the di-muon threshold, a 
-%downstream muon detector completes the trigger acceptance and may allow triggering for pion final states 
-%required for sensitivity near the $\rho$ mass.
+The kinematics of \Aprime production typically results in final state particles within a few degrees of the incoming beam, especially at low 
+$m_{\textrm{A}^\prime}$.  
+%Step
+This implies that the apparatus for $A^\prime$ search in electron interactions with fix targets must operate in 
+close proximity to an intense electron beam that passes through a high-Z target, and 
+hence it should tolerate high radiation, high background environment. To meet this challenge, HPS will 
+deploy high rate and radiation hard detector composed of 
+a silicon vertex tracker with 40 MHz readout and a PbWO$_4$ crystal calorimeter with 250 MHz readout, 
+capable of triggering multi-prong events at the rate of up 50 kHz.
+
+%\subsection{HPS Test setup}
 
@@
 planned for the full HPS experiment, demonstrates the feasibility of the detector
-technologies proposed for silicon tracker, electromagnetic calorimeter, and data acquisition systems. 
-A rendering of the HPS Test apparatus installed on the beam line is shown in 
-Fig.~\ref{fig:testrundetector}.
-Most technologies used in the HPS Test apparatus will be used in the HPS detector with some 
+technologies proposed for the silicon tracker, electromagnetic calorimeter, and data acquisition system. 
+A rendering of the HPS Test setup is shown in Fig.~\ref{fig:testrundetector}. The setup is based on the Hall-B 
+pair spectrometer (PS) magnet, 18D36 dipole. The silicon tracer was installed inside the vacuum chamber of 
+PS, and the electromagnetic calorimeter was mounted behind the vacuum flange. A new vacuum box 
+attached to the upstream end of the pair spectrometer vacuum chamber provided necessary connections to 
+the tracker (cooling, HV, and signal readout). 
+Most technologies used in the HPS Test apparatus as well as the magnet and the vacuum chamber will be 
+used in the HPS detector with some 
 improvements to each of the systems; both from lessons learned during running of the HPS Test but 
-also from less schedule and budget constraints.
-
-\subsection{Detector Components}
+also from planned upgrades for longer and more effective running.
+
 An overview of the coverage, segmentation and performance of the HPS Test detector is given in Tab.~\ref{tab:detector-overview}.
@@
 
-The silicon tracking and vertexing detector for HPS Test, or SVT, operates in an existing vacuum chamber 
-inside the pair spectrometer analyzing magnet in Hall B at JLab.  The design principles of the SVT are 
-described in further detail in the HPS Test Run Proposal  \cite{HPS_tPROP}. There are five measurement 
-stations, or ``layers,'' placed immediately downstream of the target. Each layer comprises a pair of closely-
-spaced planes and each plane is responsible for measuring a single coordinate, or ``view.'' Introduction of 
-a stereo angle between the two planes of each layer provides three-dimensional tracking and vertexing 
-throughout the acceptance of the detector with one redundant layer.
-
-In order to accommodate the dead zone, the SVT is built in two halves that are mirror reflections of one 
-another about the plane of the nominal electron beam.  Each half consists of five double-sided modules 
+In order to accommodate the dead zone, the SVT and ECal are built in two halves that are mirror reflections of one 
+another about the plane of the nominal electron beam.  Each half of SVT consists of five double-sided modules 
 mounted on a support plate that provides services to the modules and allows them to be moved as a group 
 relative to the dead zone. Each module places a pair of silicon microstrip sensors back-to-back at a 
-specified stereo angle with independent cooling and support.
-
-\subsection{Electronics, Trigger, Data Acquisition and Online Computing}
+specified stereo angle with independent cooling and support. The sensors are read out
+continuously at 40 MHz using the APV25 chip, developed for the CMS experiment at the
+LHC.
+
+The each half of ECal consists of $221$ PbWO$_4$ crystals arranged in rectangular formation, five rows, $46$ modules in each raw with first raw having  $37$ modules.
+The light readout from each module is performed by Avalanche Photodiode (APD) glued on back surface of the crystal.
+APD signals were amplified using custom-made amplifier boards before sending them to the readout electronics.
+
+The  Data Acquisition system combines two architectures, Advanced Telecom Communications Architecture (ACTA) based SVT readout system and VXS based digitization and triggering system for ECal.
+System is designed to run with up to 20 kHz trigger rate.
+
+%\subsection{Electronics, Trigger, Data Acquisition and Online Computing}
 
@@
 
-\section{The CEBAF Accelerator and Its Impact on the HPS Test Detector }
-\label{cebaf}
-\subsection{The CEBAF Accelerator}
-
-\subsection{The HPS Test Beamline}
-In Figure \ref{fig:hpstest_layout}, the layout of the parasitic run is shown.
-The silicon vertex tracker was installed inside the Hall B pair spectrometer magnet vacuum chamber with the electromagnetic calorimeter mounted downstream.
-Both the tracker and the ECal were retracted off the beam plane to allow clean passage of the photon beam through the system.
-
+%\section{The CEBAF Accelerator and Its Impact on the HPS Test Detector }
+%\label{cebaf}
+%\subsection{The CEBAF Accelerator}
+
+\section{The HPS Test Beamline}
+HPS test run studied multiple Coulomb scattering of electrons and positrons produced in a thin gold foils by 
+bremsstrahlung photons from the Hall-B tagged photon facility. In Figure \ref{fig:hpstest_layout}, the layout of 
+the test run setup on the beam line is shown. The silicon vertex tracker was installed inside the Hall B pair 
+spectrometer magnet vacuum chamber with the electromagnetic calorimeter mounted downstream. Both the 
+tracker and the ECal were retracted off the beam plane to allow clean passage of the photon beam through 
+the system. 
 \begin{figure}[ht]
@@
 
-For dedicated HPS running the photon beam was generated in the interaction of the $5.5$ GeV electrons with a gold radiator of $10^{-4}$ r.l., located $\approx 8$ meters upstream of the PS pair converter.
-After collimation ($D=6.4$ mm), the photon beam passes through the pair converter and through the HPS system.
-The converter was located $\approx 77$~cm upstream of the first layer of the silicon vertex tracker.
-Data were taken on different converters (empty, $1.8\times 10^{-3}$ r.l., $4.5\times 10^{-3}$ r.l., and $1.6\times 10^{-2}$ r.l.).
-These measurements were repeated for the reverse field setting of the pair spectrometer dipole.
+The photon beam was generated in the interaction of the $5.5$ GeV electrons with a gold radiator of 
+$10^{-4}$ r.l., located $\approx 8$ meters upstream of the PS pair converter. The primary and scattered 
+electron beams are deflected way from detectors by the dipole magnet of the photon tagging system. After 
+collimation ($D=6.4$ mm), the photon beam passes through the pair converter and through the HPS system. 
+The converter was located $\approx 77$~cm upstream of the first layer of the silicon vertex tracker. Data were 
+taken on different converters (empty, $1.8\times 10^{-3}$ r.l., $4.5\times 10^{-3}$ r.l., and $1.6\times 10^{-2}$ 
+r.l.). These measurements were repeated for the reverse field setting of the pair spectrometer dipole.
 

### 2013-10-24 hps-testrun-nim.tex
Small update from Pelle

@@
 \newcommand{\ee}{e$^+$e$^-$}
+\newcommand{\fluenceunit}{1~MeV~neutron~equivalent/cm\ensuremath{^2}}
 
@@
 of the \Aprime.  Under the assumption that this mass is generated via a Higgs-like symmetry breaking, 
-the mass would be roughly of the order $\sqrt{\epsilon} m_W \sim$~MeV-GeV.  These ranges are further 
+the mass would be roughly of the order $\sqrt{\epsilon} m_W \sim$~-GeV.  These ranges are further 
 motivated by explanations of other dark matter anomalies involving non-minimal dark sectors~
@@
 primary beam. At the edge of this ``dead zone," the radiation dose approaches $10^{15}$ electrons/cm
-$^2$/month, or roughly $3 \times 10^{13}$ 1 MeV neutron equivalent/cm$^2$/month, as shown in Fig.~
-\ref{fig:radiation} and~\ref{fig:rates}~\cite{Rashevskaya:2002nd}. 
+$^2$/month, or roughly $3 \times 10^{14}$~\fluenceunit/month, as shown in Fig.~
+\ref{fig:radiation} 
 %===================
-\begin{figure}[htp]
+\begin{figure}[]
 \includegraphics[width=7cm]{figures/radiation}
 \label{fig:radiation}
-\caption{Electron fluences: electrons bend towards $+x$.}
-\end{figure}
-\begin{figure}[htp]
+\caption{Simulation of the fluence 10~cm downstream of the target in the active region of the SVT ($|Y|>0.15~$cm) looking downstream; electrons bend towards $+x$.}
+\end{figure}
+%===================
+and~\ref{fig:rates}~\cite{Rashevskaya:2002nd}.
+%===================
+\begin{figure}[]
 \includegraphics[width=7cm]{figures/rates}
 \label{fig:rates}
-\caption{The environment near the dead zone 10 cm from the target.}
-\end{figure}
-%\begin{figure}[htp]
-%\subfigure[\label{fig:rates}The occupancy in an 8 ns window in 60 micron strips.]
-%{\includegraphics[width=8cm]{figures/rates}}
-%\subfigure[\label{fig:radiation}Electron fluences: electrons bend towards $+x$.]
-%{\includegraphics[width=7cm]{figures/radiation}}
-%\subfigure[\label{fig:rates}The occupancy in an 8 ns window in 60 micron strips.]
-%{\includegraphics[width=8cm]{figures/rates}}
-%\caption{The environment near the dead zone 10 cm from the target.}
-%\end{figure}
+\caption{Simulation of the occupancy in the SVT 10~cm downstream of the target as a function of the 
+vertical distance from the beam center.}
+\end{figure}
 %=================== 
@@
 Finally, in order protect the sensors, the detector must be movable so that it can be retracted during periods of uncertain beam conditions.
-
 %To summarize the SVT must:
@@
 
-A realistic simulation of the detector using the java-based org.lcsim package and including full backgrounds has been used to optimize the layout for acceptance, tracking efficiency, mass resolution and prompt vertex rejection~\cite{Graf:2011zzc}.
-The layout of the SVT is summarized in Table~\ref{tab:trk} and shown in Figure~\ref{fig:tracker_model}.
-
-The layout of the SVT is shown in Fig.~\ref{fig:tracker_model} and summarized in Table \ref{tab:trk}. The 
-vacuum chamber is too small vertically to accommodate 90-degree stereo layers to optimize the vertex 
-resolution. Instead, 100~mrad stereo is used in the first three layers 
+A realistic {\sc Geant4} simulation of the detector based on the {\sc SLIC}~\ref{slic} simulation 
+package~\cite{Graf:2011zzc}
+including all backgrounds has been used to optimize the layout for acceptance, tracking efficiency, mass 
+resolution and prompt vertex rejection. The layout of the SVT is summarized in Tab.~\ref{tab:trk} and rendered in Fig.~\ref{fig:tracker_model}.
+
+The layout of the SVT is shown in Fig.~\ref{fig:tracker_model} and summarized in Table \ref{tab:trk}.
+The vertex resolution with an asymmetric beam spot of $\approx 200\times40 \mu$m requires hit 
+resolutions better than XXXX (XXXX)~$\mu$m in the vertical (horizontal) measurement coordinate. 
+In addition, the vacuum chamber is too small vertically to accommodate 90-degree stereo layers to optimize 
+the vertex resolution in the horizontal coordinate. Instead, 100~mrad stereo is used in the first three layers 
 to provide higher-resolution 3-D space points for vertexing. The 50~mrad stereo of the last two layers 
@@
 \hline
-    $z$ from target (cm)  & 10 & 20 & 30 & 50 & 70  \\ 
+    $z$ from nom. target (cm)  & 10 & 20 & 30 & 50 & 70  \\ 
     Stereo angle (mrad)  & 100 & 100 & 100 & 50 & 50 \\ 
@@
 %=======================
-The Test SVT is built in two separate halves that are mirror reflections of one another about the plane of the 
+The SVT is built in two separate halves that are mirror reflections of one another about the plane of the 
 nominal electron beam.  Each half consists of five, double-sided modules mounted on a support plate that 
@@
 The sensors for the SVT are selected according to a number of requirements.  First, the sensors must be 
-radiation tolerant to approximately $1.5\times10^{14}$ 1 MeV neq/cm$^2$ for a six month run.  This 
-corresponds to about 4 MHz/mm$^2$, so the sensor and readout technology must be capable of handling 
+radiation tolerant to approximately $1.5\times10^{14}$~\fluenceunit for a six month run.  This 
+corresponds to about 4~MHz/mm$^2$, so the sensor and readout technology must be capable of handling 
 very high local occupancies. Since sensitivity is limited by multiple scattering, a material budget of less 
-than 1\% $X_0$/layer is imperative and far less is desirable.  The best vertex resolution with a small beam 
-spot ($\approx 10 \mu$m) requires single-hit resolution better than 20 $\mu$m in both measurement 
-coordinates.  Finally, the sensor technology must be mature and readily available at low cost.  Surprisingly, 
-we find that silicon microstrips are the best match to these requirements, and a supply of appropriate 
-microstrip sensors purchased from the Hamamatsu Photonics Corporation for the Run 2b upgrade of D\O~
-\cite{Denisov:2001aa} are readily available. These are $p+$ on $n$, single sided, AC coupled, polysilicon-
-biased sensors fabricated on $<100>$ silicon and have 30(60) micron sense(readout) pitch over their 4 cm 
+than 1\% $X_0$/layer is imperative and far less is desirable. To achieve the required vertex resolution  
+single-hit resolutions better than XXXX~$\mu$m are required. Finally, the sensor technology must 
+be mature and readily available at low cost.  Silicon microstrips are the best match to these requirements, and 
+a supply of appropriate microstrip sensors purchased from the Hamamatsu Photonics Corporation for the 
+Run 2b upgrade of D\O~\cite{Denisov:2001aa} are readily available. 
+These are $p+$-on-$n$, single sided, AC coupled, 
+polysilicon-biased sensors fabricated on $<100>$ silicon and have 30(60) micron sense(readout) pitch 
+over their 4 cm 
 $\times$ 10 cm surface. Although a maximum bias of 350 V is specified, the vast majority are operable to 
-1000V and therefore remain fully depleted to a dose of approximately $1.5\times10^{14}$ 1 MeV neq/cm
-$^2$.
+1000V and therefore remain fully depleted to a dose of approximately 
+$1.5\times10^{14}$~\fluenceunit.
 
 \subsubsection{Front-end Electronics}
-
 Because the regions of high occupancy are small spots in two dimensions, only a short length of any one 
@@
 very high and lowering the peak occupancy in the sensors to approximately 1\% for tracking requires a 
-trigger window and tagging of hit times to roughly 8 ns, as shown in Figure~\ref{fig:rates}.  The FADC 
+trigger window and tagging of hit times to roughly 8~ns, as shown in Fig.~\ref{fig:rates}.  The FADC 
 readout for the ECal and muon system are capable of this, but achieving achieving $2\sigma$ efficiency for 
-silicon hits then requires 2 ns time resolution for the hits in the SVT. This performance can be achieved with 
+silicon hits then requires 2~ns time resolution for the hits in the SVT. This performance can be achieved with 
 the APV25 readout ASIC developed for the CMS experiment at CERN~\cite{French:2001xb}.  When 
@@
 of three.  By fitting the known $CR$-$RC$ shaping curve to these samples, the initial time of the hit can be 
-determined to a precision of 2 ns for S/N$>$25, an achievable figure with our sensors if read out 
+determined to a precision of 2~ns for S/N$>25$, an achievable figure with our sensors if read out 
 individually~\cite{Friedl:2009zz}.  For the SVT, six-sample readout and the shortest possible shaping time 
-(35 ns) will be used to best distinguish hits that overlap in time.
+(35~ns) will be used to best distinguish hits that overlap in time.
 The APV25 chips are hosted on simple FR4 hybrids since these hybrids and their cooling system are 
-outside the tracking volume.  Along with the sensors, these are assembled into large multi-sensor modules, 
-one for each tracking view.
+outside the tracking volume.  Along with the sensors, these are assembled into half-modules, one for each 
+tracking view, with a short cable pigtail to provide power and configuration to the modules and signal 
+readout.
 
@@
 
-The sensor modules for the SVT consist of a pair of identical half-modules, sandwiched back-to-back around an aluminum cooling block at one end and a similar PEEK spacer block at the other.
-Figure \ref{fig:tracker_module} shows a prototype module assembly.
+The sensor modules for the SVT consist of a pair of identical half-modules, sandwiched back-to-back around 
+an aluminum cooling block at one end and a similar PEEK spacer block at the other. 
+Figure~\ref{fig:tracker_module} shows a single module after assembly.
 %=======================
@@
    	 \includegraphics[width=7cm]{figures/IMG_5200}
-	\caption{\small{A prototype module assembly (foreground) with the 50 mrad (left) and 100 mrad (right) module assembly fixtures in the background.
+	\caption{\small{A prototype module assembly (foreground) with the 50~mrad (left) and 100~mrad (right) module assembly fixtures in the background.
 A pair of cooling blocks and a spacer block can be seen on the fixtures.} }

### 2013-10-25 hps-testrun-nim.tex
Johns updated to abstract and intro. Some small fixes as well.

@@
 \begin{abstract}
-Recent astrophysical data motivates searches for a massive, dark sector analog to the photon. The 
-preferred parameter space for this "heavy photon" requires very high luminosity for direct production, 
-favoring fixed target experiments, and results in long-lived decays of these new force carriers to pairs of 
-light, charged fermions.  Identification of these states on large backgrounds requires precision tracking and 
-vertexing at high rates in a difficult experimental environment. The Heavy Photon Search, or HPS, 
-proposes a novel silicon tracking and vertexing detector, the HPS Silicon Vertex Tracker (SVT), to search 
+Heavy photons, aka "hidden sector" or "dark" photons, are massive cousins to the SM photon, 
+which couple to an analogue of electric charge. They arise naturally in theories with additional
+U(1) gauge groups, and have been proposed as a possible explanation for the muon g-2 anomaly,
+astrophysical puzzles, and possible sightings of light dark matter in direct detection experiments.
+Masses in the range 10 to 1000 MeV are suggested. Heavy photons couple weakly to electric charge, 
+so can be produced via electroproduction and can decay into elecron-positron pairs, albeit at rates 
+strongly suppressed compared to standard QED trident processes. Consequently, heavy photons must be identified
+above copious backgrounds, requiring high luminosity/high rate experiments, good mass resolution
+(to identify invariant mass bumps), and good vertexing (to see the long lifetimes implied by
+weak couplings). The Heavy Photon Search (HPS) will use  a silicon microstrip vertex tracker
+triggered by a high speed PbWO4 electromagnetic calorimeter to search 
 for these states in a fixed target experiment at Thomas Jefferson National Accelerator Facility (JLab). 
-The HPS SVT employs actively cooled silicon 
-microstrip sensors with fast readout directly downstream of a target and inside of a dipole magnet to 
-instrument a large acceptance with a relatively small detector. The readout is triggered by a fast, 
-radiation-hard, compact, lead tungstate electromagnetic calorimeter.  As a first step; a simpler, small scale 
-version of this detector has been assembled and operated on beam at JLab. A detector description and 
-results on multiple Coulomb scattering models are outlined in this paper.
+The first stage of HPS was the HPS Test Run experiment, designed to demonstrate the technical feasibility of the detector and data
+acquisition systems and to confirm that critical backgrounds were correctly modeled.
+This paper describes the HPS Test Run detector, reviews its performance, and presents results of
+the normalized trigger rate measurements that confirm the accuracy of the background simulation.
 \end{abstract}
@@
 
-There are two necessary parameters that determine the properties of this ``heavy photon," designated the 
-\Aprime.  The first is the mixing of this state with the Standard Model photon, $\epsilon$, which results in 
-a coupling of the \Aprime to Standard Model fermions with a strength of $\epsilon e$.  In simple models 
-with kinetic mixing, $\epsilon$ is favored to be in the range of $10^{-2} -10^{-5}$.  The second is the mass 
-of the \Aprime.  Under the assumption that this mass is generated via a Higgs-like symmetry breaking, 
-the mass would be roughly of the order $\sqrt{\epsilon} m_W \sim$~-GeV.  These ranges are further 
-motivated by explanations of other dark matter anomalies involving non-minimal dark sectors~
-\cite{TuckerSmith:2001hy} and the fact that no similar excess in proton-antiproton pairs is observed, which 
-would be simply explained if $ m_{\textrm{A}^\prime} < 2m_p$~\cite{Adriani:2010rc}.
-
-Searches for these heavy photons with high-intensity, fixed target experiments offer the best sensitivity in 
-this region of the parameter space~\cite{Bjorken:2009mm}.  In these experiments, an \Aprime is 
-radiated off the incident electron, much like a bremsstrahlung photon, which subsequently decays to a pair 
-of Standard Model fermions.  However, achieving sensitivity to this parameter space presents a number of 
-challenges.  At larger couplings, large data samples are required to identify a small invariant mass peak on 
-significant background.  At smaller couplings, the  \Aprime becomes long-lived, which enables 
-sensitivity from extremely high-luminosity beam-dump experiments that screen out the Standard Model 
-backgrounds.  However, in the intermediate region, lifetimes are too short to screen out backgrounds with a 
-shield, but signal cross sections are so small that collecting large enough event samples to distinguish the 
-signal requires unacceptable data rates or running times.  Gaining sensitivity to this region requires a fast 
-detector capable of precision mass reconstruction of \Aprime final states together with the best possible 
-rejection of prompt vertexes to eliminate backgrounds. The HPS experiment aims to achieve these goals 
-by placing a compact silicon and vertexing detector ($\approx 1$ m long) immediately downstream ($
-\approx 10$ cm) of a thin target ($\approx0.25$ X$_0$ tungsten) and inside of a dipole magnet ($\approx 
-1$ T)~\cite{HPS_proposal_2010}.
-
-The HPS Test run was proposed to DOE early in 2011 as the first stage of the HPS experiment. Its
-purposes included demonstrating that the apparatus and data acquisition systems are feasible and
-that the trigger rates and occupancies encountered in electron-beam running are as simulated.  It also
-provided valuable experience to the HPS Collaboration in all aspects of designing, building, installing,
-and running the experiment at JLab. Furthermore, in the case that HPS Test detector met all of the 
-performance goals and was given dedicated running time with an electron beam, the HPS Test Run 
-could provide new sensitivity to heavy photons. The HPS Test apparatus was installed on April 19, 2012, 
-and 
-ran parasitically with the HDice experiment, using a photon beam, until May 18. The JLab run schedule 
+Heavy photons, aka known as "hidden sector" or "dark" photons, are particles with mass 10-1000 MeV which 
+couple
+weakly to the SM photon, so can be radiated by electrons, and can decay into e+e- pairs, albeit at rates far
+below those of QED trident processes. They have been suggested by numerous Beyond Standard Model 
+theories and
+as an explanation of the current muonic g-2 anomaly, and may couple directly
+to hidden sector particles that may constitute all or some of the dark matter. Current phenomenology highlights 
+the 
+20-1000 MeV mass range, and suggests that heavy photons couple to electric charge with strength 
+$\epsilon$e, where 
+$\epsilon$ is in the range of $10^{-3} -10^{-5}$. This range of parameters makes heavy photon searches viable 
+at electron-positron colliders and in moderate energy fixed target electroproduction, and results from both
+approaches have already been reported. Fixed target experiments offer the highest sensitivity 
+for heavy photons with mass $<1000$~MeV~\cite{Bjorken:2009mm}, but require large data sets and good 
+mass resolution to identify a small mass peak above the copious QED background. At small couplings, heavy 
+photons become long-lived, so detection of a secondary decay vertex can reject the prompt QED background 
+and boost experimental sensitivity.
+The HPS experiment uses both invariant mass and vertex signatures by placing a compact silicon tracking and 
+vertexing detector ($\approx 1$~m long) immediately downstream ($\approx 10$~cm) of a thin target 
+($\approx0.25~X_0$ tungsten) and inside of a dipole magnet ($\approx 1$~T)~\cite{HPS_proposal_2010}. 
+The experiment runs at high rates, exploiting the 100\% duty cycle of the 
+CEBAF accelerator to accumulate the need statistics. The trigger is provided by a fast electromagnetic 
+calorimeter just downstream of the magnet.
+
+The HPS Test run, a simplified version of the full HPS experiment, was proposed and approved at JLab 
+as the first stage of the HPS experiment.  Its purposes included demonstrating that the apparatus and data 
+acquisition systems are technically feasible and
+that the trigger rates and occupancies encountered in electron-beam running are as simulated. Additionally,
+given dedicated running time with electron beams, the HPS Test Run could provide new sensitivity to heavy 
+photons. The HPS Test apparatus was installed on April 19, 2012, and 
+ran parasitically with the HDice experiment, using its photon beam, until May 18. The JLab run schedule 
 precluded any dedicated electron beam running, but the HPS Test Run was allowed a short and valuable
@@
 
-This paper reviews the HPS Test Run apparatus, a simplified version of that 
-planned for the full HPS experiment, and demonstrates the feasibility of the detector
-technologies proposed for silicon tracker, ECal, and data acquisition systems. It documents the
-performance of the trigger, data acquisition, silicon tracker, and ECal
-and shows that the performance assumed in calculating the physics reach of the experiment is realistic.
-Of particular importance, data from dedicated photon beam running has been used to compare
-the observed trigger rates with that expected in simulation. The trigger rate is almost entirely due to
-photons which have converted to \ee upstream of HPS and is sensitive to the multiple
-Coulomb scattering of electrons and positrons in the conversion target.  Since scattered primary beam is 
-the dominant 
-source of occupancy in running HPS in an electron beam, good agreement between data and simulation 
-confirm the background simulation used to benchmark the physics reach of the HPS experiment.
-
-The very small signal rate compared to the large background, the need to fully reconstruct the final states of 
-the electron and positron and doing it in a dense radiation environment millimeters from a high-current beam place stringent requirements on the detector, which should have,
+This paper reviews the HPS Test Run apparatus. It documents the successful performance of the trigger, data 
+acquisition, silicon tracker, and ECal and
+shows that the performance assumed in calculating the physics reach of the experiment is realistic.
+Of particular importance, data from the dedicated photon beam running has been used to compare
+the measured trigger rates with those expected in simulation. The Test Run trigger rate is almost entirely due to
+photons which have converted to \ee pairs in a thin target upstream of HPS and it is sensitive to the particulars 
+of their multiple Coulomb scattering in the conversion target.  Since, during electron beam running, the tails of 
+the multiply Coulomb scattered primary beam are the dominant source of occupancy in the tracker and the 
+trigger rate in the Ecal, they must be understood quantitatively. The trigger rates in the Test Run are also 
+sensitive to the tails of the multiple Coulomb scattering distribution. Good agreement between the measured 
+and simulated rates confirms our understanding of multiple Coulomb scattering and 
+the reliability of the background simulation used to benchmark the physics reach of the HPS experiment.
+
+The very small signal rate compared to the large background and the need to reconstruct the final states of 
+the electron and positron in a dense radiation environment millimeters from a high-current beam 
+place stringent requirements on the detector, which should have,
 \begin{itemize}
 \item large and uniform acceptance in the forward region to catch boosted decay products,
-\item excellent reconstruction efficiency for electron and positrons  with energy down to $XXXX$~MeV,
-\item good momentum resolution to separate a promptly decaying \Aprime signal from the irreducible background,
-\item excellent vertex resolution along the beam line direction to search for displaced \Aprime decays,
-\item low-noise electronics with event timing resolution down to 2~ns, 
 \item a flexible, redundant and efficient trigger selecting electron and positron pairs at rates up to 50kHz,
-\item an online computing framework and data acquisition capable of handling event rates of 50~kHz and 
-bandwidths of 100~MB/s to permanent storage,
+\item excellent track reconstruction efficiency for electrons and positrons,
+\item good angular and momentum resolution to reconstruct invariant mass precisely,
+\item excellent vertex resolution to search for displaced heavy photon decays,
+\item high rate electronics with event timing resolution down to 2~ns,
+\item data acquisition system capable of handling data rates of 100~MB/s to permanent storage,
 \item detector components that can survive and efficiently operate in a high radiation environment with 
-local doses exceeding $XXXX$~MRad
+local doses exceeding $100$~MRad
 \end{itemize}
@@
 
-A realistic {\sc Geant4} simulation of the detector based on the {\sc SLIC}~\ref{slic} simulation 
+A realistic {\sc Geant4} simulation of the detector based on the {\sc SLIC} simulation 
 package~\cite{Graf:2011zzc}
@@
 
-\subsubsection{Calibration}
-\label{sec:ecal_calibration}
+%\subsubsection{Calibration}
+%\label{sec:ecal_calibration}
 The noise and pedestal of the readout chain are calibrated by running the ECal readout in a mode where the 

### 2013-10-26 hps-testrun-nim.tex
Adding MCS theory and references. Smaller edits across all sections except ECal and DAQ. [Pelle]

@@
 % HPS stuff
+\usepackage{color}
 %\usepackage{multicol}
-\newcommand{\Aprime}{A$^\prime$}
+\newcommand{\Aprime}{A\ensuremath{^\prime}}
 \newcommand{\ee}{e$^+$e$^-$}
 \newcommand{\fluenceunit}{1~MeV~neutron~equivalent/cm\ensuremath{^2}}
+\newcommand{\geant}{{\sc Geant4}}
+\newcommand{\egs}{{\sc EGS5}}
+\newcommand{\moliere}{Moli\`{e}re}
 
@@
     \includegraphics[width=0.8\textwidth]{figures/hps_testrun_rendering}
-\caption{Rendering of the HPS Test apparatus installed on the beam line. SHOULD FIND A PIC WITH LOWER HEIGHT.}
+\caption{Rendering of the HPS Test apparatus installed on the beam line.}
 \label{fig:testrundetector}
@@
 \item detector components that can survive and efficiently operate in a high radiation environment with 
-local doses exceeding $100$~MRad
+local doses exceeding $100$~Mrad
 \end{itemize}
@@
 Accelerator Facility (CEBAF) at JLab. CEBAF can simultaneously deliver  electron 
-beams to multiple experimental hall at 499 MHz frequency with beam currents of up to 150 $\mu$A (for Hall-B 
-the current is limited to $<1 ~\mu$A).  Currently CEBAF facilities are undergoing energy upgrade that will be 
-completed in a year. The upgraded CEBAF machine will double its energy range from up to $6$ GeV during 
-the HPS test run to $12$ GeV.
+beams to multiple experimental hall at 499 MHz frequency with beam currents of up to 150 $\mu$A (Hall-B 
+is limited to $<1 ~\mu$A).  Currently CEBAF facilities are undergoing energy an upgrade that is expected to be 
+completed in end of 2014. The upgraded CEBAF machine will double its maximum energy from $6$~GeV 
+during the HPS test run to $12$~GeV.
 
@@
 to the HPS experiment. The primary goal was to demonstrate that the technology and design approach 
-chosen by HPS are sound for running in a challenging environment. Nevertheless, a secondary but 
+chosen are sound for running in such a challenging environment. Nevertheless, a secondary but 
 important aspect was that, after proving the technical concepts,  the apparatus would have the 
@@
 The kinematics of \Aprime production typically results in final state particles within a few degrees of the incoming beam, especially at low 
-$m_{\textrm{A}^\prime}$.  
+$m_{\Aprime}$.  
 %Step
-This implies that the apparatus for $A^\prime$ search in electron interactions with fix targets must operate in 
-close proximity to an intense electron beam that passes through a high-Z target, and 
-hence it should tolerate high radiation, high background environment. To meet this challenge, HPS will 
-deploy high rate and radiation hard detector composed of 
-a silicon vertex tracker with 40 MHz readout and a PbWO$_4$ crystal calorimeter with 250 MHz readout, 
-capable of triggering multi-prong events at the rate of up 50 kHz.
+This implies that the apparatus for an \Aprime search in electron interactions with fix targets must operate in 
+close proximity to an intense electron beam that passes through a high-Z target. 
+Hence it should cope with high backgrounds and tolerate the high radiation environment. 
+To meet this challenge, HPS will deploy high rate and radiation hard detector composed of 
+a silicon vertex tracker with 40~MHz readout and a PbWO$_4$ crystal calorimeter with 250~MHz 
+readout, capable of triggering multi-prong events at top to 50~kHz rate.
 
@@
 A rendering of the HPS Test setup is shown in Fig.~\ref{fig:testrundetector}. The setup is based on the Hall-B 
-pair spectrometer (PS) magnet, 18D36 dipole. The silicon tracer was installed inside the vacuum chamber of 
-PS, and the electromagnetic calorimeter was mounted behind the vacuum flange. A new vacuum box 
-attached to the upstream end of the pair spectrometer vacuum chamber provided necessary connections to 
-the tracker (cooling, HV, and signal readout). 
+pair spectrometer (PS) magnet, 18D36 dipole. The silicon vertex tracker (SVT) was installed inside the vacuum 
+chamber of PS and the electromagnetic calorimeter (ECal) was mounted behind the vacuum flange. 
+A new vacuum box 
+attached to the upstream end of the pair spectrometer vacuum chamber provided necessary services to 
+the SVT (cooling, power and signal readout). 
 Most technologies used in the HPS Test apparatus as well as the magnet and the vacuum chamber will be 
@@
 also from planned upgrades for longer and more effective running.
-
-An overview of the coverage, segmentation and performance of the HPS Test detector is given in Tab.~\ref{tab:detector-overview}.
 
@@
 
-In order to accommodate the dead zone, the SVT and ECal are built in two halves that are mirror reflections of one 
-another about the plane of the nominal electron beam.  Each half of SVT consists of five double-sided modules 
+An overview of the coverage, segmentation and performance of the HPS Test detector is given in 
+Tab.~\ref{tab:detector-overview}.  In order to accommodate the dead zone, the SVT and ECal are built in two 
+halves that are mirror reflections of one 
+another about the plane of the nominal electron beam.  Each half of the SVT consists of five double-sided 
+modules 
 mounted on a support plate that provides services to the modules and allows them to be moved as a group 
@@
 specified stereo angle with independent cooling and support. The sensors are read out
-continuously at 40 MHz using the APV25 chip, developed for the CMS experiment at the
+continuously at 40~MHz using the APV25 ASIC, developed for the CMS experiment at the
 LHC.
 
-The each half of ECal consists of $221$ PbWO$_4$ crystals arranged in rectangular formation, five rows, $46$ modules in each raw with first raw having  $37$ modules.
-The light readout from each module is performed by Avalanche Photodiode (APD) glued on back surface of the crystal.
-APD signals were amplified using custom-made amplifier boards before sending them to the readout electronics.
-
-The  Data Acquisition system combines two architectures, Advanced Telecom Communications Architecture (ACTA) based SVT readout system and VXS based digitization and triggering system for ECal.
-System is designed to run with up to 20 kHz trigger rate.
-
-%\subsection{Electronics, Trigger, Data Acquisition and Online Computing}
+Each half of the ECal consists of 221 PbWO$_4$ crystals arranged in rectangular formation. 
+There are five rows with 46 
+modules in each row except the row closest to the beam plane which has 37. The light from each crystal is read 
+out by Avalanche Photodiode (APD) glued on the back surface of the crystal. 
+Signals from the APDs were amplified using custom-made amplifier boards before being sent to the readout 
+electronics.
+
+The  Data Acquisition system combines two architectures, the Advanced Telecom Communications 
+Architecture (ATCA) based SVT readout system and VXS based digitization and triggering system for the ECal. 
+The system was designed to run at up to a 20 kHz trigger rate.
 
@@
 
-%\section{The CEBAF Accelerator and Its Impact on the HPS Test Detector }
-%\label{cebaf}
-%\subsection{The CEBAF Accelerator}
-
 \section{The HPS Test Beamline}
-HPS test run studied multiple Coulomb scattering of electrons and positrons produced in a thin gold foils by 
-bremsstrahlung photons from the Hall-B tagged photon facility. In Figure \ref{fig:hpstest_layout}, the layout of 
-the test run setup on the beam line is shown. The silicon vertex tracker was installed inside the Hall B pair 
-spectrometer magnet vacuum chamber with the electromagnetic calorimeter mounted downstream. Both the 
-tracker and the ECal were retracted off the beam plane to allow clean passage of the photon beam through 
+The HPS Test run studied multiple Coulomb scattering of electrons and positrons from bremsstrahlung photons 
+produced in the Hall-B tagged photon facility. Figure~\ref{fig:hpstest_layout} shows the layout of 
+the HPS Test setup on the beam line. The SVT was installed inside the Hall B pair 
+spectrometer magnet (PS) vacuum chamber with the ECal mounted downstream of it. Both the 
+SVT and the ECal were retracted off the beam plane to allow clean passage of the photon beam through 
 the system. 
@@
 The photon beam was generated in the interaction of the $5.5$ GeV electrons with a gold radiator of 
-$10^{-4}$ r.l., located $\approx 8$ meters upstream of the PS pair converter. The primary and scattered 
-electron beams are deflected way from detectors by the dipole magnet of the photon tagging system. After 
-collimation ($D=6.4$ mm), the photon beam passes through the pair converter and through the HPS system. 
-The converter was located $\approx 77$~cm upstream of the first layer of the silicon vertex tracker. Data were 
-taken on different converters (empty, $1.8\times 10^{-3}$ r.l., $4.5\times 10^{-3}$ r.l., and $1.6\times 10^{-2}$ 
-r.l.). These measurements were repeated for the reverse field setting of the pair spectrometer dipole.
+$10^{-4}~X_0$, located $\approx~9$~m upstream of the PS. The primary beam and scattered 
+electrons are deflected away from detectors by the dipole magnet of the photon tagging system. After 
+collimation (6.4~mm diameter), the photon beam passes through the aluminum PS pair converter and 
+later the HPS system. 
+The converter was located $\approx~77$~cm upstream of the first layer of the silicon vertex tracker. Data was 
+taken on different converters (empty, $1.8\times 10^{-3}~X_0$ , $4.5\times 10^{-3}~X_0$ and 
+$1.6 \times 10^{-2}~X_0$). 
+These measurements were repeated with the reverse field setting of the PS dipole magnet.
 
@@
 forms the primary input to the extraction of a signal from \Aprime decays; both from the precise 
-measurement of the invariant mass of it's \ee decay products and the position of it's decay vertex 
+measurement of the invariant mass of its \ee decay products and the position of its decay vertex 
 downstream of the target. Track reconstruction is also important for energy scale calibration of the 
@@
 all prompt backgrounds.  This requires great care in design, calibration, and operation of the detector. 
-Finally, the passage of degraded primary beam through the apparatus creates a region of extreme 
+Finally, the passage of the degraded primary beam through the apparatus creates a region of extreme 
 occupancy and radiation that is critical for sensitivity to low-mass A$^\prime$ that have decay products 
@@
 primary beam. At the edge of this ``dead zone," the radiation dose approaches $10^{15}$ electrons/cm
-$^2$/month, or roughly $3 \times 10^{14}$~\fluenceunit/month, as shown in Fig.~
-\ref{fig:radiation} 
+$^2$/month, or roughly $3 \times 10^{14}$~\fluenceunit/month~\cite{Rashevskaya:2002nd}, as shown in 
+Fig.~\ref{fig:radiation} and~\ref{fig:rates}.
 %===================
@@
 \label{fig:radiation}
-\caption{Simulation of the fluence 10~cm downstream of the target in the active region of the SVT ($|Y|>0.15~$cm) looking downstream; electrons bend towards $+x$.}
+\caption{\small Simulation of the fluence 10~cm downstream of the target in the active region of the SVT ($|Y|>0.15~$cm) looking downstream; electrons bend towards $+x$.}
 \end{figure}
 %===================
-and~\ref{fig:rates}~\cite{Rashevskaya:2002nd}.
 %===================
@@
 \label{fig:rates}
-\caption{Simulation of the occupancy in the SVT 10~cm downstream of the target as a function of the 
+\caption{\small Simulation of the occupancy in the SVT 10~cm downstream of the target as a function of the 
 vertical distance from the beam center.}
@@
 Meanwhile, very low-energy delta rays from beam gas interactions multiply the density of background hits, so the SVT must operate inside the beam vacuum.
-Finally, in order protect the sensors, the detector must be movable so that it can be retracted during periods of uncertain beam conditions.
+Finally, in order to protect the sensors, the detector must be movable so that it can be retracted during periods of uncertain beam conditions.
 %To summarize the SVT must:
@@
 
-A realistic {\sc Geant4} simulation of the detector based on the {\sc SLIC} simulation 
+A realistic \geant~\cite{Agostinelli2003250} simulation of the detector based on the {\sc SLIC} simulation 
 package~\cite{Graf:2011zzc}
@@
 
-The layout of the SVT is shown in Fig.~\ref{fig:tracker_model} and summarized in Table \ref{tab:trk}.
-The vertex resolution with an asymmetric beam spot of $\approx 200\times40 \mu$m requires hit 
+The vertex resolution with an asymmetric beam spot of $\approx200\times40~\mu$m requires hit 
 resolutions better than XXXX (XXXX)~$\mu$m in the vertical (horizontal) measurement coordinate. 
@@
 the vertex resolution in the horizontal coordinate. Instead, 100~mrad stereo is used in the first three layers 
-to provide higher-resolution 3-D space points for vertexing. The 50~mrad stereo of the last two layers 
+to provide higher-resolution 3D space points for vertexing. The 50~mrad stereo of the last two layers 
 breaks the tracking degeneracy of having five identical layers and minimizes fakes from ghost hits, 
@@
 \end{tabular}
-\caption{Layout of the HPS Test SVT.  Note the elimination of one layer and 90-degree stereo, and the use of only small, single-sensor-sized double-sided modules both above and below he dead zone. }
+\caption{\small Layout of the HPS Test SVT.. }
 }
@@
     \includegraphics[width=7cm]{figures/HPS_nochamber}
-\caption{A rendering of the Test SVT showing the modules on their support plates held by the hinged C-support on the left and the motion levers on the right.
-The sensors are shown in red and the hybrids in green.
-The beam enters from the right through a vacuum box with flanges for services.
-}
+\caption{\small A rendering of the HPS Test SVT showing the modules on their support plates held by the 
+hinged C-support on the left and the motion levers on the right. The sensors are shown in red and the hybrid 
+readout boards in green. The beam enters from the right through a vacuum box with flanges for services. }
 \label{fig:tracker_model}
@@
 provides services to the modules and allows them to be moved as a group relative to the dead zone. The 
-two halves of the tracker are connected to hinges mounted on a C-shaped support just beyond layer 5 that 
-defines the nominal spacing between the upper and lower halves of the tracker.  A shaft attached to each 
+two halves of the tracker are connected to hinges mounted on a C-shaped support just beyond the last layer t
+that defines the nominal spacing between the upper and lower halves of the tracker.  A shaft attached to each 
 support plate in front of layer 1 extends upstream and connects to a linear shift that transfers motion into the 
-vacuum box through bellows to open and close the tracker around the dead zone. The C-support is 
+vacuum box through bellows to open and close the two halves around the dead zone. The C-support is 
 mounted to an aluminum baseplate that defines the position of the SVT with respect to the vacuum 
@@
 a supply of appropriate microstrip sensors purchased from the Hamamatsu Photonics Corporation for the 
-Run 2b upgrade of D\O~\cite{Denisov:2001aa} are readily available. 
+Run 2b upgrade of the D\O experiment~\cite{Denisov:2001aa} are readily available. 
 These are $p+$-on-$n$, single sided, AC coupled, 
-polysilicon-biased sensors fabricated on $<100>$ silicon and have 30(60) micron sense(readout) pitch 
-over their 4 cm 
-$\times$ 10 cm surface. Although a maximum bias of 350 V is specified, the vast majority are operable to 
-1000V and therefore remain fully depleted to a dose of approximately 
+polysilicon-biased sensors fabricated on $<100>$ silicon and have 30 (60) micron sense (readout) pitch 
+over their $4\times10$~cm$^2$ surface. Although a maximum bias of 350~V is specified, the vast majority are 
+operable to 1000~V and therefore remain fully depleted to a dose of approximately 
 $1.5\times10^{14}$~\fluenceunit.
@@
 Because the regions of high occupancy are small spots in two dimensions, only a short length of any one 
-strip sees significant occupancy, and the strips in that region act as long pixels. However, the rates are still 
+strip see a significant occupancy, and the strips in that region act as long pixels. However, the rates are still 
 very high and lowering the peak occupancy in the sensors to approximately 1\% for tracking requires a 
 trigger window and tagging of hit times to roughly 8~ns, as shown in Fig.~\ref{fig:rates}.  The FADC 
-readout for the ECal and muon system are capable of this, but achieving achieving $2\sigma$ efficiency for 
+readout for the ECal and muon system are capable of this (see Sec.~\ref{sec:fadc}), but achieving 
+$2\sigma$ efficiency for 
 silicon hits then requires 2~ns time resolution for the hits in the SVT. This performance can be achieved with 
@@
 operated in ``multi-peak mode", the APV25 captures successive samples of the output of the shaper in sets 
-of three.  By fitting the known $CR$-$RC$ shaping curve to these samples, the initial time of the hit can be 
+of three at a sampling rate of approximately 40~MHz.  
+By fitting the known $CR$-$RC$ shaping curve to these samples, the initial time of the hit can be 
 determined to a precision of 2~ns for S/N$>25$, an achievable figure with our sensors if read out 
@@
 (35~ns) will be used to best distinguish hits that overlap in time.
-The APV25 chips are hosted on simple FR4 hybrids since these hybrids and their cooling system are 
+The APV25 ASICs are hosted on simple FR4 hybrids since these hybrids and their cooling system are 
 outside the tracking volume.  Along with the sensors, these are assembled into half-modules, one for each 
@@
 single small spot on the sensor, the 
-dominant heat load on the sensor, event after irradiation, is radiant heat from the inside wall of the vacuum 
+dominant heat load on the sensor, even after irradiation, is radiant heat from the inside wall of the vacuum 
 chamber, less than 0.5~W per sensor. The total power consumption budget of about 40~W is removed by a 
@@
 average support material in the tracking volume is approximately 0.06\% $X_{0}$ per double-sided module 
-for a total of 0.7\% per layer.
+for a total material budget of 0.7\% per layer.
 
 \subsection{SVT Digitization, Event Building and Data Transmission}
-\label{sec:svt_daq}
+\label{sec:svtdaq}
 The SVT Data Acquisition (DAQ) is a SLAC-standard system using consisting of a single ATCA crate with 
@@
 Hybrid readout boards and half-modules were assembled at SLAC.  Mounting APV25 chips and all 
-wirebonding and QA testing were performed at Univerity of California, Santa Cruz. Of the sensors tested 
-during production, 90\% were 
-capable of 1000~V bias. Hybrids underwent quick QA testing and each half-module was run at low 
+wirebonding and QA testing were performed at University of California, Santa Cruz. Of the sensors tested 
+during production, 90\% were capable of 1000~V bias voltage without breakdown. 
+Hybrids underwent quick QA testing and each half-module was run at low 
 temperature ($\approx5^{\circ}$ C) and fully characterized for pedestals, gains, noise and time response 
@@
 2012.  Module yields were excellent for such a small production.  Of 165 APV chips acquired, 150 were 
-used to assemble 30 production hybrids, of which 29 passed QA testing.  Of 29 modules built, 28 passed 
+used to assemble 30 production hybrids, of which 29 passed QA testing.  Of 29 half-modules built, 28 passed 
 QA testing, leaving 8 spare modules after completion of the SVT.  Full-module assembly and 
@@
 shipping of the SVT to JLab on April 11.  A custom shipping container, based on experience 
-at FNAL~\cite{shipping}, was built in order to safely send the partly assembled of the SVT. The two fully 
+from FNAL~\cite{shipping}, was built in order to safely send the partly assembled SVT to JLab. The two fully 
 assembled SVT halves were attached to a baseplate supported by four wire-rope isolators. This plate, 
-covered by a clean lexan cover was mounted inside an inner box surrounded by 4 inches of Polyurethane 
-foam to complete the two-spring construction. At JLab, the entire SVT was integrated with the full DAQ and 
-the power supplies for the first time in the cleanroom, before moving the module-loaded support plates to 
-Hall~B for final mechanical assembly and installation inside of the vacuum chamber on April 19.
+covered by a lexan cover for cleanliness, was mounted inside an inner box surrounded by 4 inches of 
+Polyurethane foam to complete the two-spring construction. At JLab, the entire SVT was integrated with the full 
+DAQ and the power supplies for the first time in the clean room, before moving the module-loaded support 
+plates to Hall~B for final mechanical assembly and installation inside of the vacuum chamber on April 19, 2012.
 
@@
 
-During the duration of the dedicated photon run all SVT modules and APV25 
-readout chips were configured to their nominal operating 
-points~\cite{Jones:1069892} while all sensors were reverse-bias at 180~V.  The 
-sensors were operated within a temperature range of  20 to 24$^\circ$C 
-throughout the test run. Multiple calibration runs established a noise level of $\approx$ 750 - 850 electrons  
-which was stable across the SVT modules.
+During the duration of the test run all SVT modules and APV25 chips were configured to their 
+nominal operating points~\cite{Jones:1069892} with all sensors reverse-biased at 180~V.  The 
+sensors were operated within a temperature range of  $20-24^\circ$C 
+throughout the test run. Multiple calibration runs, normalized with lab-based radioactive source tests, 
+established a noise level of $\approx$ XXXX-XXXX electrons which was stable across all the SVT modules.
 
 Throughout the duration of the test run, approximately 97\% of the 12,780 SVT channels were found to be 
-operating normally. The fraction of dead or noisy channels varied from 2.4\% to 4.7\%; 
-most of these were due to misconfigured readout chips (2--4 misconfigured chips out of 100 total) 
-a known noisy half-module, and a couple of known noisy readout chips.
+operating normally. The fraction of dead or noisy channels varied from 2.4\% to 4.7\%.  
+Most of these were due to misconfigured readout chips (2--4 misconfigured chips out of 100 ), 
+a known noisy half-module and a couple of known noisy readout chips.
 
 \subsubsection{Cluster and Hit Reconstruction}
+
 After a trigger is received, six samples of the corresponding output of the APV25 shaper circuit are digitized. 
 The samples from every channel on a sensor surviving the 
-data reduction, described in Sec.~\ref{sec:svtdaq}, are the basis for offline hit reconstruction. 
-The six samples of the APV25 pulse shaper output 
+data reduction algorithm (see Sec.~\ref{sec:svtdaq}) are the basis for offline hit reconstruction. 
+The six samples of the APV25 shaper output 
 are fitted to an ideal $CR-RC$ function to extract the amplitude and the $t_0$ of the hit. 
-The typical pulse shape obtained is shown in Figure~\ref{fig:pulse_shape} also demonstrates that the SVT 
+The typical pulse shape obtained is shown in Fig.~\ref{fig:pulse_shape} also demonstrates that the SVT 
 was well timed in to the trigger with the rise of the pulse at the 3rd sampling point.
@@
 	\includegraphics[width=6cm]{figures/08062012_run1351_samples_vs_amplitude}
-    	\caption{{\small The six pedestal subtracted samples associated with a hit on a track.}}
+    	\caption{{\small The six pedestal subtracted samples from individual channels associated with a hit on a 
+	track.}}
 	\label{fig:pulse_shape}
@@
 These hits are passed through a simple clustering algorithm which forms clusters by grouping adjacent 
-strips. The position of a cluster on the sensor is determined by a pulse height weighted mean (FIX THIS).
+strips. The position of a cluster on the sensor is determined by the amplitude-weighted mean.
 With a linear gain up to $\approx 3$~MIPs, the cluster charge for hits associated with a track follow 
 the characteristic Landau shape as expected, see Fig.~\ref{fig:cluster_pulse}. 
+The signal to noise ratio is XXXX.
 \begin{figure}[h]
@@
 	\includegraphics[width=6cm]{figures/run1351_mip_small.pdf}
-    	\caption{{\small The cluster charge distribution. }}
+    	\caption{{\small The cluster charge distribution for hits associated with a track. }}
 	\label{fig:cluster_pulse}
@@
 average of the fitted $t_0$ channel times. The $t_0$-resolution is studied by comparing the cluster hit time 
-with the average of all cluster hit times, the ``track time'' which has the expected jitter due to clock phase 
-and trigger $\approx 25$~ns. Figure~\ref{fig:tracktime} shows the residual to the individual cluster times. 
+with the average of all cluster hit times on the track, the ``track time'', which has the expected jitter due to clock 
+phase and trigger, approximately 25~ns. Figure~\ref{fig:tracktime} shows the residual to the individual cluster 
+times. 
 \begin{figure}[h]
@@
 \end{figure}
-After correcting for offsets from each sensor (time-of-flight, clock phase) the extracted $t0$ resolution is 
-2.6~ns. This is somewhat worse than the $\approx 2$~ns resolution expected which we attribute to the true 
+After correcting for offsets from each sensor (time-of-flight, clock phase) the extracted $t_0$ resolution is 
+2.6~ns. This is somewhat worse than the approximately 2~ns resolution expected which we attribute to the true 
 pulse shape differing from our idealized fit function which will be improved in the future. Reducing the 
 APV25 pulse shaping time will also improve time resolution. These results show that we can operate with 
-the critical six sample readout mode of the APV25 chip and achieve time resolution adequate for pileup 
-rejection during electron running.
+the six sample readout mode of the APV25 chip and achieve time resolution adequate for pileup 
+rejection during electron running in the HPS experiment.
 
 While occupancy was slightly larger than expected, good agreement between data and simulation was 
-found after taking into account dead or noisy channels. The hit efficiency, see Fig~\ref{fig:hit_efficiency} 
+found after taking into account dead or noisy channels. The hit efficiency, see Fig.~\ref{fig:hit_efficiency}, 
 was measured to be above 98\% and fairly uniform across the SVT.
@@
 function of the total signal to single-strip noise (S/N) and the crossing angle of tracks through the sensor.  
-The single-hit resolution for charged particles with $S/N > 20$, as demonstrated here, is relatively constant 
-at approximately 6 $\mu$m for tracks that are close to normal to the sensors as in HPS.
+The single-hit resolution for charged particles with signal to noise ration above 20, as demonstrated here, 
+is relatively constant at approximately 6~$\mu$m for tracks that are close to normal to the sensors as in HPS.
 
@@
 The SVT was aligned using a combination of optical, laser and touch probe surveys at SLAC and JLab. The 
-optical survey of individual modules with precision of a few microns are combined with a touch-prove survey 
-of the overall SVT support structure, with 25-100 microns precision, to locate the silicon sensor layers with 
+optical survey of individual modules with precision of a few $\mu$m are combined with a touch-prove survey 
+of the overall SVT support structure, with 25-100~$\mu$m precision, to locate the silicon sensor layers with 
 respect to the support plates and the mechanical survey balls on the base plate.
@@
 The resulting survey-based alignment has the position of the silicon sensors correct to within a few hundred 
-microns a more sophisticated global track-based alignment technique to reach 
-the final alignment precision is used.
+microns. A more sophisticated global track-based alignment technique to reach the final alignment precision 
+is being developed.
 
@@
 
-By selecting e$^{+}$e$^{-}$ pairs from the triggered events we are able to study basic distributions of pair production kinematics and in particular those related to our vertex performance.
-Pairs of opposite charge tracks, one in the top and one in the bottom half of the SVT, with larger than 400~MeV were selected.
-The pair production kinematics are relatively well reproduced given the alignment of the tracker; Fig.~\ref{fig:pair_kin} shows the invariant mass and ratio of electron momentum over the sum of electron and positron.
+By selecting \ee pairs from the triggered events we are able to study basic distributions of pair production 
+kinematics and in particular those related to our vertex performance. Pairs of opposite charge tracks, one in the 
+top and one in the bottom half of the SVT, with momentum larger than 400~MeV were selected. 
+The pair production 
+kinematics are relatively well reproduced given the alignment of the tracker; Fig.~\ref{fig:pair_kin} shows the 
+invariant mass and ratio of electron momentum over the sum of electron and positron. 
  \begin{center}
@@
 performance the foremost difference compared to electron beam running is that the target was 
-located $\sim67$~cm from our nominal target position; giving almost collinear tracks in the detector. This 
-degrades the vertex resolution along the 
+located approximately 67~cm from our nominal target position; giving almost collinear tracks in the detector. 
+This degrades the vertex resolution along the 
 beam line compared to that expected in an electron beam with tracks from the nominal target position. 
-Furthermore, tails of the vertex distributions are impossible to study with the finite sample of events from the 
-Test Run. 
-Nevertheless, useful information can still be 
+Furthermore, tails of the vertex distributions are impossible to study with the finite data sample obtained 
+in the test run. Nevertheless, useful information can still be 
 obtained by studying the vertex distributions. Figure~\ref{fig:vtx_pos} shows the distance of closest 
 approach of the momentum vectors extrapolated in the 
-upstream direction from our analyzing magnet, taking into account the measured fringe field. 
+upstream direction from our analyzing magnet, taking into account the measured fringe field of the PS magnet. 
  \begin{center}
@@
 	\includegraphics[width=5cm]{figures/h_vtx_fr_z_h_vtx_z_dataMC_trigseltwotrksel4hit_recoilmc_twotrkfilt.png}
-	\caption{Vertex position represented by the distance of closest approach of the extrapolated 
-	momentum vectors upstream of the analyzing magnet. The overall shift from zero in the x-direction is 
+	\caption{{\bf \textcolor{red}{NEED TO BE UPDATED}}Vertex position represented by the distance of 
+	closest approach of the extrapolated momentum vectors upstream of the PS magnet taking into account 
+	the measured fringe field. The overall shift from zero in the x-direction is 
 	due to a 30~mrad rotation of the SVT with respect to the beam line.}
@@
 \end{center}
-
 While the tails of the vertex distribution expected in electron beam running is not accessible here the 
 fact that the core is relatively well described provides confidence of the description of the amount of 
-material and the multiple scattering description.  These are crucial for benchmarking the physics reach of the 
-HPS detector since both the mass and vertex resolution that determine the physics reach are limited by multiple scattering.
+material and the model used for simulating multiple scattering in the target.  
+These are crucial for benchmarking the HPS \Aprime physics reach since both the mass and vertex resolution 
+that determine the sensitivity are limited by multiple scattering.
 
@@
 These occupancies are dominated by electrons which have multiple Coulomb scattered (MCS) 
-to relatively large 
-angles in the converter. Because HPS is sensitive to scattering angles far out on the tail of the MCS 
-distribution, well beyond the angles important in other experiments, care must be taken
+to relatively large angles in the target. Because HPS is sensitive to scattering angles far out on the tail of the 
+MCS distribution, well beyond the angles important in other experiments, care must be taken
 to ensure our simulations are correct in this regime.
@@
 
-In particular,
-{\sc Geant4}~\cite{Agostinelli2003250} overestimates the MCS rate by a factor of two  
-at large angles. One of the main goals of the HPS Test was to evaluate the description of the tails of the 
-multiple Coulomb scattering in order 
+One of the main goals of the HPS Test was to evaluate the description of the tails of the MCS
 to gain further confidence in the expected detector occupancy in the full HPS experiment. 
+Previous studies of multiple scattering angles show good agreement with the \moliere 
+theory~\cite{Moliere:1948zz} for a wide range 
+of materials and projectiles~\cite{Attwood:2005zz,Shen:1978ha,Gottschalk1993467}. We have verified that 
+the angular distribution $F(\theta)$ in the differential cross section $d\sigma = F( \theta) d(\cos\theta) d\phi$ 
+for the \egs~\cite{egs5} simulation program show good agreement with \moliere's analytical formula as 
+formulated by Bethe~\cite{Bethe:1953va}. 
+The small angle approximation was also shown to be in agreement with the theory formulated by Gaudsmit and 
+Saunderson~\cite{Goudsmit:1940zza,Goudsmit:1940zz} that is valid for any angle. 
+While \egs uses the more complex and time consuming \moliere 
+formula, \geant uses an approximation with two, continuously joined, functions to take into account 
+small and large angle scattering. Due to the explicit function in large angle approximation used by \geant 
+we expect that \geant will overestimate the angular distribution at angles larger than a few mrad.
 
@@
 \end{figure}
-In particular, the angular distribution of the pair produced electron and positron emerging 
-from the converter has comparable contributions from {\it i)} the pair production angle
+The angular distribution of the pair produced electron and positron emerging 
+from the converter in the test run has comparable contributions from {\it i)} the pair production angle
 and {\it ii)} the MCS of the electron and positron in the converter after production. By measuring the 
 scattering rate at several different converter thicknesses we can vary the contribution from MCS 
-to confirm our model of MCS despite the fact that all data was taken with a photon beam.
+while the contribution from the pair production angle is constant. This allows us to confirm our model of MCS 
+despite the fact that all data was taken with a photon beam.
 
@@
 
-For this analysis, we measure angular distribution of electrons and positrons using the ECal.
-Cluster reconstruction was done using the algorithm described in Sec.~\ref{sec:ecal_clustering}: build 
-clusters around seed hits (hits above a ``seed'' energy threshold and with greater energy than any 
-neighboring hits), and add all neighboring hits above an ``add'' energy threshold.
-Hit energy is calibrated by matching track momentum to cluster energy, as described in Sec.~\ref{sec:ecal_calibration}.
-
-The measured angular distribution in the ECal for the three converter thicknesses are shown in 
+We measure the vertical angular distributions of electrons and positrons using the ECal. 
+Cluster reconstruction and calibration was performed as described in Sec.~\ref{sec:ecal}. The measured 
+angular distribution in the ECal for the three converter thicknesses are shown in 
 Fig.~\ref{fig:ang_distr_data} (left).  
@@
 \end{center}
-The background fraction for the there converter thicknesses was 16\%, 52\% and 71\% 
+The background fraction for the three converter thicknesses was 16\%, 52\% and 71\% 
 for converter thicknesses of 1.6\%, 0.45\% and 0.18\%, respectively. The background fraction was also 
-cross-checked by pointing back tracks reconstructed in the SVT to identify the fraction of tracks not emanating from the converter. 
-%This can be seen in Fig.~\ref{fig:extrapol_converter} (bottom) where small 
-%satellite peaks at $\pm 10$~mm can be identified as tracks from the upstream background. The angular distribution, after normalization and subtracting the upstream background, are shown in 
-%Fig.~\ref{fig:ang_distr_data} (right).  
-We also checked that the contribution from photons to our triggered 
-sample was less than 2\% (without angular selections which would further reduce the contribution).
-
-These measured angular distributions are compared to simulation to validate the modeling of the 
-MCS. As described in more detail in Appendix XXXX, {\sc EGS5}~\cite{egs5} is used to generate 
-the electromagnetic interactions in the converter while {\sc GEANT4} is used to simulate the particles after the converter.
-Figure~\ref{fig:ang_distr_dataMC} shows the angular distribution comparing data and
-EGS5 normalized to 1~s of beam at 90~nA beam current. 
+cross-checked by pointing back tracks reconstructed in the SVT to identify the fraction of tracks not originating 
+from the converter. We also checked that the contribution from photons to our triggered 
+sample was much less than 2\%. These measured angular distributions are compared to simulation to validate 
+the modeling of the MCS. \egs~\cite{egs5} is used to generate 
+the electromagnetic interactions in the converter while \geant is used to simulate the particles after the 
+converter.  Figure~\ref{fig:ang_distr_dataMC} shows the angular distribution comparing data and 
+\egs normalized to 1~s of beam at 90~nA beam current. Taking into account systematics uncertainties 
+described below reasonable agreement is obtained;   total rates for each converter thickness is shown in 
+Fig.~\ref{fig:rate_vs_thickness} and summarized in Tab.~\ref{tab:ang_distr_dataMC}.
 \begin{center}
@@
 	\caption{Comparison between the observed and predicted angular 
-distribution using {\sc EGS5} for a converter thickness of 1.6\% (left), 0.45\% (middle) and 0.18\% 
-(right).  Only statistical uncertainties are included. }
+distribution using \egs for a converter thickness of 1.6\% (left), 0.45\% (middle) and 0.18\% 
+(right).  Only statistical uncertainties are shown. }
 	\label{fig:ang_distr_dataMC}
@@
 \end{center}
-The total rate measurements are in Fig.~\ref{fig:rate_vs_thickness} and summarized in 
-Tab.~\ref{tab:ang_distr_dataMC}.
 \begin{center}
@@
 	\includegraphics[ scale=0.3]{figures/dataMC_egs.png}
-	\caption{\small{The measured rate as a function of converter thickness comparing GEANT4 (left) and EGS5 (right)}.} 
+	\caption{\small{The measured rate as a function of converter thickness comparing \geant (left) 
+	and \egs (right)}.} 
 	\label{fig:rate_vs_thickness}
@@
 \end{center}
-The total systematic uncertainty was estimated to be between 10-18\% depending on the run including:  
-a 5\% uncertainty on the integrated current normalization, alignment of the ECal, uncertainty from the 
-background normalization, and limited Monte Carlo statistics.  
+The total systematic uncertainty was estimated to be between 10-18\% depending on the run, they include:  
+uncertainty on the integrated current normalization (5\%), alignment of the ECal, uncertainty from the 
+background normalization and limited Monte Carlo statistics.  
 \begin{center}
@@
 \hline
-EGS5 &	1162 $\pm$ 112 &	255 $\pm$ 28 &	94 $\pm$ 17	\\
+\egs &	1162 $\pm$ 112 &	255 $\pm$ 28 &	94 $\pm$ 17	\\
 \hline
-GEANT4 & 2633 $\pm$ 250 & 	371 $\pm$ 38 &	114 $\pm$ 18 \\
+\geant & 2633 $\pm$ 250 & 	371 $\pm$ 38 &	114 $\pm$ 18 \\
 \hline
@@
 In summary, the accurate modeling of the MCS is fundamental to estimate occupancies and trigger rates 
-for HPS. {\sc EGS5} predicts the correct angular distribution across all converter thicknesses while 
-{\sc GEANT4} overestimates the rates; with the disagreement increasing  with larger converter thickness. 
-This preliminary result verifies our modeling of the MCS using {\sc EGS5} for HPS.
+for HPS. \egs predicts the correct angular distribution across all converter thicknesses while 
+\geant overestimates the rates; with the disagreement increasing  with larger converter thickness. 
+This preliminary result verifies similar studies [] and gives confidence in our modeling of the MCS 
+using \egs for evaluating the physics reach of HPS.
 
@@
 
-\section{Summary and Outlook}
-
-This paper reviewed the HPS Test Run apparatus, a simplified version of that 
+\section{Summary}
+
+This paper reviewed the HPS Test run apparatus, a simplified version of that 
 planned for the full HPS experiment, and demonstrates the feasibility of the detector
-technologies proposed for silicon tracker, ECal, and data acquisition systems. It documents the
-performance of the trigger, data acquisition, silicon tracker, and ECal
-and shows that the performance assumed in calculating the physics reach of the experiment is realistic.
-Of particular importance, data from dedicated photon beam running has been used to compare
+technologies proposed for the silicon vertex tracker, the electromagnetic calorimeter, data acquisition and 
+trigger systems and their performance. Of particular importance, data from dedicated photon beam running has 
+been used to compare
 the observed trigger rates with that expected in simulation. The trigger rate is almost entirely due to
-photons which have converted to e$^+$e$^-$ upstream of HPS and is sensitive to the multiple
+photons which have converted to \ee upstream of the HPS Test setup and is sensitive to the multiple
 Coulomb scattering of electrons and positrons in the conversion target.  Since scattered primary beam is 
-the dominant 
-source of occupancy in running HPS in an electron beam, good agreement between data and simulation 
-confirm the background simulation used to benchmark the physics reach of the HPS experiment.
-
-In addition to this important test of our background simulation, the test run accomplished the following goals:\begin{enumerate}
-	\item More than 97\% of SVT channels functioned properly
-	\item SVT readout signal to noise of 25.5, required to achieve the expected spatial and temporal resolutions
+the dominant source of occupancy in running HPS in an electron beam, good agreement between data and 
+simulation confirm the background simulation used to benchmark the physics reach of the HPS experiment.
+
+In addition to this important test of our background simulation, the HPS Test run accomplished the following 
+goals:
+\begin{itemize}
+	\item More than 97\% of the SVT channels functioned properly
+	\item SVT readout signal to noise of XXXX, required to achieve the expected spatial and temporal resolutions
 	\item SVT hit time resolution of 2.6~ns, proving hit time reconstruction will work for HPS
@@
 	\item The ECal has been calibrated using SVT tracks
-	\item The SVT and JLab DAQ were successfully integrated
-	\item The trigger functioned as designed; FADC trigger rate was tested to greater than 100~kHz
+	\item The SVT and JLab data acquisition systems were successfully integrated
+	\item The trigger functioned as designed; rates greater than 100~kHz was tested in special runs
 	% deficiencies found in test run trigger performance are addressed for the 2014-2015 run
-\end{enumerate}
-
-While the Test Run successfully allowed us to test many aspects of the HPS experiment, there were 
+\end{itemize}
+
+While the HPS Test run successfully allowed us to test many aspects of the HPS experiment, there were 
 limitations to what could be achieved in some key areas such as mass resolution and vertexing 
 performance. In particular, the low statistics and lack of resonances or scattered beam electrons prohibits a 
-direct analysis of the momentum 
+direct analysis of the momentum resolution 
 and tails of the vertex distribution. However, for both of these performance parameters, the observed 
@@
 
-\subsection{Lessons Learned}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Lessons Learned and Outlook}
 
@@
 we have proposed a new design for the HPS detector that builds upon the HPS Test , principally 
-by addressing the compromises made for HPS Test to ensure the best possible performance for A$^\prime$ 
+by addressing the compromises made for HPS Test to ensure the best possible performance for \Aprime 
 physics within the envelope of the existing beam line layout and analyzing magnet. For the SVT, 
@@
 elements of the test run apparatus and addressing the weaknesses identified during assembly and 
-operation to ensure the success of the 
-experiment. The new SVT layout restores the sixth layer for more robust tracking, adds acceptance in the 
-deeper layers to increase sensitivity and provides better silicon cooling to improve longevity. Other major 
-updates needed for the full experiment are updates to the SVT electronics and 
+operation. The new SVT layout adds a sixth layer for more robust tracking, adds acceptance in the 
+three deeper layers to increase physics sensitivity and provides better silicon cooling to improve longevity. 
+Other major updates needed for the full experiment are updates to the SVT electronics and 
 DAQ; improving connectivity and cabling, moving digitization closer to the front-end electronics and 
-updating the data reduction, event handling and trigger synchronization to reach 50kHz 
-trigger rates. 
-This first generation of 
-the full experiment will be ready to take physics data when CEBAF begins operation again in 2014.
+updating the data reduction, event handling and trigger synchronization to reach 50~kHz trigger rates. 
+This first generation of the full experiment will be ready to take physics data when CEBAF begins operation 
+again in end of 2014.
 

### 2013-10-26 hps-testrun-nim.tex
Fixing spaces after macros.

@@
 the measured trigger rates with those expected in simulation. The Test Run trigger rate is almost entirely due to
-photons which have converted to \ee pairs in a thin target upstream of HPS and it is sensitive to the particulars 
+photons which have converted to \ee{} pairs in a thin target upstream of HPS and it is sensitive to the particulars 
 of their multiple Coulomb scattering in the conversion target.  Since, during electron beam running, the tails of 
@@
 important aspect was that, after proving the technical concepts,  the apparatus would have the 
-capability to discover \Aprime events. The implication was that the design of the HPS Test apparatus 
+capability to discover \Aprime{} events. The implication was that the design of the HPS Test apparatus 
 would be subject to almost the same constraints and requirements as the full experiment.
-The kinematics of \Aprime production typically results in final state particles within a few degrees of the incoming beam, especially at low 
-$m_{\Aprime}$.  
+The kinematics of \Aprime{} production typically results in final state particles within a few degrees of the incoming beam, especially at low 
+$m_{\Aprime{}}$.  
 %Step
-This implies that the apparatus for an \Aprime search in electron interactions with fix targets must operate in 
+This implies that the apparatus for an \Aprime{} search in electron interactions with fix targets must operate in 
 close proximity to an intense electron beam that passes through a high-Z target. 
@@
 charged particles and reconstruction of their momentum and angles. The precise measurements 
-forms the primary input to the extraction of a signal from \Aprime decays; both from the precise 
-measurement of the invariant mass of its \ee decay products and the position of its decay vertex 
+forms the primary input to the extraction of a signal from \Aprime{} decays; both from the precise 
+measurement of the invariant mass of its \ee{} decay products and the position of its decay vertex 
 downstream of the target. Track reconstruction is also important for energy scale calibration of the 
@@
 %important aspect was that, after proving the technical concepts,  the apparatus would have the 
-%capability to discover \Aprime events. The implication was that the design of the SVT in the 
+%capability to discover \Aprime{} events. The implication was that the design of the SVT in the 
 %HPS Test apparatus would be subject to almost the same constraints and requirements as the full 
@@
 primary beam. At the edge of this ``dead zone," the radiation dose approaches $10^{15}$ electrons/cm
-$^2$/month, or roughly $3 \times 10^{14}$~\fluenceunit/month~\cite{Rashevskaya:2002nd}, as shown in 
+$^2$/month, or roughly $3 \times 10^{14}$~\fluenceunit{}/month~\cite{Rashevskaya:2002nd}, as shown in 
 Fig.~\ref{fig:radiation} and~\ref{fig:rates}.
@@
 %\item >95\% reconstruction efficiency for electron and positrons  with energy down to $XXXX$~MeV,
-%\item momentum resolution of XXXX\% to separate a promptly decaying \Aprime signal from the irreducible background,
-%\item vertex resolution $<XXXX$~mm along the beam line direction to search for displaced \Aprime decays,
+%\item momentum resolution of XXXX\% to separate a promptly decaying \Aprime{} signal from the irreducible background,
+%\item vertex resolution $<XXXX$~mm along the beam line direction to search for displaced \Aprime{} decays,
 %\item event timing resolution down to 2~ns, 
@@
 
-A realistic \geant~\cite{Agostinelli2003250} simulation of the detector based on the {\sc SLIC} simulation 
+A realistic \geant{}~\cite{Agostinelli2003250} simulation of the detector based on the {\sc SLIC} simulation 
 package~\cite{Graf:2011zzc}
@@
 The sensors for the SVT are selected according to a number of requirements.  First, the sensors must be 
-radiation tolerant to approximately $1.5\times10^{14}$~\fluenceunit for a six month run.  This 
+radiation tolerant to approximately $1.5\times10^{14}$~\fluenceunit{} for a six month run.  This 
 corresponds to about 4~MHz/mm$^2$, so the sensor and readout technology must be capable of handling 
@@
 operable to 1000~V and therefore remain fully depleted to a dose of approximately 
-$1.5\times10^{14}$~\fluenceunit.
+$1.5\times10^{14}$~\fluenceunit{}.
 
@@
 
-By selecting \ee pairs from the triggered events we are able to study basic distributions of pair production 
+By selecting \ee{} pairs from the triggered events we are able to study basic distributions of pair production 
 kinematics and in particular those related to our vertex performance. Pairs of opposite charge tracks, one in the 
@@
 material and the model used for simulating multiple scattering in the target.  
-These are crucial for benchmarking the HPS \Aprime physics reach since both the mass and vertex resolution 
+These are crucial for benchmarking the HPS \Aprime{} physics reach since both the mass and vertex resolution 
 that determine the sensitivity are limited by multiple scattering.
@@
 \label{sec:trigger}
-The trigger system is designed to efficiently select \ee events by 
+The trigger system is designed to efficiently select \ee{} events by 
 using information from the ECal . The trigger looks for time coincidences of clusters in the top and bottom half 
@@
 Occupancies close to the beam create many of the key challenges in the HPS experiment
-and determine the limits of sensitivity to low \Aprime masses.
+and determine the limits of sensitivity to low \Aprime{} masses.
 These occupancies are dominated by electrons which have multiple Coulomb scattered (MCS) 
@@
 to gain further confidence in the expected detector occupancy in the full HPS experiment. 
-Previous studies of multiple scattering angles show good agreement with the \moliere 
+Previous studies of multiple scattering angles show good agreement with the \moliere{} 
 theory~\cite{Moliere:1948zz} for a wide range 
@@
 the angular distribution $F(\theta)$ in the differential cross section $d\sigma = F( \theta) d(\cos\theta) d\phi$ 
-for the \egs~\cite{egs5} simulation program show good agreement with \moliere's analytical formula as 
+for the \egs{}~\cite{egs5} simulation program show good agreement with \moliere{}'s analytical formula as 
 formulated by Bethe~\cite{Bethe:1953va}. 
@@
 Saunderson~\cite{Goudsmit:1940zza,Goudsmit:1940zz} that is valid for any angle. 
-While \egs uses the more complex and time consuming \moliere 
-formula, \geant uses an approximation with two, continuously joined, functions to take into account 
-small and large angle scattering. Due to the explicit function in large angle approximation used by \geant 
-we expect that \geant will overestimate the angular distribution at angles larger than a few mrad.
+While \egs{} uses the more complex and time consuming \moliere{} 
+formula, \geant{} uses an approximation with two, continuously joined, functions to take into account 
+small and large angle scattering. Due to the explicit function in large angle approximation used by \geant{} 
+we expect that \geant{} will overestimate the angular distribution at angles larger than a few mrad.
 
@@
 Converter thickness & Duration &  $e^-$ on converter \\
- (\%r.l.) & (s) & (nC)    \\   
+ (\%$X_0$) & (s) & (nC)    \\   
 \hline
@@
 sample was much less than 2\%. These measured angular distributions are compared to simulation to validate 
-the modeling of the MCS. \egs~\cite{egs5} is used to generate 
-the electromagnetic interactions in the converter while \geant is used to simulate the particles after the 
+the modeling of the MCS. \egs{}~\cite{egs5} is used to generate 
+the electromagnetic interactions in the converter while \geant{} is used to simulate the particles after the 
 converter.  Figure~\ref{fig:ang_distr_dataMC} shows the angular distribution comparing data and 
-\egs normalized to 1~s of beam at 90~nA beam current. Taking into account systematics uncertainties 
+\egs{} normalized to 1~s of beam at 90~nA beam current. Taking into account systematics uncertainties 
 described below reasonable agreement is obtained;   total rates for each converter thickness is shown in 
@@
 	\caption{Comparison between the observed and predicted angular 
-distribution using \egs for a converter thickness of 1.6\% (left), 0.45\% (middle) and 0.18\% 
+distribution using \egs{} for a converter thickness of 1.6\% (left), 0.45\% (middle) and 0.18\% 
 (right).  Only statistical uncertainties are shown. }
@@
 	\includegraphics[ scale=0.3]{figures/dataMC_egs.png}
-	\caption{\small{The measured rate as a function of converter thickness comparing \geant (left) 
-	and \egs (right)}.} 
+	\caption{\small{The measured rate as a function of converter thickness comparing \geant{} (left) 
+	and \egs{} (right)}.} 
 	\label{fig:rate_vs_thickness}
@@
 background normalization and limited Monte Carlo statistics.  
-\begin{center}
-{\small
 \begin{table}
+\begin{center}
+{\small
 \begin{tabular}{|l|c|c|c|}
 \hline
-Converter (\% r.l.) & 1.60 & 0.45 &	0.18 \\
+Converter (\% $X_0$) & 1.60 & 0.45 &	0.18 \\
 \hline
-\egs &	1162 $\pm$ 112 &	255 $\pm$ 28 &	94 $\pm$ 17	\\
+\egs{} &	1162 $\pm$ 112 &	255 $\pm$ 28 &	94 $\pm$ 17	\\
 \hline
-\geant & 2633 $\pm$ 250 & 	371 $\pm$ 38 &	114 $\pm$ 18 \\
+\geant{} & 2633 $\pm$ 250 & 	371 $\pm$ 38 &	114 $\pm$ 18 \\
 \hline
@@
 \label{tab:ang_distr_dataMC}
+}
+\end{center}
 \end{table}
-}
-\end{center}
 
@@
 In summary, the accurate modeling of the MCS is fundamental to estimate occupancies and trigger rates 
-for HPS. \egs predicts the correct angular distribution across all converter thicknesses while 
-\geant overestimates the rates; with the disagreement increasing  with larger converter thickness. 
+for HPS. \egs{} predicts the correct angular distribution across all converter thicknesses while 
+\geant{} overestimates the rates; with the disagreement increasing  with larger converter thickness. 
 This preliminary result verifies similar studies [] and gives confidence in our modeling of the MCS 
-using \egs for evaluating the physics reach of HPS.
+using \egs{} for evaluating the physics reach of HPS.
 
@@
 the observed trigger rates with that expected in simulation. The trigger rate is almost entirely due to
-photons which have converted to \ee upstream of the HPS Test setup and is sensitive to the multiple
+photons which have converted to \ee{} upstream of the HPS Test setup and is sensitive to the multiple
 Coulomb scattering of electrons and positrons in the conversion target.  Since scattered primary beam is 
@@
 we have proposed a new design for the HPS detector that builds upon the HPS Test , principally 
-by addressing the compromises made for HPS Test to ensure the best possible performance for \Aprime 
+by addressing the compromises made for HPS Test to ensure the best possible performance for \Aprime{} 
 physics within the envelope of the existing beam line layout and analyzing magnet. For the SVT, 

### 2013-10-28 hps-testrun-nim.tex
Updating SVT DAQ section and fixing figure centers.

@@
 
-\subsubsection{Support Structure}
+\subsubsection{Support Structure and Cooling}
 
@@
 chamber, less than 0.5~W per sensor. The total power consumption budget of about 40~W is removed by a 
-water/glycol mixture circulated through a flexible manifold attached to the cupper tubes in the cooling blocks. The total mass flow is about XXXXg/s to operate the sensors at XXXX degrees C.
+water/glycol mixture circulated through a flexible manifold attached to the cupper tubes in the cooling blocks. 
+During the Test run the sensors where operated at around $23^{\circ}$C with a total mass flow of 
+about XXXXg/s.
 
@@
 \label{sec:svtdaq}
-The SVT Data Acquisition (DAQ) is a SLAC-standard system using consisting of a single ATCA crate with 
-two Cluster On Board (COB) cards and a 10~Gb/s switch~\cite{Larsen:2011zb}.  
-The COBs connect to Rear Transition 
-Modules (RTM) housing 14-bit ADCs that accept input data from the APV25 chips.  
-The COB house FPGA-based 
-Data Processing Modules (DPM) and the Trigger Interface (TI) to the ECal trigger.  This system is capable 
-of 20~kHz operation, whereas upgrades for the full experiment pushes this up to 50~kHz. 
-Power is provided to each hybrid using CAEN power supplies from the decommissioned CDF SVXII 
-detector.
-
-{\bf  This needs to be expanded. I should talk about the data reduction and event handling. }
+The SVT data acquisition (DAQ) based on the Reconfigurable Cluster Element (RCE) and Cluster 
+Interconnect (CI) concept developed at SLAC as generic building blocks for DAQ systems in high energy 
+physics {\bf [need reference]}. 
+The RCE is a generic computational building block, housed on a separate daughter card called 
+Data Processing Module (DPM), that are realized on an ATCA front board called the Cluster On Board (COB), 
+see Fig.~\ref{fig:cob}.
+ \begin{figure}[]
+\begin{center}
+{\small
+	\includegraphics[width=6cm]{figures/svt_daq_module}
+	\caption{Picture of the SVT DAQ COB board with four data processing daughter cards visible.}
+	\label{fig:cob}
+}
+\end{center}
+\end{figure}
+The Gen-I RCE used in the Test run consisted of a Virtex~5 FPGA with 1~GB of DDR3 RAM. 
+The outputs of 12 SVT half-modules 
+are digitized on the Rear-Transition-Module (RTM), a custom board on the back side of the ATCA crate, 
+interfacing the HPS readout to the generic DAQ components on the COB. 
+A pre-amplifier converts the APV25 differential current output to a different voltage output scaled to the sensitive 
+range of a 14-bit ADC operating at the system clock of 41.667~MHz. 
+The RTM is organized into four sections with each section supporting three SVT half-module hybrids (15 
+APV25 channels). The RTM also includes a 4-channel Fiber Optic module and supporting logic which can be 
+used to interface to the JLab trigger system supervisor.
+Each section of the RTM, up to three hybrids, is input to a DPM which apply thresholds for data reduction and 
+organizes the sample data into UDP datagrams. The DPM also hosts an I2C controller used to configure and 
+monitor the APV25 chips on those three hybrids. A single ATCA crate with two COB cards was used, one 
+supporting four DPMs and one supporting 3 DPMs and one DPM that is configured as the trigger and data 
+transmission module. The two COB cards and their DPMs are interconnected with a 10Gb/s switch 
+card~\cite{Larsen:2011zb} which 
+also hosts two 1Gb/s Ethernet interfaces to the external SVT DAQ PC.
+
+The external PC supports three network interfaces; two standard 1Gb/s Ethernet and one custom low latency 
+data reception card. The first Ethernet interface is used for slow control and monitoring of the 8 DPM modules. 
+The second Ethernet interface serves as the interface to the JLAB data acquisition system. The third custom low 
+latency network interface is used to receive data from the SVT ATCA crate and supports a low latency, reliable 
+TTL trigger acknowledge interface to the trigger DPM. This PC hosts the SVT control and monitoring software 
+as well as the JLab read out controller (ROC) application described in more detail in Sec.~\ref{sec:daq}.
+
+This system is capable of operating up to 20~kHz and XXXX~MB/s which is well in line with the rates 
+expected and observed during the HPS Test run.
 
@@
 \begin{center}
+{\small
 	\includegraphics[width=6cm]{figures/08062012_run1351_samples_vs_amplitude}
-    	\caption{{\small The six pedestal subtracted samples from individual channels associated with a hit on a 
-	track.}}
+    	\caption{The six pedestal subtracted samples from individual channels associated with a hit on a 
+	track.}
 	\label{fig:pulse_shape}
-	\end{center}
-\end{figure}
+}
+\end{center}
+\end{figure}
+
 These hits are passed through a simple clustering algorithm which forms clusters by grouping adjacent 
@@
 \begin{center}
+{\small
 	\includegraphics[width=6cm]{figures/run1351_mip_small.pdf}
-    	\caption{{\small The cluster charge distribution for hits associated with a track. }}
+    	\caption{ The cluster charge distribution for hits associated with a track. }
 	\label{fig:cluster_pulse}
+}
 \end{center}
@@
 \begin{center}
+{\small
 %	\includegraphics[width=7cm]{figures/top_track_time.pdf}
 	\includegraphics[width=6cm]{figures/t0_resolution.pdf}
-	\caption{\small{
+	\caption{
 %	Track time distribution (left) and cluster time residual (right).
@@
 The width of the distribution is due to trigger jitter (24~ns jitter in the tracker readout clock, plus 16~ns jitter in the trigger system).
-	The cluster time residual is for a representative sensor relative to the track time.}}
+	The cluster time residual is for a representative sensor relative to the track time.}
 	\label{fig:tracktime}
+}
 \end{center}
@@
 \begin{center}
+{\small
     	\includegraphics[width=7cmh]{figures/hit_efficiency_vs_layer.pdf}
-        \caption{{\small The hit reconstruction efficiency as a function of detector layer.}} 
+        \caption{ The hit reconstruction efficiency as a function of detector layer.}
 	\label{fig:hit_efficiency}
-	\end{center}
-\end{figure}
-
+}
+\end{center}
+\end{figure}
 The spatial resolution of similar microstrip sensors is well established by test beam data, against which the 
@@
 Figure~\ref{fig:ecal-module} shows a schematic view of the module assembly.
-\begin{center}
-{\small
 \begin{figure}[]
+\begin{center}
+{\small
 \includegraphics[width=7cm]{figures/ecal-module-schematic.png}
@@
 \label{fig:ecal-module}
-\end{figure}
-}
-\end{center}
+}
+\end{center}
+\end{figure}
 The gain uniformity of the APDs is on the order of XXXX\%; with APD high voltage bias varying by as 
@@
 , and iteratively adjust the gains until the weighted E/p is equal for test run data and simulation.
-\begin{figure}[ht]
+\begin{figure}[]
+\begin{center}
+{\small
 	\includegraphics[width=7cm]{figures/ecalgainplots_corr_sim}
 	\includegraphics[width=7cm]{figures/gains}
-	\caption{\small{Weighted E/p from Monte Carlo simulation (top), calibrated values of gain in units of MeV 
-	per ADC count (bottom).}}
+	\caption{Weighted E/p from Monte Carlo simulation (top), calibrated values of gain in units of MeV 
+	per ADC count (bottom).}
 	\label{fig:gains}
+}
+\end{center}
 \end{figure}
@@
 shown in Fig. ~\ref{fig:fadc}. 
-\begin{center}
-{\small
 \begin{figure}[t]
+\begin{center}
+{\small
 \includegraphics[width=7cm]{figures/FADC250_Photo_001.jpg}
@@
 \label{fig:fadc}
-\end{figure}
-}
-\end{center}
+}
+\end{center}
+\end{figure}
 Three 20-slot VXS crates are needed to accommodate the system: one for each half of the ECal with 221 
@@
 It is a fixed gate width pulse integration with no pedestal subtraction where the sum is stored in a 17-bit register for readout (pedestal subtraction happens offline).
-\begin{center}
-{\small
 \begin{figure}[]
+\begin{center}
+{\small
 \includegraphics[width=7cm]{figures/hps_trigger_data}
@@
 \label{fig:hps_trigger_data}
-\end{figure}
-}
-\end{center}
+}
+\end{center}
+\end{figure}
 For the trigger path, every channel has, in addition to $NSB$ and $NSA$: 
@@
  \end{itemize}
-\begin{center}
-{\small
  \begin{figure}[t]
+\begin{center}
+{\small
  \includegraphics[width=7cm]{figures/hps_trigger_cal}
@@
  \label{fig:hps_trigger_cal}
- \end{figure}
-}
-\end{center}
+}
+\end{center}
+ \end{figure}
 The time coincidence window of pairs of clusters in the top and bottom half of the ECal are programmable 
@@
 These turn-on curves are shown for the top half of the ECal in Fig.~\ref{fig:turnon}. 
-\begin{center}
-{\small
 \begin{figure}[ht]
+\begin{center}
+{\small
 	\includegraphics[width=7cm]{figures/top_turnon_adc}
@@
 \label{fig:turnon}
-\end{figure}
-}
-\end{center}
+}
+\end{center}
+\end{figure}
 The trigger threshold is seen to be 1280 ADC counts as expected. The threshold is not perfectly sharp in this 
@@
 \subsection{Data Acquisition and Online Computing}
+\label{sec:daq}
 For the ECal, every VXS crate contains a Readout Controller (ROC)
@@
 Fig.~\ref{fig:ang_distr_data} (left).  
-\begin{center}
-{\small
 \begin{figure}[]
+\begin{center}
+{\small
 	\includegraphics[ width=7cm]{figures/rate_ecalrow_raw.png}
@@
 	\label{fig:ang_distr_data}
-	\end{figure}
-}
-\end{center}
+}
+\end{center}
+\end{figure}
 The background fraction for the three converter thicknesses was 16\%, 52\% and 71\% 
@@
 	\includegraphics[ scale=0.3]{figures/dataMC_egs.png}
-	\caption{\small{The measured rate as a function of converter thickness comparing \geant{} (left) 
-	and \egs{} (right)}.} 
+	\caption{The measured rate as a function of converter thickness comparing \geant{} (left) 
+	and \egs{} (right).} 
 	\label{fig:rate_vs_thickness}

### 2013-11-03 hps-testrun-nim.tex
Added Stepans edits of ecal and daq. Updated turn-on and eoverp from Sho with new root style. Removed gain plot. Removed turn-on vs energy since I didnt have that plot with new style. Added references for clas IC and FADC

@@
 \subsection{SVT Digitization, Event Building and Data Transmission}
-\label{sec:svtdaq}
+\label{sec:svt_daq}
 The SVT data acquisition (DAQ) based on the Reconfigurable Cluster Element (RCE) and Cluster 
@@
 The samples from every channel on a sensor surviving the 
-data reduction algorithm (see Sec.~\ref{sec:svtdaq}) are the basis for offline hit reconstruction. 
+data reduction algorithm (see Sec.~\ref{sec:svt_daq}) are the basis for offline hit reconstruction. 
 The six samples of the APV25 shaper output 
@@
 \section{Electromagnetic Calorimeter}
-\label{ecal}
-
-The electromagnetic calorimeter just downstream of the tracker uses detectors with comparably short 
-live time and high rate capability. It performs two essential functions for the experiment: triggering and 
-electron identification. The device is highly segmented. It is fast, able to readout at rates comparable to 
-those in the tracker, and able to provide good spatial and energy information to the trigger electronics. Like 
-the tracker system, the electromagnetic calorimeter is split to avoid impinging on the “dead zone”. The beam 
-and radiative secondaries pass through the calorimeter in vacuum, to avoid generating unnecessary backgrounds.
+\label{sec:ecal}
+
+The electromagnetic calorimeter, installed downstream of the tracker, performs two essential functions for the experiment: provides a trigger to DAQ system and 
+is used in the analysis for electron identification. 
+%The device is highly segmented.
+It is fast, able to readout at rates comparable to those in the tracker, and able to provide good spatial and energy information to the trigger electronics.
+Like the tracker, the electromagnetic calorimeter is split to avoid impinging on the “dead zone”.
+The beam and radiative secondaries pass between the two of the calorimeter in vacuum, to avoid generating unnecessary backgrounds.
+%Step\subsection{Purpose and Design Requirements}
+%StepThe electromagnetic calorimeter (ECal) provide the trigger for the data acquisition and will be used for electron identification during the data analysis.
+The ECal is positioned after the analyzing dipole magnet and cover the full acceptance region of the SVT.
+It consist of two halves, split in the horizontal beam plane.
+The gap between upper and lower parts, $XXXX$~mrad (15mrad for electron running),  as seen from the target location, is necessary to avoid the "dead zone" where occupancy and radiation prevents any instrumentation to be situated.
+The energy of electrons of interest in HPS experiment will be in the range 
+$0.5-6.5$~GeV. The ECal modules must have sufficient radiation lengths to absorb the full energy of these 
+scattered electrons, have fine enough granularity to handle a high rate of electromagnetic 
+background and survive large doses of radiation, especially near the beam plane. In addition, it needs to 
+have excellent hit time resolution, $<10$~ns, in order to beat down beam backgrounds.
+
+Requirements of a compact design, operation at high radiation and high rate environment, in the presence of a 
+high magnetic field are fulfilled by a lead-tungstate (PbWO$_{4}$) crystal calorimeter with magnetic field 
+resistant Avalanche Photodiode (APD) readout.  Such calorimeter has been operational in the inner 
+part of the CLAS detector for experiments in Hall-B at JLab since 2005 and meet all requirements set by 
+HPS. The modules from this calorimeter have been subsequently repurposed for the ECal.
 
@@
 
-\subsection{Layout}
-The modules in the ECal are arranged in two formations, as shown in Fig.~\ref{fig:ecal}. 
-\begin{center}
-{\small
-\begin{figure*}[]
-\includegraphics[width=7cm]{figures/ECal}
-\includegraphics[width=7cm]{figures/ecal_assembly}
-\caption{Schematic layout view of the two halves of the ECal (left) and a picture of one half being assembled before installation on beam line (right). }
-\label{fig:ecal}
-\end{figure*}
-}
-\end{center}
-There are 5 layers in each formation. Each layer has $46$ crystals except for the layers closest to the beam 
-plane where 9 modules were removed to allow a larger opening for the outgoing electron and photon beams. 
-The ECal is mounted downstream of the analyzing dipole magnet at the distance of about $137$~cm from the 
-upstream edge of the magnet. The two ECal modules are positioned just above and below the ECal vacuum 
-chamber, through which the beam, radiated photons, and the wall of flame will pass
-unimpeded. The innermost edge of the crystals is just $2$~cm from the beam.
-
 \subsection{ECal Components}
 
-\subsubsection{PbWO$_4$ Crystals}
-The ECal PbWO$_{4}$ crystals, from the same crystals that were used in the IC.
-The IC calorimeter was assembled from 424 lead tungstate tapered crystals with dimensions of $13.3\times13.3$~mm$^2$ (front face), $16\times16$~mm$^2$ (rear face) and 160~mm length.
+%Step\subsubsection{PbWO$_4$ Crystals}
+The HPS test run ECal uses PbWO$_{4}$ crystals, APDs, and preamplifier boards from the inner calorimeter (IC) of the CLAS detector~\cite{2008erhm.conf..421N}.
+In Fig.~\ref{fig:ecal-module} a schematic view of the module assembly is shown.
+Lead-tungstate crystals are $160$ mm long and are tapered with front face of $13.3\times13.3$~mm$^2$, tapered to $16\times16$~mm$^2$ at the rear face.
 The crystals were fabricated with very tight tolerances: $19~\mu$m for 13.3~mm dimension and $13~\mu$m for the 16~mm dimension.
 Each crystal is wrapped in VM2000 multilayer polymer mirror film.
-
-\subsubsection{Support Structure}
-In order to stabilize the 
-calorimeter's performance, the crystals, APDs, and amplifiers are enclosed within a temperature controlled 
-environment, held constant at the level of $1^\circ~$F.
-
-\subsubsection{Avalanche Photodiode Readout and Preamplifiers}
-\label{sec:apd}
-Avalanche Photodiodes (APD) S8664-55 produced by Hamamatsu Corp. are used as photodetectors. 
-They have a $5\times5$~mm$^2$ active area and quantum efficiency of about 75\%. Single APDs were 
-centered on the back ends of the crystals using MeltMount 1.7 thermal plastic adhesive. 
-The low? amplitude signals of APDs are amplified using custom?made preamplifier boards. 
-Figure~\ref{fig:ecal-module} shows a schematic view of the module assembly.
+The APDs (Hamamatsu S8664-55) with $5\times5$~mm$^2$ active area and $75\%$ quantum efficiency were glued on the rear face of the crystals using MeltMount 1.7 thermal plastic adhesive.
+The low gain of APDs ($\sim 200$) was compensated with custom made preamplifier boards, which provide factor 2000 amplification of the ADP signal.
+
 \begin{figure}[]
@@
 \end{figure}
-The gain uniformity of the APDs is on the order of XXXX\%; with APD high voltage bias varying by as 
-much as 100V. Since only a limited number of high voltage channels were available during the test, 10 
-channels were grouped together with an attempt to group modules with similar gains.
-
-The signals from the preamplifier boards were sent, through a $2:1$ signal splitter to a time-to-digital 
-converter and the Flash ADC readout boards discussed in Sec.~\ref{sec:fadc}.
-
-\subsection{Calibration and Performance}
+
+\subsection{Layout}
+
+Like the tracker, the electromagnetic calorimeter is split into two parts, beam-up and beam-down, to avoid impinging on the “dead zone”.
+The two parts of the Ecal are separated by a vacuum chamber, see Fig.~\ref{fig:ecal}.
+The beam and radiative secondaries pass between the two parts in vacuum, to avoid generating unnecessary backgrounds.
+The crystal modules in each part are arranged in rectangular formation, as shown in top panel of Fig.~\ref{fig:ecal}.
+There are 5 layers in each formation.
+Each layer has $46$ crystals except for the layers closest to the beam
+plane where 9 modules were removed to allow a larger opening for the outgoing electron and photon beams. 
+In order to have stable light yield from crystals, and stable operation of APDs and preamplifiers, the module assembly of each ECal part was enclosed inside a temperature controlled box.
+
+Inside the box PbWO$_{4}$ crystals were supported by aluminum frames stacked on top of each other.
+The bias voltage for APDs ($\sim 400$ V), the low voltage for preamplifiers ($\pm 5$ V), and the signals from APDs were transmitted in and out of the enclosure through a backplane called motherboard.
+The $221$ modules in each part of the ECal were divided into two low voltage groups and 12 bias voltage groups.
+Modules in bias voltage groups were selected to have gain uniformity of $\sim 20\%$.
+
+During the test run ECal was mounted downstream of the analyzing dipole magnet at the distance of about $147$~cm from the 
+upstream edge of the magnet. 
+%The two ECal modules are positioned just above and below the ECal vacuum chamber as shown in bottom panel of Fig.~\ref{fig:ecal}. 
+%The primary electron beam, scattered electrons and bremsstrahlung photons pass through the system in vacuum. 
+The gap between innermost edge of the crystals of two parts was just $7.4$~cm from the beam.
+The temperature stability of the system during the test run was better than $1^\circ~$F, the temperature uniformity inside the box was better than  $4^\circ~$F.
+
+\begin{center}
+{\small
+\begin{figure}
+\includegraphics[width=7cm]{figures/ECal}
+\includegraphics[width=7cm]{figures/ecal_vacuumchamber.pdf}
+%\includegraphics[width=7cm]{figures/ecal_assembly}
+\caption{Layout of PbWO$_{4}$ modules in two halves of the ECal (top) and ECal assembly together with ECal vacuum chamber (bottom). }
+\label{fig:ecal}
+\end{figure}
+}
+\end{center}
+%Step \subsubsection{Support Structure}
+%Step In order to stabilize the calorimeter's performance, the crystals, APDs, and amplifiers are enclosed within a temperature controlled environment, held constant at the level of .
+%Step\subsubsection{Avalanche Photodiode Readout and Preamplifiers}
+%Step\label{sec:apd}
+%StepAvalanche Photodiodes (APD) S8664-55 produced by Hamamatsu Corp.
+are used as photodetectors.
+They have a $5\times5$~mm$^2$ active area and quantum efficiency of about 75\%.
+Single APDs were centered on the back ends of the crystals using MeltMount 1.7 thermal plastic adhesive.
+The low?
+amplitude signals of APDs are amplified using custom?made preamplifier boards.
+%The gain uniformity of the APDs is on the order of XXXX\%; with APD high voltage bias varying by as much as 100V.
+Since only a limited number of high voltage channels were available during the test, 10 channels were grouped together with an attempt to group modules with similar gains.
+
+\subsection{Signal readout}
+\label{sec:fadc}
+Amplified APD signal from the motherboard is sent to a $2:1$ signal splitter. After the split, 2/3 of the signal is sent a discriminator then to a Time-to-Digital 
+Converter (TDC). The 1/3 of the signal is fed to a single channel of 16-channel JLAB Flash Amplitude-to-Digital Converter VXS module (FADC250)~\cite{fadc}, see Fig.\ref{fig:fadc}.  
+\begin{figure}[t]
+\begin{center}
+{\small
+\includegraphics[width=7cm]{figures/FADC250_Photo_001.jpg}
+\caption{A Jefferson Lab FADC250 VXS module.}
+\label{fig:fadc}
+}
+\end{center}
+\end{figure}
+Two 20-slot VXS crates with 14 FADC bards were needed to accommodate the system: one for each half of the ECal with 221 
+channels.
+
+The FADCs store 12-bit digitized samples at 250~MHz in 8~$\mu$s deep pipelines. 
+When a trigger is received, the appropriate part of the pipeline is accessed for the readout.
+HPS used FADCs in the integration mode.
+A predefined number of samples of the signal that exceeds a predefined threshold have been summed and stored in 17-bit register for readout.
+The number of samples for integration was defined by two parameters that could be set separately, the number of samples integrated before the signal crossed threshold ($NSB$) and  the number of samples integrated after the signal crossed threshold ($NSA$), see Fig.\ref{fig:hps_trigger_data}.
+This scheme significantly compresses the data input 
+to the FADC. During data analysis, a pedestal value is subtracted to obtain the actual summed energy.
+
+\begin{figure}[]
+\begin{center}
+{\small
+\includegraphics[width=7cm]{figures/hps_trigger_data}
+\caption{\small{FADC data paths}}
+\label{fig:hps_trigger_data}
+}
+\end{center}
+\end{figure}
+
+subsection{Calibration and Performance}
 \label{sec:ecal_calibration}
-Of 442 modules, 39 were disabled or disconnected and were not read out by the DAQ. 
+
+For various reasons only 385 out of 442 modules (87\%) were operational during the test run.  Of 442 modules, 39 were disabled or disconnected and were not read out by the DAQ. 
 13 of these were not read out because of a shortage of FADC readout boards (see Sec.~\ref{sec:fadc}).
@@
 {\small
-	\includegraphics[width=7cm]{figures/ecalgainplots_corr_sim}
-	\includegraphics[width=7cm]{figures/gains}
-	\caption{Weighted E/p from Monte Carlo simulation (top), calibrated values of gain in units of MeV 
-	per ADC count (bottom).}
+	\includegraphics[width=7cm]{figures/eoverp_simulation}
+	\caption{Weighted E/p from Monte Carlo simulation after gain calibration.}
 	\label{fig:gains}
@@
 
-\subsection{Monitoring}
+%Step\subsection{Monitoring}
 
@@
 \section{Trigger and Data Acquisition}
-The HPS Test apparatus DAQ handles the acquisition of data for two sub-detectors: the 
-SVT and ECal . It employs two DAQ architectures: the SVT is readout with Advanced 
-Telecom Communications Architecture (ATCA) hardware while the ECal and Muon System use VXS based 
+
+The HPS Test apparatus DAQ handles the acquisition of data from two sub-detectors: the 
+SVT and the ECal, with two DAQ architectures. The SVT is readout with Advanced 
+Telecom Communications Architecture (ATCA) hardware while the ECal uses VXS based 
 hardware. The trigger system receives input from the ECal and distributes a trigger signal 
@@
 
-\subsection{Electronics}
-\label{sec:electronics}
-
-\subsubsection{Flash ADC Readout Board}
-\label{sec:fadc}
-The analog signals from the individual APD's of the ECal (shaped and amplified as described in 
-Sec.~\ref{sec:aid}) are input to a single channel on the 16-channel JLab FADC250 VXS module (FADC), 
-shown in Fig. ~\ref{fig:fadc}. 
+\subsection{Trigger system}
+\label{sec:trigger}
+
+The HPS test run trigger system is designed to efficiently select \ee{} events by 
+using information from the ECal . The trigger looks for time coincidences of clusters in the top and bottom half 
+of the ECal.  The trigger system can be broken down into three sections (see Fig.~\ref{fig:hps_trigger_cal}):
+ \begin{itemize}
+ \item FADC (pulse finding): samples and digitizes the signal pulses from each detector channel. Sends the measured pulse energy and arrival time to the Crate Trigger Processor (CTP),
+\item CTP (cluster finding): groups FADC pulses from each half of the ECal into clusters. The cluster energy and arrival time are sent to the Sub-System Processor (SSP),
+ \item SSP (cluster pair finding): searches for time coincidence of pairs of clusters from the top and bottom half of the ECal and applies topological selections.
+ \end{itemize}
  \begin{figure}[t]
@@
 {\small
-\includegraphics[width=7cm]{figures/FADC250_Photo_001.jpg}
-\caption{A Jefferson Lab FADC250 VXS module.}
-\label{fig:fadc}
-}
-\end{center}
-\end{figure}
-Three 20-slot VXS crates are needed to accommodate the system: one for each half of the ECal with 221 
-channels and one for the Muon System with a total of 232 channels.
-
-The FADCs store 12-bit digitized samples at 250~MHz in 8~$\mu$s deep pipelines. 
-When a trigger is received, the appropriate part of the pipeline is accessed. If a FADC   
-signal exceeds a predefined threshold within that time window, the integrated amplitude of a pre-defined 
-number of samples before (NSB) and after (NSA) the signal passed threshold, in addition to the time, are 
-recorded. 
-%as explained in Fig.~\ref{fig:hps_trigger_data}. 
-This scheme significantly compresses the data input 
-to the FADC. During data analysis, a pedestal value is subtracted to obtain the actual summed energy.
-The main characteristics of the FADC are:
-\begin{itemize}
-\item 12-bit digitizer with sampling rate of 250~Msps, 
-\item 50$\Omega$ termination input, 
-\item front-end input range:  -0.5V, -1V or -2V (sufficient to avoid signal clipping for large pulse heights),
-\item nominal charge resolution between 10-39~fC per ADC (see Tab.~\ref{tab:charge_resolution}).
-\end{itemize}
-\begin{center}
-{\small
-\begin{table}[h]
-\centering
-\begin{tabular}{|c|c|}
-\hline
-Input range & Nominal charge resolution\\
-(V) & (fC per ADC count)\\\hline
--0.5 & 9.76  \\\hline
--1.0 & 19.53  \\\hline
--2.0 & 39.06 \\\hline
-\end{tabular}
-\caption{Nominal FADC charge resolution for different front-end input ranges.}
-\label{tab:charge_resolution}
-\end{table}
-}
-\end{center}
-As shown in Fig.~\ref{fig:hps_trigger_data}, the FADC has two parallel data paths: the readout and trigger paths.
-The trigger path runs continuously to report hits to the trigger system.
-The readout path only reports hits to the DAQ when the FADC receives a trigger.
-
-For the readout path, every FADC has the following parameters:
- \begin{itemize}
- \item the number of samples integrated before the signal crossed threshold ($NSB$), 
- \item the number of samples integrated after the signal crossed threshold ($NSA$),
- \item the readout threshold, measured in ADC counts.
- \end{itemize}
-The number of samples for a given channel integration is the sum of $NSB+NSA$ samples.
-It is a fixed gate width pulse integration with no pedestal subtraction where the sum is stored in a 17-bit register for readout (pedestal subtraction happens offline).
-\begin{figure}[]
-\begin{center}
-{\small
-\includegraphics[width=7cm]{figures/hps_trigger_data}
-\caption{\small{FADC data paths}}
-\label{fig:hps_trigger_data}
-}
-\end{center}
-\end{figure}
+ \includegraphics[width=7cm]{figures/hps_trigger_cal}
+\caption{Block diagram of the ECAL trigger system consisting of the FADC that samples and digitizes the detector channel signals and sends them for cluster finding in the CTP.
+The CTP clusters are sent to the SSP where the final trigger decision is taken based on pairs of clusters in both halves of the ECal.
+The decision is sent to the Trigger Supervisor (TS) that generates the necessary signals to readout the sub-detectors.}
+ \label{fig:hps_trigger_cal}
+}
+\end{center}
+ \end{figure}
+The time coincidence window of pairs of clusters in the top and bottom half of the ECal are programmable 
+with 4~ns resolution.
+
+As described above, the first stage of the trigger logic is incorporated into the 
+FPGA's on the FADC boards. 
 For the trigger path, every channel has, in addition to $NSB$ and $NSA$: 
@@
 converted to MeV units using a supplied gain conversion factor. The energy discriminator can be used to cut 
-off low energy pulses before reporting to the Crate Trigger Processor. 
-The values reported to the Crate Trigger Processor are the 13-bit pulse energy and the time at which the 
-pulse crossed the threshold. Data for every channel is sent every 32~ns (if there is no hit a 0 energy pulse is 
-sent) which sets a worst case double pulse resolution of 32~ns for individual channels, but less if pulses 
-occur in adjacent 32~ns windows.
-
-\subsubsection{Trigger Boards}
-Describe CTP and SSP?
-
-\subsection{Trigger}
-\label{sec:trigger}
-The trigger system is designed to efficiently select \ee{} events by 
-using information from the ECal . The trigger looks for time coincidences of clusters in the top and bottom half 
-of the ECal.  The trigger system can be broken down into three sections (see Fig.~\ref{fig:hps_trigger_cal}):
- \begin{itemize}
- \item FADC (pulse finding): samples and digitizes the signal pulses from each detector channel. Sends the measured pulse energy and arrival time to the CTP.
-\item CTP (cluster finding): groups FADC pulses from each half of the ECal into clusters. The cluster energy, arrival time, and hit pattern are sent to the SSP.
- \item SSP (cluster pair finding): searches for time coincidence of pairs of clusters from the top and bottom half of the ECal and applies topological selections.
- \end{itemize}
- \begin{figure}[t]
-\begin{center}
-{\small
- \includegraphics[width=7cm]{figures/hps_trigger_cal}
-\caption{Block diagram of the ECAL trigger system consisting of the FADC that samples and digitizes the detector channel signals and sends them for cluster finding in the CTP.
-The CTP clusters are sent to the SSP where the final trigger decision is taken based on pairs of clusters in both halves of the ECal.
-The decision is sent to the Trigger Supervisor (TS) that generates the necessary signals to readout the sub-detectors.}
- \label{fig:hps_trigger_cal}
-}
-\end{center}
- \end{figure}
-The time coincidence window of pairs of clusters in the top and bottom half of the ECal are programmable 
-with 4~ns resolution.
-
-As described above in Sec.~\ref{sec:fadc}, the first stage of the trigger logic is incorporated into the 
-FPGA's on the FADC boards which sends crystal energy and time information to the CTP. With the available 
+off low energy pulses before reporting to CTP. 
+The values reported to the CTP are the 5-bit pulse energy and 3-bit time information at which the 
+pulse crossed the threshold. Data for every channel is sent to CTP every 32~ns. With the available 
 3-bit time information, the CTP looks for time coincidence of crystal signals with 8~ns resolution (limit is 4~ns).
-The cluster finding algorithm is very fast and makes use of the parallel processing nature of FPGA's by 
+The cluster finding algorithm is fast and makes use of the parallel processing nature of FPGA's by 
 simultaneously searching for 125 clusters, up to 3x3 in size, across the calorimeter crystal array and performs 
@@
 \item Adds energy from hits together for every 3x3 square of channels in ECal.
-\item Hits are added together if they occur (leading edge) within a programmable number of 4~ns clock cycles of each other (HPS will use 8~ns time coincidence time interval).
+\item Hits are added together if they occur (leading edge) within a programmable number of 4~ns clock cycles of each other (HPS test run used 8~ns coincidence time interval).
 \item If the 3x3 energy sum is larger than the programmable cluster energy threshold and the sum is greater than any neighboring 3x3 windows, the CTP reports the cluster parameters to the SSP. 
@@
 
- The final trigger decision is made in the CTP and Sub-System Processor (SSP). The Trigger Supervisor generates all necessary signals and controls the entire DAQ 
+ The final trigger decision is made by CTPs and SSP passed to the Trigger Supervisor (TS). The TS generates all necessary signals and controls the entire DAQ 
 system readout through the Trigger Interface (TI) units. The TI units are installed in every crate that participate 
@@
 50~kHz and a latency set to $\approx 3~\mu$s to match that required by the SVT APV25 chip.
+
+During the test run, for the most part trigger system run in single cluster mode and was tested to work for up to 20 kHz trigger rates.
+
+\subsection{Data Acquisition and Online Computing}
+\label{sec:daq}
+For the ECal, every VXS crate contains a Readout Controller (ROC)
+that collects digitized information, processes it, and sends it on to the Event Builder (EB). The ROC is a single 
+blade Intel-based CPU module running DAQ software under CentOS Linux OS. For the SVT ATCA system, 
+the ROC application runs on an embedded processor situated on the ATCA main board. The EB assembles 
+information from the SVT and ECal ROCs into a single event which is passed to the Event 
+Recorder (ER) that writes it to a RAID5-based data storage system capable of handling up to 100 MB/s. The 
+EB and other critical components run on multicore Intel-based multi-CPU servers. The DAQ network system is 
+a Foundry router providing high-speed connections between the DAQ components and to the JLab 
+computing facility. The SVT ROC, which must handle large data volumes, has a 10 Gbit/s link to the Foundry 
+router, while a 1 Gbit/s link is adequate for the ECal. A 10 Gbit/s uplink to the JLab 
+computing facility is used for long-term storage.
+
+The SVT DAQ is described in more details in Sec.~\ref{sec:svt_daq}.
 
@@
 {\small
-	\includegraphics[width=7cm]{figures/top_turnon_adc}
-	\includegraphics[width=7cm]{figures/top_turnon_e}
-	\caption{Trigger turn-on as a function of probe cluster ADC counts (top) and probe cluster energy in MeV 
-	(bottom). Both plots are for the top half of the ECal; bottom is similar. Energy is not corrected for sampling 
-	fraction.}
+	\includegraphics[width=7cm]{figures/top_turn_on__bottom_tag}
+	\caption{Trigger turn-on as a function of probe cluster ADC counts. }
+%	\caption{Trigger turn-on as a function of probe cluster ADC counts (top) and probe cluster energy in MeV
+%	(bottom). Both plots are for the top half of the ECal; bottom is similar. Energy is not corrected for sampling 
+%	fraction.}
 \label{fig:turnon}
@@
 issues that led to threshold variations in the test run.
-
-\subsection{Data Acquisition and Online Computing}
-\label{sec:daq}
-For the ECal, every VXS crate contains a Readout Controller (ROC)
-that collects digitized information, processes it, and sends it on to the Event Builder (EB). The ROC is a single 
-blade Intel-based CPU module running DAQ software under CentOS Linux OS. For the SVT ATCA system, 
-the ROC application runs on an embedded processor situated on the ATCA main board. The EB assembles 
-information from the SVT, ECal and Muon System ROCs into a single event which is passed to the Event 
-Recorder (ER) that writes it to a RAID5-based data storage system capable of handling up to 100 MB/s. The 
-EB and other critical components run on multicore Intel-based multi-CPU servers. The DAQ network system is 
-a Foundry router providing high-speed connections between the DAQ components and to the JLab 
-computing facility. The SVT ROC, which must handle large data volumes, has a 10 Gbit/s link to the Foundry 
-router, while a 1 Gbit/s link is adequate for the ECal and Muon System. A 10 Gbit/s uplink to the JLab 
-computing facility is used for long-term storage.
-
-The SVT DAQ is described in more details in Sec.~\ref{sec:svt_daq}.
 

### 2013-11-03 figures/top_turn_on__bottom_tag.C

@@ -1,0 +1,138 @@
+{
+//=========Macro generated from canvas: c1/c1
+//=========  (Sun Nov  3 10:54:33 2013) by ROOT version5.34/02
+   TCanvas *c1 = new TCanvas("c1", "c1",462,167,700,500);
+   c1->Range(-800.0001,-0.13125,7200,1.18125);
+   c1->SetFillColor(0);
+   c1->SetBorderMode(0);
+   c1->SetBorderSize(2);
+   c1->SetFrameBorderMode(0);
+   c1->SetFrameBorderMode(0);
+   
+   TH1F *top_turn_on__bottom_tag = new TH1F("top_turn_on__bottom_tag","",200,0,6400);
+   top_turn_on__bottom_tag->SetBinContent(38,0.1666667);
+   top_turn_on__bottom_tag->SetBinContent(40,0.1428571);
+   top_turn_on__bottom_tag->SetBinContent(42,1);
+   top_turn_on__bottom_tag->SetBinContent(43,0.75);
+   top_turn_on__bottom_tag->SetBinContent(44,0.7272727);
+   top_turn_on__bottom_tag->SetBinContent(45,0.75);
+   top_turn_on__bottom_tag->SetBinContent(46,1);
+   top_turn_on__bottom_tag->SetBinContent(47,1);
+   top_turn_on__bottom_tag->SetBinContent(48,1);
+   top_turn_on__bottom_tag->SetBinContent(49,1);
+   top_turn_on__bottom_tag->SetBinContent(50,0.9333333);
+   top_turn_on__bottom_tag->SetBinContent(51,1);
+   top_turn_on__bottom_tag->SetBinContent(52,1);
+   top_turn_on__bottom_tag->SetBinContent(53,1);
+   top_turn_on__bottom_tag->SetBinContent(54,0.8333334);
+   top_turn_on__bottom_tag->SetBinContent(55,1);
+   top_turn_on__bottom_tag->SetBinContent(56,1);
+   top_turn_on__bottom_tag->SetBinContent(57,1);
+   top_turn_on__bottom_tag->SetBinContent(58,1);
+   top_turn_on__bottom_tag->SetBinContent(59,0.8);
+   top_turn_on__bottom_tag->SetBinContent(60,1);
+   top_turn_on__bottom_tag->SetBinContent(61,1);
+   top_turn_on__bottom_tag->SetBinContent(62,0.8181819);
[…]

### 2013-11-03 hps-testrun-nim.tex
Changing from F to C. Small changes to text.

@@
 
-The electromagnetic calorimeter, installed downstream of the tracker, performs two essential functions for the experiment: provides a trigger to DAQ system and 
-is used in the analysis for electron identification. 
+The electromagnetic calorimeter, installed downstream of the tracker, performs two essential functions for the 
+experiment: provides a trigger to DAQ system and is used in the analysis for electron identification. 
 %The device is highly segmented.
@@
 %Step\subsubsection{PbWO$_4$ Crystals}
-The HPS test run ECal uses PbWO$_{4}$ crystals, APDs, and preamplifier boards from the inner calorimeter (IC) of the CLAS detector~\cite{2008erhm.conf..421N}.
-In Fig.~\ref{fig:ecal-module} a schematic view of the module assembly is shown.
-Lead-tungstate crystals are $160$ mm long and are tapered with front face of $13.3\times13.3$~mm$^2$, tapered to $16\times16$~mm$^2$ at the rear face.
-The crystals were fabricated with very tight tolerances: $19~\mu$m for 13.3~mm dimension and $13~\mu$m for the 16~mm dimension.
-Each crystal is wrapped in VM2000 multilayer polymer mirror film.
-The APDs (Hamamatsu S8664-55) with $5\times5$~mm$^2$ active area and $75\%$ quantum efficiency were glued on the rear face of the crystals using MeltMount 1.7 thermal plastic adhesive.
-The low gain of APDs ($\sim 200$) was compensated with custom made preamplifier boards, which provide factor 2000 amplification of the ADP signal.
-
+The HPS test run ECal uses PbWO$_{4}$ crystals, APDs, and preamplifier boards from the inner calorimeter (IC) 
+of the CLAS detector~\cite{2008erhm.conf..421N}.  In Fig.~\ref{fig:ecal-module} a schematic view of the module 
+assembly is shown. Lead-tungstate crystals are $160$ mm long and are tapered with front face of 
+$13.3\times13.3$~mm$^2$, tapered to $16\times16$~mm$^2$ at the rear face. The crystals were fabricated with 
+very tight tolerances: $19~\mu$m for 13.3~mm dimension and $13~\mu$m for the 16~mm dimension. Each crystal 
+is wrapped in VM2000 multilayer polymer mirror film.
+The APDs (Hamamatsu S8664-55) with $5\times5$~mm$^2$ active area and $75\%$ quantum efficiency were 
+glued on the rear face of the crystals using MeltMount 1.7 thermal plastic adhesive. The low gain of APDs ($\sim 
+200$) was compensated with custom made preamplifier boards, which provide factor 2000 amplification of the 
+ADP signal. 
 \begin{figure}[]
@@
 
-Like the tracker, the electromagnetic calorimeter is split into two parts, beam-up and beam-down, to avoid impinging on the “dead zone”.
-The two parts of the Ecal are separated by a vacuum chamber, see Fig.~\ref{fig:ecal}.
-The beam and radiative secondaries pass between the two parts in vacuum, to avoid generating unnecessary backgrounds.
-The crystal modules in each part are arranged in rectangular formation, as shown in top panel of Fig.~\ref{fig:ecal}.
-There are 5 layers in each formation.
-Each layer has $46$ crystals except for the layers closest to the beam
+Like the tracker, the electromagnetic calorimeter is split into two parts, beam-up and beam-down, to avoid 
+impinging on the “dead zone”. The two parts of the Ecal are separated by a vacuum chamber, see 
+Fig.~\ref{fig:ecal}. The beam and radiative secondaries pass between the two parts in vacuum, to avoid 
+generating unnecessary backgrounds. The crystal modules in each part are arranged in rectangular formation, as 
+shown in top panel of Fig.~\ref{fig:ecal}. There are 5 layers in each formation. Each layer has $46$ crystals except 
+for the layers closest to the beam 
 plane where 9 modules were removed to allow a larger opening for the outgoing electron and photon beams. 
-In order to have stable light yield from crystals, and stable operation of APDs and preamplifiers, the module assembly of each ECal part was enclosed inside a temperature controlled box.
-
-Inside the box PbWO$_{4}$ crystals were supported by aluminum frames stacked on top of each other.
-The bias voltage for APDs ($\sim 400$ V), the low voltage for preamplifiers ($\pm 5$ V), and the signals from APDs were transmitted in and out of the enclosure through a backplane called motherboard.
-The $221$ modules in each part of the ECal were divided into two low voltage groups and 12 bias voltage groups.
-Modules in bias voltage groups were selected to have gain uniformity of $\sim 20\%$.
-
-During the test run ECal was mounted downstream of the analyzing dipole magnet at the distance of about $147$~cm from the 
+In order to have stable light yield from crystals, and stable operation of APDs and preamplifiers, the module 
+assembly of each ECal part was enclosed inside a temperature controlled box.
+
+Inside the box PbWO$_{4}$ crystals were supported by aluminum frames stacked on top of each other.  The bias 
+voltage for APDs ($\sim 400$ V), the low voltage for preamplifiers ($\pm 5$ V), and the signals from APDs were 
+transmitted in and out of the enclosure through a backplane called motherboard. The $221$ modules in each part 
+of the ECal were divided into two low voltage groups and 12 bias voltage groups. Modules in bias voltage groups 
+were selected to have gain uniformity of $\sim 20\%$.
+
+During the test run ECal was mounted downstream of the analyzing dipole magnet at the distance of about 
+$147$~cm from the 
 upstream edge of the magnet. 
@@
 %The primary electron beam, scattered electrons and bremsstrahlung photons pass through the system in vacuum. 
-The gap between innermost edge of the crystals of two parts was just $7.4$~cm from the beam.
-The temperature stability of the system during the test run was better than $1^\circ~$F, the temperature uniformity inside the box was better than  $4^\circ~$F.
+The gap between innermost edge of the crystals of two parts was just $7.4$~cm from the beam. The temperature 
+stability of the system during the test run was better than $1^\circ~$F, the temperature uniformity inside the box 
+was better than $3^\circ~$C.
 
@@
 \label{sec:fadc}
-Amplified APD signal from the motherboard is sent to a $2:1$ signal splitter. After the split, 2/3 of the signal is sent a discriminator then to a Time-to-Digital 
-Converter (TDC). The 1/3 of the signal is fed to a single channel of 16-channel JLAB Flash Amplitude-to-Digital Converter VXS module (FADC250)~\cite{fadc}, see Fig.\ref{fig:fadc}.  
+Amplified APD signal from the motherboard is sent to a $2:1$ signal splitter. After the split, 2/3 of the signal is sent 
+a discriminator then to a Time-to-Digital Converter. The 1/3 of the signal is fed to a single channel of 16-channel 
+JLab Flash Amplitude-to-Digital Converter VXS module (FADC250)~\cite{fadc} shown in Fig.\ref{fig:fadc}.  
 \begin{figure}[t]
@@
 \includegraphics[width=7cm]{figures/FADC250_Photo_001.jpg}
-\caption{A Jefferson Lab FADC250 VXS module.}
+\caption{A JLab FADC250 VXS module.}
 \label{fig:fadc}
@@
 \end{figure}
-Two 20-slot VXS crates with 14 FADC bards were needed to accommodate the system: one for each half of the ECal with 221 
-channels.
-
-The FADCs store 12-bit digitized samples at 250~MHz in 8~$\mu$s deep pipelines. 
-When a trigger is received, the appropriate part of the pipeline is accessed for the readout.
-HPS used FADCs in the integration mode.
-A predefined number of samples of the signal that exceeds a predefined threshold have been summed and stored in 17-bit register for readout.
-The number of samples for integration was defined by two parameters that could be set separately, the number of samples integrated before the signal crossed threshold ($NSB$) and  the number of samples integrated after the signal crossed threshold ($NSA$), see Fig.\ref{fig:hps_trigger_data}.
+Two 20-slot VXS crates with 14 FADC bards were needed to accommodate the system: one for each half of the 
+ECal with 221 channels.
+
+The FADCs store 12-bit digitized samples at 250~MSPS in 8~$\mu$s deep pipelines. 
+When a trigger is received, the appropriate part of the pipeline is accessed for the readout. HPS used FADCs in 
+the co-called integration mode. A predefined number of samples of the signal that exceeds a predefined threshold 
+have been summed and stored in 17-bit register for readout. The number of samples for integration was defined 
+by two parameters that could be set separately, the number of samples integrated before the signal crossed 
+threshold ($NSB$) and  the number of samples integrated after the signal crossed threshold ($NSA$), 
+see Fig.~\ref{fig:hps_trigger_data}. 
 This scheme significantly compresses the data input 
 to the FADC. During data analysis, a pedestal value is subtracted to obtain the actual summed energy.
-
 \begin{figure}[]
@@
 
-subsection{Calibration and Performance}
+\subsection{Calibration and Performance}
 \label{sec:ecal_calibration}
 
-For various reasons only 385 out of 442 modules (87\%) were operational during the test run.  Of 442 modules, 39 were disabled or disconnected and were not read out by the DAQ. 
-13 of these were not read out because of a shortage of FADC readout boards (see Sec.~\ref{sec:fadc}).
+Only 385 out of 442 modules (87\%) were operational during the test run.  Of 442 modules, 39 were disabled or 
+disconnected and were not read out by the DAQ. 
+13 of these were not read out because of a shortage of FADC readout boards.
 The remainder either had no HV bias on the APD, or were disabled in the FADC software due to noise.
@@
  misidentified as noisy because they had much higher hit occupancy than neighboring channels.
-Gain calibration shows that these channels have high gain (and thus lower energy threshold) but are otherwise normal.
-The abnormal channels were ignored in analysis in order to simplify comparison with Monte Carlo.
-This leaves 385 useful channels---87\% of the ECal.
+Gain calibration shows that these channels have high gain (and thus lower energy threshold) but are otherwise 
+normal. The abnormal channels were ignored in analysis in order to simplify comparison with Monte Carlo. This 
+leaves 385 useful channels---87\% of the ECal.
 
 The noise level of the ECal modules were measured to be approximately 15~MeV. The ECal was operated 
-with an effective readout threshold of 70~MeV.
-
-Modules above thresholds are clustered using a simple robust algorithm described in Sec.~\ref{sec:trigger}.
+with an effective readout threshold of 70~MeV. Modules above thresholds are clustered using a simple robust 
+algorithm described in Sec.~\ref{sec:trigger}.
 
@@
 preamplifier output is sampled every 4~ns in a time window of 100 samples: by looking at a part of the 
-window before the hit, we calibrate the readout channel. The The readout threshold
-
+window before the hit,  the readout channel pedestal can be obtained. 
 We calibrate gain of the individual ECal channels using the SVT measurement of track momentum and 
@@
 \end{figure}
-
 These gains can then be used to convert from ADC counts in a channel to the energy deposited into that ECal 
@@
 energy read out from crystals to energy of an incident particle. The conventional sampling fraction, 
-the fraction of incident energy that is deposited in crystals, is approximately 0.9  for the ECal and less at the 
+the fraction of incident energy that is deposited in crystals, is approximately 0.9  for the center of the ECal and less 
+at the 
 edges. For our readout, there is additional energy lost because crystals under the readout threshold are not 
@@
 A full computation of sampling fraction can be done using simulation.
-
-%Step\subsection{Monitoring}
 
@@
  \begin{itemize}
- \item FADC (pulse finding): samples and digitizes the signal pulses from each detector channel. Sends the measured pulse energy and arrival time to the Crate Trigger Processor (CTP),
-\item CTP (cluster finding): groups FADC pulses from each half of the ECal into clusters. The cluster energy and arrival time are sent to the Sub-System Processor (SSP),
- \item SSP (cluster pair finding): searches for time coincidence of pairs of clusters from the top and bottom half of the ECal and applies topological selections.
+ \item FADC (pulse finding): samples and digitizes the signal pulses from each detector channel. Sends the 
+ measured pulse energy and arrival time to the Crate Trigger Processor (CTP),
+\item CTP (cluster finding): groups FADC pulses from each half of the ECal into clusters. The cluster energy and 
+arrival time are sent to the Sub-System Processor (SSP),
+ \item SSP (cluster pair finding): searches for time coincidence of pairs of clusters from the top and bottom half of 
+ the ECal and applies topological selections.
  \end{itemize}
@@
  \includegraphics[width=7cm]{figures/hps_trigger_cal}
-\caption{Block diagram of the ECAL trigger system consisting of the FADC that samples and digitizes the detector channel signals and sends them for cluster finding in the CTP.
-The CTP clusters are sent to the SSP where the final trigger decision is taken based on pairs of clusters in both halves of the ECal.
-The decision is sent to the Trigger Supervisor (TS) that generates the necessary signals to readout the sub-detectors.}
+\caption{Block diagram of the ECAL trigger system consisting of the FADC that samples and digitizes the detector 
+	channel signals and sends them for cluster finding in the CTP. The CTP clusters are sent to the SSP where 
+	the final trigger decision is taken based on pairs of clusters in both halves of the ECal. The decision is sent to
+	the Trigger Supervisor (TS) that generates the necessary signals to readout the sub-detectors.}
  \label{fig:hps_trigger_cal}
@@
 As described above, the first stage of the trigger logic is incorporated into the 
-FPGA's on the FADC boards. 
-For the trigger path, every channel has, in addition to $NSB$ and $NSA$: 
+FPGA's on the FADC boards. For the trigger path, every channel has, in addition to $NSB$ and $NSA$: 
 \begin{itemize}
@@
 
- The final trigger decision is made by CTPs and SSP passed to the Trigger Supervisor (TS). The TS generates all necessary signals and controls the entire DAQ 
+The final trigger decision is made by CTPs and SSP passed to the Trigger Supervisor (TS). The TS generates all 
+necessary signals and controls the entire DAQ 
 system readout through the Trigger Interface (TI) units. The TI units are installed in every crate that participate 
@@
 
-During the test run, for the most part trigger system run in single cluster mode and was tested to work for up to 20 kHz trigger rates.
+During the test run, for the most part trigger system run in single cluster mode and was tested to work for up to 
+20~kHz trigger rates.
 
@@
 that collects digitized information, processes it, and sends it on to the Event Builder (EB). The ROC is a single 
-blade Intel-based CPU module running DAQ software under CentOS Linux OS. For the SVT ATCA system, 
-the ROC application runs on an embedded processor situated on the ATCA main board. The EB assembles 
-information from the SVT and ECal ROCs into a single event which is passed to the Event 
-Recorder (ER) that writes it to a RAID5-based data storage system capable of handling up to 100 MB/s. The 
+blade Intel-based CPU module running DAQ software under CentOS Linux OS. For the SVT DAQ system, 
+the ROC application runs on a dedicated DAQ desktop computer. The EB assembles 
+information from the SVT and Cal ROCs into a single event which is passed to the Event 
+Recorder (ER) that writes it to a RAID5-based data storage system capable of handling up to 100~MB/s. The 
 EB and other critical components run on multicore Intel-based multi-CPU servers. The DAQ network system is 
 a Foundry router providing high-speed connections between the DAQ components and to the JLab 
-computing facility. The SVT ROC, which must handle large data volumes, has a 10 Gbit/s link to the Foundry 
-router, while a 1 Gbit/s link is adequate for the ECal. A 10 Gbit/s uplink to the JLab 
+computing facility. The SVT ROC, which must handle large data volumes, has a 10~Gb/s link to the Foundry 
+router, while a 1~Gb/s link is adequate for the ECal. A 10~Gb/s uplink to the JLab 
 computing facility is used for long-term storage.
@@
 
-\subsubsection{Performance}
+\subsection{Performance}
 As discussed above, the trigger and DAQ integrate pulses differently to measure hit energy. The trigger 
@@
 In summary, the accurate modeling of the MCS is fundamental to estimate occupancies and trigger rates 
-for HPS. \egs{} predicts the correct angular distribution across all converter thicknesses while 
-\geant{} overestimates the rates; with the disagreement increasing  with larger converter thickness. 
-This preliminary result verifies similar studies [] and gives confidence in our modeling of the MCS 
+for HPS. \egs{} predicts the correct angular distribution across all converter thicknesses as expected while 
+\geant{}, using the so-called Urban model for multiple scattering overestimates the rates; with the disagreement 
+increasing  with larger converter thickness. This preliminary result verifies similar studies [] and gives confidence 
+in our modeling of the MCS 
 using \egs{} for evaluating the physics reach of HPS.

### 2013-11-06 hps-testrun-nim.tex
Adding turn-on vs E from Sho.

@@
 	\includegraphics[width=7cm]{figures/top_turn_on__bottom_tag}
-	\caption{Trigger turn-on as a function of probe cluster ADC counts. }
-%	\caption{Trigger turn-on as a function of probe cluster ADC counts (top) and probe cluster energy in MeV
-%	(bottom). Both plots are for the top half of the ECal; bottom is similar. Energy is not corrected for sampling 
-%	fraction.}
+	\includegraphics[width=7cm]{figures/top_turn_on__bottom_tag_E}
+	\caption{Trigger turn-on as a function of probe cluster ADC counts (top) and probe cluster energy in MeV
+	(bottom). Both plots are for the top half of the ECal; bottom is similar. Energy is not corrected for sampling 
+	fraction.}
 \label{fig:turnon}

### 2013-11-06 hps-testrun-nim.tex
Moved performance from SVT and ECal to its own section

@@
 
-\subsection{Monitoring and Calibration}
-
-\subsection{Data Analysis and Performance}
-
-During the duration of the test run all SVT modules and APV25 chips were configured to their 
-nominal operating points~\cite{Jones:1069892} with all sensors reverse-biased at 180~V.  The 
-sensors were operated within a temperature range of  $20-24^\circ$C 
-throughout the test run. Multiple calibration runs, normalized with lab-based radioactive source tests, 
-established a noise level of $\approx$ XXXX-XXXX electrons which was stable across all the SVT modules.
-
-Throughout the duration of the test run, approximately 97\% of the 12,780 SVT channels were found to be 
-operating normally. The fraction of dead or noisy channels varied from 2.4\% to 4.7\%.  
-Most of these were due to misconfigured readout chips (2--4 misconfigured chips out of 100 ), 
-a known noisy half-module and a couple of known noisy readout chips.
-
-\subsubsection{Cluster and Hit Reconstruction}
-
-After a trigger is received, six samples of the corresponding output of the APV25 shaper circuit are digitized. 
-The samples from every channel on a sensor surviving the 
-data reduction algorithm (see Sec.~\ref{sec:svt_daq}) are the basis for offline hit reconstruction. 
-The six samples of the APV25 shaper output 
-are fitted to an ideal $CR-RC$ function to extract the amplitude and the $t_0$ of the hit. 
-The typical pulse shape obtained is shown in Fig.~\ref{fig:pulse_shape} also demonstrates that the SVT 
-was well timed in to the trigger with the rise of the pulse at the 3rd sampling point.
-\begin{figure}[h]
-\begin{center}
-{\small
-	\includegraphics[width=6cm]{figures/08062012_run1351_samples_vs_amplitude}
-    	\caption{The six pedestal subtracted samples from individual channels associated with a hit on a 
-	track.}
-	\label{fig:pulse_shape}
-}
-\end{center}
-\end{figure}
-
-These hits are passed through a simple clustering algorithm which forms clusters by grouping adjacent 
-strips. The position of a cluster on the sensor is determined by the amplitude-weighted mean.
-With a linear gain up to $\approx 3$~MIPs, the cluster charge for hits associated with a track follow 
-the characteristic Landau shape as expected, see Fig.~\ref{fig:cluster_pulse}. 
-The signal to noise ratio is XXXX.
-\begin{figure}[h]
-\begin{center}
-{\small
-	\includegraphics[width=6cm]{figures/run1351_mip_small.pdf}
-    	\caption{ The cluster charge distribution for hits associated with a track. }
-	\label{fig:cluster_pulse}
-}
-\end{center}
-\end{figure}
-
-After clustering hits on a sensor, the hit time for each cluster is computed as the amplitude-weighted 
-average of the fitted $t_0$ channel times. The $t_0$-resolution is studied by comparing the cluster hit time 
-with the average of all cluster hit times on the track, the ``track time'', which has the expected jitter due to clock 
-phase and trigger, approximately 25~ns. Figure~\ref{fig:tracktime} shows the residual to the individual cluster 
-times. 
-\begin{figure}[h]
-\begin{center}
-{\small
-%	\includegraphics[width=7cm]{figures/top_track_time.pdf}
-	\includegraphics[width=6cm]{figures/t0_resolution.pdf}
-	\caption{
-%	Track time distribution (left) and cluster time residual (right).
-The track time is measured relative to the APV25 clock.
-The width of the distribution is due to trigger jitter (24~ns jitter in the tracker readout clock, plus 16~ns jitter in the trigger system).
-	The cluster time residual is for a representative sensor relative to the track time.}
-	\label{fig:tracktime}
-}
-\end{center}
-\end{figure}
-After correcting for offsets from each sensor (time-of-flight, clock phase) the extracted $t_0$ resolution is 
-2.6~ns. This is somewhat worse than the approximately 2~ns resolution expected which we attribute to the true 
-pulse shape differing from our idealized fit function which will be improved in the future. Reducing the 
-APV25 pulse shaping time will also improve time resolution. These results show that we can operate with 
-the six sample readout mode of the APV25 chip and achieve time resolution adequate for pileup 
-rejection during electron running in the HPS experiment.
-
-While occupancy was slightly larger than expected, good agreement between data and simulation was 
-found after taking into account dead or noisy channels. The hit efficiency, see Fig.~\ref{fig:hit_efficiency}, 
-was measured to be above 98\% and fairly uniform across the SVT.
-\begin{figure}[h]
-\begin{center}
-{\small
-    	\includegraphics[width=7cmh]{figures/hit_efficiency_vs_layer.pdf}
-        \caption{ The hit reconstruction efficiency as a function of detector layer.}
-	\label{fig:hit_efficiency}
-}
-\end{center}
-\end{figure}
-The spatial resolution of similar microstrip sensors is well established by test beam data, against which the 
-charge deposition model in the simulation is validated.  This resolution can be parameterized as a 
-function of the total signal to single-strip noise (S/N) and the crossing angle of tracks through the sensor.  
-The single-hit resolution for charged particles with signal to noise ration above 20, as demonstrated here, 
-is relatively constant at approximately 6~$\mu$m for tracks that are close to normal to the sensors as in HPS.
-
-\subsubsection{Alignment}
+\subsection{Alignment}
 The SVT was aligned using a combination of optical, laser and touch probe surveys at SLAC and JLab. The 
@@
 is being developed.
-
-\subsubsection{Momentum and Vertexing Resolution}
-
-By selecting \ee{} pairs from the triggered events we are able to study basic distributions of pair production 
-kinematics and in particular those related to our vertex performance. Pairs of opposite charge tracks, one in the 
-top and one in the bottom half of the SVT, with momentum larger than 400~MeV were selected. 
-The pair production 
-kinematics are relatively well reproduced given the alignment of the tracker; Fig.~\ref{fig:pair_kin} shows the 
-invariant mass and ratio of electron momentum over the sum of electron and positron. 
- \begin{center}
-{\small
-\begin{figure*}[ht]
-   \includegraphics[width=5cm]{figures/h_trk_top_px_h_trk_top_px_trigseltwotrksel4hit_recoilmc_twotrkfilt.png}
-   \includegraphics[width=5cm]{figures/h_invM_h_invM_dataMC_trigseltwotrksel4hit_recoilmc_twotrkfilt.png}
-   \includegraphics[width=5cm]{figures/h_sumE_h_sumE_dataMC_trigseltwotrksel4hit_recoilmc_twotrkfilt.png}
-%   \includegraphics[scale=0.25]{test2012/vertexing/figures/h_ratioEsum_h_ratioEsum_dataMC_trigseltwotrksel4hit_recoilmc_twotrkfilt.png}
-\caption{Kinematic distributions for e$^+$e$^-$ pairs selected by opposite charged tracks in the top and bottom half of the tracker: track momentum in the top half of the SVT (left), invariant mass (middle) and the sum of the track momentum for the pair.}
-\label{fig:pair_kin}
-\end{figure*}
-}
-\end{center}
-
-For the vertexing 
-performance the foremost difference compared to electron beam running is that the target was 
-located approximately 67~cm from our nominal target position; giving almost collinear tracks in the detector. 
-This degrades the vertex resolution along the 
-beam line compared to that expected in an electron beam with tracks from the nominal target position. 
-Furthermore, tails of the vertex distributions are impossible to study with the finite data sample obtained 
-in the test run. Nevertheless, useful information can still be 
-obtained by studying the vertex distributions. Figure~\ref{fig:vtx_pos} shows the distance of closest 
-approach of the momentum vectors extrapolated in the 
-upstream direction from our analyzing magnet, taking into account the measured fringe field of the PS magnet. 
- \begin{center}
-{\small
-	 \begin{figure*}[ht]
-	\includegraphics[width=5cm]{figures/h_vtx_fr_x_h_vtx_x_dataMC_trigseltwotrksel4hit_recoilmc_twotrkfilt.png}
-	\includegraphics[ width=5cm]{figures/h_vtx_fr_y_h_vtx_y_dataMC_trigseltwotrksel4hit_recoilmc_twotrkfilt.png}
-	\includegraphics[width=5cm]{figures/h_vtx_fr_z_h_vtx_z_dataMC_trigseltwotrksel4hit_recoilmc_twotrkfilt.png}
-	\caption{{\bf \textcolor{red}{NEED TO BE UPDATED}}Vertex position represented by the distance of 
-	closest approach of the extrapolated momentum vectors upstream of the PS magnet taking into account 
-	the measured fringe field. The overall shift from zero in the x-direction is 
-	due to a 30~mrad rotation of the SVT with respect to the beam line.}
-	\label{fig:vtx_pos}
-\end{figure*}
-}
-\end{center}
-While the tails of the vertex distribution expected in electron beam running is not accessible here the 
-fact that the core is relatively well described provides confidence of the description of the amount of 
-material and the model used for simulating multiple scattering in the target.  
-These are crucial for benchmarking the HPS \Aprime{} physics reach since both the mass and vertex resolution 
-that determine the sensitivity are limited by multiple scattering.
 
@@
 \end{figure}
-
-\subsection{Calibration and Performance}
-\label{sec:ecal_calibration}
-
-Only 385 out of 442 modules (87\%) were operational during the test run.  Of 442 modules, 39 were disabled or 
-disconnected and were not read out by the DAQ. 
-13 of these were not read out because of a shortage of FADC readout boards.
-The remainder either had no HV bias on the APD, or were disabled in the FADC software due to noise.
-In the data, we identified two types of abnormal channels. 
-One FADC was not sending trigger signals correctly, resulting in low efficiency.
- This affected the 13 channels read out by that FADC. 5 channels were diagnosed as noisy because they 
- had a high incidence of hits out of coincidence with the trigger. A large number of channels were originally 
- misidentified as noisy because they had much higher hit occupancy than neighboring channels.
-Gain calibration shows that these channels have high gain (and thus lower energy threshold) but are otherwise 
-normal. The abnormal channels were ignored in analysis in order to simplify comparison with Monte Carlo. This 
-leaves 385 useful channels---87\% of the ECal.
-
-The noise level of the ECal modules were measured to be approximately 15~MeV. The ECal was operated 
-with an effective readout threshold of 70~MeV. Modules above thresholds are clustered using a simple robust 
-algorithm described in Sec.~\ref{sec:trigger}.
-
-%\subsubsection{Calibration}
-%\label{sec:ecal_calibration}
-The noise and pedestal of the readout chain are calibrated by running the ECal readout in a mode where the 
-preamplifier output is sampled every 4~ns in a time window of 100 samples: by looking at a part of the 
-window before the hit,  the readout channel pedestal can be obtained. 
-We calibrate gain of the individual ECal channels using the SVT measurement of track momentum and 
-comparison to Monte Carlo simulation.  We disable all SVT and ECal channels in the simulation that were 
-inoperable or noisy in the test run, so any efficiency or bias effects that affect the real data should be reflected 
-in the simulation as well; then we use a formula to compute the ``weighted E/p'' for a crystal, representing the average E/p for clusters that include the crystal
-% $\frac{\sum_j w_{j,i}}{\sum_j\frac{P_j}{E_j}w_{j,i}}$
-, and iteratively adjust the gains until the weighted E/p is equal for test run data and simulation.
-\begin{figure}[]
-\begin{center}
-{\small
-	\includegraphics[width=7cm]{figures/eoverp_simulation}
-	\caption{Weighted E/p from Monte Carlo simulation after gain calibration.}
-	\label{fig:gains}
-}
-\end{center}
-\end{figure}
-These gains can then be used to convert from ADC counts in a channel to the energy deposited into that ECal 
-crystal.
-The other information needed to find the energy of an incident particle is the sampling fraction---the ratio of 
-energy read out from crystals to energy of an incident particle. The conventional sampling fraction, 
-the fraction of incident energy that is deposited in crystals, is approximately 0.9  for the center of the ECal and less 
-at the 
-edges. For our readout, there is additional energy lost because crystals under the readout threshold are not 
-read out.
-The weighted E/p used in calibration (see Figure \ref{fig:gains}) is an approximate measurement of sampling fraction, but the sampling fraction is energy-dependent because of the effect of readout threshold.
-A full computation of sampling fraction can be done using simulation.
 
@@
 
-\subsection{Performance}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Performance}
+
+\subsection{SVT Performance}
+
+During the duration of the test run all SVT modules and APV25 chips were configured to their 
+nominal operating points~\cite{Jones:1069892} with all sensors reverse-biased at 180~V.  The 
+sensors were operated within a temperature range of  $20-24^\circ$C 
+throughout the test run. Multiple calibration runs, normalized with lab-based radioactive source tests, 
+established a noise level of $\approx$ XXXX-XXXX electrons which was stable across all the SVT modules.
+
+Throughout the duration of the test run, approximately 97\% of the 12,780 SVT channels were found to be 
+operating normally. The fraction of dead or noisy channels varied from 2.4\% to 4.7\%.  
+Most of these were due to misconfigured readout chips (2--4 misconfigured chips out of 100 ), 
+a known noisy half-module and a couple of known noisy readout chips.
+
+\subsubsection{Cluster and Hit Reconstruction}
+
+After a trigger is received, six samples of the corresponding output of the APV25 shaper circuit are digitized. 
+The samples from every channel on a sensor surviving the 
+data reduction algorithm (see Sec.~\ref{sec:svt_daq}) are the basis for offline hit reconstruction. 
+The six samples of the APV25 shaper output 
+are fitted to an ideal $CR-RC$ function to extract the amplitude and the $t_0$ of the hit. 
+The typical pulse shape obtained is shown in Fig.~\ref{fig:pulse_shape} also demonstrates that the SVT 
+was well timed in to the trigger with the rise of the pulse at the 3rd sampling point.
+\begin{figure}[h]
+\begin{center}
+{\small
+	\includegraphics[width=6cm]{figures/08062012_run1351_samples_vs_amplitude}
+    	\caption{The six pedestal subtracted samples from individual channels associated with a hit on a 
+	track.}
+	\label{fig:pulse_shape}
+}
+\end{center}
+\end{figure}
+
+These hits are passed through a simple clustering algorithm which forms clusters by grouping adjacent 
+strips. The position of a cluster on the sensor is determined by the amplitude-weighted mean.
+With a linear gain up to $\approx 3$~MIPs, the cluster charge for hits associated with a track follow 
+the characteristic Landau shape as expected, see Fig.~\ref{fig:cluster_pulse}. 
+The signal to noise ratio is XXXX.
+\begin{figure}[h]
+\begin{center}
+{\small
+	\includegraphics[width=6cm]{figures/run1351_mip_small.pdf}
+    	\caption{ The cluster charge distribution for hits associated with a track. }
+	\label{fig:cluster_pulse}
+}
+\end{center}
+\end{figure}
+
+After clustering hits on a sensor, the hit time for each cluster is computed as the amplitude-weighted 
+average of the fitted $t_0$ channel times. The $t_0$-resolution is studied by comparing the cluster hit time 
+with the average of all cluster hit times on the track, the ``track time'', which has the expected jitter due to clock 
+phase and trigger, approximately 25~ns. Figure~\ref{fig:tracktime} shows the residual to the individual cluster 
+times. 
+\begin{figure}[h]
+\begin{center}
+{\small
+%	\includegraphics[width=7cm]{figures/top_track_time.pdf}
+	\includegraphics[width=6cm]{figures/t0_resolution.pdf}
+	\caption{
+%	Track time distribution (left) and cluster time residual (right).
+The track time is measured relative to the APV25 clock.
+The width of the distribution is due to trigger jitter (24~ns jitter in the tracker readout clock, plus 16~ns jitter in the trigger system).
+	The cluster time residual is for a representative sensor relative to the track time.}
+	\label{fig:tracktime}
+}
+\end{center}
+\end{figure}
+After correcting for offsets from each sensor (time-of-flight, clock phase) the extracted $t_0$ resolution is 
+2.6~ns. This is somewhat worse than the approximately 2~ns resolution expected which we attribute to the true 
+pulse shape differing from our idealized fit function which will be improved in the future. Reducing the 
+APV25 pulse shaping time will also improve time resolution. These results show that we can operate with 
+the six sample readout mode of the APV25 chip and achieve time resolution adequate for pileup 
+rejection during electron running in the HPS experiment.
+
+While occupancy was slightly larger than expected, good agreement between data and simulation was 
+found after taking into account dead or noisy channels. The hit efficiency, see Fig.~\ref{fig:hit_efficiency}, 
+was measured to be above 98\% and fairly uniform across the SVT.
+\begin{figure}[h]
+\begin{center}
+{\small
+    	\includegraphics[width=7cmh]{figures/hit_efficiency_vs_layer.pdf}
+        \caption{ The hit reconstruction efficiency as a function of detector layer.}
+	\label{fig:hit_efficiency}
+}
+\end{center}
+\end{figure}
+The spatial resolution of similar microstrip sensors is well established by test beam data, against which the 
+charge deposition model in the simulation is validated.  This resolution can be parameterized as a 
+function of the total signal to single-strip noise (S/N) and the crossing angle of tracks through the sensor.  
+The single-hit resolution for charged particles with signal to noise ration above 20, as demonstrated here, 
+is relatively constant at approximately 6~$\mu$m for tracks that are close to normal to the sensors as in HPS.
+
+\subsubsection{Momentum and Vertexing Resolution}
+
+By selecting \ee{} pairs from the triggered events we are able to study basic distributions of pair production 
+kinematics and in particular those related to our vertex performance. Pairs of opposite charge tracks, one in the 
+top and one in the bottom half of the SVT, with momentum larger than 400~MeV were selected. 
+The pair production 
+kinematics are relatively well reproduced given the alignment of the tracker; Fig.~\ref{fig:pair_kin} shows the 
+invariant mass and ratio of electron momentum over the sum of electron and positron. 
+ \begin{center}
+{\small
+\begin{figure*}[ht]
+   \includegraphics[width=5cm]{figures/h_trk_top_px_h_trk_top_px_trigseltwotrksel4hit_recoilmc_twotrkfilt.png}
+   \includegraphics[width=5cm]{figures/h_invM_h_invM_dataMC_trigseltwotrksel4hit_recoilmc_twotrkfilt.png}
+   \includegraphics[width=5cm]{figures/h_sumE_h_sumE_dataMC_trigseltwotrksel4hit_recoilmc_twotrkfilt.png}
+%   \includegraphics[scale=0.25]{test2012/vertexing/figures/h_ratioEsum_h_ratioEsum_dataMC_trigseltwotrksel4hit_recoilmc_twotrkfilt.png}
+\caption{Kinematic distributions for e$^+$e$^-$ pairs selected by opposite charged tracks in the top and bottom half of the tracker: track momentum in the top half of the SVT (left), invariant mass (middle) and the sum of the track momentum for the pair.}
+\label{fig:pair_kin}
+\end{figure*}
+}
+\end{center}
+
+For the vertexing 
+performance the foremost difference compared to electron beam running is that the target was 
+located approximately 67~cm from our nominal target position; giving almost collinear tracks in the detector. 
+This degrades the vertex resolution along the 
+beam line compared to that expected in an electron beam with tracks from the nominal target position. 
+Furthermore, tails of the vertex distributions are impossible to study with the finite data sample obtained 
+in the test run. Nevertheless, useful information can still be 
+obtained by studying the vertex distributions. Figure~\ref{fig:vtx_pos} shows the distance of closest 
+approach of the momentum vectors extrapolated in the 
+upstream direction from our analyzing magnet, taking into account the measured fringe field of the PS magnet. 
+ \begin{center}
+{\small
+	 \begin{figure*}[ht]
+	\includegraphics[width=5cm]{figures/h_vtx_fr_x_h_vtx_x_dataMC_trigseltwotrksel4hit_recoilmc_twotrkfilt.png}
+	\includegraphics[ width=5cm]{figures/h_vtx_fr_y_h_vtx_y_dataMC_trigseltwotrksel4hit_recoilmc_twotrkfilt.png}
+	\includegraphics[width=5cm]{figures/h_vtx_fr_z_h_vtx_z_dataMC_trigseltwotrksel4hit_recoilmc_twotrkfilt.png}
+	\caption{{\bf \textcolor{red}{NEED TO BE UPDATED}}Vertex position represented by the distance of 
+	closest approach of the extrapolated momentum vectors upstream of the PS magnet taking into account 
+	the measured fringe field. The overall shift from zero in the x-direction is 
+	due to a 30~mrad rotation of the SVT with respect to the beam line.}
+	\label{fig:vtx_pos}
+\end{figure*}
+}
+\end{center}
+While the tails of the vertex distribution expected in electron beam running is not accessible here the 
+fact that the core is relatively well described provides confidence of the description of the amount of 
+material and the model used for simulating multiple scattering in the target.  
+These are crucial for benchmarking the HPS \Aprime{} physics reach since both the mass and vertex resolution 
+that determine the sensitivity are limited by multiple scattering.
+
+\subsection{ECal and Trigger Performance}
+\label{sec:ecal_calibration}
+
+%\subsubsection{ECal Calibration and Performance}
+
+Only 385 out of 442 modules (87\%) were operational during the test run.  Of 442 modules, 39 were disabled or 
+disconnected and were not read out by the DAQ. 
+13 of these were not read out because of a shortage of FADC readout boards.
+The remainder either had no HV bias on the APD, or were disabled in the FADC software due to noise.
+In the data, we identified two types of abnormal channels. 
+One FADC was not sending trigger signals correctly, resulting in low efficiency.
+ This affected the 13 channels read out by that FADC. 5 channels were diagnosed as noisy because they 
+ had a high incidence of hits out of coincidence with the trigger. A large number of channels were originally 
+ misidentified as noisy because they had much higher hit occupancy than neighboring channels.
+Gain calibration shows that these channels have high gain (and thus lower energy threshold) but are otherwise 
+normal. The abnormal channels were ignored in analysis in order to simplify comparison with Monte Carlo. This 
+leaves 385 useful channels---87\% of the ECal.
+
+The noise level of the ECal modules were measured to be approximately 15~MeV. The ECal was operated 
+with an effective readout threshold of 70~MeV. Modules above thresholds are clustered using a simple robust 
+algorithm described in Sec.~\ref{sec:trigger}.
+
+%\subsubsection{Calibration}
+%\label{sec:ecal_calibration}
+The noise and pedestal of the readout chain are calibrated by running the ECal readout in a mode where the 
+preamplifier output is sampled every 4~ns in a time window of 100 samples: by looking at a part of the 
+window before the hit,  the readout channel pedestal can be obtained. 
+We calibrate gain of the individual ECal channels using the SVT measurement of track momentum and 
+comparison to Monte Carlo simulation.  We disable all SVT and ECal channels in the simulation that were 
+inoperable or noisy in the test run, so any efficiency or bias effects that affect the real data should be reflected 
+in the simulation as well; then we use a formula to compute the ``weighted E/p'' for a crystal, representing the average E/p for clusters that include the crystal
+% $\frac{\sum_j w_{j,i}}{\sum_j\frac{P_j}{E_j}w_{j,i}}$
+, and iteratively adjust the gains until the weighted E/p is equal for test run data and simulation.
+\begin{figure}[]
+\begin{center}
+{\small
+	\includegraphics[width=7cm]{figures/eoverp_simulation}
+	\caption{Weighted E/p from Monte Carlo simulation after gain calibration.}
+	\label{fig:gains}
+}
+\end{center}
+\end{figure}
+These gains can then be used to convert from ADC counts in a channel to the energy deposited into that ECal 
+crystal.
+The other information needed to find the energy of an incident particle is the sampling fraction---the ratio of 
+energy read out from crystals to energy of an incident particle. The conventional sampling fraction, 
+the fraction of incident energy that is deposited in crystals, is approximately 0.9  for the center of the ECal and less 
+at the 
+edges. For our readout, there is additional energy lost because crystals under the readout threshold are not 
+read out.
+The weighted E/p used in calibration (see Figure \ref{fig:gains}) is an approximate measurement of sampling fraction, but the sampling fraction is energy-dependent because of the effect of readout threshold.
+A full computation of sampling fraction can be done using simulation.
+
+%\subsubsection{Trigger Performance}
 As discussed above, the trigger and DAQ integrate pulses differently to measure hit energy. The trigger 

### 2013-11-08 hps-testrun-nim.tex
Adding new kinematic plots from TestRun-v6 geometry. Removing a few of the MCS distributions. Removed plot of G4 comparison, just use table to make the point.

@@
 \begin{figure*}[ht]
-   \includegraphics[width=5cm]{figures/h_trk_top_px_h_trk_top_px_trigseltwotrksel4hit_recoilmc_twotrkfilt.png}
-   \includegraphics[width=5cm]{figures/h_invM_h_invM_dataMC_trigseltwotrksel4hit_recoilmc_twotrkfilt.png}
-   \includegraphics[width=5cm]{figures/h_sumE_h_sumE_dataMC_trigseltwotrksel4hit_recoilmc_twotrkfilt.png}
+   \includegraphics[width=5cm]{figures/h_trk_top_px_h_trk_top_px_trigsel4hit_pair1351_twotrkfilt-v6-paper}
+   \includegraphics[width=5cm]{figures/h_invM_h_invM_trigsel4hit_pair1351_twotrkfilt-v6-paper}
+   \includegraphics[width=5cm]{figures/h_sumE_h_sumE_trigsel4hit_pair1351_twotrkfilt-v6-paper}
 %   \includegraphics[scale=0.25]{test2012/vertexing/figures/h_ratioEsum_h_ratioEsum_dataMC_trigseltwotrksel4hit_recoilmc_twotrkfilt.png}
@@
 	 \begin{figure*}[ht]
-	\includegraphics[width=5cm]{figures/h_vtx_fr_x_h_vtx_x_dataMC_trigseltwotrksel4hit_recoilmc_twotrkfilt.png}
-	\includegraphics[ width=5cm]{figures/h_vtx_fr_y_h_vtx_y_dataMC_trigseltwotrksel4hit_recoilmc_twotrkfilt.png}
-	\includegraphics[width=5cm]{figures/h_vtx_fr_z_h_vtx_z_dataMC_trigseltwotrksel4hit_recoilmc_twotrkfilt.png}
-	\caption{{\bf \textcolor{red}{NEED TO BE UPDATED}}Vertex position represented by the distance of 
+	% Plot info:
+	% TestRun-v6 geometry, twotrkfilter, trigsel, hps-java-1.8-SNAPSHOT, 4hits, chi2<10
+	\includegraphics[width=5cm]{figures/h_vtx_fr_x_h_vtx_x_trigsel4hit_pair1351_twotrkfilt-v6-paper}
+	\includegraphics[width=5cm]{figures/h_vtx_fr_y_h_vtx_y_trigsel4hit_pair1351_twotrkfilt-v6-paper}
+	\includegraphics[width=5cm]{figures/h_vtx_fr_z_h_vtx_z_trigsel4hit_pair1351_twotrkfilt-v6-paper}
+	\caption{ Vertex position represented by the distance of 
 	closest approach of the extrapolated momentum vectors upstream of the PS magnet taking into account 
@@
 While \egs{} uses the more complex and time consuming \moliere{} 
-formula, \geant{} uses an approximation with two, continuously joined, functions to take into account 
+formula, the default physics list of \geant{} uses the so-called Urban model, an approximation with two, 
+continuously joined, functions to take into account 
 small and large angle scattering. Due to the explicit function in large angle approximation used by \geant{} 
@@
 angular distribution in the ECal for the three converter thicknesses are shown in 
-Fig.~\ref{fig:ang_distr_data} (left).  
+Fig.~\ref{fig:ang_distr_data} (left). The data has been normalized to the integrated beam current and 
+the upstream background has been subtracted. 
 \begin{figure}[]
@@
 {\small
-	\includegraphics[ width=7cm]{figures/rate_ecalrow_raw.png}
+%	\includegraphics[ width=7cm]{figures/rate_ecalrow_raw.png}
 	\includegraphics[ width=7cm]{figures/rate_ecalrow_norm_subtr.png}
-	\caption{Measured raw vertical angular distributions before (top) and after (bottom) 
-	normalization and background subtraction.}
+	\caption{Measured vertical angular distributions before after integrated beam current 
+	normalization and upstream background subtraction.}
 	\label{fig:ang_distr_data}
@@
 converter.  Figure~\ref{fig:ang_distr_dataMC} shows the angular distribution comparing data and 
-\egs{} normalized to 1~s of beam at 90~nA beam current. Taking into account systematics uncertainties 
-described below reasonable agreement is obtained;   total rates for each converter thickness is shown in 
-Fig.~\ref{fig:rate_vs_thickness} and summarized in Tab.~\ref{tab:ang_distr_dataMC}.
-\begin{center}
-{\small
-	\begin{figure*}[t]
+\egs{} normalized to 1~s of beam at 90~nA beam current with a converter thickness of 1.6\%. 
+\begin{center}
+{\small
+	\begin{figure}[]
+%	\begin{figure*}[t]
 	\includegraphics[ scale=0.25]{figures/dataMC_1351_Hit_Y_top_norm_bkgsub.png}
-	\includegraphics[ scale=0.25]{figures/dataMC_1354_Hit_Y_top_norm_bkgsub.png}
-	\includegraphics[ scale=0.25]{figures/dataMC_1353_Hit_Y_top_norm_bkgsub.png}
-	\caption{Comparison between the observed and predicted angular 
-distribution using \egs{} for a converter thickness of 1.6\% (left), 0.45\% (middle) and 0.18\% 
-(right).  Only statistical uncertainties are shown. }
+%	\includegraphics[ scale=0.25]{figures/dataMC_1354_Hit_Y_top_norm_bkgsub.png}
+%	\includegraphics[ scale=0.25]{figures/dataMC_1353_Hit_Y_top_norm_bkgsub.png}
+	\caption{Comparison between the observed and predicted angular distribution using \egs{} for a 
+	converter thickness of 1.6\%. Similar agreement is found for 0.45\% and 0.18\% converter thicknesses. 
+	Only statistical uncertainties are shown. }
 	\label{fig:ang_distr_dataMC}
-	\end{figure*}
-}
-\end{center}
-\begin{center}
-{\small
-	\begin{figure*}[t]
-	\includegraphics[ scale=0.3]{figures/dataMC_geant4.png}
+%	\end{figure*}
+	\end{figure}
+}
+\end{center}
+Reasonable agreement is obtained in the most important region close to the beam. There is a hint of a 
+slightly different slope of the data at larger angles; this difference is covered by systematic uncertainties.  The 
+total rates for each converter thickness is shown in Fig.~\ref{fig:rate_vs_thickness} and summarized in 
+Tab.~\ref{tab:ang_distr_dataMC}.
+\begin{center}
+{\small
+	\begin{figure}[]
+%	\begin{figure*}[]
+	%\includegraphics[ scale=0.3]{figures/dataMC_geant4.png}
 	\includegraphics[ scale=0.3]{figures/dataMC_egs.png}
-	\caption{The measured rate as a function of converter thickness comparing \geant{} (left) 
-	and \egs{} (right).} 
+	\caption{The measured rate as a function of converter thickness for data and \egs{} simulation of MCS in 	the converter.} 
 	\label{fig:rate_vs_thickness}
-	\end{figure*}
+%	\end{figure*}
+	\end{figure}
 }
@@
 \end{table}
+As expected \egs{} show good agreement with our data while \geant{} using the default physics list 
+overestimates the MCS at these large angles.
 

### 2013-11-11 hps-testrun-nim.tex
Stepans changes to mostly ecal perf.

@@
 \label{sec:ecal}
-
-The electromagnetic calorimeter, installed downstream of the tracker, performs two essential functions for the 
-experiment: provides a trigger to DAQ system and is used in the analysis for electron identification. 
+\section{Electromagnetic Calorimeter}
+\label{ecal}
+
+The electromagnetic calorimeter, installed downstream of the tracker, performs two essential functions for the experiment: provides a trigger to DAQ system and 
+is used in the analysis for electron identification. 
 %The device is highly segmented.
@@
 
-\subsection{Purpose and Design Requirements}
-
-The electromagnetic calorimeter (ECal) provide the trigger for the data acquisition and will be used for 
-electron identification during the data analysis. The ECal is positioned after the analyzing dipole 
-magnet and cover the full acceptance region of the SVT. It consist of two halves, split in the horizontal 
-beam plane. The gap between upper and lower parts, $XXXX$~mrad (15mrad for electron running),  
-as seen from the target location, is necessary to avoid the "dead zone" where occupancy and radiation 
-prevents any instrumentation to be situated.
-
-The energy of electrons of interest will be in the range 
-$0.5-6.5$~GeV. The ECal modules must have sufficient radiation lengths to absorb the full energy of these 
-scattered electrons, have fine enough granularity to handle a high rate of electromagnetic 
-background and survive large doses of radiation, especially near the beam plane. In addition, it needs to 
-have excellent hit time resolution, $<10$~ns, in order to beat down beam backgrounds.
-
-The compact design requirements: high radiation environment , high rate and the presence of 
-high magnetic field, are fulfilled by a lead-tungstate (PbWO$_{4}$) crystal calorimeter with magnetic field 
-resistant avalanche photodiode (APD) readout.  Such crystals has been operational in the inner 
-calorimeter of the CLAS experiment~[XXXX] at JLab since 2005 and meet all requirements set by 
-HPS. These crystals were subsequently repurposed for the ECal.
-
 \subsection{ECal Components}
@@
 %Step\subsubsection{PbWO$_4$ Crystals}
-The HPS test run ECal uses PbWO$_{4}$ crystals, APDs, and preamplifier boards from the inner calorimeter (IC) 
-of the CLAS detector~\cite{2008erhm.conf..421N}.  In Fig.~\ref{fig:ecal-module} a schematic view of the module 
-assembly is shown. Lead-tungstate crystals are $160$ mm long and are tapered with front face of 
-$13.3\times13.3$~mm$^2$, tapered to $16\times16$~mm$^2$ at the rear face. The crystals were fabricated with 
-very tight tolerances: $19~\mu$m for 13.3~mm dimension and $13~\mu$m for the 16~mm dimension. Each crystal 
-is wrapped in VM2000 multilayer polymer mirror film.
-The APDs (Hamamatsu S8664-55) with $5\times5$~mm$^2$ active area and $75\%$ quantum efficiency were 
-glued on the rear face of the crystals using MeltMount 1.7 thermal plastic adhesive. The low gain of APDs ($\sim 
-200$) was compensated with custom made preamplifier boards, which provide factor 2000 amplification of the 
-ADP signal. 
+The HPS test run ECal uses PbWO$_{4}$ crystals, APDs, and preamplifier boards from the inner calorimeter (IC) of the CLAS detector\cite{2008erhm.conf..421N}.
+In Figure~\ref{fig:ecal-module} a schematic view of the module assembly is shown.
+Lead-tungstate crystals are $160$ mm long and are tapered with front face of $13.3\times13.3$~mm$^2$, tapered to $16\times16$~mm$^2$ at the rear face.
+The crystals were fabricated with very tight tolerances: $19~\mu$m for 13.3~mm dimension and $13~\mu$m for the 16~mm dimension.
+Each crystal is wrapped in VM2000 multilayer polymer mirror film.
+The APDs (Hamamatsu S8664-55) with $5\times5$~mm$^2$ active area and $75\%$ quantum efficiency were glued on the rear face of the crystals using MeltMount 1.7 thermal plastic adhesive.
+The low gain of APDs ($\sim 200$) was compensated with custom made preamplifier boards, which provide factor 2000 amplification of the ADP signal.
+
 \begin{figure}[]
@@
 
-Like the tracker, the electromagnetic calorimeter is split into two parts, beam-up and beam-down, to avoid 
-impinging on the “dead zone”. The two parts of the Ecal are separated by a vacuum chamber, see 
-Fig.~\ref{fig:ecal}. The beam and radiative secondaries pass between the two parts in vacuum, to avoid 
-generating unnecessary backgrounds. The crystal modules in each part are arranged in rectangular formation, as 
-shown in top panel of Fig.~\ref{fig:ecal}. There are 5 layers in each formation. Each layer has $46$ crystals except 
-for the layers closest to the beam 
+Like the tracker, the electromagnetic calorimeter is split into two parts, beam-up and beam-down, to avoid impinging on the “dead zone”.
+The two parts of the Ecal are separated by a vacuum chamber, see Fig.~\ref{fig:ecal}.
+The beam and radiative secondaries pass between the two parts in vacuum, to avoid generating unnecessary backgrounds.
+The crystal modules in each part are arranged in rectangular formation, as shown in top panel of Fig.~\ref{fig:ecal}.
+There are 5 layers in each formation.
+Each layer has $46$ crystals except for the layers closest to the beam
 plane where 9 modules were removed to allow a larger opening for the outgoing electron and photon beams. 
-In order to have stable light yield from crystals, and stable operation of APDs and preamplifiers, the module 
-assembly of each ECal part was enclosed inside a temperature controlled box.
-
-Inside the box PbWO$_{4}$ crystals were supported by aluminum frames stacked on top of each other.  The bias 
-voltage for APDs ($\sim 400$ V), the low voltage for preamplifiers ($\pm 5$ V), and the signals from APDs were 
-transmitted in and out of the enclosure through a backplane called motherboard. The $221$ modules in each part 
-of the ECal were divided into two low voltage groups and 12 bias voltage groups. Modules in bias voltage groups 
-were selected to have gain uniformity of $\sim 20\%$.
-
-During the test run ECal was mounted downstream of the analyzing dipole magnet at the distance of about 
-$147$~cm from the 
+In order to have stable light yield from crystals, and stable operation of APDs and preamplifiers, the module assembly of each ECal part was enclosed inside a temperature controlled box.
+
+Inside the box PbWO$_{4}$ crystals were supported by aluminum frames stacked on top of each other.
+The bias voltage for APDs ($\sim 400$ V), the low voltage for preamplifiers ($\pm 5$ V), and the signals from APDs were transmitted in and out of the enclosure through a backplane called motherboard.
+The $221$ modules in each part of the ECal were divided into two low voltage groups and 12 bias voltage groups.
+Modules in bias voltage groups were selected to have gain uniformity of $\sim 20\%$.
+
+During the test run ECal was mounted downstream of the analyzing dipole magnet at the distance of about $147$~cm from the 
 upstream edge of the magnet. 
@@
 %The primary electron beam, scattered electrons and bremsstrahlung photons pass through the system in vacuum. 
-The gap between innermost edge of the crystals of two parts was just $7.4$~cm from the beam. The temperature 
-stability of the system during the test run was better than $1^\circ~$F, the temperature uniformity inside the box 
-was better than $3^\circ~$C.
+The gap between innermost edge of the crystals of two parts was $7.4$~cm, centered on the beam plane.
+The temperature stability of the system during the test run was better than $1^\circ~$F, the temperature uniformity inside the box was better than  $4^\circ~$F.
 
@@
 \label{sec:fadc}
-Amplified APD signal from the motherboard is sent to a $2:1$ signal splitter. After the split, 2/3 of the signal is sent 
-a discriminator then to a Time-to-Digital Converter. The 1/3 of the signal is fed to a single channel of 16-channel 
-JLab Flash Amplitude-to-Digital Converter VXS module (FADC250)~\cite{fadc} shown in Fig.\ref{fig:fadc}.  
+
+ECal signal readout was organized as follows: the amplified APD signal from the motherboard is sent to a $2:1$ signal splitter.
+After the split, 2/3 of the signal is sent a discriminator then to a Time-to-Digital
+Converter (TDC). The 1/3 of the signal is fed to a single channel of 16-channel JLAB Flash Amplitude-to-Digital Converter (FADC250), see Fig.\ref{fig:fadc} \cite{fadc}.  
 \begin{figure}[t]
@@
 \includegraphics[width=7cm]{figures/FADC250_Photo_001.jpg}
-\caption{A JLab FADC250 VXS module.}
+\caption{A Jefferson Lab FADC250 VXS module.}
 \label{fig:fadc}
@@
 \end{figure}
-Two 20-slot VXS crates with 14 FADC bards were needed to accommodate the system: one for each half of the 
-ECal with 221 channels.
-
-The FADCs store 12-bit digitized samples at 250~MSPS in 8~$\mu$s deep pipelines. 
-When a trigger is received, the appropriate part of the pipeline is accessed for the readout. HPS used FADCs in 
-the co-called integration mode. A predefined number of samples of the signal that exceeds a predefined threshold 
-have been summed and stored in 17-bit register for readout. The number of samples for integration was defined 
-by two parameters that could be set separately, the number of samples integrated before the signal crossed 
-threshold ($NSB$) and  the number of samples integrated after the signal crossed threshold ($NSA$), 
-see Fig.~\ref{fig:hps_trigger_data}. 
+Two 20-slot VXS crates with 14 (for top ECal) and 13 (for bottom ECal) FADC bards were employed for the test run.
+
+The FADCs store 12-bit digitized samples at 250~MHz in 8~$\mu$s deep pipelines. 
+When a trigger is received, the appropriate part of the pipeline is accessed for the readout.
+HPS used FADCs in the integration mode.
+A predefined number of samples of the signal that exceeds a predefined threshold have been summed and stored in 17-bit register for readout.
+The number of samples for integration was defined by two parameters that could be set separately, the number of samples integrated before the signal crossed threshold ($NSB$) and  the number of samples integrated after the signal crossed threshold ($NSA$), see Fig.\ref{fig:hps_trigger_data}.
 This scheme significantly compresses the data input 
 to the FADC. During data analysis, a pedestal value is subtracted to obtain the actual summed energy.
+
+For various reasons only 385 out of 442 modules (87\%) were operational during the test run.
+The readout threshold was set to $70$ MeV, the number of samples before and after the threshold crossing were NSB=5 and NSA=30, respectively.
+
 \begin{figure}[]
@@
 {\small
-\includegraphics[width=7cm]{figures/hps_trigger_data}
+\includegraphics[width=8cm]{figures/fadc_datapath_diagram.png}
 \caption{\small{FADC data paths}}
@@
  \begin{itemize}
- \item FADC (pulse finding): samples and digitizes the signal pulses from each detector channel. Sends the 
- measured pulse energy and arrival time to the Crate Trigger Processor (CTP),
-\item CTP (cluster finding): groups FADC pulses from each half of the ECal into clusters. The cluster energy and 
-arrival time are sent to the Sub-System Processor (SSP),
- \item SSP (cluster pair finding): searches for time coincidence of pairs of clusters from the top and bottom half of 
- the ECal and applies topological selections.
+ \item FADC (pulse finding): samples and digitizes the signal pulses from each detector channel. Sends the measured pulse energy and arrival time to the Crate Trigger Processor (CTP),
+\item CTP (cluster finding): groups FADC pulses from each half of the ECal into clusters. The cluster energy and arrival time are sent to the Sub-System Processor (SSP),
+ \item SSP (cluster pair finding): searches for time coincidence of pairs of clusters from the top and bottom half of the ECal and applies topological selections.
  \end{itemize}
@@
 {\small
- \includegraphics[width=7cm]{figures/hps_trigger_cal}
-\caption{Block diagram of the ECAL trigger system consisting of the FADC that samples and digitizes the detector 
-	channel signals and sends them for cluster finding in the CTP. The CTP clusters are sent to the SSP where 
-	the final trigger decision is taken based on pairs of clusters in both halves of the ECal. The decision is sent to
-	the Trigger Supervisor (TS) that generates the necessary signals to readout the sub-detectors.}
+ \includegraphics[width=8cm]{figures/hps_trigger_cal}
+\caption{Block diagram of the ECAL trigger system consisting of the FADC that samples and digitizes signals for each detector channel and sends them for cluster finding in the CTP.
+The CTP clusters are sent to the SSP where the final trigger decision is taken based on pairs of clusters in both halves of the ECal.
+The decision is sent to the Trigger Supervisor (TS) that generates the necessary signals to readout the sub-detectors.}
  \label{fig:hps_trigger_cal}
@@
 As described above, the first stage of the trigger logic is incorporated into the 
-FPGA's on the FADC boards. For the trigger path, every channel has, in addition to $NSB$ and $NSA$: 
+FPGA's on the FADC boards. The trigger  
+integrates using a "time-over-threshold" window, see Fig. \ref{fig:hps_trigger_data}.
+For the trigger path, every channel has: 
 \begin{itemize}
@@
  \item trigger threshold, measured in ADC counts, 
- \item a pedestal, 
- \item a conversion factor (gain) that converts the ADC counts to energy in MeV (with 13 bits:  from 0 to 8191~MeV), 
+ \item an offset, 
+ \item a conversion factor that converts the ADC counts into 5-bits energy in MeV, from $50$ to $\sim1500$~MeV, 
  \item an energy discriminator threshold (minimum energy cutoff).
@@
 Note that the threshold for the trigger path can be set independently from the readout threshold.
-The pedestal value is subtracted from the integrated sum over $NSB+NSA$ samples and 
-converted to MeV units using a supplied gain conversion factor. The energy discriminator can be used to cut 
-off low energy pulses before reporting to CTP. 
+The offset is subtracted from ADC samples before they are integrated.  
 The values reported to the CTP are the 5-bit pulse energy and 3-bit time information at which the 
@@
 
-The final trigger decision is made by CTPs and SSP passed to the Trigger Supervisor (TS). The TS generates all 
-necessary signals and controls the entire DAQ 
+ The final trigger decision is made by CTPs and SSP passed to the Trigger Supervisor (TS). The TS generates all necessary signals and controls the entire DAQ 
 system readout through the Trigger Interface (TI) units. The TI units are installed in every crate that participate 
@@
 
-During the test run, for the most part trigger system run in single cluster mode and was tested to work for up to 
-20~kHz trigger rates.
+During the test run, for the most part trigger system run in single cluster mode and was tested to work for up to 20 kHz trigger rates.
 
@@
 that collects digitized information, processes it, and sends it on to the Event Builder (EB). The ROC is a single 
-blade Intel-based CPU module running DAQ software under CentOS Linux OS. For the SVT DAQ system, 
-the ROC application runs on a dedicated DAQ desktop computer. The EB assembles 
-information from the SVT and Cal ROCs into a single event which is passed to the Event 
-Recorder (ER) that writes it to a RAID5-based data storage system capable of handling up to 100~MB/s. The 
+blade Intel-based CPU module running DAQ software under CentOS Linux OS. For the SVT ATCA system, 
+the ROC application runs on an embedded processor situated on the ATCA main board. The EB assembles 
+information from the SVT and ECal ROCs into a single event which is passed to the Event 
+Recorder (ER) that writes it to a RAID5-based data storage system capable of handling up to 100 MB/s. The 
 EB and other critical components run on multicore Intel-based multi-CPU servers. The DAQ network system is 
 a Foundry router providing high-speed connections between the DAQ components and to the JLab 
-computing facility. The SVT ROC, which must handle large data volumes, has a 10~Gb/s link to the Foundry 
-router, while a 1~Gb/s link is adequate for the ECal. A 10~Gb/s uplink to the JLab 
+computing facility. The SVT ROC, which must handle large data volumes, has a 10 Gbit/s link to the Foundry 
+router, while a 1 Gbit/s link is adequate for the ECal. A 10 Gbit/s uplink to the JLab 
 computing facility is used for long-term storage.
@@
 
-%\subsubsection{ECal Calibration and Performance}
-
-Only 385 out of 442 modules (87\%) were operational during the test run.  Of 442 modules, 39 were disabled or 
-disconnected and were not read out by the DAQ. 
-13 of these were not read out because of a shortage of FADC readout boards.
-The remainder either had no HV bias on the APD, or were disabled in the FADC software due to noise.
+%step Of 442 modules, 39 were disabled or disconnected and were not read out by the DAQ.
+13 of these were not read out because of a shortage of FADC readout boards (see Sec.~\ref{sec:fadc}).The remainder either had no HV bias on the APD, or were disabled in the FADC software due to noise.
 In the data, we identified two types of abnormal channels.
 One FADC was not sending trigger signals correctly, resulting in low efficiency.
- This affected the 13 channels read out by that FADC. 5 channels were diagnosed as noisy because they 
- had a high incidence of hits out of coincidence with the trigger. A large number of channels were originally 
- misidentified as noisy because they had much higher hit occupancy than neighboring channels.
-Gain calibration shows that these channels have high gain (and thus lower energy threshold) but are otherwise 
-normal. The abnormal channels were ignored in analysis in order to simplify comparison with Monte Carlo. This 
-leaves 385 useful channels---87\% of the ECal.
-
-The noise level of the ECal modules were measured to be approximately 15~MeV. The ECal was operated 
-with an effective readout threshold of 70~MeV. Modules above thresholds are clustered using a simple robust 
-algorithm described in Sec.~\ref{sec:trigger}.
-
-%\subsubsection{Calibration}
-%\label{sec:ecal_calibration}
-The noise and pedestal of the readout chain are calibrated by running the ECal readout in a mode where the 
-preamplifier output is sampled every 4~ns in a time window of 100 samples: by looking at a part of the 
-window before the hit,  the readout channel pedestal can be obtained. 
-We calibrate gain of the individual ECal channels using the SVT measurement of track momentum and 
-comparison to Monte Carlo simulation.  We disable all SVT and ECal channels in the simulation that were 
-inoperable or noisy in the test run, so any efficiency or bias effects that affect the real data should be reflected 
-in the simulation as well; then we use a formula to compute the ``weighted E/p'' for a crystal, representing the average E/p for clusters that include the crystal
+This affected the 13 channels read out by that FADC.
+5 channels were diagnosed as noisy because they  had a high incidence of hits out of coincidence with the trigger.
+A large number of channels were originally misidentified as noisy because they had much higher hit occupancy than neighboring channels.
+Gain calibration shows that these channels have high gain (and thus lower energy threshold) but are otherwise normal.
+The abnormal channels were ignored in analysis in order to simplify comparison with Monte Carlo.
+This leaves 385 useful channels---87\% of the ECal.
+
+The gain of the individual ECal channels has been calibrated using the SVT measurement of track momentum and comparison to Monte Carlo simulation.
+The integrated pulse of the each channel was converted to energy by first subtracting the pedestal then applying a gain or conversion factor to convert ADC counts to energy in MeV.
+The pedestals have been measured using special runs where FADCs sampled APD signals every 4~ns and for each trigger a time window of 100 samples have been recorded.
+Pedestal levels were determined by looking at a part of the
+window before the actual hit. Modules above a threshold are clustered using a simple algorithm described in Sec.~\ref{sec:trigger}. The ECal was operated 
+with an effective readout threshold of 73~MeV. The noise level of the ECal modules were measured to be approximately 15~MeV.
+
+To compare data and simulation, all inoperable or noisy channels in SVT and ECal have been disabled in the simulation, so any efficiency or bias effects that affect the real data should be reflected 
+in the simulation as well. Using a formula to compute the ``weighted E/p'' for a crystal, representing the average E/p for clusters that include the crystal
 % $\frac{\sum_j w_{j,i}}{\sum_j\frac{P_j}{E_j}w_{j,i}}$
@@
 \end{figure}
+
 These gains can then be used to convert from ADC counts in a channel to the energy deposited into that ECal 
@@
 The other information needed to find the energy of an incident particle is the sampling fraction---the ratio of 
-energy read out from crystals to energy of an incident particle. The conventional sampling fraction, 
-the fraction of incident energy that is deposited in crystals, is approximately 0.9  for the center of the ECal and less 
-at the 
-edges. For our readout, there is additional energy lost because crystals under the readout threshold are not 
+energy read out from cluster to energy of an incident particle. The conventional sampling fraction, 
+the fraction of incident energy that is deposited in the cluster, is approximately 0.9  for the ECal (somewhat less at the 
+edges). For our readout, there is additional energy lost because crystals under the threshold are not 
 read out.
@@
 These turn-on curves are shown for the top half of the ECal in Fig.~\ref{fig:turnon}.
+
 \begin{figure}[ht]

### 2013-11-11 hps-testrun-nim.tex
Johns rape of the summary sections

@@
 \label{introduction}
-One of the more striking anomalies in recent astrophysical observations is an excess of high energy electrons and positrons consistent with a large, unknown source of pair production~\cite{Adriani:2008zr}\cite{FermiLAT:2011ab}.
-The existence of a massive, hidden sector vector boson; a ``dark photon;" that mixes kinetically with the Standard Model photon and mediates annihilation or decay of dark matter particles is a theoretically attractive explanation of this cosmic-ray excess~\cite{Holdom:1985ag}\cite{ArkaniHamed:2008qn}.
+One of the more striking anomalies in recent astrophysical observations is an excess of high energy electrons 
+and positrons consistent with a large, unknown source of pair production~\cite{Adriani:2008zr}\cite{FermiLAT:
+2011ab}. The existence of a massive, hidden sector vector boson; a ``dark photon;" that mixes kinetically with 
+the Standard Model photon and mediates annihilation or decay of dark matter particles is a theoretically 
+attractive explanation of this cosmic-ray excess~\cite{Holdom:1985ag}\cite{ArkaniHamed:2008qn}.
 \begin{center}
@@
 would be subject to almost the same constraints and requirements as the full experiment.
-The kinematics of \Aprime{} production typically results in final state particles within a few degrees of the incoming beam, especially at low 
-$m_{\Aprime{}}$.  
+The kinematics of \Aprime{} production typically results in final state particles within a few degrees of the 
+incoming beam, especially at low $m_{\Aprime{}}$.  
 %Step
@@
 
-\section{Summary}
-
-This paper reviewed the HPS Test run apparatus, a simplified version of that 
-planned for the full HPS experiment, and demonstrates the feasibility of the detector
-technologies proposed for the silicon vertex tracker, the electromagnetic calorimeter, data acquisition and 
-trigger systems and their performance. Of particular importance, data from dedicated photon beam running has 
-been used to compare
-the observed trigger rates with that expected in simulation. The trigger rate is almost entirely due to
-photons which have converted to \ee{} upstream of the HPS Test setup and is sensitive to the multiple
-Coulomb scattering of electrons and positrons in the conversion target.  Since scattered primary beam is 
-the dominant source of occupancy in running HPS in an electron beam, good agreement between data and 
-simulation confirm the background simulation used to benchmark the physics reach of the HPS experiment.
-
-In addition to this important test of our background simulation, the HPS Test run accomplished the following 
-goals:
-\begin{itemize}
-	\item More than 97\% of the SVT channels functioned properly
-	\item SVT readout signal to noise of XXXX, required to achieve the expected spatial and temporal resolutions
-	\item SVT hit time resolution of 2.6~ns, proving hit time reconstruction will work for HPS
-	\item SVT hit efficiency greater than 98\%
-	%\item SVT track reconstruction efficiency greater than 98\%
-	\item Survey-based SVT alignment performed as expected and will allow track-based alignment
-	\item 87\% of ECal crystals functioned properly, with defects to be corrected by planned ECal upgrades
-	\item The ECal has been calibrated using SVT tracks
-	\item The SVT and JLab data acquisition systems were successfully integrated
-	\item The trigger functioned as designed; rates greater than 100~kHz was tested in special runs
-	% deficiencies found in test run trigger performance are addressed for the 2014-2015 run
-\end{itemize}
-
-While the HPS Test run successfully allowed us to test many aspects of the HPS experiment, there were 
-limitations to what could be achieved in some key areas such as mass resolution and vertexing 
-performance. In particular, the low statistics and lack of resonances or scattered beam electrons prohibits a 
-direct analysis of the momentum resolution 
-and tails of the vertex distribution. However, for both of these performance parameters, the observed 
-agreement between data and simulation in key distributions supports the performance expected for the 
-proposed experiment.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Lessons Learned and Outlook}
-
-In the process of developing the HPS Test design, it was found that this simple system was capable of 
-delivering a surprising fraction of the physics potential anticipated for the full experiment.  With this in mind, 
-we have proposed a new design for the HPS detector that builds upon the HPS Test , principally 
-by addressing the compromises made for HPS Test to ensure the best possible performance for \Aprime{} 
-physics within the envelope of the existing beam line layout and analyzing magnet. For the SVT, 
-this design uses the same sensors, readout chips, and module concept and for the ECal the crystal and 
-detector layout will be identical, retaining the most successful 
-elements of the test run apparatus and addressing the weaknesses identified during assembly and 
-operation. The new SVT layout adds a sixth layer for more robust tracking, adds acceptance in the 
-three deeper layers to increase physics sensitivity and provides better silicon cooling to improve longevity. 
-Other major updates needed for the full experiment are updates to the SVT electronics and 
-DAQ; improving connectivity and cabling, moving digitization closer to the front-end electronics and 
-updating the data reduction, event handling and trigger synchronization to reach 50~kHz trigger rates. 
-This first generation of the full experiment will be ready to take physics data when CEBAF begins operation 
-again in end of 2014.
+\section{Summary and Outlook}
+
+%This paper reviewed 
+The HPS Test Run experiment, using a simplified version of the apparatus planned for the full HPS experiment in a parasitic photon beam, demonstrated the feasibility of the detector technologies proposed for the HPS silicon tracker, ECal, and data acquisition systems.
+Performance from each of these subsystems has been shown to be adequate to conduct the full experiment successfully.
+A measurement of the normalized trigger rates from a photon conversion target confirmed expectations from simulation, giving credance to estimates of the trigger rates and the detector backgrounds expected in electron beam running.
+
+%The test run achieved the following detector performance:\begin
+%{enumerate}
+%	\item More than 97\% of SVT channels functioned properly
+%	\item Silicon detector signal to noise was 25.5, good enough %to achieve the expected resolutions
+%	\item SVT hit time resolution was 2.6 ns, which will permit %background rejection with tight timing cuts 
+%	\item SVT hit efficiency was greater than 98\%
+%	%\item SVT track reconstruction efficiency was greater than %98\%
+%	\item 87\% of ECal crystals functioned properly, with %%defects to be corrected by planned ECal upgrades
+%	\item The ECal has been successfully calibrated using SVT %tracks
+%	\item The SVT and JLab DAQ were successfully integrated
+%	\item The trigger functioned as designed; the FADC trigger 
+%rate was tested to greater than 100~kHz
+% deficiencies found in test run trigger performance are 
+%addressed for the 2014-2015 run
+%\end{enumerate}
+
+%While the Test Run successfully allowed us to test many aspects %of the HPS experiment, there were 
+%limitations to what could be achieved in some key areas such as %mass resolution and vertexing 
+%performance. In particular, the low statistics and lack of 
+%resonances or scattered beam electrons prohibits a 
+%direct analysis of the momentum 
+%and tails of the vertex distribution. However, for both of these %performance parameters, the observed 
+%agreement between data and simulation in key distributions 
+%supports the performance expected for the 
+%proposed experiment.
+
+%\subsection{Lessons Learned}
+
+%In the process of developing the HPS Test design, it was found 
+%that this simple system was capable of 
+%delivering a surprising fraction of the physics potential 
+%anticipated for the full experiment.  With this in mind, 
+%we have proposed a new design for the HPS detector that builds 
+%upon the HPS Test , principally 
+%by addressing the compromises made for HPS Test to ensure the 
+%best possible performance for A$^\prime$ 
+%physics within the envelope of the existing beam line layout and %analyzing magnet. For the SVT, 
+%this design uses the same sensors, readout chips, and module 
+%concept and for the ECal the crystal and 
+%detector layout will be identical, retaining the most successful 
+%elements of the test run apparatus and addressing the weaknesses %identified during assembly and 
+%operation to ensure the success of the 
+%experiment. The new SVT layout restores the sixth layer for more %robust tracking, adds acceptance in the 
+%deeper layers to increase sensitivity and provides better 
+%silicon cooling to improve longevity. Other major 
+%updates needed for the full experiment are updates to the SVT 
+%electronics and 
+%DAQ; improving connectivity and cabling, moving digitization 
+%closer to the front-end electronics and 
+%updating the data reduction, event handling and trigger 
+%synchronization to reach 50kHz 
+%trigger rates. 
+%This first generation of 
+%the full experiment will be ready to take physics data when 
+%CEBAF begins operation again in 2014.
 

### 2013-11-11 hps-testrun-nim.tex
Johns edits to mCS section

@@
 One of the more striking anomalies in recent astrophysical observations is an excess of high energy electrons 
-and positrons consistent with a large, unknown source of pair production~\cite{Adriani:2008zr}\cite{FermiLAT:
-2011ab}. The existence of a massive, hidden sector vector boson; a ``dark photon;" that mixes kinetically with 
+and positrons consistent with a large, unknown source of pair 
+production~\cite{Adriani:2008zr,FermiLAT:2011ab}. 
+The existence of a massive, hidden sector vector boson; a ``dark photon;" that mixes kinetically with 
 the Standard Model photon and mediates annihilation or decay of dark matter particles is a theoretically 
@@
 
-We measure the vertical angular distributions of electrons and positrons using the ECal. 
-Cluster reconstruction and calibration was performed as described in Sec.~\ref{sec:ecal}. The measured 
+For this analysis, we measure angular distribution of electrons and positrons using the ECal.
+Cluster reconstruction was done using the algorithm described in Sec.~\ref{sec:trigger} build 
+clusters around seed hits (hits above a ``seed'' energy threshold and with greater energy than any 
+neighboring hits), and add all neighboring hits above an ``add'' energy threshold.
+Hit energy is calibrated by matching track momentum to cluster energy, as described in Sec.~\ref{sec:ecal_calibration}.
+
+The measured 
 angular distribution in the ECal for the three converter thicknesses are shown in 
-Fig.~\ref{fig:ang_distr_data} (left). The data has been normalized to the integrated beam current and 
-the upstream background has been subtracted. 
+Fig.~\ref{fig:ang_distr_data} (left). 
 \begin{figure}[]
@@
 	\includegraphics[ width=7cm]{figures/rate_ecalrow_norm_subtr.png}
-	\caption{Measured vertical angular distributions before after integrated beam current 
-	normalization and upstream background subtraction.}
+	\caption{Measured vertical angular distributions after integrated beam current 
+	normalization and background subtraction.}
 	\label{fig:ang_distr_data}
@@
 \end{figure}
-The background fraction for the three converter thicknesses was 16\%, 52\% and 71\% 
+The data has been normalized to the integrated beam current and the background has been 
+subtracted. 
+The background fraction for the there converter thicknesses was 16\%, 52\% and 71\% 
 for converter thicknesses of 1.6\%, 0.45\% and 0.18\%, respectively. The background fraction was also 
-cross-checked by pointing back tracks reconstructed in the SVT to identify the fraction of tracks not originating 
-from the converter. We also checked that the contribution from photons to our triggered 
-sample was much less than 2\%. These measured angular distributions are compared to simulation to validate 
+cross-checked by pointing back tracks reconstructed in the SVT to identify the fraction of tracks not emanating from the converter. 
+%This can be seen in Fig.~\ref{fig:extrapol_converter} (bottom) where small 
+%satellite peaks at $\pm 10$~mm can be identified as tracks from the upstream background. The angular distribution, after normalization and subtracting the upstream background, are shown in 
+%Fig.~\ref{fig:ang_distr_data} (right).  
+We also checked that the contribution from photons to our triggered 
+sample was less than 2\% (without angular selections which would further reduce the contribution).
+
+These measured angular distributions are compared to simulation to validate 
 the modeling of the MCS. \egs{}~\cite{egs5} is used to generate 
@@
 \end{center}
-The total systematic uncertainty was estimated to be between 10-18\% depending on the run, they include:  
-uncertainty on the integrated current normalization (5\%), alignment of the ECal, uncertainty from the 
-background normalization and limited Monte Carlo statistics.  
+The total systematic uncertainty was estimated to be between 10-18\% depending on the run including:  
+a 5\% uncertainty on the integrated current normalization, alignment of the ECal, uncertainty from the 
+background normalization, and limited Monte Carlo statistics.  
+\begin{center}
+{\small
 \begin{table}
-\begin{center}
-{\small
 \begin{tabular}{|l|c|c|c|}
 \hline
-Converter (\% $X_0$) & 1.60 & 0.45 &	0.18 \\
+Converter (\% r.l.) & 1.60 & 0.45 &	0.18 \\
 \hline
-\egs{} &	1162 $\pm$ 112 &	255 $\pm$ 28 &	94 $\pm$ 17	\\
+EGS5 &	1162 $\pm$ 112 &	255 $\pm$ 28 &	94 $\pm$ 17	\\
 \hline
-\geant{} & 2633 $\pm$ 250 & 	371 $\pm$ 38 &	114 $\pm$ 18 \\
+GEANT4 & 2633 $\pm$ 250 & 	371 $\pm$ 38 &	114 $\pm$ 18 \\
 \hline
@@
 \label{tab:ang_distr_dataMC}
-}
-\end{center}
 \end{table}
-As expected \egs{} show good agreement with our data while \geant{} using the default physics list 
-overestimates the MCS at these large angles.
+}
+\end{center}
 

### 2013-11-12 hps-testrun-nim.tex
John's changes to mostly detector overview and intro.

@@
 \label{introduction}
-One of the more striking anomalies in recent astrophysical observations is an excess of high energy electrons 
-and positrons consistent with a large, unknown source of pair 
-production~\cite{Adriani:2008zr,FermiLAT:2011ab}. 
-The existence of a massive, hidden sector vector boson; a ``dark photon;" that mixes kinetically with 
-the Standard Model photon and mediates annihilation or decay of dark matter particles is a theoretically 
-attractive explanation of this cosmic-ray excess~\cite{Holdom:1985ag}\cite{ArkaniHamed:2008qn}.
+One of the more striking anomalies in recent astrophysical observations is an excess of high energy 
+electrons and positrons consistent with a large, unknown source of pair 
+production~\cite{Adriani:2008zr, FermiLAT:2011ab}. The existence of a massive, hidden sector vector 
+boson; a ``dark photon;" that mixes kinetically with the Standard Model photon and mediates 
+annihilation or decay of dark matter particles is a theoretically attractive explanation of this cosmic-ray 
+excess~\cite{Holdom:1985ag}\cite{ArkaniHamed:2008qn}.
 \begin{center}
@@
     \includegraphics[width=0.8\textwidth]{figures/hps_testrun_rendering}
-\caption{Rendering of the HPS Test apparatus installed on the beam line.}
+\caption{Rendering of the HPS Test apparatus installed on the beam line. SHOULD FIND A PIC WITH LOWER HEIGHT.}
 \label{fig:testrundetector}
@@
 
-Heavy photons, aka known as "hidden sector" or "dark" photons, are particles with mass 10-1000 MeV which 
-couple
-weakly to the SM photon, so can be radiated by electrons, and can decay into e+e- pairs, albeit at rates far
-below those of QED trident processes. They have been suggested by numerous Beyond Standard Model 
-theories and
-as an explanation of the current muonic g-2 anomaly, and may couple directly
-to hidden sector particles that may constitute all or some of the dark matter. Current phenomenology highlights 
-the 
-20-1000 MeV mass range, and suggests that heavy photons couple to electric charge with strength 
-$\epsilon$e, where 
-$\epsilon$ is in the range of $10^{-3} -10^{-5}$. This range of parameters makes heavy photon searches viable 
-at electron-positron colliders and in moderate energy fixed target electroproduction, and results from both
-approaches have already been reported. Fixed target experiments offer the highest sensitivity 
-for heavy photons with mass $<1000$~MeV~\cite{Bjorken:2009mm}, but require large data sets and good 
-mass resolution to identify a small mass peak above the copious QED background. At small couplings, heavy 
-photons become long-lived, so detection of a secondary decay vertex can reject the prompt QED background 
+Heavy photons, aka "hidden sector" or "dark" photons, are particles with mass 10-1000 MeV which 
+couple weakly to the SM photon, so can be radiated by electrons, and can decay into e+e- pairs, albeit 
+at rates far below those of QED trident processes. They have been suggested by numerous Beyond 
+Standard Model theories and as an explanation of the current muonic g-2 anomaly, and may couple 
+directly to hidden sector particles that may constitute all or some of the dark matter. Current 
+phenomenology highlights the 20-1000~MeV/c$^{2}$ mass range, and suggests that heavy photons 
+couple to electric charge with strength $\epsilon$e, where 
+$\epsilon$ is in the range of $10^{-3} -10^{-5}$. This range of parameters makes heavy photon searches 
+viable at electron-positron colliders and in moderate energy fixed target electroproduction, and results 
+from both approaches have already been reported. Fixed target experiments offer the highest sensitivity 
+for heavy photons with mass $<1000$~MeV/c$^{2}$ ~\cite{Bjorken:2009mm}, but require large data 
+sets and good mass resolution
+to identify a small mass peak above the copious QED background. At small couplings, heavy photons 
+become long-lived, so detection of a secondary decay vertex can reject the prompt QED background 
 and boost experimental sensitivity.
-The HPS experiment uses both invariant mass and vertex signatures by placing a compact silicon tracking and 
-vertexing detector ($\approx 1$~m long) immediately downstream ($\approx 10$~cm) of a thin target 
-($\approx0.25~X_0$ tungsten) and inside of a dipole magnet ($\approx 1$~T)~\cite{HPS_proposal_2010}. 
-The experiment runs at high rates, exploiting the 100\% duty cycle of the 
-CEBAF accelerator to accumulate the need statistics. The trigger is provided by a fast electromagnetic 
-calorimeter just downstream of the magnet.
+The HPS experiment uses both invariant mass and vertex signatures by placing a $\approx 1$~m long 
+silicon tracking and vertexing detector (10~cm) downstream  of a 0.25 \%X$_0$ tungsten) target and 
+inside a dipole magnet~\cite{HPS_proposal_2010}. The experiment runs at high rates, exploiting the 
+100\% duty cycle of the CEBAF accelerator to accumulate the need statistics. The trigger is provided by 
+a fast electromagnetic calorimeter just downstream of the magnet.
 
 The HPS Test run, a simplified version of the full HPS experiment, was proposed and approved at JLab 
-as the first stage of the HPS experiment.  Its purposes included demonstrating that the apparatus and data 
-acquisition systems are technically feasible and
-that the trigger rates and occupancies encountered in electron-beam running are as simulated. Additionally,
-given dedicated running time with electron beams, the HPS Test Run could provide new sensitivity to heavy 
-photons. The HPS Test apparatus was installed on April 19, 2012, and 
+as the first stage of the HPS experiment. Its
+purposes included demonstrating that the apparatus and data acquisition systems are technically 
+feasible and that the trigger rates and occupancies encountered in electron-beam running are as 
+simulated. Given dedicated running time with electron beams, the HPS Test Run apparatus is capable of 
+searching for heavy photons in unexplored regions of parameter space.    
+The HPS Test apparatus was installed on April 19, 2012, and 
 ran parasitically with the HDice experiment, using its photon beam, until May 18. The JLab run schedule 
-precluded any dedicated electron beam running, but the HPS Test Run was allowed a short and valuable
-dedicated run with the photon beam.
-
-This paper reviews the HPS Test Run apparatus. It documents the successful performance of the trigger, data 
-acquisition, silicon tracker, and ECal and
-shows that the performance assumed in calculating the physics reach of the experiment is realistic.
-Of particular importance, data from the dedicated photon beam running has been used to compare
-the measured trigger rates with those expected in simulation. The Test Run trigger rate is almost entirely due to
-photons which have converted to \ee{} pairs in a thin target upstream of HPS and it is sensitive to the particulars 
-of their multiple Coulomb scattering in the conversion target.  Since, during electron beam running, the tails of 
-the multiply Coulomb scattered primary beam are the dominant source of occupancy in the tracker and the 
-trigger rate in the Ecal, they must be understood quantitatively. The trigger rates in the Test Run are also 
-sensitive to the tails of the multiple Coulomb scattering distribution. Good agreement between the measured 
-and simulated rates confirms our understanding of multiple Coulomb scattering and 
+precluded any dedicated electron beam running, but the HPS Test Run was allowed a short and 
+valuable dedicated run with the photon beam.
+
+This paper reviews the HPS Test Run apparatus; documents the successful performance of the trigger, 
+data acquisition, silicon tracker, and ECal at the level assumed in calculating the physics reach of the 
+experiment. Of particular importance, data from the dedicated photon beam running has been used to 
+compare the measured trigger rates with those expected in simulation. The Test Run trigger rate is 
+almost entirely due to photons which have converted to \ee pairs in a thin target upstream of HPS and it 
+is sensitive to their multiple Coulomb scattering in the conversion target.  During electron beam running, 
+the tails of the multiply Coulomb scattered primary beam are the dominant source of occupancy in the 
+tracker and trigger rate in the electromagnetic calorimeter. 
+The trigger rates in the Test Run are also sensitive to the tails of the multiple Coulomb
+scattering distribution. Good agreement between the measured and simulated rates confirms
+our understanding of multiple Coulomb scattering and 
 the reliability of the background simulation used to benchmark the physics reach of the HPS experiment.
 
-The very small signal rate compared to the large background and the need to reconstruct the final states of 
-the electron and positron in a dense radiation environment millimeters from a high-current beam 
-place stringent requirements on the detector, which should have,
+Searching for a small signal on a large background requires high statistics. This in turn requires the 
+experiment operate with high beam currents, handle very high data rates, and tolerate high radiation 
+levels. In particular, the following are required:
 \begin{itemize}
-\item large and uniform acceptance in the forward region to catch boosted decay products,
+\item large and uniform acceptance in the forward region close to the beam in order to catch boosted heavy photon decay products,
+\item beam passage through the apparatus in vacuum, to eliminate direct interactions with the detector and minimize beam gas interactions, 
 \item a flexible, redundant and efficient trigger selecting electron and positron pairs at rates up to 50kHz,
@@
 \item good angular and momentum resolution to reconstruct invariant mass precisely,
-\item excellent vertex resolution to search for displaced heavy photon decays,
-\item high rate electronics with event timing resolution down to 2~ns,
-\item data acquisition system capable of handling data rates of 100~MB/s to permanent storage,
+\item excellent vertex resolution to discriminate displaced heavy photon decays from prompt QED backgrounds,
+\item high rate electronics with excellent timing resolution to minimize out of time backgrounds,
+\item data handling rates of 100~MB/s to permanent storage,
 \item detector components that can survive and efficiently operate in a high radiation environment with 
-local doses exceeding $100$~Mrad
+local doses exceeding $100$~Mrad.
 \end{itemize}
@@
 \label{detector}
-The HPS experiment is proposed to run in Hall B using electron beams of Continuos Electron Beam 
-Accelerator Facility (CEBAF) at JLab. CEBAF can simultaneously deliver  electron 
-beams to multiple experimental hall at 499 MHz frequency with beam currents of up to 150 $\mu$A (Hall-B 
-is limited to $<1 ~\mu$A).  Currently CEBAF facilities are undergoing energy an upgrade that is expected to be 
-completed in end of 2014. The upgraded CEBAF machine will double its maximum energy from $6$~GeV 
-during the HPS test run to $12$~GeV.
-
-The HPS Test apparatus was designed as a 
-first step of a multi-stage approach 
-to the HPS experiment. The primary goal was to demonstrate that the technology and design approach 
-chosen are sound for running in such a challenging environment. Nevertheless, a secondary but 
-important aspect was that, after proving the technical concepts,  the apparatus would have the 
-capability to discover \Aprime{} events. The implication was that the design of the HPS Test apparatus 
-would be subject to almost the same constraints and requirements as the full experiment.
-The kinematics of \Aprime{} production typically results in final state particles within a few degrees of the 
-incoming beam, especially at low $m_{\Aprime{}}$.  
-%Step
-This implies that the apparatus for an \Aprime{} search in electron interactions with fix targets must operate in 
-close proximity to an intense electron beam that passes through a high-Z target. 
-Hence it should cope with high backgrounds and tolerate the high radiation environment. 
-To meet this challenge, HPS will deploy high rate and radiation hard detector composed of 
-a silicon vertex tracker with 40~MHz readout and a PbWO$_4$ crystal calorimeter with 250~MHz 
-readout, capable of triggering multi-prong events at top to 50~kHz rate.
-
-%\subsection{HPS Test setup}
-
-The HPS Test apparatus, a simplified version of that 
-planned for the full HPS experiment, demonstrates the feasibility of the detector
-technologies proposed for the silicon tracker, electromagnetic calorimeter, and data acquisition system. 
-A rendering of the HPS Test setup is shown in Fig.~\ref{fig:testrundetector}. The setup is based on the Hall-B 
-pair spectrometer (PS) magnet, 18D36 dipole. The silicon vertex tracker (SVT) was installed inside the vacuum 
-chamber of PS and the electromagnetic calorimeter (ECal) was mounted behind the vacuum flange. 
-A new vacuum box 
-attached to the upstream end of the pair spectrometer vacuum chamber provided necessary services to 
-the SVT (cooling, power and signal readout). 
-Most technologies used in the HPS Test apparatus as well as the magnet and the vacuum chamber will be 
-used in the HPS detector with some 
+The HPS experiment will run in Hall B at JLab using the CEBAF electron beam, a 
+499 MHz beam at energies ranging up to 11 GeV and currents up to 800 nA.  
+The design of the experiment follows from the kinematics of \Aprime production which 
+typically results in final state particles within a few degrees of the incoming beam, especially at low 
+$m_{\textrm{A}^\prime}$. So detectors must be placed close to the beam. The intense electron beam 
+and the degraded electrons produced in the target and spread out horizontally by the analyzing magnet 
+constitute a "dead zone"  which must be completely avoided, so the apparatus is split vertically above 
+and below the beam plane. The beam is transported in vacuum to minimize beam gas backgrounds. 
+Even so, background rates in the detectors remain high, so high rate detectors,
+a fast trigger, and excellent time tagging are required to minimize their impact. 
+At masses below $2 m_\mu$ only decays to electrons are allowed, so the key trigger 
+comes from a lead-tungstate calorimeter with 250~MHz readout.  
+%Above the di-muon threshold, a 
+%downstream muon detector completes the trigger acceptance and may allow triggering for pion final states 
+%required for sensitivity near the $\rho$ mass.
+
+A rendering of the HPS Test apparatus installed on the beam line is shown in 
+Fig.~\ref{fig:testrundetector}.
+Most technologies used in the HPS Test apparatus will be used in the HPS detector with some 
 improvements to each of the systems; both from lessons learned during running of the HPS Test but 
-also from planned upgrades for longer and more effective running.
-
+also from less schedule and budget constraints.
+
+An overview of the coverage, segmentation and performance of the HPS Test detector is given in 
+Tab.~\ref{tab:detector-overview}. 
 %\begin{multicols}{2}
@@
 
-An overview of the coverage, segmentation and performance of the HPS Test detector is given in 
-Tab.~\ref{tab:detector-overview}.  In order to accommodate the dead zone, the SVT and ECal are built in two 
-halves that are mirror reflections of one 
-another about the plane of the nominal electron beam.  Each half of the SVT consists of five double-sided 
-modules 
-mounted on a support plate that provides services to the modules and allows them to be moved as a group 
-relative to the dead zone. Each module places a pair of silicon microstrip sensors back-to-back at a 
-specified stereo angle with independent cooling and support. The sensors are read out
-continuously at 40~MHz using the APV25 ASIC, developed for the CMS experiment at the
-LHC.
-
-Each half of the ECal consists of 221 PbWO$_4$ crystals arranged in rectangular formation. 
-There are five rows with 46 
-modules in each row except the row closest to the beam plane which has 37. The light from each crystal is read 
-out by Avalanche Photodiode (APD) glued on the back surface of the crystal. 
-Signals from the APDs were amplified using custom-made amplifier boards before being sent to the readout 
-electronics.
+The silicon tracking and vertexing detector for HPS Test, or SVT, operates in an existing vacuum 
+chamber inside the pair spectrometer analyzing magnet in Hall B at JLab.  The design principles of the 
+SVT are described in further detail in the HPS Test Run Proposal ~\cite{HPS_tPROP}. There are five 
+measurement stations, or ``layers,'' placed immediately downstream of the target. Each layer comprises 
+a pair of closely-spaced planes and each plane is responsible for measuring a single coordinate, or 
+``view.'' Introduction of a stereo angle between the two planes of each layer provides three-dimensional 
+tracking and vertexing throughout the acceptance of the detector with one redundant layer.
+
+In order to accommodate the dead zone, the SVT is built in two halves that are mirror reflections of one 
+another about the plane of the nominal electron beam.  Each half consists of five double-sided modules 
+mounted on a support plate that provides services to the modules and allows them to be moved as a 
+group relative to the dead zone. Each module places a pair of silicon microstrip sensors back-to-back at 
+a specified stereo angle with independent cooling and support.
+
+Each half of the electromagnetic calorimeter, or ECal, consists of 221 PbWO$_4$ crystals arranged in 
+rectangular formation. There are five rows with 46 
+modules in each row except the row closest to the beam plane which has 37. The light from each crystal 
+is read out by Avalanche Photodiode (APD) glued on the back surface of the crystal. 
+Signals from the APDs were amplified using custom-made amplifier boards before being sent to the 
+readout electronics.
 
 The  Data Acquisition system combines two architectures, the Advanced Telecom Communications 
-Architecture (ATCA) based SVT readout system and VXS based digitization and triggering system for the ECal. 
-The system was designed to run at up to a 20 kHz trigger rate.
+Architecture (ATCA) based SVT readout system and VXS based digitization and triggering system for the 
+ECal. The system was designed to run at up to a 20 kHz trigger rate.
 
@@
 Interconnect (CI) concept developed at SLAC as generic building blocks for DAQ systems in high energy 
-physics {\bf [need reference]}. 
-The RCE is a generic computational building block, housed on a separate daughter card called 
-Data Processing Module (DPM), that are realized on an ATCA front board called the Cluster On Board (COB), 
-see Fig.~\ref{fig:cob}.
+physics . The RCE is a generic computational building block, housed on a separate daughter card 
+called Data Processing Module (DPM), that are realized on an ATCA front board called the Cluster On 
+Board (COB), see Fig.~\ref{fig:cob}.
  \begin{figure}[]

### 2013-11-13 hps-testrun-nim.tex
Tim's shortening of SVT detector section.

@@
 
-The principle purpose of the HPS Test Silicon Vertex Tracker (SVT) is the efficient detection of 
-charged particles and reconstruction of their momentum and angles. The precise measurements 
-forms the primary input to the extraction of a signal from \Aprime{} decays; both from the precise 
-measurement of the invariant mass of its \ee{} decay products and the position of its decay vertex 
-downstream of the target. Track reconstruction is also important for energy scale calibration of the 
-electromagnetic calorimeter due to the better momentum resolution of tracks compared to clusters 
-in the calorimeter.
-
-\subsection{SVT Requirements and Constraints}
+The Silicon Vertex Tracker (SVT) enables efficient reconstruction of charged particles and precision 
+determination of their trajectories. These measurements allow \Aprime{} decays to be distinguished from background 
+via simultaneous estimation of the invariant mass of \ee{} decay products and the position of decay vertexes 
+downstream of the target.
+
+%Track reconstruction is also important for energy scale calibration of the electromagnetic calorimeter due to the better momentum resolution of tracks compared to clusters in the calorimeter.
+
+%\subsection{SVT Requirements and Constraints}
 %The primary goal was to demonstrate that the technology and design approach 
@@
 $^2$/month, or roughly $3 \times 10^{14}$~\fluenceunit{}/month~\cite{Rashevskaya:2002nd}, as shown in 
-Fig.~\ref{fig:radiation} and~\ref{fig:rates}.
+Fig.~\ref{fig:radiation}.
+% and~\ref{fig:rates}.
 %===================
@@
 %===================
-\begin{figure}[]
-\includegraphics[width=7cm]{figures/rates}
-\label{fig:rates}
-\caption{\small Simulation of the occupancy in the SVT 10~cm downstream of the target as a function of the 
-vertical distance from the beam center.}
-\end{figure}
+%\begin{figure}[]
+%\includegraphics[width=7cm]{figures/rates}
+%\label{fig:rates}
+%\caption{\small Simulation of the occupancy in the SVT 10~cm downstream of the target as a function of the 
+%vertical distance from the beam center.}
+%\end{figure}
 %=================== 
@@
 
-\subsection{SVT Layout}
+\subsection{Layout}
 
 A realistic \geant{}~\cite{Agostinelli2003250} simulation of the detector based on the {\sc SLIC} simulation 
-package~\cite{Graf:2011zzc}
-including all backgrounds has been used to optimize the layout for acceptance, tracking efficiency, mass 
+package~\cite{Graf:2011zzc}, including all backgrounds, has been used to optimize the layout for acceptance, tracking efficiency, mass 
 resolution and prompt vertex rejection. The layout of the SVT is summarized in Tab.~\ref{tab:trk} and rendered in Fig.~\ref{fig:tracker_model}. 
-
-The vertex resolution with an asymmetric beam spot of $\approx200\times40~\mu$m requires hit 
-resolutions better than XXXX (XXXX)~$\mu$m in the vertical (horizontal) measurement coordinate. 
-In addition, the vacuum chamber is too small vertically to accommodate 90-degree stereo layers to optimize 
-the vertex resolution in the horizontal coordinate. Instead, 100~mrad stereo is used in the first three layers 
-to provide higher-resolution 3D space points for vertexing. The 50~mrad stereo of the last two layers 
-breaks the tracking degeneracy of having five identical layers and minimizes fakes from ghost hits, 
-improving pattern recognition while still providing sufficient pointing resolution into the third layer
- for robust hit 
-association in the denser environment there. Altogether, this layout comprises 20 sensors and hybrids and 
-100 APV25 chips for a total of 12780 readout channels. 
+%Vertex resolution with an asymmetric beam spot of $\approx200\times40~\mu$m requires hit resolutions better than XXXX (XXXX)~$\mu$m in the vertical (horizontal) measurement coordinate. 
+%In addition, the vacuum chamber is too small vertically to accommodate 90-degree stereo layers to optimize the vertex resolution in the horizontal coordinate. Instead, 
+100~mrad stereo is used in the first three layers to provide higher-resolution 3D space points for vertexing.
+50~mrad stereo in the last two layers breaks the tracking degeneracy of having five identical layers and minimizes fakes from ghost hits,
+improving pattern recognition while still providing sufficient pointing resolution into the third layer for robust hit association in the denser environment there.
+Altogether, this layout comprises 20 sensors and hybrids and 100 APV25 chips for a total of 12780 readout channels.
 %=======================
@@
 \begin{table}[ht]
-{\small
+{\footnotesize
 \begin{tabular}{lccccc}   
@@
 \hline
-    $z$ from nom. target (cm)  & 10 & 20 & 30 & 50 & 70  \\ 
+    $z$ from target (cm)  & 10 & 20 & 30 & 50 & 70  \\ 
     Stereo angle (mrad)  & 100 & 100 & 100 & 50 & 50 \\ 
@@
 \end{tabular}
-\caption{\small Layout of the HPS Test SVT.. }
+\caption{\small Layout of the HPS Test SVT.}
 }
 \label{tab:trk}
+\vspace*{-15mm}
 \end{table}
@@
 \label{fig:tracker_model}
-\vspace*{-5mm}
+%\vspace*{-5mm}
 \end{figure}
@@
 
-\subsection{SVT Components}
-
-\subsubsection{Silicon Sensors}
+\subsection{Components}
+
+%\subsubsection{Silicon Sensors}
 The sensors for the SVT are selected according to a number of requirements.  First, the sensors must be 
@@
 
-\subsubsection{Front-end Electronics}
+%\subsubsection{Front-end Electronics}
 Because the regions of high occupancy are small spots in two dimensions, only a short length of any one 
@@
 very high and lowering the peak occupancy in the sensors to approximately 1\% for tracking requires a 
-trigger window and tagging of hit times to roughly 8~ns, as shown in Fig.~\ref{fig:rates}.  The FADC 
+trigger window and tagging of hit times to roughly 8~ns.  The FADC 
 readout for the ECal and muon system are capable of this (see Sec.~\ref{sec:fadc}), but achieving 
@@
 
-\subsubsection{Support Structure and Cooling}
+%\subsubsection{Support Structure and Cooling}
 
@@
 
-\subsection{SVT Digitization, Event Building and Data Transmission}
+\subsection{Digitization, Event Building and Data Transmission}
 \label{sec:svt_daq}
@@
 Interconnect (CI) concept developed at SLAC as generic building blocks for DAQ systems in high energy 
-physics . The RCE is a generic computational building block, housed on a separate daughter card 
-called Data Processing Module (DPM), that are realized on an ATCA front board called the Cluster On 
-Board (COB), see Fig.~\ref{fig:cob}.
+physics {\bf [need reference]}. 
+The RCE is a generic computational building block, housed on a separate daughter card called 
+Data Processing Module (DPM), that are realized on an ATCA front board called the Cluster On Board (COB), 
+see Fig.~\ref{fig:cob}.
  \begin{figure}[]
@@
 The Gen-I RCE used in the Test run consisted of a Virtex~5 FPGA with 1~GB of DDR3 RAM. 
-The outputs of 12 SVT half-modules 
-are digitized on the Rear-Transition-Module (RTM), a custom board on the back side of the ATCA crate, 
-interfacing the HPS readout to the generic DAQ components on the COB. 
+The outputs of 12 SVT half-modules are digitized on the Rear-Transition-Module (RTM), a custom board on the back side of the ATCA crate, interfacing the HPS readout to the generic DAQ components on the COB.
 A pre-amplifier converts the APV25 differential current output to a different voltage output scaled to the sensitive 
@@
 
-Hybrid readout boards and half-modules were assembled at SLAC.  Mounting APV25 chips and all 
-wirebonding and QA testing were performed at University of California, Santa Cruz. Of the sensors tested 
-during production, 90\% were capable of 1000~V bias voltage without breakdown. 
-Hybrids underwent quick QA testing and each half-module was run at low 
-temperature ($\approx5^{\circ}$ C) and fully characterized for pedestals, gains, noise and time response 
-after assembly.  All 29 production modules were assembled between mid-February and the end of March, 
-2012.  Module yields were excellent for such a small production.  Of 165 APV chips acquired, 150 were 
-used to assemble 30 production hybrids, of which 29 passed QA testing.  Of 29 half-modules built, 28 passed 
+%Hybrid readout boards and half-modules were assembled at SLAC.  Mounting APV25 chips and all wirebonding and QA testing were performed at University of California, Santa Cruz.
+
+Of the sensors tested during production, 90\% were capable of 1000~V bias voltage without breakdown. 
+Hybrids underwent quick QA testing and each half-module was run at low temperature ($\approx5^{\circ}$ C) and 
+fully characterized for pedestals, gains, noise and time response after assembly.  
+%All 29 production modules were assembled between mid-February and the end of March, 2012.
+Module yields were excellent for such a small production.
+Of 165 APV chips acquired, 150 were used to assemble 30 production hybrids, of which 29 passed QA testing.
+Of 29 half-modules built, 28 passed 
 QA testing, leaving 8 spare modules after completion of the SVT.  Full-module assembly and 
-mechanical surveys were performed at SLAC in early April 2012 before final assembly, testing and 
-shipping of the SVT to JLab on April 11.  A custom shipping container, based on experience 
-from FNAL~\cite{shipping}, was built in order to safely send the partly assembled SVT to JLab. The two fully 
-assembled SVT halves were attached to a baseplate supported by four wire-rope isolators. This plate, 
-covered by a lexan cover for cleanliness, was mounted inside an inner box surrounded by 4 inches of 
-Polyurethane foam to complete the two-spring construction. At JLab, the entire SVT was integrated with the full 
-DAQ and the power supplies for the first time in the clean room, before moving the module-loaded support 
-plates to Hall~B for final mechanical assembly and installation inside of the vacuum chamber on April 19, 2012.
+mechanical surveys were performed at SLAC
+% in early April 2012 
+before final assembly, testing and shipping of the SVT to JLab
+% on April 11.  
+A custom shipping container with nested crates and redundant isolation for shock and vibration 
+%, based on experience from FNAL~\cite{shipping},
+was built in order to safely send the partly assembled SVT to JLab. 
+% The two fully assembled SVT halves were attached to a baseplate supported by four wire-rope isolators.
+This plate, covered by a lexan cover for cleanliness, was mounted inside an inner box surrounded by 4 inches of Polyurethane foam to complete the two-spring construction.
+At JLab, the entire SVT was integrated with the full DAQ and the power supplies 
+%for the first time in the clean room, 
+before moving the module-loaded support plates to Hall~B for final mechanical assembly and installation inside of the 
+vacuum chamber.
+% on April 19, 2012.
 
@@
 The SVT was aligned using a combination of optical, laser and touch probe surveys at SLAC and JLab. The 
-optical survey of individual modules with precision of a few $\mu$m are combined with a touch-prove survey 
+optical survey of individual modules with precision of a few $\mu$m are combined with a touch-probe survey 
 of the overall SVT support structure, with 25-100~$\mu$m precision, to locate the silicon sensor layers with 
@@
 \label{sec:ecal}
-\section{Electromagnetic Calorimeter}
-\label{ecal}
 
@@
 
-\subsection{ECal Components}
+\subsection{Components}
 

### 2013-11-15 author_list_hps_PAC39.tex
Added author list from PAC39 report.

\newcommand{\red[1]}{{\color{red}{\bf #1}}}
\newcommand{\JLAB}{Thomas Jefferson National Accelerator Facility, Newport News, Virginia 23606}
\newcommand{\CUA}{Catholic University of America, Washington, D.C. 20064}
\newcommand{\OU}{Ohio University,  Athens, Ohio 45701}
\newcommand{\YEREVAN}{Yerevan Physics Institute, 375036 Yerevan, Armenia}
\newcommand{\SCAROLINA}{University of South Carolina, Columbia, South Carolina 29208}
\newcommand{\NSU}{Norfolk State University, Norfolk, Virginia 23504}
\newcommand{\ODU}{Old Dominion University, Norfolk, Virginia 23529}
\newcommand{\genova}{Istituto Nazionale di Fisica Nucleare, Sezione di Genova e Dipartimento di Fisica dell\'Universita, 16146 Genova, Italy}
\newcommand{\SACLAY}{CEA, Centre de Saclay, Irfu/Service de Physique Nucl\'eaire 91191 Gif-sur-Yvette, France}
\newcommand{\ORSAY}{Institut de Physique Nucleaire d'Orsay, IN2P3, BP 1, 91406 Orsay, France}
\newcommand{\ECOLE}{CPhT, Ecole Polytechnique, F 91128 PALAISEAU CEDEX, France}
\newcommand{\UCSC}{University of California, Santa Cruz, CA 95064}
\newcommand{\SUNY}{Stony Brook University, Stony Brook, NY 11794-3800}
\newcommand{\FNAL}{Fermi National Accelerator Laboratory, Batavia, IL 60510-5011}
\newcommand{\HUJ}{Hebrew University of Jerusalem, Jerusalem, Israel}
\newcommand{\UNH}{University of New Hampshire, Department of Physics, Durham, NH 03824}
\newcommand{\PERIMETER}{Perimeter Institute, Ontario, Canada N2L 2Y5}
\newcommand{\RPI}{Rensselaer Polytechnic Institute, Department of Physics, Troy, NY 12181}
\newcommand{\SLAC}{SLAC National Accelerator Laboratory, Menlo Park, CA 94025}
\newcommand{\WNM}{The College of William and Mary, Department of Physics, Williamsburg, VA 23185}
\renewcommand*{\thesection}{\arabic{section}}
\newcommand{\Contact}{Contact person}

\begin{document}

\title{\bf\large{Status of the Heavy Photon Search Experiment at Jefferson Laboratory}}
\author{P. Hansson Adrian, C. Field, N. Graf, M. Graham, G. Haller, R. Herbst, J. Jaros\footnote{Co-spokesperson\label{spoks}}, 
T. Maruyama, J. McCormick, K. Moffeit, T. Nelson, H. Neal, A. Odian, M. Oriunno, S. Uemura, D. Walz}
\affiliation{\SLAC}                                 
 \author{A. Grillo, V. Fadeyev, O. Moreno}
\affiliation{\UCSC}
\author{W. Cooper}
\affiliation{\FNAL}
\author{S. Boyarinov, V. Burkert, A. Deur, H. Egiyan, L. Elouadrhiri, A. Freyberger, F.-X. Girod, 
V. Kubarovsky, Y. Sharabian, S. Stepanyan\footref{spoks}, M. Ungaro, B. Wojtsekhowski}
\affiliation{\JLAB}
\author{R. Essig}
\affiliation{\SUNY}
\author{M. Holtrop\footref{spoks}, K. Slifer, S. K. Phillips}
\affiliation{\UNH} 
\author{A. Fradi, B. Guegan, M. Guidal, S. Niccolai, S. Pisano, E. Rauly, P. Rosier and D. Sokhan}
\affiliation{\ORSAY}
\author{P. Schuster, N. Toro}
\affiliation{\PERIMETER}
\author{N. Dashyan, N. Gevorgyan, R. Paremuzyan, H. Voskanyan}
\affiliation{\YEREVAN}
\author{M. Khandaker, C. Salgado}
\affiliation{\NSU}
\author{M. Battaglieri, R. De Vita}
\affiliation{\genova}
\author{S. Bueltmann, L. Weinstein}
\affiliation{\ODU}
\author{G. Ron}
\affiliation{\HUJ}
\author{P. Stoler, A. Kubarovsky}
\affiliation{\RPI}
\author{K. Griffioen}
\affiliation{\WNM}

### 2013-11-15 hps-testrun-nim.tex
Added author list from PAC39 report.

@@
 \newcommand{\moliere}{Moli\`{e}re}
+%\include{affiliations}
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %% use optional labels to link authors explicitly to addresses:
@@
 
-\author[label1]{Per Ledin}
-\ead{contact@hps.discovery.com}
+\input{author_list_hps_PAC39_compact}
+
+%\author[label1]{Per Ledin}
+%\ead{contact@hps.discovery.com}
 %\author[slac]{Per Hansson Adrian\corref{cor1}}
@@
 %\address[slac]{SLAC National Accelerator Laboratory, 94025, Menlo Park, CA, USA}
-\address[label1]{Lule\aa~Hockey}
+%\address[label1]{Lule\aa~Hockey}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
+\clearpage
 \tableofcontents
@@
 hardware. The trigger system receives input from the ECal and distributes a trigger signal 
-to all detector sub- systems to read out a selected event.
+to all detector sub-systems to read out a selected event.
 
@@
 
-The HPS test run trigger system is designed to efficiently select \ee{} events by 
-using information from the ECal . The trigger looks for time coincidences of clusters in the top and bottom half 
-of the ECal.  The trigger system can be broken down into three sections (see Fig.~\ref{fig:hps_trigger_cal}):
+The HPS test run trigger system is designed to select \ee{} events efficiently by 
+using information from the ECal. The trigger looks for time coincidences of clusters in the top and bottom 
+half of the ECal. The trigger system can be broken down into three sections (see 
+Fig.~\ref{fig:hps_trigger_cal}):
  \begin{itemize}
- \item FADC (pulse finding): samples and digitizes the signal pulses from each detector channel. Sends the measured pulse energy and arrival time to the Crate Trigger Processor (CTP),
-\item CTP (cluster finding): groups FADC pulses from each half of the ECal into clusters. The cluster energy and arrival time are sent to the Sub-System Processor (SSP),
- \item SSP (cluster pair finding): searches for time coincidence of pairs of clusters from the top and bottom half of the ECal and applies topological selections.
+ \item FADC (pulse finding): samples and digitizes the signal pulses from each detector channel. 
+Sends the measured pulse energy and arrival time to the Crate Trigger Processor (CTP),
+\item CTP (cluster finding): groups FADC pulses from each half of the ECal into clusters. 
+The cluster energy and arrival time are sent to the Sub-System Processor (SSP),
+ \item SSP (cluster pair finding): searches for time coincidences of pairs of clusters from 
+the top and bottom half of the ECal and applies topological selections.
  \end{itemize}
@@
  \includegraphics[width=8cm]{figures/hps_trigger_cal}
-\caption{Block diagram of the ECAL trigger system consisting of the FADC that samples and digitizes signals for each detector channel and sends them for cluster finding in the CTP.
-The CTP clusters are sent to the SSP where the final trigger decision is taken based on pairs of clusters in both halves of the ECal.
-The decision is sent to the Trigger Supervisor (TS) that generates the necessary signals to readout the sub-detectors.}
+\caption{Block diagram of the ECAL trigger system consisting of the FADC that samples and digitizes 
+signals for each detector channel and sends them for cluster finding in the CTP. The CTP clusters are 
+sent to the SSP where the final trigger decision is taken based on pairs of clusters in both halves of the 
+ECal. The decision is sent to the Trigger Supervisor (TS) that generates the necessary signals to readout 
+the sub-detectors.}
  \label{fig:hps_trigger_cal}
@@
  \end{figure}
-The time coincidence window of pairs of clusters in the top and bottom half of the ECal are programmable 
-with 4~ns resolution.
+The time coincidence window of pairs of clusters in the top and bottom half of the ECal are 
+programmable with 4~ns resolution.
 
@@
 integrates using a "time-over-threshold" window, see Fig. \ref{fig:hps_trigger_data}.
-For the trigger path, every channel has: 
+For triggering purposes, every channel has: 
 \begin{itemize}
@@
  %\item number of samples integrated after the  threshold crossing (NSA),
- \item trigger threshold, measured in ADC counts, 
+ \item a trigger threshold, measured in ADC counts, 
  \item an offset, 
- \item a conversion factor that converts the ADC counts into 5-bits energy in MeV, from $50$ to $\sim1500$~MeV, 
- \item an energy discriminator threshold (minimum energy cutoff).
+ \item a conversion factor to convert ADC counts into energy in MeV, from $50$ to $\sim1500$~MeV, with 5-bit accuracy 
+ \item an energy threshold discriminator to provide aminimum energy cutoff
  \end{itemize}
@@
 The offset is subtracted from ADC samples before they are integrated.  
-The values reported to the CTP are the 5-bit pulse energy and 3-bit time information at which the 
-pulse crossed the threshold. Data for every channel is sent to CTP every 32~ns. With the available 
-3-bit time information, the CTP looks for time coincidence of crystal signals with 8~ns resolution (limit is 4~ns).
-The cluster finding algorithm is fast and makes use of the parallel processing nature of FPGA's by 
-simultaneously searching for 125 clusters, up to 3x3 in size, across the calorimeter crystal array and performs 
-the following tasks:
+The values reported to the CTP are the 5-bit pulse energy and the 3-bit time at which the 
+pulse crossed the threshold. Data from every channel is sent to the CTP every 32~ns. With the available 
+3-bit time information, the CTP looks for time coincidences of crystal signals within an 8~ns window (the 
+limit is 4~ns).
+The cluster finding algorithm is fast and makes use of the parallel processing capability of the FPGA's by 
+simultaneously searching for 125 clusters, up to 3x3 in size, across the calorimeter crystal array, and it 
+performs the following tasks:
 \begin{itemize}
-\item Adds energy from hits together for every 3x3 square of channels in ECal.
-\item Hits are added together if they occur (leading edge) within a programmable number of 4~ns clock cycles of each other (HPS test run used 8~ns coincidence time interval).
-\item If the 3x3 energy sum is larger than the programmable cluster energy threshold and the sum is greater than any neighboring 3x3 windows, the CTP reports the cluster parameters to the SSP. 
+\item Adds together the energy for every 3x3 square of channels in the ECal
+\item Hits are added together if their leading edges occurred within a programmable number of 4~ns 
+clock cycles  (HPS test run used 8~ns coincidence time interval).
+\item If the 3x3 energy sum is larger than the programmable cluster energy threshold and the sum is 
+greater than any neighboring 3x3 windows, the CTP reports the cluster parameters to the SSP. 
 \end{itemize}
-The CTP evaluates all hits in its half of the calorimeter every 4~ns. A programmable time window is used to 
-allow hits that are out of time with each other to be considered as part of a cluster sum. This is done by 
-reporting hits when they occur and then reporting them again for the next $N$ number of 4~ns clock cycles, 
-where $N \in [0,7]$. This is useful to deal with skew and jitter that develop from the detector, cabling, and 
-electronics. As described above, the CTP only selects the 3x3 window with the highest energy sum of its 
-neighbors. This filtering is applied to deal with overlapping clusters and cases where the cluster is larger than 
-a 3x3 window.
-
- The final trigger decision is made by CTPs and SSP passed to the Trigger Supervisor (TS). The TS generates all necessary signals and controls the entire DAQ 
-system readout through the Trigger Interface (TI) units. The TI units are installed in every crate that participate 
-in the readout process.
-
-The trigger system is free-running and driven by the 250~MHz global clock and has essentially zero dead 
-time at occupancies expected by HPS. The Trigger Supervisor can apply dead time if necessary, for example 
-on a `busy' or `full' condition from front-end electronics. The system is designed to handle trigger rates above 
-50~kHz and a latency set to $\approx 3~\mu$s to match that required by the SVT APV25 chip.
-
-During the test run, for the most part trigger system run in single cluster mode and was tested to work for up to 20 kHz trigger rates.
+The CTP evaluates all the hits in its half of the calorimeter every 4~ns. A programmable time window is 
+used to allow hits that are slightly out of time with each other to be considered as part of a cluster sum. 
+This is done by reporting hits when they occur and then reporting them again for the next $N$ number of 
+4~ns clock cycles, where $N \in [0,7]$. This is useful to deal with skew and jitter that develop from the 
+detector, cabling, and electronics. As described above, the CTP only selects the 3x3 window with the 
+highest energy sum of its neighbors. This filtering is applied to deal with overlapping clusters and cases 
+where the cluster is larger than a 3x3 window.
+
+The final trigger decision is made by CTPs and the SSP is passed to the Trigger Supervisor (TS). The TS 
+generates all necessary signals and controls the entire DAQ system readout through the Trigger 
+Interface (TI) units. The TI units are installed in every crate that participate in the readout process.
+
+The trigger system is free-running and driven by the 250~MHz global clock and has essentially zero 
+dead time at the occupancies expected for HPS. The Trigger Supervisor can apply dead time if 
+necessary, for example on a `busy' or `full' condition from the front-end electronics. The system is 
+designed to handle trigger rates above 50~kHz and has a latency set to $\approx 3~\mu$s to match that 
+required by the SVT APV25 chip.
+
+During the test run, for the most part the trigger system required only a single cluster in either the top or 
+bottom Ecal module. It was tested to work up to 20 kHz trigger rates.
 
@@
 For the ECal, every VXS crate contains a Readout Controller (ROC)
-that collects digitized information, processes it, and sends it on to the Event Builder (EB). The ROC is a single 
-blade Intel-based CPU module running DAQ software under CentOS Linux OS. For the SVT ATCA system, 
-the ROC application runs on an embedded processor situated on the ATCA main board. The EB assembles 
-information from the SVT and ECal ROCs into a single event which is passed to the Event 
-Recorder (ER) that writes it to a RAID5-based data storage system capable of handling up to 100 MB/s. The 
-EB and other critical components run on multicore Intel-based multi-CPU servers. The DAQ network system is 
-a Foundry router providing high-speed connections between the DAQ components and to the JLab 
-computing facility. The SVT ROC, which must handle large data volumes, has a 10 Gbit/s link to the Foundry 
-router, while a 1 Gbit/s link is adequate for the ECal. A 10 Gbit/s uplink to the JLab 
-computing facility is used for long-term storage.
-
-The SVT DAQ is described in more details in Sec.~\ref{sec:svt_daq}.
+that collects digitized information, processes it, and sends it on to the Event Builder (EB). The ROC is a 
+single blade Intel-based CPU module running DAQ software under CentOS Linux OS. For the SVT 
+ATCA system, the ROC application runs on an embedded processor situated on the ATCA main board. 
+The EB assembles information from the SVT and ECal ROCs into a single event which is passed to the 
+Event Recorder (ER) that writes it to a RAID5-based data storage system capable of handling up to 
+100~MB/s. The EB and other critical components run on multicore Intel-based multi-CPU servers. The 
+DAQ network system is a Foundry router providing high-speed connections between the DAQ 
+components and the JLab computing facility. The SVT ROC, which must handle large data volumes, has 
+a 10~Gbit/s link to the Foundry router, while a 1~Gbit/s link is adequate for the ECal. A 10~Gbit/s uplink 
+to the JLab computing facility is used for long-term storage.
+
+The SVT DAQ is described in more detail in Sec.~\ref{sec:svt_daq}.
 

### 2013-11-15 hps-testrun-nim.tex
Removed brand name of router to be consistent.

@@
 100~MB/s. The EB and other critical components run on multicore Intel-based multi-CPU servers. The 
-DAQ network system is a Foundry router providing high-speed connections between the DAQ 
+DAQ network system is a network router providing high-speed connections between the DAQ 
 components and the JLab computing facility. The SVT ROC, which must handle large data volumes, has 
-a 10~Gbit/s link to the Foundry router, while a 1~Gbit/s link is adequate for the ECal. A 10~Gbit/s uplink 
+a 10~Gbit/s link to the network router, while a 1~Gbit/s link is adequate for the ECal. A 10~Gbit/s uplink 
 to the JLab computing facility is used for long-term storage.

### 2013-11-16 hps-testrun-nim.tex
Added empty acknowledgement section.
Added new t0 figure. Added new pulse shape figure. Added description of t0 resolution stats. Changed discussion of SVT S/N and absolute calibration slightly. Added EoverP for data and MC. Updated the Ecal calibration paragraph slightly. Removed the Ecal EoverP 2D map.

@@
 
-The photon beam was generated in the interaction of the $5.5$ GeV electrons with a gold radiator of 
+The photon beam was generated in the interaction of the $5.5$~GeV electrons with a gold radiator of 
 $10^{-4}~X_0$, located $\approx~9$~m upstream of the PS. The primary beam and scattered 
@@
 sensors were operated within a temperature range of  $20-24^\circ$C 
-throughout the test run. Multiple calibration runs, normalized with lab-based radioactive source tests, 
-established a noise level of $\approx$ XXXX-XXXX electrons which was stable across all the SVT modules.
-
-Throughout the duration of the test run, approximately 97\% of the 12,780 SVT channels were found to be 
-operating normally. The fraction of dead or noisy channels varied from 2.4\% to 4.7\%.  
+throughout the test run. 
+Throughout the duration of the test run, approximately 97\% of the 12,780 SVT channels were found to
+be operating normally. The fraction of dead or noisy channels varied from 2.4\% to 4.7\%.  
 Most of these were due to misconfigured readout chips (2--4 misconfigured chips out of 100 ), 
@@
 
-After a trigger is received, six samples of the corresponding output of the APV25 shaper circuit are digitized. 
-The samples from every channel on a sensor surviving the 
+After a trigger is received, six samples of the corresponding output of the APV25 shaper circuit are digitized. The samples from every channel on a sensor surviving the 
 data reduction algorithm (see Sec.~\ref{sec:svt_daq}) are the basis for offline hit reconstruction. 
@@
 {\small
-	\includegraphics[width=6cm]{figures/08062012_run1351_samples_vs_amplitude}
+	\includegraphics[width=6cm]{figures/run1351_110513_samples_L1_top.pdf}
 	\caption{The six pedestal subtracted samples from individual channels associated with a hit on a 
@@
 the characteristic Landau shape as expected, see Fig.~\ref{fig:cluster_pulse}.  
-The signal to noise ratio is XXXX.
+A noise level between $1.1-1.5\times 10^{3}$ electrons was established through multiple calibration 
+runs giving a signal to noise ratio of $21-25$. Lab-based radioactive source tests was used to 
+provide the absolute charge normalization.
 \begin{figure}[h]
@@
 After clustering hits on a sensor, the hit time for each cluster is computed as the amplitude-weighted 
-average of the fitted $t_0$ channel times. The $t_0$-resolution is studied by comparing the cluster hit time 
-with the average of all cluster hit times on the track, the ``track time'', which has the expected jitter due to clock 
-phase and trigger, approximately 25~ns. Figure~\ref{fig:tracktime} shows the residual to the individual cluster 
+average of the fitted $t_0$ channel times. The $t_0$-resolution is studied by comparing the cluster hit 
+time with the average of all cluster hit times on the track, the ``track time'', which has the expected jitter 
+due to clock phase and trigger, approximately 25~ns. Figure~\ref{fig:tracktime} shows the residual to the individual cluster 
 times. 
@@
 {\small
-%	\includegraphics[width=7cm]{figures/top_track_time.pdf}
-	\includegraphics[width=6cm]{figures/t0_resolution.pdf}
+	\includegraphics[width=6cm]{figures/t0_resolution_run1351_110513.pdf}
 	\caption{
-%	Track time distribution (left) and cluster time residual (right).
-The track time is measured relative to the APV25 clock.
-The width of the distribution is due to trigger jitter (24~ns jitter in the tracker readout clock, plus 16~ns jitter in the trigger system).
-	The cluster time residual is for a representative sensor relative to the track time.}
+	The cluster time residual for a representative sensor relative to the track time (see text for more 
+	details). \color{red}{\bf Fix axis.} }
 	\label{fig:tracktime}
@@
 \end{figure}
-After correcting for offsets from each sensor (time-of-flight, clock phase) the extracted $t_0$ resolution is 
-2.6~ns. This is somewhat worse than the approximately 2~ns resolution expected which we attribute to the true 
+After correcting for offsets from each sensor (time-of-flight, clock phase) and accounting for the 
+correlation between the $t_0$ and track time,  the extracted $t_0$ resolution is 2.6~ns. This is somewhat 
+worse than the approximately 2~ns resolution expected which we attribute to the true 
 pulse shape differing from our idealized fit function which will be improved in the future. Reducing the 
-APV25 pulse shaping time will also improve time resolution. These results show that we can operate with 
-the six sample readout mode of the APV25 chip and achieve time resolution adequate for pileup 
+APV25 pulse shaping time will also improve time resolution. These results show that we can operate 
+with the six sample readout mode of the APV25 chip and achieve time resolution adequate for pileup 
 rejection during electron running in the HPS experiment.
@@
 While occupancy was slightly larger than expected, good agreement between data and simulation was 
-found after taking into account dead or noisy channels. The hit efficiency, see Fig.~\ref{fig:hit_efficiency}, 
-was measured to be above 98\% and fairly uniform across the SVT.
+found after taking into account dead or noisy channels. The hit efficiency was estimated by measuring 
+the number of good tracks with a hit close to the extrapolated intersection of a given sensor that was 
+excluded from the track fit itself. Tracks which intersect regions with known bad channels or very close to 
+in the edge region are excluded in the calculation of the single hit efficiency. The hit efficiency, see 
+Fig.~\ref{fig:hit_efficiency}, was measured to be above 98\% and fairly uniform across the SVT.
 \begin{figure}[h]
@@
 \end{center}
-While the tails of the vertex distribution expected in electron beam running is not accessible here the 
-fact that the core is relatively well described provides confidence of the description of the amount of 
-material and the model used for simulating multiple scattering in the target.  
-These are crucial for benchmarking the HPS \Aprime{} physics reach since both the mass and vertex resolution 
-that determine the sensitivity are limited by multiple scattering.
+%While the tails of the vertex distribution expected in electron beam running is not accessible here the 
+%fact that the core is relatively well described provides confidence of the description of the amount of 
+%material and the model used for simulating multiple scattering in the target.  
+%These are crucial for benchmarking the HPS \Aprime{} physics reach since both the mass and vertex 
+%resolution that determine the sensitivity are limited by multiple scattering.
 
@@
 
-The gain of the individual ECal channels has been calibrated using the SVT measurement of track momentum and comparison to Monte Carlo simulation.
-The integrated pulse of the each channel was converted to energy by first subtracting the pedestal then applying a gain or conversion factor to convert ADC counts to energy in MeV.
-The pedestals have been measured using special runs where FADCs sampled APD signals every 4~ns and for each trigger a time window of 100 samples have been recorded.
-Pedestal levels were determined by looking at a part of the
-window before the actual hit. Modules above a threshold are clustered using a simple algorithm described in Sec.~\ref{sec:trigger}. The ECal was operated 
-with an effective readout threshold of 73~MeV. The noise level of the ECal modules were measured to be approximately 15~MeV.
-
-To compare data and simulation, all inoperable or noisy channels in SVT and ECal have been disabled in the simulation, so any efficiency or bias effects that affect the real data should be reflected 
-in the simulation as well. Using a formula to compute the ``weighted E/p'' for a crystal, representing the average E/p for clusters that include the crystal
-% $\frac{\sum_j w_{j,i}}{\sum_j\frac{P_j}{E_j}w_{j,i}}$
-, and iteratively adjust the gains until the weighted E/p is equal for test run data and simulation.
+The integrated pulse of the each channel was converted to energy by first 
+subtracting the pedestal then applying a gain or conversion factor to convert ADC counts to energy. 
+The pedestals was measured in special runs where a 100 samples long window was recorded for each 
+trigger in which the FADCs sampled the APD signals every 4~ns.  The pedestals were extracted from the 
+part of the window before the actual hit in the calorimeter. Modules above a threshold are clustered 
+using a simple algorithm described in Sec.~\ref{sec:trigger}. The ECal was operated with an effective 
+crystal readout threshold of 73~MeV. The noise level of the ECal modules were measured to be approximately 15~MeV.
+
+To compare data and simulation, all inoperable or noisy channels in SVT and ECal have been disabled 
+in the simulation; any efficiency or bias effects that affect the real data should be reflected 
+in the simulation. Furthermore, a gain calibration is performed to equalize the gains in the 
+simulation to those observed in data by comparing the ECal cluster energy $E$ to the momentum $p$ of 
+matched tracks in the SVT.  The ``weighted $E/p$'' for each crystal is computed, representing the 
+average $E/p$ for clusters that include the crystal
+% $\frac{\sum_j w_{j,i}}{\sum_j\frac{P_j}{E_j}w_{j,i}}$.
+Iteratively, gains are adjusted until the weighted $E/p$ is similar in data and simulation. The $E/p$ 
+in data and simulation can be seen in Fig.~\ref{fig:gains}.
 \begin{figure}[]
@@
 {\small
-	\includegraphics[width=7cm]{figures/eoverp_simulation}
-	\caption{Weighted E/p from Monte Carlo simulation after gain calibration.}
+	\includegraphics[width=7cm]{figures/eoverp_MC_egs_0_016x0_June5_2013_Sho_Ecal_presentation.png}
+	\includegraphics[width=7cm]{figures/eoverp_data_run1351_June5_2013_Sho_Ecal_presentation.png}
+	\caption{The ECal energy over track momentum ratio for simulation (top) and data (bottom).\color{red}{\bf (Update style.)}} 
 	\label{fig:gains}
@@
 \end{figure}
-
-These gains can then be used to convert from ADC counts in a channel to the energy deposited into that ECal 
-crystal.
-The other information needed to find the energy of an incident particle is the sampling fraction---the ratio of 
-energy read out from cluster to energy of an incident particle. The conventional sampling fraction, 
-the fraction of incident energy that is deposited in the cluster, is approximately 0.9  for the ECal (somewhat less at the 
-edges). For our readout, there is additional energy lost because crystals under the threshold are not 
-read out.
-The weighted E/p used in calibration (see Figure \ref{fig:gains}) is an approximate measurement of sampling fraction, but the sampling fraction is energy-dependent because of the effect of readout threshold.
-A full computation of sampling fraction can be done using simulation.
+These gains can then be used to convert from the ADC counts reported by the FADC in each channels 
+to the energy deposited in the crystals. In order to find the energy of the incident particle one also needs 
+to know the  the fraction of incident energy that is deposited in the cluster or "sampling fraction". 
+The sampling fraction is parameterized from simulation that show that it is approximately 0.9 for the 
+ECal. The weighted $E/p$ shown in Fig.~\ref{fig:gains} is an approximate measurement of the sampling 
+fraction of that part of the ECal but is position- (somewhat smaller at the edges) and energy-dependent 
+because of the high readout thresholds (explaining the low value compared to 0.9). Since the 
+sampling fraction is not needed to normalize event rates it was not applied in the multiple scattering 
+analysis in Sec.~\ref{sec:mcs}.
 
 %\subsubsection{Trigger Performance}
-As discussed above, the trigger and DAQ integrate pulses differently to measure hit energy. The trigger 
-integrates using a time-over-threshold window, and the DAQ readout integrates using a constant window 
-(5 samples before and 30 samples after a threshold crossing). For every event, the trigger reports the 
-trigger decision as a bit mask (top trigger, bottom trigger, or both) and the time the trigger fires.
-
-We study trigger performance by simulating the trigger for each event and comparing to how events were 
-actually triggered.
-First, we simulate the FADC readout board to convert from readout hits (constant integration window) to 
-trigger hits (time-over-threshold integration). We then simulate the CTP clustering algorithm and the trigger 
-decision before we compare the trigger decision and trigger time reported by the simulation to what was 
-reported by the real trigger.
-
-To eliminate trigger bias in checking the trigger decision, we use a tag and probe method. To check trigger 
-performance in one half of the ECal, we tag events where there was a trigger in the other half, and exactly one 
-probe cluster in the ECal half under test. 
-We then measure trigger efficiency (proportion of tagged events where there was a trigger) as a function of 
-ADC counts and energy of the probe cluster.
-These turn-on curves are shown for the top half of the ECal in Fig.~\ref{fig:turnon}.
-
+The trigger and DAQ integrate pulses from the ECal modules differently to measure the energy 
+deposited in the each crystal. The trigger integrates the pulse using a time-over-threshold window, and 
+the DAQ readout integrates using a fixed-size window (5 samples before and 30 samples after a 
+threshold crossing). For every event, the trigger reports the trigger decision as a bit mask (top half, 
+bottom half or both) and the time the trigger fired. The trigger performance was studied by simulating the 
+trigger for each event and comparing to how the events were actually triggered.
+First, we simulate the FADC readout board to convert from readout hits (with fixed-size window 
+integration) to trigger hits (time-over-threshold integration). Secondly, the CTP clustering 
+algorithm and the trigger decision is simulated before we compare the trigger decision and trigger time 
+to what was reported by the actual trigger. To eliminate trigger bias, we use a tag and probe method. To 
+study the trigger performance in one half of the ECal, we select events which triggered the other half 
+and where there was exactly one probe cluster in the ECal half under study. We then measure trigger 
+efficiency as the fraction of tagged events that fired the trigger in the probe half as a function of the 
+probe cluster energy, shown in Fig.~\ref{fig:turnon}. As a cross-check, the turn-on from the trigger 
+threshold was measured to be 1280 in units of ADC counts as expected. The threshold was not 
+perfectly sharp because of uncertainties in the conversion from readout to trigger hits described above, 
+but based on comparisons with simulation we believe the trigger worked exactly as specified.
 \begin{figure}[ht]
@@
 {\small
-	\includegraphics[width=7cm]{figures/top_turn_on__bottom_tag}
 	\includegraphics[width=7cm]{figures/top_turn_on__bottom_tag_E}
-	\caption{Trigger turn-on as a function of probe cluster ADC counts (top) and probe cluster energy in MeV
-	(bottom). Both plots are for the top half of the ECal; bottom is similar. Energy is not corrected for sampling 
-	fraction.}
+	\caption{Trigger turn-on in the top half of the ECal (bottom is similar) for data and simulation as a 
+	function of probe cluster energy.}
 \label{fig:turnon}
@@
 \end{figure}
-The trigger threshold is seen to be 1280 ADC counts as expected. The threshold is not perfectly sharp in this 
-analysis because of uncertainties in the conversion from readout to trigger hits but based on comparisons 
-with Monte Carlo simulation we believe the trigger worked exactly as specified. 
-The trigger threshold in terms of cluster energy is very uneven for two reasons; gain variations between 
-different ECal crystals lead to threshold variations and the nonlinearity of the time-over-threshold integral 
-means that the effective threshold is higher for clusters that span multiple crystals.
-Overall the trigger appears to have functioned exactly as intended. Changes planned for the next run 
-(constant integration window and per-crystal gain calibration constants for the trigger) will solve both of the 
-issues that led to threshold variations in the test run.
+The trigger turn-on is slow and reaches an uneven plateau just below one for two reasons.  Gain 
+variations between different crystals lead to threshold variations and the nonlinearity of the 
+time-over-threshold integral means that the effective threshold is higher for clusters that span multiple 
+crystals. The effective trigger threshold is therefore dependent on position and energy of the particle 
+as well as cluster multiplicity. Overall the trigger appears to have functioned exactly as intended. 
+Changes planned for physics running (constant integration window and per-crystal gain calibration 
+constants for the trigger) will solve both of the issues that led to threshold variations in the Test run.
 
@@
 \section{Multiple Coulomb Scattering Distributions}
-
+\label{sec:mcs}
 Occupancies close to the beam create many of the key challenges in the HPS experiment
@@
 Converter thickness & Duration &  $e^-$ on converter \\
- (\%$X_0$) & (s) & (nC)    \\   
+ (\%$X_0$) & (s) & ($\mu$C)    \\   
 \hline
 %\hline
-1.6   & 911 &     24385.9     \\ %27 nA
+1.6   & 911 &   24.4 \\ %24385.9     \\ %27 nA
 %\hline
-0.18   & 2640 &    193508.9  \\  %73 nA
+0.18   & 2640 &   193.5 \\ % 193508.9  \\  %73 nA
 %\hline
-0.45  & 2149 &       140709.9  \\ %65.5 nA
+0.45  & 2149 &     140.7 \\ %  140709.9  \\ %65.5 nA
 %\hline
-0    & 1279  &   88079.6  \\
+0    & 1279  &   88.1 \\ %88079.6  \\
 \hline
@@
 
+\section{Acknowledgements}
+
 %% The Appendices part is started with the command \appendix;

### 2013-11-19 hps-testrun-nim.tex
Updating SVT hit efficiency plot.

@@
 {\small
-    	\includegraphics[width=7cmh]{figures/hit_efficiency_vs_layer.pdf}
+    	\includegraphics[width=7cmh]{figures/single_hit_efficiency_Omar_11192013.pdf}
         \caption{ The hit reconstruction efficiency as a function of detector layer.}
@@
 \end{figure}
-The spatial resolution of similar microstrip sensors is well established by test beam data, against which the 
-charge deposition model in the simulation is validated.  This resolution can be parameterized as a 
+The spatial resolution of similar microstrip sensors is well established by test beam data, against which 
+the charge deposition model in the simulation is validated.  This resolution can be parameterized as a 
 function of the total signal to single-strip noise (S/N) and the crossing angle of tracks through the sensor.  
-The single-hit resolution for charged particles with signal to noise ration above 20, as demonstrated here, 
-is relatively constant at approximately 6~$\mu$m for tracks that are close to normal to the sensors as in HPS.
+The single-hit resolution for charged particles with signal to noise ratio above 20, as demonstrated 
+here, is relatively constant at approximately 6~$\mu$m for tracks that enters approximately normal to the 
+sensors as in HPS.
 

### 2013-11-19 hps-testrun-nim.tex
Stepans edits of ECal perf and trigger perf

@@
 
-\subsection{ECal and Trigger Performance}
+\subsection{ECal Performance}
 \label{sec:ecal_calibration}
@@
 The integrated pulse of the each channel was converted to energy by first 
-subtracting the pedestal then applying a gain or conversion factor to convert ADC counts to energy. 
-The pedestals was measured in special runs where a 100 samples long window was recorded for each 
-trigger in which the FADCs sampled the APD signals every 4~ns.  The pedestals were extracted from the 
-part of the window before the actual hit in the calorimeter. Modules above a threshold are clustered 
-using a simple algorithm described in Sec.~\ref{sec:trigger}. The ECal was operated with an effective 
-crystal readout threshold of 73~MeV. The noise level of the ECal modules were measured to be approximately 15~MeV.
-
+subtracting the pedestal then applying a conversion factor to convert ADC counts to energy. 
+The pedestals are measured using special runs where a 100 samples of APD signals, $4$ ns a part, have been recorded at each trigger.  The pedestals were extracted from the 
+part of the $400$ ns window before the actual hit in the calorimeter. After subtracting the pedestal, modules with integrated pulse above a threshold are clustered 
+using a simple algorithm similar to the one deployed for the trigger, see Sec.~\ref{sec:trigger}.
+Due to a high readout threshold of $73$~MeV, the average number of modules in a cluster was $\sim 3$ and the simple clustering algorithm worked well for reconstruction of detected shower energy.
+From pedestal runs the average noise level of the ECal modules were measured to be approximately 15~MeV.
+
+In order to determine conversion factors from ADC counts to energy, the ratios the ECal cluster energy $E$ to the momentum $p$ of  matched tracks in the SVT have been studied in the data and simulation.
 To compare data and simulation, all inoperable or noisy channels in SVT and ECal have been disabled
-in the simulation; any efficiency or bias effects that affect the real data should be reflected 
-in the simulation. Furthermore, a gain calibration is performed to equalize the gains in the 
-simulation to those observed in data by comparing the ECal cluster energy $E$ to the momentum $p$ of 
-matched tracks in the SVT.  The ``weighted $E/p$'' for each crystal is computed, representing the 
-average $E/p$ for clusters that include the crystal
+in both data and the simulation. Any efficiency or bias effects that affect the real data should be reflected 
+in the simulation. 
+%Furthermore, a conversion factor calibration is performed to equalize the gains of  each channel.
+simulation to those observed in data by comparing .
+The ``weighted $E/p$'' for each crystal is computed, representing the average $E/p$ for clusters that include the crystal
 % $\frac{\sum_j w_{j,i}}{\sum_j\frac{P_j}{E_j}w_{j,i}}$.
-Iteratively, gains are adjusted until the weighted $E/p$ is similar in data and simulation. The $E/p$ 
-in data and simulation can be seen in Fig.~\ref{fig:gains}.
+Iteratively, conversion coefficients have been adjusted until the $E/p$ ratios in the data became similar to the  ones in simulation.
+The distribution of the $E/p$ ratio in data and simulation can be seen in Fig.~\ref{fig:gains}.
+The peak position of the distribution shows the sampling fraction of the ECal, the fraction of the incident energy detected in the cluster.
+The width and tails of the distribution in data indicates imperfect calibration and noise of ECal modules.
+This level of calibration and the agreement with simulation was found to be sufficient for the multiple scattering analysis using normalized event rates, see Sec.~\ref{sec:mcs}.
 \begin{figure}[]
@@
 \end{figure}
-These gains can then be used to convert from the ADC counts reported by the FADC in each channels 
-to the energy deposited in the crystals. In order to find the energy of the incident particle one also needs 
-to know the  the fraction of incident energy that is deposited in the cluster or "sampling fraction". 
-The sampling fraction is parameterized from simulation that show that it is approximately 0.9 for the 
-ECal. The weighted $E/p$ shown in Fig.~\ref{fig:gains} is an approximate measurement of the sampling 
-fraction of that part of the ECal but is position- (somewhat smaller at the edges) and energy-dependent 
-because of the high readout thresholds (explaining the low value compared to 0.9). Since the 
-sampling fraction is not needed to normalize event rates it was not applied in the multiple scattering 
-analysis in Sec.~\ref{sec:mcs}.
-
-%\subsubsection{Trigger Performance}
+%These gains can then be used to convert from the ADC counts reported by the FADC in each channels to the energy deposited in the crystals.
+In order to find the energy of the incident particle one also needs to know the  the fraction of incident energy that is deposited in the cluster or "sampling fraction".
+%The sampling fraction is parameterized from simulation that show that it is approximately 0.9 for the ECal.
+The weighted $E/p$ shown in Fig.~\ref{fig:gains} is an approximate measurement of the sampling fraction of that part of the ECal but is position- (somewhat smaller at the edges) and energy-dependent because of the high readout thresholds (explaining the low value compared to 0.9).
+Since the sampling fraction is not needed to normalize event rates it was not applied in the multiple scattering analysis in Sec.~\ref{sec:mcs}.
+
+\subsubsection{Trigger Performance}
 The trigger and DAQ integrate pulses from the ECal modules differently to measure the energy 
@@
 perfectly sharp because of uncertainties in the conversion from readout to trigger hits described above, 
-but based on comparisons with simulation we believe the trigger worked exactly as specified.
+but based on comparisons with simulation we found that the trigger worked exactly as specified.
 \begin{figure}[ht]
@@
 \end{figure}
-The trigger turn-on is slow and reaches an uneven plateau just below one for two reasons.  Gain 
-variations between different crystals lead to threshold variations and the nonlinearity of the 
+The trigger turn-on is slow and reaches an uneven plateau just below $1$ GeV for two reasons;  gain 
+variations between different crystals lead to the threshold variations and the nonlinearity of the 
 time-over-threshold integral means that the effective threshold is higher for clusters that span multiple 
 crystals. The effective trigger threshold is therefore dependent on position and energy of the particle 
-as well as cluster multiplicity. Overall the trigger appears to have functioned exactly as intended. 
-Changes planned for physics running (constant integration window and per-crystal gain calibration 
-constants for the trigger) will solve both of the issues that led to threshold variations in the Test run.
+as well as cluster multiplicity. 
+%Overall the trigger appears to have functioned exactly as intended. 
+%Changes planned for physics running (constant integration window and per-crystal gain calibration 
+%constants for the trigger) will solve both of the issues that led to threshold variations in the Test run.
 

### 2013-11-19 hps-testrun-nim.tex
Small rearrangements and edits of ECal perf and trigger perf

@@
 The integrated pulse of the each channel was converted to energy by first 
-subtracting the pedestal then applying a conversion factor to convert ADC counts to energy. 
-The pedestals are measured using special runs where a 100 samples of APD signals, $4$ ns a part, have been recorded at each trigger.  The pedestals were extracted from the 
-part of the $400$ ns window before the actual hit in the calorimeter. After subtracting the pedestal, modules with integrated pulse above a threshold are clustered 
-using a simple algorithm similar to the one deployed for the trigger, see Sec.~\ref{sec:trigger}.
-Due to a high readout threshold of $73$~MeV, the average number of modules in a cluster was $\sim 3$ and the simple clustering algorithm worked well for reconstruction of detected shower energy.
-From pedestal runs the average noise level of the ECal modules were measured to be approximately 15~MeV.
-
-In order to determine conversion factors from ADC counts to energy, the ratios the ECal cluster energy $E$ to the momentum $p$ of  matched tracks in the SVT have been studied in the data and simulation.
-To compare data and simulation, all inoperable or noisy channels in SVT and ECal have been disabled
-in both data and the simulation. Any efficiency or bias effects that affect the real data should be reflected 
-in the simulation. 
+subtracting the pedestal and then applying a conversion factor to convert ADC counts to energy. 
+The pedestals are measured using special runs where each trigger records 100 samples of signals from 
+the APDs with 4~ns between each sample. The pedestals were extracted from the 
+part of the window before the actual hit in the calorimeter. After subtracting the pedestal, modules with 
+integrated pulse above a threshold are clustered using a simple algorithm similar to the one deployed 
+for the trigger (see Sec.~\ref{sec:trigger}). Due to the high effective readout threshold of $73$~MeV the 
+average number of modules in a cluster was $\sim 3$ and the simple clustering algorithm worked well 
+for reconstruction of the detected shower energy. An average noise level of approximately 15~MeV 
+was measured in special pedestal runs.
+
+The ratio of the ECal cluster energy $E$ to the momentum $p$ of a matched track in the SVT was used 
+to determine the conversion factors from ADC counts to energy. To compare data and simulation, all 
+inoperable or noisy channels in the SVT and ECal was disabled in both data and simulation; any 
+efficiency or bias that affect the data should be reflected in the simulation. 
 %Furthermore, a conversion factor calibration is performed to equalize the gains of  each channel.
 simulation to those observed in data by comparing .
-The ``weighted $E/p$'' for each crystal is computed, representing the average $E/p$ for clusters that include the crystal
+The ``weighted $E/p$'' for each crystal is computed,
+representing the average $E/p$ for clusters that include the crystal
 % $\frac{\sum_j w_{j,i}}{\sum_j\frac{P_j}{E_j}w_{j,i}}$.
-Iteratively, conversion coefficients have been adjusted until the $E/p$ ratios in the data became similar to the  ones in simulation.
-The distribution of the $E/p$ ratio in data and simulation can be seen in Fig.~\ref{fig:gains}.
-The peak position of the distribution shows the sampling fraction of the ECal, the fraction of the incident energy detected in the cluster.
-The width and tails of the distribution in data indicates imperfect calibration and noise of ECal modules.
-This level of calibration and the agreement with simulation was found to be sufficient for the multiple scattering analysis using normalized event rates, see Sec.~\ref{sec:mcs}.
+Iteratively, conversion coefficients for each module is adjusted until the $E/p$ ratio in data and 
+simulation are similar. The distribution of the $E/p$ ratio in data and simulation can be seen in 
+Fig.~\ref{fig:gains}. 
 \begin{figure}[]
@@
 \end{figure}
+The peak position of the distribution indicates the sampling fraction of the ECal, 
+the fraction of the incident particle energy measured in the cluster. The width and tails of the distribution 
+in data indicates imperfect calibration and noise of the ECal modules. This level of calibration and the 
+agreement with simulation was found to be sufficient for the multiple scattering analysis using 
+normalized event rates described in Sec.~\ref{sec:mcs}.
+
 %These gains can then be used to convert from the ADC counts reported by the FADC in each channels to the energy deposited in the crystals.
@@
 
-\subsubsection{Trigger Performance}
+\subsection{Trigger Performance}
 The trigger and DAQ integrate pulses from the ECal modules differently to measure the energy 

### 2013-11-19 hps-testrun-nim.tex
Adding text on momentum resolution and scale

@@
 
-By selecting \ee{} pairs from the triggered events we are able to study basic distributions of pair production 
-kinematics and in particular those related to our vertex performance. Pairs of opposite charge tracks, one in the 
-top and one in the bottom half of the SVT, with momentum larger than 400~MeV were selected. 
-The pair production 
-kinematics are relatively well reproduced given the alignment of the tracker; Fig.~\ref{fig:pair_kin} shows the 
-invariant mass and ratio of electron momentum over the sum of electron and positron. 
+By selecting \ee{} pairs from the triggered events we are able to study basic distributions of pair 
+production kinematics and in particular those related to our vertex performance. Pairs of opposite charge 
+tracks, one in the top and one in the bottom half of the SVT, with momentum larger than 400~MeV were 
+selected. The pair production kinematics are relatively well reproduced given the alignment of the 
+tracker; Fig.~\ref{fig:pair_kin} shows the invariant mass and ratio of electron momentum over the sum of 
+electron and positron. 
  \begin{center}
@@
    \includegraphics[width=5cm]{figures/h_sumE_h_sumE_trigsel4hit_pair1351_twotrkfilt-v6-paper}
-%   \includegraphics[scale=0.25]{test2012/vertexing/figures/h_ratioEsum_h_ratioEsum_dataMC_trigseltwotrksel4hit_recoilmc_twotrkfilt.png}
-\caption{Kinematic distributions for e$^+$e$^-$ pairs selected by opposite charged tracks in the top and bottom half of the tracker: track momentum in the top half of the SVT (left), invariant mass (middle) and the sum of the track momentum for the pair.}
+\caption{Kinematic distributions for e$^+$e$^-$ pairs selected by opposite charged tracks in the top and bottom half of the tracker: track momentum in the top half of the SVT (left), invariant mass (middle) and the sum of the track momentum for the pair (right).}
 \label{fig:pair_kin}
@@
 \end{center}
-
-For the vertexing 
-performance the foremost difference compared to electron beam running is that the target was 
-located approximately 67~cm from our nominal target position; giving almost collinear tracks in the detector. 
-This degrades the vertex resolution along the 
+We estimate the accuracy of the SVT momentum scale and resolution by looking at the agreement 
+between data and simulation in the shape of the kinematic distributions for single- and two track 
+events.  By adjusting the overall momentum scale and smearing the simulated events with a 
+Gaussian resolution we estimate an uncertainty of 10\% on both the momentum scale and 
+resolution in the Test run. This uncertainty is
+
+For the vertexing performance the foremost difference compared to electron beam running is that the 
+target was located approximately 67~cm from our nominal target position; giving almost collinear tracks 
+in the detector. This degrades the vertex resolution along the 
 beam line compared to that expected in an electron beam with tracks from the nominal target position. 
 Furthermore, tails of the vertex distributions are impossible to study with the finite data sample obtained 
-in the test run. Nevertheless, useful information can still be 
+in the Test run. Nevertheless, useful information can still be 
 obtained by studying the vertex distributions. Figure~\ref{fig:vtx_pos} shows the distance of closest 
-approach of the momentum vectors extrapolated in the 
-upstream direction from our analyzing magnet, taking into account the measured fringe field of the PS magnet. 
+approach of the momentum vectors extrapolated in the upstream direction from our analyzing magnet, 
+taking into account the measured fringe field of the PS magnet. 
  \begin{center}
@@
 	\includegraphics[width=5cm]{figures/h_vtx_fr_z_h_vtx_z_trigsel4hit_pair1351_twotrkfilt-v6-paper}
-	\caption{ Vertex position represented by the distance of 
-	closest approach of the extrapolated momentum vectors upstream of the PS magnet taking into account 
-	the measured fringe field. The overall shift from zero in the x-direction is 
-	due to a 30~mrad rotation of the SVT with respect to the beam line.}
+	\caption{ Vertex position represented by the distance of closest approach of the extrapolated 
+	momentum vectors upstream of the PS magnet taking into account the measured fringe field. The 
+	overall shift from zero in the x-direction is due to a 30~mrad rotation of the SVT with respect to the 
+	beam line.}
 	\label{fig:vtx_pos}

### 2013-11-24 hps-testrun-nim.tex
small text fix
Added expected momentum resolution.
Adding new E/p plot

@@
 Gaussian resolution we estimate an uncertainty of 10\% on both the momentum scale and 
-resolution in the Test run. This uncertainty is
+resolution in the Test run. The expected momentum resolution from simulation is between 4-5\% 
+for tracks in the momentum range of the Test run.
 
@@
 Fig.~\ref{fig:gains}. 
+{\small
 \begin{figure}[]
 \begin{center}
-{\small
-	\includegraphics[width=7cm]{figures/eoverp_MC_egs_0_016x0_June5_2013_Sho_Ecal_presentation.png}
-	\includegraphics[width=7cm]{figures/eoverp_data_run1351_June5_2013_Sho_Ecal_presentation.png}
-	\caption{The ECal energy over track momentum ratio for simulation (top) and data (bottom).\color{red}{\bf (Update style.)}} 
+	\includegraphics[width=7cm]{figures/h_Ep_data_h_Ep_ep_dataMC_1351.pdf}
+	\caption{The ECal energy over track momentum ratio comparing data and simulation} 
 	\label{fig:gains}
-}
-\end{center}
-\end{figure}
+\end{center}
+\end{figure}
+}
 The peak position of the distribution indicates the sampling fraction of the ECal, 

### 2013-12-04 hps-testrun-nim.tex
Changed EoverP plot to Pelles based on good region. It has loose track selection and the calibration is the default as of v5 detector.
Added new t0 plot. Fixed biblio style. Changed to a test run ecal beamline picture.

@@
 Interconnect (CI) concept developed at SLAC as generic building blocks for DAQ systems in high energy 
-physics {\bf [need reference]}. 
-The RCE is a generic computational building block, housed on a separate daughter card called 
-Data Processing Module (DPM), that are realized on an ATCA front board called the Cluster On Board (COB), 
-see Fig.~\ref{fig:cob}.
+physics. The RCE is a generic computational building block, housed on a separate daughter card called 
+Data Processing Module (DPM), that are realized on an ATCA front board called the Cluster On Board 
+(COB), see Fig.~\ref{fig:cob}.
  \begin{figure}[]
@@
 The low gain of APDs ($\sim 200$) was compensated with custom made preamplifier boards, which provide factor 2000 amplification of the ADP signal.
-
 \begin{figure}[]
@@
 The temperature stability of the system during the test run was better than $1^\circ~$F, the temperature uniformity inside the box was better than  $4^\circ~$F.
-
-\begin{center}
-{\small
-\begin{figure}
-\includegraphics[width=7cm]{figures/ECal}
-\includegraphics[width=7cm]{figures/ecal_vacuumchamber.pdf}
+\begin{center}
+{\small
+\begin{figure*}[htb]
+\includegraphics[width=0.45\textwidth]{figures/ECal}
+\includegraphics[width=0.45\textwidth]{figures/ecal_picture_beamline}
+%\includegraphics[width=7cm]{figures/ecal_vacuumchamber.pdf}
 %\includegraphics[width=7cm]{figures/ecal_assembly}
-\caption{Layout of PbWO$_{4}$ modules in two halves of the ECal (top) and ECal assembly together with ECal vacuum chamber (bottom). }
+\caption{Layout of PbWO$_{4}$ modules in two halves of the ECal (left) and the ECal assembly on the beam line (right). }
 \label{fig:ecal}
-\end{figure}
+\end{figure*}
 }
@@
 {\small
-\includegraphics[width=7cm]{figures/FADC250_Photo_001.jpg}
+\includegraphics[width=5cm]{figures/FADC250_Photo_001.jpg}
 \caption{A Jefferson Lab FADC250 VXS module.}
@@
 The FADCs store 12-bit digitized samples at 250~MHz in 8~$\mu$s deep pipelines. 
-When a trigger is received, the appropriate part of the pipeline is accessed for the readout.
-HPS used FADCs in the integration mode.
-A predefined number of samples of the signal that exceeds a predefined threshold have been summed and stored in 17-bit register for readout.
-The number of samples for integration was defined by two parameters that could be set separately, the number of samples integrated before the signal crossed threshold ($NSB$) and  the number of samples integrated after the signal crossed threshold ($NSA$), see Fig.\ref{fig:hps_trigger_data}.
-This scheme significantly compresses the data input 
-to the FADC. During data analysis, a pedestal value is subtracted to obtain the actual summed energy.
-
-For various reasons only 385 out of 442 modules (87\%) were operational during the test run.
-The readout threshold was set to $70$ MeV, the number of samples before and after the threshold crossing were NSB=5 and NSA=30, respectively.
-
+When a trigger is received, the appropriate part of the pipeline is accessed for the readout. HPS used 
+FADCs in the integration mode. A predefined number of samples of the signal that exceeds a predefined 
+threshold have been summed and stored in 17-bit register for readout. The number of samples for 
+integration was defined by two parameters that could be set separately, the number of samples 
+integrated before the signal crossed threshold ($NSB$) and  the number of samples integrated after the 
+signal crossed threshold ($NSA$), see Fig.\ref{fig:hps_trigger_data}. 
 \begin{figure}[]
@@
 {\small
-\includegraphics[width=8cm]{figures/fadc_datapath_diagram.png}
-\caption{\small{FADC data paths}}
+\includegraphics[width=7cm]{figures/fadc_datapath_diagram.png}
+\caption{\small{FADC data paths.}}
 \label{fig:hps_trigger_data}
@@
 \end{figure}
+This scheme significantly compresses the data input to the FADC. During data analysis, a pedestal 
+value is subtracted to obtain the actual summed energy.
+
+For various reasons only 385 out of 442 modules (87\%) were operational during the test run. The 
+readout threshold was set to $70$ MeV, the number of samples before and after the threshold crossing 
+were 5 and 30, respectively.
 
@@
 using information from the ECal. The trigger looks for time coincidences of clusters in the top and bottom 
-half of the ECal. The trigger system can be broken down into three sections (see 
-Fig.~\ref{fig:hps_trigger_cal}):
+half of the ECal. The trigger system can be broken down into three sections as shown in 
+Fig.~\ref{fig:hps_trigger_cal}:
+ \begin{figure}[b]
+\begin{center}
+{\small
+ \includegraphics[width=8cm]{figures/hps_trigger_cal}
+\caption{Block diagram of the ECAL trigger system consisting of the FADC that samples and digitizes 
+signals for each detector channel and sends them for cluster finding in the CTP. The CTP clusters are 
+sent to the SSP where the final trigger decision is taken based on pairs of clusters in both halves of the 
+ECal. The decision is sent to the Trigger Supervisor (TS) that generates the necessary signals to readout 
+the sub-detectors.}
+ \label{fig:hps_trigger_cal}
+}
+\end{center}
+ \end{figure}
  \begin{itemize}
@@
  \end{itemize}
- \begin{figure}[t]
-\begin{center}
-{\small
- \includegraphics[width=8cm]{figures/hps_trigger_cal}
-\caption{Block diagram of the ECAL trigger system consisting of the FADC that samples and digitizes 
-signals for each detector channel and sends them for cluster finding in the CTP. The CTP clusters are 
-sent to the SSP where the final trigger decision is taken based on pairs of clusters in both halves of the 
-ECal. The decision is sent to the Trigger Supervisor (TS) that generates the necessary signals to readout 
-the sub-detectors.}
- \label{fig:hps_trigger_cal}
-}
-\end{center}
- \end{figure}
+
 The time coincidence window of pairs of clusters in the top and bottom half of the ECal are 
-programmable with 4~ns resolution.
-
-As described above, the first stage of the trigger logic is incorporated into the 
-FPGA's on the FADC boards. The trigger  
-integrates using a "time-over-threshold" window, see Fig. \ref{fig:hps_trigger_data}.
+programmable with 4~ns resolution.  As described above, the first stage of the trigger logic is 
+incorporated into the FPGA's on the FADC boards. The trigger  
+integrates using a "time-over-threshold" window as explained in Fig. \ref{fig:hps_trigger_data}.
 For triggering purposes, every channel has: 
@@
 was well timed in to the trigger with the rise of the pulse at the 3rd sampling point.
-\begin{figure}[h]
+\begin{figure}[]
 \begin{center}
@@
 provide the absolute charge normalization.
-\begin{figure}[h]
-\begin{center}
-{\small
-	\includegraphics[width=6cm]{figures/run1351_mip_small.pdf}
+\begin{figure}[]
+\begin{center}
+{\small
+	\includegraphics[width=7cm]{figures/run1351_mip_small.pdf}
     	\caption{ The cluster charge distribution for hits associated with a track. }
@@
 times. 
-\begin{figure}[h]
-\begin{center}
-{\small
-	\includegraphics[width=6cm]{figures/t0_resolution_run1351_110513.pdf}
+\begin{figure}[]
+\begin{center}
+{\small
+	\includegraphics[width=6cm]{figures/test_run_1351_hit_time_corrected_top_layer2.pdf}
 	\caption{
 	The cluster time residual for a representative sensor relative to the track time (see text for more 
-	details). \color{red}{\bf Fix axis.} }
+	details). }
 	\label{fig:tracktime}
@@
 Fig.~\ref{fig:hit_efficiency}, was measured to be above 98\% and fairly uniform across the SVT.
-\begin{figure}[h]
-\begin{center}
-{\small
-    	\includegraphics[width=7cmh]{figures/single_hit_efficiency_Omar_11192013.pdf}
+\begin{figure}[]
+\begin{center}
+{\small
+    	\includegraphics[width=7cm]{figures/single_hit_efficiency_Omar_11192013.pdf}
         \caption{ The hit reconstruction efficiency as a function of detector layer.}
@@
 {\small
-\begin{figure*}[ht]
+\begin{figure*}[t]
    \includegraphics[width=5cm]{figures/h_trk_top_px_h_trk_top_px_trigsel4hit_pair1351_twotrkfilt-v6-paper}
@@
 {\small
-	 \begin{figure*}[ht]
+	 \begin{figure*}[t]
 	% Plot info:
@@
 \begin{center}
-	\includegraphics[width=7cm]{figures/h_Ep_data_h_Ep_ep_dataMC_1351.pdf}
+	\includegraphics[width=7cm]{figures/h_ep_data_h_ep_mc_dataMC_v5_1351_goodregion_notrkcuts.pdf}
 	\caption{The ECal energy over track momentum ratio comparing data and simulation} 
@@
 These occupancies are dominated by electrons which have multiple Coulomb scattered (MCS) 
-to relatively large angles in the target. Because HPS is sensitive to scattering angles far out on the tail of the 
-MCS distribution, well beyond the angles important in other experiments, care must be taken
+to relatively large angles in the target. Because HPS is sensitive to scattering angles far out on the tail of 
+the MCS distribution, well beyond the angles important in other experiments, care must be taken
 to ensure our simulations are correct in this regime.
@@
 theory~\cite{Moliere:1948zz} for a wide range 
-of materials and projectiles~\cite{Attwood:2005zz,Shen:1978ha,Gottschalk1993467}. We have verified that 
-the angular distribution $F(\theta)$ in the differential cross section $d\sigma = F( \theta) d(\cos\theta) d\phi$ 
-for the \egs{}~\cite{egs5} simulation program show good agreement with \moliere{}'s analytical formula as 
-formulated by Bethe~\cite{Bethe:1953va}. 
-The small angle approximation was also shown to be in agreement with the theory formulated by Gaudsmit and 
-Saunderson~\cite{Goudsmit:1940zza,Goudsmit:1940zz} that is valid for any angle. 
+of materials and projectiles~\cite{Attwood:2005zz,Shen:1978ha,Gottschalk1993467}. We have verified 
+that the angular distribution $F(\theta)$ in the differential cross section 
+$d\sigma = F( \theta) d(\cos\theta) d\phi$ for the \egs{}~\cite{egs5} simulation program show good 
+agreement with \moliere{}'s analytical formula as formulated by Bethe~\cite{Bethe:1953va}. 
+The small angle approximation was also shown to be in agreement with the theory formulated by 
+Gaudsmit and Saunderson~\cite{Goudsmit:1940zza,Goudsmit:1940zz} that is valid for any angle. 
 While \egs{} uses the more complex and time consuming \moliere{} 
@@
 continuously joined, functions to take into account 
-small and large angle scattering. Due to the explicit function in large angle approximation used by \geant{} 
-we expect that \geant{} will overestimate the angular distribution at angles larger than a few mrad.
+small and large angle scattering. Due to the explicit function in large angle approximation used by 
+\geant{} we expect that \geant{} will overestimate the angular distribution at angles larger than a few 
+mrad.
 
@@
 Data was taken at three different converter thicknesses with a beam current varying between 
-$30-70$~nA, see~Tab.~\ref{tab:currents}.  The photon beam line during the test run produced a relatively 
-large fraction of pairs 
-originating upstream of the converter. This contribution was measured during data taking 
-with ``empty'' converter runs i.e. removing the converter but with all other conditions 
-the same. 
-The upstream background measured in the ``empty'' converter runs was subtracted 
-from the other runs, properly normalized using the measured integrated currents.
-\begin{table}
+$30-70$~nA, see~Tab.~\ref{tab:currents}.  
+\begin{table}[t]
 \begin{center}
@@
 \end{tabular}
+}
 \caption{Measured integrated currents for the dedicated photon runs.}
 \label{tab:currents}
-}
 \end{center}
 \end{table}
+The photon beam line during the test run produced a relatively 
+large fraction of pairs 
+originating upstream of the converter. This contribution was measured during data taking 
+with ``empty'' converter runs i.e. removing the converter but with all other conditions 
+the same. 
+The upstream background measured in the ``empty'' converter runs was subtracted 
+from the other runs, properly normalized using the measured integrated currents.
 
@@
 Hit energy is calibrated by matching track momentum to cluster energy, as described in Sec.~\ref{sec:ecal_calibration}.
-
-The measured 
-angular distribution in the ECal for the three converter thicknesses are shown in 
-Fig.~\ref{fig:ang_distr_data} (left). 
+The measured angular distribution in the ECal for the three converter thicknesses are shown in Fig.~\ref{fig:ang_distr_data}.
 \begin{figure}[]
@@
 The data has been normalized to the integrated beam current and the background has been 
-subtracted. 
-The background fraction for the there converter thicknesses was 16\%, 52\% and 71\% 
+subtracted. The background fraction for the there converter thicknesses was 16\%, 52\% and 71\% 
 for converter thicknesses of 1.6\%, 0.45\% and 0.18\%, respectively. The background fraction was also 
@@
 \egs{} normalized to 1~s of beam at 90~nA beam current with a converter thickness of 1.6\%. 
-\begin{center}
-{\small
+Reasonable agreement is obtained in the most important region close to the beam. There is a hint of a 
+slightly different slope of the data at larger angles; this difference is covered by systematic uncertainties.  
+The total rates for each converter thickness is shown in Fig.~\ref{fig:rate_vs_thickness} and summarized 
+in Tab.~\ref{tab:ang_distr_dataMC}.
 \begin{figure}[]
-%	\begin{figure*}[t]
-	\includegraphics[ scale=0.25]{figures/dataMC_1351_Hit_Y_top_norm_bkgsub.png}
-%	\includegraphics[ scale=0.25]{figures/dataMC_1354_Hit_Y_top_norm_bkgsub.png}
-%	\includegraphics[ scale=0.25]{figures/dataMC_1353_Hit_Y_top_norm_bkgsub.png}
+{\small
+	\begin{center}
+	\includegraphics[ width=7cm]{figures/dataMC_1351_Hit_Y_top_norm_bkgsub.png}
 	\caption{Comparison between the observed and predicted angular distribution using \egs{} for a 
@@
 	\label{fig:ang_distr_dataMC}
-%	\end{figure*}
-	\end{figure}
-}
-\end{center}
-Reasonable agreement is obtained in the most important region close to the beam. There is a hint of a 
-slightly different slope of the data at larger angles; this difference is covered by systematic uncertainties.  The 
-total rates for each converter thickness is shown in Fig.~\ref{fig:rate_vs_thickness} and summarized in 
-Tab.~\ref{tab:ang_distr_dataMC}.
-\begin{center}
-{\small
+\end{center}
+}
+\end{figure}
 \begin{figure}[]
-%	\begin{figure*}[]
-	%\includegraphics[ scale=0.3]{figures/dataMC_geant4.png}
-	\includegraphics[ scale=0.3]{figures/dataMC_egs.png}
-	\caption{The measured rate as a function of converter thickness for data and \egs{} simulation of MCS in 	the converter.} 
+\begin{center}
+{\small
+	\includegraphics[ width=7cm]{figures/dataMC_egs.png}
+	\caption{The measured rate as a function of converter thickness for data and \egs{} simulation 
+	of MCS in 	the converter.} 
 	\label{fig:rate_vs_thickness}
-%	\end{figure*}
-	\end{figure}
-}
-\end{center}
+}
+\end{center}
+\end{figure}
 The total systematic uncertainty was estimated to be between 10-18\% depending on the run including:  
@@
 \begin{center}
-{\small
 \begin{table}
+{\small
 \begin{tabular}{|l|c|c|c|}
@@
 thicknesses. The uncertainty on the prediction includes systematic uncertainties. }
+}
 \label{tab:ang_distr_dataMC}
 \end{table}
-}
 \end{center}

### 2014-03-06 hps-testrun-nim.tex
Updating mip, eoverp and turn on plot to latest versions

@@
 {\small
-	\includegraphics[width=7cm]{figures/run1351_mip_small.pdf}
+	%\includegraphics[width=7cm]{figures/run1351_mip_small.pdf}
+	\includegraphics[width=7cm]{figures/mip_top_layer_2.png}
     	\caption{ The cluster charge distribution for hits associated with a track. }
@@
 {\small
-	\includegraphics[width=6cm]{figures/test_run_1351_hit_time_corrected_top_layer2.pdf}
+	\includegraphics[width=7cm]{figures/test_run_1351_hit_time_corrected_top_layer2_mod.pdf}
 	\caption{
@@
 \begin{center}
-	\includegraphics[width=7cm]{figures/h_ep_data_h_ep_mc_dataMC_v5_1351_goodregion_notrkcuts.pdf}
+	\includegraphics[width=7cm]{figures/h_ep_data_0_h_ep_MC_0_dataMC_1351-v6-v6gains_2-trig-top-cl600reg0.pdf}
 	\caption{The ECal energy over track momentum ratio comparing data and simulation} 
@@
 threshold was measured to be 1280 in units of ADC counts as expected. The threshold was not 
-perfectly sharp because of uncertainties in the conversion from readout to trigger hits described above, 
-but based on comparisons with simulation we found that the trigger worked exactly as specified.
+perfectly sharp because of uncertainties in the conversion from readout to trigger hits described 
+above, but based on comparisons with simulation we found that the trigger worked exactly as 
+specified.
 \begin{figure}[ht]
@@
 {\small
-	\includegraphics[width=7cm]{figures/top_turn_on__bottom_tag_E}
-	\caption{Trigger turn-on in the top half of the ECal (bottom is similar) for data and simulation as a 
-	function of probe cluster energy.}
+	\includegraphics[width=7cm]{figures/h_cl_E_probedata_eff_h_cl_E_probeMC_eff_dataMC_1351-v7-trig-tagBot.pdf}
+	\caption{Trigger efficiency in both halves of the ECal for data and simulation as a 
+	function of cluster energy.}
 \label{fig:turnon}
@@
 \end{figure}
-The trigger turn-on is slow and reaches an uneven plateau just below $1$ GeV for two reasons;  gain 
-variations between different crystals lead to the threshold variations and the nonlinearity of the 
-time-over-threshold integral means that the effective threshold is higher for clusters that span multiple 
-crystals. The effective trigger threshold is therefore dependent on position and energy of the particle 
-as well as cluster multiplicity. 
+The trigger turn-on is slow and reaches an uneven plateau just below 1~GeV for two reasons;  
+gain variations between different crystals lead to the threshold variations and the nonlinearity of 
+the time-over-threshold integral means that the effective threshold is higher for clusters that span 
+multiple crystals. The effective trigger threshold is therefore dependent on position and energy of 
+the particle as well as cluster multiplicity. 
 %Overall the trigger appears to have functioned exactly as intended. 

### 2014-03-06 figures/h_ep_data_0_h_ep_MC_0_dataMC_1351-v6-v6gains_2-trig-top-cl600reg0.C

@@ -1,0 +1,310 @@
+{
+//=========Macro generated from canvas: cDefault/cDefault
+//=========  (Fri Jan 17 12:19:50 2014) by ROOT version5.34/14
+   TCanvas *cDefault = new TCanvas("cDefault", "cDefault",10,44,600,600);
+   gStyle->SetOptFit(1);
+   gStyle->SetOptTitle(0);
+   cDefault->Range(-0.4210526,-935.3733,2.210526,5300.449);
+   cDefault->SetFillColor(0);
+   cDefault->SetBorderMode(0);
+   cDefault->SetBorderSize(2);
+   cDefault->SetTickx(1);
+   cDefault->SetTicky(1);
+   cDefault->SetLeftMargin(0.16);
+   cDefault->SetRightMargin(0.08);
+   cDefault->SetTopMargin(0.06);
+   cDefault->SetBottomMargin(0.15);
+   cDefault->SetFrameBorderMode(0);
+   cDefault->SetFrameBorderMode(0);
+   
+   TH1F *h_ep_MC_0 = new TH1F("h_ep_MC_0","",50,0,2);
+   h_ep_MC_0->SetBinContent(5,8.328486);
+   h_ep_MC_0->SetBinContent(7,8.328486);
+   h_ep_MC_0->SetBinContent(8,16.65697);
+   h_ep_MC_0->SetBinContent(9,8.328486);
+   h_ep_MC_0->SetBinContent(10,41.64243);
+   h_ep_MC_0->SetBinContent(11,66.62789);
+   h_ep_MC_0->SetBinContent(12,141.5843);
+   h_ep_MC_0->SetBinContent(13,208.2122);
+   h_ep_MC_0->SetBinContent(14,316.4825);
+   h_ep_MC_0->SetBinContent(15,732.9068);
+   h_ep_MC_0->SetBinContent(16,1474.142);
+   h_ep_MC_0->SetBinContent(17,2956.613);
+   h_ep_MC_0->SetBinContent(18,3414.679);
+   h_ep_MC_0->SetBinContent(19,3789.461);
+   h_ep_MC_0->SetBinContent(20,2173.735);
+   h_ep_MC_0->SetBinContent(21,1016.075);
+   h_ep_MC_0->SetBinContent(22,374.7819);
+   h_ep_MC_0->SetBinContent(23,91.61335);
[…]

### 2014-03-07 hps-testrun-nim.tex
New abstract, edited intro, overview, beamline and the start of SVT

@@
 \begin{abstract}
-Heavy photons, aka "hidden sector" or "dark" photons, are massive cousins to the SM photon, 
-which couple to an analogue of electric charge. They arise naturally in theories with additional
-U(1) gauge groups, and have been proposed as a possible explanation for the muon g-2 anomaly,
-astrophysical puzzles, and possible sightings of light dark matter in direct detection experiments.
-Masses in the range 10 to 1000 MeV are suggested. Heavy photons couple weakly to electric charge, 
-so can be produced via electroproduction and can decay into elecron-positron pairs, albeit at rates 
-strongly suppressed compared to standard QED trident processes. Consequently, heavy photons must be identified
-above copious backgrounds, requiring high luminosity/high rate experiments, good mass resolution
-(to identify invariant mass bumps), and good vertexing (to see the long lifetimes implied by
-weak couplings). The Heavy Photon Search (HPS) will use  a silicon microstrip vertex tracker
-triggered by a high speed PbWO4 electromagnetic calorimeter to search 
-for these states in a fixed target experiment at Thomas Jefferson National Accelerator Facility (JLab). 
-The first stage of HPS was the HPS Test Run experiment, designed to demonstrate the technical feasibility of the detector and data
-acquisition systems and to confirm that critical backgrounds were correctly modeled.
-This paper describes the HPS Test Run detector, reviews its performance, and presents results of
-the normalized trigger rate measurements that confirm the accuracy of the background simulation.
+Construction and design of the Heavy Photon Search (HPS) experiment, designed to search for an 
+\ee resonance from heavy photon production in a fixed-target setup at the Thomas Jefferson 
+Accelerator Facility (JLab), is ongoing. As a first stage, a test apparatus was constructed and 
+operated at JLab to demonstrate that the apparatus and data acquisition systems are technically 
+feasible and that the trigger rates and occupancies encountered in electron-beam running are as 
+simulated. Given dedicated running time with electron beams, the HPS Test apparatus is 
+capable of searching for heavy photons in unexplored regions of parameter space.  Charged 
+particle tracks are measured with a compact forward silicon microstrip detector and 
+electromagnetic showers from electrons and photons are detected in a dense array of 
+PbWO$_{4}$ crystals. To allow clean passage of the scattered intense electron beam after 
+the thin tungsten target foil while keeping sensitivity to low-mass heavy photons,  the sensitive region 
+of the detectors are place at $\pm 15$~mrad with respect to the horizontal beam plane. 
+The discrimination between prompt and displaced \ee pairs requires the first layer of silicon 
+sensors to be placed only 10~cm behind the target and 0.5~mm from the beam. 
+The HPS Test apparatus included the high-speed trigger and data acquisition needed for 
+running with electron beams. Details of the layout and performance of the Test detectors and 
+associated readout electronics are presented. 
 \end{abstract}
@@
 %% keywords here, in the form: keyword \sep keyword
-silicon microstrips \sep tracking  \sep vertexing \sep heavy photon \sep electromagnetic calorimeter
+silicon microstrip \sep tracking  \sep vertexing \sep heavy photon \sep dark photon \sep hidden sector \sep electromagnetic calorimeter
 %% MSC codes here, in the form: \MSC code \sep code
@@
 \label{introduction}
-One of the more striking anomalies in recent astrophysical observations is an excess of high energy 
-electrons and positrons consistent with a large, unknown source of pair 
-production~\cite{Adriani:2008zr, FermiLAT:2011ab}. The existence of a massive, hidden sector vector 
-boson; a ``dark photon;" that mixes kinetically with the Standard Model photon and mediates 
-annihilation or decay of dark matter particles is a theoretically attractive explanation of this cosmic-ray 
-excess~\cite{Holdom:1985ag}\cite{ArkaniHamed:2008qn}.
+Heavy photons, aka "hidden sector" or "dark" photons, or from here on \Aprime{}, are particles with 
+mass $10-1000$~MeV 
+which couple weakly to the Standard Model photon~\cite{Holdom:1985ag}, so can be radiated by 
+electrons, and can decay 
+into \ee pairs, albeit at rates far below those of QED trident processes. They have been suggested by 
+numerous Beyond Standard Model theories and as an explanation of the current muonic $g-2$ 
+anomaly, and may couple directly to hidden sector particles that may constitute all or some of the 
+dark matter~\cite{ArkaniHamed:2008qn}. 
+Current phenomenology highlights the $20-1000$~MeV/c$^{2}$ mass range, and 
+suggests that \Aprime's couple to electric charge with strength $\epsilon$e, where 
+$\epsilon$ is in the range of $10^{-3} -10^{-5}$. [REFERENCE]. This range of parameters makes 
+\Aprime{} searches viable in moderate energy fixed target 
+electroproduction~\cite{Bjorken:2009mm}, but require large data sets and good mass resolution
+to identify a small mass peak above the copious QED background at very small production 
+angles. At small couplings, \Aprime's become long-lived, so detection of a displaced decay 
+vertex can reject the prompt QED background and boost experimental sensitivity.  These production 
+and kinematics poses stringent constraint on the detector requirements:
+\begin{itemize}
+\item large and uniform acceptance in the forward region close to the beam in order to catch boosted 
+\Aprime{} decay products,
+\item beam passage through the apparatus in vacuum, to eliminate direct interactions with the 
+detector and minimize beam gas interactions, 
+\item a flexible, redundant and efficient trigger selecting electron and positron pairs at rates up to 
+50~kHz,
+\item excellent track reconstruction efficiency for electrons and positrons,
+\item good angular and momentum resolution to reconstruct invariant mass precisely,
+\item excellent vertex resolution to discriminate displaced \Aprime{} decays from prompt QED 
+backgrounds,
+\item high rate electronics with excellent timing resolution to minimize out of time backgrounds,
+\item data handling rates of 100~MB/s to permanent storage,
+\item detector components that can survive and efficiently operate in a high radiation environment 
+with local doses exceeding $100$~Mrad.
+\end{itemize}
+The HPS experiment~\cite{HPS_proposal_2010} uses both invariant mass and 
+vertex signatures by placing a $\approx 1$~m long silicon tracking and vertexing detector 10~cm 
+downstream  of a 0.25\%~$\chi_0$ tungsten target inside a dipole magnet. The experiment runs at high 
+rates (up to 50kHz), exploiting the 
+100\% duty cycle of the Thomas Jefferson National Accelerator Facility (JLab) CEBAF accelerator to 
+accumulate the need statistics. The trigger is provided by a fast electromagnetic calorimeter just 
+downstream of the tracking detector.
+
+The HPS Test apparatus, a simplified version of the full HPS experiment, was proposed and 
+approved at Thomas Jefferson National Accelerator Facility (JLab) as the first stage of the HPS 
+experiment. Its purposes included demonstrating that the apparatus and data acquisition systems are 
+technically feasible and that the trigger rates and occupancies encountered in electron-beam 
+running are as simulated. Given dedicated running time with electron beams, the HPS Test Run 
+apparatus is capable of searching for heavy photons in unexplored regions of parameter space.    
+The HPS Test apparatus was installed on April 19, 2012, and ran parasitically with the HDice 
+experiment~\cite{HDice}, using its photon beam, until May 18. The JLab run schedule 
+precluded any dedicated electron beam running, but the HPS Test Run was allowed a short and 
+valuable dedicated run with the photon beam. Most technologies used in the Test apparatus will 
+be used in the HPS detector with some improvements to each of the systems; both from lessons 
+learned during running of the Test run but also from less schedule and budget constraints.
+
+This paper reviews the HPS Test Run apparatus; documents the performance of the trigger, 
+data acquisition, silicon tracking detector, and the electromagnetic calorimeter at the level assumed 
+in calculating the physics reach of the HPS experiment.
+
+%Of particular importance, data from the dedicated photon beam running has been used to 
+%compare the measured trigger rates with those expected in simulation. The Test Run trigger rate is 
+%almost entirely due to photons which have converted to \ee pairs in a thin target upstream of HPS 
+%and it 
+%is sensitive to their multiple Coulomb scattering in the conversion target.  During electron beam 
+%running, 
+%the tails of the multiply Coulomb scattered primary beam are the dominant source of occupancy in %the 
+%tracker and trigger rate in the electromagnetic calorimeter. 
+%The trigger rates in the Test Run are also sensitive to the tails of the multiple Coulomb
+%scattering distribution. Good agreement between the measured and simulated rates confirms
+%our understanding of multiple Coulomb scattering and 
+%the reliability of the background simulation used to benchmark the physics reach of the HPS 
+%experiment.
+
+\section{Detector Overview}
+\label{detector}
 \begin{center}
@@
 \end{center}
-
-Heavy photons, aka "hidden sector" or "dark" photons, are particles with mass 10-1000 MeV which 
-couple weakly to the SM photon, so can be radiated by electrons, and can decay into e+e- pairs, albeit 
-at rates far below those of QED trident processes. They have been suggested by numerous Beyond 
-Standard Model theories and as an explanation of the current muonic g-2 anomaly, and may couple 
-directly to hidden sector particles that may constitute all or some of the dark matter. Current 
-phenomenology highlights the 20-1000~MeV/c$^{2}$ mass range, and suggests that heavy photons 
-couple to electric charge with strength $\epsilon$e, where 
-$\epsilon$ is in the range of $10^{-3} -10^{-5}$. This range of parameters makes heavy photon searches 
-viable at electron-positron colliders and in moderate energy fixed target electroproduction, and results 
-from both approaches have already been reported. Fixed target experiments offer the highest sensitivity 
-for heavy photons with mass $<1000$~MeV/c$^{2}$ ~\cite{Bjorken:2009mm}, but require large data 
-sets and good mass resolution
-to identify a small mass peak above the copious QED background. At small couplings, heavy photons 
-become long-lived, so detection of a secondary decay vertex can reject the prompt QED background 
-and boost experimental sensitivity.
-The HPS experiment uses both invariant mass and vertex signatures by placing a $\approx 1$~m long 
-silicon tracking and vertexing detector (10~cm) downstream  of a 0.25 \%X$_0$ tungsten) target and 
-inside a dipole magnet~\cite{HPS_proposal_2010}. The experiment runs at high rates, exploiting the 
-100\% duty cycle of the CEBAF accelerator to accumulate the need statistics. The trigger is provided by 
-a fast electromagnetic calorimeter just downstream of the magnet.
-
-The HPS Test run, a simplified version of the full HPS experiment, was proposed and approved at JLab 
-as the first stage of the HPS experiment. Its
-purposes included demonstrating that the apparatus and data acquisition systems are technically 
-feasible and that the trigger rates and occupancies encountered in electron-beam running are as 
-simulated. Given dedicated running time with electron beams, the HPS Test Run apparatus is capable of 
-searching for heavy photons in unexplored regions of parameter space.    
-The HPS Test apparatus was installed on April 19, 2012, and 
-ran parasitically with the HDice experiment, using its photon beam, until May 18. The JLab run schedule 
-precluded any dedicated electron beam running, but the HPS Test Run was allowed a short and 
-valuable dedicated run with the photon beam.
-
-This paper reviews the HPS Test Run apparatus; documents the successful performance of the trigger, 
-data acquisition, silicon tracker, and ECal at the level assumed in calculating the physics reach of the 
-experiment. Of particular importance, data from the dedicated photon beam running has been used to 
-compare the measured trigger rates with those expected in simulation. The Test Run trigger rate is 
-almost entirely due to photons which have converted to \ee pairs in a thin target upstream of HPS and it 
-is sensitive to their multiple Coulomb scattering in the conversion target.  During electron beam running, 
-the tails of the multiply Coulomb scattered primary beam are the dominant source of occupancy in the 
-tracker and trigger rate in the electromagnetic calorimeter. 
-The trigger rates in the Test Run are also sensitive to the tails of the multiple Coulomb
-scattering distribution. Good agreement between the measured and simulated rates confirms
-our understanding of multiple Coulomb scattering and 
-the reliability of the background simulation used to benchmark the physics reach of the HPS experiment.
-
-Searching for a small signal on a large background requires high statistics. This in turn requires the 
-experiment operate with high beam currents, handle very high data rates, and tolerate high radiation 
-levels. In particular, the following are required:
-\begin{itemize}
-\item large and uniform acceptance in the forward region close to the beam in order to catch boosted heavy photon decay products,
-\item beam passage through the apparatus in vacuum, to eliminate direct interactions with the detector and minimize beam gas interactions, 
-\item a flexible, redundant and efficient trigger selecting electron and positron pairs at rates up to 50kHz,
-\item excellent track reconstruction efficiency for electrons and positrons,
-\item good angular and momentum resolution to reconstruct invariant mass precisely,
-\item excellent vertex resolution to discriminate displaced heavy photon decays from prompt QED backgrounds,
-\item high rate electronics with excellent timing resolution to minimize out of time backgrounds,
-\item data handling rates of 100~MB/s to permanent storage,
-\item detector components that can survive and efficiently operate in a high radiation environment with 
-local doses exceeding $100$~Mrad.
-\end{itemize}
-
-\section{Detector Overview}
-\label{detector}
-The HPS experiment will run in Hall B at JLab using the CEBAF electron beam, a 
-499 MHz beam at energies ranging up to 11 GeV and currents up to 800 nA.  
-The design of the experiment follows from the kinematics of \Aprime production which 
+The HPS Test apparatus was designed to run in Hall~B at JLab using the CEBAF electron beam, a 
+499~MHz beam, at an energy of 2.2 and 6.6~GeV and currents between 200 and 600~nA.  
+The overall design of the experiment follows from the kinematics of \Aprime{} production which 
 typically results in final state particles within a few degrees of the incoming beam, especially at low 
-$m_{\textrm{A}^\prime}$. So detectors must be placed close to the beam. The intense electron beam 
-and the degraded electrons produced in the target and spread out horizontally by the analyzing magnet 
-constitute a "dead zone"  which must be completely avoided, so the apparatus is split vertically above 
-and below the beam plane. The beam is transported in vacuum to minimize beam gas backgrounds. 
-Even so, background rates in the detectors remain high, so high rate detectors,
-a fast trigger, and excellent time tagging are required to minimize their impact. 
-At masses below $2 m_\mu$ only decays to electrons are allowed, so the key trigger 
-comes from a lead-tungstate calorimeter with 250~MHz readout.  
-%Above the di-muon threshold, a 
-%downstream muon detector completes the trigger acceptance and may allow triggering for pion final states 
-%required for sensitivity near the $\rho$ mass.
-
-A rendering of the HPS Test apparatus installed on the beam line is shown in 
-Fig.~\ref{fig:testrundetector}.
-Most technologies used in the HPS Test apparatus will be used in the HPS detector with some 
-improvements to each of the systems; both from lessons learned during running of the HPS Test but 
-also from less schedule and budget constraints.
-
-An overview of the coverage, segmentation and performance of the HPS Test detector is given in 
-Tab.~\ref{tab:detector-overview}. 
+$m_{\textrm{A}^\prime}$. Detectors must therefore be placed close to the beam. 
+The intense electron beam and the degraded electrons after the target are spread out horizontally by 
+the analyzing magnet constitute a "dead zone" which must be completely avoided. The apparatus is 
+split vertically $15$~mrad above and below the beam plane and the beam is transported in vacuum 
+to minimize beam-gas interaction backgrounds. Even so, background occupancy in the detectors 
+remain high and are dominated by the degraded primary beam, so high rate detectors, a fast trigger, 
+and excellent time tagging are required to minimize their impact.  
+At masses below $2 m_\mu$ only decays to electrons are allowed, so the key trigger comes from a PbWO$_{4}$ crystal calorimeter. 
  %\begin{multicols}{2}
@@
 %\end{multicols}
+A rendering of the HPS Test apparatus installed on the beam line is shown in 
+Fig.~\ref{fig:testrundetector} and an overview of the coverage, segmentation and performance is 
+given in Tab.~\ref{tab:detector-overview}.
 
 The silicon tracking and vertexing detector for HPS Test, or SVT, operates in an existing vacuum 
-chamber inside the pair spectrometer analyzing magnet in Hall B at JLab.  The design principles of the 
-SVT are described in further detail in the HPS Test Run Proposal ~\cite{HPS_tPROP}. There are five 
-measurement stations, or ``layers,'' placed immediately downstream of the target. Each layer comprises 
-a pair of closely-spaced planes and each plane is responsible for measuring a single coordinate, or 
-``view.'' Introduction of a stereo angle between the two planes of each layer provides three-dimensional 
-tracking and vertexing throughout the acceptance of the detector with one redundant layer.
-
-In order to accommodate the dead zone, the SVT is built in two halves that are mirror reflections of one 
-another about the plane of the nominal electron beam.  Each half consists of five double-sided modules 
-mounted on a support plate that provides services to the modules and allows them to be moved as a 
-group relative to the dead zone. Each module places a pair of silicon microstrip sensors back-to-back at 
-a specified stereo angle with independent cooling and support.
-
-Each half of the electromagnetic calorimeter, or ECal, consists of 221 PbWO$_4$ crystals arranged in 
-rectangular formation. There are five rows with 46 
-modules in each row except the row closest to the beam plane which has 37. The light from each crystal 
+chamber inside the pair spectrometer analyzing magnet in Hall B at JLab.  There are five 
+measurement stations, or ``layers,'' placed immediately downstream of the target. Each layer 
+comprises a pair of closely-spaced silicon microstrip sensors responsible for measuring a single 
+coordinate, or ``view.'' Introduction of a small (50 or 100~mrad) stereo angle between the two 
+sensors of each layer provides three-dimensional tracking and vertexing throughout the acceptance 
+of the detector with one redundant layer. Each layer In order to accommodate the dead zone, the 
+SVT is built in two halves that are mirror reflections of one another about the plane of the nominal 
+electron beam.  Each layer in one half are supported on a common support plate with independent 
+cooling and readout.
+
+Each half of the electromagnetic calorimeter, or ECal, consists of 221 PbWO$_4$ crystals arranged 
+in rectangular formation. There are five rows with 46 modules in each row except the row closest to 
+the beam plane which has 37. The light from each crystal 
 is read out by Avalanche Photodiode (APD) glued on the back surface of the crystal. 
@@
 The  Data Acquisition system combines two architectures, the Advanced Telecom Communications 
-Architecture (ATCA) based SVT readout system and VXS based digitization and triggering system for the 
-ECal. The system was designed to run at up to a 20 kHz trigger rate.
+Architecture (ATCA) based SVT readout system and VXS based digitization and triggering system for 
+the ECal. The system was designed to run at up to 20~kHz trigger rate.
 
@@
 
-\section{The HPS Test Beamline}
-The HPS Test run studied multiple Coulomb scattering of electrons and positrons from bremsstrahlung photons 
-produced in the Hall-B tagged photon facility. Figure~\ref{fig:hpstest_layout} shows the layout of 
+\section{The HPS Test Run Beamline}
+The HPS Test run studied multiple Coulomb scattering of electrons and positrons from 
+bremsstrahlung photons produced in the Hall B tagged photon facility. 
+Figure~\ref{fig:hpstest_layout} shows the layout of 
 the HPS Test setup on the beam line. The SVT was installed inside the Hall B pair 
 spectrometer magnet (PS) vacuum chamber with the ECal mounted downstream of it. Both the 
-SVT and the ECal were retracted off the beam plane to allow clean passage of the photon beam through 
-the system. 
+SVT and the ECal were retracted off the beam plane compared to nominal electron beam runing to 
+allow clean passage of the photon beam through the system. 
 \begin{figure}[ht]
@@
 
-The photon beam was generated in the interaction of the $5.5$~GeV electrons with a gold radiator of 
-$10^{-4}~X_0$, located $\approx~9$~m upstream of the PS. The primary beam and scattered 
-electrons are deflected away from detectors by the dipole magnet of the photon tagging system. After 
-collimation (6.4~mm diameter), the photon beam passes through the aluminum PS pair converter and 
-later the HPS system. 
-The converter was located $\approx~77$~cm upstream of the first layer of the silicon vertex tracker. Data was 
-taken on different converters (empty, $1.8\times 10^{-3}~X_0$ , $4.5\times 10^{-3}~X_0$ and 
-$1.6 \times 10^{-2}~X_0$). 
-These measurements were repeated with the reverse field setting of the PS dipole magnet.
+The photon beam was generated in the interaction of $5.5$~GeV electrons with a $10^{-4}~X_0$ 
+gold radiator located $\approx~9$~m upstream of the PS. The primary beam and scattered 
+electrons are deflected away from detectors by the dipole magnet of the photon tagging system. 
+During the dedicated HPS Test run period, the collimated (6.4~mm diameter), photon beam passes 
+through the aluminum PS pair converter and later the HPS system as shown schematically in Fig.~\ref{fig:schematic_testrun_vs_erun}.
+\begin{figure}[ht]
+\includegraphics[ width=7cm]{figures/photon_vs_electron_beam_schematic.png}
+\caption{\small{Schematic comparison of HPS Test run photon beam compared to the HPS electron beam.}}\label{fig:schematic_testrun_vs_erun}
+\end{figure}
+The PS pair converter was located $\approx~77$~cm upstream of the first layer of the SVT.
+Data was taken on different converters (empty, $1.8\times 10^{-3}~X_0$ , $4.5\times 10^{-3}~X_0$ 
+and $1.6 \times 10^{-2}~X_0$) and repeated with the reverse field setting of the PS dipole magnet.
 
@@
 The Silicon Vertex Tracker (SVT) enables efficient reconstruction of charged particles and precision 
-determination of their trajectories. These measurements allow \Aprime{} decays to be distinguished from background 
-via simultaneous estimation of the invariant mass of \ee{} decay products and the position of decay vertexes 
-downstream of the target.
+determination of their trajectories. These measurements allow \Aprime{} decays to be distinguished 
+from background via simultaneous estimation of the invariant mass of \ee{} decay products and the 
+position of decay vertexes downstream of the target.
 
@@
 
-The design of the SVT presents a number of significant challenges.  First, the A$^\prime$ decay products 
-have momenta in the range of 1 GeV, so multiple scattering dominates mass and vertexing errors for any 
-possible material budget.  Therefore, the construction of the SVT must place the smallest amount of 
-material in the tracking volume.  Second, the signal yield for long-lived A$^\prime$ will be very small, so 
-the rejection of prompt vertexes must be exceedingly pure, on the order of $10^{-7}$, in order to eliminate 
-all prompt backgrounds.  This requires great care in design, calibration, and operation of the detector. 
-Finally, the passage of the degraded primary beam through the apparatus creates a region of extreme 
-occupancy and radiation that is critical for sensitivity to low-mass A$^\prime$ that have decay products 
-nearly collinear with the beam.  This places low-mass acceptance in opposition to tracking and vertexing 
-purity and the longevity of the detector.
-
-It is this last challenge that has the most interesting and obvious impacts on the design of the SVT. To 
-achieve good vertexing performance, the first layer must be placed no more than about 10 cm downstream 
-of the target. At that distance, it is found that the active region of a sensor can be placed as close to 1.5 mm 
-from the center of the beam, defining a 15 mrad ``dead zone" in the detector around the plane of the 
-primary beam. At the edge of this ``dead zone," the radiation dose approaches $10^{15}$ electrons/cm
-$^2$/month, or roughly $3 \times 10^{14}$~\fluenceunit{}/month~\cite{Rashevskaya:2002nd}, as shown in 
-Fig.~\ref{fig:radiation}.
+The design of the SVT is primarily driven by direct physics requirement and constraints from the 
+environment at the interaction region. The \Aprime decay products 
+have momenta in the range of 1~GeV, so multiple scattering dominates mass and vertexing 
+uncertainties for any possible material budget, so the SVT must minimize the amount of 
+material in the tracking volume. The signal yield for long-lived \Aprime's is very small, so 
+the rejection of prompt vertexes must be exceedingly pure, on the order of $10^{-7}$, in order to 
+eliminate all prompt backgrounds. To achieve the required vertexing performance the first layer of the 
+SVT must be placed no more than about 10 cm downstream of the target. At that distance, it is found 
+that the active region of a sensor can be placed as close to 1.5 mm from the center of the beam, 
+defining the 15 mrad ``dead zone" mentioned previously, to maximize low-mass \Aprime acceptance 
+with decay products nearly collinear with the beam axis. At the edge of this ``dead zone," the 
+radiation dose approaches $10^{15}$ electrons/cm$^2$/month, or roughly 
+$3 \times 10^{14}$~\fluenceunit{}/month~\cite{Rashevskaya:2002nd}, as shown in 
+Fig.~\ref{fig:radiation},  requiring the sensors to be actively cooled.
 % and~\ref{fig:rates}.
@@
 \label{fig:radiation}
-\caption{\small Simulation of the fluence 10~cm downstream of the target in the active region of the SVT ($|Y|>0.15~$cm) looking downstream; electrons bend towards $+x$.}
-\end{figure}
-%===================
-%===================
-%\begin{figure}[]
-%\includegraphics[width=7cm]{figures/rates}
-%\label{fig:rates}
-%\caption{\small Simulation of the occupancy in the SVT 10~cm downstream of the target as a function of the 
-%vertical distance from the beam center.}
-%\end{figure}
-%=================== 
-This requires the sensors to be actively cooled.
-Meanwhile, very low-energy delta rays from beam gas interactions multiply the density of background hits, so the SVT must operate inside the beam vacuum.
-Finally, in order to protect the sensors, the detector must be movable so that it can be retracted during periods of uncertain beam conditions.
-%To summarize the SVT must:
-%\begin{itemize}
-%\item have a uniform acceptance in the forward region; up to $\theta_y=XXXXmrad$ and as close as 
-%possible to the beam axis to catch boosted decay products,
-%\item >95\% reconstruction efficiency for electron and positrons  with energy down to $XXXX$~MeV,
-%\item momentum resolution of XXXX\% to separate a promptly decaying \Aprime{} signal from the irreducible background,
-%\item vertex resolution $<XXXX$~mm along the beam line direction to search for displaced \Aprime{} decays,
-%\item event timing resolution down to 2~ns, 
-%\item sustain a occupancy of up to 1\%, trigger rates of $\approx50$~kHz and data rates up to 100~MB/s,
-%\item survive and efficiently operate after $1\times10^{14} neutron eq. fluence,
-%
-%dosedetector components that can survive and efficiently operate in a high radiation environment with 
-%local doses exceeding $XXXX$~MRad
-%\end{itemize}
+\caption{{\small Simulation of the electron fluence 10~cm downstream of the target in the active region 
+of the SVT ($|Y|>0.15~$mm) looking downstream; electrons bend towards $+x$.}}
+\end{figure}
+Meanwhile, very low-energy delta rays from 
+beam-gas interactions multiply the density of background hits, so the SVT must operate inside the 
+beam vacuum.  Finally, in order to protect the sensors, the detector must be movable so that it can be 
+retracted during periods of uncertain beam conditions.
 
 \subsection{Layout}
-
-A realistic \geant{}~\cite{Agostinelli2003250} simulation of the detector based on the {\sc SLIC} simulation 
-package~\cite{Graf:2011zzc}, including all backgrounds, has been used to optimize the layout for acceptance, tracking efficiency, mass 
-resolution and prompt vertex rejection. The layout of the SVT is summarized in Tab.~\ref{tab:trk} and rendered in Fig.~\ref{fig:tracker_model}. 
-%Vertex resolution with an asymmetric beam spot of $\approx200\times40~\mu$m requires hit resolutions better than XXXX (XXXX)~$\mu$m in the vertical (horizontal) measurement coordinate. 
-%In addition, the vacuum chamber is too small vertically to accommodate 90-degree stereo layers to optimize the vertex resolution in the horizontal coordinate. Instead, 
-100~mrad stereo is used in the first three layers to provide higher-resolution 3D space points for vertexing.
-50~mrad stereo in the last two layers breaks the tracking degeneracy of having five identical layers and minimizes fakes from ghost hits,
-improving pattern recognition while still providing sufficient pointing resolution into the third layer for robust hit association in the denser environment there.
-Altogether, this layout comprises 20 sensors and hybrids and 100 APV25 chips for a total of 12780 readout channels.
+The layout of the SVT is summarized in Tab.~\ref{tab:trk} and rendered in Fig.~\ref{fig:tracker_model}. 
+Each of the layers is comprised of a pair of closely-spaced silicon microstrip sensors mounted back-
+to-back to form a module. A 100~mrad stereo angle is used in the first three layers to provide higher-
+resolution 3D space points for vertexing.  Using 50~mrad in the last two layers breaks the tracking 
+degeneracy of having five identical layers and minimizes fakes from ghost hits to improve pattern 
+recognition. Altogether, this layout comprises 20 sensors and hybrids and 100 APV25 chips for a 
+total of 12780 readout channels. 
 %=======================
@@
 \end{tabular}
-\caption{\small Layout of the HPS Test SVT.}
+\caption{\small Layout of the SVT.}
 }
@@
 \includegraphics[width=7cm]{figures/HPS_nochamber}
-\caption{\small A rendering of the HPS Test SVT showing the modules on their support plates held by the 
-hinged C-support on the left and the motion levers on the right. The sensors are shown in red and the hybrid 
-readout boards in green. The beam enters from the right through a vacuum box with flanges for services. }
+\caption{\small A rendering of the SVT showing the modules on their support plates held by the 
+hinged C-support on the left and the motion levers on the right. The sensors are shown in red and the 
+hybrid readout boards in green. The beam enters from the right through a vacuum box with flanges 
+for services. }
 \label{fig:tracker_model}
@@
 %=======================
-The SVT is built in two separate halves that are mirror reflections of one another about the plane of the 
-nominal electron beam.  Each half consists of five, double-sided modules mounted on a support plate that 
-provides services to the modules and allows them to be moved as a group relative to the dead zone. The 
-two halves of the tracker are connected to hinges mounted on a C-shaped support just beyond the last layer t
-that defines the nominal spacing between the upper and lower halves of the tracker.  A shaft attached to each 
-support plate in front of layer 1 extends upstream and connects to a linear shift that transfers motion into the 
-vacuum box through bellows to open and close the two halves around the dead zone. The C-support is 
-mounted to an aluminum baseplate that defines the position of the SVT with respect to the vacuum 
-chamber. Figure~\ref{fig:tracker_halves} shows a photograph of both completed detector halves prior to 
-final assembly. 
+The SVT is built in two separate halves that are mirror reflections of one another about the plane of 
+the nominal electron beam.  Each half consists of five modules mounted on a support plate that 
+provides services to the modules and allows them to be moved as a group relative to the dead zone. 
+The two halves of the tracker are connected to hinges mounted on a C-shaped support just beyond 
+the last layer that defines the nominal spacing between the upper and lower halves of the tracker.  A 
+shaft attached to each support plate in front of layer 1 extends upstream and connects to a linear shift 
+that transfers motion into the vacuum box through bellows to open and close the two halves around 
+the dead zone. The C-support is mounted to an aluminum baseplate that defines the position of the 
+SVT with respect to the vacuum chamber. Figure~\ref{fig:tracker_halves} shows a photograph of both 
+completed detector halves prior to final assembly. 
 %=======================
@@
 \end{center}
-\vspace*{-5mm}
+%\vspace*{-5mm}
 \end{figure}
@@
 \subsection{Components}
-
-%\subsubsection{Silicon Sensors}
 The sensors for the SVT are selected according to a number of requirements.  First, the sensors must be 
@@
 between the photon and electron beam setup. 
-\begin{figure}[ht]
-\includegraphics[ width=7cm]{figures/photon_vs_electron_beam_schematic.png}
-\caption{\small{Schematic comparison of HPS Test run photon beam compared to the HPS electron beam.}}\label{fig:schematic_testrun_vs_erun}
-\end{figure}
 The angular distribution of the pair produced electron and positron emerging 

### 2014-03-08 hps-testrun-nim.tex
Shrinking the rest of the SVT sections: components, svt daq, assembly and alignment

@@
 degeneracy of having five identical layers and minimizes fakes from ghost hits to improve pattern 
-recognition. Altogether, this layout comprises 20 sensors and hybrids and 100 APV25 chips for a 
-total of 12780 readout channels. 
+recognition. Altogether, the SVTcomprises 20 sensors for a total of 12780 readout channels. 
 %=======================
@@
 \subsection{Components}
-The sensors for the SVT are selected according to a number of requirements.  First, the sensors must be 
-radiation tolerant to approximately $1.5\times10^{14}$~\fluenceunit{} for a six month run.  This 
-corresponds to about 4~MHz/mm$^2$, so the sensor and readout technology must be capable of handling 
-very high local occupancies. Since sensitivity is limited by multiple scattering, a material budget of less 
-than 1\% $X_0$/layer is imperative and far less is desirable. To achieve the required vertex resolution  
-single-hit resolutions better than XXXX~$\mu$m are required. Finally, the sensor technology must 
-be mature and readily available at low cost.  Silicon microstrips are the best match to these requirements, and 
-a supply of appropriate microstrip sensors purchased from the Hamamatsu Photonics Corporation for the 
-Run 2b upgrade of the D\O experiment~\cite{Denisov:2001aa} are readily available. 
-These are $p+$-on-$n$, single sided, AC coupled, 
-polysilicon-biased sensors fabricated on $<100>$ silicon and have 30 (60) micron sense (readout) pitch 
-over their $4\times10$~cm$^2$ surface. Although a maximum bias of 350~V is specified, the vast majority are 
-operable to 1000~V and therefore remain fully depleted to a dose of approximately 
-$1.5\times10^{14}$~\fluenceunit{}.
+The sensors for the SVT are $p+$-on-$n$, single sided, AC coupled, polysilicon-biased microstrip 
+sensors fabricated on $<100>$ silicon and have 30 (60) micron sense (readout) pitch over their 
+$4\times10$~cm$^2$ surface. This sensor technology was selected to match the requirement of 
+a $<1$\% $X_0$ per layer, single-hit resolution better than 50~$\mu$m and tolerant of a radiation 
+dose of approximately $1.5\times10^{14}$~\fluenceunit{} for a six month run. The sensors 
+were purchased from the Hamamatsu Photonics Corporation for the cancelled 
+Run 2b upgrade of the D\O~experiment~\cite{Denisov:2001aa} which satisfied the requirement that 
+the technology must be mature and available within the time and budget constraints.
 
 %\subsubsection{Front-end Electronics}
-Because the regions of high occupancy are small spots in two dimensions, only a short length of any one 
-strip see a significant occupancy, and the strips in that region act as long pixels. However, the rates are still 
-very high and lowering the peak occupancy in the sensors to approximately 1\% for tracking requires a 
-trigger window and tagging of hit times to roughly 8~ns.  The FADC 
-readout for the ECal and muon system are capable of this (see Sec.~\ref{sec:fadc}), but achieving 
-$2\sigma$ efficiency for 
-silicon hits then requires 2~ns time resolution for the hits in the SVT. This performance can be achieved with 
-the APV25 readout ASIC developed for the CMS experiment at CERN~\cite{French:2001xb}.  When 
-operated in ``multi-peak mode", the APV25 captures successive samples of the output of the shaper in sets 
-of three at a sampling rate of approximately 40~MHz.  
-By fitting the known $CR$-$RC$ shaping curve to these samples, the initial time of the hit can be 
-determined to a precision of 2~ns for S/N$>25$, an achievable figure with our sensors if read out 
-individually~\cite{Friedl:2009zz}.  For the SVT, six-sample readout and the shortest possible shaping time 
-(35~ns) will be used to best distinguish hits that overlap in time.
-The APV25 ASICs are hosted on simple FR4 hybrids since these hybrids and their cooling system are 
-outside the tracking volume.  Along with the sensors, these are assembled into half-modules, one for each 
-tracking view, with a short cable pigtail to provide power and configuration to the modules and signal 
-readout.
-
-%\subsubsection{Support Structure and Cooling}
-
-The sensor modules for the SVT consist of a pair of identical half-modules, sandwiched back-to-back around 
-an aluminum cooling block at one end and a similar PEEK spacer block at the other. 
+Despite having only small spots with very high occupancy (up to 4~MHz/mm$^2$) closest to the primary 
+beam, see Fig.~\ref{fig:radiation}, the rates are still high and lowering the peak occupancy to 
+approximately 1\% for tracking requires a trigger window and hit time tagging of roughly 8~ns. The 
+ECal readout and trigger described in Sec.~\ref{sec:fadc} can achieve such resolution. To reach this 
+performance the sensors for the SVT are readout by the APV25 ASIC developed for the CMS 
+experiment at CERN~\cite{French:2001xb}. The APV25 can capture two successive samples of three 
+of the output of the shaper at a sampling rate of approximately 40~MHz.  By fitting the known 
+$CR$-$RC$ shaping curve to these samples, the initial time of the hit can be determined to a precision 
+of 2~ns for S/N$\approx25$~\cite{Friedl:2009zz}.  For electron beam running, six-sample readout and 
+the shortest possible shaping time (35~ns) is used to best distinguish hits that overlap in time.
+The APV25 ASICs are hosted on simple FR4 hybrid readout boards, outside the tracking volume, with a 
+short twisted-pair pigtail cable to provide power and configuration and signal readout. Along with a 
+single sensor, these are glued to a polyamide-laminated carbon fiber composite backing making 
+up a half-module. A window is machined in the carbon fiber leaving only a frame around the periphery 
+of the silicon to minimize material. A 50~$\mu$m sheet of polyamide is laminated to the surface of the 
+carbon fiber with 1~mm overhang at all openings to ensure good isolation between the backside of the 
+sensor, carrying high-voltage bias, and the carbon fiber which is held near ground.
+
+The sensor modules for the SVT consist of a pair of identical half-modules, sandwiched back-to-back 
+around an aluminum cooling block at one end and a similar PEEK spacer block at the other. 
 Figure~\ref{fig:tracker_module} shows a single module after assembly.
@@
 The cooling block provides the primary mechanical support for the module as well as cooling via copper 
-tubes pressed into grooves in the plates. The spacer block defines the spacing between the sensors at the 
-far end of the module, stiffens the module structure, and improves the stability of the sensor alignments.
-
-The total power consumption of the five APV25 chips mounted on 
-the hybrid readout board is about 2~W. Since heating from the leakage current is only significant at a 
-single small spot on the sensor, the 
-dominant heat load on the sensor, even after irradiation, is radiant heat from the inside wall of the vacuum 
-chamber, less than 0.5~W per sensor. The total power consumption budget of about 40~W is removed by a 
-water/glycol mixture circulated through a flexible manifold attached to the cupper tubes in the cooling blocks. 
-During the Test run the sensors where operated at around $23^{\circ}$C with a total mass flow of 
-about XXXXg/s.
-
-Each half module consists of a single sensor and a hybrid electronic readout board glued to a 
-polyamide-laminated carbon fiber composite backing.  A window is machined in the carbon fiber leaving 
-only a frame 
-around the periphery of the silicon to minimize material. A 50~$\mu$m sheet of polyamide is laminated to 
-the surface of the carbon fiber with 1 mm overhang at all openings to ensure good isolation between the 
-backside of the sensor, carrying high-voltage bias, and the carbon fiber which is held near ground.  The 
-average support material in the tracking volume is approximately 0.06\% $X_{0}$ per double-sided module 
-for a total material budget of 0.7\% per layer.
+tubes pressed into grooves in the plates. The spacer block defines the spacing between the sensors at 
+the far end of the module, stiffens the module structure, and improves the stability of the sensor 
+alignment.  The average support material in the tracking volume is approximately 0.06\% $X_{0}$ per 
+double-sided module for a total material budget of 0.7\% per layer.
+
+The total SVT power consumption budget of about 50~W is removed by a water/glycol mixture 
+circulated through a flexible manifold attached to the copper tubes in the cooling blocks. During the Test 
+run the sensors where operated at around $23^{\circ}$C. The power consumption is dominated by five 
+APV25 ASICs on each hybrid board consuming approximately 2~W, radiant heat load is less than 
+0.5~W per sensor and leakage current is only significant in a small spot after irradiation.
 
@@
 \label{sec:svt_daq}
-The SVT data acquisition (DAQ) based on the Reconfigurable Cluster Element (RCE) and Cluster 
-Interconnect (CI) concept developed at SLAC as generic building blocks for DAQ systems in high energy 
-physics. The RCE is a generic computational building block, housed on a separate daughter card called 
+The SVT data acquisition (DAQ) is based on the Reconfigurable Cluster Element (RCE) and cluster 
+interconnect concept developed at SLAC as generic building blocks for DAQ systems. 
+The RCE is a generic computational building block, housed on a separate daughter card called 
 Data Processing Module (DPM), that are realized on an ATCA front board called the Cluster On Board 
@@
 	\includegraphics[width=6cm]{figures/svt_daq_module}
-	\caption{Picture of the SVT DAQ COB board with four data processing daughter cards visible.}
+	\caption{The SVT DAQ COB board with four data processing daughter cards visible on the left side.}
 	\label{fig:cob}
@@
 \end{figure}
-The Gen-I RCE used in the Test run consisted of a Virtex~5 FPGA with 1~GB of DDR3 RAM. 
-The outputs of 12 SVT half-modules are digitized on the Rear-Transition-Module (RTM), a custom board on the back side of the ATCA crate, interfacing the HPS readout to the generic DAQ components on the COB.
-A pre-amplifier converts the APV25 differential current output to a different voltage output scaled to the sensitive 
-range of a 14-bit ADC operating at the system clock of 41.667~MHz. 
-The RTM is organized into four sections with each section supporting three SVT half-module hybrids (15 
-APV25 channels). The RTM also includes a 4-channel Fiber Optic module and supporting logic which can be 
-used to interface to the JLab trigger system supervisor.
-Each section of the RTM, up to three hybrids, is input to a DPM which apply thresholds for data reduction and 
-organizes the sample data into UDP datagrams. The DPM also hosts an I2C controller used to configure and 
-monitor the APV25 chips on those three hybrids. A single ATCA crate with two COB cards was used, one 
-supporting four DPMs and one supporting 3 DPMs and one DPM that is configured as the trigger and data 
-transmission module. The two COB cards and their DPMs are interconnected with a 10Gb/s switch 
-card~\cite{Larsen:2011zb} which 
-also hosts two 1Gb/s Ethernet interfaces to the external SVT DAQ PC.
-
-The external PC supports three network interfaces; two standard 1Gb/s Ethernet and one custom low latency 
-data reception card. The first Ethernet interface is used for slow control and monitoring of the 8 DPM modules. 
-The second Ethernet interface serves as the interface to the JLAB data acquisition system. The third custom low 
-latency network interface is used to receive data from the SVT ATCA crate and supports a low latency, reliable 
-TTL trigger acknowledge interface to the trigger DPM. This PC hosts the SVT control and monitoring software 
-as well as the JLab read out controller (ROC) application described in more detail in Sec.~\ref{sec:daq}.
-
-This system is capable of operating up to 20~kHz and XXXX~MB/s which is well in line with the rates 
-expected and observed during the HPS Test run.
+The first generation RCE used in the Test run consisted of a Virtex~5 FPGA with 1~GB of DDR3 RAM. 
+A schematic overview of the system is shown in Fig.~\ref{fig:svtdaq}. 
+ \begin{figure}[]
+\begin{center}
+{\small
+	\includegraphics[width=6cm]{figures/svt_daq_module}
+	\caption{Block diagram overview of the SVT DAQ.}
+	\label{fig:svtdaq}
+}
+\end{center}
+\end{figure}
+The outputs of 12 SVT half-modules are digitized on the Rear-Transition-Module (RTM), a custom board 
+on the back side of the ATCA crate, interfacing the HPS readout to the generic DAQ components on the 
+COB. A pre-amplifier converts the APV25 differential current output to a different voltage output scaled to 
+the sensitive range of a 14-bit ADC operating at the system clock of 41.667~MHz. The RTM is organized 
+into four sections with each section supporting three SVT half-module hybrids (15 APV25 ASICs). The 
+RTM also includes a 4-channel fiber optic module and supporting logic which is used to interface 
+to the JLab trigger system supervisor. Each section of the RTM is input to a DPM which apply thresholds 
+for data reduction and organizes the sample data into UDP datagrams. The DPM also hosts an I$^{2}$C 
+controller used to configure and monitor the APV25 ASICs. A single ATCA crate with two COB cards 
+was used, one supporting four DPMs and one supporting 3 DPMs and one DPM that is configured as 
+the trigger and data transmission module. The two COB cards and their DPMs are interconnected with a 
+10Gb/s switch card~\cite{Larsen:2011zb} which also hosts two 1Gb/s Ethernet interfaces to the external 
+SVT DAQ PC.
+
+The external PC supports three network interfaces; two standard 1Gb/s Ethernet and one custom low 
+latency data reception card. The first is used for slow control and monitoring of the 8 
+DPM modules and the second serves as the interface to the JLAB data acquisition system. The third 
+custom low latency network interface is used to receive data from the ATCA crate and supports a low 
+latency, reliable TTL trigger acknowledge interface to the trigger DPM. This PC hosts the SVT control 
+and monitoring software as well as the JLab Read Out Controller (ROC) application described in more 
+detail in Sec.~\ref{sec:daq}.
+
+While trigger rates during the Test run was significantly lower this system was tested at trigger rates up 
+to 20~kHz and 50~MB/s.
 
@@
 
-%Hybrid readout boards and half-modules were assembled at SLAC.  Mounting APV25 chips and all wirebonding and QA testing were performed at University of California, Santa Cruz.
-
-Of the sensors tested during production, 90\% were capable of 1000~V bias voltage without breakdown. 
-Hybrids underwent quick QA testing and each half-module was run at low temperature ($\approx5^{\circ}$ C) and 
-fully characterized for pedestals, gains, noise and time response after assembly.  
-%All 29 production modules were assembled between mid-February and the end of March, 2012.
-Module yields were excellent for such a small production.
-Of 165 APV chips acquired, 150 were used to assemble 30 production hybrids, of which 29 passed QA testing.
-Of 29 half-modules built, 28 passed 
-QA testing, leaving 8 spare modules after completion of the SVT.  Full-module assembly and 
-mechanical surveys were performed at SLAC
-% in early April 2012 
-before final assembly, testing and shipping of the SVT to JLab
-% on April 11.  
-A custom shipping container with nested crates and redundant isolation for shock and vibration 
-%, based on experience from FNAL~\cite{shipping},
-was built in order to safely send the partly assembled SVT to JLab. 
-% The two fully assembled SVT halves were attached to a baseplate supported by four wire-rope isolators.
-This plate, covered by a lexan cover for cleanliness, was mounted inside an inner box surrounded by 4 inches of Polyurethane foam to complete the two-spring construction.
-At JLab, the entire SVT was integrated with the full DAQ and the power supplies 
-%for the first time in the clean room, 
-before moving the module-loaded support plates to Hall~B for final mechanical assembly and installation inside of the 
-vacuum chamber.
-% on April 19, 2012.
+%Of the sensors tested during production, 90\% were capable of 1000~V bias voltage without breakdown. 
+Hybrids with APV25 ASICs underwent quick qualification testing and each half-module was run at low 
+temperature ($\approx5^{\circ}$ C) and fully characterized for pedestals, gains, noise and time response 
+after assembly.  Of 29 half-modules built, 28 passed qualification testing, leaving 8 spare modules after 
+completion of the SVT, all capable of 1000~V bias voltage without breakdown.  Full-module assembly 
+and mechanical surveys were performed at SLAC before final assembly, testing and shipping of the 
+SVT to JLab. A custom shipping container with nested crates and redundant isolation for shock and 
+vibration was built in order to safely send the partly assembled SVT to JLab. At JLab, the entire SVT was 
+integrated with the full DAQ and the power supplies before moving the module-loaded support plates to 
+Hall B for final mechanical assembly and installation inside of the vacuum chamber.
 
 \subsection{Alignment}
-The SVT was aligned using a combination of optical, laser and touch probe surveys at SLAC and JLab. The 
-optical survey of individual modules with precision of a few $\mu$m are combined with a touch-probe survey 
-of the overall SVT support structure, with 25-100~$\mu$m precision, to locate the silicon sensor layers with 
-respect to the support plates and the mechanical survey balls on the base plate.
-After full assembly and installation of the SVT at JLab, a mechanical survey of the SVT base plate position 
-inside the pair spectrometer vacuum chamber is used to determine the global position of the SVT with 
-respect to CEBAF beam line. 
-The resulting survey-based alignment has the position of the silicon sensors correct to within a few hundred 
-microns. A more sophisticated global track-based alignment technique to reach the final alignment precision 
-is being developed.
+The SVT was aligned using a combination of optical, laser and touch probe surveys at SLAC and JLab. 
+The optical survey of individual modules with precision of a few $\mu$m are combined with a 
+touch-probe survey of the overall SVT support structure, with 25-100~$\mu$m precision, to locate the 
+silicon sensor layers with respect to the support plates and the mechanical survey balls on the base 
+plate. After full assembly and installation of the SVT at JLab, a mechanical survey of the SVT base plate 
+position inside the pair spectrometer vacuum chamber is used to determine the global position of the 
+SVT with respect to CEBAF beam line. The resulting survey-based alignment has the position of the 
+silicon sensors correct to within a few hundred microns measured from tracks in the Test run data. 
+A more sophisticated global track-based alignment technique to reach final alignment precision 
+well below 50~$\mu$m is being developed.
 
@@
 It is fast, able to readout at rates comparable to those in the tracker, and able to provide good spatial and energy information to the trigger electronics.
-Like the tracker, the electromagnetic calorimeter is split to avoid impinging on the “dead zone”.
+Like the tracker, the electromagnetic calorimeter is split to avoid impinging on the Òdead zoneÓ.
 The beam and radiative secondaries pass between the two of the calorimeter in vacuum, to avoid generating unnecessary backgrounds.
@@
 
-Like the tracker, the electromagnetic calorimeter is split into two parts, beam-up and beam-down, to avoid impinging on the “dead zone”.
+Like the tracker, the electromagnetic calorimeter is split into two parts, beam-up and beam-down, to avoid impinging on the Òdead zoneÓ.
 The two parts of the Ecal are separated by a vacuum chamber, see Fig.~\ref{fig:ecal}.

### 2014-03-09 hps-testrun-nim.tex
Rewriting ECal section.

@@
 
-The electromagnetic calorimeter, installed downstream of the tracker, performs two essential functions for the experiment: provides a trigger to DAQ system and 
-is used in the analysis for electron identification. 
-%The device is highly segmented.
-It is fast, able to readout at rates comparable to those in the tracker, and able to provide good spatial and energy information to the trigger electronics.
-Like the tracker, the electromagnetic calorimeter is split to avoid impinging on the Òdead zoneÓ.
-The beam and radiative secondaries pass between the two of the calorimeter in vacuum, to avoid generating unnecessary backgrounds.
-%Step\subsection{Purpose and Design Requirements}
-%StepThe electromagnetic calorimeter (ECal) provide the trigger for the data acquisition and will be used for electron identification during the data analysis.
-The ECal is positioned after the analyzing dipole magnet and cover the full acceptance region of the SVT.
-It consist of two halves, split in the horizontal beam plane.
-The gap between upper and lower parts, $XXXX$~mrad (15mrad for electron running),  as seen from the target location, is necessary to avoid the "dead zone" where occupancy and radiation prevents any instrumentation to be situated.
-The energy of electrons of interest in HPS experiment will be in the range 
-$0.5-6.5$~GeV. The ECal modules must have sufficient radiation lengths to absorb the full energy of these 
-scattered electrons, have fine enough granularity to handle a high rate of electromagnetic 
-background and survive large doses of radiation, especially near the beam plane. In addition, it needs to 
-have excellent hit time resolution, $<10$~ns, in order to beat down beam backgrounds.
-
-Requirements of a compact design, operation at high radiation and high rate environment, in the presence of a 
-high magnetic field are fulfilled by a lead-tungstate (PbWO$_{4}$) crystal calorimeter with magnetic field 
-resistant Avalanche Photodiode (APD) readout.  Such calorimeter has been operational in the inner 
-part of the CLAS detector for experiments in Hall-B at JLab since 2005 and meet all requirements set by 
-HPS. The modules from this calorimeter have been subsequently repurposed for the ECal.
+The electromagnetic calorimeter (ECal), installed downstream of the PS dipole magnet, performs two 
+essential 
+functions for the experiment: it provides a trigger signal to select what events to read out from the 
+detector sub-systems and is used in the analysis to identify electrons and positrons. 
+The technology and design choices are largely driven by the need for a compact forward design 
+covering the SVT \Aprime acceptance and able to fully absorb 
+electrons and positrons with energy between $0.5$-$6.5$~GeV, fine granularity and signal 
+readout speed to handle 1~MHz/cm$^{2}$ of electromagnetic background and remain operable 
+after a radiation dose larger than $X$~MRad. The lead-tungstate (PbOW$_{4}$) crystal inner 
+calorimeter of the CLAS detector [REFERENCE] in operation since 2005 in Hall B meet all the 
+requirements set by HPS. The modules from this calorimeter have been subsequently repurposed for 
+HPS.
 
@@
 
-%Step\subsubsection{PbWO$_4$ Crystals}
-The HPS test run ECal uses PbWO$_{4}$ crystals, APDs, and preamplifier boards from the inner calorimeter (IC) of the CLAS detector\cite{2008erhm.conf..421N}.
-In Figure~\ref{fig:ecal-module} a schematic view of the module assembly is shown.
-Lead-tungstate crystals are $160$ mm long and are tapered with front face of $13.3\times13.3$~mm$^2$, tapered to $16\times16$~mm$^2$ at the rear face.
-The crystals were fabricated with very tight tolerances: $19~\mu$m for 13.3~mm dimension and $13~\mu$m for the 16~mm dimension.
-Each crystal is wrapped in VM2000 multilayer polymer mirror film.
-The APDs (Hamamatsu S8664-55) with $5\times5$~mm$^2$ active area and $75\%$ quantum efficiency were glued on the rear face of the crystals using MeltMount 1.7 thermal plastic adhesive.
-The low gain of APDs ($\sim 200$) was compensated with custom made preamplifier boards, which provide factor 2000 amplification of the ADP signal.
+The ECal module shown in Fig.~\ref{fig:ecal-module} is based on a tapered 160~mm long 
+lead-tungstate (PbWO$_{4}$) crystal with a $13.3\times13.3$~mm$^2$ ($16\times16$~mm$^2$) front 
+(rear) face wrapped in VM2000 multilayer polymer mirror film. 
 \begin{figure}[]
@@
 \end{figure}
+The scintillation light, approximately $X$ photoelectrons/MeV, is readout by a 
+5$\times$5~mm$^2$ Hamamatsu S8664-55 Avalanche Photodiode (APD) with 75\% quantum 
+efficiency glued to the rear face surface using MeltMount 1.7 thermal plastic adhesive. 
+The low gain of APDs ($\sim 200$) was compensated with custom made preamplifier boards, which 
+provide factor of 2000 amplification of the APD signal.
 
 \subsection{Layout}
-
-Like the tracker, the electromagnetic calorimeter is split into two parts, beam-up and beam-down, to avoid impinging on the Òdead zoneÓ.
-The two parts of the Ecal are separated by a vacuum chamber, see Fig.~\ref{fig:ecal}.
-The beam and radiative secondaries pass between the two parts in vacuum, to avoid generating unnecessary backgrounds.
-The crystal modules in each part are arranged in rectangular formation, as shown in top panel of Fig.~\ref{fig:ecal}.
-There are 5 layers in each formation.
-Each layer has $46$ crystals except for the layers closest to the beam
-plane where 9 modules were removed to allow a larger opening for the outgoing electron and photon beams. 
-In order to have stable light yield from crystals, and stable operation of APDs and preamplifiers, the module assembly of each ECal part was enclosed inside a temperature controlled box.
-
-Inside the box PbWO$_{4}$ crystals were supported by aluminum frames stacked on top of each other.
-The bias voltage for APDs ($\sim 400$ V), the low voltage for preamplifiers ($\pm 5$ V), and the signals from APDs were transmitted in and out of the enclosure through a backplane called motherboard.
-The $221$ modules in each part of the ECal were divided into two low voltage groups and 12 bias voltage groups.
-Modules in bias voltage groups were selected to have gain uniformity of $\sim 20\%$.
-
-During the test run ECal was mounted downstream of the analyzing dipole magnet at the distance of about $147$~cm from the 
-upstream edge of the magnet. 
-%The two ECal modules are positioned just above and below the ECal vacuum chamber as shown in bottom panel of Fig.~\ref{fig:ecal}. 
-%The primary electron beam, scattered electrons and bremsstrahlung photons pass through the system in vacuum. 
-The gap between innermost edge of the crystals of two parts was $7.4$~cm, centered on the beam plane.
-The temperature stability of the system during the test run was better than $1^\circ~$F, the temperature uniformity inside the box was better than  $4^\circ~$F.
+Similar to the SVT, the ECal is built in two separate halves that are mirror reflections of one another 
+about the plane of the nominal electron beam to avoid interfering with the 15~mrad "dead zone". 
+As shown in Fig.~\ref{fig:ecal}, the 221 modules, supported by aluminum support frames, in each half 
+are arranged in rectangular formation with 5 layers and 46 crystals/layer except for the layer closest to 
+the beam where 9 modules were removed to allow a larger opening for the outgoing electron and 
+photon beams. Each half was enclosed in a temperature controlled box ($<1^{\circ}$~F stability and 
+$<4^{\circ}$~F uniformity) to stabilize the crystal light yield and the operation of the APDs and its 
+preamplifiers. Four printed circuit boards mounted on the backplane penetrated the enclosure and was 
+used to supply the $\pm 5$~V 
+operating voltage for the preamplifiers and the 400~V bias voltage to the APDs and to read out signals 
+from the APDs. Each half of the ECal was divided into 12 bias voltage groups with a gain uniformity 
+of about 20\%.
+
+During the Test run, both halves were held in place by four vertical bars attached to an above rail, 
+placing the front face of the crystals 147~cm from the upstream edge of the magnet and with a 
+8.7~cm gap between the innermost edge of the crystals in the two halves.
 \begin{center}
@@
 \includegraphics[width=0.45\textwidth]{figures/ecal_picture_beamline}
-%\includegraphics[width=7cm]{figures/ecal_vacuumchamber.pdf}
-%\includegraphics[width=7cm]{figures/ecal_assembly}
-\caption{Layout of PbWO$_{4}$ modules in two halves of the ECal (left) and the ECal assembly on the beam line (right). }
+\caption{Rendered layout view (left) and the ECal assembly on the beam line (right).}
 \label{fig:ecal}
@@
 \end{center}
-%Step \subsubsection{Support Structure}
-%Step In order to stabilize the calorimeter's performance, the crystals, APDs, and amplifiers are enclosed within a temperature controlled environment, held constant at the level of .
-%Step\subsubsection{Avalanche Photodiode Readout and Preamplifiers}
-%Step\label{sec:apd}
-%StepAvalanche Photodiodes (APD) S8664-55 produced by Hamamatsu Corp.
-are used as photodetectors.
-They have a $5\times5$~mm$^2$ active area and quantum efficiency of about 75\%.
-Single APDs were centered on the back ends of the crystals using MeltMount 1.7 thermal plastic adhesive.
-The low?
-amplitude signals of APDs are amplified using custom?made preamplifier boards.
-%The gain uniformity of the APDs is on the order of XXXX\%; with APD high voltage bias varying by as much as 100V.
-Since only a limited number of high voltage channels were available during the test, 10 channels were grouped together with an attempt to group modules with similar gains.
 
@@
 \label{sec:fadc}
-
-ECal signal readout was organized as follows: the amplified APD signal from the motherboard is sent to a $2:1$ signal splitter.
-After the split, 2/3 of the signal is sent a discriminator then to a Time-to-Digital
-Converter (TDC). The 1/3 of the signal is fed to a single channel of 16-channel JLAB Flash Amplitude-to-Digital Converter (FADC250), see Fig.\ref{fig:fadc} \cite{fadc}.  
-\begin{figure}[t]
+After a 2:1 signal splitter, $1/3$ of an amplified APD signal ($2/3$ is sent to a timing module) is fed to a 
+single channel of a JLab flash ADC (FADC) board~\cite{fadc}, 
+see Fig~.\ref{fig:fadc}.
+\begin{figure}[]
 \begin{center}
@@
 \includegraphics[width=5cm]{figures/FADC250_Photo_001.jpg}
-\caption{A Jefferson Lab FADC250 VXS module.}
+\caption{The JLab FADC250 VXS module.}
 \label{fig:fadc}
@@
 \end{figure}
-Two 20-slot VXS crates with 14 (for top ECal) and 13 (for bottom ECal) FADC bards were employed for the test run.
-
-The FADCs store 12-bit digitized samples at 250~MHz in 8~$\mu$s deep pipelines. 
-When a trigger is received, the appropriate part of the pipeline is accessed for the readout. HPS used 
-FADCs in the integration mode. A predefined number of samples of the signal that exceeds a predefined 
-threshold have been summed and stored in 17-bit register for readout. The number of samples for 
-integration was defined by two parameters that could be set separately, the number of samples 
-integrated before the signal crossed threshold ($NSB$) and  the number of samples integrated after the 
-signal crossed threshold ($NSA$), see Fig.\ref{fig:hps_trigger_data}. 
+The FADC boards are high speed VXS modules digitizing up to 16 APD signals 
+at 250~MHz and storing samples in 8~$\mu$s deep pipelines with 12-bit resolution. 
+When a trigger is received, the part 
+of the pipeline from 5 samples before and 30 after the signal crossed $\approx70$~MeV threshold are 
+summed and stored in a 17-bit register for readout as described in Fig.~\ref{fig:hps_trigger_data}.
+This scheme significantly compresses the data output of the FADC. During offline data analysis, a 
+calibrated pedestal value is subtracted to obtain the actual summed energy.
+Two 20-slot VXS crates with 14 (13) FADC boards were employed in the Test run to read out the top 
+(bottom) half of the ECal.
+In the Test run 385 out of 442 modules (87\%) was used in offline reconstruction, 39 modules were 
+disabled or not read out (no FADC channel available, no APD bias voltage or masked out due to 
+excessive noise) and 18 was masked offline due to noise. 
 \begin{figure}[]
@@
 \includegraphics[width=7cm]{figures/fadc_datapath_diagram.png}
-\caption{\small{FADC data paths.}}
+\caption{The two different readout modes of the FADC used in the Test run.}
 \label{fig:hps_trigger_data}
@@
 \end{figure}
-This scheme significantly compresses the data input to the FADC. During data analysis, a pedestal 
-value is subtracted to obtain the actual summed energy.
-
-For various reasons only 385 out of 442 modules (87\%) were operational during the test run. The 
-readout threshold was set to $70$ MeV, the number of samples before and after the threshold crossing 
-were 5 and 30, respectively.
 

### 2014-03-10 hps-testrun-nim.tex
Simplified the trigger section and moved the SVT DAQ subsection to the DAQ section.

@@
 
-\subsection{Digitization, Event Building and Data Transmission}
-\label{sec:svt_daq}
-The SVT data acquisition (DAQ) is based on the Reconfigurable Cluster Element (RCE) and cluster 
-interconnect concept developed at SLAC as generic building blocks for DAQ systems. 
-The RCE is a generic computational building block, housed on a separate daughter card called 
-Data Processing Module (DPM), that are realized on an ATCA front board called the Cluster On Board 
-(COB), see Fig.~\ref{fig:cob}.
- \begin{figure}[]
-\begin{center}
-{\small
-	\includegraphics[width=6cm]{figures/svt_daq_module}
-	\caption{The SVT DAQ COB board with four data processing daughter cards visible on the left side.}
-	\label{fig:cob}
-}
-\end{center}
-\end{figure}
-The first generation RCE used in the Test run consisted of a Virtex~5 FPGA with 1~GB of DDR3 RAM. 
-A schematic overview of the system is shown in Fig.~\ref{fig:svtdaq}. 
- \begin{figure}[]
-\begin{center}
-{\small
-	\includegraphics[width=6cm]{figures/svt_daq_module}
-	\caption{Block diagram overview of the SVT DAQ.}
-	\label{fig:svtdaq}
-}
-\end{center}
-\end{figure}
-The outputs of 12 SVT half-modules are digitized on the Rear-Transition-Module (RTM), a custom board 
-on the back side of the ATCA crate, interfacing the HPS readout to the generic DAQ components on the 
-COB. A pre-amplifier converts the APV25 differential current output to a different voltage output scaled to 
-the sensitive range of a 14-bit ADC operating at the system clock of 41.667~MHz. The RTM is organized 
-into four sections with each section supporting three SVT half-module hybrids (15 APV25 ASICs). The 
-RTM also includes a 4-channel fiber optic module and supporting logic which is used to interface 
-to the JLab trigger system supervisor. Each section of the RTM is input to a DPM which apply thresholds 
-for data reduction and organizes the sample data into UDP datagrams. The DPM also hosts an I$^{2}$C 
-controller used to configure and monitor the APV25 ASICs. A single ATCA crate with two COB cards 
-was used, one supporting four DPMs and one supporting 3 DPMs and one DPM that is configured as 
-the trigger and data transmission module. The two COB cards and their DPMs are interconnected with a 
-10Gb/s switch card~\cite{Larsen:2011zb} which also hosts two 1Gb/s Ethernet interfaces to the external 
-SVT DAQ PC.
-
-The external PC supports three network interfaces; two standard 1Gb/s Ethernet and one custom low 
-latency data reception card. The first is used for slow control and monitoring of the 8 
-DPM modules and the second serves as the interface to the JLAB data acquisition system. The third 
-custom low latency network interface is used to receive data from the ATCA crate and supports a low 
-latency, reliable TTL trigger acknowledge interface to the trigger DPM. This PC hosts the SVT control 
-and monitoring software as well as the JLab Read Out Controller (ROC) application described in more 
-detail in Sec.~\ref{sec:daq}.
-
-While trigger rates during the Test run was significantly lower this system was tested at trigger rates up 
-to 20~kHz and 50~MB/s.
-
 \subsection{Production, Assembly and Shipping}
@@
 When a trigger is received, the part 
-of the pipeline from 5 samples before and 30 after the signal crossed $\approx70$~MeV threshold are 
+of the pipeline from 5 samples before and 30 after the signal crossed a programmable 
+threshold (for the Test run this was set to $\approx70$~MeV) are 
 summed and stored in a 17-bit register for readout as described in Fig.~\ref{fig:hps_trigger_data}.
@@
 {\small
-\includegraphics[width=7cm]{figures/fadc_datapath_diagram.png}
+\includegraphics[width=8cm]{figures/fadc_datapath_diagram.png}
 \caption{The two different readout modes of the FADC used in the Test run.}
@@
 
-The HPS Test apparatus DAQ handles the acquisition of data from two sub-detectors: the 
-SVT and the ECal, with two DAQ architectures. The SVT is readout with Advanced 
-Telecom Communications Architecture (ATCA) hardware while the ECal uses VXS based 
-hardware. The trigger system receives input from the ECal and distributes a trigger signal 
-to all detector sub-systems to read out a selected event.
-
+The DAQ system handles acquisition of data from the ECal and SVT sub-detectors  with 
+two DAQ architectures. The SVT DAQ is based on Advanced Telecom Communications Architecture 
+(ATCA) hardware while the ECal uses VXS based hardware. Data from the sub-detectors are only 
+readout when a trigger signal from the trigger system is received formed on input from the ECal. 
 \subsection{Trigger system}
@@
 
-The HPS test run trigger system is designed to select \ee{} events efficiently by 
-using information from the ECal. The trigger looks for time coincidences of clusters in the top and bottom 
-half of the ECal. The trigger system can be broken down into three sections as shown in 
-Fig.~\ref{fig:hps_trigger_cal}:
+The trigger system is designed to select time coincidences of electromagnetic clusters in the 
+top and bottom halves of the ECal. Figure~\ref{fig:hps_trigger_cal} shows a schematic overview 
+of each stage of the system. 
  \begin{figure}[b]
@@
  \end{figure}
- \begin{itemize}
- \item FADC (pulse finding): samples and digitizes the signal pulses from each detector channel. 
-Sends the measured pulse energy and arrival time to the Crate Trigger Processor (CTP),
-\item CTP (cluster finding): groups FADC pulses from each half of the ECal into clusters. 
-The cluster energy and arrival time are sent to the Sub-System Processor (SSP),
- \item SSP (cluster pair finding): searches for time coincidences of pairs of clusters from 
-the top and bottom half of the ECal and applies topological selections.
- \end{itemize}
-
-The time coincidence window of pairs of clusters in the top and bottom half of the ECal are 
-programmable with 4~ns resolution.  As described above, the first stage of the trigger logic is 
-incorporated into the FPGA's on the FADC boards. The trigger  
-integrates using a "time-over-threshold" window as explained in Fig. \ref{fig:hps_trigger_data}.
-For triggering purposes, every channel has: 
-\begin{itemize}
-% \item number of samples integrated before the threshold crossing (NSB),
- %\item number of samples integrated after the  threshold crossing (NSA),
- \item a trigger threshold, measured in ADC counts, 
- \item an offset, 
- \item a conversion factor to convert ADC counts into energy in MeV, from $50$ to $\sim1500$~MeV, with 5-bit accuracy 
- \item an energy threshold discriminator to provide aminimum energy cutoff
- \end{itemize}
-Note that the threshold for the trigger path can be set independently from the readout threshold.
-The offset is subtracted from ADC samples before they are integrated.  
-The values reported to the CTP are the 5-bit pulse energy and the 3-bit time at which the 
-pulse crossed the threshold. Data from every channel is sent to the CTP every 32~ns. With the available 
-3-bit time information, the CTP looks for time coincidences of crystal signals within an 8~ns window (the 
-limit is 4~ns).
-The cluster finding algorithm is fast and makes use of the parallel processing capability of the FPGA's by 
-simultaneously searching for 125 clusters, up to 3x3 in size, across the calorimeter crystal array, and it 
-performs the following tasks:
-\begin{itemize}
-\item Adds together the energy for every 3x3 square of channels in the ECal
-\item Hits are added together if their leading edges occurred within a programmable number of 4~ns 
-clock cycles  (HPS test run used 8~ns coincidence time interval).
-\item If the 3x3 energy sum is larger than the programmable cluster energy threshold and the sum is 
-greater than any neighboring 3x3 windows, the CTP reports the cluster parameters to the SSP. 
-\end{itemize}
-The CTP evaluates all the hits in its half of the calorimeter every 4~ns. A programmable time window is 
-used to allow hits that are slightly out of time with each other to be considered as part of a cluster sum. 
-This is done by reporting hits when they occur and then reporting them again for the next $N$ number of 
-4~ns clock cycles, where $N \in [0,7]$. This is useful to deal with skew and jitter that develop from the 
-detector, cabling, and electronics. As described above, the CTP only selects the 3x3 window with the 
-highest energy sum of its neighbors. This filtering is applied to deal with overlapping clusters and cases 
-where the cluster is larger than a 3x3 window.
-
-The final trigger decision is made by CTPs and the SSP is passed to the Trigger Supervisor (TS). The TS 
-generates all necessary signals and controls the entire DAQ system readout through the Trigger 
-Interface (TI) units. The TI units are installed in every crate that participate in the readout process.
+Each channel on the FADC board have an 
+independent data path to send a 5-bit pulse energy and 3-bit pulse arrival time information to a 
+trigger processing board (CTP) in the same crate every 32~ns. Contrary to the readout path 
+described in Sec.~\ref{sec:fadc}, this energy is a pedestal subtracted time-over-threshold sum with 
+programmable offsets and minimum threshold discriminator for each channel. With input from all 
+FADC channels, i.e. one half of the ECal, the CTP performs cluster finding and calculates cluster 
+energy, shape and timing information. The 3x3 fixed-window, highly parallel, FPGA-based cluster 
+algorithm simultaneously searches for up to 125 clusters with energy sum larger than 
+the programmable energy threshold (in the Test run this was $\approx270$~MeV). Crystals in the 
+fixed-window are included in the sum if the leading edges of the pulses occurred within a 8~ns time 
+window (4~ns minimum). To take into account with clock skew and jitter throughout the system 
+clustering algorithm can allow crystal hits from $N\in[0,7]$ previous or future 4~ns clock cycles to 
+contribute to the cluster sum.  A separate sub-system board (SSP) receives the clusters (only the 
+highest energy 3x3 window to deal with overlapping and very large clusters) from 
+the top and bottom half CTP every 32~ns and searches for pairs of clusters in a 8~ns wide 
+trigger window. The trigger supervisor (TS) generates all the necessary signals and controls the 
+entire DAQ system readout through the trigger interface units installed in every crate that participate 
+in the readout process.
 
@@
 necessary, for example on a `busy' or `full' condition from the front-end electronics. The system is 
-designed to handle trigger rates above 50~kHz and has a latency set to $\approx 3~\mu$s to match that 
-required by the SVT APV25 chip.
-
-During the test run, for the most part the trigger system required only a single cluster in either the top or 
-bottom Ecal module. It was tested to work up to 20 kHz trigger rates.
-
-\subsection{Data Acquisition and Online Computing}
+designed to handle trigger rates above 50~kHz and has a latency set to $\approx 3~\mu$s to match 
+that required by the SVT APV25 ASIC. During the Test run, for the most part the trigger system 
+required only a single cluster in either the top or bottom Ecal halves and tested to above 100~kHz 
+trigger rates with low thresholds.
+
+\subsection{SVT Data Acquisition}
+%igitization, Event Building and Data Transmission}
+\label{sec:svt_daq}
+The SVT DAQ is based on the Reconfigurable Cluster Element (RCE) and cluster 
+interconnect concept developed at SLAC as generic building blocks for DAQ systems. 
+The RCE is a generic computational building block, housed on a separate daughter card called 
+Data Processing Module (DPM), that are realized on an ATCA front board called the Cluster On Board 
+(COB), see Fig.~\ref{fig:cob}.
+ \begin{figure}[]
+\begin{center}
+{\small
+	\includegraphics[width=6cm]{figures/svt_daq_module}
+	\caption{The SVT DAQ COB board with four data processing daughter cards visible on the left side.}
+	\label{fig:cob}
+}
+\end{center}
+\end{figure}
+The first generation RCE used in the Test run consisted of a Virtex~5 FPGA with 1~GB of DDR3 RAM. 
+A schematic overview of the system is shown in Fig.~\ref{fig:svtdaq}. 
+ \begin{figure}[]
+\begin{center}
+{\small
+	\includegraphics[width=6cm]{figures/svt_daq_module}
+	\caption{Block diagram overview of the SVT DAQ.}
+	\label{fig:svtdaq}
+}
+\end{center}
+\end{figure}
+The analog outputs of up to 12 SVT half-modules (60 APV25 ASICs) are digitized on the Rear-Transition-
+Module (RTM), a custom board 
+on the back side of the ATCA crate, interfacing the HPS readout to the generic DAQ components on the 
+COB. A pre-amplifier converts the APV25 differential current output to a different voltage output scaled to 
+the sensitive range of a 14-bit ADC operating at the system clock of 41.667~MHz. The RTM is organized 
+into four sections with each section supporting three SVT half-module hybrids (15 APV25 ASICs). The 
+RTM also includes a 4-channel fiber optic module and supporting logic which is used to interface 
+to the JLab trigger system supervisor. Each section of the RTM is input to a DPM which apply thresholds 
+for data reduction and organizes the sample data into UDP datagrams. The DPM also hosts an I$^{2}$C 
+controller used to configure and monitor the APV25 ASICs. A single ATCA crate with two COB cards 
+was used, one supporting four DPMs and one supporting 3 DPMs and one DPM that is configured as 
+the trigger and data transmission module. The two COB cards and their DPMs are interconnected with a 
+10Gb/s switch card~\cite{Larsen:2011zb} which also hosts two 1Gb/s Ethernet interfaces to the external 
+SVT DAQ PC.
+
+The external PC supports three network interfaces; two standard 1Gb/s Ethernet and one custom low 
+latency data reception card. The first is used for slow control and monitoring of the 8 
+DPM modules and the second serves as the interface to the JLAB data acquisition system. The third 
+custom low latency network interface is used to receive data from the ATCA crate and supports a low 
+latency, reliable TTL trigger acknowledge interface to the trigger DPM. This PC hosts the SVT control 
+and monitoring software as well as the Read Out Controller application used to interface with the 
+JLab DAQ.
+
+While trigger rates during the Test run was significantly lower this system was tested at trigger rates up 
+to 20~kHz and 50~MB/s.
+
+\subsection{General Data Acquisition and Online Computing}
 \label{sec:daq}
-For the ECal, every VXS crate contains a Readout Controller (ROC)
-that collects digitized information, processes it, and sends it on to the Event Builder (EB). The ROC is a 
-single blade Intel-based CPU module running DAQ software under CentOS Linux OS. For the SVT 
-ATCA system, the ROC application runs on an embedded processor situated on the ATCA main board. 
-The EB assembles information from the SVT and ECal ROCs into a single event which is passed to the 
-Event Recorder (ER) that writes it to a RAID5-based data storage system capable of handling up to 
-100~MB/s. The EB and other critical components run on multicore Intel-based multi-CPU servers. The 
-DAQ network system is a network router providing high-speed connections between the DAQ 
-components and the JLab computing facility. The SVT ROC, which must handle large data volumes, has 
-a 10~Gbit/s link to the network router, while a 1~Gbit/s link is adequate for the ECal. A 10~Gbit/s uplink 
-to the JLab computing facility is used for long-term storage.
-
-The SVT DAQ is described in more detail in Sec.~\ref{sec:svt_daq}.
+Every crate participating in the readout process contains a Readout Controller (ROC) that 
+collects digitized information, processes it, and sends it on to the event builder. For the ECal, both 
+VXS crates run ROC applications in a single blade Intel-based CPU module running under CentOS 
+Linux OS. For the SVT DAQ, the ROC application runs on the external PC under RHEL. 
+The event builder assembles information from the ROCs into a single event which is passed to the 
+event recorder that writes it to a RAID5-based data storage system capable of handling up to 
+100~MB/s. The event builder and other critical components run on multicore Intel-based multi-CPU 
+servers. The DAQ network system is a network router providing 10Gbit/s high-speed connection 
+to the JLab computing facility for long-term storage. For the Test run, both the SVT and ECal ROC had a 
+1Gbit/s link to the network router.
 

### 2014-03-10 hps-testrun-nim.tex
Edited the SVT performance section slightly.

@@
 
-During the duration of the test run all SVT modules and APV25 chips were configured to their 
+For the duration of the Test run all SVT modules and APV25 chips were configured to their 
 nominal operating points~\cite{Jones:1069892} with all sensors reverse-biased at 180~V.  The 
-sensors were operated within a temperature range of  $20-24^\circ$C 
-throughout the test run. 
-Throughout the duration of the test run, approximately 97\% of the 12,780 SVT channels were found to
-be operating normally. The fraction of dead or noisy channels varied from 2.4\% to 4.7\%.  
-Most of these were due to misconfigured readout chips (2--4 misconfigured chips out of 100 ), 
-a known noisy half-module and a couple of known noisy readout chips.
+sensors were operated within a temperature range of  $20-24^\circ$C.
+Approximately 97\% of the 12,780 SVT channels were found to
+be operating normally;  the fraction of dead or noisy channels varied from 2.4\% to 4.7\% throughout 
+the Test run. Most of these were due to 2-4 misconfigured APV25 ASICs, a known noisy 
+half-module and a couple of known APV25 ASICs.
 
@@
 
-After a trigger is received, six samples of the corresponding output of the APV25 shaper circuit are digitized. The samples from every channel on a sensor surviving the 
-data reduction algorithm (see Sec.~\ref{sec:svt_daq}) are the basis for offline hit reconstruction. 
-The six samples of the APV25 shaper output 
-are fitted to an ideal $CR-RC$ function to extract the amplitude and the $t_0$ of the hit. 
-The typical pulse shape obtained is shown in Fig.~\ref{fig:pulse_shape} also demonstrates that the SVT 
-was well timed in to the trigger with the rise of the pulse at the 3rd sampling point.
+After a trigger is received, six samples of the corresponding output of the APV25 ASIC shaper circuit are 
+digitized. The six pedestal-subtracted samples from every channel in the SVT are the basis for offline hit 
+reconstruction. The typical pulse shape obtained shown in Fig.~\ref{fig:pulse_shape} also 
+demonstrates that the SVT was well timed in to the trigger with the rise of the pulse at the 3rd sampling 
+point.
 \begin{figure}[]
@@
 	\includegraphics[width=6cm]{figures/run1351_110513_samples_L1_top.pdf}
-	\caption{The six pedestal subtracted samples from individual channels associated with a hit on a 
-	track.}
+	\caption{Accumulation of six pedestal-subtracted samples from individual SVT channels associated 
+	with hits on tracks.}
 	\label{fig:pulse_shape}
@@
 \end{figure}
-
 These hits are passed through a simple clustering algorithm which forms clusters by grouping adjacent 
-strips. The position of a cluster on the sensor is determined by the amplitude-weighted mean.
+strips with the position of a cluster on the sensor determined by the amplitude-weighted mean.
 With a linear gain up to $\approx 3$~MIPs, the cluster charge for hits associated with a track follow 
-the characteristic Landau shape as expected, see Fig.~\ref{fig:cluster_pulse}.  
+the characteristic Landau shape, see Fig.~\ref{fig:cluster_pulse}.  
 A noise level between $1.1-1.5\times 10^{3}$ electrons was established through multiple calibration 
@@
 
-After clustering hits on a sensor, the hit time for each cluster is computed as the amplitude-weighted 
-average of the fitted $t_0$ channel times. The $t_0$-resolution is studied by comparing the cluster hit 
-time with the average of all cluster hit times on the track, the ``track time'', which has the expected jitter 
-due to clock phase and trigger, approximately 25~ns. Figure~\ref{fig:tracktime} shows the residual to the individual cluster 
-times. 
+In order to find the time and amplitude of each hit, $t_0$,  the six samples from each channel are fitted to 
+an ideal $CR-RC$ function. After clustering hits on a sensor, the hit time for each cluster is computed as 
+the amplitude-weighted average of the individually fitted $t_0$ on each channel. The $t_0$-resolution is 
+studied by comparing the cluster hit time with the average of all cluster hit times on the track, 
+see Fig.~\ref{fig:tracktime}, which has the expected jitter due to clock phase and trigger, 
+approximately 25~ns. 
 \begin{figure}[]
@@
 	\caption{
-	The cluster time residual for a representative sensor relative to the track time (see text for more 
-	details). }
+	The residual of individual cluster times with the average of all clusters on the track. }
 	\label{fig:tracktime}
@@
 correlation between the $t_0$ and track time,  the extracted $t_0$ resolution is 2.6~ns. This is somewhat 
-worse than the approximately 2~ns resolution expected which we attribute to the true 
+worse than the approximately 2~ns resolution expected for S/N~25 which we attribute to the true 
 pulse shape differing from our idealized fit function which will be improved in the future. Reducing the 
-APV25 pulse shaping time will also improve time resolution. These results show that we can operate 
-with the six sample readout mode of the APV25 chip and achieve time resolution adequate for pileup 
-rejection during electron running in the HPS experiment.
+APV25 ASIC pulse shaping time will also improve time resolution. 
+These results show that we can operate with the six sample readout mode of the APV25 chip and 
+achieve time resolution adequate for pileup rejection during electron running in HPS.
 
@@
 excluded from the track fit itself. Tracks which intersect regions with known bad channels or very close to 
-in the edge region are excluded in the calculation of the single hit efficiency. The hit efficiency, see 
-Fig.~\ref{fig:hit_efficiency}, was measured to be above 98\% and fairly uniform across the SVT.
+in the edge region are excluded. The hit efficiency, see Fig.~\ref{fig:hit_efficiency}, was measured to be 
+above 98\% and fairly uniform across the SVT.
 \begin{figure}[]
@@
 the charge deposition model in the simulation is validated.  This resolution can be parameterized as a 
-function of the total signal to single-strip noise (S/N) and the crossing angle of tracks through the sensor.  
+function of the total signal to single-strip noise and the crossing angle of tracks through the sensor.  
 The single-hit resolution for charged particles with signal to noise ratio above 20, as demonstrated 
@@
 By selecting \ee{} pairs from the triggered events we are able to study basic distributions of pair 
-production kinematics and in particular those related to our vertex performance. Pairs of opposite charge 
-tracks, one in the top and one in the bottom half of the SVT, with momentum larger than 400~MeV were 
-selected. The pair production kinematics are relatively well reproduced given the alignment of the 
-tracker; Fig.~\ref{fig:pair_kin} shows the invariant mass and ratio of electron momentum over the sum of 
-electron and positron. 
+production kinematics. Pairs of opposite charge tracks, one in the top and one in the bottom half of the 
+SVT, with momentum larger than 400~MeV were selected. The pair production kinematics are relatively 
+well reproduced given the alignment of the tracker as shown in Fig.~\ref{fig:pair_kin}. 
  \begin{center}
@@
 \end{center}
-We estimate the accuracy of the SVT momentum scale and resolution by looking at the agreement 
+The expected momentum resolution from simulation is between 4-5\% 
+for tracks in the momentum range of the Test run. This is significantly smaller than the accuracy at 
+which we're able estimate the scale and resolution in the Test run. By looking at the agreement 
 between data and simulation in the shape of the kinematic distributions for single- and two track 
-events.  By adjusting the overall momentum scale and smearing the simulated events with a 
+events and adjusting the overall momentum scale and smearing simulated events with a 
 Gaussian resolution we estimate an uncertainty of 10\% on both the momentum scale and 
-resolution in the Test run. The expected momentum resolution from simulation is between 4-5\% 
-for tracks in the momentum range of the Test run.
+resolution.
 
 For the vertexing performance the foremost difference compared to electron beam running is that the 
-target was located approximately 67~cm from our nominal target position; giving almost collinear tracks 
-in the detector. This degrades the vertex resolution along the 
-beam line compared to that expected in an electron beam with tracks from the nominal target position. 
+target was located approximately 67~cm upstream from our nominal target position; giving almost 
+collinear tracks in the detector. This degrades the vertex resolution along the 
+beam line compared to that expected in an electron beam with nominal target position. 
 Furthermore, tails of the vertex distributions are impossible to study with the finite data sample obtained 
@@
 approach of the momentum vectors extrapolated in the upstream direction from our analyzing magnet, 
-taking into account the measured fringe field of the PS magnet. 
+taking into account the measured fringe field of the PS dipole magnet. 
  \begin{center}
@@
 	\caption{ Vertex position represented by the distance of closest approach of the extrapolated 
-	momentum vectors upstream of the PS magnet taking into account the measured fringe field. The 
-	overall shift from zero in the x-direction is due to a 30~mrad rotation of the SVT with respect to the 
-	beam line.}
+	momentum vectors upstream of the PS dipole magnet taking into account the measured fringe field. 
+	The overall shift from zero in the x-direction is due to a 30~mrad rotation of the SVT with respect to 
+	the beam line.}
 	\label{fig:vtx_pos}
@@
 \end{center}
-%While the tails of the vertex distribution expected in electron beam running is not accessible here the 
-%fact that the core is relatively well described provides confidence of the description of the amount of 
-%material and the model used for simulating multiple scattering in the target.  
-%These are crucial for benchmarking the HPS \Aprime{} physics reach since both the mass and vertex 
-%resolution that determine the sensitivity are limited by multiple scattering.
 
@@
 \label{sec:ecal_calibration}
-
-%step Of 442 modules, 39 were disabled or disconnected and were not read out by the DAQ.
-13 of these were not read out because of a shortage of FADC readout boards (see Sec.~\ref{sec:fadc}).The remainder either had no HV bias on the APD, or were disabled in the FADC software due to noise.
-In the data, we identified two types of abnormal channels.
-One FADC was not sending trigger signals correctly, resulting in low efficiency.
-This affected the 13 channels read out by that FADC.
-5 channels were diagnosed as noisy because they  had a high incidence of hits out of coincidence with the trigger.
-A large number of channels were originally misidentified as noisy because they had much higher hit occupancy than neighboring channels.
-Gain calibration shows that these channels have high gain (and thus lower energy threshold) but are otherwise normal.
-The abnormal channels were ignored in analysis in order to simplify comparison with Monte Carlo.
-This leaves 385 useful channels---87\% of the ECal.
 

### 2014-03-10 hps-testrun-nim.tex
Removed MCS section and added small subsection in performance instead. Moved run table to beamline section. Added block diagram of svt daq.

@@
 allow clean passage of the photon beam through the system. 
-\begin{figure}[ht]
+\begin{figure}[]
     \includegraphics[width=0.5\textwidth]{figures/HPS_dimensions}
@@
 During the dedicated HPS Test run period, the collimated (6.4~mm diameter), photon beam passes 
-through the aluminum PS pair converter and later the HPS system as shown schematically in Fig.~\ref{fig:schematic_testrun_vs_erun}.
-\begin{figure}[ht]
+through the aluminum PS pair converter and later the HPS system as illustrated in 
+Fig.~\ref{fig:schematic_testrun_vs_erun}.
+\begin{figure}[]
 \includegraphics[ width=7cm]{figures/photon_vs_electron_beam_schematic.png}
-\caption{\small{Schematic comparison of HPS Test run photon beam compared to the HPS electron beam.}}\label{fig:schematic_testrun_vs_erun}
+\caption{\small{Illustrative comparison of HPS Test run photon beam compared to the HPS electron 
+beam.}}
+\label{fig:schematic_testrun_vs_erun}
 \end{figure}
 The PS pair converter was located $\approx~77$~cm upstream of the first layer of the SVT.
-Data was taken on different converters (empty, $1.8\times 10^{-3}~X_0$ , $4.5\times 10^{-3}~X_0$ 
-and $1.6 \times 10^{-2}~X_0$) and repeated with the reverse field setting of the PS dipole magnet.
+
+magnet. Data was taken on three different converter thicknesses with a beam current varying between 
+30-70~nA and repeated with the reverse field setting of the PS dipole magnet.
+\begin{table}[]
+\begin{center}
+{\small
+\begin{tabular}{|c|c|c|}
+\hline
+Converter thickn. & Duration &  $e^-$ on converter \\
+ (\%$X_0$) & (s) & ($\mu$C)    \\   
+\hline
+%\hline
+1.6   & 911 &   24.4 \\ %24385.9     \\ %27 nA
+%\hline
+0.18   & 2640 &   193.5 \\ % 193508.9  \\  %73 nA
+%\hline
+0.45  & 2149 &     140.7 \\ %  140709.9  \\ %65.5 nA
+%\hline
+0    & 1279  &   88.1 \\ %88079.6  \\
+\hline
+\end{tabular}
+}
+\caption{Measured integrated currents for the dedicated photon runs.}
+\label{tab:currents}
+\end{center}
+\end{table}
+The photon beam line during the test run produced a relatively large fraction of pairs 
+originating upstream of the converter position. This contribution was measured during data taking 
+with ``empty'' converter runs i.e. removing the converter but with all other conditions the same. 
+The runs taken during the dedicated HPS Test run is summarized in Tab.~\ref{tab:currents}.
 
@@
 position of decay vertexes downstream of the target.
-
-%Track reconstruction is also important for energy scale calibration of the electromagnetic calorimeter due to the better momentum resolution of tracks compared to clusters in the calorimeter.
-
-%\subsection{SVT Requirements and Constraints}
-%The primary goal was to demonstrate that the technology and design approach 
-%chosen for the SVT was sound for running in the challenging environment at JLab. 
-%Nevertheless, a secondary but 
-%important aspect was that, after proving the technical concepts,  the apparatus would have the 
-%capability to discover \Aprime{} events. The implication was that the design of the SVT in the 
-%HPS Test apparatus would be subject to almost the same constraints and requirements as the full 
-%experiment except for certain aspects regarding longevity and robustness subject to cost, beam time 
-%and construction and design time constraints for the Test run.
 
@@
 	\includegraphics[width=6cm]{figures/svt_daq_module}
-	\caption{The SVT DAQ COB board with four data processing daughter cards visible on the left side.}
+	\caption{The SVT DAQ COB board with four data processing daughter cards (DPMs) visible on the left side.}
 	\label{fig:cob}
@@
 {\small
-	\includegraphics[width=6cm]{figures/svt_daq_module}
+	\includegraphics[width=8cm]{figures/svt-daq-sketch}
 	\caption{Block diagram overview of the SVT DAQ.}
@@
 
-The integrated pulse of the each channel was converted to energy by first 
-subtracting the pedestal and then applying a conversion factor to convert ADC counts to energy. 
+The integrated pulse of each FADC channel was converted to energy by  
+subtracting a pedestal and apply a conversion factor to convert ADC counts to energy. 
 The pedestals are measured using special runs where each trigger records 100 samples of signals from 
@@
 part of the window before the actual hit in the calorimeter. After subtracting the pedestal, modules with 
-integrated pulse above a threshold are clustered using a simple algorithm similar to the one deployed 
-for the trigger (see Sec.~\ref{sec:trigger}). Due to the high effective readout threshold of $73$~MeV the 
-average number of modules in a cluster was $\sim 3$ and the simple clustering algorithm worked well 
-for reconstruction of the detected shower energy. An average noise level of approximately 15~MeV 
-was measured in special pedestal runs.
+integrated pulse energy of about 73~MeV are clustered using a simple algorithm similar to the one 
+deployed for the trigger (see Sec.~\ref{sec:trigger}). Due to the high effective readout threshold of 
+$73$~MeV the average number of crystals in a cluster was $\sim 3$ and the simple clustering algorithm 
+worked well for reconstruction of the detected shower energy. An average noise level of approximately 
+15~MeV was measured in special pedestal runs.
 
@@
 to determine the conversion factors from ADC counts to energy. To compare data and simulation, all 
-inoperable or noisy channels in the SVT and ECal was disabled in both data and simulation; any 
+inoperable or noisy channels in the SVT and ECal was disabled in both data and simulation so that any 
 efficiency or bias that affect the data should be reflected in the simulation. 
 %Furthermore, a conversion factor calibration is performed to equalize the gains of  each channel. 
-simulation to those observed in data by comparing .
-The ``weighted $E/p$'' for each crystal is computed,
-representing the average $E/p$ for clusters that include the crystal
+%simulation to those observed in data by comparing .  The ``weighted $E/p$'' for each crystal is %computed, 
+%representing the average $E/p$ for clusters that include the crystal
 % $\frac{\sum_j w_{j,i}}{\sum_j\frac{P_j}{E_j}w_{j,i}}$.
-Iteratively, conversion coefficients for each module is adjusted until the $E/p$ ratio in data and 
-simulation are similar. The distribution of the $E/p$ ratio in data and simulation can be seen in 
+Iteratively, conversion coefficients for each crystal is adjusted until the $E$/$p$ ratio in data and 
+simulation are similar. The distribution of the $E$/$p$ ratio in data and simulation are compared in 
 Fig.~\ref{fig:gains}. 
@@
 	\includegraphics[width=7cm]{figures/h_ep_data_0_h_ep_MC_0_dataMC_1351-v6-v6gains_2-trig-top-cl600reg0.pdf}
-	\caption{The ECal energy over track momentum ratio comparing data and simulation} 
+	\caption{The ECal energy over track momentum ratio ($E$/$p$) comparing data and simulation} 
 	\label{fig:gains}
@@
 }
-The peak position of the distribution indicates the sampling fraction of the ECal, 
-the fraction of the incident particle energy measured in the cluster. The width and tails of the distribution 
+The peak position of the distribution indicates the sampling fraction of the ECal, the fraction of the 
+incident particle energy measured in the cluster. The width and tails of the distribution 
 in data indicates imperfect calibration and noise of the ECal modules. This level of calibration and the 
-agreement with simulation was found to be sufficient for the multiple scattering analysis using 
-normalized event rates described in Sec.~\ref{sec:mcs}.
-
-%These gains can then be used to convert from the ADC counts reported by the FADC in each channels to the energy deposited in the crystals.
-In order to find the energy of the incident particle one also needs to know the  the fraction of incident energy that is deposited in the cluster or "sampling fraction".
-%The sampling fraction is parameterized from simulation that show that it is approximately 0.9 for the ECal.
-The weighted $E/p$ shown in Fig.~\ref{fig:gains} is an approximate measurement of the sampling fraction of that part of the ECal but is position- (somewhat smaller at the edges) and energy-dependent because of the high readout thresholds (explaining the low value compared to 0.9).
-Since the sampling fraction is not needed to normalize event rates it was not applied in the multiple scattering analysis in Sec.~\ref{sec:mcs}.
-
-\subsection{Trigger Performance}
-The trigger and DAQ integrate pulses from the ECal modules differently to measure the energy 
-deposited in the each crystal. The trigger integrates the pulse using a time-over-threshold window, and 
-the DAQ readout integrates using a fixed-size window (5 samples before and 30 samples after a 
-threshold crossing). For every event, the trigger reports the trigger decision as a bit mask (top half, 
-bottom half or both) and the time the trigger fired. The trigger performance was studied by simulating the 
-trigger for each event and comparing to how the events were actually triggered.
-First, we simulate the FADC readout board to convert from readout hits (with fixed-size window 
-integration) to trigger hits (time-over-threshold integration). Secondly, the CTP clustering 
-algorithm and the trigger decision is simulated before we compare the trigger decision and trigger time 
-to what was reported by the actual trigger. To eliminate trigger bias, we use a tag and probe method. To 
-study the trigger performance in one half of the ECal, we select events which triggered the other half 
-and where there was exactly one probe cluster in the ECal half under study. We then measure trigger 
-efficiency as the fraction of tagged events that fired the trigger in the probe half as a function of the 
-probe cluster energy, shown in Fig.~\ref{fig:turnon}. As a cross-check, the turn-on from the trigger 
-threshold was measured to be 1280 in units of ADC counts as expected. The threshold was not 
-perfectly sharp because of uncertainties in the conversion from readout to trigger hits described 
-above, but based on comparisons with simulation we found that the trigger worked exactly as 
-specified.
-\begin{figure}[ht]
-\begin{center}
-{\small
-	\includegraphics[width=7cm]{figures/h_cl_E_probedata_eff_h_cl_E_probeMC_eff_dataMC_1351-v7-trig-tagBot.pdf}
-	\caption{Trigger efficiency in both halves of the ECal for data and simulation as a 
-	function of cluster energy.}
-\label{fig:turnon}
-}
-\end{center}
-\end{figure}
-The trigger turn-on is slow and reaches an uneven plateau just below 1~GeV for two reasons;  
-gain variations between different crystals lead to the threshold variations and the nonlinearity of 
-the time-over-threshold integral means that the effective threshold is higher for clusters that span 
-multiple crystals. The effective trigger threshold is therefore dependent on position and energy of 
-the particle as well as cluster multiplicity. 
-%Overall the trigger appears to have functioned exactly as intended. 
-%Changes planned for physics running (constant integration window and per-crystal gain calibration 
-%constants for the trigger) will solve both of the issues that led to threshold variations in the Test run.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Multiple Coulomb Scattering Distributions}
-\label{sec:mcs}
-Occupancies close to the beam create many of the key challenges in the HPS experiment
-and determine the limits of sensitivity to low \Aprime{} masses.
-These occupancies are dominated by electrons which have multiple Coulomb scattered (MCS) 
-to relatively large angles in the target. Because HPS is sensitive to scattering angles far out on the tail of 
-the MCS distribution, well beyond the angles important in other experiments, care must be taken
-to ensure our simulations are correct in this regime.
-
-\subsection{Multiple Coulomb Scattering Models}
-
-One of the main goals of the HPS Test was to evaluate the description of the tails of the MCS
-to gain further confidence in the expected detector occupancy in the full HPS experiment. 
-Previous studies of multiple scattering angles show good agreement with the \moliere{} 
-theory~\cite{Moliere:1948zz} for a wide range 
-of materials and projectiles~\cite{Attwood:2005zz,Shen:1978ha,Gottschalk1993467}. We have verified 
-that the angular distribution $F(\theta)$ in the differential cross section 
-$d\sigma = F( \theta) d(\cos\theta) d\phi$ for the \egs{}~\cite{egs5} simulation program show good 
-agreement with \moliere{}'s analytical formula as formulated by Bethe~\cite{Bethe:1953va}. 
-The small angle approximation was also shown to be in agreement with the theory formulated by 
-Gaudsmit and Saunderson~\cite{Goudsmit:1940zza,Goudsmit:1940zz} that is valid for any angle. 
-While \egs{} uses the more complex and time consuming \moliere{} 
-formula, the default physics list of \geant{} uses the so-called Urban model, an approximation with two, 
-continuously joined, functions to take into account 
-small and large angle scattering. Due to the explicit function in large angle approximation used by 
-\geant{} we expect that \geant{} will overestimate the angular distribution at angles larger than a few 
-mrad.
-
-Figure~\ref{fig:schematic_testrun_vs_erun} gives a schematic view of the main differences 
-between the photon and electron beam setup. 
-The angular distribution of the pair produced electron and positron emerging 
-from the converter in the test run has comparable contributions from {\it i)} the pair production angle
-and {\it ii)} the MCS of the electron and positron in the converter after production. By measuring the 
-scattering rate at several different converter thicknesses we can vary the contribution from MCS 
-while the contribution from the pair production angle is constant. This allows us to confirm our model of MCS 
-despite the fact that all data was taken with a photon beam.
-
-\subsection{Running Conditions}
-
-Data was taken at three different converter thicknesses with a beam current varying between 
-$30-70$~nA, see~Tab.~\ref{tab:currents}.  
-\begin{table}[t]
-\begin{center}
-{\small
-\begin{tabular}{|c|c|c|}
-\hline
-Converter thickness & Duration &  $e^-$ on converter \\
- (\%$X_0$) & (s) & ($\mu$C)    \\   
-\hline
-%\hline
-1.6   & 911 &   24.4 \\ %24385.9     \\ %27 nA
-%\hline
-0.18   & 2640 &   193.5 \\ % 193508.9  \\  %73 nA
-%\hline
-0.45  & 2149 &     140.7 \\ %  140709.9  \\ %65.5 nA
-%\hline
-0    & 1279  &   88.1 \\ %88079.6  \\
-\hline
-\end{tabular}
-}
-\caption{Measured integrated currents for the dedicated photon runs.}
-\label{tab:currents}
-\end{center}
-\end{table}
-The photon beam line during the test run produced a relatively 
-large fraction of pairs 
-originating upstream of the converter. This contribution was measured during data taking 
-with ``empty'' converter runs i.e. removing the converter but with all other conditions 
-the same. 
-The upstream background measured in the ``empty'' converter runs was subtracted 
-from the other runs, properly normalized using the measured integrated currents.
-
-\subsection{Measured Angular Distributions}
-
-For this analysis, we measure angular distribution of electrons and positrons using the ECal.
-Cluster reconstruction was done using the algorithm described in Sec.~\ref{sec:trigger} build 
-clusters around seed hits (hits above a ``seed'' energy threshold and with greater energy than any 
-neighboring hits), and add all neighboring hits above an ``add'' energy threshold.
-Hit energy is calibrated by matching track momentum to cluster energy, as described in Sec.~\ref{sec:ecal_calibration}.
-The measured angular distribution in the ECal for the three converter thicknesses are shown in Fig.~\ref{fig:ang_distr_data}.
-\begin{figure}[]
-\begin{center}
-{\small
-%	\includegraphics[ width=7cm]{figures/rate_ecalrow_raw.png}
-	\includegraphics[ width=7cm]{figures/rate_ecalrow_norm_subtr.png}
-	\caption{Measured vertical angular distributions after integrated beam current 
-	normalization and background subtraction.}
-	\label{fig:ang_distr_data}
-}
-\end{center}
-\end{figure}
-The data has been normalized to the integrated beam current and the background has been 
-subtracted. The background fraction for the there converter thicknesses was 16\%, 52\% and 71\% 
-for converter thicknesses of 1.6\%, 0.45\% and 0.18\%, respectively. The background fraction was also 
-cross-checked by pointing back tracks reconstructed in the SVT to identify the fraction of tracks not emanating from the converter. 
-%This can be seen in Fig.~\ref{fig:extrapol_converter} (bottom) where small 
-%satellite peaks at $\pm 10$~mm can be identified as tracks from the upstream background. The angular distribution, after normalization and subtracting the upstream background, are shown in 
-%Fig.~\ref{fig:ang_distr_data} (right).  
-We also checked that the contribution from photons to our triggered 
-sample was less than 2\% (without angular selections which would further reduce the contribution).
-
-These measured angular distributions are compared to simulation to validate 
-the modeling of the MCS. \egs{}~\cite{egs5} is used to generate 
-the electromagnetic interactions in the converter while \geant{} is used to simulate the particles after the 
-converter.  Figure~\ref{fig:ang_distr_dataMC} shows the angular distribution comparing data and 
-\egs{} normalized to 1~s of beam at 90~nA beam current with a converter thickness of 1.6\%. 
-Reasonable agreement is obtained in the most important region close to the beam. There is a hint of a 
-slightly different slope of the data at larger angles; this difference is covered by systematic uncertainties.  
-The total rates for each converter thickness is shown in Fig.~\ref{fig:rate_vs_thickness} and summarized 
-in Tab.~\ref{tab:ang_distr_dataMC}.
-\begin{figure}[]
-{\small
-	\begin{center}
-	\includegraphics[ width=7cm]{figures/dataMC_1351_Hit_Y_top_norm_bkgsub.png}
-	\caption{Comparison between the observed and predicted angular distribution using \egs{} for a 
-	converter thickness of 1.6\%. Similar agreement is found for 0.45\% and 0.18\% converter thicknesses. 
-	Only statistical uncertainties are shown. }
-	\label{fig:ang_distr_dataMC}
-\end{center}
-}
-\end{figure}
-\begin{figure}[]
-\begin{center}
-{\small
-	\includegraphics[ width=7cm]{figures/dataMC_egs.png}
-	\caption{The measured rate as a function of converter thickness for data and \egs{} simulation 
-	of MCS in 	the converter.} 
-	\label{fig:rate_vs_thickness}
-}
-\end{center}
-\end{figure}
-The total systematic uncertainty was estimated to be between 10-18\% depending on the run including:  
-a 5\% uncertainty on the integrated current normalization, alignment of the ECal, uncertainty from the 
-background normalization, and limited Monte Carlo statistics.  
-\begin{center}
+agreement with simulation was found to be sufficient to study normalized event rates on the Test run.
+
+\subsection{Multiple Coulomb Scattering Distributions}
+One of the main goals of the HPS Test run was to evaluate the description of the tails of the 
+multiple Coulomb scattering to gain further confidence in the expected detector occupancy in the full HPS 
+experiment. Those occupancies have been evaluated using \egs{}~\cite{egs5} simulation program 
+whose \moliere{} formulation of multiple scattering show good agreement with previous studies 
+for a wide range of materials and projectiles~\cite{Attwood:2005zz,Shen:1978ha,Gottschalk1993467} . 
+Despite all data taken with a photon beam in the Test run, the angular distribution of the pair 
+produced electron and positron emerging from the converter with different converter thickness can 
+be used to study the varying multiple Coulomb scattering contribution (pair production angle is constant). 
+Restricting clusters to a well calibrated region of the ECal we observe, within our systematic 
+uncertainties , good agreement with the rates predicted by \egs{}, see Tab.~\ref{tab:ang_distr_dataMC}.
+%\begin{center}
 \begin{table}
@@
 \hline
-Converter (\% r.l.) & 1.60 & 0.45 &	0.18 \\
+\bf Converter (\%~$X_0$) & \bf 1.60 & \bf 0.45 &	\bf 0.18 \\
 \hline
@@
 \caption{ Observed and predicted number of events for 1~s of beam at 90~nA for three different converter 
-thicknesses. The uncertainty on the prediction includes systematic uncertainties. }
+thicknesses. The uncertainty on the prediction includes systematic uncertainties from ECal alignment, background normalization, beam current normalization and limited statistics in the simulation.}
 }
@@
 \end{table}
-\end{center}
-
-\subsection{Conclusion}
-In summary, the accurate modeling of the MCS is fundamental to estimate occupancies and trigger rates 
-for HPS. \egs{} predicts the correct angular distribution across all converter thicknesses as expected while 
-\geant{}, using the so-called Urban model for multiple scattering overestimates the rates; with the disagreement 
-increasing  with larger converter thickness. This preliminary result verifies similar studies [] and gives confidence 
-in our modeling of the MCS 
-using \egs{} for evaluating the physics reach of HPS.
+%\end{center}
+
+\subsection{Trigger Performance}
+As described in Sec.~\ref{sec:fadc} and shown in Fig.~\ref{fig:hps_trigger_data} the energy from each 
+crystals are measured differently in the trigger and what is readout from the ECal. 
+The trigger performance was studied by simulating the 
+trigger for each event and comparing to how the events were actually triggered.
+First, we simulate the FADC trigger path by converting from readout hits (with fixed-size window 
+integration) to trigger hits (time-over-threshold integration). Secondly, the CTP clustering 
+algorithm and the trigger decision from the SSP is simulated before we compare the trigger decision 
+and trigger time to what was reported by the actual trigger. For every event, the trigger reports the trigger 
+decision as a bit mask (top half, bottom half or both) and the time the trigger fired. To eliminate trigger 
+bias, we use a tag and probe method: to study the trigger performance in one half of the ECal, we select 
+events which triggered the other half and where there was exactly one probe cluster in the ECal half 
+under study. We then measure trigger efficiency as the fraction of tagged events that fired the trigger in 
+the probe half as a function of the probe cluster energy, shown in Fig.~\ref{fig:turnon}. 
+\begin{figure}[ht]
+\begin{center}
+{\small
+	\includegraphics[width=7cm]{figures/h_cl_E_probedata_eff_h_cl_E_probeMC_eff_dataMC_1351-v7-trig-tagBot.pdf}
+	\caption{Trigger efficiency in both halves of the ECal for data and simulation as a 
+	function of cluster energy.}
+\label{fig:turnon}
+}
+\end{center}
+\end{figure}
+The trigger turn-on is slow and reaches an uneven plateau just below 1~GeV for two reasons;  
+gain variations between different crystals lead to the threshold variations and the nonlinearity of 
+the time-over-threshold integral means that the effective threshold is higher for clusters that span 
+multiple crystals. The effective trigger threshold is therefore dependent on position and energy of 
+the particle as well as cluster multiplicity.
+
+As a cross-check, the turn-on from the trigger threshold was measured to be 1280 in units of ADC counts 
+as expected. The threshold was not perfectly sharp because of uncertainties in the conversion from 
+readout to trigger hits described above, but based on comparisons with simulation we found that the 
+trigger worked exactly as specified.
 
@@
 
+%\section{Multiple Coulomb Scattering Distributions}
+%\label{sec:mcs}
+%Occupancies close to the beam create many of the key challenges in the HPS experiment
+%and determine the limits of sensitivity to low \Aprime{} masses.
+%These occupancies are dominated by electrons which have multiple Coulomb scattered (MCS) 
+%to relatively large angles in the target. Because HPS is sensitive to scattering angles far out on the tail of 
+%the MCS distribution, well beyond the angles important in other experiments, care must be taken
+%to ensure our simulations are correct in this regime.  
+%
+%\subsection{Multiple Coulomb Scattering Models}
+%
+%One of the main goals of the HPS Test was to evaluate the description of the tails of the MCS
+%to gain further confidence in the expected detector occupancy in the full HPS experiment. 
+%Previous studies of multiple scattering angles show good agreement with the \moliere{} 
+%theory~\cite{Moliere:1948zz} for a wide range 
+%of materials and projectiles~\cite{Attwood:2005zz,Shen:1978ha,Gottschalk1993467}. We have verified 
+%that the angular distribution $F(\theta)$ in the differential cross section 
+%$d\sigma = F( \theta) d(\cos\theta) d\phi$ for the \egs{}~\cite{egs5} simulation program show good 
+%agreement with \moliere{}'s analytical formula as formulated by Bethe~\cite{Bethe:1953va}. 
+%The small angle approximation was also shown to be in agreement with the theory formulated by 
+%Gaudsmit and Saunderson~\cite{Goudsmit:1940zza,Goudsmit:1940zz} that is valid for any angle. 
+%While \egs{} uses the more complex and time consuming \moliere{} 
+%formula, the default physics list of \geant{} uses the so-called Urban model, an approximation with two, 
+%continuously joined, functions to take into account 
+%small and large angle scattering. Due to the explicit function in large angle approximation used by 
+%\geant{} we expect that \geant{} will overestimate the angular distribution at angles larger than a few 
+%mrad.
+%
+%
+%Figure~\ref{fig:schematic_testrun_vs_erun} gives a schematic view of the main differences 
+%between the photon and electron beam setup. 
+%The angular distribution of the pair produced electron and positron emerging 
+%from the converter in the test run has comparable contributions from {\it i)} the pair production angle
+%and {\it ii)} the MCS of the electron and positron in the converter after production. By measuring the 
+%scattering rate at several different converter thicknesses we can vary the contribution from MCS 
+%while the contribution from the pair production angle is constant. This allows us to confirm our model of MCS 
+%despite the fact that all data was taken with a photon beam.
+%
+%
+%\subsection{Running Conditions}
+%
+%Data was taken at three different converter thicknesses with a beam current varying between 
+%$30-70$~nA, see~Tab.~\ref{tab:currents}.  
+%\begin{table}[t]
+%\begin{center}
+%{\small
+%\begin{tabular}{|c|c|c|}
+%\hline
+%Converter thickness & Duration &  $e^-$ on converter \\
+% (\%$X_0$) & (s) & ($\mu$C)    \\   
+%\hline
+%%\hline
+%1.6   & 911 &   24.4 \\ %24385.9     \\ %27 nA
+%%\hline
+%0.18   & 2640 &   193.5 \\ % 193508.9  \\  %73 nA
+%%\hline
+%0.45  & 2149 &     140.7 \\ %  140709.9  \\ %65.5 nA
+%%\hline
+%0    & 1279  &   88.1 \\ %88079.6  \\
+%\hline
+%\end{tabular}
+%}
+%\caption{Measured integrated currents for the dedicated photon runs.}
+%\label{tab:currents}
+%\end{center}
+%\end{table}
+%The photon beam line during the test run produced a relatively 
+%large fraction of pairs 
+%originating upstream of the converter. This contribution was measured during data taking 
+%with ``empty'' converter runs i.e. removing the converter but with all other conditions 
+%the same. 
+%The upstream background measured in the ``empty'' converter runs was subtracted 
+%from the other runs, properly normalized using the measured integrated currents.
+%
+%
+%
+%\subsection{Measured Angular Distributions}
+%
+%For this analysis, we measure angular distribution of electrons and positrons using the ECal.
+%Cluster reconstruction was done using the algorithm described in Sec.~\ref{sec:trigger} build 
+%clusters around seed hits (hits above a ``seed'' energy threshold and with greater energy than any 
+%neighboring hits), and add all neighboring hits above an ``add'' energy threshold.
+%Hit energy is calibrated by matching track momentum to cluster energy, as described in Sec.~\ref{sec:ecal_calibration}.
+The measured angular distribution in the ECal for the three converter thicknesses are shown in Fig.~\ref{fig:ang_distr_data}.
+%\begin{figure}[]
+%\begin{center}
+%{\small
+%%	\includegraphics[ width=7cm]{figures/rate_ecalrow_raw.png}
+%	\includegraphics[ width=7cm]{figures/rate_ecalrow_norm_subtr.png}
+%	\caption{Measured vertical angular distributions after integrated beam current 
+%	normalization and background subtraction.}
+%	\label{fig:ang_distr_data}
+%}
+%\end{center}
+%\end{figure}
+%The data has been normalized to the integrated beam current and the background has been 
+%subtracted. The background fraction for the there converter thicknesses was 16\%, 52\% and 71\% 
+%for converter thicknesses of 1.6\%, 0.45\% and 0.18\%, respectively. The background fraction was also 
+%cross-checked by pointing back tracks reconstructed in the SVT to identify the fraction of tracks not emanating from the converter. 
+%%This can be seen in Fig.~\ref{fig:extrapol_converter} (bottom) where small 
+%%satellite peaks at $\pm 10$~mm can be identified as tracks from the upstream background. The angular distribution, after normalization and subtracting the upstream background, are shown in 
+%%Fig.~\ref{fig:ang_distr_data} (right).  
+%We also checked that the contribution from photons to our triggered 
+%sample was less than 2\% (without angular selections which would further reduce the contribution).
+%
+%
+%These measured angular distributions are compared to simulation to validate 
+%the modeling of the MCS. \egs{}~\cite{egs5} is used to generate 
+%the electromagnetic interactions in the converter while \geant{} is used to simulate the particles after the 
+%converter.  Figure~\ref{fig:ang_distr_dataMC} shows the angular distribution comparing data and 
+%\egs{} normalized to 1~s of beam at 90~nA beam current with a converter thickness of 1.6\%. 
+%Reasonable agreement is obtained in the most important region close to the beam. There is a hint of a 
+%slightly different slope of the data at larger angles; this difference is covered by systematic uncertainties.  
+%The total rates for each converter thickness is shown in Fig.~\ref{fig:rate_vs_thickness} and summarized 
+%in Tab.~\ref{tab:ang_distr_dataMC}.
+%\begin{figure}[]
+%{\small
+%	\begin{center}
+%	\includegraphics[ width=7cm]{figures/dataMC_1351_Hit_Y_top_norm_bkgsub.png}
+%	\caption{Comparison between the observed and predicted angular distribution using \egs{} for a 
+%	converter thickness of 1.6\%. Similar agreement is found for 0.45\% and 0.18\% converter thicknesses. 
+%	Only statistical uncertainties are shown. }
+%	\label{fig:ang_distr_dataMC}
+%\end{center}
+%}
+%\end{figure}
+%\begin{figure}[]
+%\begin{center}
+%{\small
+%	\includegraphics[ width=7cm]{figures/dataMC_egs.png}
+%	\caption{The measured rate as a function of converter thickness for data and \egs{} simulation 
+%	of MCS in 	the converter.} 
+%	\label{fig:rate_vs_thickness}
+%}
+%\end{center}
+%\end{figure}
+%The total systematic uncertainty was estimated to be between 10-18\% depending on the run including:  
+%a 5\% uncertainty on the integrated current normalization, alignment of the ECal, uncertainty from the 
+%background normalization, and limited Monte Carlo statistics.  
+%\begin{center}
+%\begin{table}
+%{\small
+%\begin{tabular}{|l|c|c|c|}
+%\hline
+%Converter (\% r.l.) & 1.60 & 0.45 &	0.18 \\
+%\hline
+%EGS5 &	1162 $\pm$ 112 &	255 $\pm$ 28 &	94 $\pm$ 17	\\
+%\hline
+%GEANT4 & 2633 $\pm$ 250 & 	371 $\pm$ 38 &	114 $\pm$ 18 \\
+%\hline
+%Observed 	& 1064 $\pm$ 2 & 196 $\pm$ 1 &	92 $\pm$ 1 \\						
+%\hline
+%\end{tabular}
+%\caption{ Observed and predicted number of events for 1~s of beam at 90~nA for three different converter 
+%thicknesses. The uncertainty on the prediction includes systematic uncertainties. }
+%}
+%\label{tab:ang_distr_dataMC}
+%\end{table}
+%\end{center}
+%
+%\subsection{Conclusion}
+%In summary, the accurate modeling of the MCS is fundamental to estimate occupancies and trigger rates 
+%for HPS. \egs{} predicts the correct angular distribution across all converter thicknesses as expected while 
+%\geant{}, using the so-called Urban model for multiple scattering overestimates the rates; with the disagreement 
+%increasing  with larger converter thickness. This preliminary result verifies similar studies [] and gives confidence 
+%in our modeling of the MCS 
+%using \egs{} for evaluating the physics reach of HPS.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Summary and Outlook}
-
-%This paper reviewed 
-The HPS Test Run experiment, using a simplified version of the apparatus planned for the full HPS experiment in a parasitic photon beam, demonstrated the feasibility of the detector technologies proposed for the HPS silicon tracker, ECal, and data acquisition systems.
-Performance from each of these subsystems has been shown to be adequate to conduct the full experiment successfully.
-A measurement of the normalized trigger rates from a photon conversion target confirmed expectations from simulation, giving credance to estimates of the trigger rates and the detector backgrounds expected in electron beam running.
+The HPS Test experiment, using a simplified version of the apparatus planned for the full HPS 
+experiment in a parasitic photon beam, demonstrated the feasibility of the detector technologies 
+proposed for the silicon vertex tracker, electromagnetic calorimeter, and data acquisition systems. 
+Performance from each of these subsystems has been shown to be adequate to conduct the full 
+experiment successfully. Studies of multiple Coloumb scattering tails of electrons and positrons from 
+photon conversions further backs expectations from simulation, giving credance to estimates of the 
+detector backgrounds expected in electron beam running for HPS.
 

### 2014-03-10 hps-testrun-nim.tex
Centering pictures.

@@
 \label{detector}
-\begin{center}
-{\small
-\begin{figure*}[ht]
+{\small
+\begin{figure*}[t]
+\begin{center}
     \includegraphics[width=0.8\textwidth]{figures/hps_testrun_rendering}
@@
 \label{fig:testrundetector}
+\end{center}
 \end{figure*}
 }
-\end{center}
 The HPS Test apparatus was designed to run in Hall~B at JLab using the CEBAF electron beam, a 
@@
 8.7~cm gap between the innermost edge of the crystals in the two halves.
-\begin{center}
 {\small
 \begin{figure*}[htb]
+\begin{center}
 \includegraphics[width=0.45\textwidth]{figures/ECal}
@@
 \label{fig:ecal}
+\end{center}
 \end{figure*}
 }
-\end{center}
 
@@
 {\small
-\includegraphics[width=5cm]{figures/FADC250_Photo_001.jpg}
+\includegraphics[width=4cm]{figures/FADC250_Photo_001.jpg}
 \caption{The JLab FADC250 VXS module.}

### 2014-03-11 hps-testrun-nim.tex
Shifting around parts of the intro, trying to be consistent on HPS Test workding

@@
 angles. At small couplings, \Aprime's become long-lived, so detection of a displaced decay 
-vertex can reject the prompt QED background and boost experimental sensitivity.  These production 
-and kinematics poses stringent constraint on the detector requirements:
+vertex can reject the prompt QED background and boost experimental sensitivity.
+
+The HPS experiment~\cite{HPS_proposal_2010} uses both invariant mass and 
+vertex signatures by placing a $\approx 1$~m long silicon tracking and vertexing detector 10~cm 
+downstream  of a 0.25\%~$\chi_0$ tungsten target inside a dipole magnet. The experiment runs at high 
+rates (up to 50kHz), exploiting the 
+100\% duty cycle of the Thomas Jefferson National Accelerator Facility (JLab) CEBAF accelerator to 
+accumulate the need statistics. The trigger is provided by a fast electromagnetic calorimeter just 
+downstream of the tracking detector.
+
+The HPS Test apparatus, a simplified version of the HPS experiment, was proposed and 
+approved at Thomas Jefferson National Accelerator Facility (JLab) as the first stage of HPS. 
+Its purposes included demonstrating that the apparatus and data acquisition systems are 
+technically feasible and that the trigger rates and occupancies encountered in electron-beam 
+running are as simulated. Given dedicated running time with electron beams, the HPS Test Run 
+apparatus is capable of searching for heavy photons in unexplored regions of parameter space.    
+The stringent constraints on the detector requirements therefore also applied to the Test detector:
 \begin{itemize}
@@
 \end{itemize}
-The HPS experiment~\cite{HPS_proposal_2010} uses both invariant mass and 
-vertex signatures by placing a $\approx 1$~m long silicon tracking and vertexing detector 10~cm 
-downstream  of a 0.25\%~$\chi_0$ tungsten target inside a dipole magnet. The experiment runs at high 
-rates (up to 50kHz), exploiting the 
-100\% duty cycle of the Thomas Jefferson National Accelerator Facility (JLab) CEBAF accelerator to 
-accumulate the need statistics. The trigger is provided by a fast electromagnetic calorimeter just 
-downstream of the tracking detector.
-
-The HPS Test apparatus, a simplified version of the full HPS experiment, was proposed and 
-approved at Thomas Jefferson National Accelerator Facility (JLab) as the first stage of the HPS 
-experiment. Its purposes included demonstrating that the apparatus and data acquisition systems are 
-technically feasible and that the trigger rates and occupancies encountered in electron-beam 
-running are as simulated. Given dedicated running time with electron beams, the HPS Test Run 
-apparatus is capable of searching for heavy photons in unexplored regions of parameter space.    
-The HPS Test apparatus was installed on April 19, 2012, and ran parasitically with the HDice 
+
+The Test apparatus was installed on April 19, 2012, and ran parasitically with the HDice 
 experiment~\cite{HDice}, using its photon beam, until May 18. The JLab run schedule 
@@
 
-This paper reviews the HPS Test Run apparatus; documents the performance of the trigger, 
+This paper reviews the HPS Test apparatus; documents the performance of the trigger, 
 data acquisition, silicon tracking detector, and the electromagnetic calorimeter at the level assumed 
@@
 %\end{multicols}
-A rendering of the HPS Test apparatus installed on the beam line is shown in 
+A rendering of the apparatus installed on the beam line is shown in 
 Fig.~\ref{fig:testrundetector} and an overview of the coverage, segmentation and performance is 
@@
 Figure~\ref{fig:hpstest_layout} shows the layout of 
-the HPS Test setup on the beam line. The SVT was installed inside the Hall B pair 
+the setup on the beam line. The SVT was installed inside the Hall B pair 
 spectrometer magnet (PS) vacuum chamber with the ECal mounted downstream of it. Both the 
@@
 
-magnet. Data was taken on three different converter thicknesses with a beam current varying between 
+ Data was taken on three different converter thicknesses with a beam current varying between 
 30-70~nA and repeated with the reverse field setting of the PS dipole magnet.
@@
 with ``empty'' converter runs i.e. removing the converter but with all other conditions the same. 
-The runs taken during the dedicated HPS Test run is summarized in Tab.~\ref{tab:currents}.
+The runs taken during the time dedicated to HPS Test is summarized in Tab.~\ref{tab:currents}.
 
@@
 Module (RTM), a custom board 
-on the back side of the ATCA crate, interfacing the HPS readout to the generic DAQ components on the 
+on the back side of the ATCA crate, interfacing the HPS-specific readout to the generic DAQ components 
+on the 
 COB. A pre-amplifier converts the APV25 differential current output to a different voltage output scaled to 
@@
 \subsection{Multiple Coulomb Scattering Distributions}
-One of the main goals of the HPS Test run was to evaluate the description of the tails of the 
+One of the main goals of the Test run was to evaluate the description of the tails of the 
 multiple Coulomb scattering to gain further confidence in the expected detector occupancy in the full HPS 

### 2014-03-11 hps-testrun-nim.tex
Small edits to trigger section.

@@
 Each channel on the FADC board have an 
-independent data path to send a 5-bit pulse energy and 3-bit pulse arrival time information to a 
-trigger processing board (CTP) in the same crate every 32~ns. Contrary to the readout path 
+independent data path to send 5-bit pulse energy and 3-bit pulse arrival time information every 32~ns 
+to a 
+trigger processing board (CTP) in the same crate every. Contrary to the readout path 
 described in Sec.~\ref{sec:fadc}, this energy is a pedestal subtracted time-over-threshold sum with 
@@
 algorithm simultaneously searches for up to 125 clusters with energy sum larger than 
-the programmable energy threshold (in the Test run this was $\approx270$~MeV). Crystals in the 
-fixed-window are included in the sum if the leading edges of the pulses occurred within a 8~ns time 
-window (4~ns minimum). To take into account with clock skew and jitter throughout the system 
-clustering algorithm can allow crystal hits from $N\in[0,7]$ previous or future 4~ns clock cycles to 
+the programmable energy threshold ($\approx270$~MeV). Crystals in the 
+fixed-window are included in the sum if the leading edge of the pulse occurred within a 8~ns time 
+window (4~ns minimum). To take into account clock skew and jitter throughout the system, the
+clustering algorithm can allow for crystal hits from up to seven previous or future 4~ns clock cycles to 
 contribute to the cluster sum.  A separate sub-system board (SSP) receives the clusters (only the 
@@
 The trigger system is free-running and driven by the 250~MHz global clock and has essentially zero 
-dead time at the occupancies expected for HPS. The Trigger Supervisor can apply dead time if 
+dead time at the occupancies expected for HPS. The trigger supervisor can apply dead time if 
 necessary, for example on a `busy' or `full' condition from the front-end electronics. The system is 
@@
 that required by the SVT APV25 ASIC. During the Test run, for the most part the trigger system 
-required only a single cluster in either the top or bottom Ecal halves and tested to above 100~kHz 
-trigger rates with low thresholds.
+required only a single cluster in either the top or bottom Ecal halves and was tested to above 100~kHz 
+trigger rates by lowering thresholds.
 
@@
 \subsection{Multiple Coulomb Scattering Distributions}
+\label{sec:mcs}
 One of the main goals of the Test run was to evaluate the description of the tails of the 
@@
 whose \moliere{} formulation of multiple scattering show good agreement with previous studies 
-for a wide range of materials and projectiles~\cite{Attwood:2005zz,Shen:1978ha,Gottschalk1993467} . 
+for a wide range of materials and projectiles~\cite{Attwood:2005zz,Shen:1978ha,Gottschalk1993467}. 
 Despite all data taken with a photon beam in the Test run, the angular distribution of the pair 
@@
 Restricting clusters to a well calibrated region of the ECal we observe, within our systematic 
-uncertainties , good agreement with the rates predicted by \egs{}, see Tab.~\ref{tab:ang_distr_dataMC}.
+uncertainties , good agreement with the rates predicted by \egs{}, see Tab.~\ref{tab:mcs}.
 %\begin{center}
@@
 }
-\label{tab:ang_distr_dataMC}
+\label{tab:mcs}
 \end{table}

### 2014-03-25 hps-testrun-nim.tex
Changes from large overhaul by John and myself.

@@
 \hline
-Converter thickn. & Duration &  $e^-$ on converter \\
+Converter thickn. & Duration &  $e^-$ on radiator \\
  (\%$X_0$) & (s) & ($\mu$C)    \\   
@@
 radiation dose approaches $10^{15}$ electrons/cm$^2$/month, or roughly 
-$3 \times 10^{14}$~\fluenceunit{}/month~\cite{Rashevskaya:2002nd}, as shown in 
-Fig.~\ref{fig:radiation},  requiring the sensors to be actively cooled.
+$3 \times 10^{14}$~\fluenceunit{}/month~\cite{Rashevskaya:2002nd}, 
+requiring the sensors to be actively cooled.
 % and~\ref{fig:rates}.
 %===================
-\begin{figure}[]
-\includegraphics[width=7cm]{figures/radiation}
-\label{fig:radiation}
-\caption{{\small Simulation of the electron fluence 10~cm downstream of the target in the active region 
-of the SVT ($|Y|>0.15~$mm) looking downstream; electrons bend towards $+x$.}}
-\end{figure}
+%\begin{figure}[]
+%\includegraphics[width=7cm]{figures/radiation}
+%\label{fig:radiation}
+%\caption{{\small Simulation of the electron fluence 10~cm downstream of the target in the active region 
+%of the SVT ($|Y|>0.15~$mm) looking downstream; electrons bend towards $+x$.}}
+%\end{figure}
 Meanwhile, very low-energy delta rays from 
@@
 Despite having only small spots with very high occupancy (up to 4~MHz/mm$^2$) closest to the primary 
-beam, see Fig.~\ref{fig:radiation}, the rates are still high and lowering the peak occupancy to 
+beam, the rates are still high and lowering the peak occupancy to 
 approximately 1\% for tracking requires a trigger window and hit time tagging of roughly 8~ns. The 
@@
 {\small
-\begin{figure*}[htb]
+\begin{figure}[]
 \begin{center}
 \includegraphics[width=0.45\textwidth]{figures/ECal}
-\includegraphics[width=0.45\textwidth]{figures/ecal_picture_beamline}
-\caption{Rendered layout view (left) and the ECal assembly on the beam line (right).}
+%\includegraphics[width=0.45\textwidth]{figures/ecal_picture_beamline}
+\caption{Rendered layout view of the ECal looking downstream.}
 \label{fig:ecal}
 \end{center}
-\end{figure*}
+\end{figure}
 }
@@
 After a 2:1 signal splitter, $1/3$ of an amplified APD signal ($2/3$ is sent to a timing module) is fed to a 
-single channel of a JLab flash ADC (FADC) board~\cite{fadc}, 
-see Fig~.\ref{fig:fadc}.
-\begin{figure}[]
-\begin{center}
-{\small
-\includegraphics[width=4cm]{figures/FADC250_Photo_001.jpg}
-\caption{The JLab FADC250 VXS module.}
-\label{fig:fadc}
-}
-\end{center}
-\end{figure}
+single channel of a JLab flash ADC (FADC) board~\cite{fadc}.
+%\begin{figure}[]
+%\begin{center}
+%{\small
+%\includegraphics[width=4cm]{figures/FADC250_Photo_001.jpg}
+%\caption{The JLab FADC250 VXS module.}
+%\label{fig:fadc}
+%}
+%\end{center}
+%\end{figure}
 The FADC boards are high speed VXS modules digitizing up to 16 APD signals 
@@
 threshold (for the Test run this was set to $\approx70$~MeV) are 
-summed and stored in a 17-bit register for readout as described in Fig.~\ref{fig:hps_trigger_data}.
+summed and stored in a 17-bit register for readout.
 This scheme significantly compresses the data output of the FADC. During offline data analysis, a 
@@
 excessive noise) and 18 was masked offline due to noise. 
-\begin{figure}[]
-\begin{center}
-{\small
-\includegraphics[width=8cm]{figures/fadc_datapath_diagram.png}
-\caption{The two different readout modes of the FADC used in the Test run.}
-\label{fig:hps_trigger_data}
-}
-\end{center}
-\end{figure}
+%\begin{figure}[]
+%\begin{center}
+%{\small
+%\includegraphics[width=8cm]{figures/fadc_datapath_diagram.png}
+%\caption{The two different readout modes of the FADC used in the Test run.}
+%\label{fig:hps_trigger_data}
+%}
+%\end{center}
+%\end{figure}
 
@@
 \section{Trigger and Data Acquisition}
+\label{sec:triggerdaq}
 
@@
 
+In order to minimize cable length for the analog APV25 output signal the ATCA crate was located 
+approximately 1~m from the beam line, next to our cable vacuum feed troughs.   
+Before shielding with lead-blankets was arranged, we observed two failures of normally reliable ATCA 
+crate power supplies, time-correlated to beam instabilities.
+
 While trigger rates during the Test run was significantly lower this system was tested at trigger rates up 
@@
 With a linear gain up to $\approx 3$~MIPs, the cluster charge for hits associated with a track follow 
-the characteristic Landau shape, see Fig.~\ref{fig:cluster_pulse}.  
+the characteristic Landau shape. 
+%, see Fig.~\ref{fig:cluster_pulse}.  
 A noise level between $1.1-1.5\times 10^{3}$ electrons was established through multiple calibration 
@@
 provide the absolute charge normalization.
-\begin{figure}[]
-\begin{center}
-{\small
-	%\includegraphics[width=7cm]{figures/run1351_mip_small.pdf}
-	\includegraphics[width=7cm]{figures/mip_top_layer_2.png}
-    	\caption{ The cluster charge distribution for hits associated with a track. }
-	\label{fig:cluster_pulse}
-}
-\end{center}
-\end{figure}
+%\begin{figure}[]
+%\begin{center}
+%{\small
+%	%\includegraphics[width=7cm]{figures/run1351_mip_small.pdf}
+%	\includegraphics[width=7cm]{figures/mip_top_layer_2.png}
+%    	\caption{ The cluster charge distribution for hits associated with a track. }
+%	\label{fig:cluster_pulse}
+%}
+%\end{center}
+%\end{figure}
 
@@
 well reproduced given the alignment of the tracker as shown in Fig.~\ref{fig:pair_kin}.
+
+The expected momentum resolution from simulation is between 4-5\% 
+for tracks in the momentum range of the Test run. This is significantly smaller than the accuracy at 
+which we're able estimate the scale and resolution in the Test run. By looking at the agreement 
+between data and simulation in the shape of the kinematic distributions for single- and two track 
+events and adjusting the overall momentum scale and smearing simulated events with a 
+Gaussian resolution we estimate an uncertainty of 10\% on both the momentum scale and 
+resolution.
  \begin{center}
@@
 \end{center}
-The expected momentum resolution from simulation is between 4-5\% 
-for tracks in the momentum range of the Test run. This is significantly smaller than the accuracy at 
-which we're able estimate the scale and resolution in the Test run. By looking at the agreement 
-between data and simulation in the shape of the kinematic distributions for single- and two track 
-events and adjusting the overall momentum scale and smearing simulated events with a 
-Gaussian resolution we estimate an uncertainty of 10\% on both the momentum scale and 
-resolution.
-
-For the vertexing performance the foremost difference compared to electron beam running is that the 
-target was located approximately 67~cm upstream from our nominal target position; giving almost 
-collinear tracks in the detector. This degrades the vertex resolution along the 
-beam line compared to that expected in an electron beam with nominal target position. 
-Furthermore, tails of the vertex distributions are impossible to study with the finite data sample obtained 
-in the Test run. Nevertheless, useful information can still be 
-obtained by studying the vertex distributions. Figure~\ref{fig:vtx_pos} shows the distance of closest 
-approach of the momentum vectors extrapolated in the upstream direction from our analyzing magnet, 
-taking into account the measured fringe field of the PS dipole magnet. 
- \begin{center}
-{\small
-	 \begin{figure*}[t]
+In the Test run, as well as in electron running with HPS, the dominating source of uncertainty in the 
+tracking and vertexing is multiple Coulomb scattering. For the vertexing performance the foremost 
+difference compared to electron beam running is that the target was located approximately 67~cm 
+upstream from our nominal target position; giving almost collinear tracks in the detector. The increased 
+lever arm over which tracks are extrapolated widens the resolution with up to a factor of eight (depending 
+on momentum) compared to what is achieved at the nominal electron target position for HPS. 
+Figure~\ref{fig:impact_param} shows the horizontal and vertical positions of the extrapolated track at the 
+converter position. 
+{\small
+	 \begin{figure}[]
+ \begin{center}
 	% Plot info:
 	% TestRun-v6 geometry, twotrkfilter, trigsel, hps-java-1.8-SNAPSHOT, 4hits, chi2<10
-	\includegraphics[width=5cm]{figures/h_vtx_fr_x_h_vtx_x_trigsel4hit_pair1351_twotrkfilt-v6-paper}
-	\includegraphics[width=5cm]{figures/h_vtx_fr_y_h_vtx_y_trigsel4hit_pair1351_twotrkfilt-v6-paper}
-	\includegraphics[width=5cm]{figures/h_vtx_fr_z_h_vtx_z_trigsel4hit_pair1351_twotrkfilt-v6-paper}
-	\caption{ Vertex position represented by the distance of closest approach of the extrapolated 
-	momentum vectors upstream of the PS dipole magnet taking into account the measured fringe field. 
-	The overall shift from zero in the x-direction is due to a 30~mrad rotation of the SVT with respect to 
-	the beam line.}
-	\label{fig:vtx_pos}
-\end{figure*}
-}
-\end{center}
+	\includegraphics[width=7cm]{figures/h_trk_top_fr_conv_z_h_trk_top_conv_z_dataMC_twotrksel.png}
+	\includegraphics[width=7cm]{figures/h_trk_top_fr_conv_y_h_trk_top_conv_y_dataMC_twotrksel.png}
+	\caption{ Vertical (top) and horizontal (bottom) extrapolated track position at the converter position 
+	taking into account the measured fringe field. }
+	\label{fig:impact_param}
+\end{center}
+\end{figure}
+}
+While residual alignment show small shifts good agreement on the widths between data and simulated 
+events, indicating a good understanding of our material budget and distribution in the SVT.  
+%Furthermore, tails of the vertex distributions are impossible to study with the finite data sample obtained 
+%in the Test run. Nevertheless, useful information can still be 
+%obtained by studying the vertex distributions. Figure~\ref{fig:vtx_pos} shows the distance of closest 
+%approach of the momentum vectors extrapolated in the upstream direction from our analyzing magnet, 
+%taking into account the measured fringe field of the PS dipole magnet. 
+ %\begin{center}
+%{\small
+%	 \begin{figure*}[t]
+%	% Plot info:
+%	% TestRun-v6 geometry, twotrkfilter, trigsel, hps-java-1.8-SNAPSHOT, 4hits, chi2<10
+%	\includegraphics[width=5cm]{figures/h_vtx_fr_x_h_vtx_x_trigsel4hit_pair1351_twotrkfilt-v6-paper}
+%	\includegraphics[width=5cm]{figures/h_vtx_fr_y_h_vtx_y_trigsel4hit_pair1351_twotrkfilt-v6-paper}
+%	\includegraphics[width=5cm]{figures/h_vtx_fr_z_h_vtx_z_trigsel4hit_pair1351_twotrkfilt-v6-paper}
+%	\caption{ Vertex position represented by the distance of closest approach of the extrapolated 
+%	momentum vectors upstream of the PS dipole magnet taking into account the measured fringe field. 
+%	The overall shift from zero in the x-direction is due to a 30~mrad rotation of the SVT with respect to 
+%	the beam line.}
+%	\label{fig:vtx_pos}
+%\end{figure*}
+%}
+%\end{center}
 
@@
 
-\subsection{Multiple Coulomb Scattering Distributions}
+\subsection{Trigger Performance}
+As described above the energy from each 
+crystal is measured differently in the trigger and what is readout from the ECal. 
+The trigger performance was studied by simulating the 
+trigger for each event and comparing to how the events were actually triggered.
+First, we simulate the FADC trigger path by converting from readout hits (with fixed-size window 
+integration) to trigger hits (time-over-threshold integration). Secondly, the CTP clustering 
+algorithm and the trigger decision from the SSP is simulated before we compare the trigger decision 
+and trigger time to what was reported by the actual trigger. For every event, the trigger reports the trigger 
+decision as a bit mask (top half, bottom half or both) and the time the trigger fired. To eliminate trigger 
+bias, we use a tag and probe method: to study the trigger performance in one half of the ECal, we select 
+events which triggered the other half and where there was exactly one probe cluster in the ECal half 
+under study. We then measure trigger efficiency as the fraction of tagged events that fired the trigger in 
+the probe half as a function of the probe cluster energy, shown in Fig.~\ref{fig:turnon}. 
+\begin{figure}[ht]
+\begin{center}
+{\small
+	\includegraphics[width=7cm]{figures/h_cl_E_probedata_eff_h_cl_E_probeMC_eff_dataMC_1351-v7-trig-tagBot.pdf}
+	\caption{Trigger efficiency in both halves of the ECal for data and simulation as a 
+	function of cluster energy.}
+\label{fig:turnon}
+}
+\end{center}
+\end{figure}
+The trigger turn-on is slow and reaches an uneven plateau just below 1~GeV for two reasons;  
+gain variations between different crystals lead to the threshold variations and the nonlinearity of 
+the time-over-threshold integral means that the effective threshold is higher for clusters that span 
+multiple crystals. The effective trigger threshold is therefore dependent on position and energy of 
+the particle as well as cluster multiplicity.
+
+As a cross-check, the turn-on from the trigger threshold was measured to be 1280 in units of ADC counts 
+as expected. The threshold was not perfectly sharp because of uncertainties in the conversion from 
+readout to trigger hits described above, but based on comparisons with simulation we found that the 
+trigger worked exactly as specified.
+
+\subsection{Trigger Rate Comparisons}
 \label{sec:mcs}
-One of the main goals of the Test run was to evaluate the description of the tails of the 
-multiple Coulomb scattering to gain further confidence in the expected detector occupancy in the full HPS 
-experiment. Those occupancies have been evaluated using \egs{}~\cite{egs5} simulation program 
-whose \moliere{} formulation of multiple scattering show good agreement with previous studies 
-for a wide range of materials and projectiles~\cite{Attwood:2005zz,Shen:1978ha,Gottschalk1993467}. 
-Despite all data taken with a photon beam in the Test run, the angular distribution of the pair 
-produced electron and positron emerging from the converter with different converter thickness can 
-be used to study the varying multiple Coulomb scattering contribution (pair production angle is constant). 
-Restricting clusters to a well calibrated region of the ECal we observe, within our systematic 
-uncertainties , good agreement with the rates predicted by \egs{}, see Tab.~\ref{tab:mcs}.
+Trigger rates observed in the Test run are dominated by multiple scattered pair-produced \ee pairs in the 
+converter. In simulated events, the rate of triggers depend on the modeling of the pairs angular distribution 
+and the sub-sequent multiple Coulomb scattering in the converter. Rates from different converter 
+thicknesses are used to study the varying multiple Coulomb scattering contribution (pair production 
+angle is constant). Restricting clusters to a well calibrated region of the ECal and subtracting the 
+"no converter" background we see agreement with the rates predicted by the \egs{} simulation 
+program, see Tab.~\ref{tab:mcs}.
 %\begin{center}
@@
 %\end{center}
-
-\subsection{Trigger Performance}
-As described in Sec.~\ref{sec:fadc} and shown in Fig.~\ref{fig:hps_trigger_data} the energy from each 
-crystals are measured differently in the trigger and what is readout from the ECal. 
-The trigger performance was studied by simulating the 
-trigger for each event and comparing to how the events were actually triggered.
-First, we simulate the FADC trigger path by converting from readout hits (with fixed-size window 
-integration) to trigger hits (time-over-threshold integration). Secondly, the CTP clustering 
-algorithm and the trigger decision from the SSP is simulated before we compare the trigger decision 
-and trigger time to what was reported by the actual trigger. For every event, the trigger reports the trigger 
-decision as a bit mask (top half, bottom half or both) and the time the trigger fired. To eliminate trigger 
-bias, we use a tag and probe method: to study the trigger performance in one half of the ECal, we select 
-events which triggered the other half and where there was exactly one probe cluster in the ECal half 
-under study. We then measure trigger efficiency as the fraction of tagged events that fired the trigger in 
-the probe half as a function of the probe cluster energy, shown in Fig.~\ref{fig:turnon}. 
-\begin{figure}[ht]
-\begin{center}
-{\small
-	\includegraphics[width=7cm]{figures/h_cl_E_probedata_eff_h_cl_E_probeMC_eff_dataMC_1351-v7-trig-tagBot.pdf}
-	\caption{Trigger efficiency in both halves of the ECal for data and simulation as a 
-	function of cluster energy.}
-\label{fig:turnon}
-}
-\end{center}
-\end{figure}
-The trigger turn-on is slow and reaches an uneven plateau just below 1~GeV for two reasons;  
-gain variations between different crystals lead to the threshold variations and the nonlinearity of 
-the time-over-threshold integral means that the effective threshold is higher for clusters that span 
-multiple crystals. The effective trigger threshold is therefore dependent on position and energy of 
-the particle as well as cluster multiplicity.
-
-As a cross-check, the turn-on from the trigger threshold was measured to be 1280 in units of ADC counts 
-as expected. The threshold was not perfectly sharp because of uncertainties in the conversion from 
-readout to trigger hits described above, but based on comparisons with simulation we found that the 
-trigger worked exactly as specified.
+This gives further confidence that the dominant source of background occupancy for HPS, multiple Coulomb 
+scattered beam electrons, is well described. 
+%One of the main goals of the Test run was to evaluate the description of the tails of the 
+%multiple Coulomb scattering to gain further confidence in the expected detector occupancy in the full HPS 
+%experiment. Those occupancies have been evaluated using \egs{}~\cite{egs5} simulation program 
+%whose \moliere{} formulation of multiple scattering show good agreement with previous studies 
+%for a wide range of materials and projectiles~\cite{Attwood:2005zz,Shen:1978ha,Gottschalk1993467}. 
+%Despite all data taken with a photon beam in the Test run,
 
@@
 \section{Acknowledgements}
+The authors are grateful for the support from Hall~B at JLab and especially Hall~B technicians 
+for support during installation and decommissioning. They also would like to commend the CEBAF 
+personnel for achieving good performance when we needed it; the last few hours of operating CEBAF6. 
+The tremendous support from home institutions and supporting staff also needs praise from the authors.
+
+This work has been supported by the US Department of Energy.
 

### 2014-03-25 hps-testrun-nim.tex
Added MCS references.

@@
 %\end{center}
-This gives further confidence that the dominant source of background occupancy for HPS, multiple Coulomb 
-scattered beam electrons, is well described. 
+This gives further confidence that the dominant source of background occupancy for HPS, multiple 
+Coulomb scattered beam electrons, is well 
+described~\cite{Attwood:2005zz,Shen:1978ha,Gottschalk1993467} . 
 %One of the main goals of the Test run was to evaluate the description of the tails of the 

### 2014-04-02 hps-testrun-nim.tex
Edit from John.

@@
 \begin{abstract}
-Construction and design of the Heavy Photon Search (HPS) experiment, designed to search for an 
-\ee resonance from heavy photon production in a fixed-target setup at the Thomas Jefferson 
-Accelerator Facility (JLab), is ongoing. As a first stage, a test apparatus was constructed and 
-operated at JLab to demonstrate that the apparatus and data acquisition systems are technically 
-feasible and that the trigger rates and occupancies encountered in electron-beam running are as 
-simulated. Given dedicated running time with electron beams, the HPS Test apparatus is 
-capable of searching for heavy photons in unexplored regions of parameter space.  Charged 
-particle tracks are measured with a compact forward silicon microstrip detector and 
-electromagnetic showers from electrons and photons are detected in a dense array of 
-PbWO$_{4}$ crystals. To allow clean passage of the scattered intense electron beam after 
-the thin tungsten target foil while keeping sensitivity to low-mass heavy photons,  the sensitive region 
-of the detectors are place at $\pm 15$~mrad with respect to the horizontal beam plane. 
+The  Heavy Photon Search (HPS), an experiment to search for a hidden sector photon in fixed target 
+electroproduction, is preparing for installation at the Thomas Jefferson National Accelerator Facility 
+(JLab) in the Fall of 2014.  As the first stage of this project, the HPS Test run apparatus was 
+constructed and operated in 2012 to demonstrate the experiment's technical feasibility and to  confirm 
+that the trigger rates and occupancies are as expected. This paper describes the Test Run apparatus 
+and readout electronics and its performance. In this setting, a heavy photon can be identified as a 
+narrow\ee  mass peak above the trident background or as a decay vertex displaced from
+the production target, so charged particle tracking and vertexing are needed for its detection. In the 
+HPS Test run, charged particles are measured
+with a compact forward silicon microstrip vertex/tracker inside a dipole magnet. Electromagnetic 
+showers are detected in a PbW0$_{4}$ 
+crystal calorimeter situated behind the magnet used to trigger the experiment and identify 
+electrons and positrons. Both detectors are placed close to the 
+beam line and split top-bottom. This arrangement  provides sensitivity to low-mass heavy photons,  
+allows clear  passage of the unscattered beam, 
+and avoids the spray of degraded electrons coming from the target. 
 The discrimination between prompt and displaced \ee pairs requires the first layer of silicon 
-sensors to be placed only 10~cm behind the target and 0.5~mm from the beam. 
-The HPS Test apparatus included the high-speed trigger and data acquisition needed for 
-running with electron beams. Details of the layout and performance of the Test detectors and 
-associated readout electronics are presented. 
+sensors be placed only 10~cm downstream of the target. The expected signal is small, and the 
+trident background huge, so the experiment requires very large statistics. Accordingly, the
+HPS Test run utilizes  high-rate readout and data acquisition electronics and a fast trigger to
+perfectly exploit the essentially 100\% duty cycle of the CEBAF accelerator.
 \end{abstract}
@@
 \label{introduction}
-Heavy photons, aka "hidden sector" or "dark" photons, or from here on \Aprime{}, are particles with 
-mass $10-1000$~MeV 
-which couple weakly to the Standard Model photon~\cite{Holdom:1985ag}, so can be radiated by 
-electrons, and can decay 
-into \ee pairs, albeit at rates far below those of QED trident processes. They have been suggested by 
-numerous Beyond Standard Model theories and as an explanation of the current muonic $g-2$ 
-anomaly, and may couple directly to hidden sector particles that may constitute all or some of the 
-dark matter~\cite{ArkaniHamed:2008qn}. 
+The heavy photon (\Aprime{}), aka a "hidden sector" or "dark" photon, is a particle with mass 
+$10-1000$~MeV which couples weakly to electric charge by mixing with the Standard Model 
+photon~\cite{Holdom:1985ag}. Consequently, it can be radiated by electrons and subsequently decay 
+into \ee pairs, albeit at rates far below those of QED trident processes. Heavy photons have been 
+suggested by numerous Beyond Standard Model theories `\cite{Essig:2013lka}, to explain the 
+discrepancy 
+between theory and experiment of the muon's $g-2$ ~\cite{Pospelov:2008zw}, and as a possible 
+explanation of recent astrophysical anomalies.  Heavy photons  couple directly to  hidden sector 
+particles with "dark" or "hidden sector" charge; these particles
+could constitute all or some of the dark matter~\cite{ArkaniHamed:2008qn}. 
 Current phenomenology highlights the $20-1000$~MeV/c$^{2}$ mass range, and 
-suggests that \Aprime's couple to electric charge with strength $\epsilon$e, where 
-$\epsilon$ is in the range of $10^{-3} -10^{-5}$. [REFERENCE]. This range of parameters makes 
-\Aprime{} searches viable in moderate energy fixed target 
-electroproduction~\cite{Bjorken:2009mm}, but require large data sets and good mass resolution
-to identify a small mass peak above the copious QED background at very small production 
-angles. At small couplings, \Aprime's become long-lived, so detection of a displaced decay 
-vertex can reject the prompt QED background and boost experimental sensitivity.
-
-The HPS experiment~\cite{HPS_proposal_2010} uses both invariant mass and 
-vertex signatures by placing a $\approx 1$~m long silicon tracking and vertexing detector 10~cm 
-downstream  of a 0.25\%~$\chi_0$ tungsten target inside a dipole magnet. The experiment runs at high 
-rates (up to 50kHz), exploiting the 
-100\% duty cycle of the Thomas Jefferson National Accelerator Facility (JLab) CEBAF accelerator to 
-accumulate the need statistics. The trigger is provided by a fast electromagnetic calorimeter just 
-downstream of the tracking detector.
+suggests that  the coupling to electric charge, $\epsilon$e, has $\epsilon$ in the range of 
+$10^{-3} -10^{-5}$. [REFERENCE]. This range of parameters makes \Aprime{} searches viable in 
+medium energy fixed target electroproduction~\cite{Bjorken:2009mm}, but requires large data sets and 
+good mass resolution to identify a small mass peak above the copious QED background. At small 
+couplings, \Aprime's become long-lived, so detection of a displaced decay vertex can reject the prompt 
+QED background and boost experimental sensitivity.
+
+The HPS experiment~\cite{HPS_proposal_2010} uses both invariant mass and secondary
+vertex signatures to search for A's. It uses  a $\approx 1$~m long silicon tracking and vertexing detector
+inside a dipole magnet to measure charged particle trajectories and a fast electromagnetic calorimeter 
+just downstream of the magnet to provide a trigger and identify electrons. The experiment utilizes very 
+high rate front end electronics and runs at high trigger rates (up to 50kHz), exploiting the 100\% duty 
+cycle of the Thomas Jefferson National Accelerator Facility (JLab) CEBAF accelerator to accumulate 
+the needed statistics.
 
@@
 Its purposes included demonstrating that the apparatus and data acquisition systems are 
-technically feasible and that the trigger rates and occupancies encountered in electron-beam 
+technically feasible and  the trigger rates and occupancies to be  encountered in electron-beam 
 running are as simulated. Given dedicated running time with electron beams, the HPS Test Run 
 apparatus is capable of searching for heavy photons in unexplored regions of parameter space.    
-The stringent constraints on the detector requirements therefore also applied to the Test detector:
+The key design criteria for HPS and the HPS Test Run are the same:
 \begin{itemize}
@@
 
-The Test apparatus was installed on April 19, 2012, and ran parasitically with the HDice 
-experiment~\cite{HDice}, using its photon beam, until May 18. The JLab run schedule 
+The Test apparatus was installed on April 19, 2012, and ran parasitically in the photon beam of the HDice 
+experiment~\cite{HDice} until May 18. The JLab run schedule 
 precluded any dedicated electron beam running, but the HPS Test Run was allowed a short and 
-valuable dedicated run with the photon beam. Most technologies used in the Test apparatus will 
-be used in the HPS detector with some improvements to each of the systems; both from lessons 
-learned during running of the Test run but also from less schedule and budget constraints.
-
+valuable dedicated run at the end of scheduled CEBAF running. This final running provided
+enough data to demonstrate the functionality of the apparatus, document its performance, and
+explore trigger rates, as shown below. 
 This paper reviews the HPS Test apparatus; documents the performance of the trigger, 
@@
 
-%Of particular importance, data from the dedicated photon beam running has been used to 
-%compare the measured trigger rates with those expected in simulation. The Test Run trigger rate is 
-%almost entirely due to photons which have converted to \ee pairs in a thin target upstream of HPS 
-%and it 
-%is sensitive to their multiple Coulomb scattering in the conversion target.  During electron beam 
-%running, 
-%the tails of the multiply Coulomb scattered primary beam are the dominant source of occupancy in %the 
-%tracker and trigger rate in the electromagnetic calorimeter. 
-%The trigger rates in the Test Run are also sensitive to the tails of the multiple Coulomb
-%scattering distribution. Good agreement between the measured and simulated rates confirms
-%our understanding of multiple Coulomb scattering and 
-%the reliability of the background simulation used to benchmark the physics reach of the HPS 
-%experiment.
+This paper reviews the HPS Test apparatus; documents the performance of the trigger, 
+data acquisition, silicon tracking detector, and the electromagnetic calorimeter at the level assumed 
+in calculating the physics reach of the HPS experiment.
 
@@
 The HPS Test apparatus was designed to run in Hall~B at JLab using the CEBAF electron beam, a 
-499~MHz beam, at an energy of 2.2 and 6.6~GeV and currents between 200 and 600~nA.  
+499~MHz beam, at an energies of 2.2 and 6.6~GeV and currents between 200 and 600~nA.  
 The overall design of the experiment follows from the kinematics of \Aprime{} production which 
-typically results in final state particles within a few degrees of the incoming beam, especially at low 
+typically results in a final state particle within a few degrees of the incoming beam, especially at low 
 $m_{\textrm{A}^\prime}$. Detectors must therefore be placed close to the beam. 
-The intense electron beam and the degraded electrons after the target are spread out horizontally by 
-the analyzing magnet constitute a "dead zone" which must be completely avoided. The apparatus is 
-split vertically $15$~mrad above and below the beam plane and the beam is transported in vacuum 
-to minimize beam-gas interaction backgrounds. Even so, background occupancy in the detectors 
-remain high and are dominated by the degraded primary beam, so high rate detectors, a fast trigger, 
+The intense electron beam enlarges downstream after multiple scattering in the target and electrons 
+which have radiated in the target disperse horizontally in the field of the analyzing magnet. Together 
+they constitute a "wall of flame" which must be completely avoided. Accordingly, 
+the apparatus is split vertically to avoid a "dead zone", the region within $\pm 15$~mrad of the beam 
+plane. In addition, the beam is transported in vacuum through the tracker to minimize beam-gas 
+interaction backgrounds. Even with these precautions, the occupancies of sensors near the beam 
+plane are high, dominated by the
+multiple Coulomb scattering of the primary beam, so high rate detectors, a fast trigger, 
 and excellent time tagging are required to minimize their impact.  
-At masses below $2 m_\mu$ only decays to electrons are allowed, so the key trigger comes from a PbWO$_{4}$ crystal calorimeter. 
+The trigger comes from a highly-segmented  PbWO$_{4}$ crystal calorimeter located just downstream 
+of the dipole magnet. 
  %\begin{multicols}{2}
@@
 
-The silicon tracking and vertexing detector for HPS Test, or SVT, operates in an existing vacuum 
-chamber inside the pair spectrometer analyzing magnet in Hall B at JLab.  There are five 
-measurement stations, or ``layers,'' placed immediately downstream of the target. Each layer 
+The silicon tracking and vertexing detector for HPS Test, or SVT, resides in a vacuum 
+chamber inside the pair spectrometer analyzing magnet in Hall B at JLab. The SVT has five 
+measurement stations, or ``layers,'' beginning10 cm downstream of the target. Each layer 
 comprises a pair of closely-spaced silicon microstrip sensors responsible for measuring a single 
@@
 sensors of each layer provides three-dimensional tracking and vertexing throughout the acceptance 
-of the detector with one redundant layer. Each layer In order to accommodate the dead zone, the 
-SVT is built in two halves that are mirror reflections of one another about the plane of the nominal 
-electron beam.  Each layer in one half are supported on a common support plate with independent 
-cooling and readout.
-
-Each half of the electromagnetic calorimeter, or ECal, consists of 221 PbWO$_4$ crystals arranged 
-in rectangular formation. There are five rows with 46 modules in each row except the row closest to 
-the beam plane which has 37. The light from each crystal 
-is read out by Avalanche Photodiode (APD) glued on the back surface of the crystal. 
-Signals from the APDs were amplified using custom-made amplifier boards before being sent to the 
-readout electronics.
+of the detecto. In order to accommodate the dead zone, the 
+SVT is built in two halves that are approximately mirror reflections of one another about the plane of the 
+nominal electron beam.  Each layer in one half is supported on a common support plate with 
+independent cooling and readout.
+
+The electomagnetic calorimeter (ECal) is also split into two halves. Each half of the ECal consists of 
+221 PbWO$_4$ crystals arranged in rectangular formation. There are five rows with 46 modules in 
+each row except the row closest to the beam plane which has 37. The light from each crystal 
+is read out by an Avalanche Photodiode (APD) glued on the back surface of the crystal. 
+Signals from the APDs are amplified using custom-made amplifier boards before being sent to the 
+data acquisition electronics.
 
@@
 be operating normally;  the fraction of dead or noisy channels varied from 2.4\% to 4.7\% throughout 
-the Test run. Most of these were due to 2-4 misconfigured APV25 ASICs, a known noisy 
-half-module and a couple of known APV25 ASICs.
+the Test run. Most of these losses were due to 2-4 misconfigured APV25 ASICs, a known noisy 
+half-module and problems in two particular APV25 ASICs.
 
@@
 
-After a trigger is received, six samples of the corresponding output of the APV25 ASIC shaper circuit are 
-digitized. The six pedestal-subtracted samples from every channel in the SVT are the basis for offline hit 
-reconstruction. The typical pulse shape obtained shown in Fig.~\ref{fig:pulse_shape} also 
-demonstrates that the SVT was well timed in to the trigger with the rise of the pulse at the 3rd sampling 
+After a trigger is received, the amplitude  of every  APV25 analoge output  is sampled and digitized in 
+six consecutive time bins, separated by roughly 25~ns.  
+The typical pulse shape obtained is shown in Fig.~\ref{fig:pulse_shape}. As the figure demonstrates,  
+the SVT was well timed-in to the trigger with the rise of the pulse at the 3rd sampling 
 point.
@@
 
-In order to find the time and amplitude of each hit, $t_0$,  the six samples from each channel are fitted to 
-an ideal $CR-RC$ function. After clustering hits on a sensor, the hit time for each cluster is computed as 
-the amplitude-weighted average of the individually fitted $t_0$ on each channel. The $t_0$-resolution is 
-studied by comparing the cluster hit time with the average of all cluster hit times on the track, 
-see Fig.~\ref{fig:tracktime}, which has the expected jitter due to clock phase and trigger, 
+In order to find the time, $t_0$, and amplitude of each hit, the six samples from each channel are fitted 
+to an ideal $CR-RC$ function. After clustering hits on a sensor, the hit time for each cluster is computed 
+as the amplitude-weighted average of the individually fitted $t_0$ on each channel. The 
+$t_0$-resolution is studied by comparing the cluster hit time with the average of all cluster hit times on 
+the track, see Fig.~\ref{fig:tracktime}, which has the expected jitter due to clock phase and trigger, 
 approximately 25~ns. 

### 2014-04-02 hps-testrun-nim.tex
More edits based on comments from John

@@
 
- Data was taken on three different converter thicknesses with a beam current varying between 
-30-70~nA and repeated with the reverse field setting of the PS dipole magnet.
+ Data was taken on three different converter thicknesses with photon fluxes between 
+ 1.1-2.6$\times10^{8}$/s ($0.55<$E$_\gamma<5.5$~GeV) at beam currents varying between 
+ 30-90~nA and repeated with the reverse field setting of the PS dipole magnet.
 \begin{table}[]
@@
 By selecting \ee{} pairs from the triggered events we are able to study basic distributions of pair 
-production kinematics. Pairs of opposite charge tracks, one in the top and one in the bottom half of the 
-SVT, with momentum larger than 400~MeV were selected. The pair production kinematics are relatively 
-well reproduced given the alignment of the tracker as shown in Fig.~\ref{fig:pair_kin}.
-
-The expected momentum resolution from simulation is between 4-5\% 
-for tracks in the momentum range of the Test run. This is significantly smaller than the accuracy at 
-which we're able estimate the scale and resolution in the Test run. By looking at the agreement 
+production kinematics. Pairs of oppositely charged tracks, one in the top and one in the bottom half of 
+the SVT, with momentum larger than 400~MeV were selected. The pair production kinematics are 
+relatively well reproduced as shown in Fig.~\ref{fig:pair_kin}.
+
+The expected momentum resolution from simulation is between 4-5\% for tracks in the momentum 
+range of the Test run. By looking at the agreement 
 between data and simulation in the shape of the kinematic distributions for single- and two track 
 events and adjusting the overall momentum scale and smearing simulated events with a 
-Gaussian resolution we estimate an uncertainty of 10\% on both the momentum scale and 
-resolution.
+Gaussian resolution we estimate an agreement with the nominal scale and resolution to within 10\%.
  \begin{center}
@@
 \end{center}
-In the Test run, as well as in electron running with HPS, the dominating source of uncertainty in the 
+In the Test run, as well as in electron running with HPS, the dominant source of uncertainty in the 
 tracking and vertexing is multiple Coulomb scattering. For the vertexing performance the foremost 
@@
 While residual alignment show small shifts good agreement on the widths between data and simulated 
-events, indicating a good understanding of our material budget and distribution in the SVT.  
+events, indicating a good understanding of our material budget and distribution in the SVT.  Having 
+the dominant contribution to the vertex resolution approximately right demonstrates that the resolution 
+in HPS, with a target at 10~cm, will be as calculated.
 %Furthermore, tails of the vertex distributions are impossible to study with the finite data sample obtained 
@@
 	\includegraphics[width=7cm]{figures/h_ep_data_0_h_ep_MC_0_dataMC_1351-v6-v6gains_2-trig-top-cl600reg0.pdf}
-	\caption{The ECal energy over track momentum ratio ($E$/$p$) comparing data and simulation} 
+	\caption{The ECal energy over track momentum ratio ($E$/$p$) comparing data and simulation 
+	for inclusive events in the top half of the ECal.} 
 	\label{fig:gains}
@@
 \label{sec:mcs}
-Trigger rates observed in the Test run are dominated by multiple scattered pair-produced \ee pairs in the 
-converter. In simulated events, the rate of triggers depend on the modeling of the pairs angular distribution 
-and the sub-sequent multiple Coulomb scattering in the converter. Rates from different converter 
+Trigger rates observed in the Test run are dominated by multiple Coulomb scattered \ee pairs in the 
+converter. In simulated events, the rate of triggers depend on the modeling of the pairs angular 
+distribution and the subsequent multiple Coulomb scattering in the converter. Rates from different 
+converter 
 thicknesses are used to study the varying multiple Coulomb scattering contribution (pair production 

### 2014-04-03 hps-testrun-nim.tex
Comments by Sho.

@@
 to a 
-trigger processing board (CTP) in the same crate every. Contrary to the readout path 
+trigger processing board (CTP) in the same crate. Contrary to the readout path 
 described in Sec.~\ref{sec:fadc}, this energy is a pedestal subtracted time-over-threshold sum with 
@@
 the programmable energy threshold ($\approx270$~MeV). Crystals in the 
-fixed-window are included in the sum if the leading edge of the pulse occurred within a 8~ns time 
-window (4~ns minimum). To take into account clock skew and jitter throughout the system, the
-clustering algorithm can allow for crystal hits from up to seven previous or future 4~ns clock cycles to 
-contribute to the cluster sum.  A separate sub-system board (SSP) receives the clusters (only the 
+fixed-window are included in the sum if the leading edge of the pulse occurred within a 32~ns time 
+window to take into account clock skew and jitter throughout the system.
+%, the clustering algorithm can allow for crystal hits from up to seven previous or future 4~ns clock %cycles to contribute to the cluster sum.  
+A separate sub-system board (SSP) receives the clusters (only the 
 highest energy 3x3 window to deal with overlapping and very large clusters) from 
@@
 that required by the SVT APV25 ASIC. During the Test run, for the most part the trigger system 
-required only a single cluster in either the top or bottom Ecal halves and was tested to above 100~kHz 
-trigger rates by lowering thresholds.
+required only a single cluster in either the top or bottom Ecal halves and was tested to trigger rates 
+above 100~kHz by lowering thresholds.
 
@@
 In order to minimize cable length for the analog APV25 output signal the ATCA crate was located 
-approximately 1~m from the beam line, next to our cable vacuum feed troughs.   
+approximately 1~m from the beam line, next to our cable vacuum feed-troughs.   
 Before shielding with lead-blankets was arranged, we observed two failures of normally reliable ATCA 
@@
 collects digitized information, processes it, and sends it on to the event builder. For the ECal, both 
-VXS crates run ROC applications in a single blade Intel-based CPU module running under CentOS 
+VXS crates run ROC applications in a single blade Intel-based CPU module running CentOS 
 Linux OS. For the SVT DAQ, the ROC application runs on the external PC under RHEL. 
@@
 the SVT was well timed-in to the trigger with the rise of the pulse at the 3rd sampling 
-point.
+point. Note that in the Test run the APV25 ASICs were operating with a 50~ns shaping time.  
 \begin{figure}[]
@@
 $t_0$-resolution is studied by comparing the cluster hit time with the average of all cluster hit times on 
-the track, see Fig.~\ref{fig:tracktime}, which has the expected jitter due to clock phase and trigger, 
-approximately 25~ns. 
+the track, see Fig.~\ref{fig:tracktime}. 
 \begin{figure}[]
@@
 subtracting a pedestal and apply a conversion factor to convert ADC counts to energy. 
-The pedestals are measured using special runs where each trigger records 100 samples of signals from 
-the APDs with 4~ns between each sample. The pedestals were extracted from the 
-part of the window before the actual hit in the calorimeter. After subtracting the pedestal, modules with 
-integrated pulse energy of about 73~MeV are clustered using a simple algorithm similar to the one 
+The pedestals are measured using special runs where each trigger records 100 samples of signals 
+from the APDs with 4~ns between each sample. The pedestals were extracted from the 
+part of the window before the actual hit in the calorimeter. Modules with signal above the threshold  
+are clustered using a simple algorithm similar to the one 
 deployed for the trigger (see Sec.~\ref{sec:trigger}). Due to the high effective readout threshold of 
-$73$~MeV the average number of crystals in a cluster was $\sim 3$ and the simple clustering algorithm 
-worked well for reconstruction of the detected shower energy. An average noise level of approximately 
-15~MeV was measured in special pedestal runs.
+73~MeV the average number of crystals in a cluster was $\sim 3$ and the simple clustering 
+algorithm worked well for reconstruction of the detected shower energy. An average noise level of 
+approximately 15~MeV was measured in special pedestal runs.
 
@@
 trigger for each event and comparing to how the events were actually triggered.
-First, we simulate the FADC trigger path by converting from readout hits (with fixed-size window 
-integration) to trigger hits (time-over-threshold integration). Secondly, the CTP clustering 
-algorithm and the trigger decision from the SSP is simulated before we compare the trigger decision 
-and trigger time to what was reported by the actual trigger. For every event, the trigger reports the trigger 
-decision as a bit mask (top half, bottom half or both) and the time the trigger fired. To eliminate trigger 
-bias, we use a tag and probe method: to study the trigger performance in one half of the ECal, we select 
+To eliminate trigger bias, we use a tag and probe method: to study the trigger performance in one half 
+of the ECal, we select 
 events which triggered the other half and where there was exactly one probe cluster in the ECal half 
@@
 
-As a cross-check, the turn-on from the trigger threshold was measured to be 1280 in units of ADC counts 
-as expected. The threshold was not perfectly sharp because of uncertainties in the conversion from 
-readout to trigger hits described above, but based on comparisons with simulation we found that the 
+As a cross-check we simulate the FADC trigger path by converting from readout hits (with fixed-size 
+window integration) to trigger hits (time-over-threshold integration). The CTP clustering 
+algorithm and the trigger decision from the SSP is simulated before we compare the trigger decision 
+and trigger time to what was reported by the actual trigger. For every event, the trigger reports the 
+trigger decision as a bit mask (top half, bottom half or both) and the time the trigger fired.
+The turn-on from the trigger threshold was measured to be 1280 in units of ADC counts as expected. 
+The threshold was not perfectly sharp because of uncertainties in the conversion from readout to trigger 
+hits described above, but based on comparisons with simulation we found that the 
 trigger worked exactly as specified.

### 2014-04-03 hps-testrun-nim.tex
Comments by Ben Raydo.

@@
 The  Data Acquisition system combines two architectures, the Advanced Telecom Communications 
-Architecture (ATCA) based SVT readout system and VXS based digitization and triggering system for 
-the ECal. The system was designed to run at up to 20~kHz trigger rate.
+Architecture (ATCA) based SVT readout system and VMEbus Switched Serial (VXS) based digitization 
+and triggering system for the ECal. The system was designed to run at up to 20~kHz trigger rate.
 
@@
 
-The design of the SVT is primarily driven by direct physics requirement and constraints from the 
+The design of the SVT is primarily driven by direct physics requirements and constraints from the 
 environment at the interaction region. The \Aprime decay products 
@@
 after a radiation dose larger than $X$~MRad. The lead-tungstate (PbOW$_{4}$) crystal inner 
-calorimeter of the CLAS detector [REFERENCE] in operation since 2005 in Hall B meet all the 
-requirements set by HPS. The modules from this calorimeter have been subsequently repurposed for 
-HPS.
+calorimeter of the CLAS detector~\cite{2008erhm.conf..421N} in operation since 2005 in Hall B meets 
+all the requirements set by HPS. The modules from this calorimeter have been subsequently 
+repurposed for HPS.
 
@@
 $<4^{\circ}$~F uniformity) to stabilize the crystal light yield and the operation of the APDs and its 
-preamplifiers. Four printed circuit boards mounted on the backplane penetrated the enclosure and was 
-used to supply the $\pm 5$~V 
-operating voltage for the preamplifiers and the 400~V bias voltage to the APDs and to read out signals 
-from the APDs. Each half of the ECal was divided into 12 bias voltage groups with a gain uniformity 
-of about 20\%.
+preamplifiers. 
+Four printed circuit boards mounted on the backplane penetrated the enclosure and was used to 
+supply the $\pm 5$~V operating voltage for the preamplifiers, 400~V bias voltage to the APDs, and to 
+read out signals from the APDs. Each half of the ECal was divided into 12 bias voltage groups with a 
+gain uniformity of about 20\%.
 
@@
 threshold (for the Test run this was set to $\approx70$~MeV) are 
-summed and stored in a 17-bit register for readout.
+summed and stored in a 17-bit register for readout. In addition a 4~ns resolution timestamp of the 
+threshold crossing is reported in the readout for each pulse.
 This scheme significantly compresses the data output of the FADC. During offline data analysis, a 
@@
 (bottom) half of the ECal.
-In the Test run 385 out of 442 modules (87\%) was used in offline reconstruction, 39 modules were 
+In the Test run 385 out of 442 modules (87\%) were used in offline reconstruction, 39 modules were 
 disabled or not read out (no FADC channel available, no APD bias voltage or masked out due to 
-excessive noise) and 18 was masked offline due to noise. 
+excessive noise) and 18 were masked offline due to noise. 
 %\begin{figure}[]
@@
 two DAQ architectures. The SVT DAQ is based on Advanced Telecom Communications Architecture 
-(ATCA) hardware while the ECal uses VXS based hardware. Data from the sub-detectors are only 
+(ATCA) hardware while the ECal uses VMEbus Switched Serial (VXS) based hardware. Data from the 
+sub-detectors are only 
 readout when a trigger signal from the trigger system is received formed on input from the ECal. 
@@
  \end{figure}
-Each channel on the FADC board have an 
-independent data path to send 5-bit pulse energy and 3-bit pulse arrival time information every 32~ns 
-to a 
-trigger processing board (CTP) in the same crate. Contrary to the readout path 
+Each channel on the FADC board has an independent data path to send 5-bit pulse energy and 3-bit 
+pulse arrival time information every 32~ns to a trigger processing board (CTP), which is in the same 
+crate. The 3-bit pulse arrival time allows the trigger to know the pulse timing at 4~ns resolution. 
+Contrary to the readout path 
 described in Sec.~\ref{sec:fadc}, this energy is a pedestal subtracted time-over-threshold sum with 
@@
 window to take into account clock skew and jitter throughout the system.
-%, the clustering algorithm can allow for crystal hits from up to seven previous or future 4~ns clock %cycles to contribute to the cluster sum.  
-A separate sub-system board (SSP) receives the clusters (only the 
-highest energy 3x3 window to deal with overlapping and very large clusters) from 
-the top and bottom half CTP every 32~ns and searches for pairs of clusters in a 8~ns wide 
-trigger window. The trigger supervisor (TS) generates all the necessary signals and controls the 
-entire DAQ system readout through the trigger interface units installed in every crate that participate 
-in the readout process.
+The CTP only accepts clusters with the highest energy 3x3 window locally to deal with overlapping and 
+very large clusters. The sub-system board (SSP) receives the clusters from the top and bottom half CTP 
+at a maximum of 250MHz and searches for pairs of clusters in a 8 ns wide coincidence window. The 
+SSP sends triggers to the trigger supervisor (TS), which generates all the necessary signals and 
+controls the entire DAQ system readout through the trigger interface units installed in every crate that 
+participate in the readout process.
 

### 2014-04-03 hps-testrun-nim.tex
Comments by Matt Graham

@@
 
-\section{Performance}
+\section{Reconstruction and Performance}
 
@@
 
-After a trigger is received, the amplitude  of every  APV25 analoge output  is sampled and digitized in 
+After a trigger is received, the amplitude  of every  APV25 analogue output is sampled and digitized in 
 six consecutive time bins, separated by roughly 25~ns.  
-The typical pulse shape obtained is shown in Fig.~\ref{fig:pulse_shape}. As the figure demonstrates,  
+The typical, pedestal subtracted, pulse shape obtained is shown in Fig.~\ref{fig:pulse_shape}. 
+As the figure demonstrates,  
 the SVT was well timed-in to the trigger with the rise of the pulse at the 3rd sampling 
-point. Note that in the Test run the APV25 ASICs were operating with a 50~ns shaping time.  
+point.  
 \begin{figure}[]
@@
 \end{figure}
+In order to find the time, $t_0$, and amplitude of each hit, the six samples from each channel are fitted 
+to an ideal $CR-RC$ function. Note that in the Test run the APV25 ASICs were operating with a 50~ns 
+shaping time. 
 These hits are passed through a simple clustering algorithm which forms clusters by grouping adjacent 
@@
 provide the absolute charge normalization.
-%\begin{figure}[]
-%\begin{center}
-%{\small
-%	%\includegraphics[width=7cm]{figures/run1351_mip_small.pdf}
-%	\includegraphics[width=7cm]{figures/mip_top_layer_2.png}
-%    	\caption{ The cluster charge distribution for hits associated with a track. }
-%	\label{fig:cluster_pulse}
-%}
-%\end{center}
-%\end{figure}
-
-In order to find the time, $t_0$, and amplitude of each hit, the six samples from each channel are fitted 
-to an ideal $CR-RC$ function. After clustering hits on a sensor, the hit time for each cluster is computed 
+\begin{figure}[]
+\begin{center}
+{\small
+	%\includegraphics[width=7cm]{figures/run1351_mip_small.pdf}
+	\includegraphics[width=7cm]{figures/mip_top_layer_2.png}
+    	\caption{ The cluster charge distribution for hits associated with track follow the characteristic 		Landau shape. }
+	\label{fig:cluster_pulse}
+}
+\end{center}
+\end{figure}
+After clustering hits on a sensor, the hit time for each cluster is computed 
 as the amplitude-weighted average of the individually fitted $t_0$ on each channel. The 
-$t_0$-resolution is studied by comparing the cluster hit time with the average of all cluster hit times on 
-the track, see Fig.~\ref{fig:tracktime}. 
+$t_0$ resolution is studied by comparing the cluster hit time with the average of all cluster hit times on 
+the track shown in Fig.~\ref{fig:tracktime}. 
 \begin{figure}[]
@@
 pulse shape differing from our idealized fit function which will be improved in the future. Reducing the 
-APV25 ASIC pulse shaping time will also improve time resolution. 
+APV25 ASIC pulse shaping time to 35~ns will also improve time resolution. 
 These results show that we can operate with the six sample readout mode of the APV25 chip and 
@@
 
-While occupancy was slightly larger than expected, good agreement between data and simulation was 
-found after taking into account dead or noisy channels. The hit efficiency was estimated by measuring 
+Good agreement between observed and simulated occupancies after taking into account dead or 
+noisy channels. The hit reconstruction efficiency was estimated by measuring 
 the number of good tracks with a hit close to the extrapolated intersection of a given sensor that was 
-excluded from the track fit itself. Tracks which intersect regions with known bad channels or very close to 
-in the edge region are excluded. The hit efficiency, see Fig.~\ref{fig:hit_efficiency}, was measured to be 
-above 98\% and fairly uniform across the SVT.
+excluded from the track fit itself. Tracks which intersect regions with known bad channels or very close 
+to in the edge region are excluded. The hit reconstruction efficiency, see Fig.~\ref{fig:hit_efficiency}, 
+was measured to be above 98\% and fairly uniform across the SVT.
 \begin{figure}[]
@@
 \end{figure}
+
 The spatial resolution of similar microstrip sensors is well established by test beam data, against which 
@@
 The expected momentum resolution from simulation is between 4-5\% for tracks in the momentum 
-range of the Test run. By looking at the agreement 
-between data and simulation in the shape of the kinematic distributions for single- and two track 
-events and adjusting the overall momentum scale and smearing simulated events with a 
-Gaussian resolution we estimate an agreement with the nominal scale and resolution to within 10\%.
+range of the Test run.
+
+By comparing the shapes of the kinematic distributions for single- and two track events between data 
+and simulation we estimate an agreement with the nominal scale and resolution to within 10\%.
  \begin{center}
@@
 }
-While residual alignment show small shifts good agreement on the widths between data and simulated 
-events, indicating a good understanding of our material budget and distribution in the SVT.  Having 
-the dominant contribution to the vertex resolution approximately right demonstrates that the resolution 
-in HPS, with a target at 10~cm, will be as calculated.
+While residual alignment show small shifts, the good agreement  between data and simulated 
+events of the widths indicates a good understanding of the material budget and distribution in the SVT.  
+Having  the dominant contribution to the vertex resolution approximately right demonstrates that the 
+resolution in HPS, with a target at 10~cm, will be as calculated.
 %Furthermore, tails of the vertex distributions are impossible to study with the finite data sample obtained 
@@
 to determine the conversion factors from ADC counts to energy. To compare data and simulation, all 
-inoperable or noisy channels in the SVT and ECal was disabled in both data and simulation so that any 
-efficiency or bias that affect the data should be reflected in the simulation. 
+inoperable or noisy channels in the SVT and ECal were disabled in both data and simulation so that 
+any efficiency or bias that affect the data should be reflected in the simulation. 
 %Furthermore, a conversion factor calibration is performed to equalize the gains of  each channel. 
@@
 % $\frac{\sum_j w_{j,i}}{\sum_j\frac{P_j}{E_j}w_{j,i}}$.
-Iteratively, conversion coefficients for each crystal is adjusted until the $E$/$p$ ratio in data and 
-simulation are similar. The distribution of the $E$/$p$ ratio in data and simulation are compared in 
+Iteratively, conversion coefficients for each crystal were adjusted until the $E$/$p$ ratio in data and 
+simulation were similar. The distribution of the $E$/$p$ ratio in data and simulation are compared in 
 Fig.~\ref{fig:gains}. 
@@
 	\caption{The ECal energy over track momentum ratio ($E$/$p$) comparing data and simulation 
-	for inclusive events in the top half of the ECal.} 
+	for single cluster triggers in the top half of the ECal.} 
 	\label{fig:gains}
@@
 \subsection{Trigger Performance}
-As described above the energy from each 
+As described above in Sec.~\ref{sec:triggerdaq}, the energy from each 
 crystal is measured differently in the trigger and what is readout from the ECal. 
@@
 \label{sec:mcs}
-Trigger rates observed in the Test run are dominated by multiple Coulomb scattered \ee pairs in the 
+Trigger rates observed in the Test run are dominated by multiple Coulomb scattered \ee{} pairs in the 
 converter. In simulated events, the rate of triggers depend on the modeling of the pairs angular 
@@
 \end{tabular}
-\caption{ Observed and predicted number of events for 1~s of beam at 90~nA for three different converter 
+\caption{ Observed and predicted event rate (in Hz) normalized to 90~nA for three different converter 
 thicknesses. The uncertainty on the prediction includes systematic uncertainties from ECal alignment, background normalization, beam current normalization and limited statistics in the simulation.}

### 2014-04-03 hps-testrun-nim.tex
Stepans comments

@@
 The HPS Test apparatus was designed to run in Hall~B at JLab using the CEBAF electron beam, a 
-499~MHz beam, at an energies of 2.2 and 6.6~GeV and currents between 200 and 600~nA.  
+499~MHz beam, at energies of 2.2 and 6.6~GeV and currents between 200 and 600~nA.  
 The overall design of the experiment follows from the kinematics of \Aprime{} production which 
@@
 The silicon tracking and vertexing detector for HPS Test, or SVT, resides in a vacuum 
-chamber inside the pair spectrometer analyzing magnet in Hall B at JLab. The SVT has five 
+chamber inside the Pair Spectrometer (PS) dipole magnet in Hall B at JLab. The SVT has five 
 measurement stations, or ``layers,'' beginning10 cm downstream of the target. Each layer 
@@
 sensors of each layer provides three-dimensional tracking and vertexing throughout the acceptance 
-of the detecto. In order to accommodate the dead zone, the 
+of the detector. In order to accommodate the dead zone, the 
 SVT is built in two halves that are approximately mirror reflections of one another about the plane of the 
@@
 the setup on the beam line. The SVT was installed inside the Hall B pair 
-spectrometer magnet (PS) vacuum chamber with the ECal mounted downstream of it. Both the 
+spectrometer magnet vacuum chamber with the ECal mounted downstream of it. Both the 
 SVT and the ECal were retracted off the beam plane compared to nominal electron beam runing to 
@@
 During the dedicated HPS Test run period, the collimated (6.4~mm diameter), photon beam passes 
-through the aluminum PS pair converter and later the HPS system as illustrated in 
+through the gold PS pair converter and later the HPS system as illustrated in 
 Fig.~\ref{fig:schematic_testrun_vs_erun}.
@@
 \end{figure}
-The scintillation light, approximately $X$ photoelectrons/MeV, is readout by a 
+The scintillation light, approximately $3$ photoelectrons/MeV, is readout by a 
 5$\times$5~mm$^2$ Hamamatsu S8664-55 Avalanche Photodiode (APD) with 75\% quantum 
@@
 The low gain of APDs ($\sim 200$) was compensated with custom made preamplifier boards, which 
-provide factor of 2000 amplification of the APD signal.
+provide factor of $2600$ amplification of the APD signal.
 
@@
 about the plane of the nominal electron beam to avoid interfering with the 15~mrad "dead zone". 
-As shown in Fig.~\ref{fig:ecal}, the 221 modules, supported by aluminum support frames, in each half 
+As shown in Fig.~\ref{fig:ecal}, the 221 modules in each half, supported by aluminum support frames, 
 are arranged in rectangular formation with 5 layers and 46 crystals/layer except for the layer closest to 
@@
 \label{sec:fadc}
-After a 2:1 signal splitter, $1/3$ of an amplified APD signal ($2/3$ is sent to a timing module) is fed to a 
-single channel of a JLab flash ADC (FADC) board~\cite{fadc}.
+After a 2:1 signal splitter, $1/3$ of an amplified APD signal is fed to a 
+single channel of a JLab flash ADC (FADC) board~\cite{fadc}. $2/3$ of the signal is sent to a 
+discriminator module and then to a TDC for a timing measurement. 
 %\begin{figure}[]
@@
 FADC channels, i.e. one half of the ECal, the CTP performs cluster finding and calculates cluster 
-energy, shape and timing information. The 3x3 fixed-window, highly parallel, FPGA-based cluster 
+energy and timing information. The 3x3 fixed-window, highly parallel, FPGA-based cluster 
 algorithm simultaneously searches for up to 125 clusters with energy sum larger than 
@@
 The integrated pulse of each FADC channel was converted to energy by  
-subtracting a pedestal and apply a conversion factor to convert ADC counts to energy. 
+subtracting a pedestal and applying a conversion factor to convert ADC counts to energy. 
 The pedestals are measured using special runs where each trigger records 100 samples of signals 
@@
 in data indicates imperfect calibration and noise of the ECal modules. This level of calibration and the 
-agreement with simulation was found to be sufficient to study normalized event rates on the Test run.
+agreement with simulation was found to be sufficient to study normalized event rates in the Test run.
 
@@
 \section{Acknowledgements}
-The authors are grateful for the support from Hall~B at JLab and especially Hall~B technicians 
-for support during installation and decommissioning. They also would like to commend the CEBAF 
-personnel for achieving good performance when we needed it; the last few hours of operating CEBAF6. 
-The tremendous support from home institutions and supporting staff also needs praise from the authors.
+The authors are grateful for the support from Hall~B at JLab and especially the Hall~B engineering 
+group for support during installation and decommissioning. They also would like to commend the 
+CEBAF personnel for good beam performance; the last few hours of operating CEBAF6. 
+The tremendous support from home institutions and supporting staff also needs praise from the 
+authors.
 

### 2014-04-03 hps-testrun-nim.tex
Fixed preamp number

@@
 During the dedicated HPS Test run period, the collimated (6.4~mm diameter), photon beam passes 
-through the gold PS pair converter and later the HPS system as illustrated in 
+through the PS pair converter gold foil and later the HPS system as illustrated in 
 Fig.~\ref{fig:schematic_testrun_vs_erun}.
@@
 The low gain of APDs ($\sim 200$) was compensated with custom made preamplifier boards, which 
-provide factor of $2600$ amplification of the APD signal.
+provide factor of $2333$ amplification of the APD signal.
 

### 2014-04-08 hps-testrun-nim.tex
Edits from Tim

@@
 electroproduction, is preparing for installation at the Thomas Jefferson National Accelerator Facility 
-(JLab) in the Fall of 2014.  As the first stage of this project, the HPS Test run apparatus was 
+(JLab) in the Fall of 2014.  As the first stage of this project, the HPS Test Run apparatus was 
 constructed and operated in 2012 to demonstrate the experiment's technical feasibility and to  confirm 
@@
 the production target, so charged particle tracking and vertexing are needed for its detection. In the 
-HPS Test run, charged particles are measured
+HPS Test Run, charged particles are measured
 with a compact forward silicon microstrip vertex/tracker inside a dipole magnet. Electromagnetic 
@@
 trident background huge, so the experiment requires very large statistics. Accordingly, the
-HPS Test run utilizes  high-rate readout and data acquisition electronics and a fast trigger to
+HPS Test Run utilizes  high-rate readout and data acquisition electronics and a fast trigger to
 perfectly exploit the essentially 100\% duty cycle of the CEBAF accelerator.
@@
 good mass resolution to identify a small mass peak above the copious QED background. At small 
-couplings, \Aprime's become long-lived, so detection of a displaced decay vertex can reject the prompt 
+couplings, \Aprime{} become long-lived, so detection of a displaced decay vertex can reject the prompt 
 QED background and boost experimental sensitivity.
@@
 typically results in a final state particle within a few degrees of the incoming beam, especially at low 
-$m_{\textrm{A}^\prime}$. Detectors must therefore be placed close to the beam. 
+$m_{\Aprime}$. Detectors must therefore be placed close to the beam. 
 The intense electron beam enlarges downstream after multiple scattering in the target and electrons 
@@
 \section{The HPS Test Run Beamline}
-The HPS Test run studied multiple Coulomb scattering of electrons and positrons from 
+The HPS Test Run studied multiple Coulomb scattering of electrons and positrons from 
 bremsstrahlung photons produced in the Hall B tagged photon facility. 
@@
 electrons are deflected away from detectors by the dipole magnet of the photon tagging system. 
-During the dedicated HPS Test run period, the collimated (6.4~mm diameter), photon beam passes 
+During the dedicated HPS Test Run period, the collimated (6.4~mm diameter), photon beam passes 
 through the PS pair converter gold foil and later the HPS system as illustrated in 
@@
 \includegraphics[ width=7cm]{figures/photon_vs_electron_beam_schematic.png}
-\caption{\small{Illustrative comparison of HPS Test run photon beam compared to the HPS electron 
+\caption{\small{Illustrative comparison of HPS Test Run photon beam compared to the HPS electron 
 beam.}}
@@
 \end{table}
-The photon beam line during the test run produced a relatively large fraction of pairs 
+The photon beam line during the Test Run produced a relatively large fraction of pairs 
 originating upstream of the converter position. This contribution was measured during data taking 
@@
 The design of the SVT is primarily driven by direct physics requirements and constraints from the 
-environment at the interaction region. The \Aprime decay products 
+environment at the interaction region. The \Aprime{} decay products 
 have momenta in the range of 1~GeV, so multiple scattering dominates mass and vertexing 
 uncertainties for any possible material budget, so the SVT must minimize the amount of 
-material in the tracking volume. The signal yield for long-lived \Aprime's is very small, so 
+material in the tracking volume. The signal yield for long-lived \Aprime{} is very small, so 
 the rejection of prompt vertexes must be exceedingly pure, on the order of $10^{-7}$, in order to 
@@
 that the active region of a sensor can be placed as close to 1.5 mm from the center of the beam, 
-defining the 15 mrad ``dead zone" mentioned previously, to maximize low-mass \Aprime acceptance 
+defining the 15 mrad ``dead zone" mentioned previously, to maximize low-mass \Aprime{} acceptance 
 with decay products nearly collinear with the beam axis. At the edge of this ``dead zone," the 
@@
 degeneracy of having five identical layers and minimizes fakes from ghost hits to improve pattern 
-recognition. Altogether, the SVTcomprises 20 sensors for a total of 12780 readout channels. 
+recognition. Altogether, the SVT has 20 sensors for a total of 12780 readout channels. 
 %=======================
@@
 performance the sensors for the SVT are readout by the APV25 ASIC developed for the CMS 
-experiment at CERN~\cite{French:2001xb}. The APV25 can capture two successive samples of three 
-of the output of the shaper at a sampling rate of approximately 40~MHz.  By fitting the known 
+experiment at CERN~\cite{French:2001xb}. The APV25 can capture successive samples of the shaper output 
+in groups of three at a sampling rate of approximately 40~MHz.  By fitting the known 
 $CR$-$RC$ shaping curve to these samples, the initial time of the hit can be determined to a precision 
@@
 SVT with respect to CEBAF beam line. The resulting survey-based alignment has the position of the 
-silicon sensors correct to within a few hundred microns measured from tracks in the Test run data. 
+silicon sensors correct to within a few hundred microns measured from tracks in the Test Run data. 
 A more sophisticated global track-based alignment technique to reach final alignment precision 
@@
 The technology and design choices are largely driven by the need for a compact forward design 
-covering the SVT \Aprime acceptance and able to fully absorb 
+covering the SVT \Aprime{} acceptance and able to fully absorb 
 electrons and positrons with energy between $0.5$-$6.5$~GeV, fine granularity and signal 
@@
 
-During the Test run, both halves were held in place by four vertical bars attached to an above rail, 
+During the Test Run, both halves were held in place by four vertical bars attached to an above rail, 
 placing the front face of the crystals 147~cm from the upstream edge of the magnet and with a 
@@
 of the pipeline from 5 samples before and 30 after the signal crossed a programmable 
-threshold (for the Test run this was set to $\approx70$~MeV) are 
+threshold (for the Test Run this was set to $\approx70$~MeV) are 
 summed and stored in a 17-bit register for readout. In addition a 4~ns resolution timestamp of the 
@@
 calibrated pedestal value is subtracted to obtain the actual summed energy.
-Two 20-slot VXS crates with 14 (13) FADC boards were employed in the Test run to read out the top 
+Two 20-slot VXS crates with 14 (13) FADC boards were employed in the Test Run to read out the top 
 (bottom) half of the ECal.
-In the Test run 385 out of 442 modules (87\%) were used in offline reconstruction, 39 modules were 
+In the Test Run 385 out of 442 modules (87\%) were used in offline reconstruction, 39 modules were 
 disabled or not read out (no FADC channel available, no APD bias voltage or masked out due to 
@@
 %\includegraphics[width=8cm]{figures/fadc_datapath_diagram.png}
-%\caption{The two different readout modes of the FADC used in the Test run.}
+%\caption{The two different readout modes of the FADC used in the Test Run.}
 %\label{fig:hps_trigger_data}
@@
 designed to handle trigger rates above 50~kHz and has a latency set to $\approx 3~\mu$s to match 
-that required by the SVT APV25 ASIC. During the Test run, for the most part the trigger system 
+that required by the SVT APV25 ASIC. During the Test Run, for the most part the trigger system 
 required only a single cluster in either the top or bottom Ecal halves and was tested to trigger rates 
@@
 \end{figure}
-The first generation RCE used in the Test run consisted of a Virtex~5 FPGA with 1~GB of DDR3 RAM. 
+The first generation RCE used in the Test Run consisted of a Virtex~5 FPGA with 1~GB of DDR3 RAM. 
 A schematic overview of the system is shown in Fig.~\ref{fig:svtdaq}. 
@@
 
-While trigger rates during the Test run was significantly lower this system was tested at trigger rates up 
+While trigger rates during the Test Run was significantly lower this system was tested at trigger rates up 
 to 20~kHz and 50~MB/s.
@@
 servers. The DAQ network system is a network router providing 10Gbit/s high-speed connection 
-to the JLab computing facility for long-term storage. For the Test run, both the SVT and ECal ROC had a 
+to the JLab computing facility for long-term storage. For the Test Run, both the SVT and ECal ROC had a 
 1Gbit/s link to the network router.
@@
 
-For the duration of the Test run all SVT modules and APV25 chips were configured to their 
+For the duration of the Test Run all SVT modules and APV25 chips were configured to their 
 nominal operating points~\cite{Jones:1069892} with all sensors reverse-biased at 180~V.  The 
@@
 be operating normally;  the fraction of dead or noisy channels varied from 2.4\% to 4.7\% throughout 
-the Test run. Most of these losses were due to 2-4 misconfigured APV25 ASICs, a known noisy 
+the Test Run. Most of these losses were due to 2-4 misconfigured APV25 ASICs, a known noisy 
 half-module and problems in two particular APV25 ASICs.
@@
 In order to find the time, $t_0$, and amplitude of each hit, the six samples from each channel are fitted 
-to an ideal $CR-RC$ function. Note that in the Test run the APV25 ASICs were operating with a 50~ns 
+to an ideal $CR-RC$ function. Note that in the Test Run the APV25 ASICs were operating with a 50~ns 
 shaping time. 
@@
 The expected momentum resolution from simulation is between 4-5\% for tracks in the momentum 
-range of the Test run.
+range of the Test Run.
 
@@
 \end{center}
-In the Test run, as well as in electron running with HPS, the dominant source of uncertainty in the 
+In the Test Run, as well as in electron running with HPS, the dominant source of uncertainty in the 
 tracking and vertexing is multiple Coulomb scattering. For the vertexing performance the foremost 
@@
 %Furthermore, tails of the vertex distributions are impossible to study with the finite data sample obtained 
-%in the Test run. Nevertheless, useful information can still be 
+%in the Test Run. Nevertheless, useful information can still be 
 %obtained by studying the vertex distributions. Figure~\ref{fig:vtx_pos} shows the distance of closest 
@@
 in data indicates imperfect calibration and noise of the ECal modules. This level of calibration and the 
-agreement with simulation was found to be sufficient to study normalized event rates in the Test run.
+agreement with simulation was found to be sufficient to study normalized event rates in the Test Run.
 
@@
 \label{sec:mcs}
-Trigger rates observed in the Test run are dominated by multiple Coulomb scattered \ee{} pairs in the 
+Trigger rates observed in the Test Run are dominated by multiple Coulomb scattered \ee{} pairs in the 
 converter. In simulated events, the rate of triggers depend on the modeling of the pairs angular 
@@
 described~\cite{Attwood:2005zz,Shen:1978ha,Gottschalk1993467} . 
-%One of the main goals of the Test run was to evaluate the description of the tails of the 
+%One of the main goals of the Test Run was to evaluate the description of the tails of the 
 %multiple Coulomb scattering to gain further confidence in the expected detector occupancy in the full HPS 
@@
 %for a wide range of materials and projectiles~\cite{Attwood:2005zz,Shen:1978ha,Gottschalk1993467}. 
-%Despite all data taken with a photon beam in the Test run,
+%Despite all data taken with a photon beam in the Test Run,
 
@@
 %The angular distribution of the pair produced electron and positron emerging 
-%from the converter in the test run has comparable contributions from {\it i)} the pair production angle
+%from the converter in the Test Run has comparable contributions from {\it i)} the pair production angle
 %and {\it ii)} the MCS of the electron and positron in the converter after production. By measuring the 
@@
 %\end{table}
-%The photon beam line during the test run produced a relatively 
+%The photon beam line during the Test Run produced a relatively 
 %large fraction of pairs 
@@
 
-%The test run achieved the following detector performance:\begin
+%The Test Run achieved the following detector performance:\begin
 %{enumerate}
@@
 %rate was tested to greater than 100~kHz
-% deficiencies found in test run trigger performance are 
+% deficiencies found in Test Run trigger performance are 
 %addressed for the 2014-2015 run
@@
 %detector layout will be identical, retaining the most successful 
-%elements of the test run apparatus and addressing the weaknesses %identified during assembly and 
+%elements of the Test Run apparatus and addressing the weaknesses %identified during assembly and 
 %operation to ensure the success of the 

### 2014-04-08 hps-testrun-nim.tex
Alphabetical author list. Consistent notion of HPS Test Run.

@@
 
-\input{author_list_hps_PAC39_compact}
+\input{author_list_hps_PAC39_compact_alphabetical_order}
 
@@
 constructed and operated in 2012 to demonstrate the experiment's technical feasibility and to  confirm 
-that the trigger rates and occupancies are as expected. This paper describes the Test Run apparatus 
+that the trigger rates and occupancies are as expected. This paper describes the HPS Test Run apparatus 
 and readout electronics and its performance. In this setting, a heavy photon can be identified as a 
-narrow\ee  mass peak above the trident background or as a decay vertex displaced from
+narrow \ee{}  mass peak above the trident background or as a decay vertex displaced from
 the production target, so charged particle tracking and vertexing are needed for its detection. In the 
@@
 and avoids the spray of degraded electrons coming from the target. 
-The discrimination between prompt and displaced \ee pairs requires the first layer of silicon 
+The discrimination between prompt and displaced \ee{} pairs requires the first layer of silicon 
 sensors be placed only 10~cm downstream of the target. The expected signal is small, and the 
@@
 photon~\cite{Holdom:1985ag}. Consequently, it can be radiated by electrons and subsequently decay 
-into \ee pairs, albeit at rates far below those of QED trident processes. Heavy photons have been 
-suggested by numerous Beyond Standard Model theories `\cite{Essig:2013lka}, to explain the 
+into \ee{} pairs, albeit at rates far below those of QED trident processes. Heavy photons have been 
+suggested by numerous beyond Standard Model theories~\cite{Essig:2013lka}, to explain the 
 discrepancy 
@@
 suggests that  the coupling to electric charge, $\epsilon$e, has $\epsilon$ in the range of 
-$10^{-3} -10^{-5}$. [REFERENCE]. This range of parameters makes \Aprime{} searches viable in 
+$10^{-3} -10^{-5}$. This range of parameters makes \Aprime{} searches viable in 
 medium energy fixed target electroproduction~\cite{Bjorken:2009mm}, but requires large data sets and 
@@
 The HPS experiment~\cite{HPS_proposal_2010} uses both invariant mass and secondary
-vertex signatures to search for A's. It uses  a $\approx 1$~m long silicon tracking and vertexing detector
+vertex signatures to search for \Aprime{}. It uses  a $\approx 1$~m long silicon tracking and vertexing detector
 inside a dipole magnet to measure charged particle trajectories and a fast electromagnetic calorimeter 
@@
 
-The HPS Test apparatus, a simplified version of the HPS experiment, was proposed and 
-approved at Thomas Jefferson National Accelerator Facility (JLab) as the first stage of HPS. 
+The HPS Test Run apparatus, a simplified version of the HPS experiment, was proposed and 
+approved at JLab as the first stage of HPS. 
 Its purposes included demonstrating that the apparatus and data acquisition systems are 
@@
 \item detector components that can survive and efficiently operate in a high radiation environment 
-with local doses exceeding $100$~Mrad.
+with local doses exceeding 100~Mrad.
 \end{itemize}
 
-The Test apparatus was installed on April 19, 2012, and ran parasitically in the photon beam of the HDice 
+The HPS Test Run apparatus was installed on April 19, 2012, and ran parasitically in the photon beam of the HDice 
 experiment~\cite{HDice} until May 18. The JLab run schedule 
@@
 explore trigger rates, as shown below. 
-This paper reviews the HPS Test apparatus; documents the performance of the trigger, 
+This paper reviews the HPS Test Run apparatus; documents the performance of the trigger, 
 data acquisition, silicon tracking detector, and the electromagnetic calorimeter at the level assumed 
@@
 
-This paper reviews the HPS Test apparatus; documents the performance of the trigger, 
+This paper reviews the HPS Test Run apparatus; documents the performance of the trigger, 
 data acquisition, silicon tracking detector, and the electromagnetic calorimeter at the level assumed 
@@
     \includegraphics[width=0.8\textwidth]{figures/hps_testrun_rendering}
-\caption{Rendering of the HPS Test apparatus installed on the beam line.}
+\caption{Rendering of the HPS Test Run apparatus installed on the beam line.}
 \label{fig:testrundetector}
@@
 }
-The HPS Test apparatus was designed to run in Hall~B at JLab using the CEBAF electron beam, a 
+The HPS Test Run apparatus was designed to run in Hall~B at JLab using the CEBAF electron beam, a 
 499~MHz beam, at energies of 2.2 and 6.6~GeV and currents between 200 and 600~nA.  
@@
 typically results in a final state particle within a few degrees of the incoming beam, especially at low 
-$m_{\Aprime}$. Detectors must therefore be placed close to the beam. 
+$m_{\Aprime{}}$. Detectors must therefore be placed close to the beam. 
 The intense electron beam enlarges downstream after multiple scattering in the target and electrons 
@@
 {\small
-\caption{Overview of the coverage, segmentation and performance of the HPS Test detector. }
+\caption{Overview of the coverage, segmentation and performance of the HPS Test Run detector. }
 \begin{tabular}{lccccccc}
@@
 
-The silicon tracking and vertexing detector for HPS Test, or SVT, resides in a vacuum 
+The silicon tracking and vertexing detector for HPS Test Run, or SVT, resides in a vacuum 
 chamber inside the Pair Spectrometer (PS) dipole magnet in Hall B at JLab. The SVT has five 
-measurement stations, or ``layers,'' beginning10 cm downstream of the target. Each layer 
+measurement stations, or ``layers,'' beginning 10 cm downstream of the target. Each layer 
 comprises a pair of closely-spaced silicon microstrip sensors responsible for measuring a single 
-coordinate, or ``view.'' Introduction of a small (50 or 100~mrad) stereo angle between the two 
+coordinate, or ``view''. Introduction of a small (50 or 100~mrad) stereo angle between the two 
 sensors of each layer provides three-dimensional tracking and vertexing throughout the acceptance 
@@
 spectrometer magnet vacuum chamber with the ECal mounted downstream of it. Both the 
-SVT and the ECal were retracted off the beam plane compared to nominal electron beam runing to 
+SVT and the ECal were retracted off the beam plane compared to nominal electron beam running to 
 allow clean passage of the photon beam through the system. 
@@
  Data was taken on three different converter thicknesses with photon fluxes between 
- 1.1-2.6$\times10^{8}$/s ($0.55<$E$_\gamma<5.5$~GeV) at beam currents varying between 
+ 0.4-1.3$\times10^{8}$/s ($0.55<$E$_\gamma<5.5$~GeV) at beam currents varying between 
  30-90~nA and repeated with the reverse field setting of the PS dipole magnet.
@@
 \end{table}
-The photon beam line during the Test Run produced a relatively large fraction of pairs 
+The photon beam line during the HPS Test Run produced a relatively large fraction of pairs 
 originating upstream of the converter position. This contribution was measured during data taking 
 with ``empty'' converter runs i.e. removing the converter but with all other conditions the same. 
-The runs taken during the time dedicated to HPS Test is summarized in Tab.~\ref{tab:currents}.
+The runs taken during the time dedicated to HPS Test Run is summarized in Tab.~\ref{tab:currents}.
 
@@
 eliminate all prompt backgrounds. To achieve the required vertexing performance the first layer of the 
-SVT must be placed no more than about 10 cm downstream of the target. At that distance, it is found 
-that the active region of a sensor can be placed as close to 1.5 mm from the center of the beam, 
-defining the 15 mrad ``dead zone" mentioned previously, to maximize low-mass \Aprime{} acceptance 
+SVT must be placed no more than about 10~cm downstream of the target. At that distance, it is found 
+that the active region of a sensor can be placed as close to 1.5~mm from the center of the beam, 
+defining the 15~mrad ``dead zone" mentioned previously, to maximize low-mass \Aprime{} acceptance 
 with decay products nearly collinear with the beam axis. At the edge of this ``dead zone," the 
-radiation dose approaches $10^{15}$ electrons/cm$^2$/month, or roughly 
+radiation dose approaches $10^{15}$~electrons/cm$^2$/month, or roughly 
 $3 \times 10^{14}$~\fluenceunit{}/month~\cite{Rashevskaya:2002nd}, 
@@
     \includegraphics[width=7cm]{figures/2012-101-PHOTON-DETECTOR-001}
-\caption{\small{Both halves of the HPS Test SVT after final assembly at SLAC.  The cooling manifolds and 
+\caption{\small{Both halves of the HPS Test Run SVT after final assembly at SLAC.  The cooling manifolds and 
 integrated cable runs are clearly seen.} }
@@
 The sensors for the SVT are $p+$-on-$n$, single sided, AC coupled, polysilicon-biased microstrip 
-sensors fabricated on $<100>$ silicon and have 30 (60) micron sense (readout) pitch over their 
+sensors fabricated on $<100>$ silicon and have 30 (60)~$\mu$m sense (readout) pitch over their 
 $4\times10$~cm$^2$ surface. This sensor technology was selected to match the requirement of 
@@
 SVT with respect to CEBAF beam line. The resulting survey-based alignment has the position of the 
-silicon sensors correct to within a few hundred microns measured from tracks in the Test Run data. 
-A more sophisticated global track-based alignment technique to reach final alignment precision 
+silicon sensors correct to within a few hundred microns measured from tracks in the HPS Test Run 
+data. A more sophisticated global track-based alignment technique to reach final alignment precision 
 well below 50~$\mu$m is being developed.
@@
 The electromagnetic calorimeter (ECal), installed downstream of the PS dipole magnet, performs two 
-essential 
-functions for the experiment: it provides a trigger signal to select what events to read out from the 
-detector sub-systems and is used in the analysis to identify electrons and positrons. 
+essential functions for the experiment: it provides a trigger signal to select what events to read out from 
+the detector sub-systems and is used in the analysis to identify electrons and positrons. 
 The technology and design choices are largely driven by the need for a compact forward design 
@@
 electrons and positrons with energy between $0.5$-$6.5$~GeV, fine granularity and signal 
-readout speed to handle 1~MHz/cm$^{2}$ of electromagnetic background and remain operable 
-after a radiation dose larger than $X$~MRad. The lead-tungstate (PbOW$_{4}$) crystal inner 
+readout speed to handle 1~MHz/cm$^{2}$ of electromagnetic background and be radiation hard. 
+The lead-tungstate (PbOW$_{4}$) crystal inner 
 calorimeter of the CLAS detector~\cite{2008erhm.conf..421N} in operation since 2005 in Hall B meets 
@@
 The ECal module shown in Fig.~\ref{fig:ecal-module} is based on a tapered 160~mm long 
-lead-tungstate (PbWO$_{4}$) crystal with a $13.3\times13.3$~mm$^2$ ($16\times16$~mm$^2$) front 
+PbWO$_{4}$ crystal with a $13.3\times13.3$~mm$^2$ ($16\times16$~mm$^2$) front 
 (rear) face wrapped in VM2000 multilayer polymer mirror film. 
@@
 
-During the Test Run, both halves were held in place by four vertical bars attached to an above rail, 
+During the HPS Test Run, both halves were held in place by four vertical bars attached to an above rail, 
 placing the front face of the crystals 147~cm from the upstream edge of the magnet and with a 
@@
 \label{sec:fadc}
-After a 2:1 signal splitter, $1/3$ of an amplified APD signal is fed to a 
-single channel of a JLab flash ADC (FADC) board~\cite{fadc}. $2/3$ of the signal is sent to a 
+After a 2:1 signal splitter, $1/3$ of an amplified APD signal was fed to a 
+single channel of a JLab flash ADC (FADC) board~\cite{fadc}. $2/3$ of the signal was sent to a 
 discriminator module and then to a TDC for a timing measurement. 
@@
 of the pipeline from 5 samples before and 30 after the signal crossed a programmable 
-threshold (for the Test Run this was set to $\approx70$~MeV) are 
+threshold (for the HPS Test Run this was set to $\approx70$~MeV) are 
 summed and stored in a 17-bit register for readout. In addition a 4~ns resolution timestamp of the 
@@
 calibrated pedestal value is subtracted to obtain the actual summed energy.
-Two 20-slot VXS crates with 14 (13) FADC boards were employed in the Test Run to read out the top 
-(bottom) half of the ECal.
-In the Test Run 385 out of 442 modules (87\%) were used in offline reconstruction, 39 modules were 
-disabled or not read out (no FADC channel available, no APD bias voltage or masked out due to 
+Two 20-slot VXS crates with 14 (13) FADC boards were employed in the HPS Test Run to read out the 
+top (bottom) half of the ECal.
+In the HPS Test Run 385 out of 442 modules (87\%) were used in offline reconstruction, 39 modules 
+were disabled or not read out (no FADC channel available, no APD bias voltage or masked out due to 
 excessive noise) and 18 were masked offline due to noise. 
@@
 %\includegraphics[width=8cm]{figures/fadc_datapath_diagram.png}
-%\caption{The two different readout modes of the FADC used in the Test Run.}
+%\caption{The two different readout modes of the FADC used in the HPS Test Run.}
 %\label{fig:hps_trigger_data}
@@
 (ATCA) hardware while the ECal uses VMEbus Switched Serial (VXS) based hardware. Data from the 
-sub-detectors are only 
-readout when a trigger signal from the trigger system is received formed on input from the ECal. 
+sub-detectors are only readout when a trigger signal from the trigger system is received formed on 
+input from the ECal.
+
 \subsection{Trigger system}
 \label{sec:trigger}
-
 The trigger system is designed to select time coincidences of electromagnetic clusters in the 
@@
 very large clusters. The sub-system board (SSP) receives the clusters from the top and bottom half CTP 
-at a maximum of 250MHz and searches for pairs of clusters in a 8 ns wide coincidence window. The 
+at a maximum of 250MHz and searches for pairs of clusters in a 8~ns wide coincidence window. The 
 SSP sends triggers to the trigger supervisor (TS), which generates all the necessary signals and 
@@
 designed to handle trigger rates above 50~kHz and has a latency set to $\approx 3~\mu$s to match 
-that required by the SVT APV25 ASIC. During the Test Run, for the most part the trigger system 
+that required by the SVT APV25 ASIC. During the HPS Test Run, for the most part the trigger system 
 required only a single cluster in either the top or bottom Ecal halves and was tested to trigger rates 
@@
 \end{figure}
-The first generation RCE used in the Test Run consisted of a Virtex~5 FPGA with 1~GB of DDR3 RAM. 
+The first generation RCE used in the HPS Test Run consisted of a Virtex~5 FPGA with 1~GB of DDR3 RAM. 
 A schematic overview of the system is shown in Fig.~\ref{fig:svtdaq}. 
@@
 \end{figure}
-The analog outputs of up to 12 SVT half-modules (60 APV25 ASICs) are digitized on the Rear-Transition-
-Module (RTM), a custom board 
-on the back side of the ATCA crate, interfacing the HPS-specific readout to the generic DAQ components 
-on the 
-COB. A pre-amplifier converts the APV25 differential current output to a different voltage output scaled to 
-the sensitive range of a 14-bit ADC operating at the system clock of 41.667~MHz. The RTM is organized 
+The analog outputs of up to 12 SVT half-modules (60 APV25 ASICs) are digitized on the 
+Rear-Transition-Module (RTM), a custom board on the back side of the ATCA crate, interfacing the 
+HPS-specific readout to the generic DAQ components on the COB. A pre-amplifier converts the APV25 
+differential current output to a different voltage output scaled to the sensitive range of a 14-bit ADC 
+operating at the system clock of 41.667~MHz. The RTM is organized 
 into four sections with each section supporting three SVT half-module hybrids (15 APV25 ASICs). The 
 RTM also includes a 4-channel fiber optic module and supporting logic which is used to interface 
-to the JLab trigger system supervisor. Each section of the RTM is input to a DPM which apply thresholds 
-for data reduction and organizes the sample data into UDP datagrams. The DPM also hosts an I$^{2}$C 
-controller used to configure and monitor the APV25 ASICs. A single ATCA crate with two COB cards 
-was used, one supporting four DPMs and one supporting 3 DPMs and one DPM that is configured as 
-the trigger and data transmission module. The two COB cards and their DPMs are interconnected with a 
-10Gb/s switch card~\cite{Larsen:2011zb} which also hosts two 1Gb/s Ethernet interfaces to the external 
-SVT DAQ PC.
-
-The external PC supports three network interfaces; two standard 1Gb/s Ethernet and one custom low 
+to the JLab trigger system supervisor. Each section of the RTM is input to a DPM which apply 
+thresholds for data reduction and organizes the sample data into UDP datagrams. The DPM also hosts 
+an I$^{2}$C controller used to configure and monitor the APV25 ASICs. A single ATCA crate with two 
+COB cards was used, one supporting four DPMs and one supporting 3 DPMs and one DPM that is 
+configured as the trigger and data transmission module. The two COB cards and their DPMs are 
+interconnected with a 10~Gb/s switch card~\cite{Larsen:2011zb} which also hosts two 1Gb/s Ethernet 
+interfaces to the external SVT DAQ PC.
+
+The external PC supports three network interfaces; two standard 1~Gb/s Ethernet and one custom low 
 latency data reception card. The first is used for slow control and monitoring of the 8 
@@
 
-While trigger rates during the Test Run was significantly lower this system was tested at trigger rates up 
+While trigger rates during the HPS Test Run was significantly lower this system was tested at trigger rates up 
 to 20~kHz and 50~MB/s.
@@
 100~MB/s. The event builder and other critical components run on multicore Intel-based multi-CPU 
-servers. The DAQ network system is a network router providing 10Gbit/s high-speed connection 
-to the JLab computing facility for long-term storage. For the Test Run, both the SVT and ECal ROC had a 
-1Gbit/s link to the network router.
+servers. The DAQ network system is a network router providing 10~Gb/s high-speed connection 
+to the JLab computing facility for long-term storage. For the HPS Test Run, both the SVT and ECal ROC had 
+a 1~Gb/s link to the network router.
 
@@
 
-For the duration of the Test Run all SVT modules and APV25 chips were configured to their 
+For the duration of the HPS Test Run all SVT modules and APV25 chips were configured to their 
 nominal operating points~\cite{Jones:1069892} with all sensors reverse-biased at 180~V.  The 
@@
 be operating normally;  the fraction of dead or noisy channels varied from 2.4\% to 4.7\% throughout 
-the Test Run. Most of these losses were due to 2-4 misconfigured APV25 ASICs, a known noisy 
+the HPS Test Run. Most of these losses were due to 2-4 misconfigured APV25 ASICs, a known noisy 
 half-module and problems in two particular APV25 ASICs.
@@
 The typical, pedestal subtracted, pulse shape obtained is shown in Fig.~\ref{fig:pulse_shape}. 
-As the figure demonstrates,  
-the SVT was well timed-in to the trigger with the rise of the pulse at the 3rd sampling 
-point.  
+As the figure demonstrates,  the SVT was well timed-in to the trigger with the rise of the pulse at the 3rd 
+sampling point.  
 \begin{figure}[]
@@
 In order to find the time, $t_0$, and amplitude of each hit, the six samples from each channel are fitted 
-to an ideal $CR-RC$ function. Note that in the Test Run the APV25 ASICs were operating with a 50~ns 
-shaping time. 
-These hits are passed through a simple clustering algorithm which forms clusters by grouping adjacent 
-strips with the position of a cluster on the sensor determined by the amplitude-weighted mean.
+to an ideal $CR-RC$ function. Note that in the HPS Test Run the APV25 ASICs were operating with a 50~ns 
+shaping time. These hits are passed through a simple clustering algorithm which forms clusters by 
+grouping adjacent strips with the position of a cluster on the sensor determined by the 
+amplitude-weighted mean.
 With a linear gain up to $\approx 3$~MIPs, the cluster charge for hits associated with a track follow 
@@
 \end{figure}
-After correcting for offsets from each sensor (time-of-flight, clock phase) and accounting for the 
-correlation between the $t_0$ and track time,  the extracted $t_0$ resolution is 2.6~ns. This is somewhat 
-worse than the approximately 2~ns resolution expected for S/N~25 which we attribute to the true 
-pulse shape differing from our idealized fit function which will be improved in the future. Reducing the 
-APV25 ASIC pulse shaping time to 35~ns will also improve time resolution. 
+After correcting for offsets from each sensor (time-of-flight and clock phase) and accounting for the 
+correlation between the $t_0$ and track time,  the extracted $t_0$ resolution is 2.6~ns. This is 
+somewhat worse than the approximately 2~ns resolution expected for S/N~25 which we attribute to the 
+true pulse shape differing from our idealized fit function which will be improved in the future. Reducing 
+the APV25 ASIC pulse shaping time to 35~ns will also improve time resolution. 
 These results show that we can operate with the six sample readout mode of the APV25 chip and 
@@
 The single-hit resolution for charged particles with signal to noise ratio above 20, as demonstrated 
-here, is relatively constant at approximately 6~$\mu$m for tracks that enters approximately normal to the 
-sensors as in HPS.
+here, is relatively constant at approximately 6~$\mu$m for tracks that enters approximately normal to 
+the sensors as in HPS.
 
@@
 The expected momentum resolution from simulation is between 4-5\% for tracks in the momentum 
-range of the Test Run.
-
-By comparing the shapes of the kinematic distributions for single- and two track events between data 
-and simulation we estimate an agreement with the nominal scale and resolution to within 10\%.
+range of the HPS Test Run. By comparing the shapes of the kinematic distributions for single- and two 
+track events between data and simulation we estimate an agreement with the nominal scale and 
+resolution to within 10\%.
  \begin{center}
@@
    \includegraphics[width=5cm]{figures/h_sumE_h_sumE_trigsel4hit_pair1351_twotrkfilt-v6-paper}
-\caption{Kinematic distributions for e$^+$e$^-$ pairs selected by opposite charged tracks in the top and bottom half of the tracker: track momentum in the top half of the SVT (left), invariant mass (middle) and the sum of the track momentum for the pair (right).}
+\caption{Kinematic distributions for \ee{} pairs selected by opposite charged tracks in the top and bottom half of the tracker: track momentum in the top half of the SVT (left), invariant mass (middle) and the sum of the track momentum for the pair (right).}
 \label{fig:pair_kin}
@@
 \end{center}
-In the Test Run, as well as in electron running with HPS, the dominant source of uncertainty in the 
+In the HPS Test Run, as well as in electron running with HPS, the dominant source of uncertainty in the 
 tracking and vertexing is multiple Coulomb scattering. For the vertexing performance the foremost 
@@
 upstream from our nominal target position; giving almost collinear tracks in the detector. The increased 
-lever arm over which tracks are extrapolated widens the resolution with up to a factor of eight (depending 
-on momentum) compared to what is achieved at the nominal electron target position for HPS. 
-Figure~\ref{fig:impact_param} shows the horizontal and vertical positions of the extrapolated track at the 
-converter position. 
+lever arm over which tracks are extrapolated widens the resolution with up to a factor of eight 
+(depending on momentum) compared to what is achieved at the nominal electron target position for 
+HPS. Figure~\ref{fig:impact_param} shows the horizontal and vertical positions of the extrapolated track 
+at the converter position. 
 {\small
@@
 %Furthermore, tails of the vertex distributions are impossible to study with the finite data sample obtained 
-%in the Test Run. Nevertheless, useful information can still be 
+%in the HPS Test Run. Nevertheless, useful information can still be 
 %obtained by studying the vertex distributions. Figure~\ref{fig:vtx_pos} shows the distance of closest 
@@
 in data indicates imperfect calibration and noise of the ECal modules. This level of calibration and the 
-agreement with simulation was found to be sufficient to study normalized event rates in the Test Run.
+agreement with simulation was found to be sufficient to study normalized event rates in the 
+HPS Test Run.
 
@@
 \label{sec:mcs}
-Trigger rates observed in the Test Run are dominated by multiple Coulomb scattered \ee{} pairs in the 
+Trigger rates observed in the HPS Test Run are dominated by multiple Coulomb scattered \ee{} pairs in the 
 converter. In simulated events, the rate of triggers depend on the modeling of the pairs angular 
@@
 described~\cite{Attwood:2005zz,Shen:1978ha,Gottschalk1993467} . 
-%One of the main goals of the Test Run was to evaluate the description of the tails of the 
+%One of the main goals of the HPS Test Run was to evaluate the description of the tails of the 
 %multiple Coulomb scattering to gain further confidence in the expected detector occupancy in the full HPS 
@@
 %for a wide range of materials and projectiles~\cite{Attwood:2005zz,Shen:1978ha,Gottschalk1993467}. 
-%Despite all data taken with a photon beam in the Test Run,
+%Despite all data taken with a photon beam in the HPS Test Run,
 
@@
 %
-%One of the main goals of the HPS Test was to evaluate the description of the tails of the MCS
+%One of the main goals of the HPS Test Run was to evaluate the description of the tails of the MCS
 %to gain further confidence in the expected detector occupancy in the full HPS experiment. 
@@
 %The angular distribution of the pair produced electron and positron emerging 
-%from the converter in the Test Run has comparable contributions from {\it i)} the pair production angle
+%from the converter in the HPS Test Run has comparable contributions from {\it i)} the pair production angle
 %and {\it ii)} the MCS of the electron and positron in the converter after production. By measuring the 
@@
 %\end{table}
-%The photon beam line during the Test Run produced a relatively 
+%The photon beam line during the HPS Test Run produced a relatively 
 %large fraction of pairs 
@@
 \section{Summary and Outlook}
-The HPS Test experiment, using a simplified version of the apparatus planned for the full HPS 
+The HPS Test Run experiment, using a simplified version of the apparatus planned for the full HPS 
 experiment in a parasitic photon beam, demonstrated the feasibility of the detector technologies 
@@
 experiment successfully. Studies of multiple Coloumb scattering tails of electrons and positrons from 
-photon conversions further backs expectations from simulation, giving credance to estimates of the 
+photon conversions further backs expectations from simulation, giving credence to estimates of the 
 detector backgrounds expected in electron beam running for HPS.
@@
 
-%In the process of developing the HPS Test design, it was found 
+%In the process of developing the HPS Test Run design, it was found 
 %that this simple system was capable of 
@@
 %we have proposed a new design for the HPS detector that builds 
-%upon the HPS Test , principally 
-%by addressing the compromises made for HPS Test to ensure the 
+%upon the HPS Test Run , principally 
+%by addressing the compromises made for HPS Test Run to ensure the 
 %best possible performance for A$^\prime$ 
@@
 %detector layout will be identical, retaining the most successful 
-%elements of the Test Run apparatus and addressing the weaknesses %identified during assembly and 
+%elements of the HPS Test Run Run apparatus and addressing the weaknesses %identified during assembly and 
 %operation to ensure the success of the 

### 2014-04-22 hps-testrun-nim.tex
switched on line numbers
Ben Raydos comment on 2nd draft.

@@
 %% for the whole article with \linenumbers after \end{frontmatter}.
-%% \usepackage{lineno}
+\usepackage{lineno}
 
@@
 
+ \linenumbers
+
 \clearpage
@@
 and excellent time tagging are required to minimize their impact.  
-The trigger comes from a highly-segmented  PbWO$_{4}$ crystal calorimeter located just downstream 
-of the dipole magnet. 
+The trigger comes from a highly-segmented  lead-tungstate (PbWO$_{4}$) crystal calorimeter located just 
+downstream of the dipole magnet. 
  %\begin{multicols}{2}
@@
 readout speed to handle 1~MHz/cm$^{2}$ of electromagnetic background and be radiation hard. 
-The lead-tungstate (PbOW$_{4}$) crystal inner 
-calorimeter of the CLAS detector~\cite{2008erhm.conf..421N} in operation since 2005 in Hall B meets 
+The PbWO$_{4}$ crystal inner 
+calorimeter of the CLAS detector~\cite{2008erhm.conf..421N}, in operation since 2005 in Hall B, meets 
 all the requirements set by HPS. The modules from this calorimeter have been subsequently 
@@
 The low gain of APDs ($\sim 200$) was compensated with custom made preamplifier boards, which 
-provide factor of $2333$ amplification of the APD signal.
+provide a factor of $2333$ amplification of the APD signal.
 

### 2014-04-22 hps-testrun-nim.tex
Comments from Raphael Dupre on draft v2.

@@
 HPS Test Run, charged particles are measured
-with a compact forward silicon microstrip vertex/tracker inside a dipole magnet. Electromagnetic 
+with a compact forward silicon microstrip tracker inside a dipole magnet. Electromagnetic 
 showers are detected in a PbW0$_{4}$ 
@@
 \hline
-ECal & $15<\theta_{y} < XXXX$ & 442 & 12 & 4~ns & 1 & $1.3\times1.3$~cm$^2$  & $\sigma(E)/E \approx 4.5\%$ \\ 
+ECal & $15<\theta_{y} < XXXX$ & 442 & 12 & 4~ns & 1 & $1.33\times1.33$~cm$^2$  & $\sigma(E)/E \approx 4.5\%$ \\ 
  &  &  &  &  &  & $1.6\times1.6$~cm$^2$  &  \\ 
@@
 
-The silicon tracking and vertexing detector for HPS Test Run, or SVT, resides in a vacuum 
+The silicon vertex tracking and vertexing detector for HPS Test Run, or SVT, resides in a vacuum 
 chamber inside the Pair Spectrometer (PS) dipole magnet in Hall B at JLab. The SVT has five 

### 2014-04-22 hps-testrun-nim.tex
Added new beam line figure. Fixed acceptance numbers.

@@
 \hline
-SVT & $15<\theta_{y} < XXXX$ & 12800 & 14 & $\approx 2$~ns & 5  & $\approx 120~\mu$m $r-\phi$ & $\sigma_{d0,y}  \approx 100~\mu$m \\
-& &  &  &  & (stereo layers) & $\approx 6~\mu$m $z$ & $\sigma_{d0,x} \approx 300~\mu$m \\
+SVT & $15<\theta_{y} < 70$ & 12800 & 14 & $\approx 2$~ns & 5  & $\approx 120~\mu$m $r-\phi$ & $\sigma_{d0,y}  \approx 100~\mu$m \\
+& (5 hits) &  &  &  & (stereo layers) & $\approx 6~\mu$m $z$ & $\sigma_{d0,x} \approx 300~\mu$m \\
 & &  &  &  &  &  & $\sigma_{d0,z}\approx 1$~mm \\
 \hline
-ECal & $15<\theta_{y} < XXXX$ & 442 & 12 & 4~ns & 1 & $1.33\times1.33$~cm$^2$  & $\sigma(E)/E \approx 4.5\%$ \\ 
+ECal & $15<\theta_{y} < 60$ & 442 & 12 & 4~ns & 1 & $1.33\times1.33$~cm$^2$  & $\sigma(E)/E \approx 4.5\%$ \\ 
  &  &  &  &  &  & $1.6\times1.6$~cm$^2$  &  \\ 
@@
 \begin{figure}[]
-    \includegraphics[width=0.5\textwidth]{figures/HPS_dimensions}
+%    \includegraphics[width=0.5\textwidth]{figures/HPS_dimensions}
+    \includegraphics[width=0.45\textwidth]{figures/hps-testrun-beamline-edited2}
 \caption{\small{Layout of the HPS parasitic run.} }

### 2014-04-23 hps-testrun-nim.tex
Adding changes suggested by Larry Weinstein to 2nd draft.

@@
 constructed and operated in 2012 to demonstrate the experiment's technical feasibility and to  confirm 
-that the trigger rates and occupancies are as expected. This paper describes the HPS Test Run apparatus 
-and readout electronics and its performance. In this setting, a heavy photon can be identified as a 
-narrow \ee{}  mass peak above the trident background or as a decay vertex displaced from
-the production target, so charged particle tracking and vertexing are needed for its detection. In the 
-HPS Test Run, charged particles are measured
+that the trigger rates and occupancies are as expected. This paper describes the HPS Test Run 
+apparatus and readout electronics and its performance. In this setting, a heavy photon can be identified 
+as a narrow \ee{}  mass peak above the trident background or as a narrow mass peak with a decay 
+vertex displaced from the production target, so charged particle tracking and vertexing are needed for 
+its detection. In the HPS Test Run, charged particles are measured
 with a compact forward silicon microstrip tracker inside a dipole magnet. Electromagnetic 
@@
 trident background huge, so the experiment requires very large statistics. Accordingly, the
-HPS Test Run utilizes  high-rate readout and data acquisition electronics and a fast trigger to
-perfectly exploit the essentially 100\% duty cycle of the CEBAF accelerator.
+HPS Test Run utilizes  high-rate readout and data acquisition electronics and a fast trigger to exploit 
+the essentially 100\% duty cycle of the CEBAF accelerator.
 \end{abstract}
@@
 \label{introduction}
-The heavy photon (\Aprime{}), aka a "hidden sector" or "dark" photon, is a particle with mass 
+The heavy photon (\Aprime{}), aka a ``hidden sector'' or ``dark'' photon, is a particle with mass 
 $10-1000$~MeV which couples weakly to electric charge by mixing with the Standard Model 
@@
 between theory and experiment of the muon's $g-2$ ~\cite{Pospelov:2008zw}, and as a possible 
-explanation of recent astrophysical anomalies.  Heavy photons  couple directly to  hidden sector 
-particles with "dark" or "hidden sector" charge; these particles
+explanation of recent astrophysical 
+anomalies~\cite{Adriani:2008zr,FermiLAT:2011ab,Aguilar:2013qda}.  Heavy photons  couple directly to  
+hidden sector particles with "dark" or "hidden sector" charge; these particles
 could constitute all or some of the dark matter~\cite{ArkaniHamed:2008qn}. 
@@
 
-The HPS Test Run apparatus, a simplified version of the HPS experiment, was proposed and 
+The HPS Test Run, using a simplified version of the HPS apparatus, was proposed and 
 approved at JLab as the first stage of HPS. 
@@
 precluded any dedicated electron beam running, but the HPS Test Run was allowed a short and 
-valuable dedicated run at the end of scheduled CEBAF running. This final running provided
-enough data to demonstrate the functionality of the apparatus, document its performance, and
+valuable dedicated photon beam run at the end of scheduled CEBAF running. This final running 
+provided enough data to demonstrate the functionality of the apparatus, document its performance, and
 explore trigger rates, as shown below.
-This paper reviews the HPS Test Run apparatus; documents the performance of the trigger, 
-data acquisition, silicon tracking detector, and the electromagnetic calorimeter at the level assumed 
-in calculating the physics reach of the HPS experiment.
-
-This paper reviews the HPS Test Run apparatus; documents the performance of the trigger, 
-data acquisition, silicon tracking detector, and the electromagnetic calorimeter at the level assumed 
-in calculating the physics reach of the HPS experiment.
+
+This paper reviews the HPS Test Run apparatus, documenting the performance of the trigger, 
+data acquisition, silicon tracking detector, and the electromagnetic calorimeter at the level required for 
+calculating the physics reach of the HPS experiment.
 
@@
 The HPS Test Run apparatus was designed to run in Hall~B at JLab using the CEBAF electron beam, a 
-499~MHz beam, at energies of 2.2 and 6.6~GeV and currents between 200 and 600~nA.  
+499~MHz beam, at energies between 2.2 and 6.6~GeV and currents between 200 and 600~nA.  
 The overall design of the experiment follows from the kinematics of \Aprime{} production which 
@@
 The silicon vertex tracking and vertexing detector for HPS Test Run, or SVT, resides in a vacuum 
-chamber inside the Pair Spectrometer (PS) dipole magnet in Hall B at JLab. The SVT has five 
+chamber inside the Pair Spectrometer (PS) dipole magnet in Hall B at JLab. The magnetic field 
+strength was 0.5~T oriented vertically throughout the run. The SVT has five 
 measurement stations, or ``layers,'' beginning 10 cm downstream of the target. Each layer 
@@
 \section{The HPS Test Run Beamline}
-The HPS Test Run studied multiple Coulomb scattering of electrons and positrons from 
-bremsstrahlung photons produced in the Hall B tagged photon facility. 
-Figure~\ref{fig:hpstest_layout} shows the layout of 
+Since an electron beam was unavailable, the HPS Test Run detected the electrons and positrons 
+produced by interactions of the secondary photon beam with a thin foil just upstream of the detectors.  
+The HPS Test Run studied the performance of the detectors and the multiple coulomb scattering of the 
+electrons and positrons. Figure~\ref{fig:hpstest_layout} shows the layout of 
 the setup on the beam line. The SVT was installed inside the Hall B pair 
@@
 electrons are deflected away from detectors by the dipole magnet of the photon tagging system. 
-During the dedicated HPS Test Run period, the collimated (6.4~mm diameter), photon beam passes 
+During the dedicated HPS Test Run period, the collimated (6.4~mm diameter) photon beam passes 
 through the PS pair converter gold foil and later the HPS system as illustrated in 
@@
 
- Data was taken on three different converter thicknesses with photon fluxes between 
- 0.4-1.3$\times10^{8}$/s ($0.55<$E$_\gamma<5.5$~GeV) at beam currents varying between 
- 30-90~nA and repeated with the reverse field setting of the PS dipole magnet.
+ Data was taken on three different converter thicknesses with photon fluxes between 0.4 and 
+ $1.3\times10^8$/s at photon energies between 0.55 and 5.5 GeV produced by a 30 to 90 nA electron 
+ beam. Data was measured for both polarities of the PS dipole magnet.'
 \begin{table}[]
@@
 \end{table}
-The photon beam line during the HPS Test Run produced a relatively large fraction of pairs 
+The photon beam line during the HPS Test Run produced a relatively large number of \ee{} pairs 
 originating upstream of the converter position. This contribution was measured during data taking 
-with ``empty'' converter runs i.e. removing the converter but with all other conditions the same. 
+with ``empty'' converter runs, i.e. removing the converter but with all other conditions the same. 
 The runs taken during the time dedicated to HPS Test Run is summarized in Tab.~\ref{tab:currents}.

### 2014-04-23 hps-testrun-nim.tex
Norman Graf's comments on 2nd draft.

@@
 apparatus and readout electronics and its performance. In this setting, a heavy photon can be identified 
-as a narrow \ee{}  mass peak above the trident background or as a narrow mass peak with a decay 
-vertex displaced from the production target, so charged particle tracking and vertexing are needed for 
-its detection. In the HPS Test Run, charged particles are measured
-with a compact forward silicon microstrip tracker inside a dipole magnet. Electromagnetic 
-showers are detected in a PbW0$_{4}$ 
+as a narrow peak in the \ee{} invariant mass spectrum, above the trident background or as a narrow  
+invariant mass peak with a decay vertex displaced from the production target, so charged particle 
+tracking and vertexing are needed for its detection. 
+In the HPS Test Run, charged particles are measured with a compact forward silicon microstrip tracker 
+inside a dipole magnet. Electromagnetic showers are detected in a PbW0$_{4}$ 
 crystal calorimeter situated behind the magnet used to trigger the experiment and identify 
@@
 HPS Test Run utilizes  high-rate readout and data acquisition electronics and a fast trigger to exploit 
-the essentially 100\% duty cycle of the CEBAF accelerator.
+the essentially 100\% duty cycle of the CEBAF accelerator at JLab.
 \end{abstract}
@@
 The heavy photon (\Aprime{}), aka a ``hidden sector'' or ``dark'' photon, is a particle with mass 
-$10-1000$~MeV which couples weakly to electric charge by mixing with the Standard Model 
+$10-1000$~MeV/c$^{2}$ which couples weakly to electric charge by mixing with the Standard Model 
 photon~\cite{Holdom:1985ag}. Consequently, it can be radiated by electrons and subsequently decay 
@@
 anomalies~\cite{Adriani:2008zr,FermiLAT:2011ab,Aguilar:2013qda}.  Heavy photons  couple directly to  
-hidden sector particles with "dark" or "hidden sector" charge; these particles
+hidden sector particles with ``dark'' or ``hidden sector'' charge; these particles
 could constitute all or some of the dark matter~\cite{ArkaniHamed:2008qn}. 
@@
 The HPS experiment~\cite{HPS_proposal_2010} uses both invariant mass and secondary
-vertex signatures to search for \Aprime{}. It uses  a $\approx 1$~m long silicon tracking and vertexing detector
+vertex signatures to search for \Aprime{}. It uses  a $\approx 1$~m long silicon tracking and vertexing 
+detector
 inside a dipole magnet to measure charged particle trajectories and a fast electromagnetic calorimeter 
 just downstream of the magnet to provide a trigger and identify electrons. The experiment utilizes very 
-high rate front end electronics and runs at high trigger rates (up to 50kHz), exploiting the 100\% duty 
-cycle of the Thomas Jefferson National Accelerator Facility (JLab) CEBAF accelerator to accumulate 
-the needed statistics.
+high-rate front-end electronics and runs at high trigger rates (up to 50kHz), exploiting the 100\% duty 
+cycle of the JLab CEBAF accelerator to accumulate the needed statistics.
 
@@
 detector and minimize beam gas interactions, 
+\item detector components that can survive and efficiently operate in a high radiation environment 
+with local doses exceeding 100~Mrad.
+\item high-rate electronics with excellent timing resolution to minimize out of time backgrounds,
 \item a flexible, redundant and efficient trigger selecting electron and positron pairs at rates up to 
 50~kHz,
+\item data handling rates of 100~MB/s to permanent storage,
 \item excellent track reconstruction efficiency for electrons and positrons,
@@
 backgrounds,
-\item high rate electronics with excellent timing resolution to minimize out of time backgrounds,
-\item data handling rates of 100~MB/s to permanent storage,
-\item detector components that can survive and efficiently operate in a high radiation environment 
-with local doses exceeding 100~Mrad.
 \end{itemize}
@@
 }
-The HPS Test Run apparatus was designed to run in Hall~B at JLab using the CEBAF electron beam, a 
-499~MHz beam, at energies between 2.2 and 6.6~GeV and currents between 200 and 600~nA.  
+The HPS Test Run apparatus was designed to run in Hall~B at JLab using the CEBAF 499MHz 
+electron beam at energies between 2.2 and 6.6~GeV and currents between 200 and 600~nA.  
 The overall design of the experiment follows from the kinematics of \Aprime{} production which 
@@
 which have radiated in the target disperse horizontally in the field of the analyzing magnet. Together 
-they constitute a "wall of flame" which must be completely avoided. Accordingly, 
-the apparatus is split vertically to avoid a "dead zone", the region within $\pm 15$~mrad of the beam 
+they constitute a ``wall of flame'' which must be completely avoided. Accordingly, 
+the apparatus is split vertically to avoid a ``dead zone'', the region within $\pm 15$~mrad of the beam 
 plane. In addition, the beam is transported in vacuum through the tracker to minimize beam-gas 
@@
 plane are high, dominated by the
-multiple Coulomb scattering of the primary beam, so high rate detectors, a fast trigger, 
+multiple Coulomb scattering of the primary beam, so high-rate detectors, a fast trigger, 
 and excellent time tagging are required to minimize their impact.  
@@
 \hline
-SVT & $15<\theta_{y} < 70$ & 12800 & 14 & $\approx 2$~ns & 5  & $\approx 120~\mu$m $r-\phi$ & $\sigma_{d0,y}  \approx 100~\mu$m \\
+SVT & $15<\theta_{y} < 70$ & 12780 & 14 & $\approx 2$~ns & 5  & $\approx 120~\mu$m $r-\phi$ & $\sigma_{d0,y}  \approx 100~\mu$m \\
 & (5 hits) &  &  &  & (stereo layers) & $\approx 6~\mu$m $z$ & $\sigma_{d0,x} \approx 300~\mu$m \\
@@
 
-The silicon vertex tracking and vertexing detector for HPS Test Run, or SVT, resides in a vacuum 
+The silicon vertex tracking and vertexing detector for the HPS Test Run, or SVT, resides in a vacuum 
 chamber inside the Pair Spectrometer (PS) dipole magnet in Hall B at JLab. The magnetic field 
@@
 %\hline
-1.6   & 911 &   24.4 \\ %24385.9     \\ %27 nA
+0    & 1279  &   88.1 \\ %88079.6  \\
 %\hline
@@
 %\hline
-0    & 1279  &   88.1 \\ %88079.6  \\
+1.6   & 911 &   24.4 \\ %24385.9     \\ %27 nA
 \hline
@@
 
-The Silicon Vertex Tracker (SVT) enables efficient reconstruction of charged particles and precision 
+The Silicon Vertex Tracker (SVT) enables efficient reconstruction of charged particles and precise 
 determination of their trajectories. These measurements allow \Aprime{} decays to be distinguished 
@@
 have momenta in the range of 1~GeV, so multiple scattering dominates mass and vertexing 
-uncertainties for any possible material budget, so the SVT must minimize the amount of 
+uncertainties for any possible material budget. The SVT must therefore minimize the amount of 
 material in the tracking volume. The signal yield for long-lived \Aprime{} is very small, so 
-the rejection of prompt vertexes must be exceedingly pure, on the order of $10^{-7}$, in order to 
+the rejection of prompt vertices must be exceedingly pure, on the order of $10^{-7}$, in order to 
 eliminate all prompt backgrounds. To achieve the required vertexing performance the first layer of the 
 SVT must be placed no more than about 10~cm downstream of the target. At that distance, it is found 
-that the active region of a sensor can be placed as close to 1.5~mm from the center of the beam, 
-defining the 15~mrad ``dead zone" mentioned previously, to maximize low-mass \Aprime{} acceptance 
-with decay products nearly collinear with the beam axis. At the edge of this ``dead zone," the 
+that the active region of a sensor can be placed as close as 1.5~mm from the center of the beam, 
+defining the 15~mrad ``dead zone'' mentioned previously, to maximize low-mass \Aprime{} acceptance 
+with decay products nearly collinear with the beam axis. At the edge of this ``dead zone'', the 
 radiation dose approaches $10^{15}$~electrons/cm$^2$/month, or roughly 
@@
 $4\times10$~cm$^2$ surface. This sensor technology was selected to match the requirement of 
-a $<1$\% $X_0$ per layer, single-hit resolution better than 50~$\mu$m and tolerant of a radiation 
+$<1$\% $X_0$ per layer, single-hit resolution better than 50~$\mu$m and tolerance of a radiation 
 dose of approximately $1.5\times10^{14}$~\fluenceunit{} for a six month run. The sensors 
@@
 The total SVT power consumption budget of about 50~W is removed by a water/glycol mixture 
-circulated through a flexible manifold attached to the copper tubes in the cooling blocks. During the Test 
-run the sensors where operated at around $23^{\circ}$C. The power consumption is dominated by five 
+circulated through a flexible manifold attached to the copper tubes in the cooling blocks. During the 
+HPS Test Run the sensors were operated at around $23^{\circ}$~C. The power consumption is 
+dominated by five 
 APV25 ASICs on each hybrid board consuming approximately 2~W, radiant heat load is less than 
@@
 The SVT was aligned using a combination of optical, laser and touch probe surveys at SLAC and JLab. 
-The optical survey of individual modules with precision of a few $\mu$m are combined with a 
+The optical survey of individual modules with a precision of a few $\mu$m was combined with a 
 touch-probe survey of the overall SVT support structure, with 25-100~$\mu$m precision, to locate the 
@@
 position inside the pair spectrometer vacuum chamber is used to determine the global position of the 
-SVT with respect to CEBAF beam line. The resulting survey-based alignment has the position of the 
+SVT with respect to the CEBAF beam line. The resulting survey-based alignment has the position of the 
 silicon sensors correct to within a few hundred microns measured from tracks in the HPS Test Run 
@@
 \includegraphics[width=7cm]{figures/ecal-module-schematic.png}
-\caption{Schematic vied of an ECal module.}
+\caption{A schematic view of an ECal module.}
 \label{fig:ecal-module}
@@
 \end{figure}
-The scintillation light, approximately $3$ photoelectrons/MeV, is readout by a 
+The scintillation light, approximately $3$ photoelectrons/MeV, is read out by a 
 5$\times$5~mm$^2$ Hamamatsu S8664-55 Avalanche Photodiode (APD) with 75\% quantum 
 efficiency glued to the rear face surface using MeltMount 1.7 thermal plastic adhesive. 
-The low gain of APDs ($\sim 200$) was compensated with custom made preamplifier boards, which 
+The low gain of APDs ($\sim 200$) was compensated with custom-made preamplifier boards, which 
 provide a factor of $2333$ amplification of the APD signal.
@@
 Similar to the SVT, the ECal is built in two separate halves that are mirror reflections of one another 
-about the plane of the nominal electron beam to avoid interfering with the 15~mrad "dead zone". 
+about the plane of the nominal electron beam to avoid interfering with the 15~mrad ``dead zone''. 
 As shown in Fig.~\ref{fig:ecal}, the 221 modules in each half, supported by aluminum support frames, 
@@
 preamplifiers. 
-Four printed circuit boards mounted on the backplane penetrated the enclosure and was used to 
+Four printed circuit boards mounted on the backplane penetrated the enclosure and were used to 
 supply the $\pm 5$~V operating voltage for the preamplifiers, 400~V bias voltage to the APDs, and to 
@@
 When a trigger is received, the part 
-of the pipeline from 5 samples before and 30 after the signal crossed a programmable 
+of the pipeline from 5 samples before and 30 after the signal which crossed a programmable 
 threshold (for the HPS Test Run this was set to $\approx70$~MeV) are 
@@
 (ATCA) hardware while the ECal uses VMEbus Switched Serial (VXS) based hardware. Data from the 
-sub-detectors are only readout when a trigger signal from the trigger system is received formed on 
-input from the ECal.
+sub-detectors are only readout when a trigger signal from the trigger system is received.
 
@@
 Contrary to the readout path 
-described in Sec.~\ref{sec:fadc}, this energy is a pedestal subtracted time-over-threshold sum with 
+described in Sec.~\ref{sec:fadc}, this energy is a pedestal-subtracted time-over-threshold sum with 
 programmable offsets and minimum threshold discriminator for each channel. With input from all 
@@
 RTM also includes a 4-channel fiber optic module and supporting logic which is used to interface 
-to the JLab trigger system supervisor. Each section of the RTM is input to a DPM which apply 
+to the JLab trigger system supervisor. Each section of the RTM is input to a DPM which applies 
 thresholds for data reduction and organizes the sample data into UDP datagrams. The DPM also hosts 
@@
 
-The external PC supports three network interfaces; two standard 1~Gb/s Ethernet and one custom low 
-latency data reception card. The first is used for slow control and monitoring of the 8 
+The external PC supports three network interfaces; two standard 1~Gb/s Ethernet and one custom 
+low-latency data reception card. The first is used for slow control and monitoring of the 8 
 DPM modules and the second serves as the interface to the JLAB data acquisition system. The third 
-custom low latency network interface is used to receive data from the ATCA crate and supports a low 
+custom low-latency network interface is used to receive data from the ATCA crate and supports a low 
 latency, reliable TTL trigger acknowledge interface to the trigger DPM. This PC hosts the SVT control 
@@
 
-While trigger rates during the HPS Test Run was significantly lower this system was tested at trigger rates up 
-to 20~kHz and 50~MB/s.
+Although trigger rates during the HPS Test Run were significantly lower, this system was tested at 
+trigger rates up to 20~kHz and 50~MB/s.
 
@@
 A noise level between $1.1-1.5\times 10^{3}$ electrons was established through multiple calibration 
-runs giving a signal to noise ratio of $21-25$. Lab-based radioactive source tests was used to 
+runs giving a signal to noise ratio of $21-25$. Lab-based radioactive source tests were used to 
 provide the absolute charge normalization.
@@
 
-Good agreement between observed and simulated occupancies after taking into account dead or 
+Good agreement was obtained between observed and simulated occupancies after taking into account dead or 
 noisy channels. The hit reconstruction efficiency was estimated by measuring 
@@
 excluded from the track fit itself. Tracks which intersect regions with known bad channels or very close 
-to in the edge region are excluded. The hit reconstruction efficiency, see Fig.~\ref{fig:hit_efficiency}, 
+to the edge region are excluded. The hit reconstruction efficiency, see Fig.~\ref{fig:hit_efficiency}, 
 was measured to be above 98\% and fairly uniform across the SVT.
@@
 }
-While residual alignment show small shifts, the good agreement  between data and simulated 
+While residual alignments show small shifts, the good agreement  between data and simulated 
 events of the widths indicates a good understanding of the material budget and distribution in the SVT.  
@@
 window integration) to trigger hits (time-over-threshold integration). The CTP clustering 
-algorithm and the trigger decision from the SSP is simulated before we compare the trigger decision 
+algorithm and the trigger decision from the SSP are simulated before we compare the trigger decision 
 and trigger time to what was reported by the actual trigger. For every event, the trigger reports the 
@@
 thicknesses are used to study the varying multiple Coulomb scattering contribution (pair production 
-angle is constant). Restricting clusters to a well calibrated region of the ECal and subtracting the 
-"no converter" background we see agreement with the rates predicted by the \egs{} simulation 
-program, see Tab.~\ref{tab:mcs}.
+angle is constant). 
 %\begin{center}
@@
 }
-\label{tab:mcs}
+\label{tab:results}
 \end{table}
 %\end{center}
+Restricting clusters to a well calibrated region of the ECal and subtracting the ``no converter'' 
+background we see agreement with the rates predicted by the \egs{} simulation 
+program, see Tab.~\ref{tab:results}.
 This gives further confidence that the dominant source of background occupancy for HPS, multiple 
@@
 group for support during installation and decommissioning. They also would like to commend the 
-CEBAF personnel for good beam performance; the last few hours of operating CEBAF6. 
+CEBAF personnel for good beam performance, especially the last few hours of operating CEBAF6. 
 The tremendous support from home institutions and supporting staff also needs praise from the 

### 2014-04-23 hps-testrun-nim.tex
Fixed figure and table references in text

@@
 A rendering of the apparatus installed on the beam line is shown in 
-Fig.~\ref{fig:testrundetector} and an overview of the coverage, segmentation and performance is 
-given in Tab.~\ref{tab:detector-overview}.
+Figure~\ref{fig:testrundetector} and an overview of the coverage, segmentation and performance is 
+given in Table~\ref{tab:detector-overview}.
 
@@
 through the PS pair converter gold foil and later the HPS system as illustrated in 
-Fig.~\ref{fig:schematic_testrun_vs_erun}.
+Figure~\ref{fig:schematic_testrun_vs_erun}.
 \begin{figure}[]
@@
 with ``empty'' converter runs, i.e. removing the converter but with all other conditions the same. 
-The runs taken during the time dedicated to HPS Test Run is summarized in Tab.~\ref{tab:currents}.
+The runs taken during the time dedicated to HPS Test Run is summarized in Table~\ref{tab:currents}.
 
@@
 \subsection{Layout}
-The layout of the SVT is summarized in Tab.~\ref{tab:trk} and rendered in Fig.~\ref{fig:tracker_model}. 
+The layout of the SVT is summarized in Table~\ref{tab:trk} and rendered in Figure~\ref{fig:tracker_model}. 
 Each of the layers is comprised of a pair of closely-spaced silicon microstrip sensors mounted back-
@@
 
-The ECal module shown in Fig.~\ref{fig:ecal-module} is based on a tapered 160~mm long 
+The ECal module shown in Figure~\ref{fig:ecal-module} is based on a tapered 160~mm long 
 PbWO$_{4}$ crystal with a $13.3\times13.3$~mm$^2$ ($16\times16$~mm$^2$) front 
@@
 about the plane of the nominal electron beam to avoid interfering with the 15~mrad ``dead zone''. 
-As shown in Fig.~\ref{fig:ecal}, the 221 modules in each half, supported by aluminum support frames, 
+As shown in Figure~\ref{fig:ecal}, the 221 modules in each half, supported by aluminum support frames, 
 are arranged in rectangular formation with 5 layers and 46 crystals/layer except for the layer closest to 
@@
 Data Processing Module (DPM), that are realized on an ATCA front board called the Cluster On Board 
-(COB), see Fig.~\ref{fig:cob}.
+(COB), see Figure~\ref{fig:cob}.
  \begin{figure}[]
@@
 The first generation RCE used in the HPS Test Run consisted of a Virtex~5 FPGA with 1~GB of DDR3 RAM. 
-A schematic overview of the system is shown in Fig.~\ref{fig:svtdaq}. 
+A schematic overview of the system is shown in Figure~\ref{fig:svtdaq}. 
  \begin{figure}[]
@@
 six consecutive time bins, separated by roughly 25~ns.  
-The typical, pedestal subtracted, pulse shape obtained is shown in Fig.~\ref{fig:pulse_shape}. 
+The typical, pedestal subtracted, pulse shape obtained is shown in Figure~\ref{fig:pulse_shape}. 
 As the figure demonstrates,  the SVT was well timed-in to the trigger with the rise of the pulse at the 3rd 
@@
 the characteristic Landau shape. 
-%, see Fig.~\ref{fig:cluster_pulse}.  
+%, see Figure~\ref{fig:cluster_pulse}.  
 A noise level between $1.1-1.5\times 10^{3}$ electrons was established through multiple calibration 
@@
 $t_0$ resolution is studied by comparing the cluster hit time with the average of all cluster hit times on 
-the track shown in Fig.~\ref{fig:tracktime}. 
+the track shown in Figure~\ref{fig:tracktime}. 
 \begin{figure}[]
@@
 excluded from the track fit itself. Tracks which intersect regions with known bad channels or very close 
-to the edge region are excluded. The hit reconstruction efficiency, see Fig.~\ref{fig:hit_efficiency}, 
+to the edge region are excluded. The hit reconstruction efficiency, see Figure~\ref{fig:hit_efficiency}, 
 was measured to be above 98\% and fairly uniform across the SVT.
@@
 the SVT, with momentum larger than 400~MeV were selected. The pair production kinematics are 
-relatively well reproduced as shown in Fig.~\ref{fig:pair_kin}.
+relatively well reproduced as shown in Figure~\ref{fig:pair_kin}.
 
@@
 simulation were similar. The distribution of the $E$/$p$ ratio in data and simulation are compared in 
-Fig.~\ref{fig:gains}. 
+Figure~\ref{fig:gains}. 
 {\small
@@
 under study. We then measure trigger efficiency as the fraction of tagged events that fired the trigger in 
-the probe half as a function of the probe cluster energy, shown in Fig.~\ref{fig:turnon}. 
+the probe half as a function of the probe cluster energy, shown in Figure~\ref{fig:turnon}. 
 \begin{figure}[ht]
@@
 background we see agreement with the rates predicted by the \egs{} simulation 
-program, see Tab.~\ref{tab:results}.
+program, see Table~\ref{tab:results}.
 This gives further confidence that the dominant source of background occupancy for HPS, multiple 
@@
 %Data was taken at three different converter thicknesses with a beam current varying between 
-%$30-70$~nA, see~Tab.~\ref{tab:currents}.  
+%$30-70$~nA, see~Table~\ref{tab:currents}.  
 %\begin{table}[t]
@@
 %Hit energy is calibrated by matching track momentum to cluster energy, as described in Sec.~\ref{sec:ecal_calibration}.
-The measured angular distribution in the ECal for the three converter thicknesses are shown in Fig.~\ref{fig:ang_distr_data}.
+The measured angular distribution in the ECal for the three converter thicknesses are shown in Figure~\ref{fig:ang_distr_data}.
 %\begin{figure}[]
@@
 %cross-checked by pointing back tracks reconstructed in the SVT to identify the fraction of tracks not emanating from the converter. 
-%%This can be seen in Fig.~\ref{fig:extrapol_converter} (bottom) where small 
+%%This can be seen in Figure~\ref{fig:extrapol_converter} (bottom) where small 
 %%satellite peaks at $\pm 10$~mm can be identified as tracks from the upstream background. The angular distribution, after normalization and subtracting the upstream background, are shown in 
-%%Fig.~\ref{fig:ang_distr_data} (right).  
+%%Figure~\ref{fig:ang_distr_data} (right).  
 %We also checked that the contribution from photons to our triggered 
@@
 %slightly different slope of the data at larger angles; this difference is covered by systematic uncertainties.  
-%The total rates for each converter thickness is shown in Fig.~\ref{fig:rate_vs_thickness} and summarized 
-%in Tab.~\ref{tab:ang_distr_dataMC}.
+%The total rates for each converter thickness is shown in Figure~\ref{fig:rate_vs_thickness} and summarized 
+%in Table~\ref{tab:ang_distr_dataMC}.
 %\begin{figure}[]

### 2014-04-23 hps-testrun-nim.tex
trying to fix table nr issue..no luck

@@
 \subsection{Trigger Rate Comparisons}
-\label{sec:mcs}
 Trigger rates observed in the HPS Test Run are dominated by multiple Coulomb scattered \ee{} pairs in the 
@@
 \begin{table}
+\label{results}
 {\small
@@
 }
-\label{tab:results}
 \end{table}
@@
 background we see agreement with the rates predicted by the \egs{} simulation 
-program, see Table~\ref{tab:results}.
+program, 
+see Table~\ref{results}.
 This gives further confidence that the dominant source of background occupancy for HPS, multiple 

### 2014-04-24 hps-testrun-nim.tex
Removed illustration comparing to electron run.

@@
 During the dedicated HPS Test Run period, the collimated (6.4~mm diameter) photon beam passes 
-through the PS pair converter gold foil and later the HPS system as illustrated in 
-Figure~\ref{fig:schematic_testrun_vs_erun}.
-\begin{figure}[]
-\includegraphics[ width=7cm]{figures/photon_vs_electron_beam_schematic.png}
-\caption{\small{Illustrative comparison of HPS Test Run photon beam compared to the HPS electron 
-beam.}}
-\label{fig:schematic_testrun_vs_erun}
-\end{figure}
+through the PS pair converter gold foil and later the HPS system.
+%\begin{figure}[]
+%\includegraphics[ width=7cm]{figures/photon_vs_electron_beam_schematic.png}
+%\caption{\small{Illustrative comparison of HPS Test Run photon beam compared to the HPS electron 
+%beam.}}
+%\label{fig:schematic_testrun_vs_erun}
+%\end{figure}
 The PS pair converter was located $\approx~77$~cm upstream of the first layer of the SVT.

### 2014-04-29 hps-testrun-nim.tex
Adding new trigger efficiency plot with Bayesion (flat uniform prior) errors
Daria Sokhar and Vitaliy's comments.

@@
 with ``empty'' converter runs, i.e. removing the converter but with all other conditions the same. 
-The runs taken during the time dedicated to HPS Test Run is summarized in Table~\ref{tab:currents}.
+The runs taken during the time dedicated to HPS Test Run are summarized in Table~\ref{tab:currents}.
 
@@
 from background via simultaneous estimation of the invariant mass of \ee{} decay products and the 
-position of decay vertexes downstream of the target.
+position of decay vertices downstream of the target.
 
@@
 the last layer that defines the nominal spacing between the upper and lower halves of the tracker.  A 
-shaft attached to each support plate in front of layer 1 extends upstream and connects to a linear shift 
+shaft attached to each support plate in front of layer one extends upstream and connects to a linear shift 
 that transfers motion into the vacuum box through bellows to open and close the two halves around 
@@
 \subsection{Components}
-The sensors for the SVT are $p+$-on-$n$, single sided, AC coupled, polysilicon-biased microstrip 
-sensors fabricated on $<100>$ silicon and have 30 (60)~$\mu$m sense (readout) pitch over their 
+The sensors for the SVT are $p+$-on-$n$, single-sided, AC-coupled, polysilicon-biased microstrip 
+sensors fabricated on $<$100$>$ silicon and have 30 (60)~$\mu$m sense (readout) pitch over their 
 $4\times10$~cm$^2$ surface. This sensor technology was selected to match the requirement of 
@@
 $CR$-$RC$ shaping curve to these samples, the initial time of the hit can be determined to a precision 
-of 2~ns for S/N$\approx25$~\cite{Friedl:2009zz}.  For electron beam running, six-sample readout and 
+of 2~ns for S/N$\approx$25~\cite{Friedl:2009zz}.  For electron beam running, six-sample readout and 
 the shortest possible shaping time (35~ns) is used to best distinguish hits that overlap in time.
@@
 of the silicon to minimize material. A 50~$\mu$m sheet of polyamide is laminated to the surface of the 
-carbon fiber with 1~mm overhang at all openings to ensure good isolation between the backside of the 
+carbon fiber with 1~mm overhang at all openings to ensure good isolation between the back side of the 
 sensor, carrying high-voltage bias, and the carbon fiber which is held near ground.
@@
 Hybrids with APV25 ASICs underwent quick qualification testing and each half-module was run at low 
-temperature ($\approx5^{\circ}$ C) and fully characterized for pedestals, gains, noise and time response 
-after assembly.  Of 29 half-modules built, 28 passed qualification testing, leaving 8 spare modules after 
-completion of the SVT, all capable of 1000~V bias voltage without breakdown.  Full-module assembly 
+temperature ($\approx5^{\circ}$ C) and fully characterized for pedestals, gains, noise and time 
+response after assembly.  Of 29 half-modules built, 28 passed qualification testing, leaving eight spare 
+modules after completion of the SVT. Only sensors capable of 1000~V bias voltage without breakdown 
+were used.  Full-module assembly 
 and mechanical surveys were performed at SLAC before final assembly, testing and shipping of the 
@@
 covering the SVT \Aprime{} acceptance and able to fully absorb 
-electrons and positrons with energy between $0.5$-$6.5$~GeV, fine granularity and signal 
+electrons and positrons with energy between $0.5$-$6.5$~GeV.  It needs granularity and signal 
 readout speed to handle 1~MHz/cm$^{2}$ of electromagnetic background and be radiation hard. 
@@
 As shown in Figure~\ref{fig:ecal}, the 221 modules in each half, supported by aluminum support frames, 
-are arranged in rectangular formation with 5 layers and 46 crystals/layer except for the layer closest to 
-the beam where 9 modules were removed to allow a larger opening for the outgoing electron and 
+are arranged in rectangular formation with five layers and 46 crystals/layer except for the layer closest to 
+the beam where nine modules were removed to allow a larger opening for the outgoing electron and 
 photon beams. Each half was enclosed in a temperature controlled box ($<1^{\circ}$~F stability and 
@@
 
-During the HPS Test Run, both halves were held in place by four vertical bars attached to an above rail, 
-placing the front face of the crystals 147~cm from the upstream edge of the magnet and with a 
+During the HPS Test Run, both halves were held in place by four vertical bars attached to a rail above, 
+placing the front face of the crystals 147~cm from the upstream edge of the magnet, with a 
 8.7~cm gap between the innermost edge of the crystals in the two halves.
@@
 (ATCA) hardware while the ECal uses VMEbus Switched Serial (VXS) based hardware. Data from the 
-sub-detectors are only readout when a trigger signal from the trigger system is received.
+sub-detectors are only read out when a trigger signal from the trigger system is received.
 
@@
 sent to the SSP where the final trigger decision is taken based on pairs of clusters in both halves of the 
-ECal. The decision is sent to the Trigger Supervisor (TS) that generates the necessary signals to readout 
+ECal. The decision is sent to the Trigger Supervisor (TS) that generates the necessary signals to read out 
 the sub-detectors.}
@@
 window to take into account clock skew and jitter throughout the system.
-The CTP only accepts clusters with the highest energy 3x3 window locally to deal with overlapping and 
+The CTP only accepts clusters with the locally highest energy 3x3 window to deal with overlapping and 
 very large clusters. The sub-system board (SSP) receives the clusters from the top and bottom half CTP 
-at a maximum of 250MHz and searches for pairs of clusters in a 8~ns wide coincidence window. The 
+at a maximum of 250MHz and searches for pairs of clusters in an 8~ns wide coincidence window. The 
 SSP sends triggers to the trigger supervisor (TS), which generates all the necessary signals and 
@@
 The RCE is a generic computational building block, housed on a separate daughter card called 
-Data Processing Module (DPM), that are realized on an ATCA front board called the Cluster On Board 
+Data Processing Module (DPM), that is realized on an ATCA front board called the Cluster On Board 
 (COB), see Figure~\ref{fig:cob}.
@@
 into four sections with each section supporting three SVT half-module hybrids (15 APV25 ASICs). The 
-RTM also includes a 4-channel fiber optic module and supporting logic which is used to interface 
-to the JLab trigger system supervisor. Each section of the RTM is input to a DPM which applies 
+RTM also includes a 4-channel fiber-optic module and supporting logic which is used to interface 
+to the JLab trigger system supervisor. Each section of the RTM is input to a DPM which apply 
 thresholds for data reduction and organizes the sample data into UDP datagrams. The DPM also hosts 
 an I$^{2}$C controller used to configure and monitor the APV25 ASICs. A single ATCA crate with two 
-COB cards was used, one supporting four DPMs and one supporting 3 DPMs and one DPM that is 
+COB cards was used, one supporting four DPMs and one supporting three DPMs and one DPM that is 
 configured as the trigger and data transmission module. The two COB cards and their DPMs are 
@@
 
-The external PC supports three network interfaces; two standard 1~Gb/s Ethernet and one custom 
+The external PC supports three network interfaces: two standard 1~Gb/s Ethernet and one custom 
 low-latency data reception card. The first is used for slow control and monitoring of the 8 
@@
 In order to minimize cable length for the analog APV25 output signal the ATCA crate was located 
-approximately 1~m from the beam line, next to our cable vacuum feed-troughs.   
+approximately 1~m from the beam line, next to our cable vacuum feed-throughs.   
 Before shielding with lead-blankets was arranged, we observed two failures of normally reliable ATCA 
@@
 With a linear gain up to $\approx 3$~MIPs, the cluster charge for hits associated with a track follow 
-the characteristic Landau shape. 
-%, see Figure~\ref{fig:cluster_pulse}.  
+the characteristic Landau shape, see Figure~\ref{fig:cluster_pulse}.  
+\begin{figure}[]
+\begin{center}
+{\small
+	%\includegraphics[width=7cm]{figures/run1351_mip_small.pdf}
+	\includegraphics[width=7cm]{figures/mip_top_layer_2.png}
+    	\caption{ The cluster charge distribution for hits associated with a track follow the characteristic 		Landau shape. }
+	\label{fig:cluster_pulse}
+}
+\end{center}
+\end{figure}
 A noise level between $1.1-1.5\times 10^{3}$ electrons was established through multiple calibration 
@@
 provide the absolute charge normalization.
-\begin{figure}[]
-\begin{center}
-{\small
-	%\includegraphics[width=7cm]{figures/run1351_mip_small.pdf}
-	\includegraphics[width=7cm]{figures/mip_top_layer_2.png}
-    	\caption{ The cluster charge distribution for hits associated with track follow the characteristic 		Landau shape. }
-	\label{fig:cluster_pulse}
-}
-\end{center}
-\end{figure}
 After clustering hits on a sensor, the hit time for each cluster is computed 
@@
 the track shown in Figure~\ref{fig:tracktime}. 
+After correcting for offsets from each sensor (time-of-flight and clock phase) and accounting for the 
+correlation between the $t_0$ and track time,  the extracted $t_0$ resolution is 2.6~ns. This is 
+somewhat worse than the approximately 2~ns resolution expected for S/N$=$25 which we attribute to the 
+true pulse shape differing from our idealized fit function which will be improved in the future. Reducing 
+the APV25 ASIC pulse shaping time to 35~ns will also improve time resolution. 
+These results show that we can operate with the six sample readout mode of the APV25 chip and 
+achieve time resolution adequate for pileup rejection during electron running in HPS. 
 \begin{figure}[]
@@
 \end{figure}
-After correcting for offsets from each sensor (time-of-flight and clock phase) and accounting for the 
-correlation between the $t_0$ and track time,  the extracted $t_0$ resolution is 2.6~ns. This is 
-somewhat worse than the approximately 2~ns resolution expected for S/N~25 which we attribute to the 
-true pulse shape differing from our idealized fit function which will be improved in the future. Reducing 
-the APV25 ASIC pulse shaping time to 35~ns will also improve time resolution. 
-These results show that we can operate with the six sample readout mode of the APV25 chip and 
-achieve time resolution adequate for pileup rejection during electron running in HPS.
 
@@
 the number of good tracks with a hit close to the extrapolated intersection of a given sensor that was 
-excluded from the track fit itself. Tracks which intersect regions with known bad channels or very close 
-to the edge region are excluded. The hit reconstruction efficiency, see Figure~\ref{fig:hit_efficiency}, 
+excluded from the track fit itself. Tracks which intersect regions with known bad channels or pass very 
+close to the edge region are excluded. The hit reconstruction efficiency, see Figure~\ref{fig:hit_efficiency}, 
 was measured to be above 98\% and fairly uniform across the SVT.
@@
 function of the total signal to single-strip noise and the crossing angle of tracks through the sensor.  
-The single-hit resolution for charged particles with signal to noise ratio above 20, as demonstrated 
-here, is relatively constant at approximately 6~$\mu$m for tracks that enters approximately normal to 
+The single-hit resolution for charged particles with signal-to-noise ratio above 20, as demonstrated 
+here, is relatively constant at approximately 6~$\mu$m for tracks that enter approximately normal to 
 the sensors as in HPS.
@@
 The expected momentum resolution from simulation is between 4-5\% for tracks in the momentum 
-range of the HPS Test Run. By comparing the shapes of the kinematic distributions for single- and two 
-track events between data and simulation we estimate an agreement with the nominal scale and 
+range of the HPS Test Run. By comparing, between data and simulation, the shapes of the kinematic 
+distributions for single- and two-track events, we estimate an agreement with the nominal scale and 
 resolution to within 10\%.
@@
 {\small
-	\includegraphics[width=7cm]{figures/h_cl_E_probedata_eff_h_cl_E_probeMC_eff_dataMC_1351-v7-trig-tagBot.pdf}
+	%\includegraphics[width=7cm]{figures/h_cl_E_probedata_eff_h_cl_E_probeMC_eff_dataMC_1351-v7-trig-tagBot.pdf}
+	\includegraphics[width=7cm]{figures/h_cl_E_probedata_eff_bay_h_cl_E_probeMC_eff_bay_dataMC_1351-v7-trig-tagBot.pdf}
 	\caption{Trigger efficiency in both halves of the ECal for data and simulation as a 
@@
 Trigger rates observed in the HPS Test Run are dominated by multiple Coulomb scattered \ee{} pairs in the 
-converter. In simulated events, the rate of triggers depend on the modeling of the pairs angular 
+converter. In simulated events, the rate of triggers depend on the modeling of the pairs' angular 
 distribution and the subsequent multiple Coulomb scattering in the converter. Rates from different 

### 2014-04-29 hps-testrun-nim.tex
Trailing comment from Vitaliy.
Feedback from M. Holtrop.

@@
 inside a dipole magnet. Electromagnetic showers are detected in a PbW0$_{4}$ 
-crystal calorimeter situated behind the magnet used to trigger the experiment and identify 
+crystal calorimeter situated behind the magnet,  and are used to trigger the experiment and identify 
 electrons and positrons. Both detectors are placed close to the 
@@
 \label{introduction}
-The heavy photon (\Aprime{}), aka a ``hidden sector'' or ``dark'' photon, is a particle with mass 
-$10-1000$~MeV/c$^{2}$ which couples weakly to electric charge by mixing with the Standard Model 
+The heavy photon (\Aprime{}), aka a ``hidden sector'' or ``dark'' photon, is a massive particle which 
+couples weakly to electric charge by mixing with the Standard Model 
 photon~\cite{Holdom:1985ag}. Consequently, it can be radiated by electrons and subsequently decay 
@@
 Architecture (ATCA) based SVT readout system and VMEbus Switched Serial (VXS) based digitization 
-and triggering system for the ECal. The system was designed to run at up to 20~kHz trigger rate.
+and triggering system for the ECal.
 
@@
 Although trigger rates during the HPS Test Run were significantly lower, this system was tested at 
-trigger rates up to 20~kHz and 50~MB/s.
+trigger rates up to 20~kHz and 50~MB/s.  With optimized event blocking and improved ethernet 
+bandwidth, together with utilizing the overlapping readout and trigger functionality of the APV25, the 
+system is capable of being read out at 50~kHz trigger rate.
 
@@
 After a trigger is received, the amplitude of every  APV25 analogue output is sampled and digitized in 
-six consecutive time bins, separated by roughly 25~ns.  
+six consecutive time bins, separated by roughly 25~ns.  A data reduction algorithm is applied 
+requiring three out of six samples to be above two times the noise level and that the third sample is 
+larger than the second or that the fourth sample is larger than the third.
 The typical, pedestal subtracted, pulse shape obtained is shown in Figure~\ref{fig:pulse_shape}. 
@@
 
-Good agreement was obtained between observed and simulated occupancies after taking into account dead or 
-noisy channels. The hit reconstruction efficiency was estimated by measuring 
+Good agreement was obtained between observed and simulated occupancies after taking into account 
+dead or noisy channels. The hit reconstruction efficiency was estimated by measuring 
 the number of good tracks with a hit close to the extrapolated intersection of a given sensor that was 

### 2014-04-29 hps-testrun-nim.tex
Fixed plot axis.

@@
 environment at the interaction region. The \Aprime{} decay products 
-have momenta in the range of 1~GeV, so multiple scattering dominates mass and vertexing 
+have momenta in the range of 1~GeV$/$c, so multiple scattering dominates mass and vertexing 
 uncertainties for any possible material budget. The SVT must therefore minimize the amount of 
@@
 \begin{figure*}[t]
-   \includegraphics[width=5cm]{figures/h_trk_top_px_h_trk_top_px_trigsel4hit_pair1351_twotrkfilt-v6-paper}
-   \includegraphics[width=5cm]{figures/h_invM_h_invM_trigsel4hit_pair1351_twotrkfilt-v6-paper}
+   \includegraphics[width=5cm]{figures/h_trk_top_px_h_trk_top_px_trigsel4hit_pair1351_twotrkfilt-v6-paper-mod}
+   \includegraphics[width=5cm]{figures/h_invM_h_invM_trigsel4hit_pair1351_twotrkfilt-v6-paper-mod}
    \includegraphics[width=5cm]{figures/h_sumE_h_sumE_trigsel4hit_pair1351_twotrkfilt-v6-paper}
-\caption{Kinematic distributions for \ee{} pairs selected by opposite charged tracks in the top and bottom half of the tracker: track momentum in the top half of the SVT (left), invariant mass (middle) and the sum of the track momentum for the pair (right).}
+\caption{Kinematic distributions for \ee{} pairs selected by opposite charged tracks in the top and bottom half of the tracker: track momentum in the top half of the SVT (left), invariant mass (middle) and the sum of the track energy for the pair (right).}
 \label{fig:pair_kin}
@@
 	% TestRun-v6 geometry, twotrkfilter, trigsel, hps-java-1.8-SNAPSHOT, 4hits, chi2<10
-	\includegraphics[width=7cm]{figures/h_trk_top_fr_conv_z_h_trk_top_conv_z_dataMC_twotrksel.png}
-	\includegraphics[width=7cm]{figures/h_trk_top_fr_conv_y_h_trk_top_conv_y_dataMC_twotrksel.png}
+	\includegraphics[width=7cm]{figures/h_trk_top_fr_conv_z_h_trk_top_conv_z_dataMC_twotrksel-mod}
+	\includegraphics[width=7cm]{figures/h_trk_top_fr_conv_y_h_trk_top_conv_y_dataMC_twotrksel-mod}
 	\caption{ Vertical (top) and horizontal (bottom) extrapolated track position at the converter position 

### 2014-04-30 author_list_hps_PAC39_compact.tex
Added author list from PAC39 report.
New abstract, edited intro, overview, beamline and the start of SVT
Separate authors
Comments from Raphael Dupre on draft v2.
Adding more changes suggested by Larry Weinstein to 2nd draft.
New author list from EC.

--- 2013-11-15 author_list_hps_PAC39.tex
@@
 \newcommand{\FNAL}{Fermi National Accelerator Laboratory, Batavia, IL 60510-5011}
-\newcommand{\HUJ}{Hebrew University of Jerusalem, Jerusalem, Israel}
 \newcommand{\UNH}{University of New Hampshire, Department of Physics, Durham, NH 03824}
@@
 \newcommand{\WNM}{The College of William and Mary, Department of Physics, Williamsburg, VA 23185}
-\renewcommand*{\thesection}{\arabic{section}}
-\newcommand{\Contact}{Contact person}
+\newcommand{\GLASGOW}{University of Glasgow, Glasgow, G12 8QQ, Scotland, UK}
+\newcommand{\RUTGERS}{Rutgers University, Department of Physics and Astronomy, Piscataway, NJ 08854}
 
-\begin{document}
+\author[SLAC]{C. Field}
+\author[SLAC]{P. Hansson Adrian\corref{corrauthor}}
+\ead{phansson@slac.stanford.edu}
+\author[SLAC]{N. Graf} 
+\author[SLAC]{ M. Graham} 
+\author[SLAC]{ G. Haller} 
+\author[SLAC]{ R. Herbst} 
+\author[SLAC]{ J. Jaros}
+\author[SLAC]{T. Maruyama} 
+\author[SLAC]{ J. McCormick} 
+\author[SLAC]{ K. Moffeit} 
+\author[SLAC]{ T. Nelson} 
+\author[SLAC]{ H. Neal} 
+\author[SLAC]{ A. Odian} 
+\author[SLAC]{ M. Oriunno} 
+\author[SLAC]{ R. Partridge} 
+\author[SLAC]{ S. Uemura} 
+\author[SLAC]{ D. Walz}
+%
+\author[UCSC]{A. Grillo} 
+\author[UCSC]{ V. Fadeyev} 
+\author[UCSC]{ O. Moreno}
+%
+\author[FNAL]{W. Cooper}
+%
+\author[JLAB]{S. Boyarinov} 
+\author[JLAB]{ V. Burkert} 
+\author[JLAB]{C. Cuevas}
+\author[JLAB]{ A. Deur} 
+\author[JLAB]{ H. Egiyan}
+ \author[JLAB]{ L. Elouadrhiri} 
+ \author[JLAB]{ A. Freyberger} 
+ \author[JLAB]{ F.-X. Girod} 
+ \author[JLAB]{ S. Kaneta}
+ \author[JLAB]{ V. Kubarovsky} 
+ \author[JLAB]{ B. Raydo} 
+\author[JLAB]{ Y. Sharabian} 
+\author[JLAB]{ S. Stepanyan}
+\author[JLAB]{ M. Ungaro} 
+\author[JLAB]{ B. Wojtsekhowski}
+%
+\author[SUNY]{R. Essig}
+%
+\author[UNH]{M. Holtrop}
+\author[UNH]{ S. K. Phillips}
+%
+\author[ORSAY]{ C. Desnault}
+\author[ORSAY]{ M. Guidal} 
+\author[ORSAY]{ S. Niccolai} 
+\author[ORSAY]{ E. Rauly}
+\author[ORSAY]{ E. Rindel} 
+\author[ORSAY]{ P. Rosier}
+ %
+\author[PERIMETER]{P. Schuster} 
+\author[PERIMETER]{ N. Toro}
+%
+\author[YEREVAN]{N. Dashyan} 
+\author[YEREVAN]{ N. Gevorgyan} 
+\author[YEREVAN]{ R. Paremuzyan}
+\author[YEREVAN]{ H. Voskanyan}
+%
+\author[NSU]{M. Khandaker} 
+\author[NSU]{ C. Salgado}
+%
+\author[GENOVA]{M. Battaglieri} 
+\author[GENOVA]{ R. DeVita}
+%
+\author[ODU]{S. Bueltmann} 
+\author[ODU]{ L. B. Weinstein}
+%
+\author[RPI]{A. Kubarovsky}
+%
+\author[WNM]{K. Griffioen}
+%
+\author[GLASGOW]{D. Sokhan}
+%
+\author[RUTGERS]{Y. Gershtein}
+\author[RUTGERS]{J. Reichert}
 
-\title{\bf\large{Status of the Heavy Photon Search Experiment at Jefferson Laboratory}}
-\author{P. Hansson Adrian, C. Field, N. Graf, M. Graham, G. Haller, R. Herbst, J. Jaros\footnote{Co-spokesperson\label{spoks}}, 
-T. Maruyama, J. McCormick, K. Moffeit, T. Nelson, H. Neal, A. Odian, M. Oriunno, S. Uemura, D. Walz}
-\affiliation{\SLAC}                                 
- \author{A. Grillo, V. Fadeyev, O. Moreno}
-\affiliation{\UCSC}
-\author{W. Cooper}
-\affiliation{\FNAL}
-\author{S. Boyarinov, V. Burkert, A. Deur, H. Egiyan, L. Elouadrhiri, A. Freyberger, F.-X. Girod, 
-V. Kubarovsky, Y. Sharabian, S. Stepanyan\footref{spoks}, M. Ungaro, B. Wojtsekhowski}
-\affiliation{\JLAB}
-\author{R. Essig}
-\affiliation{\SUNY}
-\author{M. Holtrop\footref{spoks}, K. Slifer, S. K. Phillips}
-\affiliation{\UNH} 
-\author{A. Fradi, B. Guegan, M. Guidal, S. Niccolai, S. Pisano, E. Rauly, P. Rosier and D. Sokhan}
-\affiliation{\ORSAY}
-\author{P. Schuster, N. Toro}
-\affiliation{\PERIMETER}
-\author{N. Dashyan, N. Gevorgyan, R. Paremuzyan, H. Voskanyan}
-\affiliation{\YEREVAN}
-\author{M. Khandaker, C. Salgado}
-\affiliation{\NSU}
-\author{M. Battaglieri, R. De Vita}
-\affiliation{\genova}
-\author{S. Bueltmann, L. Weinstein}
-\affiliation{\ODU}
-\author{G. Ron}
-\affiliation{\HUJ}
-\author{P. Stoler, A. Kubarovsky}
-\affiliation{\RPI}
-\author{K. Griffioen}
-\affiliation{\WNM}
+\address[SLAC]{\SLAC}                                 
+\address[UCSC]{\UCSC}
+\address[FNAL]{\FNAL}
+\address[JLAB]{\JLAB}
+\address[SUNY]{\SUNY}
+\address[UNH]{\UNH}
+\address[ORSAY]{\ORSAY}
+\address[PERIMETER]{\PERIMETER}
+\address[YEREVAN]{\YEREVAN}
+\address[NSU]{\NSU}
+\address[GENOVA]{\genova}
+\address[ODU]{\ODU}
+\address[RPI]{\RPI}
+\address[WNM]{\WNM}
+\address[GLASGOW]{\GLASGOW}
+\address[RUTGERS]{\RUTGERS}
+
+\cortext[corrauthor]{Corresponding author.}

### 2014-04-30 author_list_hps_PAC39_compact_alphabetical_order.tex
Alphabetical author list. Consistent notion of HPS Test Run.
Comments from Raphael Dupre on draft v2.
Adding changes suggested by Larry Weinstein to 2nd draft.
New author list from EC.

--- 2013-11-15 author_list_hps_PAC39.tex
@@
 \newcommand{\WNM}{The College of William and Mary, Department of Physics, Williamsburg, VA 23185}
-\renewcommand*{\thesection}{\arabic{section}}
-\newcommand{\Contact}{Contact person}
+\newcommand{\GLASGOW}{University of Glasgow, Glasgow, G12 8QQ, Scotland, UK}
+\newcommand{\RUTGERS}{Rutgers University, Department of Physics and Astronomy, Piscataway, NJ 08854}
 
-\begin{document}
+\author[GENOVA]{M. Battaglieri} 
+\author[JLAB]{S. Boyarinov} 
+\author[ODU]{S. Bueltmann} 
+\author[JLAB]{ V. Burkert} 
+\author[FNAL]{W. Cooper}
+\author[JLAB]{C. Cuevas}
+\author[YEREVAN]{N. Dashyan} 
+\author[GENOVA]{ R. DeVita}
+\author[ORSAY]{ C. Desnault}
+\author[JLAB]{ A. Deur} 
+\author[JLAB]{ H. Egiyan}
+ \author[JLAB]{ L. Elouadrhiri} 
+\author[SUNY]{R. Essig}
+\author[UCSC]{ V. Fadeyev} 
+\author[SLAC]{C. Field}
+ \author[JLAB]{ A. Freyberger} 
+\author[RUTGERS]{Y. Gershtein}
+\author[YEREVAN]{ N. Gevorgyan} 
+ \author[JLAB]{ F.-X. Girod} 
+\author[SLAC]{N. Graf} 
+\author[SLAC]{ M. Graham} 
+\author[WNM]{K. Griffioen}
+\author[UCSC]{A. Grillo} 
+\author[ORSAY]{ M. Guidal} 
+\author[SLAC]{ G. Haller} 
+\author[SLAC]{P. Hansson Adrian\corref{corrauthor}}
+\ead{phansson@slac.stanford.edu}
+\author[SLAC]{ R. Herbst} 
+\author[UNH]{M. Holtrop}
+\author[SLAC]{ J. Jaros}
+ \author[JLAB]{ S. Kaneta}
+\author[NSU]{M. Khandaker} 
+ \author[JLAB]{ V. Kubarovsky} 
+\author[RPI]{A. Kubarovsky}
+\author[SLAC]{T. Maruyama} 
+\author[SLAC]{ J. McCormick} 
+\author[SLAC]{ K. Moffeit} 
+\author[UCSC]{ O. Moreno}
+\author[SLAC]{ H. Neal} 
+\author[SLAC]{ T. Nelson} 
+\author[ORSAY]{ S. Niccolai} 
+\author[SLAC]{ A. Odian} 
+\author[SLAC]{ M. Oriunno} 
+\author[YEREVAN]{ R. Paremuzyan}
+\author[SLAC]{ R. Partridge} 
+\author[UNH]{ S. K. Phillips}
+\author[ORSAY]{ E. Rauly}
+ \author[JLAB]{ B. Raydo} 
+\author[RUTGERS]{J. Reichert}
+\author[ORSAY]{ E. Rindel} 
+\author[ORSAY]{ P. Rosier}
+\author[NSU]{ C. Salgado}
+\author[PERIMETER]{P. Schuster} 
+\author[JLAB]{ Y. Sharabian} 
+\author[GLASGOW]{D. Sokhan}
+\author[JLAB]{ S. Stepanyan}
+\author[PERIMETER]{ N. Toro}
+\author[SLAC]{ S. Uemura} 
+\author[JLAB]{ M. Ungaro} 
+\author[YEREVAN]{ H. Voskanyan}
+\author[SLAC]{ D. Walz}
+\author[ODU]{ L. B. Weinstein}
+\author[JLAB]{ B. Wojtsekhowski}
+%
+%
+%
+%
+%
+%
+ %
+%
+%
+%
+%
+%
+%
+%
+%
 
-\title{\bf\large{Status of the Heavy Photon Search Experiment at Jefferson Laboratory}}
-\author{P. Hansson Adrian, C. Field, N. Graf, M. Graham, G. Haller, R. Herbst, J. Jaros\footnote{Co-spokesperson\label{spoks}}, 
-T. Maruyama, J. McCormick, K. Moffeit, T. Nelson, H. Neal, A. Odian, M. Oriunno, S. Uemura, D. Walz}
-\affiliation{\SLAC}                                 
- \author{A. Grillo, V. Fadeyev, O. Moreno}
-\affiliation{\UCSC}
-\author{W. Cooper}
-\affiliation{\FNAL}
-\author{S. Boyarinov, V. Burkert, A. Deur, H. Egiyan, L. Elouadrhiri, A. Freyberger, F.-X. Girod, 
-V. Kubarovsky, Y. Sharabian, S. Stepanyan\footref{spoks}, M. Ungaro, B. Wojtsekhowski}
-\affiliation{\JLAB}
-\author{R. Essig}
-\affiliation{\SUNY}
-\author{M. Holtrop\footref{spoks}, K. Slifer, S. K. Phillips}
-\affiliation{\UNH} 
-\author{A. Fradi, B. Guegan, M. Guidal, S. Niccolai, S. Pisano, E. Rauly, P. Rosier and D. Sokhan}
-\affiliation{\ORSAY}
-\author{P. Schuster, N. Toro}
-\affiliation{\PERIMETER}
-\author{N. Dashyan, N. Gevorgyan, R. Paremuzyan, H. Voskanyan}
-\affiliation{\YEREVAN}
-\author{M. Khandaker, C. Salgado}
-\affiliation{\NSU}
-\author{M. Battaglieri, R. De Vita}
-\affiliation{\genova}
-\author{S. Bueltmann, L. Weinstein}
-\affiliation{\ODU}
-\author{G. Ron}
-\affiliation{\HUJ}
-\author{P. Stoler, A. Kubarovsky}
-\affiliation{\RPI}
-\author{K. Griffioen}
-\affiliation{\WNM}
+\address[GENOVA]{\genova}
+\address[JLAB]{\JLAB}
+\address[ODU]{\ODU}
+\address[FNAL]{\FNAL}
+\address[YEREVAN]{\YEREVAN}
+\address[ORSAY]{\ORSAY}
+\address[SUNY]{\SUNY}
+\address[UCSC]{\UCSC}
+\address[SLAC]{\SLAC}                                 
+\address[RUTGERS]{\RUTGERS}
+\address[WNM]{\WNM}
+\address[UNH]{\UNH}
+\address[NSU]{\NSU}
+\address[RPI]{\RPI}
+\address[PERIMETER]{\PERIMETER}
+\address[GLASGOW]{\GLASGOW}
+
+\cortext[corrauthor]{Corresponding author.}

### 2014-04-30 hps-testrun-nim.tex
Added new plot from Omar on time residual.
Fixed size of plot.

@@
 {\small
-	\includegraphics[width=6cm]{figures/run1351_110513_samples_L1_top.pdf}
+	\includegraphics[width=7cm]{figures/run1351_110513_samples_L1_top.pdf}
 	\caption{Accumulation of six pedestal-subtracted samples from individual SVT channels associated 
@@
 {\small
-	\includegraphics[width=7cm]{figures/test_run_1351_hit_time_corrected_top_layer2_mod.pdf}
+	\includegraphics[width=7cm]{figures/run1351_time_residual_top_layer2.pdf}
 	\caption{

### 2014-05-20 hps-testrun-nim.tex
Updated hit efficiency plot from Omar
Final draft comments implemented.

@@
 %% keywords here, in the form: keyword \sep keyword
-silicon microstrip \sep tracking  \sep vertexing \sep heavy photon \sep dark photon \sep hidden sector \sep electromagnetic calorimeter
+silicon \sep microstrip \sep tracking  \sep vertexing \sep heavy photon \sep dark photon \sep hidden sector \sep electromagnetic calorimeter
 %% MSC codes here, in the form: \MSC code \sep code
@@
 
+%\clearpage
+%\tableofcontents
 \clearpage
-\tableofcontents
-\clearpage
-\newpage
+%\newpage
 \newpage
@@
 good mass resolution to identify a small mass peak above the copious QED background. At small 
-couplings, \Aprime{} become long-lived, so detection of a displaced decay vertex can reject the prompt 
+couplings, the \Aprime{} become long-lived, so detection of a displaced decay vertex can reject the prompt 
 QED background and boost experimental sensitivity.
@@
 The HPS experiment~\cite{HPS_proposal_2010} uses both invariant mass and secondary
-vertex signatures to search for \Aprime{}. It uses  a $\approx 1$~m long silicon tracking and vertexing 
-detector
+vertex signatures to search for \Aprime{}. It uses  a $\approx 1$~m long silicon tracking and 
+vertexing detector
 inside a dipole magnet to measure charged particle trajectories and a fast electromagnetic calorimeter 
@@
 \begin{center}
-    \includegraphics[width=0.8\textwidth]{figures/hps_testrun_rendering}
+    \includegraphics[width=0.8\textwidth]{figures/hps_testrun_rendering_2}
 \caption{Rendering of the HPS Test Run apparatus installed on the beam line.}
@@
 {\small
-\caption{Overview of the coverage, segmentation and performance of the HPS Test Run detector. }
+\caption{Overview of the coverage, segmentation and performance of the HPS Test Run detector.
+The $\sigma_{d_0}$ is the track impact parameter resolution of the SVT at the nominal electron target position.
+$\sigma_{pos}$ is the estimated position resolution perpendicular to the strip direction on the silicon sensors of the SVT.}
 \begin{tabular}{lccccccc}
 \hline 
-System & Coverage & \# channels & ADC & Time resolution & \# layers & Segmentation & Performance \\
- & (mrad) &  & (bit) & (ns) &  &  &  \\
+System & Coverage & \# channels & ADC & \# layers & Segmentation & Time resolution  & Performance \\
+ & (mrad) &  & (bit) & &  & (ns)  &  \\
 \hline
-SVT & $15<\theta_{y} < 70$ & 12780 & 14 & $\approx 2$~ns & 5  & $\approx 120~\mu$m $r-\phi$ & $\sigma_{d0,y}  \approx 100~\mu$m \\
-& (5 hits) &  &  &  & (stereo layers) & $\approx 6~\mu$m $z$ & $\sigma_{d0,x} \approx 300~\mu$m \\
-& &  &  &  &  &  & $\sigma_{d0,z}\approx 1$~mm \\
+SVT & $15<\theta_{y} < 70$ & 12780 & 14 & 5    & $30~\mu$m (sense) & $2.5$& $\sigma_{d0,y}  \approx 100~\mu$m \\
+& (5 hits) &  &  & (stereo layers) & $60~\mu$m (readout)  & & $\sigma_{d0,x} \approx 300~\mu$m \\
+& &  &  &  & ($\sigma_{pos} \approx 6~\mu$m) &  & $\sigma_{d0,z}\approx 1$~mm \\
 \hline
-ECal & $15<\theta_{y} < 60$ & 442 & 12 & 4~ns & 1 & $1.33\times1.33$~cm$^2$  & $\sigma(E)/E \approx 4.5\%$ \\ 
- &  &  &  &  &  & $1.6\times1.6$~cm$^2$  &  \\ 
+ECal & $15<\theta_{y} < 60$ & 442 & 12  & 1  & $1.33\times1.33$~cm$^2$ & 4  & $\sigma(E)/E \approx 4.5\%$ \\ 
+ &  &  &   &  & $1.6\times1.6$~cm$^2$  & (trigger)&  \\
+
+%SVT & $15<\theta_{y} < 70$ & 12780 & 14 & 5    & $\approx 120~\mu$m ($r-\phi$) & $\approx 2$& $\sigma_{d0,y}  \approx 100~\mu$m \\
+%& (5 hits) &  &  & (stereo layers) & $\approx 6~\mu$m ($z$)  & & $\sigma_{d0,x} \approx 300~\mu$m \\
+%& &  &  &  &  &  & $\sigma_{d0,z}\approx 1$~mm \\
+%\hline
+%ECal & $15<\theta_{y} < 60$ & 442 & 12  & 1  & $1.33\times1.33$~cm$^2$ & 4  & $\sigma(E)/E \approx 4.5\%$ \\ 
+% &  &  &   &  & $1.6\times1.6$~cm$^2$  & (trigger)&  \\ 
 \hline
@@
 
-The silicon vertex tracking and vertexing detector for the HPS Test Run, or SVT, resides in a vacuum 
+The silicon tracking and vertexing detector for the HPS Test Run, or SVT, resides in a vacuum 
 chamber inside the Pair Spectrometer (PS) dipole magnet in Hall B at JLab. The magnetic field 
@@
 %    \includegraphics[width=0.5\textwidth]{figures/HPS_dimensions}
-    \includegraphics[width=0.45\textwidth]{figures/hps-testrun-beamline-edited2}
+    \includegraphics[width=0.45\textwidth]{figures/hps-testrun-beamline-edited3}
 \caption{\small{Layout of the HPS parasitic run.} }
@@
 The Silicon Vertex Tracker (SVT) enables efficient reconstruction of charged particles and precise 
-determination of their trajectories. These measurements allow \Aprime{} decays to be distinguished 
-from background via simultaneous estimation of the invariant mass of \ee{} decay products and the 
+determination of their trajectories. This allow \Aprime{} decays to be distinguished 
+from background via simultaneous measurements of the invariant mass of \ee{} decay products and the 
 position of decay vertices downstream of the target.
@@
 Meanwhile, very low-energy delta rays from 
-beam-gas interactions multiply the density of background hits, so the SVT must operate inside the 
+beam-gas interactions would multiply the density of background hits, so the SVT must operate inside the 
 beam vacuum.  Finally, in order to protect the sensors, the detector must be movable so that it can be 
-retracted during periods of uncertain beam conditions.
+retracted during periods of uncertain beam conditions or beam tuning.
 
@@
 $<1$\% $X_0$ per layer, single-hit resolution better than 50~$\mu$m and tolerance of a radiation 
-dose of approximately $1.5\times10^{14}$~\fluenceunit{} for a six month run. The sensors 
-were purchased from the Hamamatsu Photonics Corporation for the cancelled 
+dose of approximately $1.5\times10^{14}$~\fluenceunit{} for a six month run. The sensors, produced by 
+Hamamatsu Photonics Corporation, were originally meant for the cancelled 
 Run 2b upgrade of the D\O~experiment~\cite{Denisov:2001aa} which satisfied the requirement that 
@@
 short twisted-pair pigtail cable to provide power and configuration and signal readout. Along with a 
-single sensor, these are glued to a polyamide-laminated carbon fiber composite backing making 
+single sensor, these are glued to a polyimide-laminated carbon fiber composite backing making 
 up a half-module. A window is machined in the carbon fiber leaving only a frame around the periphery 
@@
 electrons and positrons with energy between $0.5$-$6.5$~GeV.  It needs granularity and signal 
-readout speed to handle 1~MHz/cm$^{2}$ of electromagnetic background and be radiation hard. 
+readout speed to handle 1~MHz/cm$^{2}$ of electromagnetic background and to be radiation hard. 
 The PbWO$_{4}$ crystal inner 
-calorimeter of the CLAS detector~\cite{2008erhm.conf..421N}, in operation since 2005 in Hall B, meets 
+calorimeter of the CLAS detector~\cite{clas_ecal,clas_ecal2,clas_thesis}, in operation since 2005 in Hall B, meets 
 all the requirements set by HPS. The modules from this calorimeter have been subsequently 
@@
 that required by the SVT APV25 ASIC. During the HPS Test Run, for the most part the trigger system 
-required only a single cluster in either the top or bottom Ecal halves and was tested to trigger rates 
+required only a single cluster in either the top or bottom ECal halves and was tested to trigger rates 
 above 100~kHz by lowering thresholds.
@@
 somewhat worse than the approximately 2~ns resolution expected for S/N$=$25 which we attribute to the 
-true pulse shape differing from our idealized fit function which will be improved in the future. Reducing 
+true pulse shape differing from our idealized fit function which will be improved in the future~\cite{Friedl2007385}. Reducing 
 the APV25 ASIC pulse shaping time to 35~ns will also improve time resolution. 
@@
 excluded from the track fit itself. Tracks which intersect regions with known bad channels or pass very 
-close to the edge region are excluded. The hit reconstruction efficiency, see Figure~\ref{fig:hit_efficiency}, 
+close to the edge region were excluded. The hit reconstruction efficiency, see Figure~\ref{fig:hit_efficiency}, 
 was measured to be above 98\% and fairly uniform across the SVT.
@@
 {\small
-    	\includegraphics[width=7cm]{figures/single_hit_efficiency_Omar_11192013.pdf}
+    	\includegraphics[width=7cm]{figures/single_hit_efficiency.pdf}
         \caption{ The hit reconstruction efficiency as a function of detector layer.}
@@
 \end{figure}
-The trigger turn-on is slow and reaches an uneven plateau just below 1~GeV for two reasons;  
+The trigger turn-on is slow and reaches an uneven plateau at about 700~MeV for two reasons;  
 gain variations between different crystals lead to the threshold variations and the nonlinearity of 
@@
 thicknesses are used to study the varying multiple Coulomb scattering contribution (pair production 
-angle is constant). 
+angular distribution is constant), and are compared with Geant4~\cite{Agostinelli2003250} standard multiple 
+scattering model and EGS5~\cite{egs5}. 
 %\begin{center}
@@
 \hline
-GEANT4 & 2633 $\pm$ 250 & 	371 $\pm$ 38 &	114 $\pm$ 18 \\
+Geant4 & 2633 $\pm$ 250 & 	371 $\pm$ 38 &	114 $\pm$ 18 \\
 \hline
@@
 Coulomb scattered beam electrons, is well 
-described~\cite{Attwood:2005zz,Shen:1978ha,Gottschalk1993467} . 
+described.
+%~\cite{Attwood:2005zz,Shen:1978ha,Gottschalk1993467} . 
 %One of the main goals of the HPS Test Run was to evaluate the description of the tails of the 

### 2014-06-13 hps-testrun-nim.tex
Fixed web link to snowmass report on arxiv in references. Fixed all the labels for tables and figures. Removed line numbers.

@@
 \usepackage{lineno}
+
+\usepackage{url}
 
@@
 %% keywords here, in the form: keyword \sep keyword
-silicon \sep microstrip \sep tracking  \sep vertexing \sep heavy photon \sep dark photon \sep hidden sector \sep electromagnetic calorimeter
+silicon \sep microstrip \sep tracking  \sep vertexing \sep heavy photon \sep dark photon  \sep electromagnetic calorimeter
 %% MSC codes here, in the form: \MSC code \sep code
@@
 
- \linenumbers
+% \linenumbers
 
@@
 %\tableofcontents
-\clearpage
+%\clearpage
 %\newpage
@@
     \includegraphics[width=0.8\textwidth]{figures/hps_testrun_rendering_2}
-\caption{Rendering of the HPS Test Run apparatus installed on the beam line.}
-\label{fig:testrundetector}
+\caption{Rendering of the HPS Test Run apparatus installed on the beam line.
+\label{fig:testrundetector}}
 \end{center}
@@
 The $\sigma_{d_0}$ is the track impact parameter resolution of the SVT at the nominal electron target position.
-$\sigma_{pos}$ is the estimated position resolution perpendicular to the strip direction on the silicon sensors of the SVT.}
+$\sigma_{pos}$ is the estimated position resolution perpendicular to the strip direction on the silicon sensors of the SVT.
+\label{tab:detector-overview}}
 \begin{tabular}{lccccccc}
@@
 ECal & $15<\theta_{y} < 60$ & 442 & 12  & 1  & $1.33\times1.33$~cm$^2$ & 4  & $\sigma(E)/E \approx 4.5\%$ \\ 
- &  &  &   &  & $1.6\times1.6$~cm$^2$  & (trigger)&  \\
-
-%SVT & $15<\theta_{y} < 70$ & 12780 & 14 & 5    & $\approx 120~\mu$m ($r-\phi$) & $\approx 2$& $\sigma_{d0,y}  \approx 100~\mu$m \\
-%& (5 hits) &  &  & (stereo layers) & $\approx 6~\mu$m ($z$)  & & $\sigma_{d0,x} \approx 300~\mu$m \\
-%& &  &  &  &  &  & $\sigma_{d0,z}\approx 1$~mm \\
-%\hline
-%ECal & $15<\theta_{y} < 60$ & 442 & 12  & 1  & $1.33\times1.33$~cm$^2$ & 4  & $\sigma(E)/E \approx 4.5\%$ \\ 
-% &  &  &   &  & $1.6\times1.6$~cm$^2$  & (trigger)&  \\ 
+ &  &  &   &  & $1.6\times1.6$~cm$^2$  & (trigger)& Ref.~\cite{clas_ecal,clas_ecal2,clas_thesis}  \\ 
 \hline
 \end{tabular}
-\label{tab:detector-overview}
 }
@@
     \includegraphics[width=0.45\textwidth]{figures/hps-testrun-beamline-edited3}
-\caption{\small{Layout of the HPS parasitic run.} }
-\label{fig:hpstest_layout}
+\caption{\small{Layout of the HPS parasitic run.}
+\label{fig:hpstest_layout}}
 \end{figure}
@@
 }
-\caption{Measured integrated currents for the dedicated photon runs.}
-\label{tab:currents}
+\caption{Measured integrated currents for the dedicated photon runs.
+\label{tab:currents}}
 \end{center}
@@
 requiring the sensors to be actively cooled.
-% and~\ref{fig:rates}.
-%===================
-%\begin{figure}[]
-%\includegraphics[width=7cm]{figures/radiation}
-%\label{fig:radiation}
-%\caption{{\small Simulation of the electron fluence 10~cm downstream of the target in the active region 
-%of the SVT ($|Y|>0.15~$mm) looking downstream; electrons bend towards $+x$.}}
-%\end{figure}
 Meanwhile, very low-energy delta rays from 
@@
 \end{tabular}
-\caption{\small Layout of the SVT.}
+\caption{\small Layout of the SVT.
+\label{tab:trk}}
 }
-\label{tab:trk}
-\vspace*{-15mm}
+%\vspace*{-1mm}
 \end{table}
@@
 hybrid readout boards in green. The beam enters from the right through a vacuum box with flanges 
-for services. }
-\label{fig:tracker_model}
+for services. 
+\label{fig:tracker_model}}
 %\vspace*{-5mm}
@@
     \includegraphics[width=7cm]{figures/2012-101-PHOTON-DETECTOR-001}
-\caption{\small{Both halves of the HPS Test Run SVT after final assembly at SLAC.  The cooling manifolds and 
-integrated cable runs are clearly seen.} }
-\label{fig:tracker_halves}
+\caption{\small Both halves of the HPS Test Run SVT after final assembly at SLAC.  The cooling manifolds and 
+integrated cable runs are clearly seen.
+\label{fig:tracker_halves}}
 \end{center}
@@
    	 \includegraphics[width=7cm]{figures/IMG_5200}
-	\caption{\small{A prototype module assembly (foreground) with the 50~mrad (left) and 100~mrad (right) module assembly fixtures in the background.
-A pair of cooling blocks and a spacer block can be seen on the fixtures.} }
-	\label{fig:tracker_module}
-	\end{center}
-\vspace*{-5mm}
+	\caption{\small A prototype module assembly (foreground) with the 50~mrad (left) and 100~mrad (right) module assembly fixtures in the background.
+A pair of cooling blocks and a spacer block can be seen on the fixtures.
+\label{fig:tracker_module}}
+\end{center}
+%\vspace*{-5mm}
 \end{figure}
@@
 \begin{center}
-{\small
 \includegraphics[width=7cm]{figures/ecal-module-schematic.png}
-\caption{A schematic view of an ECal module.}
-\label{fig:ecal-module}
-}
+\caption{\small A schematic view of an ECal module.
+\label{fig:ecal-module}}
 \end{center}
@@
 8.7~cm gap between the innermost edge of the crystals in the two halves.
-{\small
 \begin{figure}[]
@@
 %\includegraphics[width=0.45\textwidth]{figures/ecal_picture_beamline}
-\caption{Rendered layout view of the ECal looking downstream.}
-\label{fig:ecal}
-\end{center}
-\end{figure}
-}
+\caption{\small Rendered layout view of the ECal looking downstream.
+\label{fig:ecal}}
+\end{center}
+\end{figure}
 
@@
 discriminator module and then to a TDC for a timing measurement. 
-%\begin{figure}[]
-%\begin{center}
-%{\small
-%\includegraphics[width=4cm]{figures/FADC250_Photo_001.jpg}
-%\caption{The JLab FADC250 VXS module.}
-%\label{fig:fadc}
-%}
-%\end{center}
-%\end{figure}
 The FADC boards are high speed VXS modules digitizing up to 16 APD signals 
@@
 excessive noise) and 18 were masked offline due to noise.
-%\begin{figure}[]
-%\begin{center}
-%{\small
-%\includegraphics[width=8cm]{figures/fadc_datapath_diagram.png}
-%\caption{The two different readout modes of the FADC used in the HPS Test Run.}
-%\label{fig:hps_trigger_data}
-%}
-%\end{center}
-%\end{figure}
 
@@
 \begin{center}
-{\small
  \includegraphics[width=8cm]{figures/hps_trigger_cal}
-\caption{Block diagram of the ECAL trigger system consisting of the FADC that samples and digitizes 
+\caption{\small Block diagram of the ECAL trigger system consisting of the FADC that samples and digitizes 
 signals for each detector channel and sends them for cluster finding in the CTP. The CTP clusters are 
@@
 ECal. The decision is sent to the Trigger Supervisor (TS) that generates the necessary signals to read out 
-the sub-detectors.}
- \label{fig:hps_trigger_cal}
-}
+the sub-detectors.
+ \label{fig:hps_trigger_cal}}
 \end{center}
@@
 \subsection{SVT Data Acquisition}
-%igitization, Event Building and Data Transmission}
 \label{sec:svt_daq}
@@
 \begin{center}
-{\small
 \includegraphics[width=6cm]{figures/svt_daq_module}
-	\caption{The SVT DAQ COB board with four data processing daughter cards (DPMs) visible on the left side.}
-	\label{fig:cob}
-}
+\caption{\small The SVT DAQ COB board with four data processing daughter cards (DPMs) visible on the left side.
+\label{fig:cob}}
 \end{center}
@@
 \begin{center}
-{\small
 \includegraphics[width=8cm]{figures/svt-daq-sketch}
-	\caption{Block diagram overview of the SVT DAQ.}
-	\label{fig:svtdaq}
-}
+\caption{\small Block diagram overview of the SVT DAQ.
+\label{fig:svtdaq}}
 \end{center}
@@
 \begin{center}
-{\small
 \includegraphics[width=7cm]{figures/run1351_110513_samples_L1_top.pdf}
-	\caption{Accumulation of six pedestal-subtracted samples from individual SVT channels associated 
-	with hits on tracks.}
-	\label{fig:pulse_shape}
-}
+\caption{\small Accumulation of six pedestal-subtracted samples from individual SVT channels associated 
+with hits on tracks.
+\label{fig:pulse_shape}}
 \end{center}
@@
 \begin{center}
-{\small
-	%\includegraphics[width=7cm]{figures/run1351_mip_small.pdf}
 \includegraphics[width=7cm]{figures/mip_top_layer_2.png}
-    	\caption{ The cluster charge distribution for hits associated with a track follow the characteristic 		Landau shape. }
-	\label{fig:cluster_pulse}
-}
+\caption{\small The cluster charge distribution for hits associated with a track follow the characteristic Landau shape. 
+\label{fig:cluster_pulse}}
 \end{center}
@@
 \begin{center}
-{\small
 \includegraphics[width=7cm]{figures/run1351_time_residual_top_layer2.pdf}
-	\caption{
-	The residual of individual cluster times with the average of all clusters on the track. }
-	\label{fig:tracktime}
-}
+\caption{\small The residual of individual cluster times with the average of all clusters on the track. 
+\label{fig:tracktime}}
 \end{center}
@@
 \begin{center}
-{\small
 \includegraphics[width=7cm]{figures/single_hit_efficiency.pdf}
-        \caption{ The hit reconstruction efficiency as a function of detector layer.}
-	\label{fig:hit_efficiency}
-}
+\caption{\small The hit reconstruction efficiency as a function of detector layer.
+\label{fig:hit_efficiency}}
 \end{center}
@@
  \begin{center}
-{\small
 \begin{figure*}[t]
@@
 \includegraphics[width=5cm]{figures/h_sumE_h_sumE_trigsel4hit_pair1351_twotrkfilt-v6-paper}
-\caption{Kinematic distributions for \ee{} pairs selected by opposite charged tracks in the top and bottom half of the tracker: track momentum in the top half of the SVT (left), invariant mass (middle) and the sum of the track energy for the pair (right).}
-\label{fig:pair_kin}
+\caption{\small Kinematic distributions for \ee{} pairs selected by opposite charged tracks in the top and bottom half of the tracker: track momentum in the top half of the SVT (left), invariant mass (middle) and the sum of the track energy for the pair (right).
+\label{fig:pair_kin}}
 \end{figure*}
-}
 \end{center}
@@
 at the converter position. 
-{\small
 \begin{figure}[]
@@
 	\includegraphics[width=7cm]{figures/h_trk_top_fr_conv_y_h_trk_top_conv_y_dataMC_twotrksel-mod}
-	\caption{ Vertical (top) and horizontal (bottom) extrapolated track position at the converter position 
-	taking into account the measured fringe field. }
-	\label{fig:impact_param}
-\end{center}
-\end{figure}
-}
+	\caption{\small Vertical (top) and horizontal (bottom) extrapolated track position at the converter position 
+	taking into account the measured fringe field. 	
+	\label{fig:impact_param}}
+\end{center}
+\end{figure}
 While residual alignments show small shifts, the good agreement  between data and simulated 
@@
 resolution in HPS, with a target at 10~cm, will be as calculated.
-%Furthermore, tails of the vertex distributions are impossible to study with the finite data sample obtained 
-%in the HPS Test Run. Nevertheless, useful information can still be 
-%obtained by studying the vertex distributions. Figure~\ref{fig:vtx_pos} shows the distance of closest 
-%approach of the momentum vectors extrapolated in the upstream direction from our analyzing magnet, 
-%taking into account the measured fringe field of the PS dipole magnet. 
- %\begin{center}
-%{\small
-%	 \begin{figure*}[t]
-%	% Plot info:
-%	% TestRun-v6 geometry, twotrkfilter, trigsel, hps-java-1.8-SNAPSHOT, 4hits, chi2<10
-%	\includegraphics[width=5cm]{figures/h_vtx_fr_x_h_vtx_x_trigsel4hit_pair1351_twotrkfilt-v6-paper}
-%	\includegraphics[width=5cm]{figures/h_vtx_fr_y_h_vtx_y_trigsel4hit_pair1351_twotrkfilt-v6-paper}
-%	\includegraphics[width=5cm]{figures/h_vtx_fr_z_h_vtx_z_trigsel4hit_pair1351_twotrkfilt-v6-paper}
-%	\caption{ Vertex position represented by the distance of closest approach of the extrapolated 
-%	momentum vectors upstream of the PS dipole magnet taking into account the measured fringe field. 
-%	The overall shift from zero in the x-direction is due to a 30~mrad rotation of the SVT with respect to 
-%	the beam line.}
-%	\label{fig:vtx_pos}
-%\end{figure*}
-%}
-%\end{center}
 
@@
 are clustered using a simple algorithm similar to the one 
-deployed for the trigger (see Sec.~\ref{sec:trigger}). Due to the high effective readout threshold of 
-73~MeV the average number of crystals in a cluster was $\sim 3$ and the simple clustering 
+deployed for the trigger (see Sec.~\ref{sec:trigger}). Due to the high effective crystal readout threshold 
+of  73~MeV the average number of crystals in a cluster was $\sim 3$ and the simple clustering 
 algorithm worked well for reconstruction of the detected shower energy. An average noise level of 
-approximately 15~MeV was measured in special pedestal runs.
+approximately 15~MeV per crystal was measured in special pedestal runs.
 
@@
 any efficiency or bias that affect the data should be reflected in the simulation. 
-%Furthermore, a conversion factor calibration is performed to equalize the gains of  each channel. 
-%simulation to those observed in data by comparing .  The ``weighted $E/p$'' for each crystal is %computed, 
-%representing the average $E/p$ for clusters that include the crystal
-% $\frac{\sum_j w_{j,i}}{\sum_j\frac{P_j}{E_j}w_{j,i}}$.
 Iteratively, conversion coefficients for each crystal were adjusted until the $E$/$p$ ratio in data and 
@@
 Figure~\ref{fig:gains}. 
-{\small
 \begin{figure}[]
@@
 	\caption{The ECal energy over track momentum ratio ($E$/$p$) comparing data and simulation 
-	for single cluster triggers in the top half of the ECal.} 
-	\label{fig:gains}
-\end{center}
-\end{figure}
-}
+	for single cluster triggers in the top half of the ECal.
+	\label{fig:gains}}
+\end{center}
+\end{figure}
 The peak position of the distribution indicates the sampling fraction of the ECal, the fraction of the 
@@
 \begin{center}
-{\small
 	%\includegraphics[width=7cm]{figures/h_cl_E_probedata_eff_h_cl_E_probeMC_eff_dataMC_1351-v7-trig-tagBot.pdf}
 	\includegraphics[width=7cm]{figures/h_cl_E_probedata_eff_bay_h_cl_E_probeMC_eff_bay_dataMC_1351-v7-trig-tagBot.pdf}
-	\caption{Trigger efficiency in both halves of the ECal for data and simulation as a 
-	function of cluster energy.}
-\label{fig:turnon}
-}
+	\caption{\small Trigger efficiency in both halves of the ECal for data and simulation as a 
+	function of cluster energy.
+\label{fig:turnon}}
 \end{center}
@@
 \begin{table}
-\label{results}
 {\small
@@
 \caption{ Observed and predicted event rate (in Hz) normalized to 90~nA for three different converter 
-thicknesses. The uncertainty on the prediction includes systematic uncertainties from ECal alignment, background normalization, beam current normalization and limited statistics in the simulation.}
+thicknesses. The uncertainty on the prediction includes systematic uncertainties from ECal alignment, background normalization, beam current normalization and limited statistics in the simulation.
+\label{results}}
 }
@@
 %~\cite{Attwood:2005zz,Shen:1978ha,Gottschalk1993467} .
-%One of the main goals of the HPS Test Run was to evaluate the description of the tails of the 
-%multiple Coulomb scattering to gain further confidence in the expected detector occupancy in the full HPS 
-%experiment. Those occupancies have been evaluated using \egs{}~\cite{egs5} simulation program 
-%whose \moliere{} formulation of multiple scattering show good agreement with previous studies 
-%for a wide range of materials and projectiles~\cite{Attwood:2005zz,Shen:1978ha,Gottschalk1993467}. 
-%Despite all data taken with a photon beam in the HPS Test Run,
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%\section{Multiple Coulomb Scattering Distributions}
-%\label{sec:mcs}
-%Occupancies close to the beam create many of the key challenges in the HPS experiment
-%and determine the limits of sensitivity to low \Aprime{} masses.
-%These occupancies are dominated by electrons which have multiple Coulomb scattered (MCS) 
-%to relatively large angles in the target. Because HPS is sensitive to scattering angles far out on the tail of 
-%the MCS distribution, well beyond the angles important in other experiments, care must be taken
-%to ensure our simulations are correct in this regime.  
-%
-%\subsection{Multiple Coulomb Scattering Models}
-%
-%One of the main goals of the HPS Test Run was to evaluate the description of the tails of the MCS
-%to gain further confidence in the expected detector occupancy in the full HPS experiment. 
-%Previous studies of multiple scattering angles show good agreement with the \moliere{} 
-%theory~\cite{Moliere:1948zz} for a wide range 
-%of materials and projectiles~\cite{Attwood:2005zz,Shen:1978ha,Gottschalk1993467}. We have verified 
-%that the angular distribution $F(\theta)$ in the differential cross section 
-%$d\sigma = F( \theta) d(\cos\theta) d\phi$ for the \egs{}~\cite{egs5} simulation program show good 
-%agreement with \moliere{}'s analytical formula as formulated by Bethe~\cite{Bethe:1953va}. 
-%The small angle approximation was also shown to be in agreement with the theory formulated by 
-%Gaudsmit and Saunderson~\cite{Goudsmit:1940zza,Goudsmit:1940zz} that is valid for any angle. 
-%While \egs{} uses the more complex and time consuming \moliere{} 
-%formula, the default physics list of \geant{} uses the so-called Urban model, an approximation with two, 
-%continuously joined, functions to take into account 
-%small and large angle scattering. Due to the explicit function in large angle approximation used by 
-%\geant{} we expect that \geant{} will overestimate the angular distribution at angles larger than a few 
-%mrad.
-%
-%
-%Figure~\ref{fig:schematic_testrun_vs_erun} gives a schematic view of the main differences 
-%between the photon and electron beam setup. 
-%The angular distribution of the pair produced electron and positron emerging 
-%from the converter in the HPS Test Run has comparable contributions from {\it i)} the pair production angle
-%and {\it ii)} the MCS of the electron and positron in the converter after production. By measuring the 
-%scattering rate at several different converter thicknesses we can vary the contribution from MCS 
-%while the contribution from the pair production angle is constant. This allows us to confirm our model of MCS 
-%despite the fact that all data was taken with a photon beam.
-%
-%
-%\subsection{Running Conditions}
-%
-%Data was taken at three different converter thicknesses with a beam current varying between 
-%$30-70$~nA, see~Table~\ref{tab:currents}.  
-%\begin{table}[t]
-%\begin{center}
-%{\small
-%\begin{tabular}{|c|c|c|}
-%\hline
-%Converter thickness & Duration &  $e^-$ on converter \\
-% (\%$X_0$) & (s) & ($\mu$C)    \\   
-%\hline
-%%\hline
-%1.6   & 911 &   24.4 \\ %24385.9     \\ %27 nA
-%%\hline
-%0.18   & 2640 &   193.5 \\ % 193508.9  \\  %73 nA
-%%\hline
-%0.45  & 2149 &     140.7 \\ %  140709.9  \\ %65.5 nA
-%%\hline
-%0    & 1279  &   88.1 \\ %88079.6  \\
-%\hline
-%\end{tabular}
-%}
-%\caption{Measured integrated currents for the dedicated photon runs.}
-%\label{tab:currents}
-%\end{center}
-%\end{table}
-%The photon beam line during the HPS Test Run produced a relatively 
-%large fraction of pairs 
-%originating upstream of the converter. This contribution was measured during data taking 
-%with ``empty'' converter runs i.e. removing the converter but with all other conditions 
-%the same. 
-%The upstream background measured in the ``empty'' converter runs was subtracted 
-%from the other runs, properly normalized using the measured integrated currents.
-%
-%
-%
-%\subsection{Measured Angular Distributions}
-%
-%For this analysis, we measure angular distribution of electrons and positrons using the ECal.
-%Cluster reconstruction was done using the algorithm described in Sec.~\ref{sec:trigger} build 
-%clusters around seed hits (hits above a ``seed'' energy threshold and with greater energy than any 
-%neighboring hits), and add all neighboring hits above an ``add'' energy threshold.
-%Hit energy is calibrated by matching track momentum to cluster energy, as described in Sec.~\ref{sec:ecal_calibration}.
-The measured angular distribution in the ECal for the three converter thicknesses are shown in Figure~\ref{fig:ang_distr_data}.
-%\begin{figure}[]
-%\begin{center}
-%{\small
-%%	\includegraphics[ width=7cm]{figures/rate_ecalrow_raw.png}
-%	\includegraphics[ width=7cm]{figures/rate_ecalrow_norm_subtr.png}
-%	\caption{Measured vertical angular distributions after integrated beam current 
-%	normalization and background subtraction.}
-%	\label{fig:ang_distr_data}
-%}
-%\end{center}
-%\end{figure}
-%The data has been normalized to the integrated beam current and the background has been 
-%subtracted. The background fraction for the there converter thicknesses was 16\%, 52\% and 71\% 
-%for converter thicknesses of 1.6\%, 0.45\% and 0.18\%, respectively. The background fraction was also 
-%cross-checked by pointing back tracks reconstructed in the SVT to identify the fraction of tracks not emanating from the converter. 
-%%This can be seen in Figure~\ref{fig:extrapol_converter} (bottom) where small 
-%%satellite peaks at $\pm 10$~mm can be identified as tracks from the upstream background. The angular distribution, after normalization and subtracting the upstream background, are shown in 
-%%Figure~\ref{fig:ang_distr_data} (right).  
-%We also checked that the contribution from photons to our triggered 
-%sample was less than 2\% (without angular selections which would further reduce the contribution).
-%
-%
-%These measured angular distributions are compared to simulation to validate 
-%the modeling of the MCS. \egs{}~\cite{egs5} is used to generate 
-%the electromagnetic interactions in the converter while \geant{} is used to simulate the particles after the 
-%converter.  Figure~\ref{fig:ang_distr_dataMC} shows the angular distribution comparing data and 
-%\egs{} normalized to 1~s of beam at 90~nA beam current with a converter thickness of 1.6\%. 
-%Reasonable agreement is obtained in the most important region close to the beam. There is a hint of a 
-%slightly different slope of the data at larger angles; this difference is covered by systematic uncertainties.  
-%The total rates for each converter thickness is shown in Figure~\ref{fig:rate_vs_thickness} and summarized 
-%in Table~\ref{tab:ang_distr_dataMC}.
-%\begin{figure}[]
-%{\small
-%	\begin{center}
-%	\includegraphics[ width=7cm]{figures/dataMC_1351_Hit_Y_top_norm_bkgsub.png}
-%	\caption{Comparison between the observed and predicted angular distribution using \egs{} for a 
-%	converter thickness of 1.6\%. Similar agreement is found for 0.45\% and 0.18\% converter thicknesses. 
-%	Only statistical uncertainties are shown. }
-%	\label{fig:ang_distr_dataMC}
-%\end{center}
-%}
-%\end{figure}
-%\begin{figure}[]
-%\begin{center}
-%{\small
-%	\includegraphics[ width=7cm]{figures/dataMC_egs.png}
-%	\caption{The measured rate as a function of converter thickness for data and \egs{} simulation 
-%	of MCS in 	the converter.} 
-%	\label{fig:rate_vs_thickness}
-%}
-%\end{center}
-%\end{figure}
-%The total systematic uncertainty was estimated to be between 10-18\% depending on the run including:  
-%a 5\% uncertainty on the integrated current normalization, alignment of the ECal, uncertainty from the 
-%background normalization, and limited Monte Carlo statistics.  
-%\begin{center}
-%\begin{table}
-%{\small
-%\begin{tabular}{|l|c|c|c|}
-%\hline
-%Converter (\% r.l.) & 1.60 & 0.45 &	0.18 \\
-%\hline
-%EGS5 &	1162 $\pm$ 112 &	255 $\pm$ 28 &	94 $\pm$ 17	\\
-%\hline
-%GEANT4 & 2633 $\pm$ 250 & 	371 $\pm$ 38 &	114 $\pm$ 18 \\
-%\hline
-%Observed 	& 1064 $\pm$ 2 & 196 $\pm$ 1 &	92 $\pm$ 1 \\						
-%\hline
-%\end{tabular}
-%\caption{ Observed and predicted number of events for 1~s of beam at 90~nA for three different converter 
-%thicknesses. The uncertainty on the prediction includes systematic uncertainties. }
-%}
-%\label{tab:ang_distr_dataMC}
-%\end{table}
-%\end{center}
-%
-%\subsection{Conclusion}
-%In summary, the accurate modeling of the MCS is fundamental to estimate occupancies and trigger rates 
-%for HPS. \egs{} predicts the correct angular distribution across all converter thicknesses as expected while 
-%\geant{}, using the so-called Urban model for multiple scattering overestimates the rates; with the disagreement 
-%increasing  with larger converter thickness. This preliminary result verifies similar studies [] and gives confidence 
-%in our modeling of the MCS 
-%using \egs{} for evaluating the physics reach of HPS.
 
@@
 Performance from each of these subsystems has been shown to be adequate to conduct the full 
-experiment successfully. Studies of multiple Coloumb scattering tails of electrons and positrons from 
+experiment successfully. Studies of multiple Coulomb scattering tails of electrons and positrons from 
 photon conversions further backs expectations from simulation, giving credence to estimates of the 
 detector backgrounds expected in electron beam running for HPS.
-
-%The Test Run achieved the following detector performance:\begin
-%{enumerate}
-%	\item More than 97\% of SVT channels functioned properly
-%	\item Silicon detector signal to noise was 25.5, good enough %to achieve the expected resolutions
-%	\item SVT hit time resolution was 2.6 ns, which will permit %background rejection with tight timing cuts 
-%	\item SVT hit efficiency was greater than 98\%
-%	%\item SVT track reconstruction efficiency was greater than %98\%
-%	\item 87\% of ECal crystals functioned properly, with %%defects to be corrected by planned ECal upgrades
-%	\item The ECal has been successfully calibrated using SVT %tracks
-%	\item The SVT and JLab DAQ were successfully integrated
-%	\item The trigger functioned as designed; the FADC trigger 
-%rate was tested to greater than 100~kHz
-% deficiencies found in Test Run trigger performance are 
-%addressed for the 2014-2015 run
-%\end{enumerate}
-
-%While the Test Run successfully allowed us to test many aspects %of the HPS experiment, there were 
-%limitations to what could be achieved in some key areas such as %mass resolution and vertexing 
-%performance. In particular, the low statistics and lack of 
-%resonances or scattered beam electrons prohibits a 
-%direct analysis of the momentum 
-%and tails of the vertex distribution. However, for both of these %performance parameters, the observed 
-%agreement between data and simulation in key distributions 
-%supports the performance expected for the 
-%proposed experiment.
-
-%\subsection{Lessons Learned}
-
-%In the process of developing the HPS Test Run design, it was found 
-%that this simple system was capable of 
-%delivering a surprising fraction of the physics potential 
-%anticipated for the full experiment.  With this in mind, 
-%we have proposed a new design for the HPS detector that builds 
-%upon the HPS Test Run , principally 
-%by addressing the compromises made for HPS Test Run to ensure the 
-%best possible performance for A$^\prime$ 
-%physics within the envelope of the existing beam line layout and %analyzing magnet. For the SVT, 
-%this design uses the same sensors, readout chips, and module 
-%concept and for the ECal the crystal and 
-%detector layout will be identical, retaining the most successful 
-%elements of the HPS Test Run Run apparatus and addressing the weaknesses %identified during assembly and 
-%operation to ensure the success of the 
-%experiment. The new SVT layout restores the sixth layer for more %robust tracking, adds acceptance in the 
-%deeper layers to increase sensitivity and provides better 
-%silicon cooling to improve longevity. Other major 
-%updates needed for the full experiment are updates to the SVT 
-%electronics and 
-%DAQ; improving connectivity and cabling, moving digitization 
-%closer to the front-end electronics and 
-%updating the data reduction, event handling and trigger 
-%synchronization to reach 50kHz 
-%trigger rates. 
-%This first generation of 
-%the full experiment will be ready to take physics data when 
-%CEBAF begins operation again in 2014.
 

### 2014-06-20 hps-testrun-nim.tex
Fixed urls including breaks, added references from Rouven and changed ph/MeV per crystal from 3 to 8

@@
 
-\usepackage{url}
+%\usepackage{url}
+\usepackage{hyperref}
 
@@
 couples weakly to electric charge by mixing with the Standard Model 
-photon~\cite{Holdom:1985ag}. Consequently, it can be radiated by electrons and subsequently decay 
+photon~\cite{Holdom:1985ag,Galison:1983pa}. Consequently, it can be radiated by electrons and subsequently decay 
 into \ee{} pairs, albeit at rates far below those of QED trident processes. Heavy photons have been 
@@
 explanation of recent astrophysical 
-anomalies~\cite{Adriani:2008zr,FermiLAT:2011ab,Aguilar:2013qda}.  Heavy photons couple directly to  
-hidden sector particles with ``dark'' or ``hidden sector'' charge; these particles
-could constitute all or some of the dark matter~\cite{ArkaniHamed:2008qn}. 
+anomalies, e.g.~\cite{Adriani:2008zr,FermiLAT:2011ab,Aguilar:2013qda}.  
+Heavy photons couple directly to  hidden sector particles with ``dark'' or ``hidden sector'' charge; these 
+particles could constitute all or some of the dark matter, e.g.~\cite{ArkaniHamed:2008qn,Pospelov:2008jd}. 
 Current phenomenology highlights the $20-1000$~MeV/c$^{2}$ mass range, and 
@@
 \end{figure}
-The scintillation light, approximately $3$ photoelectrons/MeV, is read out by a 
+The scintillation light, approximately $8$ photoelectrons/MeV, is read out by a 
 5$\times$5~mm$^2$ Hamamatsu S8664-55 Avalanche Photodiode (APD) with 75\% quantum 
@@
 
-This work has been supported by the US Department of Energy.
+This work has been supported by the US Department of Energy. Rouven Essig is supported in part by the 
+Department of Energy Early Career research program DESC0008061 and by a Sloan Foundation 
+Research Fellowship.
 

### 2014-06-23 hps-testrun-nim.tex
Added funding agencies to ack.
Added slac pub to title

@@
 \usepackage{lineno}
-
-%\usepackage{url}
-\usepackage{hyperref}
 
@@
 % HPS stuff
+%\usepackage{url}
+\usepackage{hyperref}
+\usepackage{fancyhdr}
 \usepackage{color}
@@
 %\include{affiliations}
+\fancypagestyle{firststyle}
+{
+  \fancyhf{}  % clear all header and footer fields
+  \fancyhead[R]{SLAC-PUB-xxxx}  % puts the text on the top Right side
+}
+%\pagestyle{firststyle}
+%\pagestyle{fancy}
+
+\makeatletter
+\let\ps@plain\ps@fancy 
+\makeatother
 
@@
 \begin{document}
+
+\thispagestyle{firststyle}
 
@@
 
-\title{The Heavy Photon Search Test Detector}
+%\title{The Heavy Photon Search Test Detector}
+\title{
+\begin{flushleft}
+%       \mbox{\textmd{ \normalsize -PUB-13/020 }}
+        \mbox{\textmd{ \normalsize SLAC-PUB-15999 }}
+       \end{flushleft}
+{
+The Heavy Photon Search Test Detector
+}
+}
 
@@
 
-This work has been supported by the US Department of Energy. Rouven Essig is supported in part by the 
+This work has been supported by the US Department of Energy, French Centre National de la Recherche 
+Scientifique and Italian Istituto Nazionale di Fisica Nucleare. Rouven Essig is supported in part by the 
 Department of Energy Early Career research program DESC0008061 and by a Sloan Foundation 

### 2014-06-23 hps-testrun-nim.tex
removed fancyhdr package not used anyway
moving figures around and adding more funding agencies.

--- 2014-06-20 hps-testrun-nim.tex
@@
 % HPS stuff
+%\usepackage{url}
+\usepackage{hyperref}
+%\usepackage{fancyhdr}
 \usepackage{color}
@@
 \title{The Heavy Photon Search Test Detector}
+%\title{
+%\begin{flushleft}
+%%       \mbox{\textmd{ \normalsize -PUB-13/020 }}
+%        \mbox{\textmd{ \normalsize SLAC-PUB-15999 }}
+%       \end{flushleft}
+%{
+%The Heavy Photon Search Test Detector
+%}
+%}
 
@@
 
-%\author[label1]{Per Ledin}
-%\ead{contact@hps.discovery.com}
 %\author[slac]{Per Hansson Adrian\corref{cor1}}
 %\ead{phansson@slac.stanford.edu}
-%\author[slac]{Timothy K. Nelson}
 %\address[slac]{SLAC National Accelerator Laboratory, 94025, Menlo Park, CA, USA}
-%\address[label1]{Lule\aa~Hockey}
 
@@
 %%
-% \linenumbers
+\linenumbers
 
@@
 \begin{center}
-    \includegraphics[width=0.8\textwidth]{figures/hps_testrun_rendering_2}
+    \includegraphics[width=0.8\textwidth]{hps_testrun_rendering_2}
 \caption{Rendering of the HPS Test Run apparatus installed on the beam line.
@@
 \begin{figure}[]
-%    \includegraphics[width=0.5\textwidth]{figures/HPS_dimensions}
-    \includegraphics[width=0.45\textwidth]{figures/hps-testrun-beamline-edited3}
+    \includegraphics[width=0.45\textwidth]{hps-testrun-beamline-edited3}
 \caption{\small{Layout of the HPS parasitic run.}
@@
 through the PS pair converter gold foil and later the HPS system.
-%\begin{figure}[]
-%\includegraphics[ width=7cm]{figures/photon_vs_electron_beam_schematic.png}
-%\caption{\small{Illustrative comparison of HPS Test Run photon beam compared to the HPS electron 
-%beam.}}
-%\label{fig:schematic_testrun_vs_erun}
-%\end{figure}
 The PS pair converter was located $\approx~77$~cm upstream of the first layer of the SVT.
@@
 \begin{figure}[htp]
-\includegraphics[width=7cm]{figures/HPS_nochamber}
+\includegraphics[width=7cm]{HPS_nochamber}
 \caption{\small A rendering of the SVT showing the modules on their support plates held by the 
@@
 \begin{center}
-    \includegraphics[width=7cm]{figures/2012-101-PHOTON-DETECTOR-001}
+    \includegraphics[width=7cm]{2012-101-PHOTON-DETECTOR-001}
 \caption{\small Both halves of the HPS Test Run SVT after final assembly at SLAC.  The cooling manifolds and 
@@
 	\begin{center}
-   	 \includegraphics[width=7cm]{figures/IMG_5200}
+   	 \includegraphics[width=7cm]{IMG_5200}
 	\caption{\small A prototype module assembly (foreground) with the 50~mrad (left) and 100~mrad (right) module assembly fixtures in the background.
@@
 \begin{center}
-\includegraphics[width=7cm]{figures/ecal-module-schematic.png}
+\includegraphics[width=7cm]{ecal-module-schematic.png}
 \caption{\small A schematic view of an ECal module.
@@
 \begin{center}
-\includegraphics[width=0.45\textwidth]{figures/ECal}
-%\includegraphics[width=0.45\textwidth]{figures/ecal_picture_beamline}
+\includegraphics[width=0.45\textwidth]{ECal}
 \caption{\small Rendered layout view of the ECal looking downstream.
@@
 \begin{center}
- \includegraphics[width=8cm]{figures/hps_trigger_cal}
+ \includegraphics[width=8cm]{hps_trigger_cal}
 \caption{\small Block diagram of the ECAL trigger system consisting of the FADC that samples and digitizes 
@@
 \begin{center}
-\includegraphics[width=6cm]{figures/svt_daq_module}
+\includegraphics[width=6cm]{svt_daq_module}
 \caption{\small The SVT DAQ COB board with four data processing daughter cards (DPMs) visible on the left side.
@@
 \begin{center}
-\includegraphics[width=8cm]{figures/svt-daq-sketch}
+\includegraphics[width=8cm]{svt-daq-sketch}
 \caption{\small Block diagram overview of the SVT DAQ.
@@
 \begin{center}
-\includegraphics[width=7cm]{figures/run1351_110513_samples_L1_top.pdf}
+\includegraphics[width=7cm]{run1351_110513_samples_L1_top.pdf}
 \caption{\small Accumulation of six pedestal-subtracted samples from individual SVT channels associated 
@@
 \begin{center}
-\includegraphics[width=7cm]{figures/mip_top_layer_2.png}
+\includegraphics[width=7cm]{mip_top_layer_2.png}
 \caption{\small The cluster charge distribution for hits associated with a track follow the characteristic Landau shape. 
@@
 \begin{center}
-\includegraphics[width=7cm]{figures/run1351_time_residual_top_layer2.pdf}
+\includegraphics[width=7cm]{run1351_time_residual_top_layer2.pdf}
 \caption{\small The residual of individual cluster times with the average of all clusters on the track. 
@@
 \begin{center}
-\includegraphics[width=7cm]{figures/single_hit_efficiency.pdf}
+\includegraphics[width=7cm]{single_hit_efficiency.pdf}
 \caption{\small The hit reconstruction efficiency as a function of detector layer.
@@
 \begin{figure*}[t]
-\includegraphics[width=5cm]{figures/h_trk_top_px_h_trk_top_px_trigsel4hit_pair1351_twotrkfilt-v6-paper-mod}
-\includegraphics[width=5cm]{figures/h_invM_h_invM_trigsel4hit_pair1351_twotrkfilt-v6-paper-mod}
-\includegraphics[width=5cm]{figures/h_sumE_h_sumE_trigsel4hit_pair1351_twotrkfilt-v6-paper}
+\includegraphics[width=5cm]{h_trk_top_px_h_trk_top_px_trigsel4hit_pair1351_twotrkfilt-v6-paper-mod}
+\includegraphics[width=5cm]{h_invM_h_invM_trigsel4hit_pair1351_twotrkfilt-v6-paper-mod}
+\includegraphics[width=5cm]{h_sumE_h_sumE_trigsel4hit_pair1351_twotrkfilt-v6-paper}
 \caption{\small Kinematic distributions for \ee{} pairs selected by opposite charged tracks in the top and bottom half of the tracker: track momentum in the top half of the SVT (left), invariant mass (middle) and the sum of the track energy for the pair (right).
@@
 	% TestRun-v6 geometry, twotrkfilter, trigsel, hps-java-1.8-SNAPSHOT, 4hits, chi2<10
-	\includegraphics[width=7cm]{figures/h_trk_top_fr_conv_z_h_trk_top_conv_z_dataMC_twotrksel-mod}
-	\includegraphics[width=7cm]{figures/h_trk_top_fr_conv_y_h_trk_top_conv_y_dataMC_twotrksel-mod}
+	\includegraphics[width=7cm]{h_trk_top_fr_conv_z_h_trk_top_conv_z_dataMC_twotrksel-mod}
+	\includegraphics[width=7cm]{h_trk_top_fr_conv_y_h_trk_top_conv_y_dataMC_twotrksel-mod}
 	\caption{\small Vertical (top) and horizontal (bottom) extrapolated track position at the converter position 
@@
 \begin{center}
-	\includegraphics[width=7cm]{figures/h_ep_data_0_h_ep_MC_0_dataMC_1351-v6-v6gains_2-trig-top-cl600reg0.pdf}
+	\includegraphics[width=7cm]{h_ep_data_0_h_ep_MC_0_dataMC_1351-v6-v6gains_2-trig-top-cl600reg0.pdf}
 	\caption{The ECal energy over track momentum ratio ($E$/$p$) comparing data and simulation 
@@
 \begin{center}
-	%\includegraphics[width=7cm]{figures/h_cl_E_probedata_eff_h_cl_E_probeMC_eff_dataMC_1351-v7-trig-tagBot.pdf}
-	\includegraphics[width=7cm]{figures/h_cl_E_probedata_eff_bay_h_cl_E_probeMC_eff_bay_dataMC_1351-v7-trig-tagBot.pdf}
+	\includegraphics[width=7cm]{h_cl_E_probedata_eff_bay_h_cl_E_probeMC_eff_bay_dataMC_1351-v7-trig-tagBot.pdf}
 	\caption{\small Trigger efficiency in both halves of the ECal for data and simulation as a 
@@
 
-This work has been supported by the US Department of Energy. Rouven Essig is supported in part by the 
-Department of Energy Early Career research program DESC0008061 and by a Sloan Foundation 
-Research Fellowship.
+This work has been supported by the US Department of Energy, 
+the National Science Foundation,  
+French Centre National de la Recherche Scientifique and 
+Italian Istituto Nazionale di Fisica Nucleare. 
+Rouven Essig is supported in part by the Department of Energy Early Career research program DESC0008061and by a Sloan Foundation Research Fellowship.
+Authored by Jefferson Science Associates, LLC under U.S. DOE Contract No. DE-AC05-06OR23177.
 

### 2014-06-23 figures/eoverp_simulation.C

@@ -1,319 +1,0 @@
-{
-//=========Macro generated from canvas: c1/c1
-//=========  (Sun Nov  3 10:47:06 2013) by ROOT version5.34/02
-   TCanvas *c1 = new TCanvas("c1", "c1",462,167,700,500);
-   c1->Range(-28.75,-6.875,28.75,6.875);
-   c1->SetFillColor(0);
-   c1->SetBorderMode(0);
-   c1->SetBorderSize(2);
-   c1->SetFrameBorderMode(0);
-   c1->SetFrameBorderMode(0);
-   
-   TH2F *Weighted_E_over_p___simulation = new TH2F("Weighted_E_over_p___simulation","",46,-23,23,11,-5.5,5.5);
-   Weighted_E_over_p___simulation->SetBinContent(97,0.5579334);
-   Weighted_E_over_p___simulation->SetBinContent(98,0.5217313);
-   Weighted_E_over_p___simulation->SetBinContent(99,0.5801432);
-   Weighted_E_over_p___simulation->SetBinContent(101,0.5864096);
-   Weighted_E_over_p___simulation->SetBinContent(136,0.5358216);
-   Weighted_E_over_p___simulation->SetBinContent(139,0.3039966);
-   Weighted_E_over_p___simulation->SetBinContent(145,0.5498434);
-   Weighted_E_over_p___simulation->SetBinContent(146,0.5262334);
-   Weighted_E_over_p___simulation->SetBinContent(147,0.5645973);
-   Weighted_E_over_p___simulation->SetBinContent(148,0.5952938);
-   Weighted_E_over_p___simulation->SetBinContent(149,0.5729468);
-   Weighted_E_over_p___simulation->SetBinContent(150,0.5246441);
-   Weighted_E_over_p___simulation->SetBinContent(151,0.5458525);
-   Weighted_E_over_p___simulation->SetBinContent(152,0.5935053);
-   Weighted_E_over_p___simulation->SetBinContent(153,0.6302873);
-   Weighted_E_over_p___simulation->SetBinContent(155,0.6811373);
-   Weighted_E_over_p___simulation->SetBinContent(157,0.696807);
-   Weighted_E_over_p___simulation->SetBinContent(172,0.1450471);
-   Weighted_E_over_p___simulation->SetBinContent(176,0.3996336);
-   Weighted_E_over_p___simulation->SetBinContent(178,0.1868388);
-   Weighted_E_over_p___simulation->SetBinContent(179,0.6862207);
[…]

### 2014-06-23 figures/h_cl_E_probedata_eff_h_cl_E_probeMC_eff_dataMC_1351-v7-trig-tagBot.C

@@ -1,262 +1,0 @@
-{
-//=========Macro generated from canvas: cDefault/cDefault
-//=========  (Tue Jan 14 19:43:09 2014) by ROOT version5.34/14
-   TCanvas *cDefault = new TCanvas("cDefault", "cDefault",10,32,600,600);
-   gStyle->SetOptFit(1);
-   gStyle->SetOptTitle(0);
-   cDefault->Range(-0.4210526,-0.2468354,2.210526,1.398734);
-   cDefault->SetFillColor(0);
-   cDefault->SetBorderMode(0);
-   cDefault->SetBorderSize(2);
-   cDefault->SetTickx(1);
-   cDefault->SetTicky(1);
-   cDefault->SetLeftMargin(0.16);
-   cDefault->SetRightMargin(0.08);
-   cDefault->SetTopMargin(0.06);
-   cDefault->SetBottomMargin(0.15);
-   cDefault->SetFrameBorderMode(0);
-   cDefault->SetFrameBorderMode(0);
-   
-   TH1F *h_cl_E_probeMC_eff = new TH1F("h_cl_E_probeMC_eff","bot tag",20,0,2);
-   h_cl_E_probeMC_eff->SetBinContent(2,0.06951872);
-   h_cl_E_probeMC_eff->SetBinContent(3,0.08219178);
-   h_cl_E_probeMC_eff->SetBinContent(4,0.3276353);
-   h_cl_E_probeMC_eff->SetBinContent(5,0.4895397);
-   h_cl_E_probeMC_eff->SetBinContent(6,0.5555556);
-   h_cl_E_probeMC_eff->SetBinContent(7,0.7238095);
-   h_cl_E_probeMC_eff->SetBinContent(8,0.9135802);
-   h_cl_E_probeMC_eff->SetBinContent(9,0.9622642);
-   h_cl_E_probeMC_eff->SetBinContent(10,0.9518072);
-   h_cl_E_probeMC_eff->SetBinContent(11,0.9821429);
-   h_cl_E_probeMC_eff->SetBinContent(12,0.9772727);
-   h_cl_E_probeMC_eff->SetBinContent(13,0.9767442);
-   h_cl_E_probeMC_eff->SetBinContent(14,0.9677419);
-   h_cl_E_probeMC_eff->SetBinContent(15,1);
[…]

### 2014-06-23 figures/h_ep_data_0_h_ep_MC_0_dataMC_1351-v6-v6gains_2-trig-top-cl600reg0.C

@@ -1,310 +1,0 @@
-{
-//=========Macro generated from canvas: cDefault/cDefault
-//=========  (Fri Jan 17 12:19:50 2014) by ROOT version5.34/14
-   TCanvas *cDefault = new TCanvas("cDefault", "cDefault",10,44,600,600);
-   gStyle->SetOptFit(1);
-   gStyle->SetOptTitle(0);
-   cDefault->Range(-0.4210526,-935.3733,2.210526,5300.449);
-   cDefault->SetFillColor(0);
-   cDefault->SetBorderMode(0);
-   cDefault->SetBorderSize(2);
-   cDefault->SetTickx(1);
-   cDefault->SetTicky(1);
-   cDefault->SetLeftMargin(0.16);
-   cDefault->SetRightMargin(0.08);
-   cDefault->SetTopMargin(0.06);
-   cDefault->SetBottomMargin(0.15);
-   cDefault->SetFrameBorderMode(0);
-   cDefault->SetFrameBorderMode(0);
-   
-   TH1F *h_ep_MC_0 = new TH1F("h_ep_MC_0","",50,0,2);
-   h_ep_MC_0->SetBinContent(5,8.328486);
-   h_ep_MC_0->SetBinContent(7,8.328486);
-   h_ep_MC_0->SetBinContent(8,16.65697);
-   h_ep_MC_0->SetBinContent(9,8.328486);
-   h_ep_MC_0->SetBinContent(10,41.64243);
-   h_ep_MC_0->SetBinContent(11,66.62789);
-   h_ep_MC_0->SetBinContent(12,141.5843);
-   h_ep_MC_0->SetBinContent(13,208.2122);
-   h_ep_MC_0->SetBinContent(14,316.4825);
-   h_ep_MC_0->SetBinContent(15,732.9068);
-   h_ep_MC_0->SetBinContent(16,1474.142);
-   h_ep_MC_0->SetBinContent(17,2956.613);
-   h_ep_MC_0->SetBinContent(18,3414.679);
-   h_ep_MC_0->SetBinContent(19,3789.461);
-   h_ep_MC_0->SetBinContent(20,2173.735);
-   h_ep_MC_0->SetBinContent(21,1016.075);
-   h_ep_MC_0->SetBinContent(22,374.7819);
-   h_ep_MC_0->SetBinContent(23,91.61335);
[…]

### 2014-06-23 figures/h_ep_data_h_ep_mc_dataMC_v5_1351_goodregion_notrkcuts.C

@@ -1,317 +1,0 @@
-{
-//=========Macro generated from canvas: cDefault/cDefault
-//=========  (Wed Nov 27 16:53:20 2013) by ROOT version5.34/02
-   TCanvas *cDefault = new TCanvas("cDefault", "cDefault",10,44,600,600);
-   gStyle->SetOptFit(1);
-   gStyle->SetOptTitle(0);
-   cDefault->Range(-0.4210526,-2.683257,2.210526,15.20512);
-   cDefault->SetFillColor(0);
-   cDefault->SetBorderMode(0);
-   cDefault->SetBorderSize(2);
-   cDefault->SetTickx(1);
-   cDefault->SetTicky(1);
-   cDefault->SetLeftMargin(0.16);
-   cDefault->SetRightMargin(0.08);
-   cDefault->SetTopMargin(0.06);
-   cDefault->SetBottomMargin(0.15);
-   cDefault->SetFrameBorderMode(0);
-   cDefault->SetFrameBorderMode(0);
-   
-   TH1F *h_ep_mc = new TH1F("h_ep_mc","",50,0,2);
-   h_ep_mc->SetBinContent(5,0.01211887);
-   h_ep_mc->SetBinContent(6,0.04847549);
-   h_ep_mc->SetBinContent(7,0.03635662);
-   h_ep_mc->SetBinContent(8,0.01211887);
-   h_ep_mc->SetBinContent(9,0.06059437);
-   h_ep_mc->SetBinContent(10,0.193902);
-   h_ep_mc->SetBinContent(11,0.4362794);
-   h_ep_mc->SetBinContent(12,0.7271324);
-   h_ep_mc->SetBinContent(13,1.551216);
-   h_ep_mc->SetBinContent(14,3.114551);
-   h_ep_mc->SetBinContent(15,4.871787);
-   h_ep_mc->SetBinContent(16,7.901505);
-   h_ep_mc->SetBinContent(17,10.13138);
-   h_ep_mc->SetBinContent(18,10.87063);
-   h_ep_mc->SetBinContent(19,9.695099);
-   h_ep_mc->SetBinContent(20,6.616905);
-   h_ep_mc->SetBinContent(21,2.726747);
-   h_ep_mc->SetBinContent(22,1.102818);
-   h_ep_mc->SetBinContent(23,0.2060209);
-   h_ep_mc->SetBinContent(24,0.08483211);
[…]

### 2014-06-23 figures/top_turn_on__bottom_tag.C

@@ -1,138 +1,0 @@
-{
-//=========Macro generated from canvas: c1/c1
-//=========  (Sun Nov  3 10:54:33 2013) by ROOT version5.34/02
-   TCanvas *c1 = new TCanvas("c1", "c1",462,167,700,500);
-   c1->Range(-800.0001,-0.13125,7200,1.18125);
-   c1->SetFillColor(0);
-   c1->SetBorderMode(0);
-   c1->SetBorderSize(2);
-   c1->SetFrameBorderMode(0);
-   c1->SetFrameBorderMode(0);
-   
-   TH1F *top_turn_on__bottom_tag = new TH1F("top_turn_on__bottom_tag","",200,0,6400);
-   top_turn_on__bottom_tag->SetBinContent(38,0.1666667);
-   top_turn_on__bottom_tag->SetBinContent(40,0.1428571);
-   top_turn_on__bottom_tag->SetBinContent(42,1);
-   top_turn_on__bottom_tag->SetBinContent(43,0.75);
-   top_turn_on__bottom_tag->SetBinContent(44,0.7272727);
-   top_turn_on__bottom_tag->SetBinContent(45,0.75);
-   top_turn_on__bottom_tag->SetBinContent(46,1);
-   top_turn_on__bottom_tag->SetBinContent(47,1);
-   top_turn_on__bottom_tag->SetBinContent(48,1);
-   top_turn_on__bottom_tag->SetBinContent(49,1);
-   top_turn_on__bottom_tag->SetBinContent(50,0.9333333);
-   top_turn_on__bottom_tag->SetBinContent(51,1);
-   top_turn_on__bottom_tag->SetBinContent(52,1);
-   top_turn_on__bottom_tag->SetBinContent(53,1);
-   top_turn_on__bottom_tag->SetBinContent(54,0.8333334);
-   top_turn_on__bottom_tag->SetBinContent(55,1);
-   top_turn_on__bottom_tag->SetBinContent(56,1);
-   top_turn_on__bottom_tag->SetBinContent(57,1);
-   top_turn_on__bottom_tag->SetBinContent(58,1);
-   top_turn_on__bottom_tag->SetBinContent(59,0.8);
-   top_turn_on__bottom_tag->SetBinContent(60,1);
-   top_turn_on__bottom_tag->SetBinContent(61,1);
-   top_turn_on__bottom_tag->SetBinContent(62,0.8181819);
[…]

### 2014-06-23 figures/top_turn_on__bottom_tag_E.C

@@ -1,231 +1,0 @@
-{
-//=========Macro generated from canvas: c1/c1
-//=========  (Tue Nov  5 16:38:38 2013) by ROOT version5.34/02
-   TCanvas *c1 = new TCanvas("c1", "c1",1817,129,700,500);
-   c1->Range(-0.3125,-0.13125,2.8125,1.18125);
-   c1->SetFillColor(0);
-   c1->SetBorderMode(0);
-   c1->SetBorderSize(2);
-   c1->SetFrameBorderMode(0);
-   c1->SetFrameBorderMode(0);
-   
-   TH1F *top_turn_on__bottom_tag = new TH1F("top_turn_on__bottom_tag","",200,0,2.5);
-   top_turn_on__bottom_tag->SetBinContent(5,0.02380952);
-   top_turn_on__bottom_tag->SetBinContent(6,0.02898551);
-   top_turn_on__bottom_tag->SetBinContent(8,0.02083333);
-   top_turn_on__bottom_tag->SetBinContent(9,0.01408451);
-   top_turn_on__bottom_tag->SetBinContent(11,0.03825136);
-   top_turn_on__bottom_tag->SetBinContent(12,0.02994012);
-   top_turn_on__bottom_tag->SetBinContent(13,0.04545455);
-   top_turn_on__bottom_tag->SetBinContent(14,0.06010928);
-   top_turn_on__bottom_tag->SetBinContent(15,0.06547619);
-   top_turn_on__bottom_tag->SetBinContent(16,0.06000001);
-   top_turn_on__bottom_tag->SetBinContent(17,0.06766918);
-   top_turn_on__bottom_tag->SetBinContent(18,0.07936508);
-   top_turn_on__bottom_tag->SetBinContent(19,0.1376147);
-   top_turn_on__bottom_tag->SetBinContent(20,0.1134021);
-   top_turn_on__bottom_tag->SetBinContent(21,0.15625);
-   top_turn_on__bottom_tag->SetBinContent(22,0.1428571);
-   top_turn_on__bottom_tag->SetBinContent(23,0.2795699);
-   top_turn_on__bottom_tag->SetBinContent(24,0.2142857);
-   top_turn_on__bottom_tag->SetBinContent(25,0.3207546);
-   top_turn_on__bottom_tag->SetBinContent(26,0.3181818);
-   top_turn_on__bottom_tag->SetBinContent(27,0.202381);
[…]

### 2014-06-23 figures_old/figures_old/eoverp_simulation.C

@@ -1,0 +1,319 @@
+{
+//=========Macro generated from canvas: c1/c1
+//=========  (Sun Nov  3 10:47:06 2013) by ROOT version5.34/02
+   TCanvas *c1 = new TCanvas("c1", "c1",462,167,700,500);
+   c1->Range(-28.75,-6.875,28.75,6.875);
+   c1->SetFillColor(0);
+   c1->SetBorderMode(0);
+   c1->SetBorderSize(2);
+   c1->SetFrameBorderMode(0);
+   c1->SetFrameBorderMode(0);
+   
+   TH2F *Weighted_E_over_p___simulation = new TH2F("Weighted_E_over_p___simulation","",46,-23,23,11,-5.5,5.5);
+   Weighted_E_over_p___simulation->SetBinContent(97,0.5579334);
+   Weighted_E_over_p___simulation->SetBinContent(98,0.5217313);
+   Weighted_E_over_p___simulation->SetBinContent(99,0.5801432);
+   Weighted_E_over_p___simulation->SetBinContent(101,0.5864096);
+   Weighted_E_over_p___simulation->SetBinContent(136,0.5358216);
+   Weighted_E_over_p___simulation->SetBinContent(139,0.3039966);
+   Weighted_E_over_p___simulation->SetBinContent(145,0.5498434);
+   Weighted_E_over_p___simulation->SetBinContent(146,0.5262334);
+   Weighted_E_over_p___simulation->SetBinContent(147,0.5645973);
+   Weighted_E_over_p___simulation->SetBinContent(148,0.5952938);
+   Weighted_E_over_p___simulation->SetBinContent(149,0.5729468);
+   Weighted_E_over_p___simulation->SetBinContent(150,0.5246441);
+   Weighted_E_over_p___simulation->SetBinContent(151,0.5458525);
+   Weighted_E_over_p___simulation->SetBinContent(152,0.5935053);
+   Weighted_E_over_p___simulation->SetBinContent(153,0.6302873);
+   Weighted_E_over_p___simulation->SetBinContent(155,0.6811373);
+   Weighted_E_over_p___simulation->SetBinContent(157,0.696807);
+   Weighted_E_over_p___simulation->SetBinContent(172,0.1450471);
+   Weighted_E_over_p___simulation->SetBinContent(176,0.3996336);
+   Weighted_E_over_p___simulation->SetBinContent(178,0.1868388);
+   Weighted_E_over_p___simulation->SetBinContent(179,0.6862207);
[…]

### 2014-06-23 figures_old/figures_old/h_cl_E_probedata_eff_h_cl_E_probeMC_eff_dataMC_1351-v7-trig-tagBot.C

@@ -1,0 +1,262 @@
+{
+//=========Macro generated from canvas: cDefault/cDefault
+//=========  (Tue Jan 14 19:43:09 2014) by ROOT version5.34/14
+   TCanvas *cDefault = new TCanvas("cDefault", "cDefault",10,32,600,600);
+   gStyle->SetOptFit(1);
+   gStyle->SetOptTitle(0);
+   cDefault->Range(-0.4210526,-0.2468354,2.210526,1.398734);
+   cDefault->SetFillColor(0);
+   cDefault->SetBorderMode(0);
+   cDefault->SetBorderSize(2);
+   cDefault->SetTickx(1);
+   cDefault->SetTicky(1);
+   cDefault->SetLeftMargin(0.16);
+   cDefault->SetRightMargin(0.08);
+   cDefault->SetTopMargin(0.06);
+   cDefault->SetBottomMargin(0.15);
+   cDefault->SetFrameBorderMode(0);
+   cDefault->SetFrameBorderMode(0);
+   
+   TH1F *h_cl_E_probeMC_eff = new TH1F("h_cl_E_probeMC_eff","bot tag",20,0,2);
+   h_cl_E_probeMC_eff->SetBinContent(2,0.06951872);
+   h_cl_E_probeMC_eff->SetBinContent(3,0.08219178);
+   h_cl_E_probeMC_eff->SetBinContent(4,0.3276353);
+   h_cl_E_probeMC_eff->SetBinContent(5,0.4895397);
+   h_cl_E_probeMC_eff->SetBinContent(6,0.5555556);
+   h_cl_E_probeMC_eff->SetBinContent(7,0.7238095);
+   h_cl_E_probeMC_eff->SetBinContent(8,0.9135802);
+   h_cl_E_probeMC_eff->SetBinContent(9,0.9622642);
+   h_cl_E_probeMC_eff->SetBinContent(10,0.9518072);
+   h_cl_E_probeMC_eff->SetBinContent(11,0.9821429);
+   h_cl_E_probeMC_eff->SetBinContent(12,0.9772727);
+   h_cl_E_probeMC_eff->SetBinContent(13,0.9767442);
+   h_cl_E_probeMC_eff->SetBinContent(14,0.9677419);
+   h_cl_E_probeMC_eff->SetBinContent(15,1);
[…]

### 2014-06-23 figures_old/figures_old/top_turn_on__bottom_tag_E.C

@@ -1,0 +1,231 @@
+{
+//=========Macro generated from canvas: c1/c1
+//=========  (Tue Nov  5 16:38:38 2013) by ROOT version5.34/02
+   TCanvas *c1 = new TCanvas("c1", "c1",1817,129,700,500);
+   c1->Range(-0.3125,-0.13125,2.8125,1.18125);
+   c1->SetFillColor(0);
+   c1->SetBorderMode(0);
+   c1->SetBorderSize(2);
+   c1->SetFrameBorderMode(0);
+   c1->SetFrameBorderMode(0);
+   
+   TH1F *top_turn_on__bottom_tag = new TH1F("top_turn_on__bottom_tag","",200,0,2.5);
+   top_turn_on__bottom_tag->SetBinContent(5,0.02380952);
+   top_turn_on__bottom_tag->SetBinContent(6,0.02898551);
+   top_turn_on__bottom_tag->SetBinContent(8,0.02083333);
+   top_turn_on__bottom_tag->SetBinContent(9,0.01408451);
+   top_turn_on__bottom_tag->SetBinContent(11,0.03825136);
+   top_turn_on__bottom_tag->SetBinContent(12,0.02994012);
+   top_turn_on__bottom_tag->SetBinContent(13,0.04545455);
+   top_turn_on__bottom_tag->SetBinContent(14,0.06010928);
+   top_turn_on__bottom_tag->SetBinContent(15,0.06547619);
+   top_turn_on__bottom_tag->SetBinContent(16,0.06000001);
+   top_turn_on__bottom_tag->SetBinContent(17,0.06766918);
+   top_turn_on__bottom_tag->SetBinContent(18,0.07936508);
+   top_turn_on__bottom_tag->SetBinContent(19,0.1376147);
+   top_turn_on__bottom_tag->SetBinContent(20,0.1134021);
+   top_turn_on__bottom_tag->SetBinContent(21,0.15625);
+   top_turn_on__bottom_tag->SetBinContent(22,0.1428571);
+   top_turn_on__bottom_tag->SetBinContent(23,0.2795699);
+   top_turn_on__bottom_tag->SetBinContent(24,0.2142857);
+   top_turn_on__bottom_tag->SetBinContent(25,0.3207546);
+   top_turn_on__bottom_tag->SetBinContent(26,0.3181818);
+   top_turn_on__bottom_tag->SetBinContent(27,0.202381);
[…]

### 2014-06-23 figures_old/h_ep_data_h_ep_mc_dataMC_v5_1351_goodregion_notrkcuts.C

@@ -1,0 +1,317 @@
+{
+//=========Macro generated from canvas: cDefault/cDefault
+//=========  (Wed Nov 27 16:53:20 2013) by ROOT version5.34/02
+   TCanvas *cDefault = new TCanvas("cDefault", "cDefault",10,44,600,600);
+   gStyle->SetOptFit(1);
+   gStyle->SetOptTitle(0);
+   cDefault->Range(-0.4210526,-2.683257,2.210526,15.20512);
+   cDefault->SetFillColor(0);
+   cDefault->SetBorderMode(0);
+   cDefault->SetBorderSize(2);
+   cDefault->SetTickx(1);
+   cDefault->SetTicky(1);
+   cDefault->SetLeftMargin(0.16);
+   cDefault->SetRightMargin(0.08);
+   cDefault->SetTopMargin(0.06);
+   cDefault->SetBottomMargin(0.15);
+   cDefault->SetFrameBorderMode(0);
+   cDefault->SetFrameBorderMode(0);
+   
+   TH1F *h_ep_mc = new TH1F("h_ep_mc","",50,0,2);
+   h_ep_mc->SetBinContent(5,0.01211887);
+   h_ep_mc->SetBinContent(6,0.04847549);
+   h_ep_mc->SetBinContent(7,0.03635662);
+   h_ep_mc->SetBinContent(8,0.01211887);
+   h_ep_mc->SetBinContent(9,0.06059437);
+   h_ep_mc->SetBinContent(10,0.193902);
+   h_ep_mc->SetBinContent(11,0.4362794);
+   h_ep_mc->SetBinContent(12,0.7271324);
+   h_ep_mc->SetBinContent(13,1.551216);
+   h_ep_mc->SetBinContent(14,3.114551);
+   h_ep_mc->SetBinContent(15,4.871787);
+   h_ep_mc->SetBinContent(16,7.901505);
+   h_ep_mc->SetBinContent(17,10.13138);
+   h_ep_mc->SetBinContent(18,10.87063);
+   h_ep_mc->SetBinContent(19,9.695099);
+   h_ep_mc->SetBinContent(20,6.616905);
+   h_ep_mc->SetBinContent(21,2.726747);
+   h_ep_mc->SetBinContent(22,1.102818);
+   h_ep_mc->SetBinContent(23,0.2060209);
+   h_ep_mc->SetBinContent(24,0.08483211);
[…]

### 2014-06-23 figures_old/h_trk_top_px_h_trk_top_px_trigsel4hit_pair1351_twotrkfilt-v6-paper.C

@@ -1,0 +1,371 @@
+{
+//=========Macro generated from canvas: c1/c1
+//=========  (Thu Nov  7 21:43:49 2013) by ROOT version5.34/02
+   TCanvas *c1 = new TCanvas("c1", "c1",10,32,600,600);
+   gStyle->SetOptFit(1);
+   gStyle->SetOptTitle(0);
+   c1->Range(-0.6315789,-20.10328,3.315789,113.9186);
+   c1->SetFillColor(0);
+   c1->SetBorderMode(0);
+   c1->SetBorderSize(2);
+   c1->SetTickx(1);
+   c1->SetTicky(1);
+   c1->SetLeftMargin(0.16);
+   c1->SetRightMargin(0.08);
+   c1->SetTopMargin(0.06);
+   c1->SetBottomMargin(0.15);
+   c1->SetFrameBorderMode(0);
+   c1->SetFrameBorderMode(0);
+   
+   TH1F *h_trk_top_px_mc = new TH1F("h_trk_top_px_mc","",50,0,3);
+   h_trk_top_px_mc->SetBinContent(7,2.961603);
+   h_trk_top_px_mc->SetBinContent(8,25.17362);
+   h_trk_top_px_mc->SetBinContent(9,38.50084);
+   h_trk_top_px_mc->SetBinContent(10,45.90484);
+   h_trk_top_px_mc->SetBinContent(11,63.67446);
+   h_trk_top_px_mc->SetBinContent(12,48.86644);
+   h_trk_top_px_mc->SetBinContent(13,81.44408);
+   h_trk_top_px_mc->SetBinContent(14,71.07846);
+   h_trk_top_px_mc->SetBinContent(15,57.75125);
+   h_trk_top_px_mc->SetBinContent(16,56.27045);
+   h_trk_top_px_mc->SetBinContent(17,48.86644);
+   h_trk_top_px_mc->SetBinContent(18,41.46244);
+   h_trk_top_px_mc->SetBinContent(19,35.53923);
+   h_trk_top_px_mc->SetBinContent(20,28.13523);
+   h_trk_top_px_mc->SetBinContent(21,19.25042);
+   h_trk_top_px_mc->SetBinContent(22,32.57763);
+   h_trk_top_px_mc->SetBinContent(23,19.25042);
+   h_trk_top_px_mc->SetBinContent(24,23.69282);
[…]

### 2014-10-23 hps-testrun-nim.tex
Version submitted to arxiv.
1st attempt at reviewers comments from Pelle.

@@
 %% \documentclass[final,3p,times]{elsarticle}
+
  \documentclass[final,3p,times,twocolumn]{elsarticle}
+% \documentclass[review,3p,times,twocolumn,sort&compress]{elsarticle}
+
 %% \documentclass[final,5p,times]{elsarticle}
@@
 
-\journal{Nuclear Physics B}
+\journal{Nuclear Instruments and Methods in Physics Research Section A}
 
@@
 
-The HPS experiment~\cite{HPS_proposal_2010} uses both invariant mass and secondary
-vertex signatures to search for \Aprime{}. It uses  a $\approx 1$~m long silicon tracking and 
-vertexing detector
-inside a dipole magnet to measure charged particle trajectories and a fast electromagnetic calorimeter 
-just downstream of the magnet to provide a trigger and identify electrons. The experiment utilizes very 
-high-rate front-end electronics and runs at high trigger rates (up to 50kHz), exploiting the 100\% duty 
-cycle of the JLab CEBAF accelerator to accumulate the needed statistics.
+The HPS experiment~\cite{HPS_proposal_2010} is preparing for installation in Hall-B at JLab in the Fall 
+of 2014. It searches for electro-produced \Aprime{} in interactions between electrons and nuclei in a thin 
+(0.25\% R.L.) Tungsten target foil. The electrons are supplied by the nearly continuous JLab CEBAF 
+beam with energy between 2.2 and 6.6~GeV. The HPS experiment uses both 
+invariant mass and secondary vertex signatures to search for \Aprime{} decaying into \ee{} pairs. In the 
+interesting mass and coupling range, the decay products are boosted along the beam axis with small 
+opening angles and decay lengths ranging from mm's to tens of cm's requiring HPS to operate tracking 
+detectors down to 15~mrad opening angle only 10~cm behind the target. It employs a $\approx 1$~m long 
+silicon tracking and vertexing detector
+inside a dipole magnet to measure and vertex charged particle trajectories and a fast electromagnetic 
+calorimeter just downstream of the magnet to provide a trigger and identify electrons. To overcome the 
+background occupancy from multiple scattered beam electrons both detectors have excellent timing 
+resolution and the experiment utilizes very high-rate 
+front-end electronics and runs at high trigger rates, exploiting the 499~MHz bunch structure,  100\% duty 
+cycle, of the JLab CEBAF accelerator to accumulate the needed statistics.
 
@@
 apparatus is capable of searching for heavy photons in unexplored regions of parameter space.    
-The key design criteria for HPS and the HPS Test Run are the same:
+Therefore, key design criteria and requirements for HPS and the HPS Test Run apparatus are the same:
 \begin{itemize}
-\item large and uniform acceptance in the forward region close to the beam in order to catch boosted 
-\Aprime{} decay products,
+\item uniform acceptance between 15 and $\approx$70~mrad in the forward region to catch boosted decay products close to the beam, 
 \item beam passage through the apparatus in vacuum, to eliminate direct interactions with the 
@@
 with local doses exceeding 100~Mrad.
-\item high-rate electronics with excellent timing resolution to minimize out of time backgrounds,
+\item high-rate electronics with trigger rates up to 50~kHz and data handling rates of 100~MB/s to permanent storage, 
 \item a flexible, redundant and efficient trigger selecting electron and positron pairs at rates up to 
 50~kHz,
-\item data handling rates of 100~MB/s to permanent storage,
-\item excellent track reconstruction efficiency for electrons and positrons,
-\item good angular and momentum resolution to reconstruct invariant mass precisely,
-\item excellent vertex resolution to discriminate displaced \Aprime{} decays from prompt QED 
-backgrounds,
+\item hit reconstruction efficiency higher than 99\% and average track reconstruction efficiency higher than 98\% for electrons and positrons,
+\item excellent hit time resolution to reject out-of-time background hits in the nearly continuous CEBAF 
+beam; 2~ns for hits on tracks in a 8~ns trigger window, 
+\item momentum and angular resolution better than 4.5\% and 1 to 4~mrad (across the track momentum 
+range in non-bend direction), respectively, to reach \Aprime{} 
+mass resolution of 2.5\% or less across the interesting mass range, 
+\item resolution of distance of closest approach to the beam axis less than 250 (100)~$\mu$m for tracks with 
+0.5 (1.7)~GeV/c momentum to achieve a Gaussian vertex resolution down to 1~mm at high masses to 
+discriminate displaced \Aprime{} decays from prompt QED backgrounds,
 \end{itemize}
@@
 experiment~\cite{HDice} until May 18. The JLab run schedule 
-precluded any dedicated electron beam running, but the HPS Test Run was allowed a short and 
-valuable dedicated photon beam run at the end of scheduled CEBAF running. This final running 
-provided enough data to demonstrate the functionality of the apparatus, document its performance, and
-explore trigger rates, as shown below.
+precluded any dedicated electron beam running, but the HPS Test Run was allowed a short ($\approx$6h) 
+and valuable dedicated photon beam run at the end of scheduled CEBAF running. During this dedicated 
+period, \ee{} pairs, produced in a gold foil upstream of the 
+experiment, where studied. With no dedicated electron beam running no search for \Aprime{} signal was 
+possible but this final running provided enough data to demonstrate the functionality of the 
+apparatus, document its performance, and explore trigger rates, as shown below.
 
 This paper reviews the HPS Test Run apparatus, documenting the performance of the trigger, 
-data acquisition, silicon tracking detector, and the electromagnetic calorimeter at the level required for 
-calculating the physics reach of the HPS experiment.
+data acquisition, silicon tracking and vertex detector, and the electromagnetic calorimeter at, or close 
+to, the level required for calculating the physics reach of the HPS experiment.
 
@@
 \begin{center}
-    \includegraphics[width=0.8\textwidth]{hps_testrun_rendering_2}
+    \includegraphics[width=0.8\textwidth]{hps_testrun_rendering_2.jpg}
 \caption{Rendering of the HPS Test Run apparatus installed on the beam line.
@@
 \hline
-ECal & $15<\theta_{y} < 60$ & 442 & 12  & 1  & $1.33\times1.33$~cm$^2$ & 4  & $\sigma(E)/E \approx 4.5\%$ \\ 
+ECal & $15<\theta_{y} < 60$ & 442 & 12  & 1  & $1.33\times1.33$~cm$^2$ & 4  & $\sigma(E)/E \approx 4.5\%/sqrt{E}$ \\ 
  &  &  &   &  & $1.6\times1.6$~cm$^2$  & (trigger)& Ref.~\cite{clas_ecal,clas_ecal2,clas_thesis}  \\ 
@@
 through the PS pair converter gold foil and later the HPS system.
-The PS pair converter was located $\approx~77$~cm upstream of the first layer of the SVT.
+The PS pair converter was located $\approx$77~cm upstream of the first layer of the SVT.
 
@@
  $1.3\times10^8$/s at photon energies between 0.55 and 5.5 GeV produced by a 30 to 90 nA electron 
- beam. Data was measured for both polarities of the PS dipole magnet.'
+ beam. Data was measured for both polarities of the PS dipole magnet.
 \begin{table}[]
@@
 The design of the SVT is primarily driven by direct physics requirements and constraints from the 
-environment at the interaction region. The \Aprime{} decay products 
-have momenta in the range of 1~GeV$/$c, so multiple scattering dominates mass and vertexing 
-uncertainties for any possible material budget. The SVT must therefore minimize the amount of 
-material in the tracking volume. The signal yield for long-lived \Aprime{} is very small, so 
+environment at the interaction region. 
+The \Aprime{} decay products have momenta in the range of 0.4-2.0~GeV$/$c, so multiple scattering 
+dominates mass and vertexing uncertainties for any possible material budget. The SVT must therefore 
+minimize the amount of material in the tracking volume. 
+The signal yield for long-lived \Aprime{} is very small, so 
 the rejection of prompt vertices must be exceedingly pure, on the order of $10^{-7}$, in order to 
@@
 retracted during periods of uncertain beam conditions or beam tuning.
+
+The mass resolution need to be around 2.5\% across the interesting mass range to discover the \Aprime{} 
+signal on top of the copious QED background in the bump-hunt search. With \Aprime{} decay opening 
+angles between 15-70~mrad this translates into track momentum and angular resolution of 4-5\% and 
+1-4~mrad (across the momentum range in the non-bend plane which dominates the measurement)
+~\cite{HPS_proposal_2010}. With multiple scattering dominating both mass and vertexing uncertainties, spatial hit 
+resolution less than 50~$\mu$m are required in the non-bend plane in the first few layers which dominates 
+the vertexing performance and about twice that in the non-bend plane.
+
+High background occupancies, up to 4~MHz$/$mm$^{2}$ locally,  in the region closest to the beam result 
+from beam electrons undergoing multiple scattering in the target. These background hits are rejected by  
+requiring the time reconstruction of each hit to be better than 2~ns.
 
@@
 readout speed to handle 1~MHz/cm$^{2}$ of electromagnetic background and to be radiation hard. 
-The PbWO$_{4}$ crystal inner 
-calorimeter of the CLAS detector~\cite{clas_ecal,clas_ecal2,clas_thesis}, in operation since 2005 in Hall B, meets 
-all the requirements set by HPS. The modules from this calorimeter have been subsequently 
+While the signal \Aprime{} trigger is largely insensitive to the energy resolution, in order to have the 
+possibility to improve the energy resolution from the SVT measurement  
+$\sigma(E)$/$E$$<$4.5\%/$\sqrt(E)$ is needed.
+
+The PbWO$_{4}$ crystal inner calorimeter of the CLAS detector~\cite{clas_ecal,clas_ecal2,clas_thesis}, in 
+operation since 2005 in Hall B, meets all the requirements set by HPS. The modules from this calorimeter have been subsequently 
 repurposed for HPS.
@@
 
+%The ECal module shown in Figure~\ref{fig:ecal-module} is based on a tapered 160~mm long 
+%PbWO$_{4}$ crystal with a $13.3\times13.3$~mm$^2$ ($16\times16$~mm$^2$) front 
+%(rear) face wrapped in VM2000 multilayer polymer mirror film. 
+%\begin{figure}[]
+%\begin{center}
+%\includegraphics[width=7cm]{ecal-module-schematic.png}
+%\caption{\small A schematic view of an ECal module.
+%\label{fig:ecal-module}}
+%\end{center}
+%\end{figure}
+%The scintillation light, approximately $8$ photoelectrons/MeV, is read out by a 
+%5$\times$5~mm$^2$ Hamamatsu S8664-55 Avalanche Photodiode (APD) with 75\% quantum 
+%efficiency glued to the rear face surface using MeltMount 1.7 thermal plastic adhesive. 
+%The low gain of APDs ($\sim 200$) was compensated with custom-made preamplifier boards, which 
+%provide a factor of $2333$ amplification of the APD signal.
 The ECal module shown in Figure~\ref{fig:ecal-module} is based on a tapered 160~mm long 
@@
 \end{figure}
-The scintillation light, approximately $8$ photoelectrons/MeV, is read out by a 
+The scintillation light yield, approximately $120$ photons/MeV, is read out by a 
 5$\times$5~mm$^2$ Hamamatsu S8664-55 Avalanche Photodiode (APD) with 75\% quantum 
-efficiency glued to the rear face surface using MeltMount 1.7 thermal plastic adhesive. 
-The low gain of APDs ($\sim 200$) was compensated with custom-made preamplifier boards, which 
-provide a factor of $2333$ amplification of the APD signal.
+efficiency glued to the rear face surface using MeltMount 1.7 thermal plastic adhesive. This 
+results in about 8 photoelectrons/MeV which needs to be amplified before fed into the FADC for digitization and 
+processing. The maximum energy deposited in a crystal is expected to be 4.2~GeV which needs to 
+match the input range of the FADC. The relatively low gain of the APD ($\sim$200) was compensated with 
+custom-made preamplifier boards, that provide further amplification to match the 2~V dynamic range of the 
+FADC. With a total noise level of about 10~MeV and a resolution of about 1~ADC/MeV the ADC resolution 
+fulfills the requirements from HPS.
 
@@
 top (bottom) half of the ECal.
-In the HPS Test Run 385 out of 442 modules (87\%) were used in offline reconstruction, 39 modules 
-were disabled or not read out (no FADC channel available, no APD bias voltage or masked out due to 
-excessive noise) and 18 were masked offline due to noise.
 
@@
 The trigger system is designed to select time coincidences of electromagnetic clusters in the 
-top and bottom halves of the ECal. Figure~\ref{fig:hps_trigger_cal} shows a schematic overview 
-of each stage of the system. 
+top and bottom halves of the ECal satisfying loose kinematic selections optimized on \Aprime{} events 
+to further reduce the rate. The trigger system need to be essentially dead time free, handle rates up to 
+50~kHz and importantly supply a trigger time relative to the beam bunches with 8~ns to reduce the 
+background from out-of-time hits in the high occupancy regions of the SVT.  Figure~\ref{fig:hps_trigger_cal} 
+shows a schematic overview of each stage of the system. 
  \begin{figure}[b]
@@
 designed to handle trigger rates above 50~kHz and has a latency set to $\approx 3~\mu$s to match 
-that required by the SVT APV25 ASIC. During the HPS Test Run, for the most part the trigger system 
-required only a single cluster in either the top or bottom ECal halves and was tested to trigger rates 
+that required by the SVT APV25 ASIC.
+
+During the HPS Test Run, for the most part the trigger system 
+required only a single cluster in either the top or bottom ECal halves but was tested to trigger rates 
 above 100~kHz by lowering thresholds.
@@
 \label{sec:svt_daq}
+The purpose of the SVT DAQ is to support the continuous 40~MHz readout and processing of signals from 
+each of the 20 silicon strip sensors of the SVT. The data for each strip channel, six analog samples of the 
+signal, needs to be transferred to the JLab DAQ for those events selected by the trigger at rates 
+up to 50~kHz and with data transfer rates up to 100~MB/s.
+
 The SVT DAQ is based on the Reconfigurable Cluster Element (RCE) and cluster 
@@
 
+While dedicated electron beam was precluded for the HPS Test Run the short dedicated photon beam run 
+allowed the study of some of the key performance parameters for HPS and also explore the expected 
+trigger rates during electron beam running. This section documents the performance and discusses the 
+results implication for HPS.
+
 \subsection{SVT Performance}
@@
 \subsubsection{Cluster and Hit Reconstruction}
+Track reconstruction in the SVT puts stringent requirement on the clustering and hit reconstruction. The 
+multiple scattering in the tracking material dominates the uncertainty in the track parameter estimation and 
+effectively determines the roughly 50~$\mu$m (200~$\mu$m) requirement on the spatial hit resolution in 
+the non-bend (bend) plane.  The high 
+occupancy due to multiple scattered beam electrons in the target close to the beam requires a hit time 
+resolution of 2~ns to efficiently reject out-of-time hits in HPS. Both the hit time, based on a fit to the 
+APV25 ASIC pulse shape, and the spatial position reconstruction rely on having S/N around 25 for the 
+sensors used in HPS.
 
@@
 A noise level between $1.1-1.5\times 10^{3}$ electrons was established through multiple calibration 
-runs giving a signal to noise ratio of $21-25$. Lab-based radioactive source tests were used to 
+runs giving a signal to noise ratio of $21-25$, in line with the requirement for HPS. 
+Lab-based radioactive source tests were used to 
 provide the absolute charge normalization.
@@
 somewhat worse than the approximately 2~ns resolution expected for S/N$=$25 which we attribute to the 
-true pulse shape differing from our idealized fit function which will be improved in the future~\cite{Friedl2007385}. Reducing 
+true pulse shape differing from our idealized fit function which will be improved in the 
+future~\cite{Friedl2007385}. Reducing 
 the APV25 ASIC pulse shaping time to 35~ns will also improve time resolution. 
@@
 here, is relatively constant at approximately 6~$\mu$m for tracks that enter approximately normal to 
-the sensors as in HPS.
+the sensors as in HPS. This resolution is significantly better than the requirement for reaching the mass 
+and vertex resolutions required for HPS.
 
 \subsubsection{Momentum and Vertexing Resolution}
-
-By selecting \ee{} pairs from the triggered events we are able to study basic distributions of pair 
-production kinematics. Pairs of oppositely charged tracks, one in the top and one in the bottom half of 
-the SVT, with momentum larger than 400~MeV were selected. The pair production kinematics are 
-relatively well reproduced as shown in Figure~\ref{fig:pair_kin}.
+Good track reconstruction performance is crucial to HPS. Simulations show that track momentum resolution 
+of 4-5\% is needed to reach the expected \Aprime{} mass resolution. The precise reconstruction of the 
+production vertex to reject prompt QED background requires impact parameter resolutions between 
+100-250~$\mu$m for tracks between 0.5-1.7~GeV/c. These key performance parameters where studied 
+in the HPS Test Run by selecting \ee{} pairs from photon conversions. Pairs of oppositely charged tracks, 
+one in the top and one in the bottom half of the SVT, with momentum larger than 400~MeV/c were selected 
+and basic distributions of pair production kinematics were studied.
+The kinematics are relatively well reproduced as shown in Figure~\ref{fig:pair_kin}.
 
@@
 Having the dominant contribution to the vertex resolution approximately right demonstrates that the 
-resolution in HPS, with a target at 10~cm, will be as calculated.
+Gaussian part of the vertex resolution in HPS, with a target at 10~cm, will be as calculated.
 
@@
 \label{sec:ecal_calibration}
+During the HPS Test Run 385 out of 442 modules (87\%) were used in offline reconstruction, 39 modules 
+were disabled or not read out (no FADC channel available, no APD bias voltage or masked out due to 
+excessive noise) and 18 were masked offline due to noise.
 
@@
 HPS Test Run.
+
+Since the \Aprime{} trigger in HPS is relatively insensitive to the energy resolution this level of performance 
+would be adequate. However, improvements are needed to achieve the expected energy resolution in HPS ($<4.5\%/\sqrt{E}$). The noise and and thresholds need to be closer to 10~MeV the 
+thresholds will  be lowered and a more elaborate calibration technique needs to be employed. In addition the number of 
+working channels needs to be improved by equipping the detector new and complete electronics for each 
+channel.
 
@@
 Performance from each of these subsystems has been shown to be adequate to conduct the full 
-experiment successfully. Studies of multiple Coulomb scattering tails of electrons and positrons from 
+experiment successfully with some identified improvements. Studies of multiple Coulomb scattering tails of electrons and positrons from 
 photon conversions further backs expectations from simulation, giving credence to estimates of the 

### 2014-10-23 hps-testrun-nim.tex
Feedback from Matt.

@@
 opening angles and decay lengths ranging from mm's to tens of cm's requiring HPS to operate tracking 
-detectors down to 15~mrad opening angle only 10~cm behind the target. It employs a $\approx 1$~m long 
+detectors down to 15~mrad opening angle only 10~cm behind the target. HPS employs a $\approx 1$~m long 
 silicon tracking and vertexing detector
-inside a dipole magnet to measure and vertex charged particle trajectories and a fast electromagnetic 
-calorimeter just downstream of the magnet to provide a trigger and identify electrons. To overcome the 
+inside a dipole magnet to measure charged particle trajectories and find the decay vertex position of oppositely 
+charged pairs. A fast electromagnetic calorimeter sits just downstream of the magnet to provide a trigger and 
+identify electrons. To overcome the 
 background occupancy from multiple scattered beam electrons both detectors have excellent timing 
 resolution and the experiment utilizes very high-rate 
-front-end electronics and runs at high trigger rates, exploiting the 499~MHz bunch structure,  100\% duty 
+front-end electronics. HPS is designed to run at  high trigger and data throughput rates in order to exploit the 
+499~MHz bunch structure,  100\% duty 
 cycle, of the JLab CEBAF accelerator to accumulate the needed statistics.
@@
 period, \ee{} pairs, produced in a gold foil upstream of the 
-experiment, where studied. With no dedicated electron beam running no search for \Aprime{} signal was 
-possible but this final running provided enough data to demonstrate the functionality of the 
-apparatus, document its performance, and explore trigger rates, as shown below.
+experiment, where studied. This dedicated running provided valuable data to demonstrate the functionality of 
+the apparatus, document its performance, and explore trigger rates, as shown below.
 
@@
 
-The design of the SVT is primarily driven by direct physics requirements and constraints from the 
+The design of the SVT is primarily driven by physics requirements and constraints from the 
 environment at the interaction region. 
-The \Aprime{} decay products have momenta in the range of 0.4-2.0~GeV$/$c, so multiple scattering 
+The \Aprime{} decay products have momenta in the range of 0.4-2.0~GeV$/$c (from a 2.2~GeV beam), so 
+multiple scattering 
 dominates mass and vertexing uncertainties for any possible material budget. The SVT must therefore 
@@
 
-The mass resolution need to be around 2.5\% across the interesting mass range to discover the \Aprime{} 
-signal on top of the copious QED background in the bump-hunt search. With \Aprime{} decay opening 
-angles between 15-70~mrad this translates into track momentum and angular resolution of 4-5\% and 
-1-4~mrad (across the momentum range in the non-bend plane which dominates the measurement)
-~\cite{HPS_proposal_2010}. With multiple scattering dominating both mass and vertexing uncertainties, spatial hit 
+Good mass resolution is needed across the interesting mass range to discover the \Aprime{} 
+signal on top of the copious QED background in the bump-hunt search. Track momentum and angular 
+resolution of 4-5\% and 1-4~mrad (across the momentum range in the non-bend 
+plane which dominates the measurement), respectively, translates into a 2.5\% mass resolution for \Aprime{} 
+decay opening angles between 15-70~mrad~\cite{HPS_proposal_2010}. With multiple scattering dominating 
+both mass and vertexing uncertainties, spatial hit 
 resolution less than 50~$\mu$m are required in the non-bend plane in the first few layers which dominates 
@@
 readout speed to handle 1~MHz/cm$^{2}$ of electromagnetic background and to be radiation hard. 
-While the signal \Aprime{} trigger is largely insensitive to the energy resolution, in order to have the 
+While the trigger for \Aprime{} events is largely insensitive to the energy resolution, in order to have the 
 possibility to improve the energy resolution from the SVT measurement  
@@
 The trigger system is designed to select time coincidences of electromagnetic clusters in the 
-top and bottom halves of the ECal satisfying loose kinematic selections optimized on \Aprime{} events 
-to further reduce the rate. The trigger system need to be essentially dead time free, handle rates up to 
+top and bottom halves of the ECal satisfying loose kinematic selections optimized on simulated \Aprime{} 
+events to further reduce the rate. The trigger system need to be essentially dead time free, handle rates up to 
 50~kHz and importantly supply a trigger time relative to the beam bunches with 8~ns to reduce the 
@@
 The purpose of the SVT DAQ is to support the continuous 40~MHz readout and processing of signals from 
-each of the 20 silicon strip sensors of the SVT. The data for each strip channel, six analog samples of the 
+each of the 20 silicon strip sensors of the SVT. The data for each strip channel, six samples of the 
 signal, needs to be transferred to the JLab DAQ for those events selected by the trigger at rates 
@@
 runs giving a signal to noise ratio of $21-25$, in line with the requirement for HPS. 
-Lab-based radioactive source tests were used to 
+Radioactive source tests were used to 
 provide the absolute charge normalization.

### 2014-10-23 hps-testrun-nim.tex
Introduction feedback from John.

@@
 \label{introduction}
-The heavy photon (\Aprime{}), aka a ``hidden sector'' or ``dark'' photon, is a massive particle which 
+The heavy photon (\Aprime{}), aka a ``hidden sector'' or ``dark'' photon, is a massive gauge boson which 
 couples weakly to electric charge by mixing with the Standard Model 
@@
 into \ee{} pairs, albeit at rates far below those of QED trident processes. Heavy photons have been 
-suggested by numerous beyond Standard Model theories~\cite{Essig:2013lka}, to explain the 
+suggested by numerous beyond Standard Model theories~\cite{Essig:2013lka} to explain the 
 discrepancy 
@@
 good mass resolution to identify a small mass peak above the copious QED background. At small 
-couplings, the \Aprime{} become long-lived, so detection of a displaced decay vertex can reject the prompt 
+couplings, the \Aprime{} becomes long-lived, so detection of a displaced decay vertex can reject the prompt 
 QED background and boost experimental sensitivity.
 
-The HPS experiment~\cite{HPS_proposal_2010} is preparing for installation in Hall-B at JLab in the Fall 
-of 2014. It searches for electro-produced \Aprime{} in interactions between electrons and nuclei in a thin 
-(0.25\% R.L.) Tungsten target foil. The electrons are supplied by the nearly continuous JLab CEBAF 
-beam with energy between 2.2 and 6.6~GeV. The HPS experiment uses both 
-invariant mass and secondary vertex signatures to search for \Aprime{} decaying into \ee{} pairs. In the 
-interesting mass and coupling range, the decay products are boosted along the beam axis with small 
-opening angles and decay lengths ranging from mm's to tens of cm's requiring HPS to operate tracking 
-detectors down to 15~mrad opening angle only 10~cm behind the target. HPS employs a $\approx 1$~m long 
-silicon tracking and vertexing detector
-inside a dipole magnet to measure charged particle trajectories and find the decay vertex position of oppositely 
-charged pairs. A fast electromagnetic calorimeter sits just downstream of the magnet to provide a trigger and 
-identify electrons. To overcome the 
-background occupancy from multiple scattered beam electrons both detectors have excellent timing 
-resolution and the experiment utilizes very high-rate 
-front-end electronics. HPS is designed to run at  high trigger and data throughput rates in order to exploit the 
-499~MHz bunch structure,  100\% duty 
-cycle, of the JLab CEBAF accelerator to accumulate the needed statistics.
+The HPS experiment~\cite{HPS_proposal_2010} is preparing for installation in Hall-B at JLab in the Fall of 
+2014 and searches for electro-produced A? when 2.2-6.6 GeV electrons from the JLab CEBAF accelerator 
+interact with Tungsten nuclei in a thin (0.25\% R.L.) target foil. The HPS experiment uses both 
+invariant mass and secondary vertex signatures to search for \Aprime{} decays into \ee{} pairs. 
+At CEBAF energies, the \Aprime{} decay products are boosted along the beam axis with small opening angles.
+For couplings $\epsilon << 10^{-3}$,  \Aprime{} decay lengths range from millimeters to tens of centimeters and 
+beyond. Accordingly the tracking detectors cover opening angles down to 15~mrad and are placed just 10~cm 
+downstream of the target.
+
+HPS employs a 90~cm long silicon tracking and vertexing detector located inside a dipole magnet to measure 
+momenta and decay vertex positions. A fast PbWO$_{4}$ electromagnetic calorimeter downstream of the 
+magnet provides the trigger and electron identification. Both the silicon tracker and the ECal have $\sim$ns 
+timing resolution, which eliminates much of the out-of-time background from multiple scattered beam electrons.  
+Fast front end electronics and high trigger and data rate capability and the effectively 100\% duty cycle of the 
+CEBAF accelerator allow HPS to accumulate the very large statistics needed to be sensitive to the highly 
+suppressed production of heavy photons.
 
@@
 \begin{itemize}
-\item uniform acceptance between 15 and $\approx$70~mrad in the forward region to catch boosted decay products close to the beam, 
+\item uniform acceptance between 15 and approximately 70~mrad in the forward region to catch boosted decay products close to the beam, 
 \item beam passage through the apparatus in vacuum, to eliminate direct interactions with the 
@@
 \item detector components that can survive and efficiently operate in a high radiation environment 
-with local doses exceeding 100~Mrad.
-\item high-rate electronics with trigger rates up to 50~kHz and data handling rates of 100~MB/s to permanent storage, 
-\item a flexible, redundant and efficient trigger selecting electron and positron pairs at rates up to 
-50~kHz,
+with some localized doses at the 100~Mrad level,
+\item high-rate electronics, handling trigger rates up to 50 klHz and data rates of 100 MB/s to permanent 
+storage, 
+\item a flexible, redundant and efficient trigger for selecting electron and positron pairs,
+capable of handling rates up to 50 kHz,
 \item hit reconstruction efficiency higher than 99\% and average track reconstruction efficiency higher than 98\% for electrons and positrons,
-\item excellent hit time resolution to reject out-of-time background hits in the nearly continuous CEBAF 
-beam; 2~ns for hits on tracks in a 8~ns trigger window, 
-\item momentum and angular resolution better than 4.5\% and 1 to 4~mrad (across the track momentum 
-range in non-bend direction), respectively, to reach \Aprime{} 
-mass resolution of 2.5\% or less across the interesting mass range, 
+\item 2~ns hit time resolution in the silicon vertex tracker, 
+\item A' mass resolution of 2.5\% or better, which translates to momentum resolution of 4.5\% and angular 
+resolution 2~mrad/$p$(GeV/c)) for $B$$=$0.5~T,
 \item resolution of distance of closest approach to the beam axis less than 250 (100)~$\mu$m for tracks with 
-0.5 (1.7)~GeV/c momentum to achieve a Gaussian vertex resolution down to 1~mm at high masses to 
-discriminate displaced \Aprime{} decays from prompt QED backgrounds,
+0.5 (1.7)~GeV/c. This gives a decay length resolution of about 1~mm for a 100~MeV/c$^2$ \Aprime{}.
+\item PbWO$_{4}$ electromagnetic calorimeter energy resolution $\Delta E/E$$\leq$$5\%$/$\sqrt{E}$ and transverse
+segmentation $\sim$1.5~cm (Moliere radius in PbWO$_{4}$).  The energy resolution for triggering is less 
+stringent ($\Delta E/E$$\leq$$10\%$/$\sqrt{E}$) because the electrons and positrons of interest are relatively hard. 
+The good segmentation provides good spatial resolution and guarantees minimal shower overlap with background hits.
 \end{itemize}
@@
 experiment~\cite{HDice} until May 18. The JLab run schedule 
-precluded any dedicated electron beam running, but the HPS Test Run was allowed a short ($\approx$6h) 
-and valuable dedicated photon beam run at the end of scheduled CEBAF running. During this dedicated 
-period, \ee{} pairs, produced in a gold foil upstream of the 
-experiment, where studied. This dedicated running provided valuable data to demonstrate the functionality of 
-the apparatus, document its performance, and explore trigger rates, as shown below.
+precluded any dedicated electron beam running, but the HPS Test Run was allowed an 8h dedicated photon beam run at the end of scheduled CEBAF running. During this dedicated 
+period, \ee{} pairs, produced in a gold foil upstream of the experiment, were studied. With no dedicated 
+electron beam running, it was not possible to search for an A'. However, the final running
+provided enough data to demonstrate the functionality of the apparatus, document its performance, and 
+explore trigger rates, as shown below.
 
@@
 data acquisition, silicon tracking and vertex detector, and the electromagnetic calorimeter at, or close 
-to, the level required for calculating the physics reach of the HPS experiment.
+to, the level required for the HPS experiment.
 

### 2014-10-23 hps-testrun-nim.tex
Feedback from John.

@@
 segmentation $\sim$1.5~cm (Moliere radius in PbWO$_{4}$).  The energy resolution for triggering is less 
-stringent ($\Delta E/E$$\leq$$10\%$/$\sqrt{E}$) because the electrons and positrons of interest are relatively hard. 
+stringent because the electrons and positrons of interest are relatively hard. 
 The good segmentation provides good spatial resolution and guarantees minimal shower overlap with background hits.
@@
 The electomagnetic calorimeter (ECal) is also split into two halves. Each half of the ECal consists of 
-221 PbWO$_4$ crystals arranged in rectangular formation. There are five rows with 46 modules in 
+221 PbWO$_4$ crystals arranged in rectangular formation. There are five rows with 46 crystals in 
 each row except the row closest to the beam plane which has 37. The light from each crystal 
@@
 
-Good mass resolution is needed across the interesting mass range to discover the \Aprime{} 
-signal on top of the copious QED background in the bump-hunt search. Track momentum and angular 
-resolution of 4-5\% and 1-4~mrad (across the momentum range in the non-bend 
-plane which dominates the measurement), respectively, translates into a 2.5\% mass resolution for \Aprime{} 
-decay opening angles between 15-70~mrad~\cite{HPS_proposal_2010}. With multiple scattering dominating 
-both mass and vertexing uncertainties, spatial hit 
-resolution less than 50~$\mu$m are required in the non-bend plane in the first few layers which dominates 
-the vertexing performance and about twice that in the non-bend plane.
+A mass resolution of 2.5\% is adequate to extend a bump-hunt search for an \Aprime{} into virgin territory. 
+For running at 2.2~GeV, this translates into a requirement for track momentum ($p$) resolution of 4-5\% and 
+angular resolution of 2~mrad/$p$(GeV/c)~\cite{HPS_proposal_2010}. 
+Multiple coulomb scattering dominates both the mass and vertexing uncertainties, relaxing 
+the spatial hit resolution requirement to $<100~\mu$m (50~$\mu$m) in the bend (non-bend) plane.
 
@@
 The technology and design choices are largely driven by the need for a compact forward design 
-covering the SVT \Aprime{} acceptance and able to fully absorb 
-electrons and positrons with energy between $0.5$-$6.5$~GeV. It needs granularity and signal 
-readout speed to handle 1~MHz/cm$^{2}$ of electromagnetic background and to be radiation hard. 
-While the trigger for \Aprime{} events is largely insensitive to the energy resolution, in order to have the 
-possibility to improve the energy resolution from the SVT measurement  
-$\sigma(E)$/$E$$<$4.5\%/$\sqrt(E)$ is needed.
+covering the SVT \Aprime{} 
+acceptance and able to measure the energy and positions of electrons and positrons with energy between
+$0.5$-$6.5$~GeV. It needs granularity and signal 
+readout speed to handle 1~MHz/cm$^{2}$ of electromagnetic background and radiation hardness. 
+Even modest energy resolution ($\sim$10-20\%/$\sqrt{E}$) is adequate for triggering. HPS requires better 
+energy resolution, $\sigma(E)$/$E$$<$5\%/$\sqrt{E}$, so that the ECal energy measurement can be used in 
+combination with that from the SVT to improve the overall momentum resolution.
 
@@
 efficiency glued to the rear face surface using MeltMount 1.7 thermal plastic adhesive. This 
-results in about 8 photoelectrons/MeV which needs to be amplified before fed into the FADC for digitization and 
+results in about eight photoelectrons/MeV which needs to be amplified before being fed into the FADC for digitization and 
 processing. The maximum energy deposited in a crystal is expected to be 4.2~GeV which needs to 
@@
 custom-made preamplifier boards, that provide further amplification to match the 2~V dynamic range of the 
-FADC. With a total noise level of about 10~MeV and a resolution of about 1~ADC/MeV the ADC resolution 
-fulfills the requirements from HPS.
+FADC. With a total noise level of about 10~MeV and a resolution of about 1~ADC count/MeV the ADC 
+resolution fulfills the requirements from HPS.
 
@@
 When a trigger is received, the part 
-of the pipeline from 5 samples before and 30 after the signal which crossed a programmable 
+of the pipeline from five samples before and 30 after the signal which crossed a programmable 
 threshold (for the HPS Test Run this was set to $\approx70$~MeV) are 
@@
 \label{sec:trigger}
-The trigger system is designed to select time coincidences of electromagnetic clusters in the 
-top and bottom halves of the ECal satisfying loose kinematic selections optimized on simulated \Aprime{} 
-events to further reduce the rate. The trigger system need to be essentially dead time free, handle rates up to 
-50~kHz and importantly supply a trigger time relative to the beam bunches with 8~ns to reduce the 
-background from out-of-time hits in the high occupancy regions of the SVT.  Figure~\ref{fig:hps_trigger_cal} 
-shows a schematic overview of each stage of the system. 
+The trigger system is designed to select time coincidences of electromagnetic clusters in the top and bottom 
+halves of the ECal which satisfy kinematic conditions satisfied by \Aprime{} decays and minimize backgrounds.
+The trigger system needs to be essentially dead-time free, handle rates up to 50~kHz, and supply a trigger 
+signal within 8~ns of the actual event time in order to minimize backgrounds from out-of-time hits in the SVT. 
+Figure~\ref{fig:hps_trigger_cal} shows a schematic overview of each stage of the system. 
  \begin{figure}[b]
@@
 While dedicated electron beam was precluded for the HPS Test Run the short dedicated photon beam run 
-allowed the study of some of the key performance parameters for HPS and also explore the expected 
-trigger rates during electron beam running. This section documents the performance and discusses the 
-results implication for HPS.
+allowed the study of some of the key performance parameters for HPS and the trigger rates expected during 
+electron beam running. This section documents the performance and discusses the implications of these 
+results for HPS.
 
@@
 
-After a trigger is received, the amplitude of every APV25 analogue output is sampled and digitized in 
-six consecutive time bins, separated by roughly 25~ns.  A data reduction algorithm is applied 
+After a trigger is received, the amplitude of every APV25 is sampled and digitized in the six consecutive time 
+bins associated with the trigger time. A data reduction algorithm is applied 
 requiring three out of six samples to be above two times the noise level and that the third sample is 
@@
 Good track reconstruction performance is crucial to HPS. Simulations show that track momentum resolution 
-of 4-5\% is needed to reach the expected \Aprime{} mass resolution. The precise reconstruction of the 
+of 4-5\% is needed to achieve the desired \Aprime{} mass resolution. The precise reconstruction of the 
 production vertex to reject prompt QED background requires impact parameter resolutions between 
@@
 The expected momentum resolution from simulation is between 4-5\% for tracks in the momentum 
-range of the HPS Test Run. By comparing, between data and simulation, the shapes of the kinematic 
-distributions for single- and two-track events, we estimate an agreement with the nominal scale and 
-resolution to within 10\%.
+range of the HPS Test Run. By comparing the shapes of the kinematic distributions for data and simulation, we 
+estimate an agreement with the nominal scale and resolution to within 10\%.
  \begin{center}
@@
 tracking and vertexing is multiple Coulomb scattering. For the vertexing performance the foremost 
-difference compared to electron beam running is that the target was located approximately 67~cm 
-upstream from our nominal target position; giving almost collinear tracks in the detector. The increased 
+difference between the HPS Test Run and HPS is that the HPS Test Run target is 67~cm further upstream, 
+so tracks must be extrapolated nearly eight times as far as in HPS; giving almost collinear tracks in the 
+detector. The increased 
 lever arm over which tracks are extrapolated widens the resolution with up to a factor of eight 
@@
 deployed for the trigger (see Sec.~\ref{sec:trigger}). Due to the high effective crystal readout threshold 
-of 73~MeV the average number of crystals in a cluster was $\sim 3$ and the simple clustering 
+of 73~MeV the average number of crystals in a cluster was only about three and the simple clustering 
 algorithm worked well for reconstruction of the detected shower energy. An average noise level of 
@@
 \end{figure}
-The peak position of the distribution indicates the sampling fraction of the ECal, the fraction of the 
-incident particle energy measured in the cluster. The width and tails of the distribution 
-in data indicates imperfect calibration and noise of the ECal modules. This level of calibration and the 
-agreement with simulation was found to be sufficient to study normalized event rates in the 
-HPS Test Run.
+The peak of the distribution, at $E$/$p$~0.7, gives the sampling fraction of the ECal, the fraction of the 
+incident particle energy measured in the cluster. The width of the distribution in data is greater than that in 
+simulation, indicating that the measured energy resolution is worse than the 5\%/$\sqrt{E}$  assumed in the 
+simulation. Even so, the measured energy resolution was found to be adequate for studies of the trigger rates, 
+which don't depend sensitively on the low energy threshold. The good agreement between data and 
+simulation for the track momentum cutoff at low values of momentum in Figure~\ref{fig:pair_kin} confirms this.
 
 Since the \Aprime{} trigger in HPS is relatively insensitive to the energy resolution this level of performance 
-would be adequate. However, improvements are needed to achieve the expected energy resolution in HPS ($<4.5\%/\sqrt{E}$). The noise and and thresholds need to be closer to 10~MeV the 
-thresholds will  be lowered and a more elaborate calibration technique needs to be employed. In addition the number of 
-working channels needs to be improved by equipping the detector new and complete electronics for each 
-channel.
+would be adequate. However, improvements are needed to achieve the expected energy resolution in HPS 
+($<4.5\%/\sqrt{E}$). The noise and and thresholds need to be closer to 10~MeV and a more elaborate 
+calibration technique needs to be employed to suppress the large tails in the $E$/$p$ distribution further. 
+In addition, the fraction of working channels needs significant improvement.
 

### 2014-10-23 hps-testrun-nim.tex
Edits from John and Sho.

@@
 apparatus and readout electronics and its performance. In this setting, a heavy photon can be identified 
-as a narrow peak in the \ee{} invariant mass spectrum, above the trident background or as a narrow  
+as a narrow peak in the \ee{} invariant mass spectrum above the trident background or as a narrow  
 invariant mass peak with a decay vertex displaced from the production target, so charged particle 
@@
 %%
-\linenumbers
+%\linenumbers
 
@@
 The HPS experiment~\cite{HPS_proposal_2010} is preparing for installation in Hall-B at JLab in the Fall of 
-2014 and searches for electro-produced A? when 2.2-6.6 GeV electrons from the JLab CEBAF accelerator 
-interact with Tungsten nuclei in a thin (0.25\% R.L.) target foil. The HPS experiment uses both 
+2014 to search for heavy photons by directing the 2.2-6.6~GeV CEBAF12 electron beam onto a thin 
+(0.25\% $X_{0}$) Tungsten target foil. The HPS experiment uses both 
 invariant mass and secondary vertex signatures to search for \Aprime{} decays into \ee{} pairs. 
@@
 Fast front end electronics and high trigger and data rate capability and the effectively 100\% duty cycle of the 
-CEBAF accelerator allow HPS to accumulate the very large statistics needed to be sensitive to the highly 
+CEBAF accelerator allows HPS to accumulate the very large statistics needed to be sensitive to the highly 
 suppressed production of heavy photons.
@@
 with some localized doses at the 100~Mrad level,
-\item high-rate electronics, handling trigger rates up to 50 klHz and data rates of 100 MB/s to permanent 
+\item high-rate electronics, handling trigger rates up to 50~kHz and data rates of 100~MB/s to permanent 
 storage, 
 \item a flexible, redundant and efficient trigger for selecting electron and positron pairs,
-capable of handling rates up to 50 kHz,
+capable of handling rates up to 50~kHz,
 \item hit reconstruction efficiency higher than 99\% and average track reconstruction efficiency higher than 98\% for electrons and positrons,
@@
 experiment~\cite{HDice} until May 18. The JLab run schedule 
-precluded any dedicated electron beam running, but the HPS Test Run was allowed an 8h dedicated photon beam run at the end of scheduled CEBAF running. During this dedicated 
+precluded any dedicated electron beam running, but the HPS Test Run was allowed an eight hour 
+dedicated photon beam run at the end of scheduled CEBAF running. During this dedicated 
 period, \ee{} pairs, produced in a gold foil upstream of the experiment, were studied. With no dedicated 
@@
 dominated by five 
-APV25 ASICs on each hybrid board consuming approximately 2~W, radiant heat load is less than 
+APV25 ASICs on each hybrid board consuming approximately 2~W, the radiant heat load is less than 
 0.5~W per sensor and leakage current is only significant in a small spot after irradiation.
@@
 essential functions for the experiment: it provides a trigger signal to select what events to read out from 
-the detector sub-systems and is used in the analysis to identify electrons and positrons. 
+the detector sub-systems and is used to identify electrons and positrons. 
 The technology and design choices are largely driven by the need for a compact forward design 
@@
 readout speed to handle 1~MHz/cm$^{2}$ of electromagnetic background and radiation hardness. 
-Even modest energy resolution ($\sim$10-20\%/$\sqrt{E}$) is adequate for triggering. HPS requires better 
+Even modest energy resolution is adequate for triggering. HPS requires better 
 energy resolution, $\sigma(E)$/$E$$<$5\%/$\sqrt{E}$, so that the ECal energy measurement can be used in 
@@
 The trigger system needs to be essentially dead-time free, handle rates up to 50~kHz, and supply a trigger 
-signal within 8~ns of the actual event time in order to minimize backgrounds from out-of-time hits in the SVT. 
+signal which jitters $<8$~ns from the actual event time in order to minimize backgrounds from out-of-time hits in the SVT. 
 Figure~\ref{fig:hps_trigger_cal} shows a schematic overview of each stage of the system. 
@@
 approximately 1~m from the beam line, next to our cable vacuum feed-throughs.   
-Before shielding with lead-blankets was arranged, we observed two failures of normally reliable ATCA 
+Before shielding with lead-blankets and borated polyethylene was arranged, we observed two failures of normally reliable ATCA 
 crate power supplies, time-correlated to beam instabilities.
@@
 dead or noisy channels. The hit reconstruction efficiency was estimated by measuring 
-the number of good tracks with a hit close to the extrapolated intersection of a given sensor that was 
-excluded from the track fit itself. Tracks which intersect regions with known bad channels or pass very 
+the number of good tracks with a hit close to the interpolated position on a given sensor that was excluded 
+from the track fit. Tracks which intersect regions with known bad channels or pass very 
 close to the edge region were excluded. The hit reconstruction efficiency, see Figure~\ref{fig:hit_efficiency}, 
@@
 difference between the HPS Test Run and HPS is that the HPS Test Run target is 67~cm further upstream, 
-so tracks must be extrapolated nearly eight times as far as in HPS; giving almost collinear tracks in the 
+so tracks must be extrapolated nearly eight times as far as in HPS, giving almost collinear tracks in the 
 detector. The increased 
-lever arm over which tracks are extrapolated widens the resolution with up to a factor of eight 
+lever arm over which tracks are extrapolated worsens the resolution up to a factor of eight 
 (depending on momentum) compared to what is achieved at the nominal electron target position for 
@@
 \end{figure}
-The peak of the distribution, at $E$/$p$~0.7, gives the sampling fraction of the ECal, the fraction of the 
-incident particle energy measured in the cluster. The width of the distribution in data is greater than that in 
-simulation, indicating that the measured energy resolution is worse than the 5\%/$\sqrt{E}$  assumed in the 
-simulation. Even so, the measured energy resolution was found to be adequate for studies of the trigger rates, 
-which don't depend sensitively on the low energy threshold. The good agreement between data and 
-simulation for the track momentum cutoff at low values of momentum in Figure~\ref{fig:pair_kin} confirms this.
-
-Since the \Aprime{} trigger in HPS is relatively insensitive to the energy resolution this level of performance 
-would be adequate. However, improvements are needed to achieve the expected energy resolution in HPS 
-($<4.5\%/\sqrt{E}$). The noise and and thresholds need to be closer to 10~MeV and a more elaborate 
-calibration technique needs to be employed to suppress the large tails in the $E$/$p$ distribution further. 
-In addition, the fraction of working channels needs significant improvement.
+The peak of the distribution, at $E/p\sim0.7$, gives the sampling fraction of the ECal, the fraction of the 
+incident particle energy measured in the cluster. The width of the distribution indicates the energy 
+resolution, which is worse than the required 4.5\%/$\sqrt{E}$ for HPS due to high thresholds. 
+The width in data is greater than that in simulation due to non-uniformity of the calibration of different parts 
+of the ECal.
+
+The \Aprime{} trigger in HPS is relatively insensitive to the energy of the clusters and this level of 
+performance would be adequate. However, improvements are needed to achieve the expected energy 
+resolution in HPS ($<4.5\%/\sqrt{E}$). The noise and and thresholds need to be closer to 10~MeV and a 
+more elaborate calibration technique needs to be employed to suppress the large tails in the $E$/$p$ 
+distribution further. In addition, the fraction of working channels needs significant improvement.
 
 \subsection{Trigger Performance}
-As described above in Sec.~\ref{sec:triggerdaq}, the energy from each 
-crystal is measured differently in the trigger and what is readout from the ECal. 
-The trigger performance was studied by simulating the 
+As described above in Sec.~\ref{sec:triggerdaq}, the energy from each crystal is determined slightly 
+differently in the trigger and in the readout. The trigger performance was studied by simulating the 
 trigger for each event and comparing to how the events were actually triggered.
@@
 multiple crystals. The effective trigger threshold is therefore dependent on position and energy of 
-the particle as well as cluster multiplicity.
+the particle as well as cluster multiplicity. For HPS the trigger cluster threshold will be set at a lower 
+value.
 
@@
 \subsection{Trigger Rate Comparisons}
-Trigger rates observed in the HPS Test Run are dominated by multiple Coulomb scattered \ee{} pairs in the 
+Trigger rates observed in the HPS Test Run are dominated by \ee{} pairs produced in the 
 converter. In simulated events, the rate of triggers depend on the modeling of the pairs' angular 

### 2014-10-24 author_list_hps_PAC39_compact_alphabetical_order.tex
Fixed order of Valery and Alex.
Fixed UCSC name in author list
Added Andrea and Gabriel to author list
Fixing Orsay name based on Raphaels input.

@@
 \newcommand{\SACLAY}{CEA, Centre de Saclay, Irfu/Service de Physique Nucl\'eaire 91191 Gif-sur-Yvette, France}
-\newcommand{\ORSAY}{Institut de Physique Nucleaire d'Orsay, IN2P3, BP 1, 91406 Orsay, France}
+\newcommand{\ORSAY}{Institut de Physique Nucl\'eaire, CNRS/IN2P3 and Universit\'e Paris Sud, Orsay, France}
 \newcommand{\ECOLE}{CPhT, Ecole Polytechnique, F 91128 PALAISEAU CEDEX, France}
-\newcommand{\UCSC}{University of California, Santa Cruz, CA 95064}
+\newcommand{\UCSC}{Santa Cruz Institute for Particle Physics, University of California, Santa Cruz, CA 95064}
 \newcommand{\SUNY}{Stony Brook University, Stony Brook, NY 11794-3800}
@@
 \author[JLAB]{ V. Burkert} 
+\author[GENOVA]{A. Celentano} 
+\author[ORSAY]{ G. Charles}
 \author[FNAL]{W. Cooper}
@@
 \author[NSU]{M. Khandaker} 
+\author[RPI]{A. Kubarovsky}
 \author[JLAB]{ V. Kubarovsky} 
-\author[RPI]{A. Kubarovsky}
 \author[SLAC]{T. Maruyama} 

### 2014-10-24 hps-testrun-nim.tex
Updates to ECal section based on comments from John.

@@
 algorithm simultaneously searches for up to 125 clusters with energy sum larger than 
-the programmable energy threshold ($\approx270$~MeV). Crystals in the 
+the programmable energy threshold set to about 270~MeV. This high threshold didn't hurt the trigger rate 
+rate studies for the HPS Test run since only clusters with high energies were studied but for HPS this 
+threshold will need to be lower.  Crystals in the 
 fixed-window are included in the sum if the leading edge of the pulse occurred within a 32~ns time 
@@
 algorithm worked well for reconstruction of the detected shower energy. An average noise level of 
-approximately 15~MeV per crystal was measured in special pedestal runs.
+approximately 15~MeV per crystal was measured in special pedestal runs. The high crystal noise level 
+and effective threshold didn't hurt the trigger rate studies in the HPS Test Run 
+as clusters with high energy were used for the analysis. For HPS the noise level and threshold will be 
+lowered to improve energy resolution and to allow triggering on cosmics to improve calibration.
 
@@
 %\end{center}
-Restricting clusters to a well calibrated region of the ECal and subtracting the ``no converter'' 
-background we see agreement with the rates predicted by the \egs{} simulation 
-program, 
-see Table~\ref{results}.
+Restricting to a well calibrated region of the ECal and to clusters with energy above the trigger turn-on, 
+we see agreement with the rates predicted by the \egs{} simulation program after subtracting the 
+``no converter'' background , see Table~\ref{results}.
 This gives further confidence that the dominant source of background occupancy for HPS, multiple 

### 2014-10-24 hps-testrun-nim.tex
More comments from John.

@@
 beam line and split top-bottom. This arrangement provides sensitivity to low-mass heavy photons,  
-allows clear  passage of the unscattered beam, 
+allow clear  passage of the unscattered beam, 
 and avoids the spray of degraded electrons coming from the target. 
@@
 
-% \linenumbers
+ \linenumbers
 
@@
 \item PbWO$_{4}$ electromagnetic calorimeter energy resolution $\Delta E/E$$\leq$$5\%$/$\sqrt{E}$ and transverse
-segmentation $\sim$1.5~cm (Moliere radius in PbWO$_{4}$).  The energy resolution for triggering is less 
-stringent because the electrons and positrons of interest are relatively hard. 
-The good segmentation provides good spatial resolution and guarantees minimal shower overlap with background hits.
+segmentation $\sim$1.5~cm ($<$ Moliere radius in PbWO$_{4}$).  The energy resolution requirement for
+triggering is less stringent because the electrons and positrons have $E > 0.5$~GeV. The segmentation provides good spatial resolution and guarantees minimal shower overlap with background hits.
 \end{itemize}
@@
 custom-made preamplifier boards, that provide further amplification to match the 2~V dynamic range of the 
-FADC. With a total noise level of about 10~MeV and a resolution of about 1~ADC count/MeV the ADC 
-resolution fulfills the requirements from HPS.
+FADC. The ADC has 12-bit resolution. Gains are adjusted to give about 1~ADC count/MeV.
+This dynamic range is adequate to measure the 10~MeV noise level as well as the 
+the maximum energy expected in a single crystal, about 4~GeV.
 

### 2014-10-24 hps-testrun-nim.tex
Pelles proof reading.

@@
 Current phenomenology highlights the $20-1000$~MeV/c$^{2}$ mass range, and 
-suggests that  the coupling to electric charge, $\epsilon$e, has $\epsilon$ in the range of 
+suggests that  the coupling to electric charge, $\epsilon e$, has $\epsilon$ in the range of 
 $10^{-3} -10^{-5}$. This range of parameters makes \Aprime{} searches viable in 
@@
 \item A' mass resolution of 2.5\% or better, which translates to momentum resolution of 4.5\% and angular 
-resolution 2~mrad/$p$(GeV/c)) for $B$$=$0.5~T,
+resolution of 2~mrad/$p$(GeV/c)) for $B$$=$0.5~T,
 \item resolution of distance of closest approach to the beam axis less than 250 (100)~$\mu$m for tracks with 
@@
 }
-The HPS Test Run apparatus was designed to run in Hall~B at JLab using the CEBAF 499MHz 
+The HPS Test Run apparatus was designed to run in Hall~B at JLab using the CEBAF 499~MHz 
 electron beam at energies between 2.2 and 6.6~GeV and currents between 200 and 600~nA.  
@@
 \caption{Overview of the coverage, segmentation and performance of the HPS Test Run detector.
-The $\sigma_{d_0}$ is the track impact parameter resolution of the SVT at the nominal electron target position.
+The $\sigma_{d_0}$ is the track impact parameter resolution of the SVT at the nominal oron target position.
 $\sigma_{pos}$ is the estimated position resolution perpendicular to the strip direction on the silicon sensors of the SVT.
@@
 
-The electomagnetic calorimeter (ECal) is also split into two halves. Each half of the ECal consists of 
+The electromagnetic calorimeter (ECal) is also split into two halves. Each half of the ECal consists of 
 221 PbWO$_4$ crystals arranged in rectangular formation. There are five rows with 46 crystals in 
@@
 produced by interactions of the secondary photon beam with a thin foil just upstream of the detectors.  
-The HPS Test Run studied the performance of the detectors and the multiple coulomb scattering of the 
+The HPS Test Run studied the performance of the detectors and the multiple Coulomb scattering of the 
 electrons and positrons. Figure~\ref{fig:hpstest_layout} shows the layout of 
@@
 through the PS pair converter gold foil and later the HPS system.
-The PS pair converter was located $\approx$77~cm upstream of the first layer of the SVT.
-
- Data was taken on three different converter thicknesses with photon fluxes between 0.4 and 
- $1.3\times10^8$/s at photon energies between 0.55 and 5.5 GeV produced by a 30 to 90 nA electron 
+The PS pair converter was located $\approx 77$~cm upstream of the first layer of the SVT.
+
+ Data was taken on three different converter thicknesses with photon fluxes between $0.4$-$1.3\times10^8$/s at photon energies between 0.55 and 5.5 GeV produced by a 30-90 nA electron 
  beam. Data was measured for both polarities of the PS dipole magnet.
@@
 environment at the interaction region. 
-The \Aprime{} decay products have momenta in the range of 0.4-2.0~GeV$/$c (from a 2.2~GeV beam), so 
+The \Aprime{} decay products have momenta in the range of 0.4-2.0~GeV$/$c (for a 2.2~GeV beam), so 
 multiple scattering 
@@
 For running at 2.2~GeV, this translates into a requirement for track momentum ($p$) resolution of 4-5\% and 
-angular resolution of 2~mrad/$p$(GeV/c)~\cite{HPS_proposal_2010}. 
-Multiple coulomb scattering dominates both the mass and vertexing uncertainties, relaxing 
+angular resolution of about 2~mrad/$p$(GeV/c)~\cite{HPS_proposal_2010}. 
+Multiple Coulomb scattering dominates both the mass and vertexing uncertainties, relaxing 
 the spatial hit resolution requirement to $<100~\mu$m (50~$\mu$m) in the bend (non-bend) plane.
@@
 The layout of the SVT is summarized in Table~\ref{tab:trk} and rendered in Figure~\ref{fig:tracker_model}. 
-Each of the layers is comprised of a pair of closely-spaced silicon microstrip sensors mounted back-
-to-back to form a module. A 100~mrad stereo angle is used in the first three layers to provide higher-
-resolution 3D space points for vertexing.  Using 50~mrad in the last two layers breaks the tracking 
+Each of the layers is comprised of a pair of closely-spaced silicon microstrip sensors mounted 
+back-to-back to form a module. A 100~mrad stereo angle is used in the first three layers to provide 
+higher-resolution 3D space points for vertexing.  Using 50~mrad in the last two layers breaks the tracking 
 degeneracy of having five identical layers and minimizes fakes from ghost hits to improve pattern 
@@
 performance the sensors for the SVT are readout by the APV25 ASIC developed for the CMS 
-experiment at CERN~\cite{French:2001xb}. The APV25 can capture successive samples of the shaper output 
+experiment at CERN~\cite{French:2001xb}. The APV25 ASIC can capture successive samples of the shaper output 
 in groups of three at a sampling rate of approximately 40~MHz.  By fitting the known 
@@
 up a half-module. A window is machined in the carbon fiber leaving only a frame around the periphery 
-of the silicon to minimize material. A 50~$\mu$m sheet of polyamide is laminated to the surface of the 
+of the silicon to minimize material. A 50~$\mu$m sheet of polyimide is laminated to the surface of the 
 carbon fiber with 1~mm overhang at all openings to ensure good isolation between the back side of the 
@@
 vibration was built in order to safely send the partly assembled SVT to JLab. At JLab, the entire SVT was 
-integrated with the full DAQ and the power supplies before moving the module-loaded support plates to 
+integrated with the full data acquisition and the power supplies before moving the module-loaded support plates to 
 Hall B for final mechanical assembly and installation inside of the vacuum chamber.
@@
 acceptance and able to measure the energy and positions of electrons and positrons with energy between
-$0.5$-$6.5$~GeV. It needs granularity and signal 
+$0.5$ and $\approx$4~GeV. It needs granularity and signal 
 readout speed to handle 1~MHz/cm$^{2}$ of electromagnetic background and radiation hardness. 
 Even modest energy resolution is adequate for triggering. HPS requires better 
-energy resolution, $\sigma(E)$/$E$$<$5\%/$\sqrt{E}$, so that the ECal energy measurement can be used in 
+energy resolution, $\sigma(E)/E<5\%/\sqrt{E}$, so that the ECal energy measurement can be used in 
 combination with that from the SVT to improve the overall momentum resolution.
@@
 efficiency glued to the rear face surface using MeltMount 1.7 thermal plastic adhesive. This 
-results in about eight photoelectrons/MeV which needs to be amplified before being fed into the FADC for digitization and 
+results in about eight photoelectrons/MeV which needs to be amplified before being fed into the JLab 
+Flash ADC~\cite{fadc} (FADC) board for digitization and 
 processing. The maximum energy deposited in a crystal is expected to be 4.2~GeV which needs to 
@@
 
-\subsection{Signal readout}
+\subsection{Signal Readout}
 \label{sec:fadc}
 After a 2:1 signal splitter, $1/3$ of an amplified APD signal was fed to a 
-single channel of a JLab flash ADC (FADC) board~\cite{fadc}. $2/3$ of the signal was sent to a 
+single channel of a FADC board. $2/3$ of the signal was sent to a 
 discriminator module and then to a TDC for a timing measurement. 
@@
 
-The DAQ system handles acquisition of data from the ECal and SVT sub-detectors  with 
+The data acquisition (DAQ) system handles acquisition of data from the ECal and SVT sub-detectors  with 
 two DAQ architectures. The SVT DAQ is based on Advanced Telecom Communications Architecture 
@@
 
-\subsection{Trigger system}
+\subsection{Trigger System}
 \label{sec:trigger}
 The trigger system is designed to select time coincidences of electromagnetic clusters in the top and bottom 
-halves of the ECal which satisfy kinematic conditions satisfied by \Aprime{} decays and minimize backgrounds.
+halves of the ECal which meets kinematic conditions satisfied by \Aprime{} decays and minimize backgrounds.
 The trigger system needs to be essentially dead-time free, handle rates up to 50~kHz, and supply a trigger 
@@
 very large clusters. The sub-system board (SSP) receives the clusters from the top and bottom half CTP 
-at a maximum of 250MHz and searches for pairs of clusters in an 8~ns wide coincidence window. The 
+at a maximum rate of 250~MHz and searches for pairs of clusters in an 8~ns wide coincidence window. The 
 SSP sends triggers to the trigger supervisor (TS), which generates all the necessary signals and 
@@
 During the HPS Test Run, for the most part the trigger system 
-required only a single cluster in either the top or bottom ECal halves but was tested to trigger rates 
+required only a single cluster in either the top or bottom ECal halves. It was tested to trigger rates 
 above 100~kHz by lowering thresholds.
@@
 Rear-Transition-Module (RTM), a custom board on the back side of the ATCA crate, interfacing the 
-HPS-specific readout to the generic DAQ components on the COB. A pre-amplifier converts the APV25 
+HPS-specific readout to the generic DAQ components on the COB. A preamplifier converts the APV25 ASIC 
 differential current output to a different voltage output scaled to the sensitive range of a 14-bit ADC 
@@
 configured as the trigger and data transmission module. The two COB cards and their DPMs are 
-interconnected with a 10~Gb/s switch card~\cite{Larsen:2011zb} which also hosts two 1Gb/s Ethernet 
+interconnected with a 10~Gb/s switch card~\cite{Larsen:2011zb} which also hosts two 1~Gb/s Ethernet 
 interfaces to the external SVT DAQ PC.
@@
 The external PC supports three network interfaces: two standard 1~Gb/s Ethernet and one custom 
-low-latency data reception card. The first is used for slow control and monitoring of the 8 
+low-latency data reception card. The first is used for slow control and monitoring of the eight 
 DPM modules and the second serves as the interface to the JLAB data acquisition system. The third 
@@
 latency, reliable TTL trigger acknowledge interface to the trigger DPM. This PC hosts the SVT control 
-and monitoring software as well as the Read Out Controller application used to interface with the 
+and monitoring software as well as the readout controller application used to interface with the 
 JLab DAQ.
 
-In order to minimize cable length for the analog APV25 output signal the ATCA crate was located 
+In order to minimize cable length for the analog APV25 ASIC output signal the ATCA crate was located 
 approximately 1~m from the beam line, next to our cable vacuum feed-throughs.   
@@
 Although trigger rates during the HPS Test Run were significantly lower, this system was tested at 
-trigger rates up to 20~kHz and 50~MB/s.  With optimized event blocking and improved ethernet 
-bandwidth, together with utilizing the overlapping readout and trigger functionality of the APV25, the 
+trigger rates up to 20~kHz and 50~MB/s.  With optimized event blocking and improved Ethernet 
+bandwidth, together with utilizing the overlapping readout and trigger functionality of the APV25 ASIC, the 
 system is capable of being read out at 50~kHz trigger rate.
@@
 
-For the duration of the HPS Test Run all SVT modules and APV25 chips were configured to their 
+For the duration of the HPS Test Run all SVT modules and APV25 ASICs were configured to their 
 nominal operating points~\cite{Jones:1069892} with all sensors reverse-biased at 180~V.  The 
@@
 multiple scattering in the tracking material dominates the uncertainty in the track parameter estimation and 
-effectively determines the roughly 50~$\mu$m (200~$\mu$m) requirement on the spatial hit resolution in 
+effectively determines the roughly 50~$\mu$m (100~$\mu$m) requirement on the spatial hit resolution in 
 the non-bend (bend) plane.  The high 
@@
 resolution of 2~ns to efficiently reject out-of-time hits in HPS. Both the hit time, based on a fit to the 
-APV25 ASIC pulse shape, and the spatial position reconstruction rely on having S/N around 25 for the 
+APV25 ASIC pulse shape, and the spatial position reconstruction rely on having $S/N$ around 25 for the 
 sensors used in HPS.
 
-After a trigger is received, the amplitude of every APV25 is sampled and digitized in the six consecutive time 
+After a trigger is received, the amplitude of every APV25 ASIC is sampled and digitized in the six consecutive time 
 bins associated with the trigger time. A data reduction algorithm is applied 
@@
 A noise level between $1.1-1.5\times 10^{3}$ electrons was established through multiple calibration 
-runs giving a signal to noise ratio of $21-25$, in line with the requirement for HPS. 
+runs giving a $S/N$ of $21-25$, in line with the requirement for HPS. 
 Radioactive source tests were used to 
@@
 the APV25 ASIC pulse shaping time to 35~ns will also improve time resolution. 
-These results show that we can operate with the six sample readout mode of the APV25 chip and 
+These results show that we can operate with the six sample readout mode of the APV25 ASIC and 
 achieve time resolution adequate for pileup rejection during electron running in HPS. 
@@
 function of the total signal to single-strip noise and the crossing angle of tracks through the sensor.  
-The single-hit resolution for charged particles with signal-to-noise ratio above 20, as demonstrated 
+The single-hit resolution for charged particles with $S/N>20$, as demonstrated 
 here, is relatively constant at approximately 6~$\mu$m for tracks that enter approximately normal to 
@@
 incident particle energy measured in the cluster. The width of the distribution indicates the energy 
-resolution, which is worse than the required 4.5\%/$\sqrt{E}$ for HPS due to high thresholds. 
+resolution, which is worse than the required $5\%/\sqrt{E}$ for HPS due to high thresholds. 
 The width in data is greater than that in simulation due to non-uniformity of the calibration of different parts 
@@
 performance would be adequate. However, improvements are needed to achieve the expected energy 
-resolution in HPS ($<4.5\%/\sqrt{E}$). The noise and and thresholds need to be closer to 10~MeV and a 
+resolution in HPS. The noise and and thresholds need to be closer to 10~MeV and a 
 more elaborate calibration technique needs to be employed to suppress the large tails in the $E$/$p$ 

### 2014-10-24 reviewer_comments_answers.txt
Answers to 1st round, v5.0, of the paper from NIM.

v5.0
Reviewer #1
The paper is technically correct and well done concerning the presentation of the physics program, the instrumental realization and the first experience. However, the publication should provide at the end not only a report on the work which has been done but also contain results of common interest. In order to be more specific, the introduction does not give exact values for the required resolutions with respect to tracking and timing or in particular the energy resolution of the calorimeter.

ANSWER
The revised version contains some significant changes and improvements and spells out the HPS requirements more clearly in the introduction. We hope this will clarify what the HPS Test Run performance limitations were.

In particular we better specified the requirements of both the SVT and ECal, both in the introduction and also in the sections describing the two detectors and what was driving their design (Sec. 4 and 5). Similarly,  we have better related the Test Run performance and its limitations to both the immediate needs of the Test Run (to demonstrate functionality and measure trigger rates) and the ultimate HPS requirements. For example we include the expected resolution of tracks and clusters in the ECal, but also explain what was adequate for the Test Run trigger and what needs improving for HPS offline reconstruction.

There is also no comment on the expected dynamic range to judge the acievable or achieved energy resolution. In most cases there is only the comment that the performance is sufficient or can be improved.

ANSWER
In the case of the SVT we list the 3 mip dynamic range with linear gain of the APV25 chip (Sec. 7.1.1). We also quote the typical noise and signal levels to get a feeling for the S/N~25. The resolution of the ADC is 14-bits which is discussed in Sec. 6.2.

For the ECal the maximum deposited energy in a single crystal is 4.2GeV with a beam energy of 6.6GeV. The dynamic range was checked for the CLAS IC (which was refurbished for HPS Test Run) and was found to be linear across this range to within 1-2%. The 12-bit resolution of the FADC means that we will get a resolution of about 1ADC/MeV which is enough given that our noise is of the order of 10MeV.

We improved the description of the readout chain for the ECal and in particular added comments about the requirements to be able to capture the maximum expected deposited energy and also the resolution of the ADC. We hope that this clarifies the dynamic range and what is needed for HPS.

In particular, in case of the calorimeter section the achieved performance does not appear acceptable. The high noise level as well as the extremely high thresholds indicate that there is a significant improvement necessary. With such a high threshold a shower reconstruction appears impossible except one focuses on the highest energies only. Even the detected multiplicities a without meaning. Therefore, the authors should focus more consequent on a clear picture of the overall requirements, the achievements, any general limitations and the options to reach the final goals. In that case the complex work would become more valuable for an external reader.

ANSWER
Parts of the test run performance are indeed undesirable for the HPS experiment; the dead channel count, noise level, and energy resolution were all substandard. Despite those facts, the Ecal performance was acceptable to provide a trigger for the Test Run and reliably measure normalized trigger rates.

The number of non-functioning channels (reasons listed in the paper) is much less than desirable for triggering efficiently on A' in HPS. It has already been improved by installing bigger APDS, modified amplifiers, and new HV distribution for all the crystals in the detector. The new readout chain (new APDs and preamplifiers) show noise levels of about 7.5MeV bringing thresholds down to closer to 10MeV. Simulations show that with a wel- calibrated detector the Ecal esolution will about 3.6% in HPS.

The A' trigger is relatively insensitive to the energy resolution as most of the rejection comes from combined kinematic cuts and time coincidence. Even the simple calibration procedures applied in the Test Run and the relatively high noise in the system were sufficient for Test Run triggering. The 4.5% energy resolution goal was predicated not on trigger-ability, but the desire to use the Ecal to improve on the SVT's measurement of the momentum of electrons and positrons, and so improve on the HPS invariant mass resolution.

We have edited the paper pointing out the requirements of the ECal in the Sec. 5 and added further explanations in the ECal performance section 7.2.

Reviewer #2
The paper describes in considerable technical detail a test experiment for the Heavy Photon Search (HPS) at Jefferson Lab.
The paper is well-written, comprehensive, and gives a very detailed technical description of the apparatus, results, and
prospects for the data taking run.  I recommend that it be published with the following suggestion:

The details of the HPS experiment are not provided clearly.  From other sources , I understand that HPS proposes to scatter
an electron beam from a tungsten target and that the A' would be generated in the scattering.  The test run here used a photon
beam generated from conversion in a gold foil. I suggest that the process to be measured in the HPS experiment (projectile and target) 
be clearly specified at the beginning of the paper.

ANSWER
We have updated the introduction with more information to better explain the HPS experiment, and the differences between the Test Run and HPS. Hopefully this also clarifies the purpose of the Test Run and the relevance of its performance to HPS.

### 2014-10-24 hps-testrun-nim.tex
Comments from Tim

@@
 
-% \linenumbers
+ %\linenumbers
 
@@
 radiation dose approaches $10^{15}$~electrons/cm$^2$/month, or roughly 
-$3 \times 10^{14}$~\fluenceunit{}/month~\cite{Rashevskaya:2002nd}, 
+$3 \times 10^{13}$~\fluenceunit{}/month~\cite{Rashevskaya:2002nd}, 
 requiring the sensors to be actively cooled. 
@@
 from beam electrons undergoing multiple scattering in the target. These background hits are rejected by  
-requiring the time reconstruction of each hit to be better than 2~ns.
+requiring reconstruction of the hit time relative to the trigger with 2~ns resolution.
 
@@
 of 2~ns for S/N$\approx$25~\cite{Friedl:2009zz}.  For electron beam running, six-sample readout and 
-the shortest possible shaping time (35~ns) is used to best distinguish hits that overlap in time.
-The APV25 ASICs are hosted on simple FR4 hybrid readout boards, outside the tracking volume, with a 
-short twisted-pair pigtail cable to provide power and configuration and signal readout. Along with a 
+the shortest possible shaping time (35~ns) are used to best distinguish hits that overlap in time.
+The APV25 ASICs are hosted on simple FR4 hybrid readout boards outside the tracking volume with a 
+short twisted-pair pigtail cable to provide power, configuration, and signal readout. Along with a 
 single sensor, these are glued to a polyimide-laminated carbon fiber composite backing making 
@@
 covering the SVT \Aprime{} 
-acceptance and able to measure the energy and positions of electrons and positrons with energy between
-$0.5$ and $\approx$4~GeV. It needs granularity and signal 
-readout speed to handle 1~MHz/cm$^{2}$ of electromagnetic background and radiation hardness. 
+acceptance and the ability to measure the energy and positions of electrons and positrons with energy between
+0.5 and 6.6~GeV. It needs granularity and signal 
+readout speed to handle 1~MHz/cm$^{2}$ of electromagnetic background as well as good radiation hardness. 
 Even modest energy resolution is adequate for triggering. HPS requires better 
@@
 Each channel on the FADC board has an independent data path to send 5-bit pulse energy and 3-bit 
-pulse arrival time information every 32~ns to a trigger processing board (CTP), which is in the same 
+pulse arrival time information every 32~ns to a Crate Trigger Processor board (CTP), which is in the same 
 crate. The 3-bit pulse arrival time allows the trigger to know the pulse timing at 4~ns resolution. 
@@
 The CTP only accepts clusters with the locally highest energy 3x3 window to deal with overlapping and 
-very large clusters. The sub-system board (SSP) receives the clusters from the top and bottom half CTP 
+very large clusters. The Sub-System Processor board (SSP) receives the clusters from the top and bottom half CTP 
 at a maximum rate of 250~MHz and searches for pairs of clusters in an 8~ns wide coincidence window. The 
@@
 
-During the HPS Test Run, for the most part the trigger system 
-required only a single cluster in either the top or bottom ECal halves. It was tested to trigger rates 
-above 100~kHz by lowering thresholds.
+During most of the HPS Test Run, the trigger system 
+required only a single cluster in either the top or bottom ECal halves resulting in rates below 2~kHz. However, 
+the trigger system was tested to rates above 100~kHz by lowering thresholds.
 
@@
 Data Processing Module (DPM), that is realized on an ATCA front board called the Cluster On Board 
-(COB), see Figure~\ref{fig:cob}.
+(COB), as shown in Figure~\ref{fig:cob}.
  \begin{figure}[]
@@
 In order to minimize cable length for the analog APV25 ASIC output signal the ATCA crate was located 
-approximately 1~m from the beam line, next to our cable vacuum feed-throughs.   
+approximately 1~m from the beam line, next to the cable vacuum feed-throughs.   
 Before shielding with lead-blankets and borated polyethylene was arranged, we observed two failures of normally reliable ATCA 
@@
 the APV25 ASIC pulse shaping time to 35~ns will also improve time resolution. 
-These results show that we can operate with the six sample readout mode of the APV25 ASIC and 
+These results show that HPS can operate with the six sample readout mode of the APV25 ASIC and 
 achieve time resolution adequate for pileup rejection during electron running in HPS. 
@@
 thicknesses are used to study the varying multiple Coulomb scattering contribution (pair production 
-angular distribution is constant), and are compared with Geant4~\cite{Agostinelli2003250} standard multiple 
-scattering model and EGS5~\cite{egs5}. 
+angular distribution is constant).  These rates are compared with those predicted by the standard Geant4~\cite{Agostinelli2003250} approximation for multiple 
+scattering and the more accurate model used by EGS5~\cite{egs5}. 
 %\begin{center}

### 2015-02-02 hps-testrun-nim.tex
Changes made to final published version.

@@
 
-\title{The Heavy Photon Search Test Detector}
+\title{The Heavy Photon Search test detector}
 %\title{
@@
 %% keywords here, in the form: keyword \sep keyword
-silicon \sep microstrip \sep tracking  \sep vertexing \sep heavy photon \sep dark photon  \sep electromagnetic calorimeter
+silicon \sep tracking  \sep vertexing \sep heavy photon \sep dark photon  \sep electromagnetic calorimeter
 %% MSC codes here, in the form: \MSC code \sep code
@@
 
-\section{Detector Overview}
+\section{Detector overview}
 \label{detector}
@@
 
-\section{The HPS Test Run Beamline}
+\section{The HPS Test Run beamline}
 Since an electron beam was unavailable, the HPS Test Run detected the electrons and positrons 
@@
 
-\subsection{Signal Readout}
+\subsection{Signal readout}
 \label{sec:fadc}
@@
 
-\section{Trigger and Data Acquisition}
+\section{Trigger and data acquisition}
 \label{sec:triggerdaq}
@@
 
-\subsection{Trigger System}
+\subsection{Trigger system}
 \label{sec:trigger}
@@
 
-\subsection{SVT Data Acquisition}
+\subsection{SVT data acquisition}
 \label{sec:svt_daq}
@@
 
-\subsection{General Data Acquisition and Online Computing}
+\subsection{General data acquisition and online computing}
 \label{sec:daq}
@@
 
-\section{Reconstruction and Performance}
+\section{Reconstruction and performance}
 
@@
 
-\subsection{SVT Performance}
+\subsection{SVT performance}
 
@@
 
-\subsubsection{Cluster and Hit Reconstruction}
+\subsubsection{Cluster and hit reconstruction}
 Track reconstruction in the SVT puts stringent requirement on the clustering and hit reconstruction. The 
@@
 
-\subsubsection{Momentum and Vertexing Resolution}
+\subsubsection{Momentum and vertexing resolution}
 Good track reconstruction performance is crucial to HPS. Simulations show that track momentum resolution 
@@
 
-\subsection{ECal Performance}
+\subsection{ECal performance}
 \label{sec:ecal_calibration}
@@
 
-\subsection{Trigger Performance}
+\subsection{Trigger performance}
 As described above in Sec.~\ref{sec:triggerdaq}, the energy from each crystal is determined slightly 
@@
 
-\subsection{Trigger Rate Comparisons}
+\subsection{Trigger rate comparisons}
 Trigger rates observed in the HPS Test Run are dominated by \ee{} pairs produced in the 
@@
 
-\section{Summary and Outlook}
+\section{Summary and outlook}
 The HPS Test Run experiment, using a simplified version of the apparatus planned for the full HPS 
@@
 
-This work has been supported by the US Department of Energy, 
+Work supported by the U.S. Department of Energy under contract number DE-AC02-76SF00515, 
 the National Science Foundation,  
@@
 Italian Istituto Nazionale di Fisica Nucleare. 
-Rouven Essig is supported in part by the Department of Energy Early Career research program DESC0008061and by a Sloan Foundation Research Fellowship.
-Authored by Jefferson Science Associates, LLC under U.S. DOE Contract No. DE-AC05-06OR23177.
+Rouven Essig is supported in part by the Department of Energy Early Career research program 
+DESC0008061and by a Sloan Foundation Research Fellowship. Authored by Jefferson Science 
+Associates, LLC under under U.S. Department of Energy contract No. DE-AC05-06OR23177.
 
